### 2020-03-02 draft_ABP.tex
Initial Overleaf Import

\documentclass[hidelinks,12pt]{article}
\pdfoutput=1
\usepackage{epsfig,amsfonts,amssymb}

\usepackage{comment}
\input epsf.sty
\topmargin -.1cm
\textheight 21cm
\oddsidemargin 0.15cm 
\textwidth 14cm
\usepackage{cite}
\usepackage{epsfig,amssymb,euscript,xspace,xcolor}
\usepackage{amsmath,mathtools,empheq,amsthm,hyperref,graphicx}
\usepackage{mathrsfs,float}  
\usepackage{pgf,tikz,pgfplots}
\usetikzlibrary{arrows}
\usepackage[T1]{fontenc} 
\usepackage{tikz,caption,subcaption,marvosym} 
\usetikzlibrary{decorations.markings,arrows,snakes}
\usepackage[belowskip=-15pt,aboveskip=0pt]{caption}
\usepackage[skip=10pt]{caption} % example skip set to 2pt
\usepackage{comment}

\usepackage[utf8]{inputenc}

\usepackage[titles]{tocloft}
\renewcommand{\cftdot}{} %Don't want dots in TOC

\definecolor{lightblue}{rgb}{.1,.4,.5}
\definecolor{brown1}{rgb}{.64,.43,.138}

\usepackage{hyperref,cite}
\hypersetup{linktocpage, colorlinks=true,linkcolor= blue,citecolor=blue,urlcolor=lightblue}

\newcommand{\hab}{}

\newcommand{\pii}{\pi}

\newcommand{\vq}{\xi}

\newcommand{\tree}{}

\newcommand{\epk}{\epsilon^{\mu\nu}p_{\nu}k^{\rho}k^{\sigma}}
\newcommand{\epkl}{(p. k)\epsilon^{\mu\rho}k^{\sigma}}
\newcommand{\epkll}{\epsilon^{\mu\rho}p_{\rho}k^{\nu}k^{\sigma}}
\newcommand{\epklll}{\epsilon^{\mu\nu}p_{\rho}k^{\rho}k^{\sigma}}

\textwidth 16.9cm
\oddsidemargin -.25cm

\def\ZZZ{{\hbox{ Z\kern-1.6mm Z}}}
\def\RRR{{\hbox{ R\kern-2.4mm R}}}
\def\CCC{{\hbox{ C\kern-2.0mm C}}}
\def\zzz{{\hbox{z\kern-1mm z}}}
\def\eee{e}

\newcommand{\ten}{{(10)}}
\newcommand{\bet}{{( b )}}

\newcommand{\qq}{k}
\newcommand{\pp}{l}
\newcommand{\nn}{\nonumber \\ }

\newcommand{\vt}{\vartheta}

\newcommand{\vtau} {\vec \tau}
\newcommand{\vj} {\vec J}
\newcommand{\vxi} {\vec \xi}
\newcommand{\vu} {\vec u}
\newcommand{\htau} {\vec \eta}
\newcommand{\vc}{\vec\chi}
\newcommand{\vpsi} {\vec \psi}

\newcommand{\qeq}{{\hbox{=\kern-2.3mm ? \kern.5mm }}}
\renewcommand{\qeq}{=}
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=2pt] (char){#1};}}

\newcommand{\rrho}{r}
\newcommand{\bA}{{\bf A}}
\newcommand{\tx}{\wt x}
\newcommand{\bG}{{\bf G}}
\newcommand{\bF}{{\bar F}}
\newcommand{\bbb}{{\bar b}}
\newcommand{\gam}{\tau}
\newcommand{\eps}{\epsilon}
\newcommand{\vareps}{\varepsilon}
\newcommand{\ra}{\rangle}
\newcommand{\la}{\langle}
\newcommand{\T}{\chi_{T}(k)}
\newcommand{\Tm}{\chi_{T}(k')}
\newcommand{\Cn}{{\cal C}_n}
\newcommand{\vp}{\varphi}
\newcommand{\ve}{\varepsilon}
\newcommand{\tl}{\lambda}
\newcommand{\dt}{(\vec \nabla T)^2}
\newcommand{\hp}{{\wh\Phi}}
\newcommand{\hq}{{\wh Q_B}}
\newcommand{\he}{{\wh\eta_0}}
\newcommand{\ha}{{\wh{A}}}
\newcommand{\lllb}{\Bigl\langle\Bigl\langle}
\newcommand{\rrrb}{\Bigr\rangle\Bigr\rangle}
\newcommand{\tf}{\wt f}
\newcommand{\sss}{{\cal L}_{av}}
\newcommand{\bx}{\bar x}
\newcommand{\bw}{\bar w}
\newcommand{\ws}{{\wt\sigma}}
\newcommand{\wrh}{{\wt\rho}}
\newcommand{\wv}{{\wt v}}

\newcommand{\bJ}{{\bf J}}

\newcommand{\vv} {\bar v}
\newcommand{\uu} {\bar u}

\newcommand{\K}{{\rm K_1}}
\newcommand{\Kt}{{\rm \widetilde K_1}}

\newcommand{\B}{b'}
\newcommand{\C}{c\,'}
\newcommand{\bB}{\bar b'}
\newcommand{\Bu}{B_{\vec u}}
\newcommand{\VV}{{\cal V}}
\newcommand{\BB}{{\cal B}}
\newcommand{\DD}{{\cal D}}
\newcommand{\BBB}{{\cal B}}
\newcommand{\II}{{\cal I}}
\newcommand{\AAA}{{\cal A}}
\newcommand{\GG}{{\cal G}}
\newcommand{\KK}{{\cal K}}
\newcommand{\fff}{{\bf f}}
\newcommand{\ccc}{{\bf c}}
\newcommand{\FF}{{\cal F}}
\newcommand{\JJ}{{\cal J}}
\newcommand{\HH}{{\cal H}}
\newcommand{\MM}{{\cal M}}
\newcommand{\CC}{{\cal C}}
\newcommand{\bC}{{\bf C}}
\newcommand{\OO}{{\cal O}}
\newcommand{\QQ}{{\cal Q}}
\newcommand{\PP}{{\cal P}}
\newcommand{\EE}{{\cal E}}
\newcommand{\LL}{{\cal L}}

\newcommand{\XX}{{\cal X}}

\newcommand{\rrr}{\rangle\rangle}
\newcommand{\half}{{1\over 2}}
\newcommand{\wt}{\widetilde}
\newcommand{\wh}{\widehat}
\newcommand{\wc}{\wt}
\newcommand{\wb}{\bar}
%\newcommand{\bd}{\bar{\rm D}}
\newcommand{\RR}{{\cal R}}
\newcommand{\NN}{{\cal N}}
\newcommand{\TT}{{\cal T}}
\newcommand{\bg}{\bar g}
\newcommand{\ba}{\bar a}
\newcommand{\bc}{\bar c}
\newcommand{\bd}{\bar d}
\newcommand{\bb}{\bar b}
\newcommand{\bT}{\bar \Theta}
\newcommand{\SSS}{{\cal S}}
\newcommand{\tlx}{\left(\tilde \lambda ; X^0(0) \right)}
\newcommand{\al}{\alpha}

\newcommand{\tk}{\tilde \kappa}

%\newcommand{\gcd}{{\rm gcd}}
\newcommand{\ppp}{\prime\prime}

\newcommand{\omk}{\omega_n(\vec k)}
\newcommand{\onk}{\omega^{(N)}_{\vec k_\perp}}
\newcommand{\tI}{\wt\II}
\newcommand{\hI}{\wh\II}
\newcommand{\nI}{\II}

\newcommand{\cp}{\check\Phi}
\newcommand{\cps}{\Psi}
\newcommand{\crh}{\check\rho}
\newcommand{\cs}{\check\sigma}
\newcommand{\cv}{\check v}
\newcommand{\com}{\check\Omega}

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ben}{\begin{eqnarray}\displaystyle}
\newcommand{\een}{\end{eqnarray}}

\newcommand{\refb}[1]{(\ref{#1})}
\newcommand{\p}{\partial}
\newcommand{\sectiono}[1]{\section{#1}\setcounter{equation}{0}}
\newcommand{\subsectiono}[1]{\subsection{#1}\setcounter{equation}{0}}

\newcommand{\zet}{\zeta}

\newcommand{\gsim}{\stackrel{>}{\sim}}
\newcommand{\lsim}{\stackrel{<}{\sim}}

\newcommand{\Lamb}{\Lambda}

\newcommand{\ia}{i}
\newcommand{\ja}{j}

%\renewcommand{\vec}{}

\def\one{{\hbox{ 1\kern-.8mm l}}}
\def\zero{{\hbox{ 0\kern-1.5mm 0}}}

\def\wa{{\wh a}}
\def\wb{{\wh b}}
\def\wc{{\wh c}}
\def\wc{\check}
\def\wdd{{\wh d}}

\newcommand{\bi}{{\bf i}}

\renewcommand{\theequation}{\thesection.\arabic{equation}}
\renewcommand{\theequation}{\arabic{equation}}

\newcommand{\bea}[1]{\begin{eqnarray}\label{#1} }
\newcommand{\eea}{\end{eqnarray}}

\newcommand{\wJ}{\wt J}
\newcommand{\bN}{{\bf N}}

\newcommand{\aaa}{b}

%\newcommand{\eqref}{\refb}

\newcommand{\un}{{\rm u}}

\newcommand{\dotalpha}{{\dot{\alpha}}}

\newcommand{\dotbeta}{{\dot{\beta}}}

\newcommand{\dotgamma}{{\dot{\gamma}}}

\newcommand{\dalpha}{\beta}

\newcommand{\Vm}{V}

\newcommand{\gb}{G}

\newcommand{\q}{e}

\newcommand{\PPP}{{\cal P}}

%\newcommand{\gold}{\VV_{\rm goldstino}}

\newcommand{\gold}{\VV_{\rm G}}

%\newcommand{\goldc}{\VV^c_{\rm goldstino}}

\newcommand{\goldc}{\VV^c_{\rm G}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CAN BE DELETED AT THE END %%%%%%%%%%

\usepackage{bm}
%\usepackage[table]{xcolor}
%\def\rpnote#1{{\color{magenta} #1}}
%\def\arnote#1{{\color{blue} #1}}
%\def\asnote#1{{\color{red} #1}}

\newcommand{\bM}{{\bf M}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%TO ADD A COMMENT WRITE \arnote{} %%%%%

\newcommand{\scalar}{\VV_{\rm S}}

\newcommand{\wscalar}{\wt\VV_{\rm B}}

\newcommand{\fermion}{\VV_{\rm F}}

\newcommand{\wfermion}{\wt\VV_{\rm F}}

\newcommand{\wts}{\wt\Sigma}

\newcommand{\wtsp}{\wt\Sigma^c}

\newcommand{\four}{(4)}

\newcommand{\cL} {\{\hskip -4pt\{}
\newcommand{\cR} {\}\hskip -4pt\}}
\newcommand{\sL} {[\hskip -1.5pt[}
\newcommand{\sR} {]\hskip -1.5pt]}
\newcommand{\oR}{{\overline{\RR}}}

\def\bj{{\bf j}}

\def\asnote#1{{\color{magenta}#1}}

\def\asnotea#1{{\color{orange}#1}}

\def\asnote#1{{\color{black}#1}}
\def\asnotea#1{{\color{black}#1}}

\newcommand{\mmu}{\mu}

\newcommand{\f}{\frac}

\newcommand{\non}{\nonumber}

\setlength{\intextsep}{10pt plus 2pt minus 2pt}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\def\be{\begin{equation}}
\def\ee{\end{equation}}

\newcommand{\drm}{\mathrm{d}}
\newcommand{\der}[2]{\frac{\drm #1}{\drm #2}}
\newcommand{\cross}{\times}
\newcommand{\del}{\vec{\nabla}}
\newcommand{\pd}{\partial}
\newcommand{\prd}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\dv}{\delta\hspace{-2pt}}
\newcommand\veps{\varepsilon}
\newcommand\vphi{\varphi}
%\newcommand{\com}[2]{[#1,\, #2]}
\newcommand{\tr}{\text{Tr }}
\newcommand{\td}{\text{d}}

\definecolor{wvvxds}{rgb}{0.396078431372549,0.3411764705882353,0.8235294117647058}
\definecolor{dbwrru}{rgb}{0.8588235294117647,0.3803921568627451,0.0784313725490196}
\definecolor{dtsfsf}{rgb}{0.8274509803921568,0.1843137254901961,0.1843137254901961}
\definecolor{wrwrwr}{rgb}{0.3803921568627451,0.3803921568627451,0.3803921568627451}
\definecolor{cqcqcq}{rgb}{0.7529411764705882,0.7529411764705882,0.7529411764705882}
\definecolor{rvwvcq}{rgb}{0.08235294117647059,0.396078431372549,0.7529411764705882}
\makeatletter
\newenvironment{calc}{\allowdisplaybreaks\start@align\@ne\st@rredtrue\m@ne}
{\addtocounter{equation}{1}\tag{\theequation}\endalign}
% for calculations/derivations---only last line gets an equation number, 
%	and allows page breaks for long calculations

\newenvironment{multeq}
{\incr@eqnum
	\mathdisplay@push
	\st@rredfalse\global\@eqnswtrue
	\mathdisplay{equation}
	\let\@testopt\alignsafe@testopt
	\aligned@a}
{\crcr
	\egroup
	\restorecolumn@
	\egroup
	\endmathdisplay{equation}
	\mathdisplay@pop
	\ignorespacesafterend
}
% Should be equivalent to 
% \begin{equation}\begin{split} ... \end{split}\end{equation}
% use for multiline equations/multiple equations that should get a single
% equation number, _centered_.
% Note I don't think page breaks work with this construction.
\makeatother

\DeclareMathOperator\sech{sech}
\DeclareMathOperator\csch{csch}
\newcommand\AdS{$AdS_3$\xspace}
\newcommand\re{\mathbb{R}}
\newcommand\sacomment[1]{\textcolor{blue}{[\textit{SA: #1}]}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\addtolength{\topmargin}{-2cm} 
%\addtolength{\textheight}{2.5cm}
\addtolength{\oddsidemargin}{-0.5cm} 
\addtolength{\textwidth}{1.cm}
%\addtolength{\footskip}{0.7cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newtheorem{identity}{Identity}[section]

\begin{document}

\baselineskip 24pt

\begin{center}

{\Large \bf  Binary geometries: Associahedra, Cyclohedra and Generalized Permutahedra}

\end{center}

\vskip .5cm
\medskip

\vspace*{4.0ex}

\baselineskip=15 pt

\centerline{\large \rm  {\bf Song He$^{a, b}$, Zhenjie Li$^{a, b}$, Prashanth Raman$^{a, c,d}$, Chi Zhang$^{a, b}$ } }

\vspace*{4.0ex}
{\it ~ $^a$ CAS Key Laboratory of Theoretical Physics, Institute of Theoretical Physics, Chinese Academy}

{\it of Sciences, Beijing 100190, China}

{\it ~$^b$ School of Physical Sciences, University of Chinese Academy of Sciences, No.19A Yuquan Road,}

{\it Beijing 100049, China}

{\it ~$^c$ Institute of Mathematical Sciences, Taramani, Chennai 600 113, India}

{\it ~$^d$ Homi Bhabha National Institute, Anushakti Nagar, Mumbai 400085, India}

\vspace*{1.0ex}
\centerline{\it ~E-mail : songhe@itp.ac.cn, lizhenjie@itp.ac.cn, prashanthr@imsc.res.in, zhangchi@itp.ac.cn} 
\vspace*{5.0ex}
\centerline{\bf Abstract} \bigskip

In \cite{} the study of stringy canonical forms and binary geometries with ``perfect'' u equations, associated with the scattering of particles and strings was initiated. In this paper we continue the study of binary geometries and find two large classes of new examples.  The first class corresponds to degenerations of $A_n$ and $B_n$ (associahedra and cyclohedra respectively) which have perfect $u$-equations. The second class corresponds to a large subset of  generalized permutahedra which can be realised as degenerations of the permutahedron $P_n$ which are binary positive geometries despite not having perfect $u$-equations. Both these large classes of examples have stringy integrals which factorise at any  finite $\alpha^{'}$  on all the massless poles.

\vfill \eject

\baselineskip=18pt

\tableofcontents

\newpage
\section{Introduction}
In \cite{} the notions of stringy canonical forms and binary geometries were introduced which helped in understanding the configuration spaces of clusters as generalisations of moduli space for scattering of particles and strings .

It is a natural question to ask if binary geometries whose stringy integrals factorise at any finite $\alpha'$ are extremely special and are associated to only the classical $A_n, B_n, C_n,D_n$ or  Exceptional $E_6, E_7, E_8, F_2, G_4$  type clusters  as discussed in \cite{}. In this paper we answer this question in the negative by providing infinitely many counter examples. These fall broadly into two classes, the first of which corresponds to the permutahedron $P_n$ and more generally generalised permutahedra which do not have perfect $u$-equations but are still binary. The second class corresponds to various degenerations of the associahedra and cyclohedra which are binary geometries with perfect $u$-equations. In both these cases the configuration space can be realised as hyperplane arrangements and we discuss how this allows to understand why some degenerations give us binary geometries with perfect $u$-equations while others do not.

\subsection{Invitation: stringy canonical forms and cluster configuration spaces}

{\bf review of stringy canonical forms, mention big polytopes and $u$ variables in general; then specify to cluster string integrals, then cluster configuration spaces with perfect $u$ equations, do $A_n$, $B_n$ examples; define "binary geometries"}

(stringy canonical form)

The $\mathcal I(\mathbf X,\{c\})$ is convergent when $\mathbf X$ is contained inside
the Minkowski sum $\mathcal P=\sum_I c_I \mathcal P_I$ of Newton polytopes 
$\mathcal P_I=\mathbf N[p_I]$. For a facet $F_a$ of $\mathcal P$, this condition 
requires that $\mathbf X$ should lay on one side of $F_a$ which is equivalent to 
an inequality of variables $\mathbf S=(-X_1,\dots,-X_d,c_1,\dots,c_m)$, 
$W_a^JS_J\geq 0$, where $W_a^J$ is determined by the facet $F_a$. 
These inequalities cut out a polyhedron in the $(d+m)$-dimensional space of $\mathbf S$,
which is called the \textit{big polyhedron} of $\mathcal P$, 
and the integral $\mathcal I(\mathbf S)$ converges for each point $\mathbf S$ 
inside this polyhedron.

Dually, we can describe the big polyhedron by its vertices. Suppose 
$\{V_J^A\}_{1\leq A\leq v}$ are its non-zero vertices, the point $\mathbf S$ inside 
the polyhedron can be written as $S_J = U_A V^A_J$ with non-nagetive coefficients 
$\{U_A\}_{1\leq A\leq v}$.  Therefore, the integral $\mathcal I(\mathbf S)$
can be seen as a function of `dual coordinates' $\{U_A\}$ which encourages us to 
rewrite the integral to make it manifest by
\[
	\mathcal I(U)=
	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
	\prod_{J}p_J^{-\alpha' S_J}
	=
	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
	\prod_{A}u_A^{\alpha' U_A},
\]
where we introduce a new set of variables $u_A = \prod_J p_J^{-V_J^A}$ for 
$A=1,\dots,v$. Note that there's no unique way to write $S_J=U_AV_J^A$ when
the big polyhedron is not a simplex, \textit{i.e.} $v>d+m$, and in this case,
$u$-variables $\{u_A\}$ are not independent. 
When the big polyhdron is a simplex, \textit{i.e.} $N=v=d+m$, where $N$ is 
the number of facets of the big polyhdron or the original polytope $\mathcal P$,
and inequalities $U_A=S_J(V^{-1})^J_A\geq 0$ are exactly the inequalities
$W_a^J S_J\geq 0$ up to resales $U_A\mapsto t U_A$ for non-zero factors $t$, because
there's no nontrivial linear isometry from the simplex to itself besides permutations
of vertices. Therefore, we identity the labal of facets $a$ with the label of 
vertices $A$ and get $V=W^{-1}$. Furthermore, every facet of the original polytope
$\mathcal P$ can be associated with a single $u_A$ going to zero, 
giving a “binary” geometry we will describe later.

(why cluster configuration space, perfect u eqs)

($A_n$ (sting integral?), $B_n$ (Shi arrangement?), or both from $F$-polynomial)

(binary geometries)

\[
	1-u_i=f_i(u)\prod_{j}u_j^{i||j}
\]
where $f_i$ are polynomials such that $f_i(\dots,u_i=0,\dots)=1$.

\newpage
\section{Stringy canonical forms and $u$-equations for generalized permutahedra}
In this section we shall argue that  a large subset of generalised permutahedra which are realised as degenerations of permutahderon $P_n$ are binary geometries. Before we proceed we shall review some details about the generalised permutahedra which we shall use throughout the paper.
\subsection{Generalized permutohedra} {\bf the definition, facets and combinatorial factorizations, do $P_n$ example in full details.}

\subsection{Natural stringy integrals with linear factors}

{\bf introduce a natural stringy integrals for any generalized stringy canonical forms: variables $x_0=1, x_1, \cdots, x_n$ and define $x_I=\sum_{i \in I} x_i$, the factors are $x_I^{\alpha' S_I}$ (we can say monomials $S_\{i\}=X_i$ and polynomials $S_I=-c_I$. $N=n+m$ and big polytope is a simplex, then general formula for $u$ variables, which is equivalent to ABHY conditions; again $P_n$ in full details and others as degenerations.}

\subsection{Binary geometries and $u$ equations}

{\bf argue in general to have binary geometries we must have $1-u=\prod u' p(\{u\})$ with $p(u=0)=1$, conjecture that this is true fo ALL gen. perm. Show it for gen. perm. more examples?}

\section{Configuration spaces with perfect $u$-equations from degenerating $A_n$ and $B_n$}
In this section we shall consider some degenerations of $A_n$ and $B_n$ and show that these form an infinite class of examples of binary geometries with perfect $u$-equations. To do this we shall use the fact that both $A_n$ and $B_n$ are generalised permutahedra and can be realised as a Minkowski sum of coordinate simplices.

\subsection{$A_n$ and $B_n$ as generalized permutohedra}

{\bf linear factors, (standard) string integrals, ABHY and $u$ variables, talk about hyperplane arrangement}

\subsection{Degenerations of $A_n$ and $B_n$ with perfect $u$ equations}

{\bf things I wrote in my handwritten notes...}

*******************

\section*{Permutahedron}
 For $x_1,x_2, \cdots, x_{n+1} \in \mathbb{R} $ , the permutahedron $P_n(x_1,\cdots,x_{n+1})$ is a convex polytope in $\mathbb{R}^{n+1}$ defined as the convex hull of all vectors obtained from $(x_1,x_2, \cdots, x_{n+1})$ by permutations of the coordinates:
 \bea
 P_n(x_1,x_2, \cdots, x_{n+1}) = ConvexHull \{ (x_{w(1)},x_{w(2)}, \cdots, x_{w(n+1)})~ |~ w \in S_{n+1} \}, \nonumber
 \eea
 where $S_{n+1}$ is the symmetric group.

 The permutahedron has $(n+1)!$ vertices and is of dimension at most $n$ since it lies in the hyperplane 
 \bea
 H_c= \{(t_1,t_2, \cdots, t_{n+1}) | t_1 + t_2 + \cdots + t_{n+1}= c \} \subset \mathbb{R}^{n+1}, \nonumber
 \eea
where $c= x_1+x_2+ \cdots +x_{n+1}$

For $n=2$ and distinct $x_1,x_2, x_3$ the permutahedron $P_2(x_1,x_2, x_3)$ is a hexagon. If two of the $x_i$'s are equal then the permutahedron degenerates into a triangle and if $x_1= x_2 = x_3$ then its degenerates into a single point.

We shall state a few results about permutahedra:

{\bf Rado's theorem}: For any $x_1 \ge x_2  \cdots \ge x_{n+1}$ a point $(t_1,t_2, \cdots, t_{n+1}) \in \mathbb{R}^{n+1}$ belongs to the permutahedron $P_n(t_1,t_2, \cdots, t_{n+1})$ if and only if 
\bea
t_1+ \cdots +t_{n+1} = x_1 +\cdots+ x_{n+1} \nonumber
\eea
and for any nonemepty subset $\{i_1,\cdots,i_k \} \subset \{1,\cdots, n+1 \}$, we have 
\bea
t_{i_1}+ \cdots +t_{i_k} \leq x_1 +\cdots+ x_k \nonumber
\eea
The combinatorial structure of the permutahedron $P_n (x_1, \cdots, x_{n+1}) $ does not depend on $ x_1, \cdots, x_{n+1} $ as long as all these are distinct.

{\bf Proposition 2}: For any  $x_1> \cdots > x_{n+1} $. The $d$-dimensional faces of $P_n ( x_1, \cdots, x_{n+1 })$ are in one-to-one correspondence with the disjoint subdivisions of the corresponding set $\{x_1,\cdots, x_{n+1 }\}$ into nonempty ordered blocks $B_1 \cup B_2 \cup \cdots \cup B_{n+1-d} =\{1,\cdots,n+1 \}$. The face corresponding to $B_1,\cdots, B_{n+1-d}$ is given by the $n+1-d$ linear equations 
\bea
\sum_{i \in B_1\cup \cdots \cup B_k} t_i = x_1 + \cdots +x_{| B_1 \cup \cdots \cup B_k |}, ~~~ for~ k=1,\cdots,n+1-d \nonumber
\eea 
\section*{Generalized permutahedra}
Generalized permutahedra are polytopes which are deformations of the usual permutahedron i.e., obtained by moving the vertices of the usual permutahedron so that the directions of all the edges are preserved though some of the edges may degenerate into points.

 Since each generalised permutahedron is obtained by parallel translation of facets of the usual permutahedron it is parametrized  by a collection $\{ z_I\}$ of $2^{n+1}-1$ coordinates, for non-empty sets of $I \subset [n+1] := \{1,\cdots,n+1 \}$
 \bea
 P_n^z(\{ z_I \}) = \left \{ (t_1, t_2, \cdots , t_{n+1}) \in \mathbb{R}^{n+1} | \sum_{i=1}^{n+1} t_i = z_{[n+1]},~ \sum_{i \in I} t_i \geq z_I, ~for ~subsets~ I  \right  \} \nonumber
 \eea

 If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron.

 A different construction of the generalised permutahedron is the following :

 Let, $\Delta_{[n+1]} = ConvexHull(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. For any $I \subset [n+1] $ let $\Delta_I =ConvexHull(e_i~|~i\in I)$ denote the face of the $\Delta_{[n+1]}$. The polytope $P_n^y(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I \geq 0$ for all nonempty subsets $I \subset [n+1]$
 \bea
 P_n^y(\{y_I \})= \sum_{I \subset[n+1]} y_I . \Delta_I  \nonumber
 \eea
is the generalised permutahedron $P_n^z(\{z_I \})$  provided $z_I = \sum_{J \subset I} y_J  ~ for ~all~nonempty ~I \subset [n+1]$.
Note that all generalised permutahedra cannot be written as Minkowski sum of coordinate simplices and we shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation.
\section*{Nested Complex}
Since the combinatorial structure of the generalised permutahedron depends only on the set $B$ of nonemepty subsets $I \subset [n+1]$ such that $y_I \geq 0$ which is called the {\it building set}. We can describe the combinatorial structure when $B$ additionally satisfies the following:

\noindent(1) If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$. \\
(2) $B$ contains all singletons $\{ i\}$ for $i \in S$.

A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:\\
\noindent
(1) For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.\\
(2) For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B. \\
(3) N contains all maximal elements of $B$.

The {\it nested complex} $\mathcal{N}(B)$ is defined as the poset of the set of all nested sets in $B$ ordered by inclusion.

{\bf Theorem 1}: Let us assume that the set $B$ associated with a generalised permutahedron $P_n^{y}$ is a building set on $[n+1]$. Then the poset of faces $P_n^{y}$ ordered by reverse inclusion is isomorphic to the nested complex $\mathcal{N}(B)$.

{\bf Theorem 2}: Let us assume that the set $B$ associated with a generalised permutahedron $P_n^{y}$ is a building set on $[n+1]$. The face $P_N$ of $P_n^{y}(y_I)$ associated with the nested set $N \in \mathcal{N}(B)$ is given by:
\bea
P_N = \left \{ \right (t_1,\cdots,t_{n+1}) \in \mathbb{R}^{n+1} | \sum_{i \in I} t_i =y_{I}~for~I \in N; ~ \sum_{i \in J}t_i \geq y_J, for J \in B  )\}
\eea
In particular the dimension of the face $P_N$ equals $n+1-|N|$.

In summary the above results imply that we can look at any collection of subsets of $[n+1]$ which form a building set $B$ and associate  coordinate simplex $\Delta_I$ for each $I \in B$ and resulting Minkowski sum with positive weights $y_I$ generates a generalised permutahedron associated with the building set. Further, the number of facets of the generalised permutahedron just correspond to the set of all non-singlet elements in $B$.  
We shall use $ \{0,1,\cdots,n \}$ instead of $[n+1]$ with $x_0 =1$ from now on. Since, the number of singlets correspond to the dimension of the generalised permutahedron this implies that:

{\bf Number of facets = Number of linear equation + dimension of  gen permutahedron}

Thus, generalised permutahedra have "Big Polytope" which correspond to a simplex and we can write down the stringy canonical forms and solve for the $u$-variables and examine if they satisfy some kind of $u$-equations.

Here are some interesting examples of generalised permutahedra:

(1) If $B$ consists of only singlets i.e., $B=\{ \{ 0,1,\cdots,n \}, \{ 0 \},\{ 1 \},\cdots ,\{ n \} \}$ then the generalised permutahedron is a Simplex. In this case the relevant $x$ variables are $x_i,~ i=0,\cdots,n$ and $\sum_{i=0}^n x_i$. 
The Newton polytope of the Minkowski sum is $\prod_{i=1}^{n} x_i (1+\sum_{j=1}^{n} x_j)$ and $u$-variables are 
$u_i =\frac{ x_i}{1+\sum_{i=1}^n x_i} $
which satisfy $\sum u_i =1$ as their only $u$-equation. \\

(2) If $B= \{[i] | i=1,\cdots,n+1 \}$ is the complete flag of intervals, then $P_n({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
The Newton polytope of the Minkowski sum is $x_1\cdots x_n (1+x_1) \cdots (1+x_1+\cdots +x_n)$ and $u$-variables are 
$u_i =\frac{ 1}{1+\sum_{j=1}^{i} x_j} $, ~~$u^{'}_i =\frac{ \sum_{j=1}^{i} x_j}{1+\sum_{j=1}^{i} x_j} $ for $j=1,\cdots,n$ \\
which satisfy $u_i +u^{'}_{i} =1$ as their $u$-equation. \\

(3) If $B$ corresponds to all the non empty subsets of $\{0,1,\cdots,n \}$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then $P_n({\bf Y})$ is the usual permutahedron $P_n$.

\section*{ABHY like realisation for the Permutahedron}
The following set of equations to define the $n$-dimensional Permutahedron: 
\bea
C_I = (-1)^{|I|} \left( \sum_{i \in I} X_i - \sum _{{i<j}\atop{i,j \in I}} X_{ij} +\cdots + (-1)^{|I|}  X_I \right) \nonumber
\eea
for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $X_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.

It is clear that
\bea
m= \text{No. of  C's }&=& 2^{n+1}-(n+2) \nonumber \\
N= \text{No. of X's} &=& 2^{n+1}- 2 \nonumber 
\eea
Thus we see that $N= d+m$ and hence the "Big polytope" in this case is again a simplex. We can write down the stringy integral as usual to be 
\bea
\int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} d x_i x_i^{\alpha^{'} X_i -1} \prod_{I} \left (\sum_{a\in I} x_a \right) ^{-\alpha^{'} C_I} \nonumber
\eea 
where the product is over all non-singlets $ I \subset \{0,1,\cdots,n\}$ with $x_{0} =1$.

We can then solve for the corresponding $u's$ :
\bea
u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber \\
u^{'}_J &=& \prod_{{0 \in I}\atop{ \{0,\cdots,n\} - I \subset J}} x_I^{(-1)^{|I|-|J|+\color{red}{mod(n, 2)}}} \nonumber
\eea

\section*{2d permutahedron}
In this case the building set $B=\{ \{ 0,1,2\},\{ 0,1\},\{0,2\},\{1,2\},\{0\},\{1\},\{2\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y, ~x_{01}=1+x, ~x_{02}=1+y,~ x_{12}=x+y,~ x_{012}=1+x+y$.

We can write down the Newton polynomial for the Minkowski sum as $ x_1~ x_2~(1+x_1)~(1+x_2)~(x_1+x_2)~(1+x_1+x_2)$.

The $u$-variables can be written in terms of $x$ variables as:
\bea
u_1&=&\frac{x(1+x+y)}{(x+y)(1+x)}, ~ u_2 =\frac{y(1+x+y)}{(x+y)(1+y)},~ u_{12}=\frac{(x+y)}{(1+x+y)}\nonumber \\
u^{'}_1&=&\frac{(1+y)}{(1+x+y)}, ~~~~~ u^{'}_2=\frac{(1+x)}{(1+x+y)},~~~~~ u^{'}_{12}= \frac{(1+x+y)}{(1+x)(1+y)} \nonumber
\eea
The $u$-equations are:
\bea
1-u_i &=& (u^{'}_i)^2 u_j u^{'}_{12}, ~~~ 1-u_{12} = u^{'}_{1} u^{'}_{2} u^{'}_{12} \nonumber \\
1-u^{'}_i &=& u_i u^{'}_j u_{12}, ~~~~~~~ 1-u^{'}_{12} = u_{1} u_{2} (u_{12})^2 \nonumber
\eea
where $i=1$ implies $j=2$ and vice versa.
Let us look at the $n=3$ example.

\section*{3d permutahedron}
In this case the building set $B=\{ \{ 0,1,2,3\},\{ 0,1,2\},\{0,2,3\},\{0,1,3\},\{1,2,3\},\{0,1\},\{0,2\},\{0,3\},\{1,2\} \\ ,\{2,3\},\{1,3\},\{0\},\{1\},\{2\},\{3\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y, ~x_3=z, ~x_{01}=1+x, ~x_{02}=1+y,~x_{03}=1+z,~ x_{12}=x+y,~x_{13}=x+z,~x_{23}=y+z,~ x_{012}=1+x+y,~ x_{013}=1+x+z,~ x_{023}=1+y+z,~ x_{123}=x+y+z,~ x_{0123}=1+x+y+z$. \\

The $u$ and $u'$-variables can be written interms of $x$ variables as:
{\scriptsize  \bea
u_1&=&\frac{x(1+x+y)(1+x+z)(x+y+z)}{(x+y)(x+z)(1+x)(1+x+y+z)}, ~ u_2 =\frac{y(1+x+y)(1+y+z)(x+y+z)}{(x+y)(y+z)(1+y)(1+x+y+z)},~ u_{3}=\frac{z(1+x+z)(1+y+z)(x+y+z)}{(x+z)(y+z)(1+z)(1+x+y+z)},\nonumber \\
u^{'}_1&=&\frac{(1+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_2 =\frac{(1+x+z)}{(1+x+y+z)},~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_{3}=\frac{(1+x+y)}{(1+x+y+z)},\nonumber \\
u_{12}&=&\frac{(x+y)(1+x+y+z)}{(1+x+y)(x+y+z)}, ~~~~~~~~~~~~~~~~~~ u_{23} =\frac{(y+z)(1+x+y+z)}{(1+y+z)(x+y+z)},~~~~~~~~~~~~~~~~~~~ u_{13}=\frac{(x+z)(1+x+y+z)}{(1+x+z)(x+y+z)},\nonumber \\
u^{'}_{12}&=&\frac{(1+z)(1+x+y+z)}{(1+y+z)(1+x+z)}, ~~~~~~~~~~~~~~~~~~ u^{'}_{23} =\frac{(1+x)(1+x+y+z)}{(1+x+y)(1+x+z)},~~~~~~~~~~~~~~~~~~~ u^{'}_{13}=\frac{(1+y)(1+x+y+z)}{(1+x+y))(1+y+z)},\nonumber  \\
u_{123}&=&\frac{(x+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_{123} =\frac{(1+x+y)(1+y+z)}{(1+x)(1+y)(1+z)(1+x+y+z)}\nonumber
\eea }
The $u$-equations in this case are:
{\small  \bea
1-u_i &=& u_j u_k (u_{jk})^2 (u^{'}_i)^3 (u^{'}_{ij})^2(u^{'}_{ik})^2 u^{'}_{123} \left(1+ u_i u_{ij} u_{ik} u^{'}_{j} u^{'}_{k}  u^{'}_{jk}\right), ~~ 1-u_{ij} = u_k u_{ik} u_{jk} (u^{'}_i)^2 (u^{'}_{j})^2 (u^{'}_{ij})^2 u^{'}_{ik} u^{'}_{jk} u^{'}_{123} \nonumber  \\
1-u^{'}_i &=& u_i u_{ij} u_{ik} u^{'}_{j} u^{'}_{k}  u^{'}_{jk}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 1-u^{'}_{ij} = u_i u_{j}  (u_{ij})^2 u_{ik} u_{jk} (u_{123})^2 (u^{'}_{k})^2 u^{'}_{ik} u^{'}_{jk}  \nonumber \\
1-u^{'}_{123} &=& u_1 u_{2} u_{3} (u_{12})^2 (u_{23})^2  (u_{13})^2 (u_{123})^3 \left(1+ u^{'}_{123}  u^{'}_1 u^{'}_{2} u^{'}_{3} u^{'}_{12} u^{'}_{23}  u^{'}_{13} \right), 1-u_{123} = u^{'}_1 u^{'}_{2} u^{'}_{3} u^{'}_{12} u^{'}_{23}  u^{'}_{13} u^{'}_{123}   \nonumber
\eea}
where $i,j,k \in {1,2,3}$ and $i \neq j \neq k$.

The 8 facets of the 3d permutahedron corresponding to $u_i \rightarrow 0, u^{'}_i \rightarrow 0,u_{123} \rightarrow 0 ~and ~u^{'}_{123} \rightarrow 0$  are all $B_2$'s. Similarly, the 6 facets corresponding to  $u_{ij} \rightarrow 0, u^{'}_{ij} \rightarrow 0$ are all  $A^{2}_1$.

Thus, the 3d permutahedron integral factorizes nicely on all massless poles at finite $\alpha^{'}$ !!
\section*{4d permutahedron}
The $u$ variables for the 4d permutahedron are:
{\tiny
\begin{align*}
u_1&= \frac{x (w+x+1) (x+y+1) (w+x+y) (x+z+1) (w+x+z)
   (x+y+z) (w+x+y+z+1)}{(x+1) (w+x) (x+y) (w+x+y+1) (x+z) (w+x+z+1) (x+y+z+1)
   (w+x+y+z)},\nonumber \\  u_2 &= \frac{y (w+y+1) (x+y+1) (w+x+y) (y+z+1) (w+y+z) (x+y+z)
   (w+x+y+z+1)}{(y+1) (w+y) (x+y) (w+x+y+1) (y+z) (w+y+z+1) (x+y+z+1)
   (w+x+y+z)} \nonumber \\  u_3 &= \frac{z (w+z+1) (x+z+1) (w+x+z) (y+z+1) (w+y+z) (x+y+z)
   (w+x+y+z+1)}{(z+1) (w+z) (x+z) (w+x+z+1) (y+z) (w+y+z+1) (x+y+z+1)
   (w+x+y+z)},\nonumber \\ u_4 &= \frac{w (w+x+1) (w+y+1) (w+x+y) (w+z+1) (w+x+z) (w+y+z) (w+x+y+z+1)}{(w+1)
   (w+x) (w+y) (w+x+y+1) (w+z) (w+x+z+1) (w+y+z+1) (w+x+y+z)},\nonumber \\
   u_{12} &=  \frac{(x+y) (w+x+y+1) (x+y+z+1) (w+x+y+z)}{(x+y+1) (w+x+y)
   (x+y+z) (w+x+y+z+1)},~u_{13} = \frac{(x+z) (w+x+z+1) (x+y+z+1) (w+x+y+z)}{(x+z+1) (w+x+z)
   (x+y+z) (w+x+y+z+1)},\nonumber \\ ~ u_{14} &= \frac{(w+x)(w+x+y+1) (w+x+z+1) (w+x+y+z)}{(w+x+1) (w+x+y) (w+x+z) (w+x+y+z+1)}, u_{24} = \frac{(w+y) (w+x+y+1) (w+y+z+1) (w+x+y+z)}{(w+y+1) (w+x+y) (w+y+z) (w+x+y+z+1)},\nonumber \\ ~u_{23} &=
   \frac{(y+z) (w+y+z+1) (x+y+z+1) (w+x+y+z)}{(y+z+1) (w+y+z) (x+y+z)(w+x+y+z+1)},~ u_{34} = \frac{(w+z) (w+x+z+1) (w+y+z+1) (w+x+y+z)}{(w+z+1) (w+x+z) (w+y+z) (w+x+y+z+1)}, \nonumber \\  
  u_{123} &= \frac{(x+y+z) (w+x+y+z+1)}{(x+y+z+1)(w+x+y+z)},~u_{134}= \frac{(w+x+z) (w+x+y+z+1)}{(w+x+z+1)(w+x+y+z)},~ u_{124}= \frac{(w+x+y) (w+x+y+z+1)}{(w+x+y+1) (w+x+y+z)},~ u_{234} = \frac{(w+y+z) (w+x+y+z+1)}{(w+y+z+1) (w+x+y+z)},\nonumber \\
    u_{1234} &= \frac{w+x+y+z}{w+x+y+z+1},\nonumber \\ u'_1&= \frac{w+y+z+1}{w+x+y+z+1},~~u'_2= \frac{w+x+z+1}{w+x+y+z+1}, u'_3=  \frac{w+x+y+1}{w+x+y+z+1},u'_4 = \frac{x+y+z+1}{w+x+y+z+1}, \nonumber \\  u'_{12} &= \frac{(w+z+1) (w+x+y+z+1)}{(w+x+z+1) (w+y+z+1)}, u'_{13} = \frac{(w+y+1) (w+x+y+z+1)}{(w+x+y+1) (w+y+z+1)},\nonumber \\  u'_{14} &= \frac{(y+z+1) (w+x+y+z+1)}{(w+y+z+1) (x+y+z+1)},u'_{23} = \frac{(w+x+1) (w+x+y+z+1)}{(w+x+y+1) (w+x+z+1)}, \nonumber \\ u'_{24}&= \frac{(x+z+1) (w+x+y+z+1)}{(w+x+z+1)(x+y+z+1)}, u'_{34}=  \frac{(x+y+1) (w+x+y+z+1)}{(w+x+y+1) (x+y+z+1)},\nonumber \\  
u'_{123} &=  \frac{(w+1) (w+x+y+1) (w+x+z+1) (w+y+z+1)}{(w+x+1) (w+y+1) (w+z+1) (w+x+y+z+1)},~u'_{124}= \frac{(z+1) (w+x+z+1) (w+y+z+1) (x+y+z+1)}{(w+z+1) (x+z+1) (y+z+1) (w+x+y+z+1)},\nonumber \\  u'_{134}&= \frac{(y+1) (w+x+y+1) (w+y+z+1) (x+y+z+1)}{(w+y+1)(x+y+1) (y+z+1) (w+x+y+z+1)},u'_{234} = \frac{(x+1) (w+x+y+1) (w+x+z+1) (x+y+z+1)}{(w+x+1) (x+y+1) (x+z+1) (w+x+y+z+1)},\nonumber \\  u'_{1234} &= \frac{(w+x+1) (w+y+1)(x+y+1) (w+z+1) (x+z+1) (y+z+1) (w+x+y+z+1)}{(w+1) (x+1) (y+1) (w+x+y+1) (z+1) (w+x+z+1) (w+y+z+1) (x+y+z+1)} \nonumber
\end{align*}
}
\newpage
\vspace*{-25pt}
The $u$ equations are 
{\tiny
{\begin{align*}
1-u_1&=u_2 u_3 u_4 u_{2,3}^2 u_{24}^2 u_{34}^2 u_{234}^4
   \left(u'\right)_1^8 \left(u'\right)_{12}^4 \left(u'\right)_{13}^4
   \left(u'\right)_{14}^4 \left(u'\right)_{123}^2
   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2 u'_{1234}+ 6~
 \textcolor{red}{  u_1^2} u_2 u_3 u_4 u_{12}^2 u_{13}^2 u_{14}^2 u_{23}^2 u_{24}^2
   u_{34}^2 u_{123}^2 u_{124}^2 u_{134}^2 u_{234}^3 u_{1234}
   u'_2 u'_3 u'_4 \left(u'\right)_1^4  \nonumber \\ &\left(u'\right)_{12}^3
   \left(u'\right)_{13}^3 \left(u'\right)_{14}^3
   \left(u'\right)_{23}^2 \left(u'\right)_{24}^2
   \left(u'\right)_{34}^2 \left(u'\right)_{123}^2
   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2
   \left(u'\right)_{234}^2 u'_{1234}+~2 ~\textcolor{red}{u_1} u_2 u_3 u_4 u_{12}
   u_{13} u_{14} u_{23}^2 u_{24}^2 u_{34}^2 u_{123} u_{124}
   u_{134} u_{234}^3 \left(u'\right)_1^4 \left(u'\right)_{12}^3
   \left(u'\right)_{13}^3 \nonumber \\ & \left(u'\right)_{14}^3 u'_{23} u'_{24}
   u'_{34} \left(u'\right)_{123}^2 \left(u'\right)_{124}^2
   \left(u'\right)_{134}^2 u'_{234} \left(u_{234}
   \left(1-u_{1234}\right) u_{1234} u'_1+u'_2 u'_3
   \left(1-u'_{23}\right)+u'_2 u'_4 \left(1-u'_{24}\right)+u'_3 u'_4
   \left(1-u'_{34}\right)+\left(u'\right)_1^2\right) u'_{1234} ,\nonumber \\
   1-u_2&=u_1 u_3 u_4 u_{13}^2 u_{14}^2 u_{34}^2 u_{134}^4
   \left(u'\right)_2^8 \left(u'\right)_{12}^4 \left(u'\right)_{23}^4
   \left(u'\right)_{24}^4 \left(u'\right)_{123}^2
   \left(u'\right)_{124}^2 \left(u'\right)_{234}^2 u'_{1234}+~6
   u_1 \textcolor{red}{u_2^2} u_3 u_4 u_{1,2}^2 u_{13}^2 u_{14}^2 u_{23}^2 u_{24}^2
   u_{34}^2 u_{123}^2 u_{124}^2 u_{134}^3 u_{234}^2 u_{1234}
   u'_1 u'_3 u'_4 \left(u'\right)_2^4 \nonumber \\ &\left(u'\right)_{12}^3
   \left(u'\right)_{13}^2 \left(u'\right)_{14}^2
   \left(u'\right)_{23}^3 \left(u'\right)_{24}^3
   \left(u'\right)_{34}^2 \left(u'\right)_{123}^2
   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2
   \left(u'\right)_{234}^2 u'_{1234}+~2~ u_1 \textcolor{red}{u_2} u_3 u_4 u_{12}
   u_{13}^2 u_{14}^2 u_{23} u_{24} u_{34}^2 u_{123} u_{124}
   u_{134}^3 u_{234} \left(u'\right)_2^4 \left(u'\right)_{12}^3
   u'_{13} u'_{14} \nonumber \\ & \left(u'\right)_{23}^3 \left(u'\right)_{24}^3
   u'_{34} \left(u'\right)_{123}^2 \left(u'\right)_{124}^2
   u'_{134} \left(u'\right)_{234}^2 \left(u_{134}
   \left(1-u_{1234}\right) u_{1234} u'_2+u'_1 u'_3
   \left(1-u'_{13}\right)+u'_1 u'_4 \left(1-u'_{14}\right)+u'_3 u'_4
   \left(1-u'_{34}\right)+\left(u'\right)_2^2\right) u'_{1234} ,\nonumber \\
   1-u_3&=u_1 u_2 u_4 u_{12}^2 u_{14}^2 u_{24}^2 u_{124}^4
   \left(u'\right)_3^8 \left(u'\right)_{13}^4 \left(u'\right)_{23}^4
   \left(u'\right)_{34}^4 \left(u'\right)_{123}^2
   \left(u'\right)_{134}^2 \left(u'\right)_{234}^2 u'_{1234}+~6
   u_1 u_2 \textcolor{red}{u_3^2} u_4 u_{12}^2 u_{13}^2 u_{14}^2 u_{23}^2 u_{24}^2
   u_{34}^2 u_{123}^2 u_{124}^3 u_{134}^2 u_{234}^2 u_{1234}
   u'_1 u'_2 u'_4 \left(u'\right)_3^4 \nonumber \\ & \left(u'\right)_{12}^2
   \left(u'\right)_{13}^3 \left(u'\right)_{14}^2
   \left(u'\right)_{23}^3 \left(u'\right)_{24}^2
   \left(u'\right)_{34}^3 \left(u'\right)_{123}^2
   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2
   \left(u'\right)_{234}^2 u'_{1234} +~2 ~u_1 u_2 \textcolor{red}{u_3} u_4 u_{1,2}^2
   u_{13} u_{14}^2 u_{23} u_{24}^2 u_{34} u_{123} u_{124}^3
   u_{134} u_{234} \left(u'\right)_3^4 u'_{12}
   \left(u'\right)_{13}^3 u'_{14} \nonumber \\ &\left(u'\right)_{23}^3 u'_{24}
   \left(u'\right)_{34}^3 \left(u'\right)_{123}^2 u'_{124}
   \left(u'\right)_{134}^2 \left(u'\right)_{234}^2 \left(u_{124}
   \left(1-u_{1234}\right) u_{1234} u'_3+u'_1 u'_2
   \left(1-u'_{12}\right)+u'_1 u'_4 \left(1-u'_{14}\right)+u'_2 u'_4
   \left(1-u'_{24}\right)+\left(u'\right)_3^2\right) u'_{1234} ,\nonumber \\
   1-u_4 &= u_1 u_2 u_3 u_{12}^2 u_{13}^2 u_{23}^2 u_{123}^4
   \left(u'\right)_4^8 \left(u'\right)_{14}^4 \left(u'\right)_{24}^4
   \left(u'\right)_{34}^4 \left(u'\right)_{124}^2
   \left(u'\right)_{134}^2 \left(u'\right)_{234}^2 u'_{1234}+~6
   u_1 u_2 u_3 \textcolor{red}{u_4^2} u_{12}^2 u_{13}^2 u_{14}^2 u_{23}^2 u_{24}^2
   u_{34}^2 u_{123}^3 u_{124}^2 u_{134}^2 u_{234}^2 u_{1234}
   u'_1 u'_2 u'_3 \left(u'\right)_4^4 \nonumber\\ &\left(u'\right)_{12}^2
   \left(u'\right)_{13}^2 \left(u'\right)_{14}^3
   \left(u'\right)_{23}^2 \left(u'\right)_{24}^3
   \left(u'\right)_{34}^3 \left(u'\right)_{123}^2
   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2
   \left(u'\right)_{234}^2 u'_{1234}+~2 u_1 u_2 u_3 \textcolor{red}{u_4} u_{12}^2
   u_{13}^2 u_{14} u_{23}^2 u_{24} u_{34} u_{123}^3 u_{124}
   u_{134} u_{234} \left(u'\right)_4^4 u'_{12} u'_{13}
   \left(u'\right)_{14}^3 \nonumber\\ &u'_{23} \left(u'\right)_{24}^3
   \left(u'\right)_{34}^3 u'_{123} \left(u'\right)_{124}^2
   \left(u'\right)_{134}^2 \left(u'\right)_{234}^2 \left(u_{123}
   \left(1-u_{1234}\right) u_{1234} u'_4+u'_1 u'_2
   \left(1-u'_{12}\right)+u'_1 u'_3 \left(1-u'_{13}\right)+u'_2 u'_3
   \left(1-u'_{23}\right)+\left(u'\right)_4^2\right) u'_{1234},\nonumber \\
    1-u_{12}&= u_3 u_4
   u_{13} u_{14} u_{23} u_{24} u_{34}^2 u_{134}^2 u_{234}^2 \left(u'\right)_1^3
   \left(u'\right)_2^3 \left(u'\right)_{12}^3 \left(u'\right)_{13}^2
   \left(u'\right)_{14}^2 \left( u'\right)_{23}^2 \left(u'\right)_{24}^2 \left(1+u_{12}
   u_{123} u_{124} u_{1234} u'_3 u'_4 u'_{34}\right) \left(u'\right)_{123}^2
   \left(u'\right)_{124}^2 u'_{134} u'_{234} u'_{1234},\nonumber \\
     1-u_{13}&=u_2 u_4 u_{12}
   u_{14} u_{23} u_{24}^2 u_{34} u_{124}^2 u_{234}^2 \left(u'\right)_1^3
   \left(u'\right)_3^3 \left(u'\right)_{12}^2 \left(u'\right)_{13}^3
   \left(u'\right)_{14}^2 \left(u'\right)_{23}^2 \left(1+ u_{13} u_{123} u_{134} u_{1234}
   u'_2 u'_4 u'_{24}\right) \left(u'\right)_{34}^2 \left(u'\right)_{123}^2 u'_{124}
   \left(u'\right)_{134}^2 u'_{234} u'_{1234},\nonumber \\ 
   1-u_{14}&= u_2 u_3 u_{12} u_{13} u_{23}^2 u_{24} u_{34} u_{123}^2 u_{234}^2
   \left(u'\right)_1^3 \left(u'\right)_4^3 \left(u'\right)_{12}^2 \left(u'\right)_{13}^2
   \left(u'\right)_{14}^3 \left(1+ u_{14} u_{124} u_{134} u_{1234} u'_2 u'_3
   u'_{23}\right) \left(u'\right)_{24}^2 \left(u'\right)_{34}^2 u'_{123}
   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2 u'_{234} u'_{1234}, \nonumber \\ 
    1-u_{34}&= u_1 u_2 u_{12}^2 u_{13}
   u_{14} u_{23} u_{24} u_{123}^2 u_{124}^2 \left(u'\right)_3^3 \left(u'\right)_4^3
   \left(1+u_{34} u_{134} u_{234} u_{1234} u'_1 u'_2 u'_{12}\right)
   \left(u'\right)_{13}^2 \left(u'\right)_{14}^2 \left(u'\right)_{23}^2
   \left(u'\right)_{24}^2 \left(u'\right)_{34}^3 u'_{123} u'_{124}
   \left(u'\right)_{134}^2 \left(u'\right)_{234}^2 u'_{1234}, \nonumber \\ 
   1-u_{24}&=u_1 u_3 u_{12} u_{13}^2 u_{14}
   u_{23} u_{34} u_{123}^2 u_{134}^2 \left(u'\right)_2^3 \left(u'\right)_4^3
   \left(u'\right)_{12}^2 \left(1+ u_{24} u_{124} u_{234} u_{1234} u'_1 u'_3
   u'_{13}\right) \left(u'\right)_{14}^2 \left(u'\right)_{23}^2 \left(u'\right)_{24}^3
   \left(u'\right)_{34}^2 u'_{123} \left(u'\right)_{124}^2 u'_{134}
   \left(u'\right)_{234}^2 u'_{1234},\nonumber \\
    1-u_{23}&=u_1 u_4 u_{12} u_{13} u_{14}^2 u_{24}
   u_{34} u_{124}^2 u_{134}^2 \left(u'\right)_2^3 \left(u'\right)_3^3
   \left(u'\right)_{12}^2 \left(u'\right)_{13}^2 \left(1+u_{23} u_{123} u_{234} u_{1234}
   u'_1 u'_4 u'_{14}\right) \left(u'\right)_{23}^3 \left(u'\right)_{24}^2
   \left(u'\right)_{34}^2 \left(u'\right)_{123}^2 u'_{124} u'_{134}
   \left(u'\right)_{234}^2 u'_{1234},\nonumber \\ 
   1-u_{124}&=u_3 u_{13} u_{23} u_{34} u_{123} u_{134}
   u_{234} \left(u'\right)_1^2 \left(u'\right)_2^2 \left(u'\right)_4^2
   \left(u'\right)_{12}^2 u'_{13} \left(u'\right)_{14}^2 u'_{23} \left(u'\right)_{24}^2
   u'_{34} u'_{123} \left(u'\right)_{124}^2 u'_{134} u'_{234} u'_{1234},\nonumber \\ 
   1-u_{123}&=u_4 u_{14}
   u_{24} u_{34} u_{124} u_{134} u_{234} \left(u'\right)_1^2 \left(u'\right)_2^2
   \left(u'\right)_3^2 \left(u'\right)_{12}^2 \left(u'\right)_{13}^2 u'_{14}
   \left(u'\right)_{23}^2 u'_{24} u'_{34} \left(u'\right)_{123}^2 u'_{124} u'_{134}
   u'_{234} u'_{1234},\nonumber \\ 
   1-u_{134}&=u_2 u_{12} u_{23} u_{24} u_{123} u_{124} u_{234}
   \left(u'\right)_1^2 \left(u'\right)_3^2 \left(u'\right)_4^2 u'_{12}
   \left(u'\right)_{13}^2 \left(u'\right)_{14}^2 u'_{23} u'_{24} \left(u'\right)_{34}^2
   u'_{123} u'_{124} \left(u'\right)_{134}^2 u'_{234} u'_{1234},\nonumber \\ 
   1-u_{234}&=u_1 u_{12} u_{13} u_{14} u_{123} u_{124} u_{134}
   \left(u'\right)_2^2 \left(u'\right)_3^2 \left(u'\right)_4^2 u'_{12} u'_{13} u'_{14}
   \left(u'\right)_{23}^2 \left(u'\right)_{24}^2 \left(u'\right)_{34}^2 u'_{123} u'_{124}
   u'_{134} \left(u'\right)_{234}^2 u'_{1234},\nonumber \\ 
   1-u_{1234}&=u'_1
   u'_2 u'_3 u'_4 u'_{12} u'_{13} u'_{14} u'_{23} u'_{24} u'_{34} u'_{123} u'_{124}
   u'_{134} u'_{234} u'_{1234},\nonumber \\ 
   1-u'_1&=u_1 u_{12} u_{13} u_{14} u_{123}
   u_{124} u_{134} u_{1234} u'_2 u'_3 u'_4 u'_{23} u'_{24} u'_{34} u'_{234},\nonumber \\ 
   1-u'_2&=u_2
   u_{12} u_{23} u_{24} u_{123} u_{124} u_{234} u_{1234} u'_1 u'_3 u'_4 u'_{13} u'_{14}
   u'_{34} u'_{134},\nonumber \\ 
   1-u'_3&=u_3 u_{13} u_{23} u_{34} u_{123} u_{134} u_{234} u_{1234} u'_1
   u'_2 u'_4 u'_{12} u'_{14} u'_{24} u'_{124},\nonumber \\ 
   1-u'_4&=u_4 u_{14} u_{24} u_{34} u_{124}
   u_{134} u_{234} u_{1234} u'_1 u'_2 u'_3 u'_{12} u'_{13} u'_{23} u'_{123},\nonumber \\ 
   1-u'_{12}&=u_1
   u_2 u_{12}^2 u_{13} u_{14} u_{23} u_{24} u_{123}^2 u_{124}^2 u_{134} u_{234}
   u_{1234}^2 \left(u'\right)_3^2 \left(u'\right)_4^2 u'_{13} u'_{14} u'_{23} u'_{24}
   \left(u'\right)_{34}^2 u'_{134} u'_{234},\nonumber \\
   1-u'_{13}&=u_1 u_3 u_{12} u_{13}^2 u_{14}
   u_{23} u_{34} u_{123}^2 u_{124} u_{134}^2 u_{234} u_{1234}^2 \left(u'\right)_2^2
   \left(u'\right)_4^2 u'_{12} u'_{14} u'_{23} \left(u'\right)_{24}^2 u'_{34} u'_{124}
   u'_{234},\nonumber \\
   1-u'_{14}&=u_1 u_4 u_{12} u_{13} u_{14}^2 u_{24} u_{34} u_{123} u_{124}^2
   u_{134}^2 u_{234} u_{1234}^2 \left(u'\right)_2^2 \left(u'\right)_3^2 u'_{12} u'_{13}
   \left(u'\right)_{23}^2 u'_{24} u'_{34} u'_{123} u'_{234},\nonumber \\ 1-u'_{23}&=u_2 u_3 u_{12}
   u_{13} u_{23}^2 u_{24} u_{34} u_{123}^2 u_{124} u_{134} u_{234}^2 u_{1234}^2
   \left(u'\right)_1^2 \left(u'\right)_4^2 u'_{12} u'_{13} \left(u'\right)_{14}^2 u'_{24}
   u'_{34} u'_{124} u'_{134},\nonumber \\ 1-u'_{24}&=u_2 u_4 u_{12} u_{14} u_{23} u_{24}^2 u_{34}
   u_{123} u_{124}^2 u_{134} u_{234}^2 u_{1234}^2 \left(u'\right)_1^2 \left(u'\right)_3^2
   u'_{12} \left(u'\right)_{13}^2 u'_{14} u'_{23} u'_{34} u'_{123} u'_{134},\nonumber \\ 1-u'_{34}&=u_3
   u_4 u_{13} u_{14} u_{23} u_{24} u_{34}^2 u_{123} u_{124} u_{134}^2 u_{234}^2
   u_{1234}^2 \left(u'\right)_1^2 \left(u'\right)_2^2 \left(u'\right)_{12}^2 u'_{13}
   u'_{14} u'_{23} u'_{24} u'_{123} u'_{124},\nonumber \\
   1-u'_{123}&=u_1 u_2 u_3 u_{12}^2 u_{13}^2
   u_{14} u_{23}^2 u_{24} u_{34} u_{123}^3 u_{124}^2 u_{134}^2 u_{234}^2 u_{1234}^3
   \left(u'\right)_4^3 \left(u'\right)_{14}^2 \left(u'\right)_{24}^2
   \left(u'\right)_{34}^2 \left(1+ u'_1 u'_2 u'_3 u'_{12} u'_{13} u'_{23} u'_{123}\right)
   u'_{124} u'_{134} u'_{234},\nonumber \\ 
   1-u'_{124}&=u_1 u_2 u_4 u_{12}^2 u_{13} u_{14}^2 u_{23}
   u_{24}^2 u_{34} u_{123}^2 u_{124}^3 u_{134}^2 u_{234}^2 u_{1234}^3 \left(u'\right)_3^3
   \left(u'\right)_{13}^2 \left(u'\right)_{23}^2 \left(u'\right)_{34}^2 u'_{123}
   \left(1+u'_1 u'_2 u'_4 u'_{12} u'_{14} u'_{24} u'_{124}\right) u'_{134}
   u'_{234},\nonumber \\ 
   1-u'_{134}&=u_1 u_3 u_4 u_{12} u_{13}^2 u_{14}^2 u_{23} u_{24} u_{34}^2
   u_{123}^2 u_{124}^2 u_{134}^3 u_{234}^2 u_{1234}^3 \left(u'\right)_2^3
   \left(u'\right)_{12}^2 \left(u'\right)_{23}^2 \left(u'\right)_{24}^2 u'_{123} u'_{124}
   \left(1+ u'_1 u'_3 u'_4 u'_{13} u'_{14} u'_{34} u'_{134}\right) u'_{234},\nonumber \\ 
   1-u'_{234}&=u_2
   u_3 u_4 u_{12} u_{13} u_{14} u_{23}^2 u_{24}^2 u_{34}^2 u_{123}^2 u_{124}^2 u_{134}^2
   u_{234}^3 u_{1234}^3 \left(u'\right)_1^3 \left(u'\right)_{12}^2 \left(u'\right)_{13}^2
   \left(u'\right)_{14}^2 u'_{123} u'_{124} u'_{134} \left(u'_2 u'_3 u'_4 u'_{23} u'_{24}
   u'_{34} u'_{234}+1\right) ,\nonumber \\
   1-u'_{1234}&=6 u_1 u_2 u_3 u_4 u_{12}^2 u_{13}^2 u_{14}^2 u_{23}^2
   u_{24}^2 u_{34}^2 u_{123}^3 u_{124}^3 u_{134}^3 u_{234}^3
   u_{1234}^4 u'_1 u'_2 u'_3 u'_4 \left(u'\right)_{12}^2
   \left(u'\right)_{13}^2 \left(u'\right)_{14}^2
   \left(u'\right)_{23}^2 \left(u'\right)_{24}^2
   \left(u'\right)_{34}^2 \left(u'\right)_{123}^2
   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2
   \left(u'\right)_{234}^2 \textcolor{red}{\left(u'\right)_{1234}^2} - \nonumber \\  u_1 u_2& u_3 u_4
   u_{12}^2 u_{13}^2 u_{14}^2 u_{23}^2 u_{24}^2 u_{34}^2
   u_{123}^3 u_{124}^3 u_{134}^3 u_{234}^3 u_{1234}^4
   u'_{12} u'_{13} u'_{14} u'_{23} u'_{24} u'_{34} u'_{123}
   u'_{124} u'_{134} u'_{234} \left(-3
   u_{1234}^2+\left(1-u'_1\right){}^2+\left(1-u'_2\right){}^2+\left(1
   -u'_3\right){}^2+\left(1-u'_4\right){}^2\right) \textcolor{red}{u'_{1234}} \nonumber \\ & + u_1 u_2
   u_3 u_4 u_{12}^2 u_{13}^2 u_{14}^2 u_{23}^2 u_{24}^2 u_{34}^2
   u_{123}^4 u_{124}^4 u_{134}^4 u_{234}^4 u_{1234}^8 \nonumber
  \end{align*} }}
The $u$-equations for $u_1,u_2,u_3,u_4,u^{'}_{1234}$ are quadratic in the coresponding $u$'s. The 10 facets obtained by setting $u^{'}_{i}, ~u_{i}, u^{'}_{1234}, u_{1234} \rightarrow 0$ are all $P_3$ and the 20 facets obtained by setting $u^{'}_{ij}, ~u_{ij}, ~u^{'}_{ijk},~u_{ijk} \rightarrow 0$ are all $A_1 \times P_2$ . Thus, 4d permutahderon is indeed a binary positive geometry!

More generally the following are some of the $u$-equations for the $n$-dimensional permutahderon:\\

For $|I| =n-1$ and $s_K = \begin{cases}  1,~ if K \not\subset I & \\ 2, ~if K \subset I\end{cases}$

\bea
1-u_{I} &=& \prod_ {S - I \subset J } u_{J} \prod_ {K \cap I \ne \Phi } (u^{'}_{K})^{s_K}  \nonumber \\
1-u_{12\cdots n} &=& \prod_ {{I \subset S}\atop {I \ne \Phi}} u^{'}_{I} \nonumber
\eea

For $t_J = \begin{cases}  1,~ if I  \not\subset J & \\ 2, ~if I \subset J \end{cases}$

\bea
1-u^{'}_{i} &=& \prod_ {\{ i \} \subset J } u_{J} \prod_ {K \subset S- \{i\} } u^{'}_{K} \nonumber \\
1-u^{'}_{i j} &=& \prod_ {\{i,j \}\cap J \ne \Phi} u^{t_J}_{J} \prod_ {K \subset S-\{i, j \} } (u^{'}_{K})^{2} u^{'}_{K \cup {i}} u^{'}_{K \cup{j} } \nonumber 
\eea

and for $|I| =n-2$ with $S- I = \{i, j\}$

\bea
1-u_{I}= u_i u_j u^{2}_{ij} \prod_{J \subset I} u_{J \cup \{i\}} u_{J \cup \{j\}} u^{2}_{J \cup \{i,j\}} \prod_{K \subset S-I} (u^{'}_K)^{3} (u^{'}_{K \cup \{i\}})^{2}  (u^{'}_{K \cup\{j\}})^{2}  u^{'}_{K\cup \{i,j\}} \left( 1+ u^{'}_i u^{'}_j u^{'}_{ij} \prod_{I \subset L} u_L \right)                       \nonumber
\eea
The other $u$-equations are not two or three term equations and seem to be some higher  order polynomials in the corresponding $u$'s and it would be nice if we could classify all of them.

\section*{Associahedra}
If $B=\{ \{i,i+1,\cdots,j \} | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then $P_n({\bf Y})$ is the associahedron .
\section*{2d associahedron as generalized permutahedron}
In this case the building set $B=\{ \{ 0,1,2\},\{ 0,1\},\{1,2\},\{0\},\{1\},\{2\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y, ~x_{01}=1+x,~ x_{12}=x+y,~ x_{012}=1+x+y$.

We can write down the Newton polynomial for the Minkowski sum as $ x_1~ x_2~(1+x_1)~(x_1+x_2)~(1+x_1+x_2)$.

The $u$-variables can be written in terms of $x$ variables as:
\bea
u_1=\frac{x
   (x+y+1)}{(x+1)
   (x+y)},u_2=\frac{x +y}
   {x+y+1},u_3=\frac{y}{x+y},u_4=\frac{x+1}{x+y+1},u_5=\frac{1}{x+1} \nonumber
\eea
The $u$-equations are:
\bea
1-u_1=u_3 u_5,1-u_2=u_4
   u_5,1-u_3=u_1 u_4,1-u_4=u_2
   u_3,1-u_5=u_1 u_2 \nonumber
\eea
Notice that these are precisely the $u$ equations for the ABHY realisation of $A_2$.
\section*{3d associahedron as generalized permutahedron}
In this case the building set $B=\{ \{ 0,1,2,3\},\{ 0,1,2\},\{1,2,3\},\{0,1\},\{1,2\},\{2,3\},\{0\},\{1\},\{2\},\{3\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y,~x_3 =y, ~x_{01}=1+x,~ x_{12}=x+y,~x_{23}=y+z,~ x_{012}=1+x+y,~ x_{123}=x+y+z,~ x_{0123}=1+x+y+z$.

We can write down the Newton polynomial for the Minkowski sum as $ x_1~ x_2~x_3~(1+x_1)~(x_1+x_2)~(x_2+x_3)~(1+x_1+x_2)~(x_1+x_2+x_3)~(1+x_1+x_2+x_3)$. \\

The $u$-variables can be written in terms of $x$ variables as:
{\scriptsize \bea
u_1&=&\frac{x
   (x+y+1)}{(x+1)
   (x+y)},~u_2=\frac{(x+y
   )
   (x+y+ z+1)}{(x+y+1)
   (x+ y+z)},~u_3=\frac{x+
   y+ z}{x+y+z +1},~u_4=
   \frac{y}{x+z},\nonumber \\ u_5&=&\frac{
   y
   (x+y+z)}{(x+y)
   (y+z)},~u_6= \frac{y+z}
   {x+y+z},u_7=\frac{x+y+1}{x+y+z+1},u_8=\frac{x+1}{x+y+1},u_9=\frac{
   1}{x+1} \nonumber
   \eea}
   and satisfy the $u$-equations 
   \bea
   1-u_1&=&u_5 u_6 u_9,~1-u_2=u_4
   u_6 u_8 u_9,~1-u_3=u_7 u_8
   u_9,~1-u_4=u_2 u_5 u_7, \nonumber \\ 1-u_5&=&u_1
   u_4 u_8,1-u_6=u_1 u_2 u_7
   u_8,1-u_7=u_3 u_4 u_6,1-u_8=u_2
   u_3 u_5 u_6,1-u_9=u_1 u_2
   u_3 \nonumber
   \eea
  We see again that these are precisely the $u$ equations of ABHY realisation of $A_3$ !

This is not a coincidence and it extends to all $n$ since the corresponding Newton polytope is given by $\prod_{1\leq  i \leq j \leq n} (x_i +x_{i+1}+\cdots+x_j)$ is nothing but the Loday's realisation of the associahedron which is equivalent to the ABHY type $A_n$ associahedron.

Thus remarkably both the generalised permutahedron realisation and ABHY realisation of the associahedra $A_n$ are  the same. \\
\section*{Cyclohedra}
If $B$  is the set of cyclic intervals, then $P_n({\bf Y})$ is a cyclohedron.
\section*{3d cyclohedron}
The 2d cyclohedron is the same as the 2d permutahedron as they both have the same building sets.

 Let us look at the 3d case. In this case the building set $B=\{ \{ 0,1,2,3\},\{ 0,1,2\},\{1,2,3\},\{2,3,0\},\{3,0,1\}, \\  \{0,1\},\{1,2\},\{2,3\},\{0,3\},\{0\},\{1\},\{2\},\{3\}\}$.

 The Newton polynomial of the Minkowski sum is $x y z(1+x)(x+y)(y+z)(1+z)(1+x+y)(x+y+z)(y+z+1)(z+1+x)(1+x+y+z)$ and

 we  find the relevant $u$'s as:
\bea
u_1 &=&\frac{x (x+y+1)}{(x+1) (x+y)},~u_2 = \frac{(x+y) (x+y+z+1)}{(x+y+1) (x+y+z)},~u_3 = \frac{x+y+z}{x+y+z+1},~~~~~~~~~~~~~~u_4= \frac{z
   (y+z+1)}{(z+1) (y+z)}, \nonumber \\
   u_5 &=& \frac{y (x+y+z)}{(x+y) (y+z)},~u_6 = \frac{(y+z) (x+y+z+1)}{(y+z+1) (x+y+z)},~u_7 =
   \frac{y+z+1}{x+y+z+1},~~~~~~~~~~~~~~~u_8= \frac{x+z+1}{x+y+z+1}, \nonumber \\
   u_9 &=& \frac{x+y+1}{x+y+z+1},~u_{10} = \frac{(z+1) (x+y+z+1)}{(x+z+1) (y+z+1)},~u_{11}=
   \frac{(x+1) (x+y+z+1)}{(x+y+1) (x+z+1)},~u_{12} =\frac{x+z+1}{(x+1) (z+1)} \nonumber
\eea
and the u-equations  are:
\bea
1-u_1&=&u_5 u_6 u_7^2 u_{10} u_{12},~1-u_2=u_4 u_6 u_7^2 u_8^2 u_{10}^2 u_{11} u_{12},~1-u_3=u_7 u_8 u_9 u_{10} u_{11} u_{12},~1-u_4=u_2 u_5
   u_9^2 u_{11} u_{12}, \nonumber \\
   1-u_5 &=& u_1 u_4 u_8^2 u_{10} u_{11},~1-u_6=u_1 u_2 u_8^2 u_9^2 u_{10} u_{11}^2 u_{12},~1-u_7=u_1 u_2 u_3 u_8 u_9
   u_{11},~1-u_8=u_2 u_3 u_5 u_6 u_7 u_9, \nonumber \\
   1-u_9&=&u_3 u_4 u_6 u_7 u_8 u_{10},~1-u_{10}=u_1 u_2^2 u_3^2 u_5 u_6 u_9^2 u_{11},~1-u_{11}=u_2 u_3^2 u_4
   u_5 u_6^2 u_7^2 u_{10},~1-u_{12}=u_1 u_2 u_3^2 u_4 u_6 \nonumber
\eea
The $u$-equations above are that of ABHY realisation $B_3$ of the cyclohedron. This fact also generalizes to all $n$.

Thus, the gen.permutahedron realisation and ABHY type $B_n$ realisation of the cyclohedron are one and the same.

We can now consider several degenerations of both $A_n$ and $B_n$ and show that they are binary geometries with perfect $u$-equations.
\newpage
\section*{Minkowski sum of $n$ A2's }
We can also consider general Minkowski sums of non-simplices and see if these also give us any instance of polytopes with perfect $u$ equations. One such case is the following:

We consider the Minkowski sum of $n-1$ $A_2$'s with following Newton polynomial :
\bea \label {new}
\prod_{i=1}^{n} (1+x_i ) \prod_{i=1}^{n-1} (1+x_i +x_i x_{i+1}) 
\eea 
This gives a family of simple $n$-dimensional polytopes with $3n-1$ facets  and Pell number $P_n$ (~recursively defined as $ P_n=2 P_{n-1} +P_{n-2}$ with $P_1=1,~ P_2=2$) of vertices which we shall call $X_n$.

We can solve for $u$-variables for this family and we get :
\bea
u_1 &=& \frac{p_n}{q_n}, ~u_2 = \frac{p_{n-1}q_n}{p_{n-1,n}},~u_3 = \frac{p_{n-2}q_{n-1}}{p_{n-2,n-1}}, \cdots,
u_{n-2} = \frac{p_1 q_2}{p_{12}}, ~u_{n-1} = \frac{p_{2}q_3}{p_{23}},~u_n = \frac{p_{3}q_{4}}{p_{34}}, \nonumber \\
u_{n+1} &=& \frac{1}{q_1}, ~u_{n+2} = \frac{p_{12}}{q_{1}q_{2}},~u_{n+3} = \frac{q_{1}}{p_{23}}, \cdots,
u_{3n-1} = \frac{ q_{n-1}}{p_{n-1n}} \nonumber
\eea
where $p_i =x_i$, $q_i= 1+x_i$ and $p_{i~i+1}=1+x_i+ x_i x_{i+1}$.

The $u$ equations obtained from these $u$ variables are of three types viz. $1-u$ being the product of two, three or four $u$'s  for any $n$.

There are exactly 4 $u$'s which have $1-u$ is product of 2 u's:
\bea
1-u_{1} =u_{3n-2} u_{3n-1},~
1-u_{n-2} =u_{n+1} u_{n+3},~
1-u_{n+1} =u_{n-2} u_{n+2},~
1-u_{3n-1} = \begin{cases}
u_{2} u_{3} , n=3\\
u_{1} u_{4} , n=4\\
u_{1} u_{2} , n\geq 5
\end{cases} \nonumber 
\eea
The facets corresponding to setting any of these $u \to 0$ is $X_{n-1}$.

There are exactly $n-3$ $u$'s which have $1-u$ is product of 4 u's:
\bea
1-u_{n+4} =u_{n} u_{n+2}u_{n+4} u_{n+6} ~~and~~
1-u_{n+6+ 2 i} =u_{n-3-i} u_{n+4+2 i} u_{n+5+2 i} u_{n+8+2 i}~ for~i=0,\cdots,(n-5) \nonumber 
\eea
The facets corresponding to setting any of these $u \to 0$ is $A^{m}_1 \times X_{n-m-1}$.

All the other $2n-2$ $u$'s correspond to $1-u$ is product of 3 u's and we do not yet have a complete classification of the facets.

We can also replace the first the first term in the Newton polynomial \eqref{ new} with $(1+x_1+ x_2)$ and we get an identical system of $u$-equations

\bea
u_1 &=& \frac{p_n}{q_n}, ~u_2 = \frac{p_{n-1}q_n}{p_{n-1,n}},~u_3 = \frac{p_{n-2}q_{n-1}}{p_{n-2,n-1}}, \cdots,
u_{n-3} = \frac{p_4 q_5}{p_{45}}, ~u_{n-2} = \frac{p_{1}}{q_{1}},~u_{n-1} = \frac{p_{2}q_{3}}{p_{23}},~u_{n} = \frac{p_{3}q_{4}}{p_{34}}, \nonumber \\
u_{n+1} &=& \frac{q_2}{p_{12}}, ~u_{n+2} = \frac{q_{1}}{p_{12}},~u_{n+3} = \frac{p_{23}}{q_{2}q_{3}}, \cdots,
u_{3n-1} = \frac{ p_{12}}{q_{1}q_{2}} \nonumber
\eea
where $p_i =x_i$, $q_i= 1+x_i$ and $p_{i~i+1}=1+x_i+ x_i x_{i+1}$ with $p_{12}= 1+x_1+x_2$.

The $u$ equations obtained from these $u$ variables are of three types viz. $1-u$ being the product of two, three or four $u$'s  for any $n$.

There are exactly 4 $u$'s which have $1-u$ is product of 2 u's:
\bea
1-u_{1} =u_{3n-2} u_{3n-3},~
1-u_{n-2} =u_{n+1} u_{3n-1},~
1-u_{n+1} =u_{n-2} u_{n+2},~
1-u_{3n-1} = \begin{cases}
u_{2} u_{3} , n=3\\
u_{1} u_{4} , n=4\\
u_{1} u_{2} , n\geq 5
\end{cases} \nonumber 
\eea
The facets corresponding to setting any of these $u \to 0$ is $X_{n-1}$.

There are exactly $n-3$ $u$'s which have $1-u$ is product of 4 u's:
\bea
1-u_{n+3} =u_{n} u_{n+2}u_{n+5} u_{3n-1} ~~and~~
1-u_{n+5+ 2 i} =u_{n-3-i} u_{n+3+2 i} u_{n+4+2 i} u_{n+7+2 i}~ for~i=0,\cdots,(n-5) \nonumber 
\eea
It would be nice to see if these also correspond to some degeneration of the associahedron or if they  are generalised permutahedra. 
\newpage
\section{Discussions}
There are several interesting open questions, like the question of  whether degenerations of other cluster types (in particular $C_n$ and $D_n$ can also give binary geometries with (perfect?) $u$-equations.\\\\
\noindent
Though many examples of degenerations of $A_n$ and $B_n$ were products of lower dimensional objects of the same type, there were examples where we got non-trivial degenerations which did not factor. We would like to completely classify these cases and this would settle the question of identifying all the ``atoms'' of binary geometries with perfect $u$-equations. One class of examples which is certainly of both mathematical and physical interest in this context are the Stokes polytopes (and more generally Accordiohedra).
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{utphys}
\bibliography{final}
\end{document}

### 2020-03-02 draft_ABP.tex
update

@@
 
-It is a natural question to ask if binary geometries whose stringy integrals factorise at any finite $\alpha'$ are extremely special and are associated to only the classical $A_n, B_n, C_n,D_n$ or  Exceptional $E_6, E_7, E_8, F_2, G_4$  type clusters  as discussed in \cite{}.
+It is a natural question to ask if binary geometries whose stringy integrals factorise at any finite $\alpha^{'}$ are extremely special and are associated to only the classical $A_n, B_n, C_n,D_n$ or  Exceptional $E_6, E_7, E_8, F_2, G_4$  type clusters  as discussed in \cite{}.
 In this paper we answer this question in the negative by providing infinitely many counter examples.
@@
 {\bf review of stringy canonical forms, mention big polytopes and $u$ variables in general; then specify to cluster string integrals, then cluster configuration spaces with perfect $u$ equations, do $A_n$, $B_n$ examples; define "binary geometries"}
+
+*******************
 
@@
 
+*******************
+
 \newpage
@@
 $N=n+m$ and big polytope is a simplex, then general formula for $u$ variables, which is equivalent to ABHY conditions; again $P_n$ in full details and others as degenerations.}
+
+*******************
+
+In the last subsection, we have seen that any $n$-dimensional generalized 
+permutahedron can be constructed by a Minkowski sum of some simplices labeled by
+subsets of $[0,n]$. For a simplex labeled by a subset $I$, it can be realized as the 
+Newton Polytope of the linear polynomial $x_I=\sum_{i\in I}x_i$. Therefore, we can
+write down a natrual stringy canonical for the generalized permutahedron 
+$\mathscr P$
+\[
+	I_{\mathscr P}(\{S_I\})=\int_{\mathbb R^{n+1}_+}
+	\frac{\prod_{i=0}^n \mathrm{d}\log x_i}
+	{\operatorname{GL}(1)_+}\prod_{I\in\mathscr P}x_I^{\alpha' S_I},
+\]
+where the global $\operatorname{GL}(1)_+$ redundance $x_i\mapsto a x_i$ require that 
+$\sum_{I\in\mathscr P}S_I = 0$.
+
+Generally, we can consider arbitrary set of subsets of $[0,n]$ in above integrals. 
+However, the big polytope of this integral is usually not a simplex.
+It's highly non-trivial to figure out all such sets whose big polytopes are simplices,
+but we can easily see that every generalized permutahedron satisfies $N=n+m$
+because each facet $F_I$ corresponds to a set of nested set $\{[0,n],I\}$ for 
+$I\neq [0,n]$.
+
+***
+
+The following set of equations to define the $n$-dimensional Permutahedron: 
+\bea
+C_I = (-1)^{|I|} \left( \sum_{i \in I} X_i - \sum _{{i<j}\atop{i,j \in I}} X_{ij} +\cdots + (-1)^{|I|+1}  X_I \right) \nonumber
+\eea
+for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $X_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.
 

### 2020-03-02 draft_ABP.tex
update

@@
 requires that $\mathbf X$ should lay on one side of $F_a$ which is equivalent to 
-an inequality of variables $\mathbf S=(-X_1,\dots,-X_d,c_1,\dots,c_m)$, 
+an inequality of variables $\mathbf S=(X_1,\dots,X_d,-c_1,\dots,-c_m)$, 
 $W_a^JS_J\geq 0$, where $W_a^J$ is determined by the facet $F_a$. 
-These inequalities cut out a polyhedron in the $(d+m)$-dimensional space of $\mathbf S$,
-which is called the \textit{big polyhedron} of $\mathcal P$, 
+These inequalities cut out a polyhedron in the $(d+m)$-dimensional space of 
+$\mathbf S$, which is called the \textit{big polyhedron} of $\mathcal P$, 
 and the integral $\mathcal I(\mathbf S)$ converges for each point $\mathbf S$ 
@@
 \[
-	\mathcal I(U)=
+	\mathcal I(\mathbf U)=
 	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
-	\prod_{J}p_J^{-\alpha' S_J}
+	\prod_{A}u_A^{\alpha' U_A}
 	=
 	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
-	\prod_{A}u_A^{\alpha' U_A},
+	\prod_{J}p_J^{\alpha' S_J},
 \]
-where we introduce a new set of variables $u_A = \prod_J p_J^{-V_J^A}$ for 
+where we introduce a new set of variables $u_A = \prod_J p_J^{V_J^A}$ for 
 $A=1,\dots,v$. Note that there's no unique way to write $S_J=U_AV_J^A$ when
@@
 $\mathcal P$ can be associated with a single $u_A$ going to zero, 
-giving a “binary” geometry we will describe later.
-
-(why cluster configuration space, perfect u eqs)
+giving a ``binary geometry'' we will describe later.
+
+Generally, the big polyhdron of a stringy integral is not necessary to be a simplex.
+
+(cluster configuration space, perfect u eqs)
 
@@
 Newton Polytope of the linear polynomial $x_I=\sum_{i\in I}x_i$. Therefore, we can
-write down a natrual stringy canonical for the generalized permutahedron 
+write down a natrual stringy canonical form for the generalized permutahedron 
 $\mathscr P$
 \[
-	I_{\mathscr P}(\{S_I\})=\int_{\mathbb R^{n+1}_+}
+	\mathcal I_{\mathscr P}(\{S_I\})=\int_{\mathbb R^{n+1}_+}
 	\frac{\prod_{i=0}^n \mathrm{d}\log x_i}
@@
 $I\neq [0,n]$.
+Therefore, for a generalized permutahedron $\mathscr P$, we can write the matrix 
+$W^J_A$ of facets and get the ABHY conditions $S_J=F_A(W^{-1})^A_J\geq 0$ and 
+its $u$-variables $u_A=\prod_J p_J^{(W^{-1})^A_J}$.
 
@@
 
-The following set of equations to define the $n$-dimensional Permutahedron: 
+($P_n$)
+
+As shown in the last subsection, the $n$-dimensional permutahedron is associated 
+with the set of all non-empty subsets of $[0,n]$, which is denoted by $\mathscr P_n$. 
+The number of facets of $\mathscr P_n$ is $2^n-2$.
+
+(equations of facets?)
+
+ABHY conditions:
 \bea
@@
 for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $X_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.
+
+(proof?)
+
+Then we can then solve for the corresponding $u's$ :
+\bea
+u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber \\
+u^{'}_J &=& \prod_{{0 \in I}\atop{ \{0,\cdots,n\} - I \subset J}} x_I^{(-1)^{|I|-|J|+\color{red}{mod(n, 2)}}} \nonumber
+\eea
+
+(notation!)
 

### 2020-03-03 draft_ABP.tex
update;

@@
 with the set of all non-empty subsets of $[0,n]$, which is denoted by $\mathscr P_n$. 
-The number of facets of $\mathscr P_n$ is $2^n-2$.
-
-(equations of facets?)
-
-ABHY conditions:
-\bea
-C_I = (-1)^{|I|} \left( \sum_{i \in I} X_i - \sum _{{i<j}\atop{i,j \in I}} X_{ij} +\cdots + (-1)^{|I|+1}  X_I \right) \nonumber
-\eea
-for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $X_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.
-
-(proof?)
-
-Then we can then solve for the corresponding $u's$ :
-\bea
-u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber \\
-u^{'}_J &=& \prod_{{0 \in I}\atop{ \{0,\cdots,n\} - I \subset J}} x_I^{(-1)^{|I|-|J|+\color{red}{mod(n, 2)}}} \nonumber
-\eea
+Each facet of $P_n$ is lebeled by a non-empty proper subset $I$ of $[0,n]$, whose
+equation is 
+\begin{equation}
+	F_J:=\sum_{J\neq \varnothing, J\subset I} S_J=0,
+\end{equation}
+so the number of facets of $\mathscr P_n$ is $2^n-2$. The AHBY condition 
+can be solved from above equations:
+\[
+	S_I = (-1)^{|I|+1}\sum_{i\in I} S_i,
+\]
+for all non-empty subsets $I \subset [0,n]$ which are not singlets.
+
+(proof of equations fo facets or ABHY condition?)
+
+To get $u$-equations, we should solve $S_J$ by $F_J$ for eq.(\theequation), the 
+solution is 
+\[
+	S_I=\sum_{J\neq \varnothing,J\subset I} (-1)^{|J|-|I|}F_J,
+\]
+then
+\[
+	\prod_{I\neq \varnothing,I\subset [0,n]}u_I^{F_I}=
+	\prod_{I\neq \varnothing,I\subset [0,n]}x_I^{S_I}=
+	\prod_{\varnothing\neq J\subset I\subset [0,n]}
+	x_I^{(-1)^{|J|-|I|}F_J}=
+	\prod_{J\neq \varnothing,J\subset [0,n]}
+	\prod_{I\supset J}(x_I^{(-1)^{|J|-|I|}})^{F_J}
+\]
+gives that
+\[
+	u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}
+\]
 

### 2020-03-05 draft_ABP.tex
update

@@
 with the set of all non-empty subsets of $[0,n]$, which is denoted by $\mathscr P_n$. 
-Each facet of $P_n$ is lebeled by a non-empty proper subset $I$ of $[0,n]$, whose
-equation is 
-\begin{equation}
+Each facet of $\mathscr P_n$ is lebeled by a non-empty proper subset $I$ of $[0,n]$, 
+whose equation is 
+\begin{equation}\label{Pnfacet}
 	F_J:=\sum_{J\neq \varnothing, J\subset I} S_J=0,
@@
 
-(proof of equations fo facets or ABHY condition?)
-
-To get $u$-equations, we should solve $S_J$ by $F_J$ for eq.(\theequation), the 
+(Zhenjie: proof of equations of facets or ABHY condition?)
+
+To get $u$-equations, we should solve $S_J$ by $F_J$ from eq.\eqref{Pnfacet}, the 
 solution is 
-\[
+\begin{equation}\label{SinF}
 	S_I=\sum_{J\neq \varnothing,J\subset I} (-1)^{|J|-|I|}F_J,
-\]
+\end{equation}
 then
@@
 \[
-	u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}
+	u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}.
 \]
-
-(notation!)
+For example, the $u$-variables of $\mathscr P_2$ are
+\[
+	u_{1}  = \frac{x_1 x_{123}}{x_{12}x_{13}},\quad 
+	u_{2}  = \frac{x_2 x_{123}}{x_{12}x_{23}},\quad
+	u_{3}  = \frac{x_3 x_{123}}{x_{13}x_{23}},\quad
+	u_{12} = \frac{x_{12}}{x_{123}},\quad 
+	u_{13} = \frac{x_{13}}{x_{123}},\quad
+	u_{23} = \frac{x_{23}}{x_{123}}.
+\]
+They satisfy the following equtions
+\begin{align*}
+	&1-u_{1}=u_{2} u_{3} u_{23}^2,
+	1-u_{2}=u_{1} u_{3} u_{13}^2,
+	1-u_{3}=u_{1} u_{2} u_{12}^2,\\
+	&1-u_{12}=u_{3} u_{13} u_{23},
+	1-u_{13}=u_{2} u_{12} u_{23},
+	1-u_{23}=u_{1} u_{12} u_{13}.
+\end{align*}
+We will discuss these $u$-equations in the next subsection.
+
+For a $n$-dimensional general permutahedron $\mathscr A$, it can be achieved 
+from $\mathscr P_n$ by setting $S_J$ to be $0$ for any 
+$J\in \mathscr P_n-\mathscr A$. Facets of $\mathscr A$ are degenerations of facets 
+of $\mathscr P_n$ eq.\eqref{Pnfacet}, but some of them become spurious. If a pole
+is spurious, it can be written as a positive linear combination of some true facets.
+Such relations are sequence of eq.\eqref{SinF} for $I\not\in \mathscr A$.
+For example, for $\mathscr A=\{123,12,23,1,2,3\}$, we have that
+\[
+	0=S_{13}=F_{13}-F_{1}-F_{3},
+\]
+so $F_{13}$ is not a true facet of $\mathscr A$, there're only $5$ facets left in
+$\mathscr A$.
+
+(Zhenjie: what are the facets of general permutahedra?  I believe they are known.)
 

### 2020-03-05 draft_ABP.tex
update

@@
 Generally, the big polyhdron of a stringy integral is not necessary to be a simplex.
-
-(cluster configuration space, perfect u eqs)
+It's known that stringy integrals associated to the $A_n$, $B_n$, $C_n$, $D_n$,
+$E_6$, $E_7$, $E_8$, $F_2$ and $G_4$ type clusters are in this type. What's more,
+they satisfy the so called $u$-equations with the form
+\begin{equation}\label{perfectu}
+	1-u_i=\prod_{j}u_j^{(i||j)},
+\end{equation}
+where $(i||j)\geq 0$ is a integral defined in the cluster algebra context \cite{}.
+Varieties defined by $u$-equations associated with finite type clusters 
+are called cluster configuration spaces. 
+For this type equations, once $u_i$ goes to $0$, it forces some $u_j$ to go to $1$.
+Therefore, these $u$-equations reveal the binary structure of the cluster
+configuration spaces. ...
 
 ($A_n$ (sting integral?), $B_n$ (Shi arrangement?), or both from $F$-polynomial)
+
+For example, $A_n$ type cluster configuration spaces come from original string 
+amplitudes
+\[
+	\int_{z_1<z_2<\cdots <z_n}
+	\frac{\mathrm dz_2\cdots \mathrm dz_{n-2}}{(z_1-z_2)\cdots (z_{n-2}-z_{n-1})}
+	\prod_{i<j} (z_i-z_j)^{\alpha' s_{ij}},
+\]
+where we fix the gauge by setting $z_1=0$, $z_{n-1}=1$ and $z_n=\infty$.
+The $u$-variables of this configuration space are
+\[
+	u_{ij}=\frac{(z_{i-1}-z_j)(z_i-z_{j-1})}{(z_i-z_j)(z_{i-1}-z_{j-1})},
+\]
+and they satisfy the $u$-equations
+\[
+	1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl},
+\]
+where $(i,j)\not\sim (k,l)$ means that diagonals $(i,j)$ and $(k,l)$ of
+$(n+3)$-gon are crossed.
+
+(Zhenjie: we should use another parametrization of $A_n$) 
+(mention hyperplane arrangement)
+
+$B_n$: Shi arrangement
+
+The Shi arrangement of $B_n$ contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
+on the real line with the freedom corresponding to the global transformation 
+$z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. Then the Shi arrangement is 
+given by the following hyperplains
+\[
+    z_i-z_j=0\quad \text{and}\quad z_i-z_j=1,
+\]
+for $1\leq i<j\leq n+1$.
+
+The the $u$ variables of $B_n$ can be solved by these $z_i$ by 
+\[
+    u_1=1+z_1-z_2,\quad \dots,\quad u_{n}=1+z_{n}-z_{n+1},\quad u_{n+1}=z_{n+1}-z_1
+\]
+and 
+\[
+\begin{aligned}
+    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad &&\text{for $i<j$},\\
+    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad &&\text{for $i<j$},
+\end{aligned}
+\]
+where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices are living in $\mathbb Z_{2n+2}$.
+
+(u eq of $B_n$)
 

### 2020-03-06 draft_ABP.tex
update a commit
Update draft_ABP.tex

@@
 permutahedron can be constructed by a Minkowski sum of some simplices labeled by
-subsets of $[0,n]$. For a simplex labeled by a subset $I$, it can be realized as the 
-Newton Polytope of the linear polynomial $x_I=\sum_{i\in I}x_i$. Therefore, we can
-write down a natrual stringy canonical form for the generalized permutahedron 
+subsets of $[0,n]$. For a simplex labeled by a subset $I$, 
+it is natrual to associate the linear polynomial $x_I=\sum_{i\in I}x_i$ whose Newton polytope is the corresponding simplex.
+Therefore, we can write down a natrual stringy canonical form for the generalized permutahedron with the building set
 $\mathscr P$
 \[
-	\mathcal I_{\mathscr P}(\{S_I\})=\int_{\mathbb R^{n+1}_+}
+	\mathcal I_{\mathscr P}(\{S_I\})=\int_{\mathbb R^{n}_+}
 	\frac{\prod_{i=0}^n \mathrm{d}\log x_i}
@@
 
-(Zhenjie: what are the facets of general permutahedra?  I believe they are known.)
+(Zhenjie: Are facets of $\mathscr A$ associated with $J$ just the $F_J$ of $\mathscr P_n$ after setting all $S_I=0$ for $I\not\in \mathscr A$? How to prove it?)
 

### 2020-03-06 draft_ABP.tex
Update draft_ABP.tex

@@
 $\mathscr P$
-\[
+\begin{equation} \label{stringyintforgenpermutohedron}
    \mathcal I_{\mathscr P}(\{S_I\})=\int_{\mathbb R^{n}_+}
@@
 	{\operatorname{GL}(1)_+}\prod_{I\in\mathscr P}x_I^{\alpha' S_I},
-\]
+\end{equation}
 where the global $\operatorname{GL}(1)_+$ redundance $x_i\mapsto a x_i$ require that 
@@
 
-Generally, we can consider arbitrary set of subsets of $[0,n]$ in above integrals. 
-However, the big polytope of this integral is usually not a simplex.
+Generally, we can consider an arbitrary set of subsets of $[0,n]$ in eq.\eqref{stringyintforgenpermutohedron}. 
+However, the big polytope for such integral in general is not a simplex.
 It's highly non-trivial to figure out all such sets whose big polytopes are simplices,
 but we can easily see that every generalized permutahedron satisfies $N=n+m$
-because each facet $F_I$ corresponds to a set of nested set $\{[0,n],I\}$ for 
-$I\neq [0,n]$.
+because each facet $F_I$ is given by a nested set $\{[0,n],I\}$ for $I\neq [0,n]$.
 Therefore, for a generalized permutahedron $\mathscr P$, we can write the matrix 

### 2020-03-07 draft_ABP.tex
update

@@
 \subsection{Generalized permutohedra} {\bf the definition, facets and combinatorial factorizations, do $P_n$ example in full details.}
-
+******************************************************************************************
+\section*{Permutahedron}
+ For $x_1,x_2, \cdots, x_{n+1} \in \mathbb{R} $ , the permutahedron ${\mathscr P_n}(x_1,\cdots,x_{n+1})$ is a convex polytope in $\mathbb{R}^{n+1}$ defined as the convex hull of all vectors obtained from $(x_1,x_2, \cdots, x_{n+1})$ by permutations of the coordinates:
+ \bea
+{\mathscr P_n}(x_1,x_2, \cdots, x_{n+1}) = {\rm ConvexHull} \{ (x_{w(1)},x_{w(2)}, \cdots, x_{w(n+1)})~ |~ w \in S_{n+1} \}, \nonumber
+ \eea
+ where $S_{n+1}$ is the symmetric group.
+
+ The permutahedron has $(n+1)!$ vertices and is of dimension at most $n$ since it lies in the hyperplane 
+ \bea
+ H_c= \{(t_1,t_2, \cdots, t_{n+1}) | t_1 + t_2 + \cdots + t_{n+1}= c \} \subset \mathbb{R}^{n+1}, \nonumber
+ \eea
+where $c= x_1+x_2+ \cdots +x_{n+1}$.
+
+For $n=1$ and distinct $x_1,x_2$ the permutahedron ${\mathscr P_1}(x_1,x_2)$ is a line. If  $x_1=x_2$ then it degenerates into a single point.
+
+For $n=2$ and distinct $x_1,x_2, x_3$ the permutahedron ${\mathscr P_2}(x_1,x_2, x_3)$ is a hexagon.
+If two of the $x_i$'s are equal then the permutahedron degenerates into a triangle and if $x_1= x_2 = x_3$ then its degenerates into a single point.
+
+We shall list a few results about permutahedra which shall be useful for later purposes: 
+\begin{itemize}
+\item {\bf Coordinate independence:} The combinatorial structure of the permutahedron ${\mathscr P_n} (x_1, \cdots, x_{n+1}) $ does not depend on $ x_1, \cdots, x_{n+1} $ as long as all these are distinct.
+Henceforth  we will choose $ \{x_1, \cdots, x_{n+1}\} = \{0,1,\cdots,n \} := [0,n ]$.
+\\
+\item {\bf Facial Structure:} The $(n-k)$ faces of ${\mathscr P_n}$ are in an $1-1$ correspondence with the decomposition of $[0,n]$ into $k$ parts.
+More precisely, for each $(S_1,\cdots,S_k)$ with $S_i \neq \emptyset ~ \forall i$ and $[0,n] = S_1 \sqcup \cdots \sqcup S_k$ the corresponding face $\pi_{S_1,\cdots,S_k}$ has vertices which are permutations such that the entries $ \{x_i | i \in S_1 \}$ are largest $|S_1|$ numbers in $[0,n]$, $\{x_i | i \in S_2 \}$ are largest $|S_2|$ numbers in $[0,n]$ and so on.
+
+Further the face $\pi_{S_1,\cdots,S_k}$   is isomorphic to ${\mathscr P_{\left(| S_1|-1\right)} }\times {\mathscr P_{\left(| S_2|-1\right)} } \cdots \times{\mathscr P_{\left(| S_k|-1\right)} } $.
+
+It follows from above that ${\mathscr P_n}$ has $2^{n+1} -2$ facets corresponding to all the non-empty proper subsets of $I$ for which we have a decomposition $[0,n] = S \sqcup S^c$ and the facets are isomorphic to one of the following product of lower dimensional permutahedra  $ \{ {\mathscr P_{n-1}}, {\mathscr P_{n-2}} \times A_1, \cdots ,{\mathscr P_{\lfloor{n/2 \rfloor}}} \times {\mathscr P_{n-1-\lfloor n/2 \rfloor}}  \} $\footnote {More generally the number of $(n-k)$ facets of ${\mathscr P_n}$ is $ k!
+S(n,k)$ where $S(n,k)$ is the Stirling number of the second kind which counts the number $k$ partitions of  $I$ and there are $p(n+1,k)$ types where $p(n+1,k)$ is the number of $k$ partitions of $(n+1)$.}.
+
+It also follows from above that a face $\pi_{S_1,\cdots,S_k}$ is contained in another face $\pi_{T_1,\cdots,T_l}$ if and only if each $T_i$ is a union of consecutive $S_j$ or equivalently if $(S_1,\cdots,S_k)$ is a refinement of $(T_1,\cdots,T_l)$.
+\item {\bf Minkowski decomposition:}   Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_{n+1})$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$.
+For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull}(e_i~|~i\in I)$ denote the face of the $\Delta_{[0,n]}$.
+The polytope $P_n(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I > 0$ for all nonempty subsets $I \subset [n+1]$
+ \bea
+ P_n(\{y_I \})= \sum_{I \subset[n+1]} y_I . \Delta_I  \nonumber
+ \eea
+ is the permutahedron ${\mathscr P_n}$
+\end{itemize}
+We shall now talk about generalized permutahedra which are polytopes obtained by deformations of the usual permutahedron i.e., obtained by moving the vertices of the usual permutahedron so that the directions of all the edges are preserved though some of the edges may degenerate into points.
+
+\section*{Generalized permutahedra}
+
+A  generalised permutahedron is obtained by parallel translation of facets of the usual permutahedron it is parametrized  by a collection $\{ z_I\}$ of $2^{n+1}-1$ coordinates, for non-empty sets of $I \subset [0,n] $
+ \bea
+ P_n^z(\{ z_I \}) = \left \{ (t_0 , t_2, \cdots , t_{n}) \in \mathbb{R}^{n+1} | \sum_{i=0}^{n} t_i = z_{[0,n]},~ \sum_{i \in I} t_i \geq z_I, {\rm for ~subsets} ~I  \right  \} \nonumber
+ \eea
+ (a better notation for generalized permutahedron ??)
+
+ If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron. 
+ \begin{itemize}
+ \item The combinatorial structure of the generalised permutahedron depends only on the set $B$ of nonemepty subsets $I \subset [0,n]$ such that $y_I \geq 0$ which is called the {\it building set}.
+To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
+\section*{Nested Complex}
+If $B$ additionally satisfies the following:
+
+\noindent(1) If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$. \\
+(2) $B$ contains all singletons $\{ i\}$ for $i \in S$.
+
+A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:\\
+\noindent
+(1) For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.\\
+(2) For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B. \\
+(3) N contains all maximal elements of $B$.
+
+The {\it nested complex} $\mathcal{N}(B)$ is defined as the poset of the set of all nested sets in $B$ ordered by inclusion.
+
+\item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$.
+For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull(e_i~|~i\in I)}$ denote the face of the $\Delta_{[0,n]}$.
+The polytope $P_n^y(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I \geq 0$ for all nonempty subsets $I \subset [0,n]$
+ \bea
+ P_n^y(\{y_I \})= \sum_{I \subset[0,n]} y_I . \Delta_I  \nonumber
+ \eea
+is the generalised permutahedron $P_n^z(\{z_I \})$ if $z_I = \sum_{J \subset I} y_J  ~{\rm for~all~nonempty} I \subset [0,n]$.
+\footnote{Not all generalised permutahedra cannot be written as Minkowski sum of coordinate simplices.
+We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation.}
+
+\item {\bf Facial structure:} Let us assume that the set $B$ associated with a generalised permutahedron $P_n^{y}$ is a building set on $[0,n]$.
+Then the poset of faces $P_n^{y}$ ordered by reverse inclusion is isomorphic to the nested complex $\mathcal{N}(B)$.
+
+For each decomposition $[0,n]=  \sqcup_{I \subset N } S_I $ where $S_I$ are non-empty, the face $P_N$ of $P_n^{y}(y_I)$ associated with the nested set $N \in \mathcal{N}(B)$ is:
+\bea
+P_N = \sum_{{J \subset B}\atop{J \cap S_I \neq \emptyset}} y_{J} \Delta_{J \cap S_I}
+\eea
+\end{itemize}
+In summary the above results imply that we can look at any collection of subsets of $[0, n]$ which form a building set $B$ and associate  coordinate simplex $\Delta_I$ for each $I \in B$ and resulting Minkowski sum with positive weights $y_I$ generates a generalised permutahedron associated with the building set.
+Further, the number of facets of the generalised permutahedron just correspond to the set of all non-singlet elements in $B$.
+
+We shall set $x_0 =1$ from now on. Since, the number of singlets correspond to the dimension of the generalised permutahedron this implies that:
+
+{\bf Number of facets = Number of linear equation + dimension of  gen permutahedron}
+
+Thus, generalised permutahedra have ``Big Polytopes" which are simplices and we can write down the stringy canonical forms and solve for the $u$-variables and examine if they satisfy some kind of $u$-equations.
+We shall do this in subsequent sections (see section(2.2)).
+
+Here are some interesting examples of generalised permutahedra:
+
+(1) If $B$ consists of only singlets i.e., $B=\{ \{ 0,1,\cdots,n \}, \{ 0 \},\{ 1 \},\cdots ,\{ n \} \}$ then the generalised permutahedron is a Simplex.
+In this case the relevant $x$ variables are $x_i,~ i=0,\cdots,n$ and $\sum_{i=0}^n x_i$.
+The Newton polytope of the Minkowski sum is $\prod_{i=1}^{n} x_i (1+\sum_{j=1}^{n} x_j)$ and $u$-variables are 
+$u_i =\frac{ x_i}{1+\sum_{i=1}^n x_i} $
+which satisfy $\sum u_i =1$ as their only $u$-equation. \\
+
+(2) If $B= \{[i] | i=1,\cdots,n+1 \}$ is the complete flag of intervals, then $P_n({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
+The Newton polytope of the Minkowski sum is $x_1\cdots x_n (1+x_1) \cdots (1+x_1+\cdots +x_n)$ and $u$-variables are 
+$u_i =\frac{ 1}{1+\sum_{j=1}^{i} x_j} $, ~~$u^{'}_i =\frac{ \sum_{j=1}^{i} x_j}{1+\sum_{j=1}^{i} x_j} $ for $j=1,\cdots,n$ \\
+which satisfy $u_i +u^{'}_{i} =1$ as their $u$-equation. \\
+
+(3) If $B$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then $P_n({\bf Y})$ is the usual permutahedron $P_n$.
+
+(4)If $B=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then $P_n({\bf Y})$ is the associahedron.
+
+(5) If $B=\{ [1,i] \cup [j,n] | 1\leq  i \leq j \leq n\}$ is the set of cyclic intervals, then $P_n({\bf Y})$ is the Cyclohedron.
+
+The cases (4) and (5) will be considered in section (3.2). In this section we shall restrict ourselves to the permutahedron example ${\mathscr P_n}$.  
 \subsection{Natural stringy integrals with linear factors}

### 2020-03-07 draft_ABP.tex
merge from overleaf

@@
 
-($A_n$ (sting integral?), $B_n$ (Shi arrangement?), or both from $F$-polynomial)
-
 For example, $A_n$ type cluster configuration spaces come from original string 
@@
 \[
-	\int_{z_1<z_2<\cdots <z_n}
+	\mathcal I_n = \int_{z_1<z_2<\cdots <z_n}
 	\frac{\mathrm dz_2\cdots \mathrm dz_{n-2}}{(z_1-z_2)\cdots (z_{n-2}-z_{n-1})}
-	\prod_{i<j} (z_i-z_j)^{\alpha' s_{ij}},
+	\prod_{i<j} (z_j-z_i)^{\alpha' s_{ij}},
 \]
 where we fix the gauge by setting $z_1=0$, $z_{n-1}=1$ and $z_n=\infty$.
-The $u$-variables of this configuration space are
-\[
-	u_{ij}=\frac{(z_{i-1}-z_j)(z_i-z_{j-1})}{(z_i-z_j)(z_{i-1}-z_{j-1})},
+It's not in the form of stringy integrals, but we can use a positive
+parametrization 
+\[
+z_3=1+x_2,\quad z_4=1+x_2+x_3,\quad \dots, \quad 
+z_{n-1}=1+x_2+\cdots+x_{n-2}
+\]
+to rewrite the integral $\mathcal I_n$, then
+\[
+    \mathcal I_n=\int_{\mathbb R_+^{n-3}}
+	\frac{\mathrm dx_2\cdots \mathrm dx_{n-2}}{x_2\cdots x_{n-2}}
+	\prod_{i<j} p_{ij}^{\alpha' s_{ij}},
+\]
+where $p_{ij}=x_i+\cdots+x_{j-1}$. The $u$-variables of this configuration space are
+\[
+	u_{ij}=\frac{p_{i-1,j}p_{i,j-1}}{p_{ij}p_{i-1,j-1}},
 \]
@@
 
-(Zhenjie: we should use another parametrization of $A_n$) 
-(mention hyperplane arrangement)
-
-$B_n$: Shi arrangement
-
-The Shi arrangement of $B_n$ contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
-on the real line with the freedom corresponding to the global transformation 
+Another example still comes from a hyperplane arrangement, the Shi arrangement,
+which is also $B_n$ type cluster stringy integral.
+The Shi arrangement contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
+on the real line with the freedom of global transformation 
 $z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. Then the Shi arrangement is 
@@
 \]
-for $1\leq i<j\leq n+1$.
-
-The the $u$ variables of $B_n$ can be solved by these $z_i$ by 
+for $1\leq i<j\leq n+1$. Its stringy integral is
+\[
+	\mathcal I_n = \int_{z_1<z_2<\cdots <z_n<0}
+	\frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(z_1-z_2)\cdots (z_{n}-z_{n+1})}
+    \prod_{1\leq i<j \leq n}(z_j-z_i)^{s_{ij}}|z_i-z_j-1|^{t_{ij}}
+\]
+(Zhenjie: Carefully check the notation!)
+The $u$-variables of this configuration space are
 \[

### 2020-03-07 draft_ABP.tex
merge from overleaf

@@
 \usepackage{epsfig,amssymb,euscript,xspace,xcolor}
-\usepackage{amsmath,mathtools,empheq,amsthm,hyperref,graphicx}
+\usepackage{amsmath,mathtools,empheq,amsthm,hyperref,graphicx,paralist}
 \usepackage{mathrsfs,float}  
@@
 Therefore, these $u$-equations reveal the binary structure of the cluster
-configuration spaces. ...
+configuration spaces.
 
@@
 
-\section*{Generalized permutahedra}
+\subsection*{Generalized permutahedra}
 
@@
 To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
-\section*{Nested Complex}
+ \end{itemize}
+
+\subsection*{Nested Complex}
 If $B$ additionally satisfies the following:
-
-\noindent(1) If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$. \\
-(2) $B$ contains all singletons $\{ i\}$ for $i \in S$.
-
-A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:\\
-\noindent
-(1) For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.\\
-(2) For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B. \\
-(3) N contains all maximal elements of $B$.
+\begin{compactenum}[\quad (1)]
+    \item If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$.
+    \item $B$ contains all singletons $\{ i\}$ for $i \in S$.
+\end{compactenum}
+
+A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
+\begin{compactenum}[\quad (1)]
+    \item For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
+    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
+    \item $N$ contains all maximal elements of $B$.
+\end{compactenum}
 
@@
 
+ \begin{itemize}
 \item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$.

### 2020-03-07 draft_ABP.tex
merge from overleaf
update sec 1.1

@@
 on the real line with the freedom of global transformation 
-$z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. Then the Shi arrangement is 
+$z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. The Shi arrangement is 
 given by the following hyperplains
 \[
-    z_i-z_j=0\quad \text{and}\quad z_i-z_j=1,
-\]
-for $1\leq i<j\leq n+1$. Its stringy integral is
-\[
-	\mathcal I_n = \int_{z_1<z_2<\cdots <z_n<0}
-	\frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(z_1-z_2)\cdots (z_{n}-z_{n+1})}
-    \prod_{1\leq i<j \leq n}(z_j-z_i)^{s_{ij}}|z_i-z_j-1|^{t_{ij}}
-\]
-(Zhenjie: Carefully check the notation!)
+	z_i-z_j=0\quad \text{and}\quad z_i-z_j=1\quad \text{for $1\leq i<j\leq n+1$},
+\]
+and its stringy integral is 
+\[
+\mathcal I_n = \int_{1>z_1>z_2>\cdots >z_n>0}
+\frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(1-z_1)(z_1-z_2)\cdots (z_{n}-0)}
+\prod_{0\leq i<j \leq n}(z_i-z_j)^{s_{ij}}(1-z_i+z_j)^{t_{ij}},
+\]
+where the positive region is given by $0<z_i-z_j<1$ for $1\leq i<j \leq n+1$.
 The $u$-variables of this configuration space are
@@
 where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices are living in $\mathbb Z_{2n+2}$.
-
-(u eq of $B_n$)
+They satisfy the following $u$-equations 
+\begin{align*}	
+1-u_{ij}&=\prod\limits_{j\prec k \prec i}u_k^2 u_{ki}u_{jk}\!\!\prod\limits_{j\prec k\prec l\prec i}u_{kl}^2\!\!\prod\limits_{\substack{j\prec k\prec i\\i\prec l\prec j}}u_{kl}u_{lk},\\
+1-u_{i}&=\prod\limits_{j\neq i}u_j \prod_{i\prec j\prec k\prec i}u_{jk}.
+\end{align*}
 
@@
 \begin{equation}\label{Pnfacet}
-	F_J:=\sum_{J\neq \varnothing, J\subset I} S_J=0,
+	F_I:=\sum_{J\neq \varnothing, J\subset I} S_J=0,
 \end{equation}

### 2020-03-07 draft_ABP.tex
merge from overleaf

@@
 $z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. The Shi arrangement is 
-given by the following hyperplains
+given by the following hyperplanes
 \[
@@
 \section{Stringy canonical forms and $u$-equations for generalized permutahedra}
-In this section we shall argue that  a large subset of generalised permutahedra which are realised as degenerations of permutahderon $P_n$ are binary geometries.
+In this section we shall argue that  a large subset of generalised permutahedra which are realised as degenerations of permutahderon ${\mathscr P_n}$ are binary geometries.
 Before we proceed we shall review some details about the generalised permutahedra which we shall use throughout the paper.
@@
 \end{itemize}
-We shall now talk about generalized permutahedra which are polytopes obtained by deformations of the usual permutahedron i.e., obtained by moving the vertices of the usual permutahedron so that the directions of all the edges are preserved though some of the edges may degenerate into points.
+We shall now talk about generalized permutahedra which are polytopes obtained by deformations of the usual permutahedron i.e., obtained by moving the vertices of the usual permutahedron so that the directions of all the edges are preserved or equivalently translating facets without allowing them to move past vertices which may cause some of the edges to degenerate into points.
 
@@
 A  generalised permutahedron is obtained by parallel translation of facets of the usual permutahedron it is parametrized  by a collection $\{ z_I\}$ of $2^{n+1}-1$ coordinates, for non-empty sets of $I \subset [0,n] $
- \bea
- P_n^z(\{ z_I \}) = \left \{ (t_0 , t_2, \cdots , t_{n}) \in \mathbb{R}^{n+1} | \sum_{i=0}^{n} t_i = z_{[0,n]},~ \sum_{i \in I} t_i \geq z_I, {\rm for ~subsets} ~I  \right  \} \nonumber
+ \bea \label{genperm_defi}
+ P_n^z(\{ z_I \}) = \left \{ (t_0 , t_2, \cdots , t_{n}) \in \mathbb{R}^{n+1} | \sum_{i=0}^{n} t_i = z_{[0,n]},~ \sum_{i \in I} t_i \geq z_I, {\rm for ~subsets} ~I  \right  \}
  \eea
@@
 \end{compactenum}
-
 A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
@@
 \end{compactenum}
-
 The {\it nested complex} $\mathcal{N}(B)$ is defined as the poset of the set of all nested sets in $B$ ordered by inclusion.
@@
  \eea
-is the generalised permutahedron $P_n^z(\{z_I \})$ if $z_I = \sum_{J \subset I} y_J  ~{\rm for~all~nonempty} I \subset [0,n]$.
+is the generalised permutahedron $P_n^z(\{z_I \})$ if $z_I = \sum_{J \subset I} y_J  ~{\rm for~all~nonempty}~I \subset [0,n]$.
 \footnote{Not all generalised permutahedra cannot be written as Minkowski sum of coordinate simplices.
-We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation.}
+We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation which are called Nestohedra.}
 
@@
 \end{itemize}
+\section*{Braid arrangement}
+The braid arrangement in $\mathbb{R}^{n+1}$ consists of $\left({n}\atop{2}\right)$ hyperplanes 
+\bea
+z_i =z_j ~~{\rm for ~ all}~~0 \leq i<j \leq n
+\eea
+
 In summary the above results imply that we can look at any collection of subsets of $[0, n]$ which form a building set $B$ and associate  coordinate simplex $\Delta_I$ for each $I \in B$ and resulting Minkowski sum with positive weights $y_I$ generates a generalised permutahedron associated with the building set.
@@
 
-Thus, generalised permutahedra have ``Big Polytopes" which are simplices and we can write down the stringy canonical forms and solve for the $u$-variables and examine if they satisfy some kind of $u$-equations.
-We shall do this in subsequent sections (see section(2.2)).
+Thus, generalised permutahedra have big Polytopes which are simplices and as emphasized in the previous section we can solve for the $u$-variables and examine if they satisfy some kind of $u$-equations.
 
@@
 \end{equation}
-so the number of facets of $\mathscr P_n$ is $2^n-2$. The AHBY condition 
-can be solved from above equations:
+which is the consequence of eq.\eqref{genperm_defi} and $P_n^y(\{S_I\})=P_n^z(\{F_I\})$, (Zhenjie: Right?)
+so the number of facets of $\mathscr P_n$ is $2^n-2$. 
+AHBY condition can be solved from above equations:
 \[
@@
 for all non-empty subsets $I \subset [0,n]$ which are not singlets.
-
-(Zhenjie: proof of equations of facets or ABHY condition?)
 

### 2020-03-08 draft_ABP.tex
Update draft_ABP.tex

--- 2020-03-07 draft_ABP.tex
@@
 \usepackage{epsfig,amssymb,euscript,xspace,xcolor}
-\usepackage{amsmath,mathtools,empheq,amsthm,hyperref,graphicx,paralist}
+\usepackage{amsmath,mathtools,empheq,amsthm,hyperref,graphicx}
 \usepackage{mathrsfs,float}  
@@
 Therefore, these $u$-equations reveal the binary structure of the cluster
-configuration spaces.
+configuration spaces. ...
+
+($A_n$ (sting integral?), $B_n$ (Shi arrangement?), or both from $F$-polynomial)
 
@@
 \[
-	\mathcal I_n = \int_{z_1<z_2<\cdots <z_n}
+	\int_{z_1<z_2<\cdots <z_n}
 	\frac{\mathrm dz_2\cdots \mathrm dz_{n-2}}{(z_1-z_2)\cdots (z_{n-2}-z_{n-1})}
-	\prod_{i<j} (z_j-z_i)^{\alpha' s_{ij}},
+	\prod_{i<j} (z_i-z_j)^{\alpha' s_{ij}},
 \]
 where we fix the gauge by setting $z_1=0$, $z_{n-1}=1$ and $z_n=\infty$.
-It's not in the form of stringy integrals, but we can use a positive
-parametrization 
+The $u$-variables of this configuration space are
 \[
-z_3=1+x_2,\quad z_4=1+x_2+x_3,\quad \dots, \quad 
-z_{n-1}=1+x_2+\cdots+x_{n-2}
-\]
-to rewrite the integral $\mathcal I_n$, then
-\[
-    \mathcal I_n=\int_{\mathbb R_+^{n-3}}
-	\frac{\mathrm dx_2\cdots \mathrm dx_{n-2}}{x_2\cdots x_{n-2}}
-	\prod_{i<j} p_{ij}^{\alpha' s_{ij}},
-\]
-where $p_{ij}=x_i+\cdots+x_{j-1}$. The $u$-variables of this configuration space are
-\[
-	u_{ij}=\frac{p_{i-1,j}p_{i,j-1}}{p_{ij}p_{i-1,j-1}},
+	u_{ij}=\frac{(z_{i-1}-z_j)(z_i-z_{j-1})}{(z_i-z_j)(z_{i-1}-z_{j-1})},
 \]
@@
 
-Another example still comes from a hyperplane arrangement, the Shi arrangement,
-which is also $B_n$ type cluster stringy integral.
-The Shi arrangement contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
-on the real line with the freedom of global transformation 
+(Zhenjie: we should use another parametrization of $A_n$) 
+(mention hyperplane arrangement)
+
+$B_n$: Shi arrangement
+
+The Shi arrangement of $B_n$ contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
+on the real line with the freedom corresponding to the global transformation 
 $z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. Then the Shi arrangement is 
@@
 \]
-for $1\leq i<j\leq n+1$. Its stringy integral is
-\[
-	\mathcal I_n = \int_{z_1<z_2<\cdots <z_n<0}
-	\frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(z_1-z_2)\cdots (z_{n}-z_{n+1})}
-    \prod_{1\leq i<j \leq n}(z_j-z_i)^{s_{ij}}|z_i-z_j-1|^{t_{ij}}
-\]
-(Zhenjie: Carefully check the notation!)
-The $u$-variables of this configuration space are
+for $1\leq i<j\leq n+1$.
+
+The the $u$ variables of $B_n$ can be solved by these $z_i$ by 
 \[
@@
 \subsection{Generalized permutohedra} {\bf the definition, facets and combinatorial factorizations, do $P_n$ example in full details.}
-******************************************************************************************
-\section*{Permutahedron}
- For $x_1,x_2, \cdots, x_{n+1} \in \mathbb{R} $ , the permutahedron ${\mathscr P_n}(x_1,\cdots,x_{n+1})$ is a convex polytope in $\mathbb{R}^{n+1}$ defined as the convex hull of all vectors obtained from $(x_1,x_2, \cdots, x_{n+1})$ by permutations of the coordinates:
- \bea
-{\mathscr P_n}(x_1,x_2, \cdots, x_{n+1}) = {\rm ConvexHull} \{ (x_{w(1)},x_{w(2)}, \cdots, x_{w(n+1)})~ |~ w \in S_{n+1} \}, \nonumber
- \eea
- where $S_{n+1}$ is the symmetric group.
-
- The permutahedron has $(n+1)!$ vertices and is of dimension at most $n$ since it lies in the hyperplane 
- \bea
- H_c= \{(t_1,t_2, \cdots, t_{n+1}) | t_1 + t_2 + \cdots + t_{n+1}= c \} \subset \mathbb{R}^{n+1}, \nonumber
- \eea
-where $c= x_1+x_2+ \cdots +x_{n+1}$.
-
-For $n=1$ and distinct $x_1,x_2$ the permutahedron ${\mathscr P_1}(x_1,x_2)$ is a line. If  $x_1=x_2$ then it degenerates into a single point.
-
-For $n=2$ and distinct $x_1,x_2, x_3$ the permutahedron ${\mathscr P_2}(x_1,x_2, x_3)$ is a hexagon.
-If two of the $x_i$'s are equal then the permutahedron degenerates into a triangle and if $x_1= x_2 = x_3$ then its degenerates into a single point.
-
-We shall list a few results about permutahedra which shall be useful for later purposes: 
-\begin{itemize}
-\item {\bf Coordinate independence:} The combinatorial structure of the permutahedron ${\mathscr P_n} (x_1, \cdots, x_{n+1}) $ does not depend on $ x_1, \cdots, x_{n+1} $ as long as all these are distinct.
-Henceforth  we will choose $ \{x_1, \cdots, x_{n+1}\} = \{0,1,\cdots,n \} := [0,n ]$.
-\\
-\item {\bf Facial Structure:} The $(n-k)$ faces of ${\mathscr P_n}$ are in an $1-1$ correspondence with the decomposition of $[0,n]$ into $k$ parts.
-More precisely, for each $(S_1,\cdots,S_k)$ with $S_i \neq \emptyset ~ \forall i$ and $[0,n] = S_1 \sqcup \cdots \sqcup S_k$ the corresponding face $\pi_{S_1,\cdots,S_k}$ has vertices which are permutations such that the entries $ \{x_i | i \in S_1 \}$ are largest $|S_1|$ numbers in $[0,n]$, $\{x_i | i \in S_2 \}$ are largest $|S_2|$ numbers in $[0,n]$ and so on.
-
-Further the face $\pi_{S_1,\cdots,S_k}$   is isomorphic to ${\mathscr P_{\left(| S_1|-1\right)} }\times {\mathscr P_{\left(| S_2|-1\right)} } \cdots \times{\mathscr P_{\left(| S_k|-1\right)} } $.
-
-It follows from above that ${\mathscr P_n}$ has $2^{n+1} -2$ facets corresponding to all the non-empty proper subsets of $I$ for which we have a decomposition $[0,n] = S \sqcup S^c$ and the facets are isomorphic to one of the following product of lower dimensional permutahedra  $ \{ {\mathscr P_{n-1}}, {\mathscr P_{n-2}} \times A_1, \cdots ,{\mathscr P_{\lfloor{n/2 \rfloor}}} \times {\mathscr P_{n-1-\lfloor n/2 \rfloor}}  \} $\footnote {More generally the number of $(n-k)$ facets of ${\mathscr P_n}$ is $ k!
-S(n,k)$ where $S(n,k)$ is the Stirling number of the second kind which counts the number $k$ partitions of  $I$ and there are $p(n+1,k)$ types where $p(n+1,k)$ is the number of $k$ partitions of $(n+1)$.}.
-
-It also follows from above that a face $\pi_{S_1,\cdots,S_k}$ is contained in another face $\pi_{T_1,\cdots,T_l}$ if and only if each $T_i$ is a union of consecutive $S_j$ or equivalently if $(S_1,\cdots,S_k)$ is a refinement of $(T_1,\cdots,T_l)$.
-\item {\bf Minkowski decomposition:}   Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_{n+1})$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$.
-For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull}(e_i~|~i\in I)$ denote the face of the $\Delta_{[0,n]}$.
-The polytope $P_n(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I > 0$ for all nonempty subsets $I \subset [n+1]$
- \bea
- P_n(\{y_I \})= \sum_{I \subset[n+1]} y_I . \Delta_I  \nonumber
- \eea
- is the permutahedron ${\mathscr P_n}$
-\end{itemize}
-We shall now talk about generalized permutahedra which are polytopes obtained by deformations of the usual permutahedron i.e., obtained by moving the vertices of the usual permutahedron so that the directions of all the edges are preserved though some of the edges may degenerate into points.
-
-\subsection*{Generalized permutahedra}
-
-A  generalised permutahedron is obtained by parallel translation of facets of the usual permutahedron it is parametrized  by a collection $\{ z_I\}$ of $2^{n+1}-1$ coordinates, for non-empty sets of $I \subset [0,n] $
- \bea
- P_n^z(\{ z_I \}) = \left \{ (t_0 , t_2, \cdots , t_{n}) \in \mathbb{R}^{n+1} | \sum_{i=0}^{n} t_i = z_{[0,n]},~ \sum_{i \in I} t_i \geq z_I, {\rm for ~subsets} ~I  \right  \} \nonumber
- \eea
- (a better notation for generalized permutahedron ??)
-
- If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron. 
- \begin{itemize}
- \item The combinatorial structure of the generalised permutahedron depends only on the set $B$ of nonemepty subsets $I \subset [0,n]$ such that $y_I \geq 0$ which is called the {\it building set}.
-To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
- \end{itemize}
-
-\subsection*{Nested Complex}
-If $B$ additionally satisfies the following:
-\begin{compactenum}[\quad (1)]
-    \item If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$.
-    \item $B$ contains all singletons $\{ i\}$ for $i \in S$.
-\end{compactenum}
-
-A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
-\begin{compactenum}[\quad (1)]
-    \item For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
-    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
-    \item $N$ contains all maximal elements of $B$.
-\end{compactenum}
-
-The {\it nested complex} $\mathcal{N}(B)$ is defined as the poset of the set of all nested sets in $B$ ordered by inclusion.
-
- \begin{itemize}
-\item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$.
-For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull(e_i~|~i\in I)}$ denote the face of the $\Delta_{[0,n]}$.
-The polytope $P_n^y(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I \geq 0$ for all nonempty subsets $I \subset [0,n]$
- \bea
- P_n^y(\{y_I \})= \sum_{I \subset[0,n]} y_I . \Delta_I  \nonumber
- \eea
-is the generalised permutahedron $P_n^z(\{z_I \})$ if $z_I = \sum_{J \subset I} y_J  ~{\rm for~all~nonempty} I \subset [0,n]$.
-\footnote{Not all generalised permutahedra cannot be written as Minkowski sum of coordinate simplices.
-We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation.}
-
-\item {\bf Facial structure:} Let us assume that the set $B$ associated with a generalised permutahedron $P_n^{y}$ is a building set on $[0,n]$.
-Then the poset of faces $P_n^{y}$ ordered by reverse inclusion is isomorphic to the nested complex $\mathcal{N}(B)$.
-
-For each decomposition $[0,n]=  \sqcup_{I \subset N } S_I $ where $S_I$ are non-empty, the face $P_N$ of $P_n^{y}(y_I)$ associated with the nested set $N \in \mathcal{N}(B)$ is:
-\bea
-P_N = \sum_{{J \subset B}\atop{J \cap S_I \neq \emptyset}} y_{J} \Delta_{J \cap S_I}
-\eea
-\end{itemize}
-In summary the above results imply that we can look at any collection of subsets of $[0, n]$ which form a building set $B$ and associate  coordinate simplex $\Delta_I$ for each $I \in B$ and resulting Minkowski sum with positive weights $y_I$ generates a generalised permutahedron associated with the building set.
-Further, the number of facets of the generalised permutahedron just correspond to the set of all non-singlet elements in $B$.
-
-We shall set $x_0 =1$ from now on. Since, the number of singlets correspond to the dimension of the generalised permutahedron this implies that:
-
-{\bf Number of facets = Number of linear equation + dimension of  gen permutahedron}
-
-Thus, generalised permutahedra have ``Big Polytopes" which are simplices and we can write down the stringy canonical forms and solve for the $u$-variables and examine if they satisfy some kind of $u$-equations.
-We shall do this in subsequent sections (see section(2.2)).
-
-Here are some interesting examples of generalised permutahedra:
-
-(1) If $B$ consists of only singlets i.e., $B=\{ \{ 0,1,\cdots,n \}, \{ 0 \},\{ 1 \},\cdots ,\{ n \} \}$ then the generalised permutahedron is a Simplex.
-In this case the relevant $x$ variables are $x_i,~ i=0,\cdots,n$ and $\sum_{i=0}^n x_i$.
-The Newton polytope of the Minkowski sum is $\prod_{i=1}^{n} x_i (1+\sum_{j=1}^{n} x_j)$ and $u$-variables are 
-$u_i =\frac{ x_i}{1+\sum_{i=1}^n x_i} $
-which satisfy $\sum u_i =1$ as their only $u$-equation. \\
-
-(2) If $B= \{[i] | i=1,\cdots,n+1 \}$ is the complete flag of intervals, then $P_n({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
-The Newton polytope of the Minkowski sum is $x_1\cdots x_n (1+x_1) \cdots (1+x_1+\cdots +x_n)$ and $u$-variables are 
-$u_i =\frac{ 1}{1+\sum_{j=1}^{i} x_j} $, ~~$u^{'}_i =\frac{ \sum_{j=1}^{i} x_j}{1+\sum_{j=1}^{i} x_j} $ for $j=1,\cdots,n$ \\
-which satisfy $u_i +u^{'}_{i} =1$ as their $u$-equation. \\
-
-(3) If $B$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then $P_n({\bf Y})$ is the usual permutahedron $P_n$.
-
-(4)If $B=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then $P_n({\bf Y})$ is the associahedron.
-
-(5) If $B=\{ [1,i] \cup [j,n] | 1\leq  i \leq j \leq n\}$ is the set of cyclic intervals, then $P_n({\bf Y})$ is the Cyclohedron.
-
-The cases (4) and (5) will be considered in section (3.2). In this section we shall restrict ourselves to the permutahedron example ${\mathscr P_n}$.  
+
 \subsection{Natural stringy integrals with linear factors}
@@
 {\bf argue in general to have binary geometries we must have $1-u=\prod u' p(\{u\})$ with $p(u=0)=1$, conjecture that this is true fo ALL gen. perm. Show it for gen. perm. more examples?}
+
+(Chi: I have checked several examples of graph associahedra, there is a conjecture for $u$ variables for this kind of generalized permutohedra: \\
+For a element $I$ in the building set $\mathcal{B}$, we define $I_{\text{max}}=\Bigl(\bigcup_{j\sim I} \{j\} \Bigr)\cup I$
+where $j\sim I$ means the singleton $j$ is attached to $I$ in the corresponding graph, then 
+\begin{equation}
+   u_{I} = \prod_{ I \subset J \subset I_{\text{max}}}x_J^{(-1)^{|I|-|J|}}.
+\end{equation}
+This conjecture can easily be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
+)
+
+\subsubsection{Example: Binary geometries for Cayley graph, graph associahedra and generalized permutohedra. }
+
+In the above, we have shown that the binary geometries exist for permutohedra even through the $u$ equtions are not perfect and conjecture that such binary geometries exist for generalized permutohedra.
+In the remainder of this section, we will give more example on such binary geometries without perfect $u$ equtions.
+
+We start with the Cayley graph proposed in \cite{} and further studied in \cite{}.
+In \cite{}, the ABHY realization for general Cayley graphs have been proposed, here we will use several examples to illustrate that the binary geometries exist for general Cayley graphs.
+The first Cayley graph which is nether associahedron nor permutahderon is so-called  ``next-to-$A_{3}$'', in terms of generalized permutahdera, the building set for next-to-$A_{3}$ is
+\begin{equation}
+   \mathscr{NA}_{3}=\{\{1,2,3,4\},\{1,2,3\},\{1,3,4\},\{2,3,4\},\{1,2\},\{1,3\},\{2,3\},\{3,4\},\{1\},\{2\},\{3\},\{4\}\}
+\end{equation}
+
+the $u$ variables are 
+\begin{align}
+   &u_{1}=\frac{x_{1}x_{123}}{x_{12}x_{13}} \:, \quad  u_{2}=\frac{x_{2}x_{123}}{x_{12}x_{23}} \:,  \quad 
+   u_{3}=\frac{x_{3}x_{134}x_{234}x_{123}}{x_{34}x_{13}x_{23}x_{1234}} \:, \quad 
+   u_{4}=\frac{x_{4}}{x_{34}} \\
+   &u_{12}=\frac{x_{12}}{x_{123}} \:, \quad u_{13}=\frac{x_{13}x_{1234}}{x_{134}x_{123}} \:,\quad 
+   u_{23}=\frac{x_{23}x_{1234}}{x_{123}x_{234}} \:, \quad u_{34}=\frac{x_{34}x_{1234}}{x_{134}x_{234}} \\
+   &u_{123}=\frac{x_{123}}{x_{1234}} \:, \quad u_{134}=\frac{x_{134}}{x_{1234}} \:, \quad 
+   u_{234}=\frac{x_{234}}{x_{1234}}
+\end{align}
+The $u$ equations are
+\begin{align}
+   &1-u_{1}=u_{2}u_{3}u_{23}^{2}u_{34}u_{234}^{2} \:, \\
+   &1-u_{2}=u_{1}u_{3}u_{13}^{2}u_{34}u_{123}^{2} \:, \\
+   &1-u_{3}= u_{1}u_{2}u_{4}u_{12}^{2}(1+u_{3}u_{13}u_{23}u_{34}u_{123}u_{134}u_{234}) \:, \\
+   &1-u_{4}=u_{3}u_{13}u_{23}u_{123}  \:, \\
+   &1-u_{12} =u_{3}u_{13}u_{23}u_{34}u_{134}u_{234} \:, \\
+   &1-u_{13} =u_{2}u_{4}u_{12}u_{23}u_{34}u_{234}^{2} \:, \\
+   &1-u_{23}= u_{1}u_{4}u_{12}u_{13}u_{34}u_{134}^{2} \:, \\
+   &1-u_{34}= u_{1}u_{2}u_{12}^{2}u_{13}u_{23}u_{123}^{2} \:, \\
+   &1-u_{123}=u_{4}u_{34}u_{134}u_{234} \:, \\
+   &1-u_{134}=u_{2}u_{12}u_{23}u_{123}u_{234} \:, \\
+   &1-u_{234}=u_{1}u_{12}u_{13}u_{123}u_{134} \:, 
+\end{align}
 

### 2020-03-08 draft_ABP.tex
update 2.2

--- 2020-03-07 draft_ABP.tex
@@
  \bea \label{genperm_defi}
- P_n^z(\{ z_I \}) = \left \{ (t_0 , t_2, \cdots , t_{n}) \in \mathbb{R}^{n+1} | \sum_{i=0}^{n} t_i = z_{[0,n]},~ \sum_{i \in I} t_i \geq z_I, {\rm for ~subsets} ~I  \right  \}
+ P_n^z(\{ z_I \}) = \left \{ (t_0 , t_1, \cdots , t_{n}) \in \mathbb{R}^{n+1} | \sum_{i=0}^{n} t_i = z_{[0,n]},~ \sum_{i \in I} t_i \geq z_I, {\rm for ~subsets} ~I  \right  \}
  \eea
@@
 because each facet $F_I$ is given by a nested set $\{[0,n],I\}$ for $I\neq [0,n]$.
-Therefore, for a generalized permutahedron $\mathscr P$, we can write the matrix 
-$W^J_A$ of facets and get the ABHY conditions $S_J=F_A(W^{-1})^A_J\geq 0$ and 
+Therefore, for a generalized permutahedron $\mathscr P$, we can write down the matrix 
+$W^J_A$ of facets and then get the ABHY conditions $S_J=F_A(W^{-1})^A_J\geq 0$ and 
 its $u$-variables $u_A=\prod_J p_J^{(W^{-1})^A_J}$.
 
-***
-
-($P_n$)
-
-As shown in the last subsection, the $n$-dimensional permutahedron is associated 
-with the set of all non-empty subsets of $[0,n]$, which is denoted by $\mathscr P_n$. 
-Each facet of $\mathscr P_n$ is lebeled by a non-empty proper subset $I$ of $[0,n]$, 
-whose equation is 
-\begin{equation}\label{Pnfacet}
-	F_I:=\sum_{J\neq \varnothing, J\subset I} S_J=0,
+Let's first write down equations of facets of a generalised permutahedron
+with the building set $\mathscr P$. The ABHY polytope of 
+eq.\eqref{stringyintforgenpermutohedron} is given by the Minkowski sum
+\[
+	- \sum_{I\in\mathscr P,|I|>1}S_I.\Delta_I
+\]
+in $(S_0,\dots,S_n)$-space, where $\Delta_I=\operatorname{ConvexHull}
+(\{e_i\}_{i\in I})$. Meanwhile, we know from the last subsection that the facet 
+labeled by a nested set $\{[0,n],I\}$ is given by
+\begin{align*}
+	\biggl\{(S_0,S_1,\dots,S_n)\in \mathbb R^{n+1}\,\bigg |\,
+		\sum_{i\in I}S_i = -\sum_{J\subset I,|J|>1,J\in \mathscr P}S_J,
+		\quad
+		&\sum_{i=0}^nS_i=-\sum_{J\in \mathscr P,|J|>1}S_J,\\
+		&\sum_{i\in K}S_i\geq -\sum_{J\subset I,|J|>1,J\in \mathscr P}S_J
+	\biggr\},
+\end{align*}
+where the second constrain is just $\sum_{I\in \mathscr P}S_I=0$, so the equation 
+of this facet is 
+\begin{equation}\label{GPfacet}
+	F_I:=\sum_{J\subset I,J\in\mathscr P}S_J=0.
 \end{equation}
-which is the consequence of eq.\eqref{genperm_defi} and $P_n^y(\{S_I\})=P_n^z(\{F_I\})$, (Zhenjie: Right?)
-so the number of facets of $\mathscr P_n$ is $2^n-2$. 
-AHBY condition can be solved from above equations:
+
+Within all generalized permutahedrons, the original permutahedron is quite simple
+and important because any other generalized permutahedron can be degenerated from
+permutahedron by setting some $S_I$ to be zero.
+The building set of the $n$-dimensional permutahedron $\mathscr P_n$ is 
+the set of all non-empty subsets of $[0,n]$. AHBY conditions can be solved from 
+eq.\eqref{GPfacet}
 \[
@@
 for all non-empty subsets $I \subset [0,n]$ which are not singlets.
-
-To get $u$-equations, we should solve $S_J$ by $F_J$ from eq.\eqref{Pnfacet}, the 
-solution is 
+To get $u$-equations, we should solve $S_J$ by $F_J$ from eq.\eqref{GPfacet}, the 
+solution for permutahedron $\mathscr P_n$ is 
 \begin{equation}\label{SinF}
@@
 We will discuss these $u$-equations in the next subsection.
-
-For a $n$-dimensional general permutahedron $\mathscr A$, it can be achieved 
-from $\mathscr P_n$ by setting $S_J$ to be $0$ for any 
-$J\in \mathscr P_n-\mathscr A$. Facets of $\mathscr A$ are degenerations of facets 
-of $\mathscr P_n$ eq.\eqref{Pnfacet}, but some of them become spurious. If a pole
-is spurious, it can be written as a positive linear combination of some true facets.
-Such relations are sequence of eq.\eqref{SinF} for $I\not\in \mathscr A$.
-For example, for $\mathscr A=\{123,12,23,1,2,3\}$, we have that
-\[
-	0=S_{13}=F_{13}-F_{1}-F_{3},
-\]
-so $F_{13}$ is not a true facet of $\mathscr A$, there're only $5$ facets left in
-$\mathscr A$.
-
-(Zhenjie: Are facets of $\mathscr A$ associated with $J$ just the $F_J$ of $\mathscr P_n$ after setting all $S_I=0$ for $I\not\in \mathscr A$? How to prove it?)
 

### 2020-03-08 draft_ABP.tex
Updates from Overleaf

--- 2020-03-08 draft_ABP.tex
@@
 \end{equation}
-This conjecture can easily be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
+This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
 )

### 2020-03-08 draft_ABP.tex
update 1.1

@@
 
-(stringy canonical form)
-
-The $\mathcal I(\mathbf X,\{c\})$ is convergent when $\mathbf X$ is contained inside
-the Minkowski sum $\mathcal P=\sum_I c_I \mathcal P_I$ of Newton polytopes 
-$\mathcal P_I=\mathbf N[p_I]$. For a facet $F_a$ of $\mathcal P$, this condition 
-requires that $\mathbf X$ should lay on one side of $F_a$ which is equivalent to 
-an inequality of variables $\mathbf S=(X_1,\dots,X_d,-c_1,\dots,-c_m)$, 
-$W_a^JS_J\geq 0$, where $W_a^J$ is determined by the facet $F_a$. 
-These inequalities cut out a polyhedron in the $(d+m)$-dimensional space of 
+Stringy canonical forms (or stringy integral) are generalizations of tree level string integrals
+\begin{equation}\label{stringint}
+\int_{\mathcal M_{0,n}^+}
+\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i+1}}
+\prod_{i<j}(z_j-z_i)^{\alpha' s_{ij}},
+\end{equation}
+where $\mathcal M_{0,n}^+$ is the postive part of moduli space of $n$ punctures on
+the Riemann sphere.
+In the context of stringy canonical form, the form $\mathsf{PT}(n):=\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i+1}}$ is understood
+as the canonical form of the moduli space $\mathcal M_{0,n}^+$, and each factor 
+$(z_j-z_i)$ in the Kobe-Nieson factor $\prod_{i<j}(z_j-z_i)^{\alpha' s_{ij}}$ 
+is a nowhere vanishing function on $\mathcal M_{0,n}^+$.
+With a positive parameterization $\{x_1,\dots,x_{n-3}\}$ of $\mathcal M_{0,n}^+$, 
+this canonical form becomes $\prod_{i=1}^{n-3}\mathrm d \log x_i$, 
+the Koba-Nieson factor becomes a product of powers of some polynomials with 
+non-negative coefficients, and the string integral turns into the form
+\begin{equation}\label{stringycanonicalform}
+	\mathcal I(\mathbf X,\{c\})=
+	\int_{\mathbb R_+^d}\prod_{i=1}^d \frac{\mathrm d x_i}{x_i}x_i^{\alpha'X_i}
+	\prod_{I=1}^m p_I(x)^{-\alpha' c_I},
+\end{equation}
+where $p_I$ are polynomials with non-negative coefficients. For general stringy
+canonical forms eq.\eqref{stringycanonicalform}, we allow $p_I$ to be any Laurent 
+polynomial with non-negative coefficients in the integral.
+
+Many remarkable aspects of string integral, \textit{e.g.} field-theory limit, 
+factorization, scattering equations, $u$-variables ..., can be carried to
+stringy canonical forms. Almost all of these aspects are related to a hidden 
+polytope $\mathcal P=\sum_I c_I N[p_I]$ of string canonical form 
+eq.\eqref{stringycanonicalform}, where $N[p_I]$ is the Newton polytope of $p_I$ and 
+the sum is understood as the Minkowski sum. For example, 
+eq.\eqref{stringycanonicalform} is convergent if and only if 
+$\mathbf X=(X_1,\dots,X_D)$ is in the interior of $\mathcal P$, equations of
+facets of $\mathcal P$ are massless poles of eq.\eqref{stringycanonicalform}
+and the residue on this facet is still a stringy canonical form of this facet.
+For stringy integrals eq.\eqref{stringint}, these polytopes are nothing but the ABHY
+associahedra~\cite{}.
+
+This polytope can also be realized in $\mathbf x$-space and understood
+as a blow-up of $\mathbb R_+^D$, but it's usually difficult to use $\mathbf x$ to
+describe this polytope, even for the string integrals eq.\eqref{stringint}. For
+example, a facet may correspond to a complicated limit process of $\mathbf x\to 0$
+or $\infty$.
+%However, as proven in \cite{},
+%the saddle point equations of the Kobe-Nieson factor, \textit{i.e} scattering equations,
+%\[
+	%\frac{\partial}{\partial x_i}\left(
+	%\prod_{i=1}^d x_i^{\alpha'X_i} \prod_I p_I(x)^{-\alpha' c_I},
+	%\right)=0\quad \text{for all $i$}
+%\]
+%give us a diffeomorphism between the interiors of two polytopes in different spaces.
+However, for a limited class of stringy canonical forms, we can introduce
+the so-called $u$-variables $\{u_A\}$ to replace $\mathbf x$ such that the polytope 
+is described by $\{u_A\geq 0\}$ and a set of polynomial equations of $\{u_A\}$, and each
+facet is simply given by an equation $u_A=0$. One way to construct these $u$-variables
+is first constructing variables $\{U_A\}$ with similar properties in the space of
+$\mathbf S=(X_1,\dots,X_d,-c_1,\dots,-c_m)$ such that $\mathcal P=\sum_I c_I N[p_I]$ 
+is simply given by $\{U_A\geq 0\}$ and each facet is given by a $U_A=0$, and then
+relating $\{U_A\}$ to $\{u_A\}$ by the integral
+\[
+	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
+	\prod_{A}u_A^{\alpha' U_A}
+	=
+	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
+	\prod_{J}p_J^{\alpha' S_J}.
+\]
+
+The construction of $\{U_A\}$ comes from the viewpoint of \textit{big polyhedron}.
+The polytope $\mathcal P=\sum_I c_I N[p_I]$ is bounded by the inequalites
+$W_a^JS_J\geq 0$ of variables $\mathbf S=(X_1,\dots,X_d,-c_1,\dots,-c_m)$ in space 
+of $\mathbf X$, where $W_a^J$ is determined by the facet $F_a$ of $\mathcal P$. 
+These inequalities also cut out a polyhedron in the $(d+m)$-dimensional space of 
 $\mathbf S$, which is called the \textit{big polyhedron} of $\mathcal P$, 
@@
 $\{V_J^A\}_{1\leq A\leq v}$ are its non-zero vertices, the point $\mathbf S$ inside 
-the polyhedron can be written as $S_J = U_A V^A_J$ with non-nagetive coefficients 
+the polyhedron can be written as $S_J = U_A V^A_J$ with non-negative coefficients 
 $\{U_A\}_{1\leq A\leq v}$.  Therefore, the integral $\mathcal I(\mathbf S)$
@@
 $u$-variables $\{u_A\}$ are not independent. 
-When the big polyhdron is a simplex, \textit{i.e.} $N=v=d+m$, where $N$ is 
-the number of facets of the big polyhdron or the original polytope $\mathcal P$,
+When the big polyhedron is a simplex, \textit{i.e.} $N=v=d+m$, where $N$ is 
+the number of facets of the big polyhedron or the original polytope $\mathcal P$,
 and inequalities $U_A=S_J(V^{-1})^J_A\geq 0$ are exactly the inequalities
@@
 there's no nontrivial linear isometry from the simplex to itself besides permutations
-of vertices. Therefore, we identity the labal of facets $a$ with the label of 
+of vertices. Therefore, we identity the label of facets $a$ with the label of 
 vertices $A$ and get $V=W^{-1}$. Furthermore, every facet of the original polytope
@@
 
-Generally, the big polyhdron of a stringy integral is not necessary to be a simplex.
+Generally, the big polyhedron of a stringy integral is not necessary to be a simplex.
 It's known that stringy integrals associated to the $A_n$, $B_n$, $C_n$, $D_n$,

### 2020-03-08 draft_ABP.tex
merge from overleaf

--- 2020-03-08 draft_ABP.tex
@@
 \begin{itemize}
-\item {\bf Coordinate independence:} The combinatorial structure of the permutahedron ${\mathscr P_n} (x_1, \cdots, x_{n+1}) $ does not depend on $ x_1, \cdots, x_{n+1} $ as long as all these are distinct.
+\item {\bf Parameter independence:} The combinatorial structure of the permutahedron ${\mathscr P_n} (x_1, \cdots, x_{n+1}) $ does not depend on $ x_1, \cdots, x_{n+1} $ as long as all these are distinct.
 Henceforth  we will choose $ \{x_1, \cdots, x_{n+1}\} = \{0,1,\cdots,n \} := [0,n ]$.
@@
 
-It follows from above that ${\mathscr P_n}$ has $2^{n+1} -2$ facets corresponding to all the non-empty proper subsets of $I$ for which we have a decomposition $[0,n] = S \sqcup S^c$ and the facets are isomorphic to one of the following product of lower dimensional permutahedra  $ \{ {\mathscr P_{n-1}}, {\mathscr P_{n-2}} \times A_1, \cdots ,{\mathscr P_{\lfloor{n/2 \rfloor}}} \times {\mathscr P_{n-1-\lfloor n/2 \rfloor}}  \} $\footnote {More generally the number of $(n-k)$ facets of ${\mathscr P_n}$ is $ k!
+It follows from above that ${\mathscr P_n}$ has $2^{n+1} -2$ facets corresponding to all the non-empty proper subsets of $[0,n]$ for which we have a decomposition $[0,n] = S \sqcup S^c$ and the facets are isomorphic to one of the following product of lower dimensional permutahedra  $ \{ {\mathscr P_{n-1}}, {\mathscr P_{n-2}} \times A_1, \cdots ,{\mathscr P_{\lfloor{n/2 \rfloor}}} \times {\mathscr P_{n-1-\lfloor n/2 \rfloor}}  \} $\footnote {More generally the number of $(n-k)$ facets of ${\mathscr P_n}$ is $ k!
 S(n,k)$ where $S(n,k)$ is the Stirling number of the second kind which counts the number $k$ partitions of  $I$ and there are $p(n+1,k)$ types where $p(n+1,k)$ is the number of $k$ partitions of $(n+1)$.}.
@@
  \eea
- (a better notation for generalized permutahedron ??)
-
  If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron.
+
+ Unlike the permutahedron not all generalised permutahedra can be represented as a Minkowski sum of co-ordinate simplices.
+We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation which are called Nestohedra which we denote by ${\mathscr N}$.
+Throughout the paper we shall mean Nestohedra whenever we refer to generalized permutahedra unless stated otherwise.
  \begin{itemize}
- \item The combinatorial structure of the generalised permutahedron depends only on the set $B$ of nonemepty subsets $I \subset [0,n]$ such that $y_I \geq 0$ which is called the {\it building set}.
-To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
+ \item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
+  \bea
+{\mathscr N_n}^y(\{y_I \})= \sum y_I . \Delta_I  \nonumber
+ \eea
+ for some collection of subsets $I \in [0,n]$
  \end{itemize}
-
-\subsection*{Nested Complex}
-If $B$ additionally satisfies the following:
+  \begin{itemize}
+ \item{\bf Parameter Independence:} The combinatorial structure of the generalised permutahedron ${\mathscr N_n({y_I})}$ is independent of the parameters $y_I$ and depends only on the collection of subsets $I \in [0,n]$ called the  building set $B$.
+\end{itemize}
+A collection of non-empty subsets of $[0,n]$ is called a building set $B$ if it satisfies the following:
 \begin{compactenum}[\quad (1)]
@@
 \end{compactenum}
+To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
+\subsection*{Nested Complex}
 A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
@@
  \begin{itemize}
-\item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$.
-For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull(e_i~|~i\in I)}$ denote the face of the $\Delta_{[0,n]}$.
-The polytope $P_n^y(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I \geq 0$ for all nonempty subsets $I \subset [0,n]$
- \bea
- P_n^y(\{y_I \})= \sum_{I \subset[0,n]} y_I . \Delta_I  \nonumber
- \eea
-is the generalised permutahedron $P_n^z(\{z_I \})$ if $z_I = \sum_{J \subset I} y_J  ~{\rm for~all~nonempty}~I \subset [0,n]$.
-\footnote{Not all generalised permutahedra cannot be written as Minkowski sum of coordinate simplices.
-We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation which are called Nestohedra.}
-
-\item {\bf Facial structure:} Let us assume that the set $B$ associated with a generalised permutahedron $P_n^{y}$ is a building set on $[0,n]$.
-Then the poset of faces $P_n^{y}$ ordered by reverse inclusion is isomorphic to the nested complex $\mathcal{N}(B)$.
-
-For each decomposition $[0,n]=  \sqcup_{I \subset N } S_I $ where $S_I$ are non-empty, the face $P_N$ of $P_n^{y}(y_I)$ associated with the nested set $N \in \mathcal{N}(B)$ is:
+
+\item {\bf Facial structure:} Let us assume that the set $B$ associated with a generalised permutahedron ${\mathscr N_n}^{y}$ is a building set on $[0,n]$.
+Then the poset of faces ${\mathscr N_n}^{y}$ ordered by reverse inclusion is isomorphic to the nested complex $\mathcal{N}(B)$.
+
+For each decomposition $[0,n]=  \sqcup_{I \subset N } S_I $ where $S_I$ are non-empty, the face $P_N$ of ${\mathscr N_n}^{y}(y_I)$ associated with the nested set $N \in \mathcal{N}(B)$ is:
 \bea
@@
 \end{itemize}
-\section*{Braid arrangement}
-The braid arrangement in $\mathbb{R}^{n+1}$ consists of $\left({n}\atop{2}\right)$ hyperplanes 
-\bea
-z_i =z_j ~~{\rm for ~ all}~~0 \leq i<j \leq n
-\eea
 
 In summary the above results imply that we can look at any collection of subsets of $[0, n]$ which form a building set $B$ and associate  coordinate simplex $\Delta_I$ for each $I \in B$ and resulting Minkowski sum with positive weights $y_I$ generates a generalised permutahedron associated with the building set.
-Further, the number of facets of the generalised permutahedron just correspond to the set of all non-singlet elements in $B$.
-
-We shall set $x_0 =1$ from now on. Since, the number of singlets correspond to the dimension of the generalised permutahedron this implies that:
-
-{\bf Number of facets = Number of linear equation + dimension of  gen permutahedron}
+Further, the number of facets $N$ of the generalised permutahedron just corresponds to the set of all elements in $B$ excluding the maximal set.
+
+Let, $m$ denote the number of non-singlet elements in $B$ i.e., the number of linear equations as explained in (1.1) 
+\bea
+N &=& |B|-1 \nonumber \\
+ &=& (n+1+m)-1 \nonumber  \\
+ &=& n+m \nonumber
+\eea
+{\bf Number of facets = Number of linear equations + dimension of  gen permutahedron}
 
@@
 (1) If $B$ consists of only singlets i.e., $B=\{ \{ 0,1,\cdots,n \}, \{ 0 \},\{ 1 \},\cdots ,\{ n \} \}$ then the generalised permutahedron is a Simplex.
-In this case the relevant $x$ variables are $x_i,~ i=0,\cdots,n$ and $\sum_{i=0}^n x_i$.
+In this case the relevant $x$ variables are $x_i,~ i=0,\cdots,n$ with $x_0=1$ and $\sum_{i=0}^n x_i$.
 The Newton polytope of the Minkowski sum is $\prod_{i=1}^{n} x_i (1+\sum_{j=1}^{n} x_j)$ and $u$-variables are 
@@
 
-(2) If $B= \{[i] | i=1,\cdots,n+1 \}$ is the complete flag of intervals, then $P_n({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
+(2) If $B= \{[i] | i=1,\cdots,n+1 \}$ is the complete flag of intervals, then ${\mathscr N_n}^y({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
 The Newton polytope of the Minkowski sum is $x_1\cdots x_n (1+x_1) \cdots (1+x_1+\cdots +x_n)$ and $u$-variables are 
@@
 
-(3) If $B$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then $P_n({\bf Y})$ is the usual permutahedron $P_n$.
-
-(4)If $B=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then $P_n({\bf Y})$ is the associahedron.
-
-(5) If $B=\{ [1,i] \cup [j,n] | 1\leq  i \leq j \leq n\}$ is the set of cyclic intervals, then $P_n({\bf Y})$ is the Cyclohedron.
-
-The cases (4) and (5) will be considered in section (3.2). In this section we shall restrict ourselves to the permutahedron example ${\mathscr P_n}$.  
+(3) If $B$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then ${\mathscr N_n}({\bf Y})$ is the usual permutahedron $P_n$.
+\\
+
+(4)If $B=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr N_n}({\bf Y})$ is the associahedron. \\
+
+(5) If $B=\{ [1,i] \cup [j,n] | 1\leq  i \leq j \leq n\}$ is the set of cyclic intervals, then ${\mathscr N_n}({\bf Y})$ is the Cyclohedron.\\
+
+(6) Let $\Gamma$ be a graph on the vertex set $[0,n]$.
+Let us assume that $B = B(\Gamma)$ is the set of subsets $I \in [n]$ such that the induced graph $\Gamma$ is connected, then  ${\mathscr N_n}({\bf Y})$ is a graph associahedron.\\
+
+\section*{Braid arrangement}
+The braid arrangement in $\mathbb{R}^{n+1}$ consists of $\left({n}\atop{2}\right)$ hyperplanes 
+\bea
+z_i =z_j ~~{\rm for ~ all}~~0 \leq i<j \leq n
+\eea 
 \subsection{Natural stringy integrals with linear factors}
@@
 \]
-They satisfy the following equtions
+They satisfy the following equations
 \begin{align*}
@@
 
-{\bf argue in general to have binary geometries we must have $1-u=\prod u' p(\{u\})$ with $p(u=0)=1$, conjecture that this is true fo ALL gen. perm. Show it for gen. perm. more examples?}
+{\bf argue in general to have binary geometries we must have $1-u=\prod u' p(\{u\})$ with $p(u=0)=1$, conjecture that this is true of ALL gen. perm. Show it for gen. perm. more examples?}
 
@@
 In the above, we have shown that the binary geometries exist for permutohedra even through the $u$ equtions are not perfect and conjecture that such binary geometries exist for generalized permutohedra.
-In the remainder of this section, we will give more example on such binary geometries without perfect $u$ equtions.
+In the remainder of this section, we will give more example on such binary geometries without perfect $u$ equations.
 
@@
 \end{align} 
-
+\subsection{Permutahedron as a binary geometry}
+In this section we shall try to argue that the permutahedron is a binary geometry. We shall first summarise the following facts about the permutahedron from our discussion in the earlier sections:
+\begin{enumerate}
+\item The $u$-variables for the permutahedron are: 
+\bea
+u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber \\
+u^{'}_J &=& \prod_{{0 \in I}\atop{ \{0,\cdots,n\} - I \subset J}} x_I^{(-1)^{|I|-|J|+mod(n, 2)}} \nonumber
+\eea
+From above it is evident that $u^{'}_{I} = u_{\bar{I}} $ where $\bar{I}=[0,n]-I$ for all subsets $I$ that do not contain $0$.
+And the $2^{n+1}-2$ facets corresponding to proper subsets of $[0,n]$ correspond to the two copies of the $2^{n}-1$ non-empty subsets of $[1,n]$.
+
+\item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :
+
+{\bf compatible if} $I\cap J = \emptyset$ or $I\cap J \neq \emptyset$ and either $I \subset J$ or $J \subset I$
+
+{\bf incompatible if}   $I\cap J \neq \emptyset$ or $I\cap J = \emptyset$ and neither $I \not\subset J$ or $J \not\subset I$
+
+Thus, each $u_I$ is compatible with itself and incompatible with $u^{'}_I$.
+
+\item  Since, the permutahedron is permutation invariant in all $x_i$'s this should be reflected at the level of $u$'s and all $u_I$ and $u^{'}_{J}$ with the same $|I|$ and $|J| =n-|I|$ should have similar $u$-equations.
+We see that this is indeed the case :
+
+Some of the $u$-equations for the $n$-dimensional permutahderon:\\
+
+For $|I| =n-1$ and $s_K = \begin{cases}  1,~ if K \not\subset I & \\ 2, ~if K \subset I\end{cases}$
+
+\bea
+1-u_{I} &=& \prod_ {S - I \subset J } u_{J} \prod_ {K \cap I \ne \Phi } (u^{'}_{K})^{s_K}  \nonumber \\
+1-u_{12\cdots n} &=& \prod_ {{I \subset S}\atop {I \ne \Phi}} u^{'}_{I} \nonumber
+\eea
+
+For $t_J = \begin{cases}  1,~ if I  \not\subset J & \\ 2, ~if I \subset J \end{cases}$
+
+\bea
+1-u^{'}_{i} &=& \prod_ {\{ i \} \subset J } u_{J} \prod_ {K \subset S- \{i\} } u^{'}_{K} \nonumber \\
+1-u^{'}_{i j} &=& \prod_ {\{i,j \}\cap J \ne \Phi} u^{t_J}_{J} \prod_ {K \subset S-\{i, j \} } (u^{'}_{K})^{2} u^{'}_{K \cup {i}} u^{'}_{K \cup{j} } \nonumber 
+\eea
+
+and for $|I| =n-2$ with $S- I = \{i, j\}$
+
+\bea
+1-u_{I}= u_i u_j u^{2}_{ij} \prod_{J \subset I} u_{J \cup \{i\}} u_{J \cup \{j\}} u^{2}_{J \cup \{i,j\}} \prod_{K \subset S-I} (u^{'}_K)^{3} (u^{'}_{K \cup \{i\}})^{2}  (u^{'}_{K \cup\{j\}})^{2}  u^{'}_{K\cup \{i,j\}} \left( 1+ u^{'}_i u^{'}_j u^{'}_{ij} \prod_{I \subset L} u_L \right)                       \nonumber
+\eea
+
+The other $u$-equations are not two or three term equations and seem to be polynomials of order $|I|=n-2$ in the corresponding $u$'s.Thus, the most general $u$-equations can be conjectured to be:
+\bea
+1-u_{I} = \prod_{J} u^{s_J}_{J} P_{|I|}(u_I, u_J,u_K) 
+\eea
+where, $J$ are all sets incompatible with $I$
+
+ $K$ are all sets compatible with $I$ excluding itself
+
+  $s_J$ are positive integers. 
+\end{enumerate}
+We shall now try to argue ${\mathscr P_n}$ is binary. We proceed inductively by first noticing that 
 \section{Configuration spaces with perfect $u$-equations from degenerating $A_n$ and $B_n$}
@@
 *******************
+\subsection*{Degenerations which lead to products}
+In this section we provide an answer to the question of which degenerations of $A_n$ and $B_n$ give the most general products of such geometries.
+We begin by stating the following results about Nestohedra.
+
+The maximal set of a building set $B_{max}$ is the set of all inclusion maximal elements of the building set $B$. A building set $B$ is connected if $B_{max}$ has a single element.
+
+{\bf Theorem:}If $B_1, B_2,\cdots B_n$ are connected subsets of a building set $B$ then the corresponding nestohedron ${\mathscr N_B}$ is isomorphic to the product of the nestohedra ${\mathscr N}_{ B_1} \times{\mathscr N}_{ B_2} \cdots \times {\mathscr N}_{B_n}$.
 

### 2020-03-09 draft_ABP.tex
merge from overleaf

@@
 The construction of $\{U_A\}$ comes from the viewpoint of \textit{big polyhedron}.
-The polytope $\mathcal P=\sum_I c_I N[p_I]$ is bounded by the inequalites
+The polytope $\mathcal P=\sum_I c_I N[p_I]$ is bounded by the inequalities
 $W_a^JS_J\geq 0$ of variables $\mathbf S=(X_1,\dots,X_d,-c_1,\dots,-c_m)$ in space 
@@
 
-Within all generalized permutahedrons, the original permutahedron is quite simple
+Within all generalized permutahedra, the original permutahedron is quite simple
 and important because any other generalized permutahedron can be degenerated from
@@
 {\bf Theorem:}If $B_1, B_2,\cdots B_n$ are connected subsets of a building set $B$ then the corresponding nestohedron ${\mathscr N_B}$ is isomorphic to the product of the nestohedra ${\mathscr N}_{ B_1} \times{\mathscr N}_{ B_2} \cdots \times {\mathscr N}_{B_n}$.
+
+We can use the above result to construct 	a degeneration of $A_n$ which is a most general product i.e., $\prod_{p_i} A_{p_i}$ such that $\sum_{i} p_{i} = n$.
+
+Let us consider the  $A_4$ example for which the allowed possibilities are : $A_1^{4}$, $A_1^2 \times A_2$, $A_1 \times A_3$ and $A^{2}_2$.
+
+For the $A_1^{4}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} \}$ where $\{0,01\} , \{1,12\},\{2,23\},\{3,34\}$ generate the 4 $A_1$'s.
+
+For the $A_1^{2} \times A_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{234} \}$ where $\{0,01\} , \{1,12\} $ generate the 2 $A_1$'s and $\{2,3,4,23,34,234\}$ generates the $A_2$'s.
+
+For the $A_1 \times A_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{123},{234},{1234} \}$ where $\{0,01\}$ is the generates the $A_1$ and $\{{1},{2},{3},{4},{12},{23},{34},{123},{234},{1234} \}$ generate  $A_3$'s.
+
+For the $A_2^{2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} ,{012},{234}\}$ where $\{0,1,2,01,12,012\}$  and $\{2,3,4,23,34,234\}$ generate the 2 $A_2$'s.
+
+We can similarly find a degeneration of $A_n,B_n,~or~ {\mathscr P_n}$ which would correspond to any product.
 

### 2020-03-09 draft_ABP.tex
update

--- 2020-03-08 draft_ABP.tex
@@
 \]
-where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices are living in $\mathbb Z_{2n+2}$.
+where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices live in $\mathbb Z_{2n+2}$.
 They satisfy the following $u$-equations 
@@
 1-u_{ij}&=\prod\limits_{j\prec k \prec i}u_k^2 u_{ki}u_{jk}\!\!\prod\limits_{j\prec k\prec l\prec i}u_{kl}^2\!\!\prod\limits_{\substack{j\prec k\prec i\\i\prec l\prec j}}u_{kl}u_{lk},\\
-1-u_{i}&=\prod\limits_{j\neq i}u_j \prod_{i\prec j\prec k\prec i}u_{jk}.
+1-u_{i}&=\prod\limits_{j\neq i}u_j \prod_{i\prec j\prec k\prec i}u_{jk},
 \end{align*}
+where labels are vertices of a $n$-gon and $\prec$ is the counterclockwise order on
+the $n$-gon.
 
@@
 The building set of the $n$-dimensional permutahedron $\mathscr P_n$ is 
-the set of all non-empty subsets of $[0,n]$. AHBY conditions can be solved from 
-eq.\eqref{GPfacet}
-\[
-	S_I = (-1)^{|I|+1}\sum_{i\in I} S_i,
-\]
-for all non-empty subsets $I \subset [0,n]$ which are not singlets.
+the set of all non-empty subsets of $[0,n]$. 
 To get $u$-equations, we should solve $S_J$ by $F_J$ from eq.\eqref{GPfacet}, the 

### 2020-03-09 draft_ABP.tex
Updates from Overleaf

@@
 This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
+
+Based on the above conjecture,  there is a statement for the binary geometries corresponding to the facet $u_{I}\to 0$, 
+that is the $u$-system for the facet $u_{I}\to 0$ is corresponding to the generlaized permutohedra $\mathcal{P}_{I}\otimes \mathcal{P}_{\bar{I}}$ with building sets  
+\[
+\mathcal{B}_{I} = \{J\vert J\subset I, J\in \mathcal{B}\}
+\]
+and 
+\[
+\mathcal{B}_{\bar{I}} = \{J-I\vert  J\in \mathcal{B}-\mathcal{B}_{I} \}
+\]
+where $J-I$ means the complement of $J$ with respect to $I$. This statement directly follow from the fact that $u_{I}\to 0$ is equivalent to take $x_{i}\to t x_{i} $ for $i\in I$ then take $t \to 0$
 )
@@
    &1-u_{1}=u_{2}u_{3}u_{23}^{2}u_{34}u_{234}^{2} \:, \\
-   &1-u_{2}=u_{1}u_{3}u_{13}^{2}u_{34}u_{123}^{2} \:, \\
+   &1-u_{2}=u_{1}u_{3}u_{13}^{2}u_{34}u_{134}^{2} \:, \\
    &1-u_{3}= u_{1}u_{2}u_{4}u_{12}^{2}(1+u_{3}u_{13}u_{23}u_{34}u_{123}u_{134}u_{234}) \:, \\
@@
 From above it is evident that $u^{'}_{I} = u_{\bar{I}} $ where $\bar{I}=[0,n]-I$ for all subsets $I$ that do not contain $0$. 
+({\bf Zhenjie: so why do we need $u'_J$?})
 And the $2^{n+1}-2$ facets corresponding to proper subsets of $[0,n]$ correspond to the two copies of the $2^{n}-1$ non-empty subsets of $[1,n]$.
@@
 
-The other $u$-equations are not two or three term equations and seem to be polynomials of order $|I|=n-2$ in the corresponding $u$'s.Thus, the most general $u$-equations can be conjectured to be:
+The other $u$-equations are not two or three term equations and seem to be polynomials of order $|I|=n-2$ in the corresponding $u$'s. Thus, the most general $u$-equations can be conjectured to be:
 \bea
@@
 {\bf linear factors, (standard) string integrals, ABHY and $u$ variables, talk about hyperplane arrangement}
+
+Let's define $[i,j]=\{i,i+1,\dots,j\}$ for $i,j\in \mathbb Z/(n+1)\mathbb Z$.
+
+The building set of $A_n$ is
+\[\left\{
+\begin{aligned}
+	&[0,n],\\
+	&[0,n-1],[1,n],\\
+	&[0,n-2],[1,n-1],[2,n],\\
+	&\hspace{3ex}\vdots\\
+	&[0,1],[1,2],\dots,[n-1,n],\\
+	&\{0\},\{1\},\dots,\{n\}
+\end{aligned}\right.
+\]
+
+The
+
+The building set of $B_n$ is
+\[\left\{
+\begin{aligned}
+	&[0,n],\\
+	&[0,n-1],[1,n],[2,0]\dots,[n,n-2]\\
+	&[0,n-2],[1,n-1],[2,n],\dots,[n,n-3]\\
+	&\hspace{3ex}\vdots\\
+	&[0,1],[1,2],\dots,[n-1,n],[n,0],\\
+	&\{0\},\{1\},\dots,\{n\}
+\end{aligned}\right.
+\]
 

### 2020-03-16 draft_ABP.tex
Updates from Overleaf

@@
 \[
-	u_{1}  = \frac{x_1 x_{123}}{x_{12}x_{13}},\quad 
-	u_{2}  = \frac{x_2 x_{123}}{x_{12}x_{23}},\quad
-	u_{3}  = \frac{x_3 x_{123}}{x_{13}x_{23}},\quad
-	u_{12} = \frac{x_{12}}{x_{123}},\quad 
-	u_{13} = \frac{x_{13}}{x_{123}},\quad
-	u_{23} = \frac{x_{23}}{x_{123}}.
+	u_{0}  = \frac{x_0 x_{012}}{x_{01}x_{02}},\quad 
+	u_{1}  = \frac{x_1 x_{012}}{x_{01}x_{12}},\quad
+	u_{2}  = \frac{x_2 x_{012}}{x_{02}x_{12}},\quad
+	u_{01} = \frac{x_{01}}{x_{012}},\quad 
+	u_{02} = \frac{x_{02}}{x_{012}},\quad
+	u_{12} = \frac{x_{12}}{x_{012}}.
 \]
@@
 \begin{align*}
-	&1-u_{1}=u_{2} u_{3} u_{23}^2,
-	1-u_{2}=u_{1} u_{3} u_{13}^2,
-	1-u_{3}=u_{1} u_{2} u_{12}^2,\\
-	&1-u_{12}=u_{3} u_{13} u_{23},
-	1-u_{13}=u_{2} u_{12} u_{23},
-	1-u_{23}=u_{1} u_{12} u_{13}.
+	&1-u_{0}=u_{1} u_{2} u_{12}^2,
+	1-u_{1}=u_{0} u_{2} u_{02}^2,
+	1-u_{2}=u_{0} u_{1} u_{01}^2,\\
+	&1-u_{01}=u_{2} u_{02} u_{12},
+	1-u_{02}=u_{1} u_{01} u_{12},
+	1-u_{12}=u_{0} u_{01} u_{02}.
 \end{align*}
@@
 From above it is evident that $u^{'}_{I} = u_{\bar{I}} $ where $\bar{I}=[0,n]-I$ for all subsets $I$ that do not contain $0$. 
-({\bf Zhenjie: so why do we need $u'_J$?})
 And the $2^{n+1}-2$ facets corresponding to proper subsets of $[0,n]$ correspond to the two copies of the $2^{n}-1$ non-empty subsets of $[1,n]$.
@@
 
-{\bf compatible if} $I\cap J = \emptyset$ or $I\cap J \neq \emptyset$ and either $I \subset J$ or $J \subset I$
-
-{\bf incompatible if}   $I\cap J \neq \emptyset$ or $I\cap J = \emptyset$ and neither $I \not\subset J$ or $J \not\subset I$
+% {\bf compatible if} $I\cap J = \emptyset$ or $I\cap J \neq \emptyset$ and either $I \subset J$ or $J \subset I$
+
+% {\bf incompatible if}   $I\cap J \neq \emptyset$ or $I\cap J = \emptyset$ and neither $I \not\subset J$ or $J \not\subset I$
+
+{\bf compatible if and only if} $\{[0,n],I,J\}$ is a nested set, i.e.
+\[
+I\subset J\quad \text{or}\quad J\subset I\quad \text{or}\quad (J\cap I=\varnothing \quad \text{and}\quad J\cup I\not\in \mathscr P_n).
+\]
+For permutohedron, $J\cup I$ is always contained in $\mathscr P_n$ for any $I$ and $J$, so it's compatible if and only if $J\subset I$ or $I\subset J$.
 
@@
 Let's define $[i,j]=\{i,i+1,\dots,j\}$ for $i,j\in \mathbb Z/(n+1)\mathbb Z$.
+%For the symbol $X=x,u,S,F$, we also use the notation $X_{ij}:=X_{[i,j-1]}$.
 
@@
 \]
-
-The
+The facets are given by eq.\eqref{GPfacet}
+\[
+F^A_{[i,j]}=\sum_{i\leq k\leq l\leq j}S_{[k,l]},
+\]
+and their solution is 
+\[
+S_{[i,j]}=F^A_{[i,j]}+F^A_{[i+1,j-1]}-F^A_{[i,j-1]}-F^A_{[i+1,j]},
+\]
+where $F^A_{[k,l]}:=0$ when $k>l$ or $[k,l]=[0,n]$. Using this solution to rewrite the integrand
+\[
+\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{S_{[i,j]}}
+=\prod_{0\leq i\leq j\leq n}\frac{x_{[i,j]}^{F^A_{[i,j]}}x_{[i,j]}^{F^A_{[i+1,j-1]}}}{x_{[i,j]}^{F^A_{[i,j-1]}}x_{[i,j]}^{F^A_{[i+1,j]}}}
+=
+\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F^A_{[i,j]}}
+\prod_{1\leq i\leq j\leq n-1}x_{[i-1,j+1]}^{F^A_{[i,j]}}
+\prod_{0\leq i\leq j\leq n-1}x_{[i,j+1]}^{-F^A_{[i,j]}}
+\prod_{1\leq i\leq j\leq n}x_{[i-1,j]}^{-F^A_{[i,j]}},
+\]
+and we get that
+\[
+u_{i,j+2}:=u_{[i,j]}=\frac{x_{[i,j]}x_{[i-1,j+1]}}{x_{[i,j+1]}x_{[i-1,j]}} \quad \text{for $0\leq i\leq j\leq n$,}
+\]
+where $x_{[i,n+1]}:=1$ and  $x_{[-1,j]}:=1$. $u$-equations are
+\[
+1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl}.
+\]
 
@@
 \end{aligned}\right.
+\]
+The facets are given by eq.\eqref{GPfacet}
+\[
+F^B_{[i,j]}=\sum_{[k,l]\subset [i,j]}S_{[k,l]},
+\]
+and their solution is 
+\[
+S_{[i,i]}=F^B_{[i,i]},\quad S_{[i,j]}=F^B_{[i,j]}+F^B_{[i+1,j-1]}-F^B_{[i,j-1]}-F^B_{[i+1,j]}\quad \text{for $i\neq j$},
+\]
+where $F^B_{[i+1,i]}:=0$. Therefore, the $u$-variables are
+\[
+u_i:=u_{[i,i-2]}=\frac{x_{[i,i-2]}}{x_{[0,n]}},\quad 
+u_{i,j+2}:=u_{[i,j]}=\frac{x_{[i,j]}x_{[i-1,j+1]}}{x_{[i,j+1]}x_{[i-1,j]}}
+\quad \text{for $i-j\neq 2$}.
+\]
+$u$-equations are
+\[
+1-u_i=U_{[i+1,i-1]},\quad 
+1-u_{ij}=U_{[i+1,j],[j+1,i-1]}U_{[j+1,i-1],[i,j-1]}U^2_{[j+1,i-1]},
+\]
+where 
+\[
+U_{A,B}=\prod_{a\in A,b\in B}u_{ab},\quad 
+U_A=\prod_{a\in A}u_a\prod_{a<b\in A}u_{ab}.
 \]

### 2020-03-31 draft_ABP.tex
Updates from Overleaf

@@
 \usepackage{comment}
+
+\usepackage{enumitem}
 
@@
 ******************************************************************************************
-\section*{Permutahedron}
+\subsubsection*{Permutahedron}
  For $x_1,x_2, \cdots, x_{n+1} \in \mathbb{R} $ , the permutahedron ${\mathscr P_n}(x_1,\cdots,x_{n+1})$ is a convex polytope in $\mathbb{R}^{n+1}$ defined as the convex hull of all vectors obtained from $(x_1,x_2, \cdots, x_{n+1})$ by permutations of the coordinates:
@@
  \bea
- H_c= \{(t_1,t_2, \cdots, t_{n+1}) | t_1 + t_2 + \cdots + t_{n+1}= c \} \subset \mathbb{R}^{n+1}, \nonumber
+ H_c= \{(t_1,t_2, \cdots, t_{n+1}) ~|~ t_1 + t_2 + \cdots + t_{n+1}= c \} \subset \mathbb{R}^{n+1}, \nonumber
  \eea
@@
 
-\subsection*{Generalized permutahedra}
+\subsubsection*{Generalized permutahedra}
 
@@
 To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
-\subsection*{Nested Complex}
+
+\subsubsection*{Nested Complex}
 A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
@@
 \begin{equation}
-   u_{I} = \prod_{ I \subset J \subset I_{\text{max}}}x_J^{(-1)^{|I|-|J|}}.
+   u_{I} = \prod_{ I \subset J \subset I_{\text{max}}}x_J^{(-1)^{|I|-|J|}}. \label{uvarforgraph}
 \end{equation}
-This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
-
-Based on the above conjecture,  there is a statement for the binary geometries corresponding to the facet $u_{I}\to 0$, 
-that is the $u$-system for the facet $u_{I}\to 0$ is corresponding to the generlaized permutohedra $\mathcal{P}_{I}\otimes \mathcal{P}_{\bar{I}}$ with building sets  
-\[
-\mathcal{B}_{I} = \{J\vert J\subset I, J\in \mathcal{B}\}
-\]
-and 
-\[
-\mathcal{B}_{\bar{I}} = \{J-I\vert  J\in \mathcal{B}-\mathcal{B}_{I} \}
-\]
-where $J-I$ means the complement of $J$ with respect to $I$. This statement directly follow from the fact that $u_{I}\to 0$ is equivalent to take $x_{i}\to t x_{i} $ for $i\in I$ then take $t \to 0$
-)
+
+\subsubsection{The binary aspects of $u$-variables for graph associahedra}
+
+Here we want to show that the $u_{I}$'s defined in \eqref{uvarforgraph} have the desired binary property, that is, $u_{I}$ and $u_{J}$ are compatible if and only if $I$ and $J$ are one of the following three cases:
+\begin{enumerate}
+   \item $I\subset J$\:,
+   \item $J\subset I$ \:,
+   \item $I\cap J=\emptyset$ and $I\cup J \notin \mathcal{B}$ \:.
+\end{enumerate}
+In other words, this means that $u_{I}$ and $u_{J}$ are incompatible if $I$ and $J$ are one of the following two cases:
+\begin{enumerate}[resume]
+   \item $I\cap J=\emptyset$ and $I\cup J \in \mathcal{B}$ \:, 
+   \item $I\cap J \neq \emptyset,I, J $ \:.
+\end{enumerate}
+
+A crucial observation here is that $u_{J}\to 0$ is equivalent to $x_{J}\to 0 $ according to \eqref{uvarforgraph} since all $x_{i}$ are non-negative.
+We can approach this limit by replacing $x_{j}$ with $ \epsilon x_{j}$ for all $j\in J$ then taking $\epsilon \to 0$.
+Then the remaining task is just to consider the behaviour of the other $u_{I}$'s under this limit.
+In the following arrangement, it is convenient to introduce
+\begin{equation}
+  p(J_{1},J_{2},\cdots,J_{n}):= \sum_{j\in J } x_{j} \:.
+\end{equation}
+where $J= \bigcup_{a=1}^{n} J_{a}$
+
+For case (1). First note that if $j\in J$ is not attached to $I$, then $x_{j}$ is independent of $u_{I}$ according to \eqref{uvarforgraph}. Thus, we can decompose $J$ into three parts, 
+\begin{equation}
+   J= I\cup J_{c}\cup \bar{J}_{c}
+\end{equation}
+where $J_{c}$ is the set of all singletons in $J$ connected with $I$, $\bar{J}_{c}$ is the set of remaining singletons.
+Furthermore, We denote $K=I_{\text{max}}-I-J_{c} $ as the set of all singletons which don't belong to $J$ but is connected with $I$.
+Then we have
+\begin{align}
+   \lim_{\epsilon \to 0}\log u_{I}&=\lim_{\epsilon \to 0}\sum_{\psi\subset J_{c},\kappa\subset K} (-1)^{\lvert \psi\rvert  +\lvert\kappa\rvert} \log p(I_{\epsilon},\psi_{\epsilon},\kappa) \nonumber \\
+   &= (-1)^{\lvert \psi\rvert }\sum_{\psi\subset J_{c}}\log p(I,\psi) + \biggl(\log\epsilon +\sum_{\kappa\neq \emptyset}(-1)^{\lvert\kappa\rvert}\log p(\kappa)\biggr)\sum_{\psi\subset J_{c}}(-1)^{\lvert \psi\rvert } \binom{\lvert\psi\rvert }{\lvert J_{c}\rvert } \nonumber \\
+   &=  (-1)^{\lvert \psi\rvert }\sum_{\psi\subset J_{c}}\log p(I,\psi) 
+     \:,
+\end{align}
+where $I_{\epsilon}$ and $\psi_{\epsilon}$ indicate that their elements are multiplied with $\epsilon$.
+
+Case (2) and (3) are trivial, we leave them to the reader.
+
+Now let us consider case (4). For this case, we can decompose J into two parts,
+\begin{equation}
+   J=J_{c}\cup \bar{J}_{c}
+\end{equation}
+where again $J_{c}$ is the set of all singletons in $J$ connected with $I$, $\bar{J}_{c}$ is the set of remaining singletons.
+As the above, we denote $K=I_{\text{max}}-I-J_{c} $ as the set of all singletons which don't belong to $J$ but is connected with $I$.
+Then
+\begin{align}
+   \lim_{\epsilon \to 0}\log u_{I}&=\lim_{\epsilon \to 0}\sum_{\psi\subset J_{c},\kappa\subset K} (-1)^{\lvert \psi\rvert  +\lvert\kappa\rvert} \log p(I,\psi_{\epsilon},\kappa) \nonumber \\ 
+   &= \sum_{\kappa\subset K}(-1)^{\lvert\kappa\rvert}\log p(I,\kappa)\Biggl(\sum_{\psi\subset J_{c}}(-1)^{\lvert \psi\rvert } \binom{\lvert\psi\rvert }{\lvert J_{c}\rvert } \Biggr)\nonumber \\
+   &=  0
+     \:.
+\end{align}
+The argument for case (5) is similar with case (4), we omit here.
+
+\paragraph{Quickly review of the facet structure of graph associahedra} Given a graph $\Gamma$ and its subgraph $\Gamma_{J}$, construct a new graph $\Gamma_{J}^{\ast}$ called the reconnected complement: If $V$ and $J$ are the sets of nodes of $\Gamma$ and $\Gamma_{J}$ respectively, then $V-J$ is the set of nodes of $\Gamma_{J}^{\ast}$.
+There is an edge between nodes $a$ and $b$ in $\Gamma_{J}^{\ast}$ if either $\{a, b\}$ or $\{a, b\}\cup J$ is connected in $\Gamma$.
+If we denote the corresponding graph associahedron for $\Gamma$ by $\mathcal{P}\Gamma$, then each subgraph $\Gamma_{J}$ corresponds a facet of $\mathcal{P}\Gamma$.
+In particular, this facet is combinatorially equivalent to $\mathcal{P}\Gamma_{J}\times \mathcal{P}\Gamma_{J}^{\ast}$\cite{}.
+
+It can easily check that, under the limit of $u_{J}\to 0$, $u_{I}$ in case (1) give the $u$-variables for $\mathcal{P}\Gamma_{J}$, while  $u_{I}$ in case (2) and (3) give the $u$-variables for $\mathcal{P}\Gamma_{J}^{\ast}$
+
+{\bf A conjecture for $u$-variables of generalized permutahdera (nextohedra)}
+
+For each element $ I\in \mathcal B$, we define $I^{(0)}=\{I\}$ and  $I^{(1)}$ as the set of all $J\supsetneq I $ such that  $I$ is the ``maximal subset'' of $J$ in $\mathcal{B}$ (that is, there is no $K\in \mathcal{B}$ such that $I\subsetneq K\subsetneq J $).
+Then, we recursively define
+\begin{equation}
+   I^{(i+1)} = \{I^{(i)}_{a}\cup I^{(i)}_{b}\vert I_{a,b}^{(i)}\in I^{(i)},\text{$I_{a}^{(i)}$ and $I_{b}^{(i)}$ are ``maximal subsets'' of $I^{(i)}_{a}\cup I^{(i)}_{b}$ }\}
+\end{equation} 
+and stop when $\lvert I^{(s)}\rvert =1$. With the defination of $I^{(i)}$, the coresponding $u$-variable is
+\begin{equation}
+   u_{I} =\prod_{i}(-1)^{i} \prod_{I_{a}^{(i)}\in I^{(i)}} p(I_{a}^{(i)})
+\end{equation}
+
+% This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
+
+% Based on the above conjecture,  there is a statement for the binary geometries corresponding to the facet $u_{I}\to 0$, 
+% that is the $u$-system for the facet $u_{I}\to 0$ is corresponding to the generlaized permutohedra $\mathcal{P}_{I}\otimes \mathcal{P}_{\bar{I}}$ with building sets  
+% \[
+% \mathcal{B}_{I} = \{J\vert J\subset I, J\in \mathcal{B}\}
+% \]
+% and 
+% \[
+% \mathcal{B}_{\bar{I}} = \{J-I\vert  J\in \mathcal{B}-\mathcal{B}_{I} \}
+% \]
+% where $J-I$ means the complement of $J$ with respect to $I$. This statement directly follow from the fact that $u_{I}\to 0$ is equivalent to take $x_{i}\to t x_{i} $ for $i\in I$ then take $t \to 0$
+% )
 
@@
 
-Thus, each $u_I$ is compatible with itself and incompatible with $u^{'}_I$.
+% Thus, each $u_I$ is compatible with itself and incompatible with $u^{'}_I$.
 

### 2020-04-01 draft_ABP.tex
Updates from Overleaf

@@
 \end{equation}
+
+**************
+
+(Zhenjie: A possible way to find some $u$-equations of generalized permutohedra:)
+
+For a generic generalized permutohedra $\mathscr P$, it's usually difficult to solve $S_I$ by $\{F_I\}$  from eq.\eqref{GPfacet} and then get $u$-variables, but we can directly use eq.\eqref{GPfacet} to express $x_I$ by $\{u_I\}$ which give us many algebraic equations of $u$-variables.
+In fact,
+\[
+\prod_{I\in \mathscr P}x_I^{S_I}=\prod_{J\in \mathscr P}u_J^{F_J}=\prod_{J\in\mathscr P}\prod_{I\subset J,I\in \mathscr P}u_J^{S_I}=\prod_{I\in\mathscr P}\biggl(\prod_{J\supset I,J\in\mathscr P}u_J\bigg)^{S_I},
+\]
+so
+\[
+x_I=\prod_{J\supset I,J\in\mathscr P}u_J
+\]
+for any $I\in \mathscr P$, where we introduce a fake $u$-variable $u_{[0,n]}:=x_{[0,n]}$.
+We know some algebraic equations of $\{x_I\}$, for example, $x_I+x_J=x_{[0,n]}$ for $I\cap J=\varnothing$ and $I\cup J=[0,n]$, so (I will omit all $\text{sth}\in \mathscr P$ for short.)
+\[
+\prod_{K\supset I}u_K+\prod_{K\supset J}u_K=u_{[0,n]},
+\]
+or (since we always assume that $u_{[0,n]}=x_{[0,n]}\neq 0$)
+\[
+\prod_{I\subset K\neq [0,n]}u_K +
+\prod_{J\subset K\neq [0,n]}u_K = 1.
+\]
+(Zhenjie: I guess all possible $u$-equations are consequences of some algebraic equations of $x_I$ which is in fact we have seen in the calculation of $1-u_I$.)
 

### 2020-04-02 draft_ABP.tex
Update draft_ABP.tex

@@
 Therefore, for a generalized permutahedron $\mathscr P$, we can write down the matrix 
-$W^J_A$ of facets and then get the ABHY conditions $S_J=F_A(W^{-1})^A_J\geq 0$ and 
+$W^J_A$ of facets and then get $S_J=F_A(W^{-1})^A_J\geq 0$ and 
 its $u$-variables $u_A=\prod_J p_J^{(W^{-1})^A_J}$.
@@
 Let's first write down equations of facets of a generalised permutahedron
-with the building set $\mathscr P$. The ABHY polytope of 
+with the building set $\mathscr P$. The polytope of 
 eq.\eqref{stringyintforgenpermutohedron} is given by the Minkowski sum
@@
 
+For permutahedra, we can give a ABHY construction from eq.\eqref{SinF} by setting 
+$S_I=-c_I$ for any non-singleton $I\in \mathscr P_n$, where $c_I$ are positive 
+constants, and a ABHY polytope is given by 
+\begin{equation}\label{ABHY}
+	F_I\geq 0,\quad -c_I=\sum_{J\neq \varnothing,J\subset I}(-1)^{|J|-|I|}F_J
+\end{equation}
+in $\{S_i=F_i\,:\,1\leq i\leq n\}$-space, where the last equation is a gauge fixing. 
+According to eq.\eqref{genperm_defi}, this polytope is a $n$-dimensional 
+permutahedron $\mathscr P_n$. {\bf (???)}
+The ABHY construction of any generalized permutohedra can be obtained by 
+setting $c_I=0$ for all $I$ not in the building set.
+
+For example, the building set of $\mathscr A_2$ is $\mathscr P_2-\{\{0,2\}\}$,
+its ABHY construction can be obtained from $\mathscr P_2$ by setting $c_{02}=0$, 
+\[
+	0=-c_{02}=F_{02}-F_2,
+\]
+therefore the whole ABHY conditions for $\mathscr A_2$ is 
+\[
+	-c_{01}=F_{01}-F_0-F_1,\quad -c_{12}=F_{12}-F_1-F_2,\quad 
+	-c_{012}=-F_{01}-F_{12}+F_1,\quad F_I\geq 0,
+\]
+and its solution in $(F_1,F_2)$ space is 
+\[
+	\left\{\begin{aligned}
+		F_1&\geq 0,F_2\geq 0\\
+		F_0&=c_{01}+c_{12}+c_{012}-F_1-F_2\geq 0,\\
+		F_{12}&=F_1+F_2-c_{12}\geq 0,\\
+		F_{01}&=c_{012}+c_{12}-F_2\geq 0.
+	\end{aligned}\right.
+\]
+
 \subsection{Binary geometries and $u$ equations}
@@
 
-(Zhenjie: A possible way to find some $u$-equations of generalized permutohedra:)
+({\bf Zhenjie}: A possible way to find some $u$-equations of generalized permutohedra)
 
@@
 \]
-for any $I\in \mathscr P$, where we introduce a fake $u$-variable $u_{[0,n]}:=x_{[0,n]}$.
-We know some algebraic equations of $\{x_I\}$, for example, $x_I+x_J=x_{[0,n]}$ for $I\cap J=\varnothing$ and $I\cup J=[0,n]$, so (I will omit all $\text{sth}\in \mathscr P$ for short.)
-\[
-\prod_{K\supset I}u_K+\prod_{K\supset J}u_K=u_{[0,n]},
-\]
-or (since we always assume that $u_{[0,n]}=x_{[0,n]}\neq 0$)
-\[
-\prod_{I\subset K\neq [0,n]}u_K +
-\prod_{J\subset K\neq [0,n]}u_K = 1.
-\]
-(Zhenjie: I guess all possible $u$-equations are consequences of some algebraic equations of $x_I$ which is in fact we have seen in the calculation of $1-u_I$.)
-
+for any $I\in \mathscr P$, where we introduce a fake $u$-variable 
+$u_{[0,n]}:=x_{[0,n]}$. We know some algebraic equations of $\{x_I\}$, 
+for example, linear equations $x_I+x_J=x_{I\cup J}$ for $I\cap J=\varnothing$, 
+so (I will omit all $\text{sth}\in \mathscr P$ for short.)
+\begin{equation*}
+	\prod_{K\supset I}u_K+\prod_{K\supset J}u_K=\prod_{K\supset I\cup J}u_K
+\end{equation*}
+or equivalently
+\begin{equation}
+\prod_{I\subset K,K\not\supset I\cup J}u_K +
+\prod_{J\subset K,K\not\supset I\cup J}u_K = 1.
+\end{equation}
+({\bf Zhenjie}: I conjecture that all possible $u$-equations are consequences of 
+some algebraic equations of $x_I$ which is in fact we have seen in 
+the calculation of $1-u_I$. For example, the nonlinear equation (although it's
+the consequence of linear equations)
+\[
+	x_0x_{012}+x_1x_2=x_{01}x_{02}
+\]
+tell us the $u$-equation of $u_0$ of 2d permutohedron $\mathscr P_2$. Therefore,
+another related conjecture is that the variety generated by $u$-equations 
+is the one generated by eq.(\theequation) for all disjoint $I$, $J\in \mathscr P$ 
+in $u$-space. Can we prove that generalized permutohedra are binary geometries in
+this way?
+)
 % This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.

### 2020-04-03 draft_ABP.tex
Updates from Overleaf

@@
 
-**************
+\subsection{u eqs}
 
@@
 
-For a generic generalized permutohedra $\mathscr P$, it's usually difficult to solve $S_I$ by $\{F_I\}$  from eq.\eqref{GPfacet} and then get $u$-variables, but we can directly use eq.\eqref{GPfacet} to express $x_I$ by $\{u_I\}$ which give us many algebraic equations of $u$-variables.
+For a generic generalized permutohedra $\mathscr P$, it's usually difficult to solve $S_I$ by $\{F_I\}$  from eq.\eqref{GPfacet} and then get $u$-variables in terms of $\{x_I\}$, but we can directly use eq.\eqref{GPfacet} to express $x_I$ by $\{u_I\}$ which gives us many algebraic equations of $u$-variables.
 In fact,
@@
 for example, linear equations $x_I+x_J=x_{I\cup J}$ for $I\cap J=\varnothing$, 
-so (I will omit all $\text{sth}\in \mathscr P$ for short.)
+so (I will omit all $\text{sth}\in \mathscr P$ for convenience.)
 \begin{equation*}
@@
 \]
-tell us the $u$-equation of $u_0$ of 2d permutohedron $\mathscr P_2$. Therefore,
+tells us the $u$-equation of $u_0$ of 2d permutohedron $\mathscr P_2$. Therefore,
 another related conjecture is that the variety generated by $u$-equations 
@@
 )
+
+For permutohedron $\mathscr P_n$, I conjecture that
+\[
+1-u_I=1-\prod_{J\supset I}x_J^{(-1)^{|J|-|I|}}=\frac{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J-\prod_{|J|-|I| \text{ even}; J\supset I}x_J}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J}
+=\frac{f_{I,n}\prod_{i\not\in I}x_i}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J},
+\]
+where $f_{I,n}$ is an irreducible polynomial with positive coefficients.
+It's easy to see $x_i$ for $i\not\in I$ is a factor of numerator by setting $x_i=0$, but it's not obvious whether $f_{I,n}$ is irreducible.
+I've checked many examples, and corresponding polynomials $f_{I,n}$ are always irreducible.
+
+From
+\[
+\prod_{i\not\in I}x_i=\prod_J u_J^{|J|-|I\cap J|}
+\quad\text{and}\quad
+\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
+=
+\prod_{J\supset I}u_J^{2^{|J|-|I|-1}},
+\]
+then
+\[
+\prod_{i\not\in I}x_i\bigg/\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
+=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supset I} u_J^{|J|-|I|-2^{|J|-|I|-1}}.
+\]
+Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's naturally to conjecture that
+\[
+1-u_I=g(u)\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
+\]
+where $g$ is a polynomial.
+The product $\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}$ has appeared in all known examples with right powers.
+It's clear that any compatible $u_J$ for $J\subset I$ doesn't appear in the product because $I\cap J=J$.
+Thus, the final conjecture is about the compatibility degree:
+\[
+(I||J)=|J|-|I\cap J|\text{ for $I\not\subset J$},\quad  (I||J)=0 \text{ for $I\subset J$}.
+\]
+It's not symmetric when $|I|\neq |J|$.
+
 % This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.

### 2020-04-06 draft_ABP.tex
Updates from Overleaf

@@
 \begin{equation}
-   u_{I} =\prod_{i}(-1)^{i} \prod_{I_{a}^{(i)}\in I^{(i)}} p(I_{a}^{(i)})
+   u_{I} =\prod_{i}\prod_{I_{a}^{(i)}\in I^{(i)}} p(I_{a}^{(i)})^{(-1)^{i} }
 \end{equation}
@@
 so
-\[
+\begin{equation}
 x_I=\prod_{J\supset I,J\in\mathscr P}u_J
-\]
+\end{equation}
 for any $I\in \mathscr P$, where we introduce a fake $u$-variable 
@@
 where $f_{I,n}$ is an irreducible polynomial with positive coefficients.
-It's easy to see $x_i$ for $i\not\in I$ is a factor of numerator by setting $x_i=0$, but it's not obvious whether $f_{I,n}$ is irreducible.
+It's easy to see $x_i$ for $i\not\in I$ is a factor of the numerator by setting $x_i=0$, but it's not obvious whether $f_{I,n}$ is irreducible.
 I've checked many examples, and corresponding polynomials $f_{I,n}$ are always irreducible.
@@
 \]
-Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's naturally to conjecture that
-\[
+Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's natural to conjecture that
+\begin{equation}
 1-u_I=g(u)\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
-\]
+\end{equation}
 where $g$ is a polynomial.

### 2020-04-12 draft_ABP.tex
Updates from Overleaf

@@
 
-{\Large \bf  Binary geometries: Associahedra, Cyclohedra and Generalized Permutahedra}
+{\Large \bf  Binary geometries: Associahedra, Cyclohedra and (Generalized) Permutahedra}
 
@@
 
+% This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
+
+% Based on the above conjecture,  there is a statement for the binary geometries corresponding to the facet $u_{I}\to 0$, 
+% that is the $u$-system for the facet $u_{I}\to 0$ is corresponding to the generlaized permutohedra $\mathcal{P}_{I}\otimes \mathcal{P}_{\bar{I}}$ with building sets  
+% \[
+% \mathcal{B}_{I} = \{J\vert J\subset I, J\in \mathcal{B}\}
+% \]
+% and 
+% \[
+% \mathcal{B}_{\bar{I}} = \{J-I\vert  J\in \mathcal{B}-\mathcal{B}_{I} \}
+% \]
+% where $J-I$ means the complement of $J$ with respect to $I$. This statement directly follow from the fact that $u_{I}\to 0$ is equivalent to take $x_{i}\to t x_{i} $ for $i\in I$ then take $t \to 0$
+% )
+
 \subsection{u eqs}
@@
 =
-\prod_{J\supset I}u_J^{2^{|J|-|I|-1}},
+\prod_{J\supsetneq I}u_J^{2^{|J|-|I|-1}},
 \]
@@
 \prod_{i\not\in I}x_i\bigg/\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
-=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supset I} u_J^{|J|-|I|-2^{|J|-|I|-1}}.
+=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supsetneq I} u_J^{|J|-|I|-2^{|J|-|I|-1}}.
 \]
@@
 It's not symmetric when $|I|\neq |J|$.
-
-% This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
-
-% Based on the above conjecture,  there is a statement for the binary geometries corresponding to the facet $u_{I}\to 0$, 
-% that is the $u$-system for the facet $u_{I}\to 0$ is corresponding to the generlaized permutohedra $\mathcal{P}_{I}\otimes \mathcal{P}_{\bar{I}}$ with building sets  
-% \[
-% \mathcal{B}_{I} = \{J\vert J\subset I, J\in \mathcal{B}\}
-% \]
-% and 
-% \[
-% \mathcal{B}_{\bar{I}} = \{J-I\vert  J\in \mathcal{B}-\mathcal{B}_{I} \}
-% \]
-% where $J-I$ means the complement of $J$ with respect to $I$. This statement directly follow from the fact that $u_{I}\to 0$ is equivalent to take $x_{i}\to t x_{i} $ for $i\in I$ then take $t \to 0$
-% )
 
@@
 \subsection{Permutahedron as a binary geometry}
-In this section we shall try to argue that the permutahedron is a binary geometry. We shall first summarise the following facts about the permutahedron from our discussion in the earlier sections:
+
+\textcolor{red}{(Prashanth: An attempt to prove $P_n$ is binary using Chi's method.)}
+
+In this section we shall try to argue that the permutahedron is a binary geometry. We shall first summarise the following facts about the permutahedron:
 \begin{enumerate}
@@
 \bea
-u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber \\
-u^{'}_J &=& \prod_{{0 \in I}\atop{ \{0,\cdots,n\} - I \subset J}} x_I^{(-1)^{|I|-|J|+mod(n, 2)}} \nonumber
-\eea
-From above it is evident that $u^{'}_{I} = u_{\bar{I}} $ where $\bar{I}=[0,n]-I$ for all subsets $I$ that do not contain $0$. 
-And the $2^{n+1}-2$ facets corresponding to proper subsets of $[0,n]$ correspond to the two copies of the $2^{n}-1$ non-empty subsets of $[1,n]$.
-
+u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber 
+\eea
+The above relations can also be inverted to obtain $x_I$ as follows:
+
+For $0 \notin I $
+\bea
+x_I &=& \frac{\prod_{I \subset J} u_{J}}{1-\prod_{I \subset J} u_{J}} \\
+\frac{1}{1+ x_I} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}}
+\eea
+From the above relations it is clear that taking $u_I \rightarrow 0$ for $0 \notin I$ implies $x_J \rightarrow 0$ for all $J \subset I$ and taking $u_\bar{I} \rightarrow 0$ for $0 \in I$ implies $x_J \rightarrow \infty $ for all $I \subset J$.
+In fact we shall argue that there is unique choice of $x_I$'s which we can take to $0$ or $\infty$ which corresponds to setting a particular $u_I \rightarrow 0$ or $u_\bar{I} \rightarrow 0$ respectively.
 \item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :
@@
 
+The above  follows directly from the following relations amongst $u$ for each $I$ such that $0\notin I$ :
+\bea
+1-\prod_{I \subset J} u_{J} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}} \\
+1-\prod_{J \subset I} u_{\bar{J}} &=& \prod_{I \subset J} u_{J} \prod_{J \subset \bar{I} } u_{\bar{J}}
+\eea
+
 % Thus, each $u_I$ is compatible with itself and incompatible with $u^{'}_I$.
 
-\item  Since, the permutahedron is permutation invariant in all $x_i$'s this should be reflected at the level of $u$'s and all $u_I$ and $u^{'}_{J}$ with the same $|I|$ and $|J| =n-|I|$ should have similar $u$-equations.
-We see that this is indeed the case :
+\item  Since, the permutahedron is permutation invariant in all $x_i$'s this should be reflected at the level of $u$'s and this is indeed the case as $u_I$ with the same $|I|$ have similar $u$'s.
+i.e $u_J$ can be obtained from $u_I$ for $|J|=|I|$ by interchange of some of the $x_i$'s.
+
+We shall prove $\mathscr P_{n+1}$ is binary by showing that whenever we take some $u_I \rightarrow 0$ (by taking a unique set of $x_i \rightarrow 0, \infty$) then $u_J \rightarrow 1$ for $J$ incompatible with $I$ and the remaining $u$'s reduce to the $u$'s corresponding to $\matchscr P_k \times \mathscr P_{n-k}$.
+
+It is enough to consider $u_1, u_{12},\cdots,u_{12...n(n+1)} \rightarrow 0$ and  $u_0, u_{0(n+1)},u_{0,n(n+1)}\cdots,u_{02...n(n+1)} \rightarrow 0$.
+
+We have the following cases:
+\begin{enumerate}
+    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e $I = \{ \{1\},\{1,2\},\cdots,\{1,2,\cdots, \lfloor \frac{n+1}{2} \rfloor -1 \} \}$
+
+    In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots \lfloor \frac{n+1}{2} \rfloor$ and consider the limit $t \rightarrow 0$ to give:
+    \bea
+    u^{(n+1)}_{J \cup  I} &\rightarrow& u_{J}^{((n+1)-|I|)} ~\text{with}~ J\subseteq\bar{I}\\
+     u^{(n+1)}_{K} &\rightarrow& u_{K}^{(|I|-1)} ~\text{with}~ K\subsetneq I
+    \eea
+   which gives $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$
+
+    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{\{1,2,\cdots, \lfloor \frac{n+1}{2} \rfloor\},\cdots,\{1,2,\cdots, (n+1) \} \}$
+     In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots \lfloor \frac{n+1}{2} \rfloor-1$ and $x_{\lfloor \frac{n+1}{2} \rfloor} \rightarrow t$ and  consider the limit $t \rightarrow 0$ to give:
+    \bea
+    u^{(n+1)}_{J } &\rightarrow& u_{J}^{((n+1)-|I|)} ~\text{with}~ J\subseteq \{1,\cdots,|I|-1\}\\
+     u^{(n+1)}_{J \cup \{|I|\}} &\rightarrow& u_{K \cup\{0\}}^{((n+1)-|I|)} ~\text{with}~ J\subsetneq I\{1,\cdots,|I|-1\}
+    \eea
+     \bea
+    u^{(n+1)}_{K \cup I } &\rightarrow& u_{J}^{(|I|-1)} ~\text{with}~ K\subseteq \{|I|+1,\cdots,n+1\}\\
+     u^{(n+1)}_{K \cup \{0\}\cup I} &\rightarrow& u_{K \cup{0}}^{(|I|-1)} ~\text{with}~ K\subsetneq I\{|I|+1,\cdots,n+1\}
+    \eea
+   which gives $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$ 
+    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{\{0\},\{0,(n+1)\},\cdots,\{0,\lfloor \frac{n+1}{2} \rfloor+2,\cdots,(n+1)\}$
+    In this case we take $x_i \rightarrow \frac{ x_i}{t}$ for $i=1,\cdots \lfloor \frac{n+1}{2} \rfloor$ and $x_{\lfloor \frac{n+1}{2}+1 \rfloor} \rightarrow \frac{1}{t}$ and  consider the limit $t \rightarrow 0$ to give:
+    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{\{0,\lfloor \frac{n+1}{2} \rfloor+1,\cdots,(n+1)\},\cdots,\{0,2,\cdots,(n+1)\} \}$
+    In this case we take $x_i \rightarrow \frac{ x_i}{t}$ for $i=1,\cdots \lfloor \frac{n+1}{2} \rfloor$ and $x_{\lfloor \frac{n+1}{2}+1 \rfloor} \rightarrow \frac{1}{t}$ and  consider the limit $t \rightarrow 0$ to give:
+\end{enumerate}
 
@@
  $K$ are all sets compatible with $I$ excluding itself 
-
  $s_J$ are positive integers.
+
 \end{enumerate}

### 2020-04-12 draft_ABP.tex
Updates from Overleaf

@@
 \eea
-From the above relations it is clear that taking $u_I \rightarrow 0$ for $0 \notin I$ implies $x_J \rightarrow 0$ for all $J \subset I$ and taking $u_\bar{I} \rightarrow 0$ for $0 \in I$ implies $x_J \rightarrow \infty $ for all $I \subset J$.
-In fact we shall argue that there is unique choice of $x_I$'s which we can take to $0$ or $\infty$ which corresponds to setting a particular $u_I \rightarrow 0$ or $u_\bar{I} \rightarrow 0$ respectively.
+From the above relations it is clear that taking $u_I \rightarrow 0$ for $0 \notin I$ implies $x_J \rightarrow 0$ for all $J \subset I$ and taking $u_{\bar{I}} \rightarrow 0$ for $0 \in I$ implies $x_J \rightarrow \infty $ for all $I \subset J$.
+In fact we shall argue that there is unique choice of $x_I$'s which we can take to $0$ or $\infty$ which corresponds to setting a particular $u_I \rightarrow 0$ or $u_{\bar{I}} \rightarrow 0$ respectively.
 \item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :
@@
 
-We shall prove $\mathscr P_{n+1}$ is binary by showing that whenever we take some $u_I \rightarrow 0$ (by taking a unique set of $x_i \rightarrow 0, \infty$) then $u_J \rightarrow 1$ for $J$ incompatible with $I$ and the remaining $u$'s reduce to the $u$'s corresponding to $\matchscr P_k \times \mathscr P_{n-k}$.
+We shall prove $\mathscr P_{n+1}$ is binary by showing that whenever we take some $u_I \rightarrow 0$ (by taking a unique set of $x_i \rightarrow 0, \infty$) then $u_J \rightarrow 1$ for $J$ incompatible with $I$ and the remaining $u$'s reduce to the $u$'s corresponding to $\mathscr P_k \times \mathscr P_{n-k}$.
 

### 2020-04-13 draft_ABP.tex
Updates from Overleaf

--- 2020-04-12 draft_ABP.tex
@@
 \eea
-From the above relations it is clear that taking $u_I \rightarrow 0$ for $0 \notin I$ implies $x_J \rightarrow 0$ for all $J \subset I$ and taking $u_\bar{I} \rightarrow 0$ for $0 \in I$ implies $x_J \rightarrow \infty $ for all $I \subset J$.
-In fact we shall argue that there is unique choice of $x_I$'s which we can take to $0$ or $\infty$ which corresponds to setting a particular $u_I \rightarrow 0$ or $u_\bar{I} \rightarrow 0$ respectively.
+From the above relations it is clear that taking $u_I \rightarrow 0$ for $0 \notin I$ implies $x_J \rightarrow 0$ for all $J \subset I$ and taking $u_{\bar{I}} \rightarrow 0$ implies $x_J \rightarrow \infty $ for all $I \subset J$.
+In fact we shall argue that there is unique choice of $x_I$'s which we can take to $0$ or $\infty$ which corresponds to setting only a particular $u_I \rightarrow 0$ or $u_{\bar{I}} \rightarrow 0$ respectively.
 \item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :
@@
 
-We shall prove $\mathscr P_{n+1}$ is binary by showing that whenever we take some $u_I \rightarrow 0$ (by taking a unique set of $x_i \rightarrow 0, \infty$) then $u_J \rightarrow 1$ for $J$ incompatible with $I$ and the remaining $u$'s reduce to the $u$'s corresponding to $\matchscr P_k \times \mathscr P_{n-k}$.
-
-It is enough to consider $u_1, u_{12},\cdots,u_{12...n(n+1)} \rightarrow 0$ and  $u_0, u_{0(n+1)},u_{0,n(n+1)}\cdots,u_{02...n(n+1)} \rightarrow 0$.
+We shall prove $\mathscr P_{n+1}$ is binary by showing that whenever we take some $u_I \rightarrow 0$ (by taking a unique set of $x_i \rightarrow 0, \infty$) then $u_J \rightarrow 1$ for $J$ incompatible with $I$ and the remaining $u$'s reduce to the $u$'s corresponding to $\mathscr P_{k-1} \times \mathscr P_{(n+1)-k}$.
+
+By the argument given above it is sufficient to consider $u_1, u_{12},\cdots,u_{12...n(n+1)} \rightarrow 0$ and $u_0, u_{0(n+1)},u_{0,n(n+1)}\cdots,u_{02...n(n+1)} \rightarrow 0$.
 
@@
 \begin{enumerate}
-    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e $I = \{ \{1\},\{1,2\},\cdots,\{1,2,\cdots, \lfloor \frac{n+1}{2} \rfloor -1 \} \}$
-
-    In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots \lfloor \frac{n+1}{2} \rfloor$ and consider the limit $t \rightarrow 0$ to give:
-    \bea
-    u^{(n+1)}_{J \cup  I} &\rightarrow& u_{J}^{((n+1)-|I|)} ~\text{with}~ J\subseteq\bar{I}\\
-     u^{(n+1)}_{K} &\rightarrow& u_{K}^{(|I|-1)} ~\text{with}~ K\subsetneq I
-    \eea
-   which gives $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$
-
-    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{\{1,2,\cdots, \lfloor \frac{n+1}{2} \rfloor\},\cdots,\{1,2,\cdots, (n+1) \} \}$
-     In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots \lfloor \frac{n+1}{2} \rfloor-1$ and $x_{\lfloor \frac{n+1}{2} \rfloor} \rightarrow t$ and  consider the limit $t \rightarrow 0$ to give:
-    \bea
-    u^{(n+1)}_{J } &\rightarrow& u_{J}^{((n+1)-|I|)} ~\text{with}~ J\subseteq \{1,\cdots,|I|-1\}\\
-     u^{(n+1)}_{J \cup \{|I|\}} &\rightarrow& u_{K \cup\{0\}}^{((n+1)-|I|)} ~\text{with}~ J\subsetneq I\{1,\cdots,|I|-1\}
-    \eea
-     \bea
-    u^{(n+1)}_{K \cup I } &\rightarrow& u_{J}^{(|I|-1)} ~\text{with}~ K\subseteq \{|I|+1,\cdots,n+1\}\\
-     u^{(n+1)}_{K \cup \{0\}\cup I} &\rightarrow& u_{K \cup{0}}^{(|I|-1)} ~\text{with}~ K\subsetneq I\{|I|+1,\cdots,n+1\}
-    \eea
-   which gives $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$ 
-    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{\{0\},\{0,(n+1)\},\cdots,\{0,\lfloor \frac{n+1}{2} \rfloor+2,\cdots,(n+1)\}$
-    In this case we take $x_i \rightarrow \frac{ x_i}{t}$ for $i=1,\cdots \lfloor \frac{n+1}{2} \rfloor$ and $x_{\lfloor \frac{n+1}{2}+1 \rfloor} \rightarrow \frac{1}{t}$ and  consider the limit $t \rightarrow 0$ to give:
-    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{\{0,\lfloor \frac{n+1}{2} \rfloor+1,\cdots,(n+1)\},\cdots,\{0,2,\cdots,(n+1)\} \}$
-    In this case we take $x_i \rightarrow \frac{ x_i}{t}$ for $i=1,\cdots \lfloor \frac{n+1}{2} \rfloor$ and $x_{\lfloor \frac{n+1}{2}+1 \rfloor} \rightarrow \frac{1}{t}$ and  consider the limit $t \rightarrow 0$ to give:
+    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e $I =  \{1,2,\cdots, k \}$ with $k= 1,2,\cdots, \lfloor \frac{n+1}{2} \rfloor -1$
+
+    In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots, k $ and consider the limit $t \rightarrow 0$ to get:
+    \bea
+    u^{(n+1)}_{J \cup  I} &\rightarrow& u_{J}^{((n+1)-k )} ~\text{with}~ J\subseteq\bar{I}\\
+     u^{(n+1)}_{K} &\rightarrow& u_{K}^{(k-1)} ~\text{with}~ K\subsetneq I
+    \eea
+   which is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$
+
+    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{1,2,\cdots,k \}$ with $k= \lfloor \frac{n+1}{2} \rfloor,\cdots,(n+1)$
+
+     In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots k-1$ and $x_{k} \rightarrow t$ and  consider the limit $t \rightarrow 0$ to get:
+    \bea
+    u^{(n+1)}_{J } &\rightarrow& u_{J}^{((n+1)-k)} ~\text{with}~ J\subseteq \{1,\cdots,k-1\}\\
+     u^{(n+1)}_{J \cup \{k\}} &\rightarrow& u_{K \cup\{0\}}^{((n+1)-k)} ~\text{with}~ J\subsetneq \{1,\cdots,k-1\}
+    \eea
+     \bea
+    u^{(n+1)}_{K \cup I } &\rightarrow& u_{J}^{(k-1)} ~\text{with}~ K\subseteq \{k +1,\cdots,n+1\}\\
+     u^{(n+1)}_{K \cup \{0\}\cup I} &\rightarrow& u_{K \cup\{0\}}^{(k-1)} ~\text{with}~ K\subsetneq \{k +1,\cdots,n+1\}
+    \eea
+   which is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$ 
+    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{0,(k+1),\cdots,(n+1)\}$ with $k= \lfloor \frac{n+1}{2} \rfloor+1,\cdots,(n+1)$
+
+    In this case we take $x_i \rightarrow \frac{ x_i}{t}$ for $i=1,\cdots k-1$ and $x_{k} \rightarrow \frac{1}{t}$ and  consider the limit $t \rightarrow 0$ to get:
+    \bea
+    u^{(n+1)}_{J \cup I } &\rightarrow& u_{J}^{(n+1)-k} ~\text{with}~ J\subseteq \{1,\cdots,(k-1)\}\\
+     u^{(n+1)}_{J \cup \{k\}\cup I} &\rightarrow& u_{J \cup\{0\}}^{(k-1)} ~\text{with}~ J\subsetneq \{1 ,\cdots, k\}
+    \eea
+     \bea
+    u^{(n+1)}_{K} &\rightarrow& u_{K}^{k-1} ~\text{with}~ K\subseteq I
+    \eea
+    which again is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$. 
+    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ $I = \{0,(k+1),\cdots,(n+1)\}$ with $k= 1,\cdots, \lfloor \frac{n+1}{2} \rfloor+1$.
+
+    In this case we take $x_i \rightarrow \frac{x_i}{t}$ for $i=1,\cdots, k$ and consider the limit $t \rightarrow 0$ to get:
+    \bea
+    u^{(n+1)}_{J} &\rightarrow& u_{J}^{(n+1)-k} ~\text{with}~ J\subseteq I
+    \eea
+     \bea
+    u^{(n+1)}_{K \cup I} &\rightarrow& u_{K}^{k-1} ~\text{with}~ K\subsetneq \{1,\cdots,k\}
+    \eea
+
+     which again is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$. 
 \end{enumerate}
-
-Some of the $u$-equations for the $n$-dimensional permutahderon:\\
+This proves that the permutahedron $\mathscr P_n$ is indeed a binary geometry for all $n$.
+
+The above proof did not explicitly use the $u$- equations for $\mathscr P_n$. 
+The $u$-equations for $\mathscr P_n$ are complicated polynomials and Some of them are:\\
 
@@
 \end{enumerate}
-We shall now try to argue ${\mathscr P_n}$ is binary. We proceed inductively by first noticing that 
+
 \section{Configuration spaces with perfect $u$-equations from degenerating $A_n$ and $B_n$}
@@
 {\bf things I wrote in my handwritten notes...}
+
+The degenerations of $A_n$ is given by setting some $c$s in ABHY construction or deleting the corresponding elements in the building set.
+Note that the building set after deletion doesn't need to be a new building set, \emph{i.e.} a degeneration of $A_n$ may not be a generalized permutohedron.
+However, we can still ask the following question: are these degenerations binary geometries?
+Of course, we should require at least that the number of facets of the degeneration of $A_n$ should be equal to the size of the corresponding deleted building set.
+Before answer this question, let's first find all degenerations of $A_n$ with this property.
+
+%For convenience, we abuse the name `building set' for degenerations of $A_n$ in this subsection.
+
+From the following equations for facets $\{F_{ij}\}$ of $A_n$
+\[
+F_{ac}+F_{bd}-F_{bc}-F_{ad}=\sum_{a\leq p<b\atop{c\leq q<d}}c_{pq}
+\]
+for $1\leq a<b<c<d\leq n+3$, ({\bf Zhenjie}: I conjecture that) we find the most economical way to get a degeneration which satisfies the above property is setting all $c$s on the RHS of 
+\begin{align*}
+    &F_{ac}+F_{bd}-F_{ad}=\sum_{a\leq p<b< q<d}c_{pq}\quad \text{for $a<b<c=b+1<d$ }\\
+    \text{or}&\\
+    &F_{1c}+F_{b,n+3}-F_{bc}=\sum_{1\leq p<b\atop{c\leq q<n+3}}c_{pq}\quad \text{for $a=1$ and $d=n+3$}
+\end{align*}
+to be zero, and all wanted degenerations can be got by setting $c$s in several above equations. 
+%We should see what happens when we set $c$s to be zero in only one above equations: 
+{\bf (proof?)}
+
+The basic idea for counting: Suppose that
+\[
+F_{ac}+F_{bd}-F_{ad}=0.
+\]
+Since $F_{ad}$, $F_{bd}$, $F_{ac}\geq 0$, the above equation force $F_{ac}$ and $F_{bd}$ to be zero when $F_{ad}=0$.
+Therefore, $F_{ad}$ cannot be a true facet of the degeneration.
+We should count the number of deleted $c$ and such spurious facets.
+They should be equal.
+
+(Conjecture: they are all binary.)
+
+(Find those with perfect $u$-eq?)
 

### 2020-04-13 draft_ABP.tex
Updates from Overleaf

@@
 to be zero, and all wanted degenerations can be got by setting $c$s in several above equations.
-%We should see what happens when we set $c$s to be zero in only one above equations: 
-{\bf (proof?)}
-
-The basic idea for counting: Suppose that
-\[
-F_{ac}+F_{bd}-F_{ad}=0.
-\]
-Since $F_{ad}$, $F_{bd}$, $F_{ac}\geq 0$, the above equation force $F_{ac}$ and $F_{bd}$ to be zero when $F_{ad}=0$.
-Therefore, $F_{ad}$ cannot be a true facet of the degeneration.
-We should count the number of deleted $c$ and such spurious facets.
-They should be equal.
+
+We can see what happens from mesh when we set $c$s to be zero in only one above equations: an equation above corresponds a big diamond whose top or bottom corner and all $c$s are zero. For example,
+\begin{center}
+	\begin{tikzpicture}
+		\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$0$}
+		-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$B$}-- cycle;
+		\draw (-1,-1) -- (1,1);
+		\draw (-1,1) -- (2,-2);
+		\draw (0,-2) -- (2,0);
+			\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,1) {};
+	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,2) {};
+	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,1) {};
+	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
+	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
+	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,0) {};
+	\end{tikzpicture}
+\end{center}
+this diamond tells us that
+\[
+A+C-B=0.
+\]
+Since $A,B,C\geq 0$, the above equation force $A$ and $C$ to vanish when $B=0$.
+Therefore, $B$ is no longer a facet of the degeneration.
+Similarly, it's pleasure to show that black points are all vanishing facets in the above example, and generally
+the number of vanishing facets equals the number of deleted $c$s for degenerations of this type.
+
+One can use these diamonds to build a degeneration with more vanishing facets. For example, in $A_3$
+\begin{center}
+\begin{tikzpicture}
+	\fill[green!30] (2,1) -- (0,-1) -- (1,-2) -- (3,0);
+	\fill[blue!30] (3,0) -- (2,-1) -- (3,-2) -- (4,-1);
+	\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) -- (0,1);
+	\draw[thick] (-1,-2) -- (2,1);
+	\draw[thick] (-2,-1) -- (-1,-2);
+	\draw[thick] (-1,0) -- (1,-2) -- (3,0);
+	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,0) {};
+	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,1) {};
+	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (3,0) {};
+\end{tikzpicture}
+\end{center}
+after setting $c$s in green and purple diamonds to be zero, three facets (black points) vanish and building set after deletion is 
+\[
+\{\{0,1,2,3\},\{0,1,2\},\{0,1\},\{0\},\{1\},\{2\},\{3\}\}.
+\]
+One can further check that it's a cube or $A_1^3$.
 

### 2020-04-14 draft_ABP.tex
Updates from Overleaf

@@
 \]
-for $1\leq a<b<c<d\leq n+3$, ({\bf Zhenjie}: I conjecture that) we find the most economical way to get a degeneration which satisfies the above property is setting all $c$s on the RHS of 
+for $1\leq a<b<c<d\leq n+3$, an economical way to get a degeneration which satisfies the above property is setting all $c$s on the RHS of 
 \begin{align*}
@@
 
-We can see what happens from mesh when we set $c$s to be zero in only one above equations: an equation above corresponds a big diamond whose top or bottom corner and all $c$s are zero. For example,
+From the viewpoint of mesh, an equation above corresponds a big diamond whose top or bottom corner and all $c$s are zero. For example,
 \begin{center}
-	\begin{tikzpicture}
+	\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
 		\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$0$}
@@
 	\end{tikzpicture}
+	\qquad \text{or}
+	\qquad
+	\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
+		\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$B$}
+		-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$0$}-- cycle;
+		\draw (-1,-1) -- (1,1);
+		\draw (-1,1) -- (2,-2);
+		\draw (0,-2) -- (2,0);
+			\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
+	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-3) {};
+	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,-1) {};
+	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,-2) {};
+	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,-2) {};
+	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
+	\end{tikzpicture}
 \end{center}
-this diamond tells us that
+we can see that
 \[
@@
 Therefore, $B$ is no longer a facet of the degeneration.
-Similarly, it's pleasure to show that black points are all vanishing facets in the above example, and generally
+Similarly, black points are all vanishing facets in the above example, and generally
 the number of vanishing facets equals the number of deleted $c$s for degenerations of this type.
@@
 	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (3,0) {};
+	\node at (-2.5,-1) {$\{0\}$};
+\node at (-0.5,-1) {$\{1\}$};
+\node at (1.5,-1) {$\{2\}$};
+\node at (3.5,-1) {$\{3\}$};
+\node at (-1.6,0) {$\{0,1\}$};
+\node at (0.4,0) {$\{1,2\}$};
+\node at (2.4,0) {$\{2,3\}$};
+\node at (-0.8,1) {$\{0,1,2\}$};
+\node at (1.2,1) {$\{1,2,3\}$};
+\node at (1,2.2) {$\{0,1,2,3\}$};
 \end{tikzpicture}
@@
 \[
-\{\{0,1,2,3\},\{0,1,2\},\{0,1\},\{0\},\{1\},\{2\},\{3\}\}.
-\]
-One can further check that it's a cube or $A_1^3$.
-
-(Conjecture: they are all binary.)
+\{\{0,1,2,3\},\{0,1,2\},\{1,2,3\},\{0,1\},\{2,3\},\{0\},\{3\}\}.
+\]
+
+Suppose $\mathscr D$ is the set of all vanishing facets in the building set, we can read from the mesh that
+\[
+F_{I'}=\sum_{I\not\in \mathscr D}M_{I'}^IF_I
+\]
+for any $I'\in \mathscr D$, where $M$ is a matrix with non-negative entries. Therefore,
+\[
+\prod_{I\in \mathscr A_n}u_{I}^{F_{I}}=
+\prod_{I'\in \mathscr D}u_{I'}^{F_{I'}}
+\cdot
+\prod_{I\not\in \mathscr D}u_{I}^{F_{I}}=
+\prod_{I\not\in \mathscr D}\biggl(
+u_I\prod_{I'\in \mathscr D}u_{I'}^{M_{I'}^I}
+\bigg)^{F_I},
+\]
+so the new $u$-variables of the degeneration are
+\[
+    \tilde u_{I}=u_I\prod_{I'\in \mathscr D}u_{I'}^{M_{I'}^I}
+\]
+for any $I\not\in \mathscr D$. 
+%From the viewpoint of mesh, the product are taken over all diamonds whose $c$s are all zero, top (respectively, bottom) corner is a deleted element $I'$, bottom (respectively, top) corner is 0 and left or right corner is $I$, because for such diamond $F_{I'}=F_I+\cdots$ or $M^I_{I'}=1$.
+For example, in the above example of $A_3$,
+\[
+F_{123}=F_{1}+F_2+F_3, \quad F_{12}=F_1+F_2, \quad F_{23}=F_2+F_3,
+\]
+so 
+\begin{align*}
+\tilde u_{1}&=u_1 u_{123} u_{12}=\frac{x_1x_{012}}{x_{12}x_{01}}\frac{x_{123}}{x_{0123}}\frac{x_{12}x_{0123}}{x_{123}x_{012}}=\frac{x_1}{x_{01}},\\
+\tilde u_{2}&=u_2 u_{123} u_{12}u_{23}=\frac{x_2x_{123}}{x_{23}x_{12}}\frac{x_{123}}{x_{0123}}\frac{x_{12}x_{0123}}{x_{123}x_{012}}\frac{x_{23}}{x_{123}}=\frac{x_{2}}{x_{012}},\dots
+\end{align*}
+
+(Conjecture: they are all binary. In fact, I guess that $\tilde u_I\to 0$ is still given by $x_i\to 0$ for $i\in I$, then Chi's proof can be applied here.)
 

### 2020-04-20 draft_ABP.tex
Update draft_ABP.tex
Updates from Overleaf

@@
 \section{Introduction}
-In \cite{} the notions of stringy canonical forms and binary geometries were introduced which helped in understanding the configuration spaces of clusters as generalisations of moduli space for scattering of particles and strings .
-
-It is a natural question to ask if binary geometries whose stringy integrals factorise at any finite $\alpha^{'}$ are extremely special and are associated to only the classical $A_n, B_n, C_n,D_n$ or  Exceptional $E_6, E_7, E_8, F_2, G_4$  type clusters  as discussed in \cite{}.
-In this paper we answer this question in the negative by providing infinitely many counter examples.
-These fall broadly into two classes, the first of which corresponds to the permutahedron $P_n$ and more generally generalised permutahedra which do not have perfect $u$-equations but are still binary.
+
+In \cite{} the notion of {\it stringy canonical forms} were introduced as a general framework for generalizing tree-level string amplitudes, or integrals over the moduli space ${\cal M}_{0, n}$.
+Various nice properties of string amplitudes and their field-theory limits, such as factorizations for $\alpha' \to 0$ limit and finite $\alpha'$, channel duality and exponent softness, scattering equations, {\it etc.} all naturally extend to stringy canonical forms.
+To briefly summarize the idea, let's begin with the disk integral for open-string amplitudes with ordering $(1,2,\cdots, n)$:
+\begin{equation}\label{stringint}
+{\cal I}^{\rm open-string}_{1,2,\cdots,n} (\{s\}):=\int_{\mathcal M_{0,n}^+}
+\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i{+}1}}
+\prod_{i<j}(z_j{-}z_i)^{\alpha' s_{ij}},
+\end{equation}
+where $\mathcal M_{0,n}^+$ is the positive part of moduli space for the ordering, and $\mathsf{PT}_n:=\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i+1}}$ its canonical form~\cite{};  %each factor  $(z_j-z_i)$ in the Kobe-Nieson factor $\prod_{i<j}(z_j-z_i)^{\alpha' s_{ij}}$ is a nowhere vanishing function on $\mathcal M_{0,n}^+$.
+With a positive parameterization $\{x_1,\dots,x_{n-3}\}$ of $\mathcal M_{0,n}^+$, 
+this canonical form becomes $\prod_{i=1}^{n-3}\mathrm d \log x_i$, and the Koba-Nieson factor $\prod_{i<j}(z_j-z_i)^{\alpha' s_{i j}}$ becomes a product of powers of polynomials with 
+non-negative coefficients~\cite{}: $\prod_i x_i^{\alpha' X_i} \prod_I p_I(x)^{-\alpha' c_I}$.
+Note that we have factored out $n{-}3$ monomials, $x_i$, and left with $n(n{-}3)/2-(n{-}3)$ positive polynomials $p_I(x)$, with exponents $X_i$'s and $c_I$'s given by linear combinations of the Mandelstam variables $s_{i,j}$.
+
+\paragraph{Stringy canonical forms} Motivated by this rewriting of string integral~\eqref{stringint}, we define a general stringy integral as a $d$-dimensional integral~\cite{}
+\begin{equation}\label{stringycanonicalform}
+	\mathcal I (\mathbf X,\{c\})=
+	\int_{\mathbb R_+^d}\prod_{i=1}^d \frac{\mathrm d x_i}{x_i}x_i^{\alpha'X_i}
+	\prod_{I=1}^m p_I(x)^{-\alpha' c_I},
+\end{equation}
+where we allow $m$ arbitrary Laurent polynomial with non-negative coefficients, $p_I(x)$, and without loss of generality we assume exponents $X_i>0$ and $c_I>0$~\footnote{These are ``positive" stringy canonical forms, which are integrals over $\mathbb R_+^d$.
+We can also consider ``complex" case with the integrand mod-squared and integrated over $\mathbb C^d$, which are generalizations of closed-string amplitudes~\cite{}.}.
+
+Any integral of the form \eqref{stringycanonicalform} inherits various remarkable properties of string amplitudes \eqref{stringint}, which all depend on the existence of a polytope $\mathcal P:=\sum_I c_I N[p_I]$; here $N[p_I]$ is the Newton polytope of the polynomial $p_I$, and we take the (weighted) Minkowski sum~\cite{}.
+First of all, one can show that the integral \eqref{stringycanonicalform} is convergent if and only if $\mathbf X=(X_1,\dots,X_d)$ is in the interior of the polytope $\mathcal P$ (we assume that ${\cal P}$ is $d$ dimensional).
+The leading order of the integral in its $\alpha'$ expansion, dressed with $d^d \mathbf X$, is given by the canonical form of the polytope, ${\Omega}(\cal P)$, thus it can be viewed as $\alpha'$-deformation of $\Omega(\cal P)$ (hence the name ``stringy canonical form").
+Generically the poles of $\Omega(\cal P)$ are given by equations of
+facets for $\mathcal P$, which are also poles of the integral at finite $\alpha'$, and the residue on any such pole is given by a stringy canonical form defined for that facet (see~\cite{} for details).
+
+For the string integral \eqref{stringint}, ${\cal P}$ is nothing but the ABHY associahedron~\cite{}, whose canonical form gives bi-adjoint $\phi^3$ amplitude as the $\alpha'\to 0$ limit of \eqref{stringint}~\cite{}.
+The poles are the planar variables $X_{i,j}$, on which \eqref{stringint} factorizes into lower-point integrals even for finite $\alpha'$.
+Moreover, the saddle point equations as $\alpha' \to \infty$ can be written as $X_i=\sum_I c_I \partial \log p_I/\partial \log x_i$ for $i=1,\cdots, d$; they provide a diffeomorphism from the integration domain to ${\cal P}$, thus $\Omega(\mathcal P)$ can be computed as a pushforward of $\prod_i d\log x_i$ via summing over the saddle points~\cite{}.
+In particular, for the string integral \eqref{stringint}, the scattering equations provide a map from ${\cal M}_{0,n}^+$ to ABHY associahedron, and the pushforward is equivalent to the CHY formula for $\phi^3$ amplitude~\cite{}.
+
+\paragraph{Configuration spaces} One way to describe the combinatorics of the polytope ${\cal P}$ is through the {\it configuration space}, {\it e.g.} as blow-up of $\mathbb R_+^D$ in the $\mathbf x$-space.
+However, it is usually difficult to use $\mathbf x$ for this, even for the string integrals \eqref{stringint}.
+For example, a facet usually corresponds to a complicated limit process with $x \to 0$ or $\infty$.
+As proposed in~\cite{}, an elegant way to realize ${\cal P}$ in configuration space is by introducing a set of constrained $u$ variables $\{u_\alpha\}$.
+The configuration space is the variety defined by a set of polynomial equations satisfied by $\{u_\alpha\}$ (or $u$ equations), and the polytope ${\cal P}$ can be realized combinatorially by $\{u_\alpha \geq 0\}$.
+%facet is simply given by an equation $u_A=0$. 
+To define the $u$ variables, we first construct the so-called \textit{big polyhedron} in the space $\mathbf S:=(X_1,\dots,X_d,-c_1,\dots,-c_m) \in \mathbb R^{d{+}m}$.  %then $\{u_A\}$ 
+%\[
+%	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
+%	\prod_{A}u_A^{\alpha' U_A}
+%	=
+%	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
+%	\prod_{J}p_J^{\alpha' S_J}.
+%\]
+
+The polytope ${\cal P}$ is bounded by inequalities $W_a^JS_J\geq 0$ in the space of $\mathbf X$, where $W_a^J$ is determined by the facet $F_a$ of $\mathcal P$.
+These inequalities also cut out a polyhedron in the $(d+m)$-dimensional space of $\mathbf S$, which is defined to be the big polyhedron of $\mathcal P$,
+and the integral $\mathcal I(\mathbf S)$ converges for each point $\mathbf S$ 
+inside this polyhedron. Dually, we can describe the big polyhedron by its vertices. Suppose 
+$\{V_J^\alpha\}_{1\leq \alpha \leq v}$ are its non-zero vertices ($v$ denotes the number of vertices), a point $\mathbf S$ inside 
+the polyhedron can be written as $S_J = F_\alpha V^\alpha_J$ with non-negative coefficients 
+$\{F_\alpha\}_{1\leq \alpha \leq v}$.  Therefore, the integral $\mathcal I(\mathbf S)$
+can be seen as a function of ``dual coordinates" $\{F_A\}$ which encourages us to 
+rewrite the integral to make it manifest by (here we collectively denote $p_J=(x_1, \cdots, x_d, p_1, \cdots, p_m)$)~\footnote{Note that one can indeed treat the monomials $x_i^{\alpha' X_i}$ on the equal footing as polynomials, since Minkowski sum w.r.t.
+them amounts to merely translating the polytope $c_I N[p_I]$ by $-X_i$ in the $i$-th direction~\cite{}.}.
+
+\begin{equation}
+	\mathcal I(\mathbf F)=
+	\int_{\mathbb R_+^d} \prod_{i=1}^d \frac{d x_i}{x_i}~%\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
+	\prod_{\alpha}u_\alpha^{\alpha' F_\alpha}
+	=
+	\int_{\mathbb R_+^d}\prod_{i=1}^d \frac{d x_i}{x_i}~%\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
+	\prod_{J}^{d{+}m} p_J^{\alpha' S_J},
+\end{equation}
+where we introduce a new set of variables $u_\alpha = \prod_J p_J^{V_J^\alpha}$ for 
+$\alpha=1,\dots, v$. Note that there's no unique way to write $S_J=F_\alpha V_J^\alpha$ if the big polyhedron is not a simplex, \textit{i.e.} $v>d+m$, and in this case,
+$u$-variables $\{u_\alpha \}$ are not independent. Therefore, it is an important special case when the big polyhedron is a simplex, \textit{i.e.} $N=v=d+m$, where $N$ is 
+the number of facets of the big polyhedron or the original polytope $\mathcal P$,
+and inequalities $F_\alpha=S_J(V^{-1})^J_\alpha \geq 0$ are exactly the inequalities $W_a^J S_J\geq 0$ up to resales $F_\alpha \mapsto t F_\alpha$ for non-zero factors $t$, because
+there's no nontrivial linear isometry from the simplex to itself besides permutations of vertices. Therefore, we identity the label of facets $a$ with the label of 
+vertices $A$ and get $V=W^{-1}$. Furthermore, every facet of the original polytope $\mathcal P$ can be associated with a single $u_\alpha$ going to zero. 
+%Generally, the big polyhedron of a stringy integral is not necessary to be a simplex.
+
+\paragraph{Cluster stringy integrals and binary geometries} A class of very special integrals belong to this case~\cite{}: stringy canonical forms for generalized associahedra of finite-type cluster algebras, namely $A_n$, $B_n$, $C_n$, $D_n$, and exceptional cases ($E_6$, $E_7$, $E_8$, $F_4$, $G_2$).
+These ``cluster stringy integrals"~\cite{}, and the associated ``cluster configuration space"~\cite{}, turn out to be much more special and rigid extensions of string amplitudes \eqref{stringint} and the moduli space ${\cal M}_{0,n}$, which correspond to the case of type $A_{n{-}3}$.
+The leading order of such an integral is given by canonical function of the corresponding generalized associahedra, whose combinatorics is attached to the Dynkin diagram (each facet is given by removing a node), {\it e.g.} $D_n \to D_m \times A_{n{-}1{-}m}$ or $A_{n{-}1}$~\cite{}.
+Even at finite $\alpha'$, it has the remarkable factorization property tied to the Dynkin diagram.
+Moreover, for type $B/C$ (known as ``cyclohedron") and $D$, the leading order is associated with one-loop bi-adjoint $\phi^3$ amplitudes.
+
+These nice properties become manifest in the configuration space: not only the big polyhedron is a simplex, the $u$-equations are of very special form:
+\begin{equation}\label{perfectu}
+	1-u_\alpha=\prod_{\beta} u_\beta^{(\beta|\alpha)},
+\end{equation}
+where the product is over all $N$ variables ($N$ facets), and the integer $(\beta | \alpha)\geq 0$ is the so-called compatibility degree defined in the corresponding cluster algebra~\cite{}.
+%Varieties defined by $u$-equations associated with finite type clusters  are called cluster configuration spaces. 
+We see that when $u_\alpha$ (for a facet $\alpha$) goes to $0$, it forces all the $u_\beta$ with $\beta | \alpha>0$ goes to $1$ (for facets $\beta$ are exactly those {\it incompatible} with $\alpha$); the remaining $u$'s that are compatible with $u_\alpha$ satisfy $u$ equations for the facet, which factorizes as removing a node of the Dynkin diagram.
+Therefore, we say that the configuration space is a {\it binary geometry}.
+Note that this is true also for the complex case, and if we further require all $u$ variables to be positive, we have $0<u<1$ which gives the positive configuration space~\cite{}.
+The binary property is what guarantees the stringy integral to factorize even at finite $\alpha'$: on the pole $X_\alpha \to 0$, $u_\alpha\to 0$ forces all incompatible $u_\beta\to 1$ which decoupled from $\prod u^{\alpha' X}$, and the integral becomes the factorized one for the facet $\alpha$.
+
+For example, the string integral \eqref{stringint} corresponds to type $A_{n{-}3}$, %and we can use a positive parametrization $z_i=1+x_2+\cdots+x_{i{-}1}$ for $i=2,3,\cdots, n{-}1$ (with gauge fixing $z_1=0, z_2=1$ and $z_n=\infty$).
+The integral is rewritten as
+%\[
+%    \mathcal I_n=\int_{\mathbb R_+^{n-3}}
+%	\frac{\mathrm dx_2\cdots \mathrm dx_{n-2}}{x_2\cdots x_{n-2}}
+%	\prod_{i<j} p_{ij}^{\alpha' s_{ij}},
+%\] where $p_{ij}=x_i+\cdots+x_{j-1}$. 
+and the $N=n(n{-}3)/2$ $u$ variables of this configuration space are~\cite{}
+\[
+	u_{i j}=\frac{(z_{i-1}-z_j)(z_i-z_{j-1})}{(z_i-z_j)(z_{i-1}-z_{j-1})},
+\]
+and they satisfy the $u$-equations
+\[
+	1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl},
+\]
+where $(i,j)\not\sim (k,l)$ means that the diagonals $(i,j)$ and $(k,l)$ of $n$-gon are crossed, thus the two facets are incompatible (note here compatibility degree is just $0$ or $1$).
+For $u_{i,j}\to 0$, all incompatible $u_{k,l} \to 1$, and the remaining $u$'s fall into those of the two polygons divided by $(i,j)$, with their own $u$ equations.
+The Koba-Nilesen factor becomes $\prod_{i,j} u_{i,j}^{\alpha' X_{i,j}}$ where $X_{i,j}$ are planar variables for the facets of ABHY associahedron, which makes the factorization of string amplitude at finite $\alpha'$ manifest.
+All these generalize to integrals and configuration spaces for finite type cluster algebra.
+
+\subsection{Summary of main results}
+
+It is a natural question to ask if binary geometries, whose stringy integrals factorize at any finite $\alpha^{'}$, are extremely special and can only be products of generalized associahedra of finite type.
+In this paper we answer the question in the negative by providing infinitely many new examples of binary geometries.
+Before proceeding, we remark that $u$ equations of the form \eqref{perfectu} (which we refer to as ``perfect" $u$ equations) imply binary geometries, but the converse is not true.
+Broadly speaking, for a $n$-dimensional polytope ${\cal P}$ where each facet is associated with a $u$ variable,  if for any $u_\alpha\to 0$, we have for all incompatible facets $\beta$, $u_\beta \to 1$, then we regard such an $n$-dimensional variety (defined by the $u$ equations) as a binary geometry.
+From this definition, we see that one can realize simplex as a binary geometry since all facets are compatible with each other.
+Consider $u$ equations for a $n$-dimensional simplex with facets labelled by $\alpha=0,1,\cdots, n$
+\[
+1-u_\alpha=\sum_{\beta \neq \alpha} u_\beta\,.
+\] 
+As $u_\alpha\to 1$, there is no $u\to 1$, and all $n$ remaining $u$ variables satisfy the same equations for that facet, which is an $(n{-}1)$-dim simplex.
+Although this example is trivial, it does show that we do not necessarily need perfect $u$ equations to have binary geometries.
+Generically, for a $n$-dimensional polytope ${\cal P}$ with $N$ facets,  have an $n$-dimensional configuration space defined by $u$ equations
+\be\label{genueq}
+1-u_\alpha=p_\alpha(\{u\}) \prod_\beta u_\beta^{\beta|\alpha} 
+\ee
+where $\beta |\alpha \geq 0$ are integers which vanishes for $\beta$ compatible with $\alpha$, and $p_\alpha(\{u\})$ is an arbitrary polynomial which must equal to unity on the facet $\alpha$, $p_\alpha (\{u\})|_{u_\alpha=0}=1$.
+When $u_\alpha \to 0$, since it appears on the RHS ofequation with $1-u_\beta$ for any incompatible $\beta$, we have $u_\beta\to 1$ for any polynomial $p_\beta (\{u\})$.
+However, in the equation with $1-u_\alpha$, since all the incompatible $u_\beta \to 1$ we find $p_\alpha (\{u\})|_{u_\alpha=0}=1$ (where we evaluate the polynomial at $u_\alpha=0$ and all incompatible $u_\beta=1$).
+For cluster configuration spaces, we have perfect $u$ equations with $p_\alpha=1$ for all $\alpha$.
+
+As the main result of the paper, we present infinitely many new examples of binary geometries which have $u$ equations of the form \eqref{genueq}, and (also infinitely) many of them with perfect $u$ equations.
+The key is to consider a class of stringy integrals for {\it generalized permutohedra} that can be realized as Minkowski sum of coordinate simplices as follows (more details will be given later).
+Given the label set $[0,n]=\{0,1,\cdots, n\}$, we define a {\it building set} $\mathbf B$ as a collection of subsets $I \subset [0,n]$ that satisfy (1).
+if $I, J \in {\mathbf B}$ and $I\cap J\neq \emptyset$, then $I\cup J \in {\mathbf B}$, and (2).
+it contains all {\it singletons} $\{i\}$.
+For each subset $I$ we have a simplex $\Delta_I$ as the convex hull of unit vectors ${\bf e}_i$ with $i\in I$, and the generalized permutohedron ${\mathscr P}(\mathbf B)$ is given by (weighted) Minkowski sum of $\Delta_I$ (defined on a $n$-dimensional hyperplane of the $(n{+}1)$-dim space)~\cite{}.
+It is very natural to define stringy canonical form for such a building set $\mathbf B$: for each subset $I$, we have the simplest {\it linear} polynomial $x_I:=\sum_{i\in I} x_i$ (for singletons, $x_{\{i\}}=x_i$ are the coordinates), and
+\begin{equation}\label{intgenperm}
+{\cal I}_{\mathbf B}(\{S\}):=\int_{\mathbb R_+^n}\frac{1}{{\rm vol}~GL(1)} \prod_{i=0}^n \frac{d x_i}{x_i} %x_i^{S_i}
+\prod_{I \in {\mathbf B}} x_I^{\alpha' S_I}\,,
+\end{equation}
+where the integration domain is defined projectively, {\it i.e.} up to a $GL(1)$ redundancy which can be fixed by fixing, say, $x_0=1$; the exponents $S_I$ satisfy $\sum_I S_I=0$ (if we fix the gauge by $x_0=1$, $S_0$ drops out and the rest $S_I$ are independent).
+By construction, ${\cal I}_{\mathbf B}$ is indeed the stringy canonical form for the generalized permutohedron $\sum_I S_I N[x_I]=\sum_I S_I \Delta_I={\mathscr P}(\mathbf B)$.
+Note that one can split the product as $\prod_I x_I^{\alpha' S_I}=\prod_{i=1}^n x_i^{\alpha' X_i} \prod_I^m x_I^{-\alpha' c_I}$ with $X_i:=S_{\{i\}}$ for singletons, $-c_I=S_I$ for non-singleton $I$'s (we denote their total number as $m$), and it suffices to take the Minkowski sum w.r.t.
+the non-singelton $I$'s, since the singleton ones are merely translating the polytope.
+
+Let's list three examples of ${\mathscr P} (\mathbf B)$ and ${\cal I}_{\mathbf B}$ which will be our main examples throughout the paper. 
+\begin{itemize}
+\item Consider $\mathbf B$ as the collection of all $n(n{+}3)/2+1$ consecutive intervals within $[0,n]$, ${\mathscr P}(\mathbf B) \equiv {\mathscr A}_n$ is the $n$-dim associahedron, \eqref{intgenperm} is nothing but $(n{+}3)$-pt string integral \eqref{stringint}; {\it e.g.} for $n=2$, ${\mathbf B}=\{\{i\}, \{0,1\}, \{1,2\}, \{0,1,2\}\}$, and we have a pentagon ${\mathscr A}_2$.
+\item Consider $\mathbf B$ as the collection of all $n(n{+}1)+1$ cyclic intervals of $[0,n]$ which can wrap around $n$, ${\mathscr P} (\mathbf B) \equiv {\mathscr B}_n$ is the $n$-dim cyclohedron, and in sec.
+2 we will show that non-trivially \eqref{intgenperm} is the cluster stringy integral for type $B_n$ (not that for type $C_n$); {\it e.g.} $n=2$, ${\mathbf B}=\{\{i\}, \{0,1\}, \{1,2\}, \{2,0\}, \{0,1,2\}\}$, and we have a hexagon ${\mathscr B}_2$.
+\item Consider $\mathbf B$ as the collection of all $2^{n{+}1}-1$ subsets of $[0,n]$, ${\mathscr P}(\mathbf B) \equiv {\mathscr P}_n$ is the $n$-dim permutohedron (for $n=2$, it coincide with ${\mathscr B}_2$ the hexagon).
+All generalized permutohedra (and their stringy integrals) can be obtained from (that of) ${\mathscr P}_n$.
+\end{itemize}
+
+Although associahedra and cyclohedra are special cases of generalized permutohedra, it is interesting that \eqref{intgenperm} in these cases turn out to be exactly cluster stringy integrals of type $A$ and $B$!
+It is not completely surprising since these are the only two cases of cluster configuration spaces that can be identified with hyperplane arrangement (which is consistent with the linear polynomials), while {\it e.g.} for type $C$ we do not know such a hyperplane arrangement and for type $D_4$ {\it etc.} we know this is impossible from point-count argument~\cite{}.
+In sec.
+2, we will go further and discover more binary geometries with perfect $u$ equations, which can be obtained by ``degenerating" type $A$ and $B$ integrals by requiring certain $S_I=0$ (for example, type $A$ integral is in fact a degeneration of the type $B$ integral, which was not obvious before).
+Some of these cases are products of lower-dim $A$'s and $B$'s, but we will see entirely new binary geometries with perfect $u$ equations.
+
+Moreover, a remarkable statement we will make in sec.
+3 is that, the configuration space for any ${\cal I}_{\mathbf B}$ is always binary, which means that any $u_\alpha \to 0$ forces all the incompatible ones $u_\beta\to 1$.
+As we will see explicitly with ${\mathscr P}_n$, its $u$ equations indeed take the form of \eqref{genueq}, which is no longer perfect for $n>2$, but the space is binary and the integral factorizes as product of lower-dim permutohedron integrals at finite $\alpha'$!.
+Note that an important feature of any generalized permutohedron is that its facets are labelled by all subsets $I$ in ${\mathbf B}$ except for the complete set $[0,n]$, and on each facet it factorizes as product of two generalized permutohedra.
+The total number of facets $N$ equals $|{\mathbf B}|-1=n+m$, thus the big polyhedron is indeed a simplex as expected.
+In sec.
+3, we will present the formula for $u$ variables for any generalized permutohedron (which is equivalent to the formula for its ABHY-like realization), from which the binary and factorization properties follows.
+%These fall broadly into two classes, the first of which corresponds to the permutahedron $P_n$ and more generally generalised permutahedra which do not have perfect $u$-equations but are still binary.
 The second class corresponds to various degenerations of the associahedra and cyclohedra which are binary geometries with perfect $u$-equations.
@@
 
-\subsection{Invitation: stringy canonical forms and cluster configuration spaces}
-
-{\bf review of stringy canonical forms, mention big polytopes and $u$ variables in general; then specify to cluster string integrals, then cluster configuration spaces with perfect $u$ equations, do $A_n$, $B_n$ examples; define "binary geometries"}
-
-*******************
-
-Stringy canonical forms (or stringy integral) are generalizations of tree level string integrals
-\begin{equation}\label{stringint}
-\int_{\mathcal M_{0,n}^+}
-\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i+1}}
-\prod_{i<j}(z_j-z_i)^{\alpha' s_{ij}},
-\end{equation}
-where $\mathcal M_{0,n}^+$ is the postive part of moduli space of $n$ punctures on
-the Riemann sphere.
-In the context of stringy canonical form, the form $\mathsf{PT}(n):=\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i+1}}$ is understood
-as the canonical form of the moduli space $\mathcal M_{0,n}^+$, and each factor 
-$(z_j-z_i)$ in the Kobe-Nieson factor $\prod_{i<j}(z_j-z_i)^{\alpha' s_{ij}}$ 
-is a nowhere vanishing function on $\mathcal M_{0,n}^+$.
-With a positive parameterization $\{x_1,\dots,x_{n-3}\}$ of $\mathcal M_{0,n}^+$, 
-this canonical form becomes $\prod_{i=1}^{n-3}\mathrm d \log x_i$, 
-the Koba-Nieson factor becomes a product of powers of some polynomials with 
-non-negative coefficients, and the string integral turns into the form
-\begin{equation}\label{stringycanonicalform}
-	\mathcal I(\mathbf X,\{c\})=
-	\int_{\mathbb R_+^d}\prod_{i=1}^d \frac{\mathrm d x_i}{x_i}x_i^{\alpha'X_i}
-	\prod_{I=1}^m p_I(x)^{-\alpha' c_I},
-\end{equation}
-where $p_I$ are polynomials with non-negative coefficients. For general stringy
-canonical forms eq.\eqref{stringycanonicalform}, we allow $p_I$ to be any Laurent 
-polynomial with non-negative coefficients in the integral.
-
-Many remarkable aspects of string integral, \textit{e.g.} field-theory limit, 
-factorization, scattering equations, $u$-variables ..., can be carried to
-stringy canonical forms. Almost all of these aspects are related to a hidden 
-polytope $\mathcal P=\sum_I c_I N[p_I]$ of string canonical form 
-eq.\eqref{stringycanonicalform}, where $N[p_I]$ is the Newton polytope of $p_I$ and 
-the sum is understood as the Minkowski sum. For example, 
-eq.\eqref{stringycanonicalform} is convergent if and only if 
-$\mathbf X=(X_1,\dots,X_D)$ is in the interior of $\mathcal P$, equations of
-facets of $\mathcal P$ are massless poles of eq.\eqref{stringycanonicalform}
-and the residue on this facet is still a stringy canonical form of this facet.
-For stringy integrals eq.\eqref{stringint}, these polytopes are nothing but the ABHY
-associahedra~\cite{}.
-
-This polytope can also be realized in $\mathbf x$-space and understood
-as a blow-up of $\mathbb R_+^D$, but it's usually difficult to use $\mathbf x$ to
-describe this polytope, even for the string integrals eq.\eqref{stringint}. For
-example, a facet may correspond to a complicated limit process of $\mathbf x\to 0$
-or $\infty$.
+%\subsection{Invitation: stringy canonical forms and cluster configuration spaces}
+
+%{\bf review of stringy canonical forms, mention big polytopes and $u$ variables in general; then specify to cluster string integrals, then cluster configuration spaces with perfect $u$ equations, do $A_n$, $B_n$ examples; define "binary geometries"}
+
+%Stringy canonical forms (or stringy integral) are generalizations of tree level string integrals
+%\begin{equation}\label{stringint}
+%\int_{\mathcal M_{0,n}^+}
+%\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i+1}}
+%\prod_{i<j}(z_j-z_i)^{\alpha' s_{ij}},
+%\end{equation}
+%where $\mathcal M_{0,n}^+$ is the postive part of moduli space of $n$ punctures on
+%the Riemann sphere.
+%In the context of stringy canonical form, the form $\mathsf{PT}(n):=\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i+1}}$ is understood
+%as the canonical form of the moduli space $\mathcal M_{0,n}^+$, and each factor 
+%$(z_j-z_i)$ in the Kobe-Nieson factor $\prod_{i<j}(z_j-z_i)^{\alpha' s_{ij}}$ 
+%is a nowhere vanishing function on $\mathcal M_{0,n}^+$.
+%With a positive parameterization $\{x_1,\dots,x_{n-3}\}$ of $\mathcal M_{0,n}^+$, 
+%this canonical form becomes $\prod_{i=1}^{n-3}\mathrm d \log x_i$, 
+%the Koba-Nieson factor becomes a product of powers of some polynomials with 
+%non-negative coefficients, and the string integral turns into the form
+%\begin{equation}\label{stringycanonicalform}
+%	\mathcal I(\mathbf X,\{c\})=
+%	\int_{\mathbb R_+^d}\prod_{i=1}^d \frac{\mathrm d x_i}{x_i}x_i^{\alpha'X_i}
+%	\prod_{I=1}^m p_I(x)^{-\alpha' c_I},
+%\end{equation}
+%where $p_I$ are polynomials with non-negative coefficients. For general stringy
+%canonical forms eq.\eqref{stringycanonicalform}, we allow $p_I$ to be any Laurent 
+%polynomial with non-negative coefficients in the integral.
+
+%Many remarkable aspects of string integral, \textit{e.g.} field-theory limit, 
+%factorization, scattering equations, $u$-variables ..., can be carried to
+%stringy canonical forms. Almost all of these aspects are related to a hidden 
+%polytope $\mathcal P=\sum_I c_I N[p_I]$ of string canonical form 
+%eq.\eqref{stringycanonicalform}, where $N[p_I]$ is the Newton polytope of $p_I$ and 
+%the sum is understood as the Minkowski sum. For example, 
+%eq.\eqref{stringycanonicalform} is convergent if and only if 
+%$\mathbf X=(X_1,\dots,X_D)$ is in the interior of $\mathcal P$, equations of
+%facets of $\mathcal P$ are massless poles of eq.\eqref{stringycanonicalform}
+%and the residue on this facet is still a stringy canonical form of this facet.
+%For stringy integrals eq.\eqref{stringint}, these polytopes are nothing but the ABHY
+%associahedra~\cite{}.
+%
+%This polytope can also be realized in $\mathbf x$-space and understood
+%as a blow-up of $\mathbb R_+^D$, but it's usually difficult to use $\mathbf x$ to
+%describe this polytope, even for the string integrals eq.\eqref{stringint}. For
+%example, a facet may correspond to a complicated limit process of $\mathbf x\to 0$
+%or $\infty$.
 %However, as proven in \cite{},
@@
 %give us a diffeomorphism between the interiors of two polytopes in different spaces.
-However, for a limited class of stringy canonical forms, we can introduce
-the so-called $u$-variables $\{u_A\}$ to replace $\mathbf x$ such that the polytope 
-is described by $\{u_A\geq 0\}$ and a set of polynomial equations of $\{u_A\}$, and each
-facet is simply given by an equation $u_A=0$. One way to construct these $u$-variables
-is first constructing variables $\{U_A\}$ with similar properties in the space of
-$\mathbf S=(X_1,\dots,X_d,-c_1,\dots,-c_m)$ such that $\mathcal P=\sum_I c_I N[p_I]$ 
-is simply given by $\{U_A\geq 0\}$ and each facet is given by a $U_A=0$, and then
-relating $\{U_A\}$ to $\{u_A\}$ by the integral
-\[
-	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
-	\prod_{A}u_A^{\alpha' U_A}
-	=
-	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
-	\prod_{J}p_J^{\alpha' S_J}.
-\]
-
-The construction of $\{U_A\}$ comes from the viewpoint of \textit{big polyhedron}.
-The polytope $\mathcal P=\sum_I c_I N[p_I]$ is bounded by the inequalities
-$W_a^JS_J\geq 0$ of variables $\mathbf S=(X_1,\dots,X_d,-c_1,\dots,-c_m)$ in space 
-of $\mathbf X$, where $W_a^J$ is determined by the facet $F_a$ of $\mathcal P$. 
-These inequalities also cut out a polyhedron in the $(d+m)$-dimensional space of 
-$\mathbf S$, which is called the \textit{big polyhedron} of $\mathcal P$, 
-and the integral $\mathcal I(\mathbf S)$ converges for each point $\mathbf S$ 
-inside this polyhedron.
-
-Dually, we can describe the big polyhedron by its vertices. Suppose 
-$\{V_J^A\}_{1\leq A\leq v}$ are its non-zero vertices, the point $\mathbf S$ inside 
-the polyhedron can be written as $S_J = U_A V^A_J$ with non-negative coefficients 
-$\{U_A\}_{1\leq A\leq v}$.  Therefore, the integral $\mathcal I(\mathbf S)$
-can be seen as a function of `dual coordinates' $\{U_A\}$ which encourages us to 
-rewrite the integral to make it manifest by
-\[
-	\mathcal I(\mathbf U)=
-	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
-	\prod_{A}u_A^{\alpha' U_A}
-	=
-	\int_{\mathbb R_+^m}\frac{\mathrm d x_1\cdots \mathrm d x_n}{x_1\cdots x_n}
-	\prod_{J}p_J^{\alpha' S_J},
-\]
-where we introduce a new set of variables $u_A = \prod_J p_J^{V_J^A}$ for 
-$A=1,\dots,v$. Note that there's no unique way to write $S_J=U_AV_J^A$ when
-the big polyhedron is not a simplex, \textit{i.e.} $v>d+m$, and in this case,
-$u$-variables $\{u_A\}$ are not independent. 
-When the big polyhedron is a simplex, \textit{i.e.} $N=v=d+m$, where $N$ is 
-the number of facets of the big polyhedron or the original polytope $\mathcal P$,
-and inequalities $U_A=S_J(V^{-1})^J_A\geq 0$ are exactly the inequalities
-$W_a^J S_J\geq 0$ up to resales $U_A\mapsto t U_A$ for non-zero factors $t$, because
-there's no nontrivial linear isometry from the simplex to itself besides permutations
-of vertices. Therefore, we identity the label of facets $a$ with the label of 
-vertices $A$ and get $V=W^{-1}$. Furthermore, every facet of the original polytope
-$\mathcal P$ can be associated with a single $u_A$ going to zero, 
-giving a ``binary geometry'' we will describe later.
-
-Generally, the big polyhedron of a stringy integral is not necessary to be a simplex.
-It's known that stringy integrals associated to the $A_n$, $B_n$, $C_n$, $D_n$,
-$E_6$, $E_7$, $E_8$, $F_2$ and $G_4$ type clusters are in this type. What's more,
-they satisfy the so called $u$-equations with the form
-\begin{equation}\label{perfectu}
-	1-u_i=\prod_{j}u_j^{(i||j)},
-\end{equation}
-where $(i||j)\geq 0$ is a integral defined in the cluster algebra context \cite{}.
-Varieties defined by $u$-equations associated with finite type clusters 
-are called cluster configuration spaces. 
-For this type equations, once $u_i$ goes to $0$, it forces some $u_j$ to go to $1$.
-Therefore, these $u$-equations reveal the binary structure of the cluster
-configuration spaces.
-
-For example, $A_n$ type cluster configuration spaces come from original string 
-amplitudes
-\[
-	\mathcal I_n = \int_{z_1<z_2<\cdots <z_n}
-	\frac{\mathrm dz_2\cdots \mathrm dz_{n-2}}{(z_1-z_2)\cdots (z_{n-2}-z_{n-1})}
-	\prod_{i<j} (z_j-z_i)^{\alpha' s_{ij}},
-\]
-where we fix the gauge by setting $z_1=0$, $z_{n-1}=1$ and $z_n=\infty$.
-It's not in the form of stringy integrals, but we can use a positive
-parametrization 
-\[
-z_3=1+x_2,\quad z_4=1+x_2+x_3,\quad \dots, \quad 
-z_{n-1}=1+x_2+\cdots+x_{n-2}
-\]
-to rewrite the integral $\mathcal I_n$, then
-\[
-    \mathcal I_n=\int_{\mathbb R_+^{n-3}}
-	\frac{\mathrm dx_2\cdots \mathrm dx_{n-2}}{x_2\cdots x_{n-2}}
-	\prod_{i<j} p_{ij}^{\alpha' s_{ij}},
-\]
-where $p_{ij}=x_i+\cdots+x_{j-1}$. The $u$-variables of this configuration space are
-\[
-	u_{ij}=\frac{p_{i-1,j}p_{i,j-1}}{p_{ij}p_{i-1,j-1}},
-\]
-and they satisfy the $u$-equations
-\[
-	1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl},
-\]
-where $(i,j)\not\sim (k,l)$ means that diagonals $(i,j)$ and $(k,l)$ of
-$(n+3)$-gon are crossed.
-
-Another example still comes from a hyperplane arrangement, the Shi arrangement,
-which is also $B_n$ type cluster stringy integral.
-The Shi arrangement contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
-on the real line with the freedom of global transformation 
-$z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. The Shi arrangement is 
-given by the following hyperplanes
-\[
-	z_i-z_j=0\quad \text{and}\quad z_i-z_j=1\quad \text{for $1\leq i<j\leq n+1$},
-\]
-and its stringy integral is 
-\[
-\mathcal I_n = \int_{1>z_1>z_2>\cdots >z_n>0}
-\frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(1-z_1)(z_1-z_2)\cdots (z_{n}-0)}
-\prod_{0\leq i<j \leq n}(z_i-z_j)^{s_{ij}}(1-z_i+z_j)^{t_{ij}},
-\]
-where the positive region is given by $0<z_i-z_j<1$ for $1\leq i<j \leq n+1$.
-The $u$-variables of this configuration space are
-\[
-    u_1=1+z_1-z_2,\quad \dots,\quad u_{n}=1+z_{n}-z_{n+1},\quad u_{n+1}=z_{n+1}-z_1
-\]
-and 
-\[
-\begin{aligned}
-    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad &&\text{for $i<j$},\\
-    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad &&\text{for $i<j$},
-\end{aligned}
-\]
-where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices live in $\mathbb Z_{2n+2}$.
-They satisfy the following $u$-equations 
-\begin{align*}	
-1-u_{ij}&=\prod\limits_{j\prec k \prec i}u_k^2 u_{ki}u_{jk}\!\!\prod\limits_{j\prec k\prec l\prec i}u_{kl}^2\!\!\prod\limits_{\substack{j\prec k\prec i\\i\prec l\prec j}}u_{kl}u_{lk},\\
-1-u_{i}&=\prod\limits_{j\neq i}u_j \prod_{i\prec j\prec k\prec i}u_{jk},
-\end{align*}
-where labels are vertices of a $n$-gon and $\prec$ is the counterclockwise order on
-the $n$-gon.
-
-(binary geometries)
-
-\[
-	1-u_i=f_i(u)\prod_{j}u_j^{i||j}
-\]
-where $f_i$ are polynomials such that $f_i(\dots,u_i=0,\dots)=1$.
+
+%Another example still comes from a hyperplane arrangement, the Shi arrangement,
+%which is also $B_n$ type cluster stringy integral.
+%The Shi arrangement contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
+%on the real line with the freedom of global transformation 
+%$z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. The Shi arrangement is 
+%given by the following hyperplanes
+%\[
+%	z_i-z_j=0\quad \text{and}\quad z_i-z_j=1\quad \text{for $1\leq i<j\leq n+1$},
+%\]
+%and its stringy integral is 
+%\[
+%\mathcal I_n = \int_{1>z_1>z_2>\cdots >z_n>0}
+%\frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(1-z_1)(z_1-z_2)\cdots (z_{n}-0)}
+%\prod_{0\leq i<j \leq n}(z_i-z_j)^{s_{ij}}(1-z_i+z_j)^{t_{ij}},
+%\]
+%where the positive region is given by $0<z_i-z_j<1$ for $1\leq i<j \leq n+1$.
+%The $u$-variables of this configuration space are
+%\[
+%    u_1=1+z_1-z_2,\quad \dots,\quad u_{n}=1+z_{n}-z_{n+1},\quad u_{n+1}=z_{n+1}-z_1
+%\]
+%and 
+%\[
+%\begin{aligned}
+%    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad &&\text{for $i<j$},\\
+%    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad &&\text{for $i<j$},
+%\end{aligned}
+%\]
+%where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices live in $\mathbb Z_{2n+2}$.
+%They satisfy the following $u$-equations 
+%\begin{align*}	
+%1-u_{ij}&=\prod\limits_{j\prec k \prec i}u_k^2 u_{ki}u_{jk}\!\!\prod\limits_{j\prec k\prec l\prec i}u_{kl}^2\!\!\prod\limits_{\substack{j\prec k\prec i\\i\prec l\prec j}}u_{kl}u_{lk},\\
+%1-u_{i}&=\prod\limits_{j\neq i}u_j \prod_{i\prec j\prec k\prec i}u_{jk},
+%\end{align*}
+%where labels are vertices of a $n$-gon and $\prec$ is the counterclockwise order on
+%the $n$-gon.
+%(binary geometries)
+%
+%\[
+%	1-u_i=f_i(u)\prod_{j}u_j^{i||j}
+%\]
+%where $f_i$ are polynomials such that $f_i(\dots,u_i=0,\dots)=1$.
 
@@
 \newpage
-\section{Stringy canonical forms and $u$-equations for generalized permutahedra}
-In this section we shall argue that  a large subset of generalised permutahedra which are realised as degenerations of permutahderon ${\mathscr P_n}$ are binary geometries.
-Before we proceed we shall review some details about the generalised permutahedra which we shall use throughout the paper.
-\subsection{Generalized permutohedra} {\bf the definition, facets and combinatorial factorizations, do $P_n$ example in full details.}
-******************************************************************************************
-\subsubsection*{Permutahedron}
- For $x_1,x_2, \cdots, x_{n+1} \in \mathbb{R} $ , the permutahedron ${\mathscr P_n}(x_1,\cdots,x_{n+1})$ is a convex polytope in $\mathbb{R}^{n+1}$ defined as the convex hull of all vectors obtained from $(x_1,x_2, \cdots, x_{n+1})$ by permutations of the coordinates:
- \bea
-{\mathscr P_n}(x_1,x_2, \cdots, x_{n+1}) = {\rm ConvexHull} \{ (x_{w(1)},x_{w(2)}, \cdots, x_{w(n+1)})~ |~ w \in S_{n+1} \}, \nonumber
- \eea
- where $S_{n+1}$ is the symmetric group.
-
- The permutahedron has $(n+1)!$ vertices and is of dimension at most $n$ since it lies in the hyperplane 
- \bea
- H_c= \{(t_1,t_2, \cdots, t_{n+1}) ~|~ t_1 + t_2 + \cdots + t_{n+1}= c \} \subset \mathbb{R}^{n+1}, \nonumber
- \eea
-where $c= x_1+x_2+ \cdots +x_{n+1}$.
-
-For $n=1$ and distinct $x_1,x_2$ the permutahedron ${\mathscr P_1}(x_1,x_2)$ is a line. If  $x_1=x_2$ then it degenerates into a single point.
-
-For $n=2$ and distinct $x_1,x_2, x_3$ the permutahedron ${\mathscr P_2}(x_1,x_2, x_3)$ is a hexagon.
-If two of the $x_i$'s are equal then the permutahedron degenerates into a triangle and if $x_1= x_2 = x_3$ then its degenerates into a single point.
-
-We shall list a few results about permutahedra which shall be useful for later purposes: 
-\begin{itemize}
-\item {\bf Parameter independence:} The combinatorial structure of the permutahedron ${\mathscr P_n} (x_1, \cdots, x_{n+1}) $ does not depend on $ x_1, \cdots, x_{n+1} $ as long as all these are distinct.
-Henceforth  we will choose $ \{x_1, \cdots, x_{n+1}\} = \{0,1,\cdots,n \} := [0,n ]$.
-\\
-\item {\bf Facial Structure:} The $(n-k)$ faces of ${\mathscr P_n}$ are in an $1-1$ correspondence with the decomposition of $[0,n]$ into $k$ parts.
-More precisely, for each $(S_1,\cdots,S_k)$ with $S_i \neq \emptyset ~ \forall i$ and $[0,n] = S_1 \sqcup \cdots \sqcup S_k$ the corresponding face $\pi_{S_1,\cdots,S_k}$ has vertices which are permutations such that the entries $ \{x_i | i \in S_1 \}$ are largest $|S_1|$ numbers in $[0,n]$, $\{x_i | i \in S_2 \}$ are largest $|S_2|$ numbers in $[0,n]$ and so on.
-
-Further the face $\pi_{S_1,\cdots,S_k}$   is isomorphic to ${\mathscr P_{\left(| S_1|-1\right)} }\times {\mathscr P_{\left(| S_2|-1\right)} } \cdots \times{\mathscr P_{\left(| S_k|-1\right)} } $.
-
-It follows from above that ${\mathscr P_n}$ has $2^{n+1} -2$ facets corresponding to all the non-empty proper subsets of $[0,n]$ for which we have a decomposition $[0,n] = S \sqcup S^c$ and the facets are isomorphic to one of the following product of lower dimensional permutahedra  $ \{ {\mathscr P_{n-1}}, {\mathscr P_{n-2}} \times A_1, \cdots ,{\mathscr P_{\lfloor{n/2 \rfloor}}} \times {\mathscr P_{n-1-\lfloor n/2 \rfloor}}  \} $\footnote {More generally the number of $(n-k)$ facets of ${\mathscr P_n}$ is $ k!
-S(n,k)$ where $S(n,k)$ is the Stirling number of the second kind which counts the number $k$ partitions of  $I$ and there are $p(n+1,k)$ types where $p(n+1,k)$ is the number of $k$ partitions of $(n+1)$.}.
-
-It also follows from above that a face $\pi_{S_1,\cdots,S_k}$ is contained in another face $\pi_{T_1,\cdots,T_l}$ if and only if each $T_i$ is a union of consecutive $S_j$ or equivalently if $(S_1,\cdots,S_k)$ is a refinement of $(T_1,\cdots,T_l)$.
-\item {\bf Minkowski decomposition:}   Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_{n+1})$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$.
-For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull}(e_i~|~i\in I)$ denote the face of the $\Delta_{[0,n]}$.
-The polytope $P_n(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I > 0$ for all nonempty subsets $I \subset [n+1]$
- \bea
- P_n(\{y_I \})= \sum_{I \subset[n+1]} y_I . \Delta_I  \nonumber
- \eea
- is the permutahedron ${\mathscr P_n}$
-\end{itemize}
-We shall now talk about generalized permutahedra which are polytopes obtained by deformations of the usual permutahedron i.e., obtained by moving the vertices of the usual permutahedron so that the directions of all the edges are preserved or equivalently translating facets without allowing them to move past vertices which may cause some of the edges to degenerate into points.
-
-\subsubsection*{Generalized permutahedra}
-
-A  generalised permutahedron is obtained by parallel translation of facets of the usual permutahedron it is parametrized  by a collection $\{ z_I\}$ of $2^{n+1}-1$ coordinates, for non-empty sets of $I \subset [0,n] $
- \bea \label{genperm_defi}
- P_n^z(\{ z_I \}) = \left \{ (t_0 , t_1, \cdots , t_{n}) \in \mathbb{R}^{n+1} | \sum_{i=0}^{n} t_i = z_{[0,n]},~ \sum_{i \in I} t_i \geq z_I, {\rm for ~subsets} ~I  \right  \}
- \eea
- If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron.
-
- Unlike the permutahedron not all generalised permutahedra can be represented as a Minkowski sum of co-ordinate simplices.
-We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation which are called Nestohedra which we denote by ${\mathscr N}$.
-Throughout the paper we shall mean Nestohedra whenever we refer to generalized permutahedra unless stated otherwise.
- \begin{itemize}
- \item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
-  \bea
-{\mathscr N_n}^y(\{y_I \})= \sum y_I . \Delta_I  \nonumber
- \eea
- for some collection of subsets $I \in [0,n]$
- \end{itemize}
-  \begin{itemize}
- \item{\bf Parameter Independence:} The combinatorial structure of the generalised permutahedron ${\mathscr N_n({y_I})}$ is independent of the parameters $y_I$ and depends only on the collection of subsets $I \in [0,n]$ called the  building set $B$.
-\end{itemize}
-A collection of non-empty subsets of $[0,n]$ is called a building set $B$ if it satisfies the following:
-\begin{compactenum}[\quad (1)]
-    \item If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$.
-    \item $B$ contains all singletons $\{ i\}$ for $i \in S$.
-\end{compactenum}
-To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
-
-\subsubsection*{Nested Complex}
-A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
-\begin{compactenum}[\quad (1)]
-    \item For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
-    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
-    \item $N$ contains all maximal elements of $B$.
-\end{compactenum}
-The {\it nested complex} $\mathcal{N}(B)$ is defined as the poset of the set of all nested sets in $B$ ordered by inclusion.
-
-\begin{itemize}
-
-\item {\bf Facial structure:} Let us assume that the set $B$ associated with a generalised permutahedron ${\mathscr N_n}^{y}$ is a building set on $[0,n]$.
-Then the poset of faces ${\mathscr N_n}^{y}$ ordered by reverse inclusion is isomorphic to the nested complex $\mathcal{N}(B)$.
-
-For each decomposition $[0,n]=  \sqcup_{I \subset N } S_I $ where $S_I$ are non-empty, the face $P_N$ of ${\mathscr N_n}^{y}(y_I)$ associated with the nested set $N \in \mathcal{N}(B)$ is:
-\bea
-P_N = \sum_{{J \subset B}\atop{J \cap S_I \neq \emptyset}} y_{J} \Delta_{J \cap S_I}
-\eea
-\end{itemize}
-
-In summary the above results imply that we can look at any collection of subsets of $[0, n]$ which form a building set $B$ and associate  coordinate simplex $\Delta_I$ for each $I \in B$ and resulting Minkowski sum with positive weights $y_I$ generates a generalised permutahedron associated with the building set.
-Further, the number of facets $N$ of the generalised permutahedron just corresponds to the set of all elements in $B$ excluding the maximal set.
-
-Let, $m$ denote the number of non-singlet elements in $B$ i.e., the number of linear equations as explained in (1.1) 
-\bea
-N &=& |B|-1 \nonumber \\
- &=& (n+1+m)-1 \nonumber  \\
- &=& n+m \nonumber
-\eea
-{\bf Number of facets = Number of linear equations + dimension of  gen permutahedron}
-
-Thus, generalised permutahedra have big Polytopes which are simplices and as emphasized in the previous section we can solve for the $u$-variables and examine if they satisfy some kind of $u$-equations.
-
-Here are some interesting examples of generalised permutahedra:
-
-(1) If $B$ consists of only singlets i.e., $B=\{ \{ 0,1,\cdots,n \}, \{ 0 \},\{ 1 \},\cdots ,\{ n \} \}$ then the generalised permutahedron is a Simplex.
-In this case the relevant $x$ variables are $x_i,~ i=0,\cdots,n$ with $x_0=1$ and $\sum_{i=0}^n x_i$.
-The Newton polytope of the Minkowski sum is $\prod_{i=1}^{n} x_i (1+\sum_{j=1}^{n} x_j)$ and $u$-variables are 
-$u_i =\frac{ x_i}{1+\sum_{i=1}^n x_i} $
-which satisfy $\sum u_i =1$ as their only $u$-equation. \\
-
-(2) If $B= \{[i] | i=1,\cdots,n+1 \}$ is the complete flag of intervals, then ${\mathscr N_n}^y({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
-The Newton polytope of the Minkowski sum is $x_1\cdots x_n (1+x_1) \cdots (1+x_1+\cdots +x_n)$ and $u$-variables are 
-$u_i =\frac{ 1}{1+\sum_{j=1}^{i} x_j} $, ~~$u^{'}_i =\frac{ \sum_{j=1}^{i} x_j}{1+\sum_{j=1}^{i} x_j} $ for $j=1,\cdots,n$ \\
-which satisfy $u_i +u^{'}_{i} =1$ as their $u$-equation. \\
-
-(3) If $B$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then ${\mathscr N_n}({\bf Y})$ is the usual permutahedron $P_n$.
-\\
-
-(4)If $B=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr N_n}({\bf Y})$ is the associahedron. \\
-
-(5) If $B=\{ [1,i] \cup [j,n] | 1\leq  i \leq j \leq n\}$ is the set of cyclic intervals, then ${\mathscr N_n}({\bf Y})$ is the Cyclohedron.\\
-
-(6) Let $\Gamma$ be a graph on the vertex set $[0,n]$.
-Let us assume that $B = B(\Gamma)$ is the set of subsets $I \in [n]$ such that the induced graph $\Gamma$ is connected, then  ${\mathscr N_n}({\bf Y})$ is a graph associahedron.\\
-
-\section*{Braid arrangement}
-The braid arrangement in $\mathbb{R}^{n+1}$ consists of $\left({n}\atop{2}\right)$ hyperplanes 
-\bea
-z_i =z_j ~~{\rm for ~ all}~~0 \leq i<j \leq n
-\eea 
-\subsection{Natural stringy integrals with linear factors}
-
-{\bf introduce a natural stringy integrals for any generalized stringy canonical forms: variables $x_0=1, x_1, \cdots, x_n$ and define $x_I=\sum_{i \in I} x_i$, the factors are $x_I^{\alpha' S_I}$ (we can say monomials $S_\{i\}=X_i$ and polynomials $S_I=-c_I$.
-$N=n+m$ and big polytope is a simplex, then general formula for $u$ variables, which is equivalent to ABHY conditions; again $P_n$ in full details and others as degenerations.}
-
-*******************
-
-In the last subsection, we have seen that any $n$-dimensional generalized 
-permutahedron can be constructed by a Minkowski sum of some simplices labeled by
-subsets of $[0,n]$. For a simplex labeled by a subset $I$, 
-it is natrual to associate the linear polynomial $x_I=\sum_{i\in I}x_i$ whose Newton polytope is the corresponding simplex.
-Therefore, we can write down a natrual stringy canonical form for the generalized permutahedron with the building set
-$\mathscr P$
-\begin{equation} \label{stringyintforgenpermutohedron}
-   \mathcal I_{\mathscr P}(\{S_I\})=\int_{\mathbb R^{n}_+}
-	\frac{\prod_{i=0}^n \mathrm{d}\log x_i}
-	{\operatorname{GL}(1)_+}\prod_{I\in\mathscr P}x_I^{\alpha' S_I},
-\end{equation}
-where the global $\operatorname{GL}(1)_+$ redundance $x_i\mapsto a x_i$ require that 
-$\sum_{I\in\mathscr P}S_I = 0$.
-
-Generally, we can consider an arbitrary set of subsets of $[0,n]$ in eq.\eqref{stringyintforgenpermutohedron}. 
-However, the big polytope for such integral in general is not a simplex.
-It's highly non-trivial to figure out all such sets whose big polytopes are simplices,
-but we can easily see that every generalized permutahedron satisfies $N=n+m$
-because each facet $F_I$ is given by a nested set $\{[0,n],I\}$ for $I\neq [0,n]$.
-Therefore, for a generalized permutahedron $\mathscr P$, we can write down the matrix 
-$W^J_A$ of facets and then get $S_J=F_A(W^{-1})^A_J\geq 0$ and 
-its $u$-variables $u_A=\prod_J p_J^{(W^{-1})^A_J}$.
-
-Let's first write down equations of facets of a generalised permutahedron
-with the building set $\mathscr P$. The polytope of 
-eq.\eqref{stringyintforgenpermutohedron} is given by the Minkowski sum
-\[
-	- \sum_{I\in\mathscr P,|I|>1}S_I.\Delta_I
-\]
-in $(S_0,\dots,S_n)$-space, where $\Delta_I=\operatorname{ConvexHull}
-(\{e_i\}_{i\in I})$. Meanwhile, we know from the last subsection that the facet 
-labeled by a nested set $\{[0,n],I\}$ is given by
-\begin{align*}
-	\biggl\{(S_0,S_1,\dots,S_n)\in \mathbb R^{n+1}\,\bigg |\,
-		\sum_{i\in I}S_i = -\sum_{J\subset I,|J|>1,J\in \mathscr P}S_J,
-		\quad
-		&\sum_{i=0}^nS_i=-\sum_{J\in \mathscr P,|J|>1}S_J,\\
-		&\sum_{i\in K}S_i\geq -\sum_{J\subset I,|J|>1,J\in \mathscr P}S_J
-	\biggr\},
-\end{align*}
-where the second constrain is just $\sum_{I\in \mathscr P}S_I=0$, so the equation 
-of this facet is 
-\begin{equation}\label{GPfacet}
-	F_I:=\sum_{J\subset I,J\in\mathscr P}S_J=0.
-\end{equation}
-
-Within all generalized permutahedra, the original permutahedron is quite simple
-and important because any other generalized permutahedron can be degenerated from
-permutahedron by setting some $S_I$ to be zero.
-The building set of the $n$-dimensional permutahedron $\mathscr P_n$ is 
-the set of all non-empty subsets of $[0,n]$. 
-To get $u$-equations, we should solve $S_J$ by $F_J$ from eq.\eqref{GPfacet}, the 
-solution for permutahedron $\mathscr P_n$ is 
-\begin{equation}\label{SinF}
-	S_I=\sum_{J\neq \varnothing,J\subset I} (-1)^{|J|-|I|}F_J,
-\end{equation}
-then
-\[
-	\prod_{I\neq \varnothing,I\subset [0,n]}u_I^{F_I}=
-	\prod_{I\neq \varnothing,I\subset [0,n]}x_I^{S_I}=
-	\prod_{\varnothing\neq J\subset I\subset [0,n]}
-	x_I^{(-1)^{|J|-|I|}F_J}=
-	\prod_{J\neq \varnothing,J\subset [0,n]}
-	\prod_{I\supset J}(x_I^{(-1)^{|J|-|I|}})^{F_J}
-\]
-gives that
-\[
-	u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}.
-\]
-For example, the $u$-variables of $\mathscr P_2$ are
-\[
-	u_{0}  = \frac{x_0 x_{012}}{x_{01}x_{02}},\quad 
-	u_{1}  = \frac{x_1 x_{012}}{x_{01}x_{12}},\quad
-	u_{2}  = \frac{x_2 x_{012}}{x_{02}x_{12}},\quad
-	u_{01} = \frac{x_{01}}{x_{012}},\quad 
-	u_{02} = \frac{x_{02}}{x_{012}},\quad
-	u_{12} = \frac{x_{12}}{x_{012}}.
-\]
-They satisfy the following equations
-\begin{align*}
-	&1-u_{0}=u_{1} u_{2} u_{12}^2,
-	1-u_{1}=u_{0} u_{2} u_{02}^2,
-	1-u_{2}=u_{0} u_{1} u_{01}^2,\\
-	&1-u_{01}=u_{2} u_{02} u_{12},
-	1-u_{02}=u_{1} u_{01} u_{12},
-	1-u_{12}=u_{0} u_{01} u_{02}.
-\end{align*}
-We will discuss these $u$-equations in the next subsection.
-
-For permutahedra, we can give a ABHY construction from eq.\eqref{SinF} by setting 
-$S_I=-c_I$ for any non-singleton $I\in \mathscr P_n$, where $c_I$ are positive 
-constants, and a ABHY polytope is given by 
-\begin{equation}\label{ABHY}
-	F_I\geq 0,\quad -c_I=\sum_{J\neq \varnothing,J\subset I}(-1)^{|J|-|I|}F_J
-\end{equation}
-in $\{S_i=F_i\,:\,1\leq i\leq n\}$-space, where the last equation is a gauge fixing. 
-According to eq.\eqref{genperm_defi}, this polytope is a $n$-dimensional 
-permutahedron $\mathscr P_n$. {\bf (???)}
-The ABHY construction of any generalized permutohedra can be obtained by 
-setting $c_I=0$ for all $I$ not in the building set.
-
-For example, the building set of $\mathscr A_2$ is $\mathscr P_2-\{\{0,2\}\}$,
-its ABHY construction can be obtained from $\mathscr P_2$ by setting $c_{02}=0$, 
-\[
-	0=-c_{02}=F_{02}-F_2,
-\]
-therefore the whole ABHY conditions for $\mathscr A_2$ is 
-\[
-	-c_{01}=F_{01}-F_0-F_1,\quad -c_{12}=F_{12}-F_1-F_2,\quad 
-	-c_{012}=-F_{01}-F_{12}+F_1,\quad F_I\geq 0,
-\]
-and its solution in $(F_1,F_2)$ space is 
-\[
-	\left\{\begin{aligned}
-		F_1&\geq 0,F_2\geq 0\\
-		F_0&=c_{01}+c_{12}+c_{012}-F_1-F_2\geq 0,\\
-		F_{12}&=F_1+F_2-c_{12}\geq 0,\\
-		F_{01}&=c_{012}+c_{12}-F_2\geq 0.
-	\end{aligned}\right.
-\]
-
-\subsection{Binary geometries and $u$ equations}
-
-{\bf argue in general to have binary geometries we must have $1-u=\prod u' p(\{u\})$ with $p(u=0)=1$, conjecture that this is true of ALL gen. perm. Show it for gen. perm. more examples?}
-
-(Chi: I have checked several examples of graph associahedra, there is a conjecture for $u$ variables for this kind of generalized permutohedra: \\
-For a element $I$ in the building set $\mathcal{B}$, we define $I_{\text{max}}=\Bigl(\bigcup_{j\sim I} \{j\} \Bigr)\cup I$
-where $j\sim I$ means the singleton $j$ is attached to $I$ in the corresponding graph, then 
-\begin{equation}
-   u_{I} = \prod_{ I \subset J \subset I_{\text{max}}}x_J^{(-1)^{|I|-|J|}}. \label{uvarforgraph}
-\end{equation}
-
-\subsubsection{The binary aspects of $u$-variables for graph associahedra}
-
-Here we want to show that the $u_{I}$'s defined in \eqref{uvarforgraph} have the desired binary property, that is, $u_{I}$ and $u_{J}$ are compatible if and only if $I$ and $J$ are one of the following three cases:
-\begin{enumerate}
-   \item $I\subset J$\:,
-   \item $J\subset I$ \:,
-   \item $I\cap J=\emptyset$ and $I\cup J \notin \mathcal{B}$ \:.
-\end{enumerate}
-In other words, this means that $u_{I}$ and $u_{J}$ are incompatible if $I$ and $J$ are one of the following two cases:
-\begin{enumerate}[resume]
-   \item $I\cap J=\emptyset$ and $I\cup J \in \mathcal{B}$ \:, 
-   \item $I\cap J \neq \emptyset,I, J $ \:.
-\end{enumerate}
-
-A crucial observation here is that $u_{J}\to 0$ is equivalent to $x_{J}\to 0 $ according to \eqref{uvarforgraph} since all $x_{i}$ are non-negative.
-We can approach this limit by replacing $x_{j}$ with $ \epsilon x_{j}$ for all $j\in J$ then taking $\epsilon \to 0$.
-Then the remaining task is just to consider the behaviour of the other $u_{I}$'s under this limit.
-In the following arrangement, it is convenient to introduce
-\begin{equation}
-  p(J_{1},J_{2},\cdots,J_{n}):= \sum_{j\in J } x_{j} \:.
-\end{equation}
-where $J= \bigcup_{a=1}^{n} J_{a}$
-
-For case (1). First note that if $j\in J$ is not attached to $I$, then $x_{j}$ is independent of $u_{I}$ according to \eqref{uvarforgraph}. Thus, we can decompose $J$ into three parts, 
-\begin{equation}
-   J= I\cup J_{c}\cup \bar{J}_{c}
-\end{equation}
-where $J_{c}$ is the set of all singletons in $J$ connected with $I$, $\bar{J}_{c}$ is the set of remaining singletons.
-Furthermore, We denote $K=I_{\text{max}}-I-J_{c} $ as the set of all singletons which don't belong to $J$ but is connected with $I$.
-Then we have
-\begin{align}
-   \lim_{\epsilon \to 0}\log u_{I}&=\lim_{\epsilon \to 0}\sum_{\psi\subset J_{c},\kappa\subset K} (-1)^{\lvert \psi\rvert  +\lvert\kappa\rvert} \log p(I_{\epsilon},\psi_{\epsilon},\kappa) \nonumber \\
-   &= (-1)^{\lvert \psi\rvert }\sum_{\psi\subset J_{c}}\log p(I,\psi) + \biggl(\log\epsilon +\sum_{\kappa\neq \emptyset}(-1)^{\lvert\kappa\rvert}\log p(\kappa)\biggr)\sum_{\psi\subset J_{c}}(-1)^{\lvert \psi\rvert } \binom{\lvert\psi\rvert }{\lvert J_{c}\rvert } \nonumber \\
-   &=  (-1)^{\lvert \psi\rvert }\sum_{\psi\subset J_{c}}\log p(I,\psi) 
-     \:,
-\end{align}
-where $I_{\epsilon}$ and $\psi_{\epsilon}$ indicate that their elements are multiplied with $\epsilon$.
-
-Case (2) and (3) are trivial, we leave them to the reader.
-
-Now let us consider case (4). For this case, we can decompose J into two parts,
-\begin{equation}
-   J=J_{c}\cup \bar{J}_{c}
-\end{equation}
-where again $J_{c}$ is the set of all singletons in $J$ connected with $I$, $\bar{J}_{c}$ is the set of remaining singletons.
-As the above, we denote $K=I_{\text{max}}-I-J_{c} $ as the set of all singletons which don't belong to $J$ but is connected with $I$.
-Then
-\begin{align}
-   \lim_{\epsilon \to 0}\log u_{I}&=\lim_{\epsilon \to 0}\sum_{\psi\subset J_{c},\kappa\subset K} (-1)^{\lvert \psi\rvert  +\lvert\kappa\rvert} \log p(I,\psi_{\epsilon},\kappa) \nonumber \\ 
-   &= \sum_{\kappa\subset K}(-1)^{\lvert\kappa\rvert}\log p(I,\kappa)\Biggl(\sum_{\psi\subset J_{c}}(-1)^{\lvert \psi\rvert } \binom{\lvert\psi\rvert }{\lvert J_{c}\rvert } \Biggr)\nonumber \\
-   &=  0
-     \:.
-\end{align}
-The argument for case (5) is similar with case (4), we omit here.
-
-\paragraph{Quickly review of the facet structure of graph associahedra} Given a graph $\Gamma$ and its subgraph $\Gamma_{J}$, construct a new graph $\Gamma_{J}^{\ast}$ called the reconnected complement: If $V$ and $J$ are the sets of nodes of $\Gamma$ and $\Gamma_{J}$ respectively, then $V-J$ is the set of nodes of $\Gamma_{J}^{\ast}$.
-There is an edge between nodes $a$ and $b$ in $\Gamma_{J}^{\ast}$ if either $\{a, b\}$ or $\{a, b\}\cup J$ is connected in $\Gamma$.
-If we denote the corresponding graph associahedron for $\Gamma$ by $\mathcal{P}\Gamma$, then each subgraph $\Gamma_{J}$ corresponds a facet of $\mathcal{P}\Gamma$.
-In particular, this facet is combinatorially equivalent to $\mathcal{P}\Gamma_{J}\times \mathcal{P}\Gamma_{J}^{\ast}$\cite{}.
-
-It can easily check that, under the limit of $u_{J}\to 0$, $u_{I}$ in case (1) give the $u$-variables for $\mathcal{P}\Gamma_{J}$, while  $u_{I}$ in case (2) and (3) give the $u$-variables for $\mathcal{P}\Gamma_{J}^{\ast}$
-
-{\bf A conjecture for $u$-variables of generalized permutahdera (nextohedra)}
-
-For each element $ I\in \mathcal B$, we define $I^{(0)}=\{I\}$ and  $I^{(1)}$ as the set of all $J\supsetneq I $ such that  $I$ is the ``maximal subset'' of $J$ in $\mathcal{B}$ (that is, there is no $K\in \mathcal{B}$ such that $I\subsetneq K\subsetneq J $).
-Then, we recursively define
-\begin{equation}
-   I^{(i+1)} = \{I^{(i)}_{a}\cup I^{(i)}_{b}\vert I_{a,b}^{(i)}\in I^{(i)},\text{$I_{a}^{(i)}$ and $I_{b}^{(i)}$ are ``maximal subsets'' of $I^{(i)}_{a}\cup I^{(i)}_{b}$ }\}
-\end{equation} 
-and stop when $\lvert I^{(s)}\rvert =1$. With the defination of $I^{(i)}$, the coresponding $u$-variable is
-\begin{equation}
-   u_{I} =\prod_{i}\prod_{I_{a}^{(i)}\in I^{(i)}} p(I_{a}^{(i)})^{(-1)^{i} }
-\end{equation}
-
-% This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
-
-% Based on the above conjecture,  there is a statement for the binary geometries corresponding to the facet $u_{I}\to 0$, 
-% that is the $u$-system for the facet $u_{I}\to 0$ is corresponding to the generlaized permutohedra $\mathcal{P}_{I}\otimes \mathcal{P}_{\bar{I}}$ with building sets  
-% \[
-% \mathcal{B}_{I} = \{J\vert J\subset I, J\in \mathcal{B}\}
-% \]
-% and 
-% \[
-% \mathcal{B}_{\bar{I}} = \{J-I\vert  J\in \mathcal{B}-\mathcal{B}_{I} \}
-% \]
-% where $J-I$ means the complement of $J$ with respect to $I$. This statement directly follow from the fact that $u_{I}\to 0$ is equivalent to take $x_{i}\to t x_{i} $ for $i\in I$ then take $t \to 0$
-% )
-
-\subsection{u eqs}
-
-({\bf Zhenjie}: A possible way to find some $u$-equations of generalized permutohedra)
-
-For a generic generalized permutohedra $\mathscr P$, it's usually difficult to solve $S_I$ by $\{F_I\}$  from eq.\eqref{GPfacet} and then get $u$-variables in terms of $\{x_I\}$, but we can directly use eq.\eqref{GPfacet} to express $x_I$ by $\{u_I\}$ which gives us many algebraic equations of $u$-variables.
-In fact,
-\[
-\prod_{I\in \mathscr P}x_I^{S_I}=\prod_{J\in \mathscr P}u_J^{F_J}=\prod_{J\in\mathscr P}\prod_{I\subset J,I\in \mathscr P}u_J^{S_I}=\prod_{I\in\mathscr P}\biggl(\prod_{J\supset I,J\in\mathscr P}u_J\bigg)^{S_I},
-\]
-so
-\begin{equation}
-x_I=\prod_{J\supset I,J\in\mathscr P}u_J
-\end{equation}
-for any $I\in \mathscr P$, where we introduce a fake $u$-variable 
-$u_{[0,n]}:=x_{[0,n]}$. We know some algebraic equations of $\{x_I\}$, 
-for example, linear equations $x_I+x_J=x_{I\cup J}$ for $I\cap J=\varnothing$, 
-so (I will omit all $\text{sth}\in \mathscr P$ for convenience.)
-\begin{equation*}
-	\prod_{K\supset I}u_K+\prod_{K\supset J}u_K=\prod_{K\supset I\cup J}u_K
-\end{equation*}
-or equivalently
-\begin{equation}
-\prod_{I\subset K,K\not\supset I\cup J}u_K +
-\prod_{J\subset K,K\not\supset I\cup J}u_K = 1.
-\end{equation}
-({\bf Zhenjie}: I conjecture that all possible $u$-equations are consequences of 
-some algebraic equations of $x_I$ which is in fact we have seen in 
-the calculation of $1-u_I$. For example, the nonlinear equation (although it's
-the consequence of linear equations)
-\[
-	x_0x_{012}+x_1x_2=x_{01}x_{02}
-\]
-tells us the $u$-equation of $u_0$ of 2d permutohedron $\mathscr P_2$. Therefore,
-another related conjecture is that the variety generated by $u$-equations 
-is the one generated by eq.(\theequation) for all disjoint $I$, $J\in \mathscr P$ 
-in $u$-space. Can we prove that generalized permutohedra are binary geometries in
-this way?
-)
-
-For permutohedron $\mathscr P_n$, I conjecture that
-\[
-1-u_I=1-\prod_{J\supset I}x_J^{(-1)^{|J|-|I|}}=\frac{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J-\prod_{|J|-|I| \text{ even}; J\supset I}x_J}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J}
-=\frac{f_{I,n}\prod_{i\not\in I}x_i}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J},
-\]
-where $f_{I,n}$ is an irreducible polynomial with positive coefficients.
-It's easy to see $x_i$ for $i\not\in I$ is a factor of the numerator by setting $x_i=0$, but it's not obvious whether $f_{I,n}$ is irreducible.
-I've checked many examples, and corresponding polynomials $f_{I,n}$ are always irreducible.
-
-From
-\[
-\prod_{i\not\in I}x_i=\prod_J u_J^{|J|-|I\cap J|}
-\quad\text{and}\quad
-\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
-=
-\prod_{J\supsetneq I}u_J^{2^{|J|-|I|-1}},
-\]
-then
-\[
-\prod_{i\not\in I}x_i\bigg/\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
-=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supsetneq I} u_J^{|J|-|I|-2^{|J|-|I|-1}}.
-\]
-Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's natural to conjecture that
-\begin{equation}
-1-u_I=g(u)\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
-\end{equation}
-where $g$ is a polynomial.
-The product $\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}$ has appeared in all known examples with right powers.
-It's clear that any compatible $u_J$ for $J\subset I$ doesn't appear in the product because $I\cap J=J$.
-Thus, the final conjecture is about the compatibility degree:
-\[
-(I||J)=|J|-|I\cap J|\text{ for $I\not\subset J$},\quad  (I||J)=0 \text{ for $I\subset J$}.
-\]
-It's not symmetric when $|I|\neq |J|$.
-
-\subsubsection{Example: Binary geometries for Cayley graph, graph associahedra and generalized permutohedra. }
-
-In the above, we have shown that the binary geometries exist for permutohedra even through the $u$ equtions are not perfect and conjecture that such binary geometries exist for generalized permutohedra.
-In the remainder of this section, we will give more example on such binary geometries without perfect $u$ equations.
-
-We start with the Cayley graph proposed in \cite{} and further studied in \cite{}.
-In \cite{}, the ABHY realization for general Cayley graphs have been proposed, here we will use several examples to illustrate that the binary geometries exist for general Cayley graphs.
-The first Cayley graph which is nether associahedron nor permutahderon is so-called  ``next-to-$A_{3}$'', in terms of generalized permutahdera, the building set for next-to-$A_{3}$ is
-\begin{equation}
-   \mathscr{NA}_{3}=\{\{1,2,3,4\},\{1,2,3\},\{1,3,4\},\{2,3,4\},\{1,2\},\{1,3\},\{2,3\},\{3,4\},\{1\},\{2\},\{3\},\{4\}\}
-\end{equation}
-
-the $u$ variables are 
-\begin{align}
-   &u_{1}=\frac{x_{1}x_{123}}{x_{12}x_{13}} \:, \quad  u_{2}=\frac{x_{2}x_{123}}{x_{12}x_{23}} \:,  \quad 
-   u_{3}=\frac{x_{3}x_{134}x_{234}x_{123}}{x_{34}x_{13}x_{23}x_{1234}} \:, \quad 
-   u_{4}=\frac{x_{4}}{x_{34}} \\
-   &u_{12}=\frac{x_{12}}{x_{123}} \:, \quad u_{13}=\frac{x_{13}x_{1234}}{x_{134}x_{123}} \:,\quad 
-   u_{23}=\frac{x_{23}x_{1234}}{x_{123}x_{234}} \:, \quad u_{34}=\frac{x_{34}x_{1234}}{x_{134}x_{234}} \\
-   &u_{123}=\frac{x_{123}}{x_{1234}} \:, \quad u_{134}=\frac{x_{134}}{x_{1234}} \:, \quad 
-   u_{234}=\frac{x_{234}}{x_{1234}}
-\end{align}
-The $u$ equations are
-\begin{align}
-   &1-u_{1}=u_{2}u_{3}u_{23}^{2}u_{34}u_{234}^{2} \:, \\
-   &1-u_{2}=u_{1}u_{3}u_{13}^{2}u_{34}u_{134}^{2} \:, \\
-   &1-u_{3}= u_{1}u_{2}u_{4}u_{12}^{2}(1+u_{3}u_{13}u_{23}u_{34}u_{123}u_{134}u_{234}) \:, \\
-   &1-u_{4}=u_{3}u_{13}u_{23}u_{123}  \:, \\
-   &1-u_{12} =u_{3}u_{13}u_{23}u_{34}u_{134}u_{234} \:, \\
-   &1-u_{13} =u_{2}u_{4}u_{12}u_{23}u_{34}u_{234}^{2} \:, \\
-   &1-u_{23}= u_{1}u_{4}u_{12}u_{13}u_{34}u_{134}^{2} \:, \\
-   &1-u_{34}= u_{1}u_{2}u_{12}^{2}u_{13}u_{23}u_{123}^{2} \:, \\
-   &1-u_{123}=u_{4}u_{34}u_{134}u_{234} \:, \\
-   &1-u_{134}=u_{2}u_{12}u_{23}u_{123}u_{234} \:, \\
-   &1-u_{234}=u_{1}u_{12}u_{13}u_{123}u_{134} \:, 
-\end{align} 
-\subsection{Permutahedron as a binary geometry}
-
-\textcolor{red}{(Prashanth: An attempt to prove $P_n$ is binary using Chi's method.)}
-
-In this section we shall try to argue that the permutahedron is a binary geometry. We shall first summarise the following facts about the permutahedron:
-\begin{enumerate}
-\item The $u$-variables for the permutahedron are: 
-\bea
-u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber 
-\eea
-The above relations can also be inverted to obtain $x_I$ as follows:
-
-For $0 \notin I $
-\bea
-x_I &=& \frac{\prod_{I \subset J} u_{J}}{1-\prod_{I \subset J} u_{J}} \\
-\frac{1}{1+ x_I} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}}
-\eea
-From the above relations it is clear that taking $u_I \rightarrow 0$ for $0 \notin I$ implies $x_J \rightarrow 0$ for all $J \subset I$ and taking $u_{\bar{I}} \rightarrow 0$ implies $x_J \rightarrow \infty $ for all $I \subset J$.
-In fact we shall argue that there is unique choice of $x_I$'s which we can take to $0$ or $\infty$ which corresponds to setting only a particular $u_I \rightarrow 0$ or $u_{\bar{I}} \rightarrow 0$ respectively.
-\item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :
-
-% {\bf compatible if} $I\cap J = \emptyset$ or $I\cap J \neq \emptyset$ and either $I \subset J$ or $J \subset I$
-
-% {\bf incompatible if}   $I\cap J \neq \emptyset$ or $I\cap J = \emptyset$ and neither $I \not\subset J$ or $J \not\subset I$
-
-{\bf compatible if and only if} $\{[0,n],I,J\}$ is a nested set, i.e.
-\[
-I\subset J\quad \text{or}\quad J\subset I\quad \text{or}\quad (J\cap I=\varnothing \quad \text{and}\quad J\cup I\not\in \mathscr P_n).
-\]
-For permutohedron, $J\cup I$ is always contained in $\mathscr P_n$ for any $I$ and $J$, so it's compatible if and only if $J\subset I$ or $I\subset J$.
-
-The above  follows directly from the following relations amongst $u$ for each $I$ such that $0\notin I$ :
-\bea
-1-\prod_{I \subset J} u_{J} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}} \\
-1-\prod_{J \subset I} u_{\bar{J}} &=& \prod_{I \subset J} u_{J} \prod_{J \subset \bar{I} } u_{\bar{J}}
-\eea
-
-% Thus, each $u_I$ is compatible with itself and incompatible with $u^{'}_I$.
-
-\item  Since, the permutahedron is permutation invariant in all $x_i$'s this should be reflected at the level of $u$'s and this is indeed the case as $u_I$ with the same $|I|$ have similar $u$'s.
-i.e $u_J$ can be obtained from $u_I$ for $|J|=|I|$ by interchange of some of the $x_i$'s.
-
-We shall prove $\mathscr P_{n+1}$ is binary by showing that whenever we take some $u_I \rightarrow 0$ (by taking a unique set of $x_i \rightarrow 0, \infty$) then $u_J \rightarrow 1$ for $J$ incompatible with $I$ and the remaining $u$'s reduce to the $u$'s corresponding to $\mathscr P_{k-1} \times \mathscr P_{(n+1)-k}$.
-
-By the argument given above it is sufficient to consider $u_1, u_{12},\cdots,u_{12...n(n+1)} \rightarrow 0$ and $u_0, u_{0(n+1)},u_{0,n(n+1)}\cdots,u_{02...n(n+1)} \rightarrow 0$.
-
-We have the following cases:
-\begin{enumerate}
-    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e $I =  \{1,2,\cdots, k \}$ with $k= 1,2,\cdots, \lfloor \frac{n+1}{2} \rfloor -1$
-
-    In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots, k $ and consider the limit $t \rightarrow 0$ to get:
-    \bea
-    u^{(n+1)}_{J \cup  I} &\rightarrow& u_{J}^{((n+1)-k )} ~\text{with}~ J\subseteq\bar{I}\\
-     u^{(n+1)}_{K} &\rightarrow& u_{K}^{(k-1)} ~\text{with}~ K\subsetneq I
-    \eea
-   which is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$
-
-    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{1,2,\cdots,k \}$ with $k= \lfloor \frac{n+1}{2} \rfloor,\cdots,(n+1)$
-
-     In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots k-1$ and $x_{k} \rightarrow t$ and  consider the limit $t \rightarrow 0$ to get:
-    \bea
-    u^{(n+1)}_{J } &\rightarrow& u_{J}^{((n+1)-k)} ~\text{with}~ J\subseteq \{1,\cdots,k-1\}\\
-     u^{(n+1)}_{J \cup \{k\}} &\rightarrow& u_{K \cup\{0\}}^{((n+1)-k)} ~\text{with}~ J\subsetneq \{1,\cdots,k-1\}
-    \eea
-     \bea
-    u^{(n+1)}_{K \cup I } &\rightarrow& u_{J}^{(k-1)} ~\text{with}~ K\subseteq \{k +1,\cdots,n+1\}\\
-     u^{(n+1)}_{K \cup \{0\}\cup I} &\rightarrow& u_{K \cup\{0\}}^{(k-1)} ~\text{with}~ K\subsetneq \{k +1,\cdots,n+1\}
-    \eea
-   which is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$ 
-    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{0,(k+1),\cdots,(n+1)\}$ with $k= \lfloor \frac{n+1}{2} \rfloor+1,\cdots,(n+1)$
-
-    In this case we take $x_i \rightarrow \frac{ x_i}{t}$ for $i=1,\cdots k-1$ and $x_{k} \rightarrow \frac{1}{t}$ and  consider the limit $t \rightarrow 0$ to get:
-    \bea
-    u^{(n+1)}_{J \cup I } &\rightarrow& u_{J}^{(n+1)-k} ~\text{with}~ J\subseteq \{1,\cdots,(k-1)\}\\
-     u^{(n+1)}_{J \cup \{k\}\cup I} &\rightarrow& u_{J \cup\{0\}}^{(k-1)} ~\text{with}~ J\subsetneq \{1 ,\cdots, k\}
-    \eea
-     \bea
-    u^{(n+1)}_{K} &\rightarrow& u_{K}^{k-1} ~\text{with}~ K\subseteq I
-    \eea
-    which again is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$. 
-    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ $I = \{0,(k+1),\cdots,(n+1)\}$ with $k= 1,\cdots, \lfloor \frac{n+1}{2} \rfloor+1$.
-
-    In this case we take $x_i \rightarrow \frac{x_i}{t}$ for $i=1,\cdots, k$ and consider the limit $t \rightarrow 0$ to get:
-    \bea
-    u^{(n+1)}_{J} &\rightarrow& u_{J}^{(n+1)-k} ~\text{with}~ J\subseteq I
-    \eea
-     \bea
-    u^{(n+1)}_{K \cup I} &\rightarrow& u_{K}^{k-1} ~\text{with}~ K\subsetneq \{1,\cdots,k\}
-    \eea
-
-     which again is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$. 
-\end{enumerate}
-This proves that the permutahedron $\mathscr P_n$ is indeed a binary geometry for all $n$.
-
-The above proof did not explicitly use the $u$- equations for $\mathscr P_n$. 
-The $u$-equations for $\mathscr P_n$ are complicated polynomials and Some of them are:\\
-
-For $|I| =n-1$ and $s_K = \begin{cases}  1,~ if K \not\subset I & \\ 2, ~if K \subset I\end{cases}$
-
-\bea
-1-u_{I} &=& \prod_ {S - I \subset J } u_{J} \prod_ {K \cap I \ne \Phi } (u^{'}_{K})^{s_K}  \nonumber \\
-1-u_{12\cdots n} &=& \prod_ {{I \subset S}\atop {I \ne \Phi}} u^{'}_{I} \nonumber
-\eea
-
-For $t_J = \begin{cases}  1,~ if I  \not\subset J & \\ 2, ~if I \subset J \end{cases}$
-
-\bea
-1-u^{'}_{i} &=& \prod_ {\{ i \} \subset J } u_{J} \prod_ {K \subset S- \{i\} } u^{'}_{K} \nonumber \\
-1-u^{'}_{i j} &=& \prod_ {\{i,j \}\cap J \ne \Phi} u^{t_J}_{J} \prod_ {K \subset S-\{i, j \} } (u^{'}_{K})^{2} u^{'}_{K \cup {i}} u^{'}_{K \cup{j} } \nonumber 
-\eea
-
-and for $|I| =n-2$ with $S- I = \{i, j\}$
-
-\bea
-1-u_{I}= u_i u_j u^{2}_{ij} \prod_{J \subset I} u_{J \cup \{i\}} u_{J \cup \{j\}} u^{2}_{J \cup \{i,j\}} \prod_{K \subset S-I} (u^{'}_K)^{3} (u^{'}_{K \cup \{i\}})^{2}  (u^{'}_{K \cup\{j\}})^{2}  u^{'}_{K\cup \{i,j\}} \left( 1+ u^{'}_i u^{'}_j u^{'}_{ij} \prod_{I \subset L} u_L \right)                       \nonumber
-\eea
-
-The other $u$-equations are not two or three term equations and seem to be polynomials of order $|I|=n-2$ in the corresponding $u$'s. Thus, the most general $u$-equations can be conjectured to be:
-\bea
-1-u_{I} = \prod_{J} u^{s_J}_{J} P_{|I|}(u_I, u_J,u_K) 
-\eea
-where, $J$ are all sets incompatible with $I$
-
- $K$ are all sets compatible with $I$ excluding itself 
- $s_J$ are positive integers.
-
-\end{enumerate}
 
@@
 
-The building set of $A_n$ is
-\[\left\{
-\begin{aligned}
-	&[0,n],\\
-	&[0,n-1],[1,n],\\
-	&[0,n-2],[1,n-1],[2,n],\\
-	&\hspace{3ex}\vdots\\
-	&[0,1],[1,2],\dots,[n-1,n],\\
-	&\{0\},\{1\},\dots,\{n\}
-\end{aligned}\right.
-\]
+The building set of $A_n$ is $\{[i,j]\,:\, 0\leq i\leq j\leq n\}$.
 The facets are given by eq.\eqref{GPfacet}
@@
 
-The building set of $B_n$ is
-\[\left\{
-\begin{aligned}
-	&[0,n],\\
-	&[0,n-1],[1,n],[2,0]\dots,[n,n-2]\\
-	&[0,n-2],[1,n-1],[2,n],\dots,[n,n-3]\\
-	&\hspace{3ex}\vdots\\
-	&[0,1],[1,2],\dots,[n-1,n],[n,0],\\
-	&\{0\},\{1\},\dots,\{n\}
-\end{aligned}\right.
-\]
+The building set of $B_n$ is $\{[i,i+k]\,:\,0\leq i, k\leq n\}$.
 The facets are given by eq.\eqref{GPfacet}
@@
 
+$B_n$ type cluster stringy integral also comes from a hyperplane arrangement, the Shi arrangement.
+The Shi arrangement contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
+on the real line with the freedom of global transformation 
+$z_i\to z_i+a$ which can be used to fix $z_{n+1}=0$. The Shi arrangement is 
+given by the following hyperplanes
+\[
+	z_i-z_j=0\quad \text{and}\quad z_i-z_j=1\quad \text{for $1\leq i<j\leq n+1$},
+\]
+and its stringy integral is 
+\[
+\mathcal I_n = \int_{1>z_1>z_2>\cdots >z_n>0}
+\frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(1-z_1)(z_1-z_2)\cdots (z_{n}-0)}
+\prod_{0\leq i<j \leq n}(z_i-z_j)^{s_{ij}}(1-z_i+z_j)^{t_{ij}},
+\]
+where the positive region is given by $0<z_i-z_j<1$ for $1\leq i<j \leq n+1$.
+The $u$-variables of this configuration space are
+\[
+    u_1=1+z_1-z_2,\quad \dots,\quad u_{n}=1+z_{n}-z_{n+1},\quad u_{n+1}=z_{n+1}-z_1
+\]
+and 
+\[
+\begin{aligned}
+    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad &&\text{for $i<j$},\\
+    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad &&\text{for $i<j$},
+\end{aligned}
+\]
+where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices live in $\mathbb Z_{2n+2}$.
+%They satisfy the following $u$-equations 
+%\begin{align*}	
+%1-u_{ij}&=\prod\limits_{j\prec k \prec i}u_k^2 u_{ki}u_{jk}\!\!\prod\limits_{j\prec k\prec l\prec i}u_{kl}^2\!\!\prod\limits_{\substack{j\prec k\prec i\\i\prec l\prec j}}u_{kl}u_{lk},\\
+%1-u_{i}&=\prod\limits_{j\neq i}u_j \prod_{i\prec j\prec k\prec i}u_{jk},
+%\end{align*}
+%where labels are vertices of a $n$-gon and $\prec$ is the counterclockwise order on
+%the $n$-gon.
+
 \subsection{Degenerations of $A_n$ and $B_n$ with perfect $u$ equations}
@@
 However, we can still ask the following question: are these degenerations binary geometries?
-Of course, we should require at least that the number of facets of the degeneration of $A_n$ should be equal to the size of the corresponding deleted building set.
+Of course, we should require at least that the number of facets of the degeneration of $A_n$ should be equal to the size of the corresponding deleted building set minus one, \emph{i.e.} its big polytope is a simplex.
 Before answer this question, let's first find all degenerations of $A_n$ with this property.
@@
 
-From the viewpoint of mesh, an equation above corresponds a big diamond whose top or bottom corner and all $c$s are zero. For example,
+From the viewpoint of mesh, an equation above corresponds to a big diamond whose top or bottom corner and all $c$s are zero. For example,
 \begin{center}
@@
 \]
-Since $A,B,C\geq 0$, the above equation force $A$ and $C$ to vanish when $B=0$.
+Since $A,B,C\geq 0$, the above equation forces $A$ and $C$ to vanish when $B=0$.
 Therefore, $B$ is no longer a facet of the degeneration.
@@
 
-One can use these diamonds to build a degeneration with more vanishing facets. For example, in $A_3$
+One can use these diamonds to build a degeneration with more vanishing facets whose big polytope is a simplex. For example, in $A_3$
 \begin{center}
@@
 	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (3,0) {};
-	\node at (-2.5,-1) {$\{0\}$};
-\node at (-0.5,-1) {$\{1\}$};
-\node at (1.5,-1) {$\{2\}$};
-\node at (3.5,-1) {$\{3\}$};
-\node at (-1.6,0) {$\{0,1\}$};
-\node at (0.4,0) {$\{1,2\}$};
-\node at (2.4,0) {$\{2,3\}$};
-\node at (-0.8,1) {$\{0,1,2\}$};
-\node at (1.2,1) {$\{1,2,3\}$};
-\node at (1,2.2) {$\{0,1,2,3\}$};
+	\node at (-2.5,-1) {$13$};
+\node at (-0.5,-1) {$24$};
+\node at (1.5,-1) {$35$};
+\node at (3.5,-1) {$46$};
+\node at (-1.5,0) {$14$};
+\node at (0.5,0) {$25$};
+\node at (2.5,0) {$36$};
+\node at (-0.5,1) {$15$};
+\node at (1.5,1) {$26$};
+\node at (1,2.2) {$16$};
 \end{tikzpicture}
@@
 \[
-\{\{0,1,2,3\},\{0,1,2\},\{1,2,3\},\{0,1\},\{2,3\},\{0\},\{3\}\}.
-\]
-
-Suppose $\mathscr D$ is the set of all vanishing facets in the building set, we can read from the mesh that
+\{16,15,26,14,36,13,46\}.
+\]
+One can further check that it's a cube or $A_1^3$.
+
+We can play the game for any degenerations of $A_n$, count black points and deleted $c$s in each degeneration, and find that for $A_2$, $A_3$ and $A_4$, there're respectively $5$, $42$ and $565$ possible degenerations whose big polytopes are simplices.
+For these degenerations, we can easily find their $u$-variables if their sets of all vanishing facets are known.
+
+Suppose $\mathscr D$ is the set of all vanishing facets of a degeneration in the building set, 
+we can read from the mesh that
 \[
@@
 \]
-for any $I'\in \mathscr D$, where $M$ is a matrix with non-negative entries. Therefore,
+for any $I'\in \mathscr D$, where $M$ is a matrix with non-negative entries. 
+Therefore,
 \[
@@
 for any $I\not\in \mathscr D$.
-%From the viewpoint of mesh, the product are taken over all diamonds whose $c$s are all zero, top (respectively, bottom) corner is a deleted element $I'$, bottom (respectively, top) corner is 0 and left or right corner is $I$, because for such diamond $F_{I'}=F_I+\cdots$ or $M^I_{I'}=1$.
-For example, in the above example of $A_3$,
-\[
-F_{123}=F_{1}+F_2+F_3, \quad F_{12}=F_1+F_2, \quad F_{23}=F_2+F_3,
+
+The simplest degenerations of $A_n$ are those with one $c_{i,i+2}$ vanishing. For the one with $c_{i,i+2}=0$, we get 
+\[
+F_{i,i+3}=F_{i,i+2}+F_{i+1,i+3},
 \]
 so 
-\begin{align*}
-\tilde u_{1}&=u_1 u_{123} u_{12}=\frac{x_1x_{012}}{x_{12}x_{01}}\frac{x_{123}}{x_{0123}}\frac{x_{12}x_{0123}}{x_{123}x_{012}}=\frac{x_1}{x_{01}},\\
-\tilde u_{2}&=u_2 u_{123} u_{12}u_{23}=\frac{x_2x_{123}}{x_{23}x_{12}}\frac{x_{123}}{x_{0123}}\frac{x_{12}x_{0123}}{x_{123}x_{012}}\frac{x_{23}}{x_{123}}=\frac{x_{2}}{x_{012}},\dots
-\end{align*}
-
-(Conjecture: they are all binary. In fact, I guess that $\tilde u_I\to 0$ is still given by $x_i\to 0$ for $i\in I$, then Chi's proof can be applied here.)
+\[
+\tilde u_{i,i+2}=u_{i,i+2} u_{i,i+3},\quad 
+\tilde u_{i+1,i+3}=u_{i+1,i+3} u_{i,i+3},\quad 
+\tilde u_I=u_I \text{ for the other $I\neq (i,i+3)$}.
+\]
+They satisfy the following $u$-equation
+\[
+1-\tilde u_{i,i+2}=\prod_{j\neq i,i+2,i+3} \tilde u_{i+1,j},\quad 
+1-\tilde u_{i+1,i+3}=\prod_{j\neq i,i+2,i+3} \tilde u_{i+2,j}
+\]
+and $u$-equations for $\{u_{kl}\,:\, (k,l)\neq (i,i+3),(i,i+2),(i+1,i+3)\}$ with the change of variables above.
+Similarly, one can easily find the $u$-variables and $u$-equations for the degenerations with $c_{i,i+2}=0$ for several $i$.
+
+The next simplest degenerations of $A_n$ is setting $c_{i-1,i+1}=c_{i,i+2}=c_{i-1,i+2}=0$, we have seen an example in $A_3$ above.
+
+% For example, in the above example of $A_3$,
+% \[
+% F_{123}=F_{1}+F_2+F_3, \quad F_{12}=F_1+F_2, \quad F_{23}=F_2+F_3,
+% \]
+% so the $u$-variables are
+% \begin{align*}
+% \tilde u_{1}&=u_1 u_{123} u_{12}=\frac{x_1}{x_{01}},\quad 
+% \tilde u_{2}=u_2 u_{123} u_{12}u_{23}=\frac{x_{2}}{x_{012}},\quad 
+% \tilde u_{3}=u_3u_{123}u_{23}=\frac{x_3}{x_{0123}},\\
+% \tilde u_{0}&=u_{0}=\frac{x_{0}}{x_{01}},\quad 
+% \tilde u_{01}=u_{01}=\frac{x_{01}}{x_{012}},\quad 
+% \tilde u_{012}=u_{012}=\frac{x_{012}}{x_{0123}},
+% \end{align*}
+% and they satisfy the following $u$-equations:
+% \[
+% 	\tilde u_1+\tilde u_0=1,\quad \tilde u_2+\tilde u_{01}=1,
+% 	\quad \tilde u_{3}+\tilde u_{012}=1.
+% \]
 
@@
 We can similarly find a degeneration of $A_n,B_n,~or~ {\mathscr P_n}$ which would correspond to any product.
+
+\section{Stringy canonical forms and $u$-equations for generalized permutahedra}
+In this section we shall argue that  a large subset of generalised permutahedra which are realised as degenerations of permutahderon ${\mathscr P_n}$ are binary geometries.
+Before we proceed we shall review some details about the generalised permutahedra which we shall use throughout the paper.
+\subsection{Generalized permutohedra} {\bf the definition, facets and combinatorial factorizations, do $P_n$ example in full details.}
+******************************************************************************************
+\subsubsection*{Permutahedron}
+ For $x_1,x_2, \cdots, x_{n+1} \in \mathbb{R} $ , the permutahedron ${\mathscr P_n}(x_1,\cdots,x_{n+1})$ is a convex polytope in $\mathbb{R}^{n+1}$ defined as the convex hull of all vectors obtained from $(x_1,x_2, \cdots, x_{n+1})$ by permutations of the coordinates:
+ \bea
+{\mathscr P_n}(x_1,x_2, \cdots, x_{n+1}) = {\rm ConvexHull} \{ (x_{w(1)},x_{w(2)}, \cdots, x_{w(n+1)})~ |~ w \in S_{n+1} \}, \nonumber
+ \eea
+ where $S_{n+1}$ is the symmetric group.
+
+ The permutahedron has $(n+1)!$ vertices and is of dimension at most $n$ since it lies in the hyperplane 
+ \bea
+ H_c= \{(t_1,t_2, \cdots, t_{n+1}) ~|~ t_1 + t_2 + \cdots + t_{n+1}= c \} \subset \mathbb{R}^{n+1}, \nonumber
+ \eea
+where $c= x_1+x_2+ \cdots +x_{n+1}$.
+
+For $n=1$ and distinct $x_1,x_2$ the permutahedron ${\mathscr P_1}(x_1,x_2)$ is a line. If  $x_1=x_2$ then it degenerates into a single point.
+
+For $n=2$ and distinct $x_1,x_2, x_3$ the permutahedron ${\mathscr P_2}(x_1,x_2, x_3)$ is a hexagon.
+If two of the $x_i$'s are equal then the permutahedron degenerates into a triangle and if $x_1= x_2 = x_3$ then its degenerates into a single point.
+
+We shall list a few results about permutahedra which shall be useful for later purposes: 
+\begin{itemize}
+\item {\bf Parameter independence:} The combinatorial structure of the permutahedron ${\mathscr P_n} (x_1, \cdots, x_{n+1}) $ does not depend on $ x_1, \cdots, x_{n+1} $ as long as all these are distinct.
+Henceforth  we will choose $ \{x_1, \cdots, x_{n+1}\} = \{0,1,\cdots,n \} := [0,n ]$.
+\\
+\item {\bf Facial Structure:} The $(n-k)$ faces of ${\mathscr P_n}$ are in an $1-1$ correspondence with the decomposition of $[0,n]$ into $k$ parts.
+More precisely, for each $(S_1,\cdots,S_k)$ with $S_i \neq \emptyset ~ \forall i$ and $[0,n] = S_1 \sqcup \cdots \sqcup S_k$ the corresponding face $\pi_{S_1,\cdots,S_k}$ has vertices which are permutations such that the entries $ \{x_i | i \in S_1 \}$ are largest $|S_1|$ numbers in $[0,n]$, $\{x_i | i \in S_2 \}$ are largest $|S_2|$ numbers in $[0,n]$ and so on.
+
+Further the face $\pi_{S_1,\cdots,S_k}$   is isomorphic to ${\mathscr P_{\left(| S_1|-1\right)} }\times {\mathscr P_{\left(| S_2|-1\right)} } \cdots \times{\mathscr P_{\left(| S_k|-1\right)} } $.
+
+It follows from above that ${\mathscr P_n}$ has $2^{n+1} -2$ facets corresponding to all the non-empty proper subsets of $[0,n]$ for which we have a decomposition $[0,n] = S \sqcup S^c$ and the facets are isomorphic to one of the following product of lower dimensional permutahedra  $ \{ {\mathscr P_{n-1}}, {\mathscr P_{n-2}} \times A_1, \cdots ,{\mathscr P_{\lfloor{n/2 \rfloor}}} \times {\mathscr P_{n-1-\lfloor n/2 \rfloor}}  \} $\footnote {More generally the number of $(n-k)$ facets of ${\mathscr P_n}$ is $ k!
+S(n,k)$ where $S(n,k)$ is the Stirling number of the second kind which counts the number $k$ partitions of  $I$ and there are $p(n+1,k)$ types where $p(n+1,k)$ is the number of $k$ partitions of $(n+1)$.}.
+
+It also follows from above that a face $\pi_{S_1,\cdots,S_k}$ is contained in another face $\pi_{T_1,\cdots,T_l}$ if and only if each $T_i$ is a union of consecutive $S_j$ or equivalently if $(S_1,\cdots,S_k)$ is a refinement of $(T_1,\cdots,T_l)$.
+\item {\bf Minkowski decomposition:}   Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_{n+1})$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$.
+For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull}(e_i~|~i\in I)$ denote the face of the $\Delta_{[0,n]}$.
+The polytope $P_n(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I > 0$ for all nonempty subsets $I \subset [n+1]$
+ \bea
+ P_n(\{y_I \})= \sum_{I \subset[n+1]} y_I . \Delta_I  \nonumber
+ \eea
+ is the permutahedron ${\mathscr P_n}$
+\end{itemize}
+We shall now talk about generalized permutahedra which are polytopes obtained by deformations of the usual permutahedron i.e., obtained by moving the vertices of the usual permutahedron so that the directions of all the edges are preserved or equivalently translating facets without allowing them to move past vertices which may cause some of the edges to degenerate into points.
+
+\subsubsection*{Generalized permutahedra}
+
+A  generalised permutahedron is obtained by parallel translation of facets of the usual permutahedron it is parametrized  by a collection $\{ z_I\}$ of $2^{n+1}-1$ coordinates, for non-empty sets of $I \subset [0,n] $
+ \bea \label{genperm_defi}
+ P_n^z(\{ z_I \}) = \left \{ (t_0 , t_1, \cdots , t_{n}) \in \mathbb{R}^{n+1} | \sum_{i=0}^{n} t_i = z_{[0,n]},~ \sum_{i \in I} t_i \geq z_I, {\rm for ~subsets} ~I  \right  \}
+ \eea
+ If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron.
+
+ Unlike the permutahedron not all generalised permutahedra can be represented as a Minkowski sum of co-ordinate simplices.
+We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation which are called Nestohedra which we denote by ${\mathscr N}$.
+Throughout the paper we shall mean Nestohedra whenever we refer to generalized permutahedra unless stated otherwise.
+ \begin{itemize}
+ \item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
+  \bea
+{\mathscr N_n}^y(\{y_I \})= \sum y_I . \Delta_I  \nonumber
+ \eea
+ for some collection of subsets $I \in [0,n]$
+ \end{itemize}
+  \begin{itemize}
+ \item{\bf Parameter Independence:} The combinatorial structure of the generalised permutahedron ${\mathscr N_n({y_I})}$ is independent of the parameters $y_I$ and depends only on the collection of subsets $I \in [0,n]$ called the  building set $B$.
+\end{itemize}
+A collection of non-empty subsets of $[0,n]$ is called a building set $B$ if it satisfies the following:
+\begin{compactenum}[\quad (1)]
+    \item If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$.
+    \item $B$ contains all singletons $\{ i\}$ for $i \in S$.
+\end{compactenum}
+To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
+
+\subsubsection*{Nested Complex}
+A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
+\begin{compactenum}[\quad (1)]
+    \item For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
+    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
+    \item $N$ contains all maximal elements of $B$.
+\end{compactenum}
+The {\it nested complex} $\mathcal{N}(B)$ is defined as the poset of the set of all nested sets in $B$ ordered by inclusion.
+
+\begin{itemize}
+
+\item {\bf Facial structure:} Let us assume that the set $B$ associated with a generalised permutahedron ${\mathscr N_n}^{y}$ is a building set on $[0,n]$.
+Then the poset of faces ${\mathscr N_n}^{y}$ ordered by reverse inclusion is isomorphic to the nested complex $\mathcal{N}(B)$.
+
+For each decomposition $[0,n]=  \sqcup_{I \subset N } S_I $ where $S_I$ are non-empty, the face $P_N$ of ${\mathscr N_n}^{y}(y_I)$ associated with the nested set $N \in \mathcal{N}(B)$ is:
+\bea
+P_N = \sum_{{J \subset B}\atop{J \cap S_I \neq \emptyset}} y_{J} \Delta_{J \cap S_I}
+\eea
+\end{itemize}
+
+In summary the above results imply that we can look at any collection of subsets of $[0, n]$ which form a building set $B$ and associate  coordinate simplex $\Delta_I$ for each $I \in B$ and resulting Minkowski sum with positive weights $y_I$ generates a generalised permutahedron associated with the building set.
+Further, the number of facets $N$ of the generalised permutahedron just corresponds to the set of all elements in $B$ excluding the maximal set.
+
+Let, $m$ denote the number of non-singlet elements in $B$ i.e., the number of linear equations as explained in (1.1) 
+\bea
+N &=& |B|-1 \nonumber \\
+ &=& (n+1+m)-1 \nonumber  \\
+ &=& n+m \nonumber
+\eea
+{\bf Number of facets = Number of linear equations + dimension of  gen permutahedron}
+
+Thus, generalised permutahedra have big Polytopes which are simplices and as emphasized in the previous section we can solve for the $u$-variables and examine if they satisfy some kind of $u$-equations.
+
+Here are some interesting examples of generalised permutahedra:
+
+(1) If $B$ consists of only singlets i.e., $B=\{ \{ 0,1,\cdots,n \}, \{ 0 \},\{ 1 \},\cdots ,\{ n \} \}$ then the generalised permutahedron is a Simplex.
+In this case the relevant $x$ variables are $x_i,~ i=0,\cdots,n$ with $x_0=1$ and $\sum_{i=0}^n x_i$.
+The Newton polytope of the Minkowski sum is $\prod_{i=1}^{n} x_i (1+\sum_{j=1}^{n} x_j)$ and $u$-variables are 
+$u_i =\frac{ x_i}{1+\sum_{i=1}^n x_i} $
+which satisfy $\sum u_i =1$ as their only $u$-equation. \\
+
+(2) If $B= \{[i] | i=1,\cdots,n+1 \}$ is the complete flag of intervals, then ${\mathscr N_n}^y({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
+The Newton polytope of the Minkowski sum is $x_1\cdots x_n (1+x_1) \cdots (1+x_1+\cdots +x_n)$ and $u$-variables are 
+$u_i =\frac{ 1}{1+\sum_{j=1}^{i} x_j} $, ~~$u^{'}_i =\frac{ \sum_{j=1}^{i} x_j}{1+\sum_{j=1}^{i} x_j} $ for $j=1,\cdots,n$ \\
+which satisfy $u_i +u^{'}_{i} =1$ as their $u$-equation. \\
+
+(3) If $B$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then ${\mathscr N_n}({\bf Y})$ is the usual permutahedron $P_n$.
+\\
+
+(4)If $B=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr N_n}({\bf Y})$ is the associahedron. \\
+
+(5) If $B=\{ [1,i] \cup [j,n] | 1\leq  i \leq j \leq n\}$ is the set of cyclic intervals, then ${\mathscr N_n}({\bf Y})$ is the Cyclohedron.\\
+
+(6) Let $\Gamma$ be a graph on the vertex set $[0,n]$.
+Let us assume that $B = B(\Gamma)$ is the set of subsets $I \in [n]$ such that the induced graph $\Gamma$ is connected, then  ${\mathscr N_n}({\bf Y})$ is a graph associahedron.\\
+
+\section*{Braid arrangement}
+The braid arrangement in $\mathbb{R}^{n+1}$ consists of $\left({n}\atop{2}\right)$ hyperplanes 
+\bea
+z_i =z_j ~~{\rm for ~ all}~~0 \leq i<j \leq n
+\eea 
+\subsection{Natural stringy integrals with linear factors}
+
+{\bf introduce a natural stringy integrals for any generalized stringy canonical forms: variables $x_0=1, x_1, \cdots, x_n$ and define $x_I=\sum_{i \in I} x_i$, the factors are $x_I^{\alpha' S_I}$ (we can say monomials $S_\{i\}=X_i$ and polynomials $S_I=-c_I$.
+$N=n+m$ and big polytope is a simplex, then general formula for $u$ variables, which is equivalent to ABHY conditions; again $P_n$ in full details and others as degenerations.}
+
+*******************
+
+In the last subsection, we have seen that any $n$-dimensional generalized 
+permutahedron can be constructed by a Minkowski sum of some simplices labeled by
+subsets of $[0,n]$. For a simplex labeled by a subset $I$, 
+it is natrual to associate the linear polynomial $x_I=\sum_{i\in I}x_i$ whose Newton polytope is the corresponding simplex.
+Therefore, we can write down a natrual stringy canonical form for the generalized permutahedron with the building set
+$\mathscr P$
+\begin{equation} \label{stringyintforgenpermutohedron}
+   \mathcal I_{\mathscr P}(\{S_I\})=\int_{\mathbb R^{n}_+}
+	\frac{\prod_{i=0}^n \mathrm{d}\log x_i}
+	{\operatorname{GL}(1)_+}\prod_{I\in\mathscr P}x_I^{\alpha' S_I},
+\end{equation}
+where the global $\operatorname{GL}(1)_+$ redundance $x_i\mapsto a x_i$ require that 
+$\sum_{I\in\mathscr P}S_I = 0$.
+
+Generally, we can consider an arbitrary set of subsets of $[0,n]$ in eq.\eqref{stringyintforgenpermutohedron}. 
+However, the big polytope for such integral in general is not a simplex.
+It's highly non-trivial to figure out all such sets whose big polytopes are simplices,
+but we can easily see that every generalized permutahedron satisfies $N=n+m$
+because each facet $F_I$ is given by a nested set $\{[0,n],I\}$ for $I\neq [0,n]$.
+Therefore, for a generalized permutahedron $\mathscr P$, we can write down the matrix 
+$W^J_A$ of facets and then get $S_J=F_A(W^{-1})^A_J\geq 0$ and 
+its $u$-variables $u_A=\prod_J p_J^{(W^{-1})^A_J}$.
+
+Let's first write down equations of facets of a generalised permutahedron
+with the building set $\mathscr P$. The polytope of 
+eq.\eqref{stringyintforgenpermutohedron} is given by the Minkowski sum
+\[
+	- \sum_{I\in\mathscr P,|I|>1}S_I.\Delta_I
+\]
+in $(S_0,\dots,S_n)$-space, where $\Delta_I=\operatorname{ConvexHull}
+(\{e_i\}_{i\in I})$. Meanwhile, we know from the last subsection that the facet 
+labeled by a nested set $\{[0,n],I\}$ is given by
+\begin{align*}
+	\biggl\{(S_0,S_1,\dots,S_n)\in \mathbb R^{n+1}\,\bigg |\,
+		\sum_{i\in I}S_i = -\sum_{J\subset I,|J|>1,J\in \mathscr P}S_J,
+		\quad
+		&\sum_{i=0}^nS_i=-\sum_{J\in \mathscr P,|J|>1}S_J,\\
+		&\sum_{i\in K}S_i\geq -\sum_{J\subset I,|J|>1,J\in \mathscr P}S_J
+	\biggr\},
+\end{align*}
+where the second constrain is just $\sum_{I\in \mathscr P}S_I=0$, so the equation 
+of this facet is 
+\begin{equation}\label{GPfacet}
+	F_I:=\sum_{J\subset I,J\in\mathscr P}S_J=0.
+\end{equation}
+
+Within all generalized permutahedra, the original permutahedron is quite simple
+and important because any other generalized permutahedron can be degenerated from
+permutahedron by setting some $S_I$ to be zero.
+The building set of the $n$-dimensional permutahedron $\mathscr P_n$ is 
+the set of all non-empty subsets of $[0,n]$. 
+To get $u$-equations, we should solve $S_J$ by $F_J$ from eq.\eqref{GPfacet}, the 
+solution for permutahedron $\mathscr P_n$ is 
+\begin{equation}\label{SinF}
+	S_I=\sum_{J\neq \varnothing,J\subset I} (-1)^{|J|-|I|}F_J,
+\end{equation}
+then
+\[
+	\prod_{I\neq \varnothing,I\subset [0,n]}u_I^{F_I}=
+	\prod_{I\neq \varnothing,I\subset [0,n]}x_I^{S_I}=
+	\prod_{\varnothing\neq J\subset I\subset [0,n]}
+	x_I^{(-1)^{|J|-|I|}F_J}=
+	\prod_{J\neq \varnothing,J\subset [0,n]}
+	\prod_{I\supset J}(x_I^{(-1)^{|J|-|I|}})^{F_J}
+\]
+gives that
+\[
+	u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}.
+\]
+For example, the $u$-variables of $\mathscr P_2$ are
+\[
+	u_{0}  = \frac{x_0 x_{012}}{x_{01}x_{02}},\quad 
+	u_{1}  = \frac{x_1 x_{012}}{x_{01}x_{12}},\quad
+	u_{2}  = \frac{x_2 x_{012}}{x_{02}x_{12}},\quad
+	u_{01} = \frac{x_{01}}{x_{012}},\quad 
+	u_{02} = \frac{x_{02}}{x_{012}},\quad
+	u_{12} = \frac{x_{12}}{x_{012}}.
+\]
+They satisfy the following equations
+\begin{align*}
+	&1-u_{0}=u_{1} u_{2} u_{12}^2,
+	1-u_{1}=u_{0} u_{2} u_{02}^2,
+	1-u_{2}=u_{0} u_{1} u_{01}^2,\\
+	&1-u_{01}=u_{2} u_{02} u_{12},
+	1-u_{02}=u_{1} u_{01} u_{12},
+	1-u_{12}=u_{0} u_{01} u_{02}.
+\end{align*}
+We will discuss these $u$-equations in the next subsection.
+
+For permutahedra, we can give a ABHY construction from eq.\eqref{SinF} by setting 
+$S_I=-c_I$ for any non-singleton $I\in \mathscr P_n$, where $c_I$ are positive 
+constants, and a ABHY polytope is given by 
+\begin{equation}\label{ABHY}
+	F_I\geq 0,\quad -c_I=\sum_{J\neq \varnothing,J\subset I}(-1)^{|J|-|I|}F_J
+\end{equation}
+in $\{S_i=F_i\,:\,1\leq i\leq n\}$-space, where the last equation is a gauge fixing. 
+According to eq.\eqref{genperm_defi}, this polytope is a $n$-dimensional 
+permutahedron $\mathscr P_n$. {\bf (???)}
+The ABHY construction of any generalized permutohedra can be obtained by 
+setting $c_I=0$ for all $I$ not in the building set.
+
+For example, the building set of $\mathscr A_2$ is $\mathscr P_2-\{\{0,2\}\}$,
+its ABHY construction can be obtained from $\mathscr P_2$ by setting $c_{02}=0$, 
+\[
+	0=-c_{02}=F_{02}-F_2,
+\]
+therefore the whole ABHY conditions for $\mathscr A_2$ is 
+\[
+	-c_{01}=F_{01}-F_0-F_1,\quad -c_{12}=F_{12}-F_1-F_2,\quad 
+	-c_{012}=-F_{01}-F_{12}+F_1,\quad F_I\geq 0,
+\]
+and its solution in $(F_1,F_2)$ space is 
+\[
+	\left\{\begin{aligned}
+		F_1&\geq 0,F_2\geq 0\\
+		F_0&=c_{01}+c_{12}+c_{012}-F_1-F_2\geq 0,\\
+		F_{12}&=F_1+F_2-c_{12}\geq 0,\\
+		F_{01}&=c_{012}+c_{12}-F_2\geq 0.
+	\end{aligned}\right.
+\]
+
+\subsection{Binary geometries and $u$ equations}
+
+% {\bf argue in general to have binary geometries we must have $1-u=\prod u' p(\{u\})$ with $p(u=0)=1$, conjecture that this is true of ALL gen. perm. Show it for gen. perm. more examples?}
+
+\subsubsection{The binary aspects of $u$-variables for permutohedra}
+
+Here we will show that the $u_{I}$'s for the permutahderon $\mathscr{P}_{n}$, which is defined as 
+\begin{equation}
+   u_{I}:= \prod_{J\supset I}x_J^{(-1)^{|I|-|J|}} \:, \label{uforpn}
+\end{equation}
+have the desired binary property, that is, $u_{I}$ and $u_{J}$ are compatible if and only if $I \subset J$ or $J\subset I$, otherwise, they are incompatible.
+Forthermore, we will show that the $u$-variables compatible with $u_{I}$ will become the $u$-variables for the facet $\mathscr{P}_{\lvert I \rvert-1}\times \mathscr{P}_{n-\lvert I\rvert}$ as $u_{I}$ gose to 0.
+% In other words, this means that $u_{I}$ and $u_{J}$ are incompatible if $I$ and $J$ are one of the following two cases:
+% \begin{enumerate}[resume]
+%    \item $I\cap J=\emptyset$ and $I\cup J \in \mathcal{B}$ \:, 
+%    \item $I\cap J \neq \emptyset,I, J $ \:.
+% \end{enumerate}
+
+A crucial observation here is that $u_{I}\to 0$ is equivalent to $x_{I}\to 0 $ according to \eqref{uforpn} since all $x_{i}$ are positive.
+We can approach this limit by replacing $x_{i}$ with $ \epsilon x_{i}$ for all $i\in I$ then taking $\epsilon \to 0$.
+Then the remaining task is just to consider the behaviour of the other $u_{J}$'s under this limit.
+% In the following arrangement, it is convenient to introduce 
+% \begin{equation}
+%   p(J_{1},J_{2},\cdots,J_{n}):= \sum_{j\in J } x_{j} \:.
+% \end{equation}
+% where $J= \bigcup_{a=1}^{n} J_{a}$
+
+Let us first show that the $u$-variables incompatible with $u_{I}$ become 1 as $u_{I}$ goes to 0.
+It is obvious that $u_{I}$ and $u_{J}$ are incompatible if either (1) $I\cap J=  \varnothing$  or (2) $I\cap J \neq \varnothing,I, J $.
+For the first case, let us denote $K=[0,n]-(I\cup J)$ as the complement set of $[0,n]$ with respect to $I\cup J$.
+Then we find the logarithm of $u_{J}$ can be written as
+\begin{equation}
+     \log u_{J} = \sum_{\kappa\subset K,\psi\subset I} (-1)^{\lvert\kappa\rvert+\lvert \psi\rvert }\log (x_{J}+x_{ \kappa} +x_{ \psi} )\:. \label{1incompuvarforPn}
+\end{equation}
+As $x_{i}\to 0$ with $i\in I$, we have 
+\begin{equation}
+   \log u_{J} \to \sum_{\kappa\subset K} (-1)^{\lvert \kappa\rvert } \log (x_{J}+x_{ \kappa})\Biggl(\sum_{\psi\subset I}(-1)^{\lvert\psi\rvert}\binom{\lvert \psi \rvert }{\lvert I \rvert }\Biggr)=0 \label{incompn1}
+\end{equation}
+where the binomial expansion of $(1-1)^{\lvert I \rvert}$ has been used. For the second case, the logarithm of $u_{J}$ can be written as 
+\begin{equation}
+   \log u_{J} = \sum_{\psi'\subset I',\kappa\subset K}(-1)^{\lvert \psi' \rvert+ \lvert \kappa\rvert}  \log (x_{J'}+ x_{(I\cap J)}+x_{ \psi'}+x_{\kappa })
+\end{equation}
+where $I'=I-J$, $J'=J-I$ and $K=[0,n]-(I\cup J)$. Then a similar argument as in \eqref{incompn1} gives $\log u_{J}\to 0$ under the limits of all $x_{i}\to 0$ with $i\in I$.
+
+Now let us consider the behaviour of compatible $u$-variables under this limit. For $J\subset I$, we again introduce $I'=I-J$ and $K=[0,n]-I$, then the logarithm of $u_{J}$ can be written as 
+\begin{equation}
+     \log u_{J}=\sum_{\psi'\subset I', \kappa \subset K} (-1)^{\lvert \psi'\rvert +\lvert \kappa \rvert} \log (x_{J}+x_{\psi'}+x_{\kappa})
+\end{equation}
+Next, we replac $x_{i}$ with $ \epsilon x_{i}$ for all $i\in I$ and take $\epsilon \to 0$, then 
+\begin{align}
+   \log u_{J} &\to \lim_{\epsilon \to 0} \sum_{\psi'\subset I', \kappa \subset K} (-1)^{\lvert \psi'\rvert +\lvert \kappa \rvert} \log (\epsilon x_{J}+ \epsilon x_{\psi'}+x_{\kappa}) \nonumber  \\
+    &=\lim_{\epsilon\to 0} \biggl(\log \epsilon+\sum_{\kappa\subset K,\kappa \neq \varnothing}\log x_{\kappa}\biggr)\Biggr( \sum_{\psi'\subset I'}(-1)^{\lvert\psi'\rvert}\binom{\lvert \psi' \rvert }{\lvert I \rvert }\Biggr)
+    +\sum_{\psi'\subset I'} (-1)^{\lvert \psi'\rvert }\log (x_{J}+x_{\psi'}) \nonumber \\
+    &=\sum_{\psi'\subset I'} (-1)^{\lvert \psi'\rvert }\log (x_{J}+x_{\psi'}) \label{subP1}
+\end{align}
+Obviously, the expression in the last line of \eqref{subP1} is exactly the $u$-variable for the permutahderon $\mathscr{P}_{\lvert I\rvert -1}$.
+For $J\supset I$, under the limit of $x_I\to 0$, the logarithm of $u_{J}$ simply becomes
+\begin{equation}
+   \log u_{J} = \sum_{\kappa \subset K} (-1)^{\kappa} \log (x_{I}+x_{J-I}+x_{\kappa}) 
+   \to  \sum_{\kappa \subset K} (-1)^{\kappa} \log (x_{J-I}+x_{\kappa}) 
+\end{equation}
+where $K=[0,n]-J$, which is exactly the $u$-variable for the permutahderon $\mathscr{P}_{n-\lvert I\rvert}$
+
+\subsubsection{The binary aspects of $u$-variables for generalized permutohedra}
+
+Inspired by the $u$-variables for permutahdera, we come up with the $u$-variables for generalized permutohedra.
+To this end, let us define the generating set $\mathbf{I}$ for $I\in\mathbf{B}$ as the set of the minimum extensions of $I$ on $\mathbf{B}$, that is there is no $J\in\mathbf{B}$ such that $I\subsetneq J\subsetneq I_{a}$ for any $I_{a}\in \mathbf{I}$.
+Then, the $u$-variables for the generalized permutohedron with building set $\mathbf{B}$ are
+\begin{equation}
+   \log u_{I} :=  \log x_{I}- \sum_{I_{a}\in \mathbf{I}} \log x_{I_{a}}+\cdots +(-1)^{k}\sum _{I_{a_{1}},\cdots,I_{a_{k}}\in \mathbf{I}} \log x_{I_{a_{1}}\cup\cdots \cup I_{a_{k}}} +\cdots \:.
+\label{uvarforgenpermu}
+\end{equation}
+It is easy to check that the $u$-variables for associahedra, cyclohedra and permutohedra defined above can be viewed as the special cases of \eqref{uvarforgenpermu}.
+Let us give another slight nontrivial example to illustrate this defination.
+
+\paragraph{Example:} For the generalized permutahderon with building set 
+\[
+\mathbf{B}=\{\{0\},\{1\},\{2\},\{3\},\{0,1,2\},\{1,3\},\{0,1,2,3\}\},
+\]
+the corresponding $u$-variables are
+\begin{gather*}
+   u_{0}=\frac{x_{0}}{x_{012}} \:,\quad  u_{1}=\frac{x_{1}x_{0123}}{x_{012}x_{13}} \:,\quad 
+   u_{2}=\frac{x_{2}}{x_{012}} \:, \quad u_{3}=\frac{x_{3}}{x_{13}} \\
+   u_{012}=\frac{x_{012}}{x_{0123}}\:,\qquad u_{13}=\frac{x_{13}}{x_{0123}} \:, \quad 
+\end{gather*}
+
+For generalized permutahdera, $u_{I}$ and $u_{J}$ are incompatible if $I$ and $J$ are one of the following two cases:
+\begin{enumerate}
+   \item $I\cap J=\varnothing$ and $I\cup J \in \mathbf{B}$ \:, 
+   \item $I\cap J \neq \varnothing,I, J $ \:,
+\end{enumerate}
+while $u_{I}$ and $u_{J}$ are compatible if $I$ and $J$ are one of the following three cases:
+\begin{enumerate}[resume]
+   \item $J\subset I$\:,
+   \item $I\subset J$ \:,
+   \item $I\cap J=\varnothing$ and $I\cup J \notin \mathbf{B}$ \:.
+\end{enumerate}
+We will follow the argument in the cases of permutahdera: replacing $x_{i}$ with $ \epsilon x_{i}$ for all $i\in I$ and taking $\epsilon \to 0$, then considering the behaviour of the other $u_{J}$'s under this limit case by case.
+For future convenience, we assume that the generating set $\mathbf{J}$ for $J$ has $s$ elements denoted by $J_{a}$ with $a\in[1,s]$, and introduce
+\begin{equation}
+   p(J_{1},\ldots,J_{r}) = \sum_{a\in J_{1}\cup\cdots\cup J_{r}}x_{a}
+\end{equation}
+
+For case (1), some elements in $\mathbf{J}$ are subsets of $I\cup J$ since $I\cup J \in \mathbf{B}$ (an extreme case is that  $I\cup J$ is one element in $\mathbf{J}$, but the argument is the same).
+Without loss of generality, we denote such elements by $J_{1},\ldots J_{s'}$.
+Then the logarithm of $u_{J}$ can be written as
+\begin{equation}
+   \log u_{J}= \sum_{\substack {1 \leq a_{1}<\cdots<a_{k}\leq s'\\ s'<b_{1}<\cdots b_{l}\leq s}}(-1)^{k+l}\log\Bigl( x_{J}+ p(J_{a_{1}}-J,\ldots,J_{a_{k}}-J) + p(J_{b_{1}}-J,\ldots, J_{b_{l}}-J)\Bigr) \:.
+\label{logu1}
+\end{equation}
+Since the second term in eq.\eqref{logu1} goes to 0 under the limits of $x_{i}\to 0$ with $i\in I$, $\log u_{J}$ goes to 0 under this limit as in eq.\eqref{1incompuvarforPn}.
+The whole argument can be carried over to case (2) by replacing $x_{J}$ with $x_{I\cap J}+ x_{J-I}$.
+
+For case (3), we again denote $J_{1},\ldots J_{s'}$ as the elements in $\mathbf{J}$ which are subsets of $ I$.
+After replacing $x_{i}$ with $\epsilon x_{i}$ for $i\in I$, we find the limit of $\log u_{J}$ as $\epsilon \to 0$ is
+\begin{align}
+  &\quad \lim_{\epsilon\to 0}  \sum_{\substack {1 \leq a_{1}<\cdots<a_{k}\leq s'\\ s'<b_{1}<\cdots b_{l}\leq s}}(-1)^{k+l}\log\Bigl( \epsilon x_{J}+\epsilon p(J_{a_{1}}-J,\ldots,J_{a_{k}}-J) + p(J_{b_{1}}-J,\ldots, J_{b_{l}}-J)\Bigr) \nonumber \\
+  &=\sum_{\substack {1 \leq a_{1}<\cdots<a_{k}\leq s'}}(-1)^{k}\log\Bigl( x_{J}+ p(J_{a_{1}}-J,\ldots,J_{a_{k}}-J) \Bigr). 
+\end{align}
+Remarkably, they are $u$-variables for the generalized permutohedron with the building set
+\begin{equation}
+   \mathbf{B}_{I} = \{J\in\mathbf{B} \vert J\subset I\}.
+\end{equation}
+
+Case (4) and (5) are quite trivial.
+For case (4), the limit behaviour of $u_{J}$ as $x_{I}\to 0$ can be simply obtained by replacing each $x_{K}$ in eq.\eqref{uvarforgenpermu} with $x_{K-I}$.
+For case (5), $u_{J}$ is  independent of $x_{i}$ with $i\in I$.
+Remarkably, they are $u$-variables for the generalized permutohedron with the building set
+\begin{equation}
+   \mathbf{B}_{\bar{I}} = \{J-I \vert J\subset I\}.
+\end{equation}
+
+% This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
+
+% Based on the above conjecture,  there is a statement for the binary geometries corresponding to the facet $u_{I}\to 0$, 
+% that is the $u$-system for the facet $u_{I}\to 0$ is corresponding to the generlaized permutohedra $\mathcal{P}_{I}\otimes \mathcal{P}_{\bar{I}}$ with building sets  
+% \[
+% \mathcal{B}_{I} = \{J\vert J\subset I, J\in \mathcal{B}\}
+% \]
+% and 
+% \[
+% \mathcal{B}_{\bar{I}} = \{J-I\vert  J\in \mathcal{B}-\mathcal{B}_{I} \}
+% \]
+% where $J-I$ means the complement of $J$ with respect to $I$. This statement directly follow from the fact that $u_{I}\to 0$ is equivalent to take $x_{i}\to t x_{i} $ for $i\in I$ then take $t \to 0$
+% )
+
+\subsection{u eqs}
+
+({\bf Zhenjie}: A possible way to find some $u$-equations of generalized permutohedra)
+
+For a generic generalized permutohedra $\mathscr P$, it's usually difficult to solve $S_I$ by $\{F_I\}$  from eq.\eqref{GPfacet} and then get $u$-variables in terms of $\{x_I\}$, but we can directly use eq.\eqref{GPfacet} to express $x_I$ by $\{u_I\}$ which gives us many algebraic equations of $u$-variables.
+In fact,
+\[
+\prod_{I\in \mathscr P}x_I^{S_I}=\prod_{J\in \mathscr P}u_J^{F_J}=\prod_{J\in\mathscr P}\prod_{I\subset J,I\in \mathscr P}u_J^{S_I}=\prod_{I\in\mathscr P}\biggl(\prod_{J\supset I,J\in\mathscr P}u_J\bigg)^{S_I},
+\]
+so
+\begin{equation}
+x_I=\prod_{J\supset I,J\in\mathscr P}u_J
+\end{equation}
+for any $I\in \mathscr P$, where we introduce a fake $u$-variable 
+$u_{[0,n]}:=x_{[0,n]}$. We know some algebraic equations of $\{x_I\}$, 
+for example, linear equations $x_I+x_J=x_{I\cup J}$ for $I\cap J=\varnothing$, 
+so (I will omit all $\text{sth}\in \mathscr P$ for convenience.)
+\begin{equation*}
+	\prod_{K\supset I}u_K+\prod_{K\supset J}u_K=\prod_{K\supset I\cup J}u_K
+\end{equation*}
+or equivalently
+\begin{equation}
+\prod_{I\subset K,K\not\supset I\cup J}u_K +
+\prod_{J\subset K,K\not\supset I\cup J}u_K = 1.
+\end{equation}
+({\bf Zhenjie}: I conjecture that all possible $u$-equations are consequences of 
+some algebraic equations of $x_I$ which is in fact we have seen in 
+the calculation of $1-u_I$. For example, the nonlinear equation (although it's
+the consequence of linear equations)
+\[
+	x_0x_{012}+x_1x_2=x_{01}x_{02}
+\]
+tells us the $u$-equation of $u_0$ of 2d permutohedron $\mathscr P_2$. Therefore,
+another related conjecture is that the variety generated by $u$-equations 
+is the one generated by eq.(\theequation) for all disjoint $I$, $J\in \mathscr P$ 
+in $u$-space. Can we prove that generalized permutohedra are binary geometries in
+this way?
+)
+
+For permutohedron $\mathscr P_n$, I conjecture that
+\[
+1-u_I=1-\prod_{J\supset I}x_J^{(-1)^{|J|-|I|}}=\frac{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J-\prod_{|J|-|I| \text{ even}; J\supset I}x_J}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J}
+=\frac{f_{I,n}\prod_{i\not\in I}x_i}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J},
+\]
+where $f_{I,n}$ is an irreducible polynomial with positive coefficients.
+It's easy to see $x_i$ for $i\not\in I$ is a factor of the numerator by setting $x_i=0$, but it's not obvious whether $f_{I,n}$ is irreducible.
+I've checked many examples, and corresponding polynomials $f_{I,n}$ are always irreducible.
+
+From
+\[
+\prod_{i\not\in I}x_i=\prod_J u_J^{|J|-|I\cap J|}
+\quad\text{and}\quad
+\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
+=
+\prod_{J\supsetneq I}u_J^{2^{|J|-|I|-1}},
+\]
+then
+\[
+\prod_{i\not\in I}x_i\bigg/\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
+=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supsetneq I} u_J^{|J|-|I|-2^{|J|-|I|-1}}.
+\]
+Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's natural to conjecture that
+\begin{equation}
+1-u_I=g(u)\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
+\end{equation}
+where $g$ is a polynomial.
+The product $\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}$ has appeared in all known examples with right powers.
+It's clear that any compatible $u_J$ for $J\subset I$ doesn't appear in the product because $I\cap J=J$.
+Thus, the final conjecture is about the compatibility degree:
+\[
+(I||J)=|J|-|I\cap J|\text{ for $I\not\subset J$},\quad  (I||J)=0 \text{ for $I\subset J$}.
+\]
+It's not symmetric when $|I|\neq |J|$.
+
+\subsection{Permutahedron as a binary geometry}
+
+\textcolor{red}{(Prashanth: An attempt to prove $P_n$ is binary using Chi's method.)}
+
+In this section we shall try to argue that the permutahedron is a binary geometry. We shall first summarise the following facts about the permutahedron:
+\begin{enumerate}
+\item The $u$-variables for the permutahedron are: 
+\bea
+u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber 
+\eea
+The above relations can also be inverted to obtain $x_I$ as follows:
+
+For $0 \notin I $
+\bea
+x_I &=& \frac{\prod_{I \subset J} u_{J}}{1-\prod_{I \subset J} u_{J}} \\
+\frac{1}{1+ x_I} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}}
+\eea
+From the above relations it is clear that taking $u_I \rightarrow 0$ for $0 \notin I$ implies $x_J \rightarrow 0$ for all $J \subset I$ and taking $u_{\bar{I}} \rightarrow 0$ implies $x_J \rightarrow \infty $ for all $I \subset J$.
+In fact we shall argue that there is unique choice of $x_I$'s which we can take to $0$ or $\infty$ which corresponds to setting only a particular $u_I \rightarrow 0$ or $u_{\bar{I}} \rightarrow 0$ respectively.
+\item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :
+
+% {\bf compatible if} $I\cap J = \emptyset$ or $I\cap J \neq \emptyset$ and either $I \subset J$ or $J \subset I$
+
+% {\bf incompatible if}   $I\cap J \neq \emptyset$ or $I\cap J = \emptyset$ and neither $I \not\subset J$ or $J \not\subset I$
+
+{\bf compatible if and only if} $\{[0,n],I,J\}$ is a nested set, i.e.
+\[
+I\subset J\quad \text{or}\quad J\subset I\quad \text{or}\quad (J\cap I=\varnothing \quad \text{and}\quad J\cup I\not\in \mathscr P_n).
+\]
+For permutohedron, $J\cup I$ is always contained in $\mathscr P_n$ for any $I$ and $J$, so it's compatible if and only if $J\subset I$ or $I\subset J$.
+
+The above  follows directly from the following relations amongst $u$ for each $I$ such that $0\notin I$ :
+\bea
+1-\prod_{I \subset J} u_{J} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}} \\
+1-\prod_{J \subset I} u_{\bar{J}} &=& \prod_{I \subset J} u_{J} \prod_{J \subset \bar{I} } u_{\bar{J}}
+\eea
+
+% Thus, each $u_I$ is compatible with itself and incompatible with $u^{'}_I$.
+
+\item  Since, the permutahedron is permutation invariant in all $x_i$'s this should be reflected at the level of $u$'s and this is indeed the case as $u_I$ with the same $|I|$ have similar $u$'s.
+i.e $u_J$ can be obtained from $u_I$ for $|J|=|I|$ by interchange of some of the $x_i$'s.
+
+We shall prove $\mathscr P_{n+1}$ is binary by showing that whenever we take some $u_I \rightarrow 0$ (by taking a unique set of $x_i \rightarrow 0, \infty$) then $u_J \rightarrow 1$ for $J$ incompatible with $I$ and the remaining $u$'s reduce to the $u$'s corresponding to $\mathscr P_{k-1} \times \mathscr P_{(n+1)-k}$.
+
+By the argument given above it is sufficient to consider $u_1, u_{12},\cdots,u_{12...n(n+1)} \rightarrow 0$ and $u_0, u_{0(n+1)},u_{0,n(n+1)}\cdots,u_{02...n(n+1)} \rightarrow 0$.
+
+We have the following cases:
+\begin{enumerate}
+    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e $I =  \{1,2,\cdots, k \}$ with $k= 1,2,\cdots, \lfloor \frac{n+1}{2} \rfloor -1$
+
+    In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots, k $ and consider the limit $t \rightarrow 0$ to get:
+    \bea
+    u^{(n+1)}_{J \cup  I} &\rightarrow& u_{J}^{((n+1)-k )} ~\text{with}~ J\subseteq\bar{I}\\
+     u^{(n+1)}_{K} &\rightarrow& u_{K}^{(k-1)} ~\text{with}~ K\subsetneq I
+    \eea
+   which is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$
+
+    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{1,2,\cdots,k \}$ with $k= \lfloor \frac{n+1}{2} \rfloor,\cdots,(n+1)$
+
+     In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots k-1$ and $x_{k} \rightarrow t$ and  consider the limit $t \rightarrow 0$ to get:
+    \bea
+    u^{(n+1)}_{J } &\rightarrow& u_{J}^{((n+1)-k)} ~\text{with}~ J\subseteq \{1,\cdots,k-1\}\\
+     u^{(n+1)}_{J \cup \{k\}} &\rightarrow& u_{K \cup\{0\}}^{((n+1)-k)} ~\text{with}~ J\subsetneq \{1,\cdots,k-1\}
+    \eea
+     \bea
+    u^{(n+1)}_{K \cup I } &\rightarrow& u_{J}^{(k-1)} ~\text{with}~ K\subseteq \{k +1,\cdots,n+1\}\\
+     u^{(n+1)}_{K \cup \{0\}\cup I} &\rightarrow& u_{K \cup\{0\}}^{(k-1)} ~\text{with}~ K\subsetneq \{k +1,\cdots,n+1\}
+    \eea
+   which is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$ 
+    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{0,(k+1),\cdots,(n+1)\}$ with $k= \lfloor \frac{n+1}{2} \rfloor+1,\cdots,(n+1)$
+
+    In this case we take $x_i \rightarrow \frac{ x_i}{t}$ for $i=1,\cdots k-1$ and $x_{k} \rightarrow \frac{1}{t}$ and  consider the limit $t \rightarrow 0$ to get:
+    \bea
+    u^{(n+1)}_{J \cup I } &\rightarrow& u_{J}^{(n+1)-k} ~\text{with}~ J\subseteq \{1,\cdots,(k-1)\}\\
+     u^{(n+1)}_{J \cup \{k\}\cup I} &\rightarrow& u_{J \cup\{0\}}^{(k-1)} ~\text{with}~ J\subsetneq \{1 ,\cdots, k\}
+    \eea
+     \bea
+    u^{(n+1)}_{K} &\rightarrow& u_{K}^{k-1} ~\text{with}~ K\subseteq I
+    \eea
+    which again is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$. 
+    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ $I = \{0,(k+1),\cdots,(n+1)\}$ with $k= 1,\cdots, \lfloor \frac{n+1}{2} \rfloor+1$.
+
+    In this case we take $x_i \rightarrow \frac{x_i}{t}$ for $i=1,\cdots, k$ and consider the limit $t \rightarrow 0$ to get:
+    \bea
+    u^{(n+1)}_{J} &\rightarrow& u_{J}^{(n+1)-k} ~\text{with}~ J\subseteq I
+    \eea
+     \bea
+    u^{(n+1)}_{K \cup I} &\rightarrow& u_{K}^{k-1} ~\text{with}~ K\subsetneq \{1,\cdots,k\}
+    \eea
+
+     which again is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$. 
+\end{enumerate}
+This proves that the permutahedron $\mathscr P_n$ is indeed a binary geometry for all $n$.
+
+The above proof did not explicitly use the $u$- equations for $\mathscr P_n$. 
+The $u$-equations for $\mathscr P_n$ are complicated polynomials and Some of them are:\\
+
+For $|I| =n-1$ and $s_K = \begin{cases}  1,~ if K \not\subset I & \\ 2, ~if K \subset I\end{cases}$
+
+\bea
+1-u_{I} &=& \prod_ {S - I \subset J } u_{J} \prod_ {K \cap I \ne \Phi } (u^{'}_{K})^{s_K}  \nonumber \\
+1-u_{12\cdots n} &=& \prod_ {{I \subset S}\atop {I \ne \Phi}} u^{'}_{I} \nonumber
+\eea
+
+For $t_J = \begin{cases}  1,~ if I  \not\subset J & \\ 2, ~if I \subset J \end{cases}$
+
+\bea
+1-u^{'}_{i} &=& \prod_ {\{ i \} \subset J } u_{J} \prod_ {K \subset S- \{i\} } u^{'}_{K} \nonumber \\
+1-u^{'}_{i j} &=& \prod_ {\{i,j \}\cap J \ne \Phi} u^{t_J}_{J} \prod_ {K \subset S-\{i, j \} } (u^{'}_{K})^{2} u^{'}_{K \cup {i}} u^{'}_{K \cup{j} } \nonumber 
+\eea
+
+and for $|I| =n-2$ with $S- I = \{i, j\}$
+
+\bea
+1-u_{I}= u_i u_j u^{2}_{ij} \prod_{J \subset I} u_{J \cup \{i\}} u_{J \cup \{j\}} u^{2}_{J \cup \{i,j\}} \prod_{K \subset S-I} (u^{'}_K)^{3} (u^{'}_{K \cup \{i\}})^{2}  (u^{'}_{K \cup\{j\}})^{2}  u^{'}_{K\cup \{i,j\}} \left( 1+ u^{'}_i u^{'}_j u^{'}_{ij} \prod_{I \subset L} u_L \right)                       \nonumber
+\eea
+
+The other $u$-equations are not two or three term equations and seem to be polynomials of order $|I|=n-2$ in the corresponding $u$'s. Thus, the most general $u$-equations can be conjectured to be:
+\bea
+1-u_{I} = \prod_{J} u^{s_J}_{J} P_{|I|}(u_I, u_J,u_K) 
+\eea
+where, $J$ are all sets incompatible with $I$
+
+ $K$ are all sets compatible with $I$ excluding itself 
+ $s_J$ are positive integers.
+
+\end{enumerate}
 

### 2020-04-20 draft_ABP.tex
update

@@
 To do this we shall use the fact that both $A_n$ and $B_n$ are generalised permutahedra and can be realised as a Minkowski sum of coordinate simplices.
+For future convenience, let's define $[i,j]=\{i,i+1,\dots,j\}$ for 
+$i,j\in \mathbb Z/(n+1)\mathbb Z$.
 
@@
 
-Let's define $[i,j]=\{i,i+1,\dots,j\}$ for $i,j\in \mathbb Z/(n+1)\mathbb Z$.
-%For the symbol $X=x,u,S,F$, we also use the notation $X_{ij}:=X_{[i,j-1]}$.
-
-The building set of $A_n$ is $\{[i,j]\,:\, 0\leq i\leq j\leq n\}$.
-The facets are given by eq.\eqref{GPfacet}
-\[
-F^A_{[i,j]}=\sum_{i\leq k\leq l\leq j}S_{[k,l]},
+\subsubsection*{$n$-dimensional associahedron $\mathscr A_n$}
+
+The building set of $\mathscr A_n$ is $\mathbf B= \{[i,j]\,:\, 0\leq i\leq j\leq n\}$.
+The stringy canonical form of this building set $\mathcal I_{\mathbf B}(\{S\})$
+is related with the original string integral eq.\eqref{stringint} by 
+\[
+	z_{j}-z_i=x_{[i,j-1]},
+\]
+so Mandelstam variables are related to $S$ by $s_{ij}=S_{[i,j-1]}$.
+The facets of $\mathscr A_n$ are given by
+\[
+	F_{[i,j]}=\sum_{[k,l]\subset [i,j]}S_{[k,l]},
 \]
 and their solution is 
-\[
-S_{[i,j]}=F^A_{[i,j]}+F^A_{[i+1,j-1]}-F^A_{[i,j-1]}-F^A_{[i+1,j]},
-\]
-where $F^A_{[k,l]}:=0$ when $k>l$ or $[k,l]=[0,n]$. Using this solution to rewrite the integrand
-\[
+\begin{equation}\label{Ansf}
+S_{[i,j]}=F_{[i,j]}+F_{[i+1,j-1]}-F_{[i,j-1]}-F_{[i+1,j]},
+\end{equation}
+where $F_{[k,l]}:=0$ when $k>l$ or $[k,l]=[0,n]$. Using this solution to rewrite 
+the integrand of the stringy canonical form $\mathcal I_{\mathbf B}(\{S\})$
+\begin{align*}
 \prod_{0\leq i\leq j\leq n}x_{[i,j]}^{S_{[i,j]}}
-=\prod_{0\leq i\leq j\leq n}\frac{x_{[i,j]}^{F^A_{[i,j]}}x_{[i,j]}^{F^A_{[i+1,j-1]}}}{x_{[i,j]}^{F^A_{[i,j-1]}}x_{[i,j]}^{F^A_{[i+1,j]}}}
-=
-\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F^A_{[i,j]}}
-\prod_{1\leq i\leq j\leq n-1}x_{[i-1,j+1]}^{F^A_{[i,j]}}
-\prod_{0\leq i\leq j\leq n-1}x_{[i,j+1]}^{-F^A_{[i,j]}}
-\prod_{1\leq i\leq j\leq n}x_{[i-1,j]}^{-F^A_{[i,j]}},
-\]
+&=\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F_{[i,j]}}x_{[i,j]}^{F_{[i+1,j-1]}}\bigg /
+x_{[i,j]}^{F_{[i,j-1]}}x_{[i,j]}^{F_{[i+1,j]}}\\
+&=
+\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F_{[i,j]}}
+\prod_{1\leq i\leq j\leq n-1}x_{[i-1,j+1]}^{F_{[i,j]}}
+\prod_{0\leq i\leq j\leq n-1}x_{[i,j+1]}^{-F_{[i,j]}}
+\prod_{1\leq i\leq j\leq n}x_{[i-1,j]}^{-F_{[i,j]}},
+\end{align*}
 and we get that
@@
 \]
-where $x_{[i,n+1]}:=1$ and  $x_{[-1,j]}:=1$. $u$-equations are
+with $x_{[i,n+1]}:=1$ and $x_{[-1,j]}:=1$, whose $u$-equations are
 \[
@@
 
-The building set of $B_n$ is $\{[i,i+k]\,:\,0\leq i, k\leq n\}$.
-The facets are given by eq.\eqref{GPfacet}
-\[
-F^B_{[i,j]}=\sum_{[k,l]\subset [i,j]}S_{[k,l]},
+The ABHY construction of $\mathscr A_n$ is given by 
+\[
+	S_{[i,j]}=-c_{[i,j]} \,\,\text{ for all $i<j$,}\quad
+	F_{[i,j]}\geq 0 \,\,\text{ for all $i\leq j$},
+\]
+where $c$s are positive numbers. We can use a mesh to represent these conditions.
+For example, the mesh of $\mathscr A_3$ is 
+\begin{center}
+\begin{tikzpicture}
+	\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) node[below]{0} -- (0,1);
+	\draw[thick] (-1,-2) node[below]{0} -- (2,1);
+	\draw[thick] (-2,-1) -- (-1,-2);
+	\draw[thick] (-1,0) -- (1,-2) node[below]{0}-- (3,0);
+	\node at (-2.5,-1) {$[0,0]$};
+	\node at (-0.65,-1) {$[1,1]$};
+	\node at (1.35,-1) {$[2,2]$};
+	\node at (3.35,-1) {$[3,3]$};
+	\node at (-1.5,0) {$[0,1]$};
+	\node at (0.35,0) {$[1,2]$};
+	\node at (2.35,0) {$[2,3]$};
+	\node at (-0.5,1) {$[0,2]$};
+	\node at (1.35,1) {$[1,3]$};
+	\node at (1,2.2) {$[0,3]$};
+\end{tikzpicture}
+\end{center}
+Each diamond in the mesh whose top corner\footnote{
+It looks different with the usual mesh where label of $c$ follows the left corner
+in each diamond. This is because the mismatch of the correspondence of labels 
+$F_{ij}=F_{[i,j-2]}$ and $s_{ij}=S_{[i,j-1]}$.
+}
+is label by $[i,j]$ represents 
+\[
+	c_{[i,j]}=F_{[i,j-l]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]},
+\]
+and each big diamond (which is made of several diamonds) gives us an equation
+\[
+	\sum_{i\leq a<j\atop{k<b\leq l}} c_{[a,b]} = 
+	F_{[i,k]}+F_{[j,l]}-F_{[i,l]}-F_{[j,k]}
+\]
+where $F_{[a,b]}:=0$ when $a>b$ or $[a,b]=[0,n]$
+
+\subsubsection*{$n$-dimensional cyclohedron $\mathscr B_n$}
+
+The building set of $\mathscr B_n$ is $\mathbf B=\{[i,i+k]\,:\,0\leq i, k\leq n\}$.
+The facets are given by 
+\[
+F_{[i,j]}=\sum_{[k,l]\subset [i,j]}S_{[k,l]},
 \]
@@
 \[
-S_{[i,i]}=F^B_{[i,i]},\quad S_{[i,j]}=F^B_{[i,j]}+F^B_{[i+1,j-1]}-F^B_{[i,j-1]}-F^B_{[i+1,j]}\quad \text{for $i\neq j$},
-\]
-where $F^B_{[i+1,i]}:=0$. Therefore, the $u$-variables are
+S_{[i,i]}=F_{[i,i]},\quad S_{[i,j]}=F_{[i,j]}+F_{[i+1,j-1]}-F_{[i,j-1]}-F_{[i+1,j]}\quad \text{for $i\neq j$},
+\]
+where $F_{[i+1,i]}:=0$. Therefore, the $u$-variables are
 \[
@@
 
-$B_n$ type cluster stringy integral also comes from a hyperplane arrangement, the Shi arrangement.
-The Shi arrangement contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
-on the real line with the freedom of global transformation 
+Like $A_n$, $B_n$ type cluster stringy canonical form also comes from a hyperplane 
+arrangement, the Shi arrangement. The Shi arrangement contains $n+1$ punctures 
+$\{z_i\}_{i=1,\dots,n+1}$ on the real line with the freedom of global transformation 
 $z_i\to z_i+a$ which can be used to fix $z_{n+1}=0$. The Shi arrangement is 
@@
 \[
-    u_1=1+z_1-z_2,\quad \dots,\quad u_{n}=1+z_{n}-z_{n+1},\quad u_{n+1}=z_{n+1}-z_1
+    u_1=\tilde z_1-z_2,\quad \dots,\quad u_{n}=\tilde z_{n}-z_{n+1},
+    \quad u_{n+1}=z_{n+1}-z_1
 \]
 and 
-\[
-\begin{aligned}
-    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad &&\text{for $i<j$},\\
-    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad &&\text{for $i<j$},
-\end{aligned}
-\]
+\begin{align*}
+    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad \text{for $i<j$},\\
+    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad \text{for $i<j$},
+\end{align*}
 where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices live in $\mathbb Z_{2n+2}$.
@@
 
-From the following equations for facets $\{F_{ij}\}$ of $A_n$
-\[
-F_{ac}+F_{bd}-F_{bc}-F_{ad}=\sum_{a\leq p<b\atop{c\leq q<d}}c_{pq}
-\]
-for $1\leq a<b<c<d\leq n+3$, an economical way to get a degeneration which satisfies the above property is setting all $c$s on the RHS of 
+From the following equations for facets $\{F_{[i,j]}\}$ of $A_n$
+\[
+	F_{[i,k]}+F_{[j,l]}-F_{[i,l]}-F_{[j,k]}=
+	\sum_{i\leq a<j\atop{k<b\leq l}} c_{[a,b]} 
+\]
+where $F_{[a,b]}:=0$ when $a>b$ or $[a,b]=[0,n]$,
+an economical way to get a degeneration which satisfies the above property is setting all $c$s on the RHS of 
 \begin{align*}
-    &F_{ac}+F_{bd}-F_{ad}=\sum_{a\leq p<b< q<d}c_{pq}\quad \text{for $a<b<c=b+1<d$ }\\
+&F_{[i,j-1]}+F_{[j,l]}-F_{[i,l]}= \sum_{i\leq a<j\leq b\leq l} c_{[a,b]} 
+\quad \text{for $i<j=k+1\leq l$ }\\[-1.5ex]
 \text{or}&\\
-    &F_{1c}+F_{b,n+3}-F_{bc}=\sum_{1\leq p<b\atop{c\leq q<n+3}}c_{pq}\quad \text{for $a=1$ and $d=n+3$}
+&F_{[0,k]}+F_{[j,n]}-F_{[j,k]}= \sum_{0\leq a<j\atop{k<b\leq n}} c_{[a,b]} 
+\quad \text{for $0<j\leq n$ and $0\leq k<n$}
 \end{align*}
@@
 \end{tikzpicture}
-	\qquad \text{or}
-	\qquad
+\qquad \text{or}\qquad
 \begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
@@
 \node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (3,0) {};
-	\node at (-2.5,-1) {$13$};
-\node at (-0.5,-1) {$24$};
-\node at (1.5,-1) {$35$};
-\node at (3.5,-1) {$46$};
-\node at (-1.5,0) {$14$};
-\node at (0.5,0) {$25$};
-\node at (2.5,0) {$36$};
-\node at (-0.5,1) {$15$};
-\node at (1.5,1) {$26$};
-\node at (1,2.2) {$16$};
+\node at (-2.5,-1) {$[0,0]$};
+\node at (-0.65,-1) {$[1,1]$};
+\node at (1.35,-1) {$[2,2]$};
+\node at (3.35,-1) {$[3,3]$};
+\node at (-1.5,0) {$[0,1]$};
+\node at (0.35,0) {$[1,2]$};
+\node at (2.35,0) {$[2,3]$};
+\node at (-0.5,1) {$[0,2]$};
+\node at (1.35,1) {$[1,3]$};
+\node at (1,2.2) {$[0,3]$};
 \end{tikzpicture}
@@
 \[
-\{16,15,26,14,36,13,46\}.
-\]
-One can further check that it's a cube or $A_1^3$.
-
-We can play the game for any degenerations of $A_n$, count black points and deleted $c$s in each degeneration, and find that for $A_2$, $A_3$ and $A_4$, there're respectively $5$, $42$ and $565$ possible degenerations whose big polytopes are simplices.
+	\{[0,3],[0,2],[0,1],[0,0],[1,1],[2,2],[3,3]\}.
+\]
+One can further check that it's a cube (or $A_1^3$).
+
+We can play the game for any degenerations of $A_n$, count black points and deleted $c$s in each degeneration, and find that for $A_2$, $A_3$ and $A_4$, there're respectively $4$, $41$ and $580$ possible degenerations whose big polytopes are simplices.
 For these degenerations, we can easily find their $u$-variables if their sets of all vanishing facets are known.
@@
 
-The simplest degenerations of $A_n$ are those with one $c_{i,i+2}$ vanishing. For the one with $c_{i,i+2}=0$, we get 
-\[
-F_{i,i+3}=F_{i,i+2}+F_{i+1,i+3},
-\]
-so 
-\[
-\tilde u_{i,i+2}=u_{i,i+2} u_{i,i+3},\quad 
-\tilde u_{i+1,i+3}=u_{i+1,i+3} u_{i,i+3},\quad 
-\tilde u_I=u_I \text{ for the other $I\neq (i,i+3)$}.
+The simplest degenerations of $A_n$ are those with one $c_{[i,i+1]}$ vanishing. For the one with $c_{[i,i+1]}=0$, we get 
+\[
+	F_{[i,i+1]}=F_{i}+F_{i+1},
+\]
+where $F_i=F_{[i,i]}$, so 
+\[
+	\tilde u_{i}=u_{i} u_{[i,i+1]},\quad 
+	\tilde u_{i+1}=u_{i+1} u_{[i,i+1]},\quad 
+	\tilde u_I=u_I \text{ for the other $I\neq [i,i+1]$}.
 \]
@@
 \[
-1-\tilde u_{i,i+2}=\prod_{j\neq i,i+2,i+3} \tilde u_{i+1,j},\quad 
-1-\tilde u_{i+1,i+3}=\prod_{j\neq i,i+2,i+3} \tilde u_{i+2,j}
-\]
-and $u$-equations for $\{u_{kl}\,:\, (k,l)\neq (i,i+3),(i,i+2),(i+1,i+3)\}$ with the change of variables above.
-Similarly, one can easily find the $u$-variables and $u$-equations for the degenerations with $c_{i,i+2}=0$ for several $i$.
-
-The next simplest degenerations of $A_n$ is setting $c_{i-1,i+1}=c_{i,i+2}=c_{i-1,i+2}=0$, we have seen an example in $A_3$ above.
-
-% For example, in the above example of $A_3$,
-% \[
-% F_{123}=F_{1}+F_2+F_3, \quad F_{12}=F_1+F_2, \quad F_{23}=F_2+F_3,
-% \]
-% so the $u$-variables are
-% \begin{align*}
-% \tilde u_{1}&=u_1 u_{123} u_{12}=\frac{x_1}{x_{01}},\quad 
-% \tilde u_{2}=u_2 u_{123} u_{12}u_{23}=\frac{x_{2}}{x_{012}},\quad 
-% \tilde u_{3}=u_3u_{123}u_{23}=\frac{x_3}{x_{0123}},\\
-% \tilde u_{0}&=u_{0}=\frac{x_{0}}{x_{01}},\quad 
-% \tilde u_{01}=u_{01}=\frac{x_{01}}{x_{012}},\quad 
-% \tilde u_{012}=u_{012}=\frac{x_{012}}{x_{0123}},
-% \end{align*}
-% and they satisfy the following $u$-equations:
-% \[
-% 	\tilde u_1+\tilde u_0=1,\quad \tilde u_2+\tilde u_{01}=1,
-% 	\quad \tilde u_{3}+\tilde u_{012}=1.
-% \]
-
-(Find those with perfect $u$-eq?)
-
-*******************
-\subsection*{Degenerations which lead to products}
-In this section we provide an answer to the question of which degenerations of $A_n$ and $B_n$ give the most general products of such geometries.
-We begin by stating the following results about Nestohedra.
-
-The maximal set of a building set $B_{max}$ is the set of all inclusion maximal elements of the building set $B$. A building set $B$ is connected if $B_{max}$ has a single element.
-
-{\bf Theorem:}If $B_1, B_2,\cdots B_n$ are connected subsets of a building set $B$ then the corresponding nestohedron ${\mathscr N_B}$ is isomorphic to the product of the nestohedra ${\mathscr N}_{ B_1} \times{\mathscr N}_{ B_2} \cdots \times {\mathscr N}_{B_n}$.
-
-We can use the above result to construct 	a degeneration of $A_n$ which is a most general product i.e., $\prod_{p_i} A_{p_i}$ such that $\sum_{i} p_{i} = n$.
-
-Let us consider the  $A_4$ example for which the allowed possibilities are : $A_1^{4}$, $A_1^2 \times A_2$, $A_1 \times A_3$ and $A^{2}_2$.
-
-For the $A_1^{4}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} \}$ where $\{0,01\} , \{1,12\},\{2,23\},\{3,34\}$ generate the 4 $A_1$'s.
-
-For the $A_1^{2} \times A_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{234} \}$ where $\{0,01\} , \{1,12\} $ generate the 2 $A_1$'s and $\{2,3,4,23,34,234\}$ generates the $A_2$'s.
-
-For the $A_1 \times A_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{123},{234},{1234} \}$ where $\{0,01\}$ is the generates the $A_1$ and $\{{1},{2},{3},{4},{12},{23},{34},{123},{234},{1234} \}$ generate  $A_3$'s.
-
-For the $A_2^{2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} ,{012},{234}\}$ where $\{0,1,2,01,12,012\}$  and $\{2,3,4,23,34,234\}$ generate the 2 $A_2$'s.
-
-We can similarly find a degeneration of $A_n,B_n,~or~ {\mathscr P_n}$ which would correspond to any product.
+	1-\tilde u_{i}=\prod_{0\leq a\leq i-1}\tilde u_{[a,i-1]}
+	\prod_{i+1< b\leq n} \tilde u_{[i+1,b]},\quad 
+	1-\tilde u_{i+1}=\prod_{0\leq a <i-1} \tilde u_{[a,i]}
+	\prod_{i+2\leq b\leq n} \tilde u_{[i+2,b]},\quad 
+\]
+and the other $u$-equations are original $u$-equations for
+$\{u_{[i,j]}\,:\, [i,j]\neq [i,i],[i,i+1],[i+1,i+1]\}$ in terms of new variables.
+Similarly, one can easily find the $u$-variables and $u$-equations for the degenerations with $c_{[i,i+1]}=0$ for several $i$.
+
+%The next simplest degenerations of $A_n$ is setting $c_{[i-1,i]}=c_{[i,i+1]}=c_{[i-1,i+1]}=0$ for $1\leq i\leq n-1$, we have seen an example in $A_3$ above.
+The vanishing facets of this degeneration are
+%\[
+	%F_{[i-1,i+1]}=F_{i-1}+F_i+F_{i+1},\quad F_{[i-1,i]}=F_{i-1}+F_i,
+	%\quad F_{[i,i+1]}=F_i+F_{i+1},
+%\]
+%so $u$-variables of this degeneration are 
+%\[
+	%\tilde u_{i-1}=u_{i-1}u_{[i-1,i+1]}u_{[i-1,i]}, \quad 
+	%\tilde u_{i}=u_iu_{[i-1,i+1]}u_{[i,i+1]},\quad
+	%\tilde u_{i+1}=u_{i+1}u_{[i-1,i+1]}u_{[i,i+1]} 
+%\]
+%and $\tilde u_I=u_I$ for the other $I$. ($u$-eqs...)
+
+The nest simplest degenerations of $\mathscr A_n$ may be products 
+$\mathscr A_i\times \mathscr A_{n-i}$, which can be realized as the following
+mesh,
+\begin{center}
+\usetikzlibrary{decorations.pathmorphing}
+\begin{tikzpicture}[scale=2]
+\fill[green!20] (0.4498,-0.558) -- (1.2997,-1.4584) -- (2.8779,0.1223) --(2,1);
+\draw (-0.5,-1.5) -- (2,1) -- (4.5,-1.5);
+\draw[decorate,decoration=zigzag] (-0.5,-1.5)--(4.5,-1.5);
+\node at (1.7,-1.3) {$[i,i]$};
+\node at (0.3,-0.4) {$[0,i]$};
+\node at (3.1,0.2) {$[i,n]$};
+\end{tikzpicture}
+\end{center}
+where $c$s in green region vanish, \emph{i.e.} $c_{[a,b]}=0$ for $0\leq a<i<b\leq n$.
+Vanishing facets of this degeneration are
+\[
+F_{[a,b]}=F_{[a,n]}+F_{[0,b]}\quad \text{for $0<a\leq i\leq b<n$},
+\]
+so new $u$-variables are
+\[
+	\tilde u_{[0,b]} = u_{[0,b]}\prod_{a=1}^{i} u_{[a,b]},\quad 
+	\tilde u_{[a,n]} = u_{[a,n]}\prod_{b=i}^{n-1} u_{[a,b]},
+\]
+and $\tilde u_{I}=u_{I}$ for the other $I$. The $u$-equations are the union of 
+$u$-equations of the following two independent meshes
+\begin{center}\footnotesize
+\begin{tikzpicture}[scale=1.5,baseline={([yshift=-.5ex]current bounding box.center)}]
+\draw (0.5,-2.5) -- (3,0) -- (5.5,-2.5);
+\draw (5.5,-2.5) -- (5,-3) -- (2.5,-0.5);
+\draw (5,-2) -- (4,-3) -- (2,-1);
+\draw (4.5,-1.5) -- (3,-3) -- (1.5,-1.5);
+\draw (0.5,-2.5) -- (1,-3) -- (3.5,-0.5);
+\node at (2,-2.8) {$\cdots$};
+\node at (2.6,-2.1) {$\ddots$};
+\node at (3.1,-1.6) {$\ddots$};
+\node at (3.6,-1.1) {$\ddots$};
+\node at (0.3,-2.5) {$[0,0]$};
+\node at (3.1,-2.5) {$[i{-}2,i{-}2]$};
+\node at (4.1,-2.5) {$[i{-}1,i{-}1]$};
+\node at (5.2,-2.5) {$[i,n]$};
+\node at (4.6,-2) {$[i{-}1,n]$};
+\node at (3.6,-2) {$[i {-}2,i{-}1]$};
+\node at (4.2,-1.5) {$[i{-}2,n]$};
+\node at (3.2,-0.5) {$[1,n]$};
+\node at (3,0.2) {$[0,n]$};
+\node at (2.1,-0.5) {$[0,i{-}1]$};
+\node at (1.7,-1) {$[0,i{-}2]$};
+\end{tikzpicture}\quad 
+\begin{tikzpicture}[scale=1.5,baseline={([yshift=-.5ex]current bounding box.center)}]
+\draw (0.5,-2.5) -- (3,0) -- (5.5,-2.5);
+\draw (5.5,-2.5) -- (5,-3) -- (2.5,-0.5);
+\draw (4.5,-1.5) -- (3,-3) -- (1.5,-1.5);
+\draw (4,-1) -- (2,-3) -- (1,-2);
+\draw (0.5,-2.5) -- (1,-3) -- (3.5,-0.5);
+\node at (4,-2.6) {$\cdots$};
+\node[rotate=90] at (3.2,-2.2) {$\ddots$};
+\node[rotate=90] at (2.7,-1.7) {$\ddots$};
+\node[rotate=90] at (2.2,-1.2) {$\ddots$};
+\node at (3,0.2) {$[0,n]$};
+
+\node at (3.9,-0.5) {$[i{+}1,n]$};
+\node at (4.4,-1) {$[i{+}2,n]$};
+\node at (4.9,-1.5) {$[i{+}3,n]$};
+\node at (2.1,-0.5) {$[0,n{-}1]$};
+\node at (1.2,-1.4) {$[0,i{+}2]$};
+\node at (0.2,-2.5) {$[0,i]$};
+\node at (0.6,-2) {$[0,i{+}1]$};
+\node at (1.2,-2.5) {$[i{+}1,i{+}1]$};
+\node at (1.7,-2) {$[i{+}1,i{+}2]$};
+\node at (2.1,-2.5) {$[i{+}2,i{+}2]$};
+\end{tikzpicture}
+\end{center}
+
+(direct proof?)
+
+(Find all with perfect $u$-eq?)
+
+degenerations of $B_n$ ...
 
@@
 
-\section*{Braid arrangement}
+\subsection*{Braid arrangement}
 The braid arrangement in $\mathbb{R}^{n+1}$ consists of $\left({n}\atop{2}\right)$ hyperplanes 
@@
 \eea
+
+\subsection*{Degenerations which lead to products}
+In this section we provide an answer to the question of which degenerations of $A_n$ and $B_n$ give the most general products of such geometries.
+We begin by stating the following results about Nestohedra.
+
+The maximal set of a building set $B_{max}$ is the set of all inclusion maximal elements of the building set $B$. A building set $B$ is connected if $B_{max}$ has a single element.
+
+{\bf Theorem:}If $B_1, B_2,\cdots B_n$ are connected subsets of a building set $B$ then the corresponding nestohedron ${\mathscr N_B}$ is isomorphic to the product of the nestohedra ${\mathscr N}_{ B_1} \times{\mathscr N}_{ B_2} \cdots \times {\mathscr N}_{B_n}$.
+
+We can use the above result to construct 	a degeneration of $A_n$ which is a most general product i.e., $\prod_{p_i} A_{p_i}$ such that $\sum_{i} p_{i} = n$.
+
+Let us consider the  $A_4$ example for which the allowed possibilities are : $A_1^{4}$, $A_1^2 \times A_2$, $A_1 \times A_3$ and $A^{2}_2$.
+
+For the $A_1^{4}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} \}$ where $\{0,01\} , \{1,12\},\{2,23\},\{3,34\}$ generate the 4 $A_1$'s.
+
+For the $A_1^{2} \times A_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{234} \}$ where $\{0,01\} , \{1,12\} $ generate the 2 $A_1$'s and $\{2,3,4,23,34,234\}$ generates the $A_2$'s.
+
+For the $A_1 \times A_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{123},{234},{1234} \}$ where $\{0,01\}$ is the generates the $A_1$ and $\{{1},{2},{3},{4},{12},{23},{34},{123},{234},{1234} \}$ generate  $A_3$'s.
+
+For the $A_2^{2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} ,{012},{234}\}$ where $\{0,1,2,01,12,012\}$  and $\{2,3,4,23,34,234\}$ generate the 2 $A_2$'s.
+
+We can similarly find a degeneration of $A_n,B_n,~or~ {\mathscr P_n}$ which would correspond to any product.
+
 \subsection{Natural stringy integrals with linear factors}

### 2020-04-20 draft_ABP.tex
Updates from Overleaf

--- 2020-04-20 draft_ABP.tex
@@
 Before we proceed we shall review some details about the generalised permutahedra which we shall use throughout the paper.
-\subsection{Generalized permutohedra} {\bf the definition, facets and combinatorial factorizations, do $P_n$ example in full details.}
-******************************************************************************************
-\subsubsection*{Permutahedron}
- For $x_1,x_2, \cdots, x_{n+1} \in \mathbb{R} $ , the permutahedron ${\mathscr P_n}(x_1,\cdots,x_{n+1})$ is a convex polytope in $\mathbb{R}^{n+1}$ defined as the convex hull of all vectors obtained from $(x_1,x_2, \cdots, x_{n+1})$ by permutations of the coordinates:
- \bea
-{\mathscr P_n}(x_1,x_2, \cdots, x_{n+1}) = {\rm ConvexHull} \{ (x_{w(1)},x_{w(2)}, \cdots, x_{w(n+1)})~ |~ w \in S_{n+1} \}, \nonumber
- \eea
- where $S_{n+1}$ is the symmetric group.
-
- The permutahedron has $(n+1)!$ vertices and is of dimension at most $n$ since it lies in the hyperplane 
- \bea
- H_c= \{(t_1,t_2, \cdots, t_{n+1}) ~|~ t_1 + t_2 + \cdots + t_{n+1}= c \} \subset \mathbb{R}^{n+1}, \nonumber
- \eea
-where $c= x_1+x_2+ \cdots +x_{n+1}$.
-
-For $n=1$ and distinct $x_1,x_2$ the permutahedron ${\mathscr P_1}(x_1,x_2)$ is a line. If  $x_1=x_2$ then it degenerates into a single point.
-
-For $n=2$ and distinct $x_1,x_2, x_3$ the permutahedron ${\mathscr P_2}(x_1,x_2, x_3)$ is a hexagon.
-If two of the $x_i$'s are equal then the permutahedron degenerates into a triangle and if $x_1= x_2 = x_3$ then its degenerates into a single point.
-
-We shall list a few results about permutahedra which shall be useful for later purposes: 
-\begin{itemize}
-\item {\bf Parameter independence:} The combinatorial structure of the permutahedron ${\mathscr P_n} (x_1, \cdots, x_{n+1}) $ does not depend on $ x_1, \cdots, x_{n+1} $ as long as all these are distinct.
-Henceforth  we will choose $ \{x_1, \cdots, x_{n+1}\} = \{0,1,\cdots,n \} := [0,n ]$.
-\\
-\item {\bf Facial Structure:} The $(n-k)$ faces of ${\mathscr P_n}$ are in an $1-1$ correspondence with the decomposition of $[0,n]$ into $k$ parts.
-More precisely, for each $(S_1,\cdots,S_k)$ with $S_i \neq \emptyset ~ \forall i$ and $[0,n] = S_1 \sqcup \cdots \sqcup S_k$ the corresponding face $\pi_{S_1,\cdots,S_k}$ has vertices which are permutations such that the entries $ \{x_i | i \in S_1 \}$ are largest $|S_1|$ numbers in $[0,n]$, $\{x_i | i \in S_2 \}$ are largest $|S_2|$ numbers in $[0,n]$ and so on.
-
-Further the face $\pi_{S_1,\cdots,S_k}$   is isomorphic to ${\mathscr P_{\left(| S_1|-1\right)} }\times {\mathscr P_{\left(| S_2|-1\right)} } \cdots \times{\mathscr P_{\left(| S_k|-1\right)} } $.
-
-It follows from above that ${\mathscr P_n}$ has $2^{n+1} -2$ facets corresponding to all the non-empty proper subsets of $[0,n]$ for which we have a decomposition $[0,n] = S \sqcup S^c$ and the facets are isomorphic to one of the following product of lower dimensional permutahedra  $ \{ {\mathscr P_{n-1}}, {\mathscr P_{n-2}} \times A_1, \cdots ,{\mathscr P_{\lfloor{n/2 \rfloor}}} \times {\mathscr P_{n-1-\lfloor n/2 \rfloor}}  \} $\footnote {More generally the number of $(n-k)$ facets of ${\mathscr P_n}$ is $ k!
-S(n,k)$ where $S(n,k)$ is the Stirling number of the second kind which counts the number $k$ partitions of  $I$ and there are $p(n+1,k)$ types where $p(n+1,k)$ is the number of $k$ partitions of $(n+1)$.}.
-
-It also follows from above that a face $\pi_{S_1,\cdots,S_k}$ is contained in another face $\pi_{T_1,\cdots,T_l}$ if and only if each $T_i$ is a union of consecutive $S_j$ or equivalently if $(S_1,\cdots,S_k)$ is a refinement of $(T_1,\cdots,T_l)$.
-\item {\bf Minkowski decomposition:}   Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_{n+1})$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$.
-For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull}(e_i~|~i\in I)$ denote the face of the $\Delta_{[0,n]}$.
-The polytope $P_n(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I > 0$ for all nonempty subsets $I \subset [n+1]$
- \bea
- P_n(\{y_I \})= \sum_{I \subset[n+1]} y_I . \Delta_I  \nonumber
- \eea
- is the permutahedron ${\mathscr P_n}$
-\end{itemize}
-We shall now talk about generalized permutahedra which are polytopes obtained by deformations of the usual permutahedron i.e., obtained by moving the vertices of the usual permutahedron so that the directions of all the edges are preserved or equivalently translating facets without allowing them to move past vertices which may cause some of the edges to degenerate into points.
-
-\subsubsection*{Generalized permutahedra}
-
-A  generalised permutahedron is obtained by parallel translation of facets of the usual permutahedron it is parametrized  by a collection $\{ z_I\}$ of $2^{n+1}-1$ coordinates, for non-empty sets of $I \subset [0,n] $
- \bea \label{genperm_defi}
- P_n^z(\{ z_I \}) = \left \{ (t_0 , t_1, \cdots , t_{n}) \in \mathbb{R}^{n+1} | \sum_{i=0}^{n} t_i = z_{[0,n]},~ \sum_{i \in I} t_i \geq z_I, {\rm for ~subsets} ~I  \right  \}
- \eea
- If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron.
-
- Unlike the permutahedron not all generalised permutahedra can be represented as a Minkowski sum of co-ordinate simplices.
-We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation which are called Nestohedra which we denote by ${\mathscr N}$.
-Throughout the paper we shall mean Nestohedra whenever we refer to generalized permutahedra unless stated otherwise.
- \begin{itemize}
- \item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
-  \bea
-{\mathscr N_n}^y(\{y_I \})= \sum y_I . \Delta_I  \nonumber
+\subsection{Generalized permutohedra} 
+A generalised permutahedron is a polytope that obtained as Minkowski sums and diffrences of co-ordinate simplices.
+
+Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
+  \bea
+{\mathscr P_n}^y(\{y_I \})= \sum y_I . \Delta_I  
  \eea
  for some collection of subsets $I \in [0,n]$
- \end{itemize}
-  \begin{itemize}
- \item{\bf Parameter Independence:} The combinatorial structure of the generalised permutahedron ${\mathscr N_n({y_I})}$ is independent of the parameters $y_I$ and depends only on the collection of subsets $I \in [0,n]$ called the  building set $B$.
-\end{itemize}
-A collection of non-empty subsets of $[0,n]$ is called a building set $B$ if it satisfies the following:
+ We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation only as Minkowski sums i.e., all $y_I \ge 0$ \footnote{This is mainly due to the subtle nature of the Minkowski difference operation, which makes the shape of the resulting polytope dependent on the relative magnitudes of $y_I$'s.}which are called Nestohedra.
+Throughout the paper we shall mean Nestohedra whenever we refer to generalized permutahedra unless stated otherwise.\\
+
+ The combinatorial structure of the generalised permutahedron ${\mathscr P_n({y_I})}$ (Nestohedra) is independent of the parameters $y_I$ and depends only on the collection of subsets $I \in [0,n]$ called the  building set ${\mathbf B}$.
+A collection of non-empty subsets of $[0,n]$ is called a building set ${\mathbf B}$ if it satisfies the following:
 \begin{compactenum}[\quad (1)]
-    \item If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$.
-    \item $B$ contains all singletons $\{ i\}$ for $i \in S$.
+    \item If $I,J \in {\mathbf B}$ and $I \cap J \neq \phi $, then $I \cup J \in {\mathbf B}$.
+    \item ${\mathbf B}$ contains all singletons $\{ i\}$ for $i \in S$.
 \end{compactenum}
@@
 \subsubsection*{Nested Complex}
-A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
+A subset ${\mathbf N}$ in the building set ${\mathbf B}$ is called a {\it nested set} if it satisfies the following conditions:
 \begin{compactenum}[\quad (1)]
-    \item For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
+    \item For any $I,J \in {\mathbf N}$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
     \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
-    \item $N$ contains all maximal elements of $B$.
+    \item ${\mathbf N}$ contains all maximal elements of $B$.
 \end{compactenum}
-The {\it nested complex} $\mathcal{N}(B)$ is defined as the poset of the set of all nested sets in $B$ ordered by inclusion.
-
-\begin{itemize}
-
-\item {\bf Facial structure:} Let us assume that the set $B$ associated with a generalised permutahedron ${\mathscr N_n}^{y}$ is a building set on $[0,n]$.
-Then the poset of faces ${\mathscr N_n}^{y}$ ordered by reverse inclusion is isomorphic to the nested complex $\mathcal{N}(B)$.
-
-For each decomposition $[0,n]=  \sqcup_{I \subset N } S_I $ where $S_I$ are non-empty, the face $P_N$ of ${\mathscr N_n}^{y}(y_I)$ associated with the nested set $N \in \mathcal{N}(B)$ is:
-\bea
-P_N = \sum_{{J \subset B}\atop{J \cap S_I \neq \emptyset}} y_{J} \Delta_{J \cap S_I}
-\eea
-\end{itemize}
-
-In summary the above results imply that we can look at any collection of subsets of $[0, n]$ which form a building set $B$ and associate  coordinate simplex $\Delta_I$ for each $I \in B$ and resulting Minkowski sum with positive weights $y_I$ generates a generalised permutahedron associated with the building set.
-Further, the number of facets $N$ of the generalised permutahedron just corresponds to the set of all elements in $B$ excluding the maximal set.
-
-Let, $m$ denote the number of non-singlet elements in $B$ i.e., the number of linear equations as explained in (1.1) 
-\bea
-N &=& |B|-1 \nonumber \\
+The {\it nested complex} ${\mathbf N}({\mathbf B})$ is defined as the poset of the set of all nested sets in ${\mathbf B}$ ordered by inclusion.\\
+
+ {\bf Facial structure:}
+
+ Let us assume that the set ${\mathbf B}$ associated with a generalised permutahedron ${\mathscr P_n}^{y}$ is a building set on $[0,n]$.
+Then the poset of faces ${\mathscr P_n}^{y}$ ordered by reverse inclusion is isomorphic to the nested complex ${\mathbf N}({\mathbf B})$.
+
+For each decomposition $[0,n]=  \sqcup_{I \subset {\mathbf N} } S_I $ where $S_I$ are non-empty, the face $P_n$ of ${\mathscr P_n}^{y}(y_I)$ associated with the nested set ${\mathbf N} \in {\mathbf N}({\mathbf B})$ is:
+\bea
+P_n = \sum_{{J \subset {\mathbf B}}\atop{J \cap S_I \neq \emptyset}} y_{J} \Delta_{J \cap S_I}
+\eea
+
+In summary the above results mean the following:\\
+
+(1) We can look at any collection of subsets of $[0, n]$ which form a building set ${\mathbf B}$ and associate  coordinate simplex $\Delta_I$ for each $I \in {\mathbf B}$ and resulting Minkowski sum with positive weights $y_I$ generates a polytope of dimension $n$ called the generalised permutahedron (Nestohedron) associated with the building set.
+\\
+
+(2) The number of facets $N$ of the generalised permutahedron just corresponds to the set of all elements in ${\mathbf B}$ excluding the maximal set. \\
+
+(3) Two facets corresponding to the sets $I$ and $J$ in ${\mathbf B}$ intersect i.e., are {\it compatible} with each other if and only if  either $I \subset J$,~ $J \subset I$~ or $I \cap J = \emptyset ~{\text and} ~ I \cup J \notin {\mathbf B}$.
+
+Let us look at a couple of examples to appreciate these facts better:\\
+(1) Consider the generalized permutahedron with building set ${\mathbf B}= \{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,1,2\} \}$.
+
+The polygon has 5 facets which correspond to the sets $\{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\}\}$ and their compatability is shown in the figure below.
+
+The polytope in this case is the 2d associahedron ${\mathscr A_2}$.\\
+(2) Consider the generalized permutahedron with building set ${\mathbf B}= \{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,2\},\{0,1,2\} \}$
+
+The polygon has 6 facets which correspond to the sets $\{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,2\}\}$ and their compatability is shown in the figure below.
+
+The polytope in this case is the 2d cyclohedron ${\mathscr B_2}$ which also coincides with 2d permutahderon ${\mathscr P_2}$.
+\begin{figure}[H]
+\begin{center}
+
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,511); %set diagram left start at 0, and has height of 511
+
+%Shape: Regular Polygon [id:dp6636381249952382] 
+\draw   (332.23,134.19) -- (310.06,198.57) -- (241.97,197.38) -- (222.06,132.26) -- (277.84,93.2) -- cycle ;
+%Shape: Regular Polygon [id:dp8232688760864714] 
+\draw   (533.33,149) -- (502.83,201.83) -- (441.83,201.83) -- (411.33,149) -- (441.83,96.17) -- (502.83,96.17) -- cycle ;
+
+% Text Node
+\draw (401.67,176.33) node [anchor=north west][inner sep=0.75pt]   [align=left] {01};
+% Text Node
+\draw (461,212) node [anchor=north west][inner sep=0.75pt]   [align=left] {0};
+% Text Node
+\draw (412,109) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+% Text Node
+\draw (463,78) node [anchor=north west][inner sep=0.75pt]   [align=left] {12};
+% Text Node
+\draw (527,101) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+% Text Node
+\draw (523,179) node [anchor=north west][inner sep=0.75pt]   [align=left] {02};
+% Text Node
+\draw (268,204) node [anchor=north west][inner sep=0.75pt]   [align=left] {0};
+% Text Node
+\draw (226,96) node [anchor=north west][inner sep=0.75pt]   [align=left] {12};
+% Text Node
+\draw (310,100) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+% Text Node
+\draw (336,163) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
+% Text Node
+\draw (203,160) node [anchor=north west][inner sep=0.75pt]   [align=left] {01};
+% Text Node
+\draw (262,235) node [anchor=north west][inner sep=0.75pt]   [align=left] {(a)};
+% Text Node
+\draw (454,235) node [anchor=north west][inner sep=0.75pt]   [align=left] {(b)};
+% Text Node
+\draw (155,263) node [anchor=north west][inner sep=0.75pt]   [align=left] {Figure showing the compatible\textbackslash incompatible facets of the 2d associahedron  \\ and permutahedron as generalized permutahedra};
+
+\end{tikzpicture}
+\end{center}
+\end{figure}
+An improtant fact about generalised permutahedra which makes them particularly interesting is the following:
+Let, $m$ denote the number of non-singlet elements in ${\mathbf B}$ i.e., the number of $c_J$'s as explained in equation (2) 
+\bea
+N &=& |{\mathbf B}|-1 \nonumber \\
  &=& (n+1+m)-1 \nonumber  \\
@@
 
-Thus, generalised permutahedra have big Polytopes which are simplices and as emphasized in the previous section we can solve for the $u$-variables and examine if they satisfy some kind of $u$-equations.
+Thus, generalised permutahedra have big Polytopes which are simplices. Thus its quite natural to wonder if the associated $u$-variables satisfy some kind of $u$-equations.
+
+We claim and we shall show in the next section that this indeed the case. Further we show that all these polytopes are binary geometries even though some of them do not admit perfect $u$-equations.
 
@@
 
-(1) If $B$ consists of only singlets i.e., $B=\{ \{ 0,1,\cdots,n \}, \{ 0 \},\{ 1 \},\cdots ,\{ n \} \}$ then the generalised permutahedron is a Simplex.
+(1) If ${\mathbf B}$ consists of only singlets i.e., ${\mathbf B}=\{ \{ 0,1,\cdots,n \}, \{ 0 \},\{ 1 \},\cdots ,\{ n \} \}$ then the generalised permutahedron is a Simplex.
 In this case the relevant $x$ variables are $x_i,~ i=0,\cdots,n$ with $x_0=1$ and $\sum_{i=0}^n x_i$.
@@
 
-(2) If $B= \{[i] | i=1,\cdots,n+1 \}$ is the complete flag of intervals, then ${\mathscr N_n}^y({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
+(2) If ${\mathbf B}= \{[i] | i=1,\cdots,n+1 \}$ is the complete flag of intervals, then ${\mathscr P_n}^y({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
 The Newton polytope of the Minkowski sum is $x_1\cdots x_n (1+x_1) \cdots (1+x_1+\cdots +x_n)$ and $u$-variables are 
@@
 
-(3) If $B$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then ${\mathscr N_n}({\bf Y})$ is the usual permutahedron $P_n$.
+(3) If ${\mathbf B}$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then ${\mathscr P_n}({\bf Y})$ is the usual permutahedron ${\mathscr P_n}$.
 \\
 
-(4)If $B=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr N_n}({\bf Y})$ is the associahedron. \\
-
-(5) If $B=\{ [1,i] \cup [j,n] | 1\leq  i \leq j \leq n\}$ is the set of cyclic intervals, then ${\mathscr N_n}({\bf Y})$ is the Cyclohedron.\\
+(4)If ${\mathbf B}=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr P_n}({\bf Y})$ is the associahedron. \\
+
+(5) If ${\mathbf B}=\{ [1,i] \cup [j,n] | 1\leq  i \leq j \leq n\}$ is the set of cyclic intervals, then ${\mathscr P_n}({\bf Y})$ is the Cyclohedron.\\
 
 (6) Let $\Gamma$ be a graph on the vertex set $[0,n]$.
-Let us assume that $B = B(\Gamma)$ is the set of subsets $I \in [n]$ such that the induced graph $\Gamma$ is connected, then  ${\mathscr N_n}({\bf Y})$ is a graph associahedron.\\
+Let us assume that ${\mathbf B} = {\mathbf B}(\Gamma)$ is the set of subsets $I \in [n]$ such that the induced graph $\Gamma$ is connected, then  ${\mathscr P_n}({\bf Y})$ is a graph associahedron.
+
+It is clear that any  generalized permutahedron can be obtained as a degeneration of  permutahedron ${\mathscr P_n}$i.e., by removing some elements from its building set.
+This makes the permutahedron a very important example of generalized permutahedra and we shall devote the rest of this section to studying its properties and proving it is binary.
+\subsubsection*{Permutahedron}
+
+Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_{n+1})$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$.
+For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull}(e_i~|~i\in I)$ denote the face of the $\Delta_{[0,n]}$.
+The polytope $P_n(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I > 0$ for all nonempty subsets $I \subset [n+1]$
+ \bea
+ P_n(\{y_I \})= \sum_{I \subset[n+1]} y_I . \Delta_I  
+ \eea
+ is the permutahedron ${\mathscr P_n}$
+
+{\bf Facial Structure:}
+
+The $(n-k)$ faces of ${\mathscr P_n}$ are in an $1-1$ correspondence with the decomposition of $[0,n]$ into $k$ parts.
+More precisely, for each $(S_1,\cdots,S_k)$ with $S_i \neq \emptyset ~ \forall i$ and $[0,n] = S_1 \sqcup \cdots \sqcup S_k$ the corresponding face $\pi_{S_1,\cdots,S_k}$ has vertices which are permutations such that the entries $ \{x_i | i \in S_1 \}$ are largest $|S_1|$ numbers in $[0,n]$, $\{x_i | i \in S_2 \}$ are largest $|S_2|$ numbers in $[0,n]$ and so on.
+
+Further the face $\pi_{S_1,\cdots,S_k}$   is isomorphic to ${\mathscr P_{\left(| S_1|-1\right)} }\times {\mathscr P_{\left(| S_2|-1\right)} } \cdots \times{\mathscr P_{\left(| S_k|-1\right)} } $.
+
+It follows from above that ${\mathscr P_n}$ has $2^{n+1} -2$ facets corresponding to all the non-empty proper subsets of $[0,n]$ for which we have a decomposition $[0,n] = S \sqcup S^c$ and the facets are isomorphic to one of the following product of lower dimensional permutahedra  $ \{ {\mathscr P_{n-1}}, {\mathscr P_{n-2}} \times A_1, \cdots ,{\mathscr P_{\lfloor{n/2 \rfloor}}} \times {\mathscr P_{n-1-\lfloor n/2 \rfloor}}  \} $\footnote {More generally the number of $(n-k)$ facets of ${\mathscr P_n}$ is $ k!
+S(n,k)$ where $S(n,k)$ is the Stirling number of the second kind which counts the number $k$ partitions of  $I$ and there are $p(n+1,k)$ types where $p(n+1,k)$ is the number of $k$ partitions of $(n+1)$.}.
+
+It also follows from above that a face $\pi_{S_1,\cdots,S_k}$ is contained in another face $\pi_{T_1,\cdots,T_l}$ if and only if each $T_i$ is a union of consecutive $S_j$ or equivalently if $(S_1,\cdots,S_k)$ is a refinement of $(T_1,\cdots,T_l)$.
+
+\section*{ABHY like realisation for the Permutahedron}
+The following set of equations to define the $n$-dimensional Permutahedron: 
+\bea
+C_I = (-1)^{|I|} \left( \sum_{i \in I} X_i - \sum _{{i<j}\atop{i,j \in I}} X_{ij} +\cdots + (-1)^{|I|}  X_I \right) \nonumber
+\eea
+for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $X_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.
+
+It is clear that
+\bea
+m= \text{No. of  C's }&=& 2^{n+1}-(n+2) \nonumber \\
+N= \text{No. of X's} &=& 2^{n+1}- 2 \nonumber 
+\eea
+Thus we see that $N= d+m$ as expected. We can write down the stringy integral as usual to be 
+\bea
+\int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} d x_i x_i^{\alpha^{'} X_i -1} \prod_{I} \left (\sum_{a\in I} x_a \right) ^{-\alpha^{'} C_I} \nonumber
+\eea 
+where the product is over all non-singlets $ I \subset \{0,1,\cdots,n\}$ with $x_{0} =1$.
+
+Let us look at the $n=2,3$ examples:
+
+\section*{2d permutahedron}
+In this case the building set $B=\{ \{ 0,1,2\},\{ 0,1\},\{0,2\},\{1,2\},\{0\},\{1\},\{2\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y, ~x_{01}=1+x, ~x_{02}=1+y,~ x_{12}=x+y,~ x_{012}=1+x+y$.
+
+We can write down the Newton polynomial for the Minkowski sum as $ x_1~ x_2~(1+x_1)~(1+x_2)~(x_1+x_2)~(1+x_1+x_2)$.
+
+The $u$-variables can be written in terms of $x$ variables as:
+\bea
+u_1&=&\frac{x(1+x+y)}{(x+y)(1+x)}, ~ u_2 =\frac{y(1+x+y)}{(x+y)(1+y)},~ u_{12}=\frac{(x+y)}{(1+x+y)}\nonumber \\
+u^{'}_1&=&\frac{(1+y)}{(1+x+y)}, ~~~~~ u^{'}_2=\frac{(1+x)}{(1+x+y)},~~~~~ u^{'}_{12}= \frac{(1+x+y)}{(1+x)(1+y)} \nonumber
+\eea
+The $u$-equations are:
+\bea
+1-u_i &=& (u^{'}_i)^2 u_j u^{'}_{12}, ~~~ 1-u_{12} = u^{'}_{1} u^{'}_{2} u^{'}_{12} \nonumber \\
+1-u^{'}_i &=& u_i u^{'}_j u_{12}, ~~~~~~~ 1-u^{'}_{12} = u_{1} u_{2} (u_{12})^2 \nonumber
+\eea
+where $i=1$ implies $j=2$ and vice versa.
+
+\section*{3d permutahedron}
+In this case the building set $B=\{ \{ 0,1,2,3\},\{ 0,1,2\},\{0,2,3\},\{0,1,3\},\{1,2,3\},\{0,1\},\{0,2\},\{0,3\},\{1,2\} \\ ,\{2,3\},\{1,3\},\{0\},\{1\},\{2\},\{3\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y, ~x_3=z, ~x_{01}=1+x, ~x_{02}=1+y,~x_{03}=1+z,~ x_{12}=x+y,~x_{13}=x+z,~x_{23}=y+z,~ x_{012}=1+x+y,~ x_{013}=1+x+z,~ x_{023}=1+y+z,~ x_{123}=x+y+z,~ x_{0123}=1+x+y+z$.
+\\
+
+The $u$ and $u'$-variables can be written interms of $x$ variables as:
+{\scriptsize  \bea
+u_1&=&\frac{x(1+x+y)(1+x+z)(x+y+z)}{(x+y)(x+z)(1+x)(1+x+y+z)}, ~ u_2 =\frac{y(1+x+y)(1+y+z)(x+y+z)}{(x+y)(y+z)(1+y)(1+x+y+z)},~ u_{3}=\frac{z(1+x+z)(1+y+z)(x+y+z)}{(x+z)(y+z)(1+z)(1+x+y+z)},\nonumber \\
+u^{'}_1&=&\frac{(1+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_2 =\frac{(1+x+z)}{(1+x+y+z)},~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_{3}=\frac{(1+x+y)}{(1+x+y+z)},\nonumber \\
+u_{12}&=&\frac{(x+y)(1+x+y+z)}{(1+x+y)(x+y+z)}, ~~~~~~~~~~~~~~~~~~ u_{23} =\frac{(y+z)(1+x+y+z)}{(1+y+z)(x+y+z)},~~~~~~~~~~~~~~~~~~~ u_{13}=\frac{(x+z)(1+x+y+z)}{(1+x+z)(x+y+z)},\nonumber \\
+u^{'}_{12}&=&\frac{(1+z)(1+x+y+z)}{(1+y+z)(1+x+z)}, ~~~~~~~~~~~~~~~~~~ u^{'}_{23} =\frac{(1+x)(1+x+y+z)}{(1+x+y)(1+x+z)},~~~~~~~~~~~~~~~~~~~ u^{'}_{13}=\frac{(1+y)(1+x+y+z)}{(1+x+y))(1+y+z)},\nonumber  \\
+u_{123}&=&\frac{(x+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_{123} =\frac{(1+x+y)(1+y+z)}{(1+x)(1+y)(1+z)(1+x+y+z)}\nonumber
+\eea }
+The $u$-equations in this case are:
+{\small  \bea
+1-u_i &=& u_j u_k (u_{jk})^2 (u^{'}_i)^3 (u^{'}_{ij})^2(u^{'}_{ik})^2 u^{'}_{123} \left(1+ u_i u_{ij} u_{ik} u^{'}_{j} u^{'}_{k}  u^{'}_{jk}\right), ~~ 1-u_{ij} = u_k u_{ik} u_{jk} (u^{'}_i)^2 (u^{'}_{j})^2 (u^{'}_{ij})^2 u^{'}_{ik} u^{'}_{jk} u^{'}_{123} \nonumber  \\
+1-u^{'}_i &=& u_i u_{ij} u_{ik} u^{'}_{j} u^{'}_{k}  u^{'}_{jk}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 1-u^{'}_{ij} = u_i u_{j}  (u_{ij})^2 u_{ik} u_{jk} (u_{123})^2 (u^{'}_{k})^2 u^{'}_{ik} u^{'}_{jk}  \nonumber \\
+1-u^{'}_{123} &=& u_1 u_{2} u_{3} (u_{12})^2 (u_{23})^2  (u_{13})^2 (u_{123})^3 \left(1+ u^{'}_{123}  u^{'}_1 u^{'}_{2} u^{'}_{3} u^{'}_{12} u^{'}_{23}  u^{'}_{13} \right), 1-u_{123} = u^{'}_1 u^{'}_{2} u^{'}_{3} u^{'}_{12} u^{'}_{23}  u^{'}_{13} u^{'}_{123}   \nonumber
+\eea}
+where $i,j,k \in {1,2,3}$ and $i \neq j \neq k$.
+
+The 8 facets of the 3d permutahedron corresponding to $u_i \rightarrow 0, u^{'}_i \rightarrow 0,u_{123} \rightarrow 0 ~and ~u^{'}_{123} \rightarrow 0$  are all $B_2$'s.
+Similarly, the 6 facets corresponding to  $u_{ij} \rightarrow 0, u^{'}_{ij} \rightarrow 0$ are all  $A^{2}_1$.
+
+Thus, the 3d permutahedron integral factorizes nicely on all massless poles at finite $\alpha^{'}$ !!
+We shall list a few results about permutahedra which shall be useful for later purposes: 
+\begin{enumerate}
+\item The $u$-variables for the permutahedron are: 
+\bea
+u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber 
+\eea
+The above relations can also be inverted to obtain $x_I$ as follows:
+
+For $0 \notin I $
+\bea
+x_I &=& \frac{\prod_{I \subset J} u_{J}}{1-\prod_{I \subset J} u_{J}} \\
+\frac{1}{1+ x_I} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}}
+\eea
+From the above relations it is clear that taking $u_I \rightarrow 0$ for $0 \notin I$ implies $x_J \rightarrow 0$ for all $J \subset I$ and taking $u_{\bar{I}} \rightarrow 0$ implies $x_J \rightarrow \infty $ for all $I \subset J$.
+In fact we shall argue that there is unique choice of $x_I$'s which we can take to $0$ or $\infty$ which corresponds to setting only a particular $u_I \rightarrow 0$ or $u_{\bar{I}} \rightarrow 0$ respectively.
+\item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :
+
+% {\bf compatible if} $I\cap J = \emptyset$ or $I\cap J \neq \emptyset$ and either $I \subset J$ or $J \subset I$
+
+% {\bf incompatible if}   $I\cap J \neq \emptyset$ or $I\cap J = \emptyset$ and neither $I \not\subset J$ or $J \not\subset I$
+
+{\bf compatible if and only if} $\{[0,n],I,J\}$ is a nested set, i.e.
+\[
+I\subset J\quad \text{or}\quad J\subset I\quad \text{or}\quad (J\cap I=\varnothing \quad \text{and}\quad J\cup I\not\in \mathscr P_n).
+\]
+For permutohedron, $J\cup I$ is always contained in $\mathscr P_n$ for any $I$ and $J$, so it's compatible if and only if $J\subset I$ or $I\subset J$.
+
+The above  follows directly from the following relations amongst $u$ for each $I$ such that $0\notin I$ :
+\bea
+1-\prod_{I \subset J} u_{J} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}} \\
+1-\prod_{J \subset I} u_{\bar{J}} &=& \prod_{I \subset J} u_{J} \prod_{J \subset \bar{I} } u_{\bar{J}}
+\eea
 

### 2020-04-21 draft_ABP.tex
Updates from Overleaf

@@
 
-(direct proof?)
+(better figure?)
+
+One could use this construction of products to produce any finite product $\mathscr A_{i_1}\times \cdots \times \mathscr A_{i_k}$, and this construction is also valid for any generalized permutahderon.
+The direct proof of this argument for $\mathscr A_n$ is using the global $u$-equations of $\mathscr A_n$. ...
 
@@
 
-degenerations of $B_n$ ...
+The story of degenerations of $B_n$ is very similar. The first thing to do is to find degenerations whose big polytopes are simplices.
 
@@
 \eea
+\end{enumerate}
 

### 2020-04-21 draft_ABP.tex
update

@@
 \[
-S_{[i,i]}=F_{[i,i]},\quad S_{[i,j]}=F_{[i,j]}+F_{[i+1,j-1]}-F_{[i,j-1]}-F_{[i+1,j]}\quad \text{for $i\neq j$},
-\]
-where $F_{[i+1,i]}:=0$. Therefore, the $u$-variables are
+	S_{[i,i]}=F_{[i,i]},\quad S_{[i,j]}=F_{[i,j]}+F_{[i+1,j-1]}-F_{[i,j-1]}-F_{[i+1,j]}\quad \text{for $i\neq j$ and $[i,j]\neq [0,n]$},
+\]
+and
+\[
+	S_{[0,n]}=F_{[0,n]}-\sum_{i=0}^n F_{[i,i-2]} +\sum_{i=0}^n F_{[i,i-3]},
+\]
+where $F_{[i+1,i]}=F_{[0,n]}=0$. Therefore, the $u$-variables are
 \[
@@
 \]
+
+The ABHY construction of $\mathscr B_n$ is similar: $F_{[i,j]}\geq 0$ for all $[i,j]\in\mathbf B$,
+\[
+	F_{[i,j-1]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]}
+	=c_{[i,j]}\,\,\text{for $i\neq j$ and $[i,j]\neq [0,n]$}, \quad 
+\]
+and 
+\begin{equation}\label{abhyB}
+	c_{[0,n]}=\sum_{i=0}^n F_{[i,i-2]}-\sum_{i=0}^n F_{[i,i-3]},
+\end{equation}
+where $F_{[i+1,i]}=0$ and $c$s are all positive constants. We can also
+use a mesh to represent this conditions. For example, the mesh for $\mathscr B_3$
+is 
+\begin{center}
+\begin{tikzpicture}
+	\draw[thick] (-1,-2) node[below]{$0$} -- (2,1);
+	\draw[thick] (-2,-1) -- (-1,-2);
+	\draw[thick] (-1,0) -- (1,-2) node[below]{$0$}-- (4,1);
+	\draw[thick] (2,1) -- (4,-1) -- (5,-2);
+	\draw[thick] (4,1) -- (6,-1);
+	\draw[thick] (5,-2) node[below]{$0$} -- (7,0) -- (6,1) ;
+	\draw[thick] (-2,-1) -- (0,1) -- (2,-1);
+	\draw[thick] (2,-1) -- (3,-2) node[below]{$0$} -- (6,1);
+	\node at (-2.5,-1) {$[0,0]$};
+	\node at (-0.65,-1) {$[1,1]$};
+	\node at (1.35,-1) {$[2,2]$};
+	\node at (3.35,-1) {$[3,3]$};
+	\node at (5.35,-1) {$[0,0]$};
+	\node at (-1.5,0) {$[0,1]$};
+	\node at (0.35,0) {$[1,2]$};
+	\node at (2.35,0) {$[2,3]$};
+	\node at (4.35,0) {$[3,0]$};
+	\node at (6.35,0) {$[0,1]$};
+	\node at (0,1.2) {$[0,2]$};
+	\node at (2,1.2) {$[1,3]$};
+	\node at (4,1.2) {$[2,0]$};
+	\node at (6,1.2) {$[3,1]$};
+\end{tikzpicture}
+\end{center}
+with an additional equation \eqref{abhyB}.
+
+%In order to represent this `strange'
+%condition in the mesh, we add a special layer of diamonds on the mesh, for example,
+%the new mesh for $B_3$ is 
+%\begin{center}
+%\begin{tikzpicture}
+	%\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) node[below]{$0$} -- (0,1);
+	%\draw[thick] (-1,-2) node[below]{$0$} -- (3,2);
+	%\draw[thick] (-2,-1) -- (-1,-2);
+	%\draw[thick] (-1,0) -- (1,-2) node[below]{$0$}-- (5,2);
+	%\draw[thick] (3,2) -- (6,-1) -- (5,-2);
+	%\draw[thick] (5,2) -- (6,1) -- (7,0);
+	%\draw[thick] (4,-1) -- (5,-2) node[below]{$0$} -- (8,1) -- (7,2) -- cycle;
+	%\node at (-2.5,-1) {$[0,0]$};
+	%\node at (-0.65,-1) {$[1,1]$};
+	%\node at (1.35,-1) {$[2,2]$};
+	%\node at (3.35,-1) {$[3,3]$};
+	%\node at (5.35,-1) {$[0,0]$};
+	%\node at (-1.5,0) {$[0,1]$};
+	%\node at (0.35,0) {$[1,2]$};
+	%\node at (2.35,0) {$[2,3]$};
+	%\node at (4.35,0) {$[3,0]$};
+	%\node at (6.35,0) {$[0,1]$};
+	%\node at (-0.5,1) {$[0,2]$};
+	%\node at (1.35,1) {$[1,3]$};
+	%\node at (3.5,1) {$[2,0]$};
+	%\node at (5.5,1) {$[3,1]$};
+	%\node at (7.5,1) {$[0,2]$};
+	%\node at (1,2.2) {$[0]$};
+	%\node at (3,2.2) {$[1]$};
+	%\node at (5,2.2) {$[2]$};
+	%\node at (7,2.2) {$[3]$};
+%\end{tikzpicture}
+%\end{center}
+%each diamond represents a new relation
+%\[
+	%F_{[i,i-2]}+F_{[i+1,i-1]}-2F_{[i+1,i-2]}=2c_{[i]},
+%\]
+%and $\sum_{i=0}^n c_{[i]}=c_{[0,n]}$. (the above equation is meaningless.....)
+
+%Each big diamond gives us an equation
+%\[
+	%\sum_{a\in [i,j-1]\atop{b\in [k+1,l]}} c_{[a,b]} = 
+	%F_{[i,k]}+F_{[j,l]}-F_{[i,l]}-F_{[j,k]}
+%\]
+%where $F_{[i+1,i]}:=0$ and $[i,l],[j,k]\neq [0,n]$.
 
@@
 One could use this construction of products to produce any finite product $\mathscr A_{i_1}\times \cdots \times \mathscr A_{i_k}$, and this construction is also valid for any generalized permutahderon.
-The direct proof of this argument for $\mathscr A_n$ is using the global $u$-equations of $\mathscr A_n$. ...
-
-(Find all with perfect $u$-eq?)
-
-The story of degenerations of $B_n$ is very similar. The first thing to do is to find degenerations whose big polytopes are simplices.
+The direct proof of this argument for $\mathscr A_n$ is using global $u$-equations of $\mathscr A_n$. ...
+
+The story of degenerations of $B_n$ is very similar. 
+% The first thing to do is to find degenerations whose big polytopes are simplices. 
+With the help of the mesh of $\mathscr B_n$, we could get many classes of degenerations with perfect $u$-equations. 
+For example, setting $c_{[i,i+1]}=0$, then
+\[
+	F_{[i,i+1]}=F_{i}+F_{i+1},
+\]
+where $F_i=F_{[i,i]}$, so 
+\[
+	\tilde u_{i}=u_{i} u_{[i,i+1]},\quad 
+	\tilde u_{i+1}=u_{i+1} u_{[i,i+1]},\quad 
+	\tilde u_I=u_I \text{ for the other $I\neq [i,i+1]$}.
+\]
+The $u$-equations of this degeneration are
+\[
+	1-\tilde u_i=\tilde u_{[i+1,i-1]}
+	\prod_{a=i+2}^{i-1}\tilde u_{[a,i-1]}\tilde u_{[i+1,a]},\quad
+	1-\tilde u_{i+1}=
+	\tilde u_{[i+2,i]}\prod_{a=i+2}^{i-1}\tilde u_{[a,i]}\tilde u_{[i+2,a]},
+\]
+and the other $u$-equations are old $u$-equations in terms of new $u$-variables.
+
+A more interesting degeneration is the product $\mathscr B_i\times \mathscr A_{n-i}$.
+In particular,$\mathscr A_n$ is also a degeneration of $\mathscr B_n$.
+
+(Zhenjie: the only known example for me $\mathscr B_3\to \mathscr B_{2}\times \mathscr A_1$: $c_{[i-1,i]}=c_{[i-1,i+1]}=c_{[i,i+2]}=c_{[i+1,i+2]}=0$)
+
+%\begin{center}
+%\begin{tikzpicture}
+	%\draw[thick] (-1,-2) node[below]{$0$} -- (2,1);
+	%\draw[thick] (-2,-1) -- (-1,-2);
+	%\draw[thick] (-1,0) -- (1,-2) node[below]{$0$}-- (4,1);
+	%\draw[thick] (2,1) -- (4,-1) -- (5,-2);
+	%\draw[thick] (4,1) -- (6,-1);
+	%\draw[thick] (5,-2) node[below]{$0$} -- (7,0) -- (6,1) ;
+	%\draw[thick] (-2,-1) -- (0,1) -- (2,-1);
+	%\draw[thick] (2,-1) -- (3,-2) node[below]{$0$} -- (6,1);
+	%\node at (-2.5,-1) {$[0,0]$};
+	%\node at (-0.65,-1) {$[1,1]$};
+	%\node at (1.35,-1) {$[2,2]$};
+	%\node at (3.35,-1) {$[3,3]$};
+	%\node at (5.35,-1) {$[0,0]$};
+	%\node at (-1.5,0) {$[0,1]$};
+	%\node at (0.35,0) {$[1,2]$};
+	%\node at (2.35,0) {$[2,3]$};
+	%\node at (4.35,0) {$[3,0]$};
+	%\node at (6.35,0) {$[0,1]$};
+	%\node at (0,1.2) {$[0,2]$};
+	%\node at (2,1.2) {$[1,3]$};
+	%\node at (4,1.2) {$[2,0]$};
+	%\node at (6,1.2) {$[3,1]$};
+%\end{tikzpicture}
+%\end{center}
 

### 2020-04-21 draft_ABP.tex
Updates from Overleaf

--- 2020-04-21 draft_ABP.tex
@@
 \bea
-C_I = (-1)^{|I|} \left( \sum_{i \in I} X_i - \sum _{{i<j}\atop{i,j \in I}} X_{ij} +\cdots + (-1)^{|I|}  X_I \right) \nonumber
-\eea
-for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $X_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.
+C_I = (-1)^{|I|} \left( \sum_{i \in I} F_i - \sum _{{i<j}\atop{i,j \in I}} F_{ij} +\cdots + (-1)^{|I|}  F_I \right) \nonumber
+\eea
+for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $F_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.
 
@@
 m= \text{No. of  C's }&=& 2^{n+1}-(n+2) \nonumber \\
-N= \text{No. of X's} &=& 2^{n+1}- 2 \nonumber 
+N= \text{No. of F's} &=& 2^{n+1}- 2 \nonumber 
 \eea
@@
 \bea
-\int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} d x_i x_i^{\alpha^{'} X_i -1} \prod_{I} \left (\sum_{a\in I} x_a \right) ^{-\alpha^{'} C_I} \nonumber
+\int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} d x_i x_i^{\alpha^{'} F_i -1} \prod_{I} \left (\sum_{a\in I} x_a \right) ^{-\alpha^{'} C_I} \nonumber
 \eea 
@@
 u_1&=&\frac{x(1+x+y)}{(x+y)(1+x)}, ~ u_2 =\frac{y(1+x+y)}{(x+y)(1+y)},~ u_{12}=\frac{(x+y)}{(1+x+y)}\nonumber \\
-u^{'}_1&=&\frac{(1+y)}{(1+x+y)}, ~~~~~ u^{'}_2=\frac{(1+x)}{(1+x+y)},~~~~~ u^{'}_{12}= \frac{(1+x+y)}{(1+x)(1+y)} \nonumber
+u_{02}&=&\frac{(1+y)}{(1+x+y)}, ~~~~~ u_{01}=\frac{(1+x)}{(1+x+y)},~~~~~ u_{0}= \frac{(1+x+y)}{(1+x)(1+y)} \nonumber
 \eea
@@
 \bea
-1-u_i &=& (u^{'}_i)^2 u_j u^{'}_{12}, ~~~ 1-u_{12} = u^{'}_{1} u^{'}_{2} u^{'}_{12} \nonumber \\
-1-u^{'}_i &=& u_i u^{'}_j u_{12}, ~~~~~~~ 1-u^{'}_{12} = u_{1} u_{2} (u_{12})^2 \nonumber
+1-u_i &=& (u_{0j})^2 u_j u_{0}, ~~~ 1-u_{12} = u_{02} u_{01} u_{0} \nonumber \\
+1-u_{0 j} &=& u_i u_{0 i} u_{12}, ~~~~~~~ 1-u_{0} = u_{1} u_{2} (u_{12})^2 \nonumber
 \eea
@@
 u_1&=&\frac{x(1+x+y)(1+x+z)(x+y+z)}{(x+y)(x+z)(1+x)(1+x+y+z)}, ~ u_2 =\frac{y(1+x+y)(1+y+z)(x+y+z)}{(x+y)(y+z)(1+y)(1+x+y+z)},~ u_{3}=\frac{z(1+x+z)(1+y+z)(x+y+z)}{(x+z)(y+z)(1+z)(1+x+y+z)},\nonumber \\
-u^{'}_1&=&\frac{(1+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_2 =\frac{(1+x+z)}{(1+x+y+z)},~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_{3}=\frac{(1+x+y)}{(1+x+y+z)},\nonumber \\
+u_{023}&=&\frac{(1+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u_{013} =\frac{(1+x+z)}{(1+x+y+z)},~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u_{012}=\frac{(1+x+y)}{(1+x+y+z)},\nonumber \\
 u_{12}&=&\frac{(x+y)(1+x+y+z)}{(1+x+y)(x+y+z)}, ~~~~~~~~~~~~~~~~~~ u_{23} =\frac{(y+z)(1+x+y+z)}{(1+y+z)(x+y+z)},~~~~~~~~~~~~~~~~~~~ u_{13}=\frac{(x+z)(1+x+y+z)}{(1+x+z)(x+y+z)},\nonumber \\
-u^{'}_{12}&=&\frac{(1+z)(1+x+y+z)}{(1+y+z)(1+x+z)}, ~~~~~~~~~~~~~~~~~~ u^{'}_{23} =\frac{(1+x)(1+x+y+z)}{(1+x+y)(1+x+z)},~~~~~~~~~~~~~~~~~~~ u^{'}_{13}=\frac{(1+y)(1+x+y+z)}{(1+x+y))(1+y+z)},\nonumber  \\
-u_{123}&=&\frac{(x+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_{123} =\frac{(1+x+y)(1+y+z)}{(1+x)(1+y)(1+z)(1+x+y+z)}\nonumber
+u_{03}&=&\frac{(1+z)(1+x+y+z)}{(1+y+z)(1+x+z)}, ~~~~~~~~~~~~~~~~~~ u_{01} =\frac{(1+x)(1+x+y+z)}{(1+x+y)(1+x+z)},~~~~~~~~~~~~~~~~~~~ u_{02}=\frac{(1+y)(1+x+y+z)}{(1+x+y))(1+y+z)},\nonumber  \\
+u_{123}&=&\frac{(x+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~ u_{0} =\frac{(1+x+y)(1+y+z)}{(1+x)(1+y)(1+z)(1+x+y+z)}\nonumber
 \eea }
@@
 {\small  \bea
-1-u_i &=& u_j u_k (u_{jk})^2 (u^{'}_i)^3 (u^{'}_{ij})^2(u^{'}_{ik})^2 u^{'}_{123} \left(1+ u_i u_{ij} u_{ik} u^{'}_{j} u^{'}_{k}  u^{'}_{jk}\right), ~~ 1-u_{ij} = u_k u_{ik} u_{jk} (u^{'}_i)^2 (u^{'}_{j})^2 (u^{'}_{ij})^2 u^{'}_{ik} u^{'}_{jk} u^{'}_{123} \nonumber  \\
-1-u^{'}_i &=& u_i u_{ij} u_{ik} u^{'}_{j} u^{'}_{k}  u^{'}_{jk}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 1-u^{'}_{ij} = u_i u_{j}  (u_{ij})^2 u_{ik} u_{jk} (u_{123})^2 (u^{'}_{k})^2 u^{'}_{ik} u^{'}_{jk}  \nonumber \\
-1-u^{'}_{123} &=& u_1 u_{2} u_{3} (u_{12})^2 (u_{23})^2  (u_{13})^2 (u_{123})^3 \left(1+ u^{'}_{123}  u^{'}_1 u^{'}_{2} u^{'}_{3} u^{'}_{12} u^{'}_{23}  u^{'}_{13} \right), 1-u_{123} = u^{'}_1 u^{'}_{2} u^{'}_{3} u^{'}_{12} u^{'}_{23}  u^{'}_{13} u^{'}_{123}   \nonumber
+1-u_i &=& u_j u_k (u_{jk})^2 (u_{0jk})^3 (u_{0k})^2(u_{0 j})^2 u_{0} \left(1+ u_i u_{ij} u_{ik} u_{0ik} u^_{0ij}  u_{0i}\right),  1-u_{ij} = u_k u_{ik} u_{jk} (u_{0jk})^2 (u_{0ik})^2 (u_{0 k})^2 u_{0 j} u_{0 i} u_{0} \nonumber  \\
+1-u_{0 j k} &=& u_i u_{ij} u_{ik} u_{0 i k} u_{0 i j}  u_{0 i}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 1-u_{0 k} = u_i u_{j}  (u_{ij})^2 u_{ik} u_{jk} (u_{123})^2 (u_{0 i j})^2 u_{0 j} u_{0 i}  \nonumber \\
+1-u_{0} &=& u_1 u_{2} u_{3} (u_{12})^2 (u_{23})^2  (u_{13})^2 (u_{123})^3 \left(1+ u_{0}  u_{023} u_{013} u_{012} u_{03} u_{01}  u_{02} \right), 1-u_{123} = u_{023} u_{013} u_{012} u_{03} u_{01}  u_{02} u_{0}   \nonumber
 \eea}
@@
 
-The 8 facets of the 3d permutahedron corresponding to $u_i \rightarrow 0, u^{'}_i \rightarrow 0,u_{123} \rightarrow 0 ~and ~u^{'}_{123} \rightarrow 0$  are all $B_2$'s.
-Similarly, the 6 facets corresponding to  $u_{ij} \rightarrow 0, u^{'}_{ij} \rightarrow 0$ are all  $A^{2}_1$.
+The 8 facets of the 3d permutahedron corresponding to $u_i \rightarrow 0, u_{0jk} \rightarrow 0,u_{123} \rightarrow 0 ~and ~u_{0} \rightarrow 0$  are all $B_2$'s.
+Similarly, the 6 facets corresponding to  $u_{ij} \rightarrow 0, u_{0k} \rightarrow 0$ are all  $A^{2}_1$.
 
@@
 
-In this section we shall try to argue that the permutahedron is a binary geometry. We shall first summarise the following facts about the permutahedron:
-\begin{enumerate}
-\item The $u$-variables for the permutahedron are: 
-\bea
-u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber 
-\eea
-The above relations can also be inverted to obtain $x_I$ as follows:
-
-For $0 \notin I $
-\bea
-x_I &=& \frac{\prod_{I \subset J} u_{J}}{1-\prod_{I \subset J} u_{J}} \\
-\frac{1}{1+ x_I} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}}
-\eea
-From the above relations it is clear that taking $u_I \rightarrow 0$ for $0 \notin I$ implies $x_J \rightarrow 0$ for all $J \subset I$ and taking $u_{\bar{I}} \rightarrow 0$ implies $x_J \rightarrow \infty $ for all $I \subset J$.
-In fact we shall argue that there is unique choice of $x_I$'s which we can take to $0$ or $\infty$ which corresponds to setting only a particular $u_I \rightarrow 0$ or $u_{\bar{I}} \rightarrow 0$ respectively.
-\item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :
-
-% {\bf compatible if} $I\cap J = \emptyset$ or $I\cap J \neq \emptyset$ and either $I \subset J$ or $J \subset I$
-
-% {\bf incompatible if}   $I\cap J \neq \emptyset$ or $I\cap J = \emptyset$ and neither $I \not\subset J$ or $J \not\subset I$
-
-{\bf compatible if and only if} $\{[0,n],I,J\}$ is a nested set, i.e.
-\[
-I\subset J\quad \text{or}\quad J\subset I\quad \text{or}\quad (J\cap I=\varnothing \quad \text{and}\quad J\cup I\not\in \mathscr P_n).
-\]
-For permutohedron, $J\cup I$ is always contained in $\mathscr P_n$ for any $I$ and $J$, so it's compatible if and only if $J\subset I$ or $I\subset J$.
-
-The above  follows directly from the following relations amongst $u$ for each $I$ such that $0\notin I$ :
-\bea
-1-\prod_{I \subset J} u_{J} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}} \\
-1-\prod_{J \subset I} u_{\bar{J}} &=& \prod_{I \subset J} u_{J} \prod_{J \subset \bar{I} } u_{\bar{J}}
-\eea
-
-% Thus, each $u_I$ is compatible with itself and incompatible with $u^{'}_I$.
-
-\item  Since, the permutahedron is permutation invariant in all $x_i$'s this should be reflected at the level of $u$'s and this is indeed the case as $u_I$ with the same $|I|$ have similar $u$'s.
+In this section we shall try to argue that the permutahedron is a binary geometry.
+
+Since, the permutahedron is permutation invariant in all $x_i$'s this should be reflected at the level of $u$'s and this is indeed the case as $u_I$ with the same $|I|$ have similar $u$'s.
 i.e $u_J$ can be obtained from $u_I$ for $|J|=|I|$ by interchange of some of the $x_i$'s.
@@
 
-\end{enumerate}
-
-\section*{Permutahedron}
- For $x_1,x_2, \cdots, x_{n+1} \in \mathbb{R} $ , the permutahedron $P_n(x_1,\cdots,x_{n+1})$ is a convex polytope in $\mathbb{R}^{n+1}$ defined as the convex hull of all vectors obtained from $(x_1,x_2, \cdots, x_{n+1})$ by permutations of the coordinates:
- \bea
- P_n(x_1,x_2, \cdots, x_{n+1}) = ConvexHull \{ (x_{w(1)},x_{w(2)}, \cdots, x_{w(n+1)})~ |~ w \in S_{n+1} \}, \nonumber
- \eea
- where $S_{n+1}$ is the symmetric group.
-
- The permutahedron has $(n+1)!$ vertices and is of dimension at most $n$ since it lies in the hyperplane 
- \bea
- H_c= \{(t_1,t_2, \cdots, t_{n+1}) | t_1 + t_2 + \cdots + t_{n+1}= c \} \subset \mathbb{R}^{n+1}, \nonumber
- \eea
-where $c= x_1+x_2+ \cdots +x_{n+1}$
-
-For $n=2$ and distinct $x_1,x_2, x_3$ the permutahedron $P_2(x_1,x_2, x_3)$ is a hexagon.
-If two of the $x_i$'s are equal then the permutahedron degenerates into a triangle and if $x_1= x_2 = x_3$ then its degenerates into a single point.
-
-We shall state a few results about permutahedra:
-
-{\bf Rado's theorem}: For any $x_1 \ge x_2  \cdots \ge x_{n+1}$ a point $(t_1,t_2, \cdots, t_{n+1}) \in \mathbb{R}^{n+1}$ belongs to the permutahedron $P_n(t_1,t_2, \cdots, t_{n+1})$ if and only if 
-\bea
-t_1+ \cdots +t_{n+1} = x_1 +\cdots+ x_{n+1} \nonumber
-\eea
-and for any nonemepty subset $\{i_1,\cdots,i_k \} \subset \{1,\cdots, n+1 \}$, we have 
-\bea
-t_{i_1}+ \cdots +t_{i_k} \leq x_1 +\cdots+ x_k \nonumber
-\eea
-The combinatorial structure of the permutahedron $P_n (x_1, \cdots, x_{n+1}) $ does not depend on $ x_1, \cdots, x_{n+1} $ as long as all these are distinct.
-
-{\bf Proposition 2}: For any  $x_1> \cdots > x_{n+1} $.
-The $d$-dimensional faces of $P_n ( x_1, \cdots, x_{n+1 })$ are in one-to-one correspondence with the disjoint subdivisions of the corresponding set $\{x_1,\cdots, x_{n+1 }\}$ into nonempty ordered blocks $B_1 \cup B_2 \cup \cdots \cup B_{n+1-d} =\{1,\cdots,n+1 \}$.
-The face corresponding to $B_1,\cdots, B_{n+1-d}$ is given by the $n+1-d$ linear equations
-\bea
-\sum_{i \in B_1\cup \cdots \cup B_k} t_i = x_1 + \cdots +x_{| B_1 \cup \cdots \cup B_k |}, ~~~ for~ k=1,\cdots,n+1-d \nonumber
-\eea 
-\section*{Generalized permutahedra}
-Generalized permutahedra are polytopes which are deformations of the usual permutahedron i.e., obtained by moving the vertices of the usual permutahedron so that the directions of all the edges are preserved though some of the edges may degenerate into points.
-
- Since each generalised permutahedron is obtained by parallel translation of facets of the usual permutahedron it is parametrized  by a collection $\{ z_I\}$ of $2^{n+1}-1$ coordinates, for non-empty sets of $I \subset [n+1] := \{1,\cdots,n+1 \}$
- \bea
- P_n^z(\{ z_I \}) = \left \{ (t_1, t_2, \cdots , t_{n+1}) \in \mathbb{R}^{n+1} | \sum_{i=1}^{n+1} t_i = z_{[n+1]},~ \sum_{i \in I} t_i \geq z_I, ~for ~subsets~ I  \right  \} \nonumber
- \eea
-
- If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron.
-
- A different construction of the generalised permutahedron is the following :
-
- Let, $\Delta_{[n+1]} = ConvexHull(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$.
-For any $I \subset [n+1] $ let $\Delta_I =ConvexHull(e_i~|~i\in I)$ denote the face of the $\Delta_{[n+1]}$.
-The polytope $P_n^y(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I \geq 0$ for all nonempty subsets $I \subset [n+1]$
- \bea
- P_n^y(\{y_I \})= \sum_{I \subset[n+1]} y_I . \Delta_I  \nonumber
- \eea
-is the generalised permutahedron $P_n^z(\{z_I \})$  provided $z_I = \sum_{J \subset I} y_J  ~ for ~all~nonempty ~I \subset [n+1]$.
-Note that all generalised permutahedra cannot be written as Minkowski sum of coordinate simplices and we shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation.
-\section*{Nested Complex}
-Since the combinatorial structure of the generalised permutahedron depends only on the set $B$ of nonemepty subsets $I \subset [n+1]$ such that $y_I \geq 0$ which is called the {\it building set}.
-We can describe the combinatorial structure when $B$ additionally satisfies the following:
-
-\noindent(1) If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$. \\
-(2) $B$ contains all singletons $\{ i\}$ for $i \in S$.
-
-A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:\\
+\section*{A degeneration of ${\mathescr P_n}$ with perfect $u$-equations}
+We can also consider general Minkowski sums of non-simplices and see if these also give us any instance of polytopes with perfect $u$ equations. One such case is the following:
+
+We consider the Minkowski sum of $n-1$ $A_2$'s with following Newton polynomial :
+\bea \label {new}
+\prod_{i=1}^{n} (1+x_i ) \prod_{i=1}^{n-1} (1+x_i +x_i x_{i+1}) 
+\eea 
+This gives a family of simple $n$-dimensional polytopes with $3n-1$ facets  and Pell number $P_n$ (~recursively defined as $ P_n=2 P_{n-1} +P_{n-2}$ with $P_1=1,~ P_2=2$) of vertices which we shall call $X_n$.
+
+We can solve for $u$-variables for this family and we get :
+\bea
+u_1 &=& \frac{p_n}{q_n}, ~u_2 = \frac{p_{n-1}q_n}{p_{n-1,n}},~u_3 = \frac{p_{n-2}q_{n-1}}{p_{n-2,n-1}}, \cdots,
+u_{n-2} = \frac{p_1 q_2}{p_{12}}, ~u_{n-1} = \frac{p_{2}q_3}{p_{23}},~u_n = \frac{p_{3}q_{4}}{p_{34}}, \nonumber \\
+u_{n+1} &=& \frac{1}{q_1}, ~u_{n+2} = \frac{p_{12}}{q_{1}q_{2}},~u_{n+3} = \frac{q_{1}}{p_{23}}, \cdots,
+u_{3n-1} = \frac{ q_{n-1}}{p_{n-1n}} \nonumber
+\eea
+where $p_i =x_i$, $q_i= 1+x_i$ and $p_{i~i+1}=1+x_i+ x_i x_{i+1}$.
+
+The $u$ equations obtained from these $u$ variables are of three types viz. $1-u$ being the product of two, three or four $u$'s  for any $n$.
+
+There are exactly 4 $u$'s which have $1-u$ is product of 2 u's:
+\bea
+1-u_{1} =u_{3n-2} u_{3n-1},~
+1-u_{n-2} =u_{n+1} u_{n+3},~
+1-u_{n+1} =u_{n-2} u_{n+2},~
+1-u_{3n-1} = \begin{cases}
+u_{2} u_{3} , n=3\\
+u_{1} u_{4} , n=4\\
+u_{1} u_{2} , n\geq 5
+\end{cases} \nonumber 
+\eea
+The facets corresponding to setting any of these $u \to 0$ is $X_{n-1}$.
+
+There are exactly $n-3$ $u$'s which have $1-u$ is product of 4 u's:
+\bea
+1-u_{n+4} =u_{n} u_{n+2}u_{n+4} u_{n+6} ~~and~~
+1-u_{n+6+ 2 i} =u_{n-3-i} u_{n+4+2 i} u_{n+5+2 i} u_{n+8+2 i}~ for~i=0,\cdots,(n-5) \nonumber 
+\eea
+The facets corresponding to setting any of these $u \to 0$ is $A^{m}_1 \times X_{n-m-1}$.
+
+All the other $2n-2$ $u$'s correspond to $1-u$ is product of 3 u's and we do not yet have a complete classification of the facets.
+
+We can also replace the first the first term in the Newton polynomial \eqref{ new} with $(1+x_1+ x_2)$ and we get an identical system of $u$-equations
+
+\bea
+u_1 &=& \frac{p_n}{q_n}, ~u_2 = \frac{p_{n-1}q_n}{p_{n-1,n}},~u_3 = \frac{p_{n-2}q_{n-1}}{p_{n-2,n-1}}, \cdots,
+u_{n-3} = \frac{p_4 q_5}{p_{45}}, ~u_{n-2} = \frac{p_{1}}{q_{1}},~u_{n-1} = \frac{p_{2}q_{3}}{p_{23}},~u_{n} = \frac{p_{3}q_{4}}{p_{34}}, \nonumber \\
+u_{n+1} &=& \frac{q_2}{p_{12}}, ~u_{n+2} = \frac{q_{1}}{p_{12}},~u_{n+3} = \frac{p_{23}}{q_{2}q_{3}}, \cdots,
+u_{3n-1} = \frac{ p_{12}}{q_{1}q_{2}} \nonumber
+\eea
+where $p_i =x_i$, $q_i= 1+x_i$ and $p_{i~i+1}=1+x_i+ x_i x_{i+1}$ with $p_{12}= 1+x_1+x_2$.
+
+The $u$ equations obtained from these $u$ variables are of three types viz. $1-u$ being the product of two, three or four $u$'s  for any $n$.
+
+There are exactly 4 $u$'s which have $1-u$ is product of 2 u's:
+\bea
+1-u_{1} =u_{3n-2} u_{3n-3},~
+1-u_{n-2} =u_{n+1} u_{3n-1},~
+1-u_{n+1} =u_{n-2} u_{n+2},~
+1-u_{3n-1} = \begin{cases}
+u_{2} u_{3} , n=3\\
+u_{1} u_{4} , n=4\\
+u_{1} u_{2} , n\geq 5
+\end{cases} \nonumber 
+\eea
+The facets corresponding to setting any of these $u \to 0$ is $X_{n-1}$.
+
+There are exactly $n-3$ $u$'s which have $1-u$ is product of 4 u's:
+\bea
+1-u_{n+3} =u_{n} u_{n+2}u_{n+5} u_{3n-1} ~~and~~
+1-u_{n+5+ 2 i} =u_{n-3-i} u_{n+3+2 i} u_{n+4+2 i} u_{n+7+2 i}~ for~i=0,\cdots,(n-5) \nonumber 
+\eea
+It would be nice to see if these also correspond to some degeneration of the associahedron or if they  are generalised permutahedra.
+
+\newpage
+\section{Discussions}
+There are several interesting open questions, like the question of  whether degenerations of other cluster types (in particular $C_n$ and $D_n$ can also give binary geometries with (perfect?) $u$-equations.\\\\
 \noindent
-(1) For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.\\
-(2) For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B. \\
-(3) N contains all maximal elements of $B$.
-
-The {\it nested complex} $\mathcal{N}(B)$ is defined as the poset of the set of all nested sets in $B$ ordered by inclusion.
-
-{\bf Theorem 1}: Let us assume that the set $B$ associated with a generalised permutahedron $P_n^{y}$ is a building set on $[n+1]$.
-Then the poset of faces $P_n^{y}$ ordered by reverse inclusion is isomorphic to the nested complex $\mathcal{N}(B)$.
-
-{\bf Theorem 2}: Let us assume that the set $B$ associated with a generalised permutahedron $P_n^{y}$ is a building set on $[n+1]$.
-The face $P_N$ of $P_n^{y}(y_I)$ associated with the nested set $N \in \mathcal{N}(B)$ is given by:
-\bea
-P_N = \left \{ \right (t_1,\cdots,t_{n+1}) \in \mathbb{R}^{n+1} | \sum_{i \in I} t_i =y_{I}~for~I \in N; ~ \sum_{i \in J}t_i \geq y_J, for J \in B  )\}
-\eea
-In particular the dimension of the face $P_N$ equals $n+1-|N|$.
-
-In summary the above results imply that we can look at any collection of subsets of $[n+1]$ which form a building set $B$ and associate  coordinate simplex $\Delta_I$ for each $I \in B$ and resulting Minkowski sum with positive weights $y_I$ generates a generalised permutahedron associated with the building set.
-Further, the number of facets of the generalised permutahedron just correspond to the set of all non-singlet elements in $B$.
-We shall use $ \{0,1,\cdots,n \}$ instead of $[n+1]$ with $x_0 =1$ from now on. Since, the number of singlets correspond to the dimension of the generalised permutahedron this implies that:
-
-{\bf Number of facets = Number of linear equation + dimension of  gen permutahedron}
-
-Thus, generalised permutahedra have "Big Polytope" which correspond to a simplex and we can write down the stringy canonical forms and solve for the $u$-variables and examine if they satisfy some kind of $u$-equations.
-
-Here are some interesting examples of generalised permutahedra:
-
-(1) If $B$ consists of only singlets i.e., $B=\{ \{ 0,1,\cdots,n \}, \{ 0 \},\{ 1 \},\cdots ,\{ n \} \}$ then the generalised permutahedron is a Simplex.
-In this case the relevant $x$ variables are $x_i,~ i=0,\cdots,n$ and $\sum_{i=0}^n x_i$.
-The Newton polytope of the Minkowski sum is $\prod_{i=1}^{n} x_i (1+\sum_{j=1}^{n} x_j)$ and $u$-variables are 
-$u_i =\frac{ x_i}{1+\sum_{i=1}^n x_i} $
-which satisfy $\sum u_i =1$ as their only $u$-equation. \\
-
-(2) If $B= \{[i] | i=1,\cdots,n+1 \}$ is the complete flag of intervals, then $P_n({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
-The Newton polytope of the Minkowski sum is $x_1\cdots x_n (1+x_1) \cdots (1+x_1+\cdots +x_n)$ and $u$-variables are 
-$u_i =\frac{ 1}{1+\sum_{j=1}^{i} x_j} $, ~~$u^{'}_i =\frac{ \sum_{j=1}^{i} x_j}{1+\sum_{j=1}^{i} x_j} $ for $j=1,\cdots,n$ \\
-which satisfy $u_i +u^{'}_{i} =1$ as their $u$-equation. \\
-
-(3) If $B$ corresponds to all the non empty subsets of $\{0,1,\cdots,n \}$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then $P_n({\bf Y})$ is the usual permutahedron $P_n$.
-
-\section*{ABHY like realisation for the Permutahedron}
-The following set of equations to define the $n$-dimensional Permutahedron: 
-\bea
-C_I = (-1)^{|I|} \left( \sum_{i \in I} X_i - \sum _{{i<j}\atop{i,j \in I}} X_{ij} +\cdots + (-1)^{|I|}  X_I \right) \nonumber
-\eea
-for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $X_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.
-
-It is clear that
-\bea
-m= \text{No. of  C's }&=& 2^{n+1}-(n+2) \nonumber \\
-N= \text{No. of X's} &=& 2^{n+1}- 2 \nonumber 
-\eea
-Thus we see that $N= d+m$ and hence the "Big polytope" in this case is again a simplex. We can write down the stringy integral as usual to be 
-\bea
-\int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} d x_i x_i^{\alpha^{'} X_i -1} \prod_{I} \left (\sum_{a\in I} x_a \right) ^{-\alpha^{'} C_I} \nonumber
-\eea 
-where the product is over all non-singlets $ I \subset \{0,1,\cdots,n\}$ with $x_{0} =1$.
-
-We can then solve for the corresponding $u's$ :
-\bea
-u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber \\
-u^{'}_J &=& \prod_{{0 \in I}\atop{ \{0,\cdots,n\} - I \subset J}} x_I^{(-1)^{|I|-|J|+\color{red}{mod(n, 2)}}} \nonumber
-\eea
-
-\section*{2d permutahedron}
-In this case the building set $B=\{ \{ 0,1,2\},\{ 0,1\},\{0,2\},\{1,2\},\{0\},\{1\},\{2\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y, ~x_{01}=1+x, ~x_{02}=1+y,~ x_{12}=x+y,~ x_{012}=1+x+y$.
-
-We can write down the Newton polynomial for the Minkowski sum as $ x_1~ x_2~(1+x_1)~(1+x_2)~(x_1+x_2)~(1+x_1+x_2)$.
-
-The $u$-variables can be written in terms of $x$ variables as:
-\bea
-u_1&=&\frac{x(1+x+y)}{(x+y)(1+x)}, ~ u_2 =\frac{y(1+x+y)}{(x+y)(1+y)},~ u_{12}=\frac{(x+y)}{(1+x+y)}\nonumber \\
-u^{'}_1&=&\frac{(1+y)}{(1+x+y)}, ~~~~~ u^{'}_2=\frac{(1+x)}{(1+x+y)},~~~~~ u^{'}_{12}= \frac{(1+x+y)}{(1+x)(1+y)} \nonumber
-\eea
-The $u$-equations are:
-\bea
-1-u_i &=& (u^{'}_i)^2 u_j u^{'}_{12}, ~~~ 1-u_{12} = u^{'}_{1} u^{'}_{2} u^{'}_{12} \nonumber \\
-1-u^{'}_i &=& u_i u^{'}_j u_{12}, ~~~~~~~ 1-u^{'}_{12} = u_{1} u_{2} (u_{12})^2 \nonumber
-\eea
-where $i=1$ implies $j=2$ and vice versa.
-Let us look at the $n=3$ example.
-
-\section*{3d permutahedron}
-In this case the building set $B=\{ \{ 0,1,2,3\},\{ 0,1,2\},\{0,2,3\},\{0,1,3\},\{1,2,3\},\{0,1\},\{0,2\},\{0,3\},\{1,2\} \\ ,\{2,3\},\{1,3\},\{0\},\{1\},\{2\},\{3\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y, ~x_3=z, ~x_{01}=1+x, ~x_{02}=1+y,~x_{03}=1+z,~ x_{12}=x+y,~x_{13}=x+z,~x_{23}=y+z,~ x_{012}=1+x+y,~ x_{013}=1+x+z,~ x_{023}=1+y+z,~ x_{123}=x+y+z,~ x_{0123}=1+x+y+z$.
-\\
-
-The $u$ and $u'$-variables can be written interms of $x$ variables as:
-{\scriptsize  \bea
-u_1&=&\frac{x(1+x+y)(1+x+z)(x+y+z)}{(x+y)(x+z)(1+x)(1+x+y+z)}, ~ u_2 =\frac{y(1+x+y)(1+y+z)(x+y+z)}{(x+y)(y+z)(1+y)(1+x+y+z)},~ u_{3}=\frac{z(1+x+z)(1+y+z)(x+y+z)}{(x+z)(y+z)(1+z)(1+x+y+z)},\nonumber \\
-u^{'}_1&=&\frac{(1+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_2 =\frac{(1+x+z)}{(1+x+y+z)},~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_{3}=\frac{(1+x+y)}{(1+x+y+z)},\nonumber \\
-u_{12}&=&\frac{(x+y)(1+x+y+z)}{(1+x+y)(x+y+z)}, ~~~~~~~~~~~~~~~~~~ u_{23} =\frac{(y+z)(1+x+y+z)}{(1+y+z)(x+y+z)},~~~~~~~~~~~~~~~~~~~ u_{13}=\frac{(x+z)(1+x+y+z)}{(1+x+z)(x+y+z)},\nonumber \\
-u^{'}_{12}&=&\frac{(1+z)(1+x+y+z)}{(1+y+z)(1+x+z)}, ~~~~~~~~~~~~~~~~~~ u^{'}_{23} =\frac{(1+x)(1+x+y+z)}{(1+x+y)(1+x+z)},~~~~~~~~~~~~~~~~~~~ u^{'}_{13}=\frac{(1+y)(1+x+y+z)}{(1+x+y))(1+y+z)},\nonumber  \\
-u_{123}&=&\frac{(x+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~ u^{'}_{123} =\frac{(1+x+y)(1+y+z)}{(1+x)(1+y)(1+z)(1+x+y+z)}\nonumber
-\eea }
-The $u$-equations in this case are:
-{\small  \bea
-1-u_i &=& u_j u_k (u_{jk})^2 (u^{'}_i)^3 (u^{'}_{ij})^2(u^{'}_{ik})^2 u^{'}_{123} \left(1+ u_i u_{ij} u_{ik} u^{'}_{j} u^{'}_{k}  u^{'}_{jk}\right), ~~ 1-u_{ij} = u_k u_{ik} u_{jk} (u^{'}_i)^2 (u^{'}_{j})^2 (u^{'}_{ij})^2 u^{'}_{ik} u^{'}_{jk} u^{'}_{123} \nonumber  \\
-1-u^{'}_i &=& u_i u_{ij} u_{ik} u^{'}_{j} u^{'}_{k}  u^{'}_{jk}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 1-u^{'}_{ij} = u_i u_{j}  (u_{ij})^2 u_{ik} u_{jk} (u_{123})^2 (u^{'}_{k})^2 u^{'}_{ik} u^{'}_{jk}  \nonumber \\
-1-u^{'}_{123} &=& u_1 u_{2} u_{3} (u_{12})^2 (u_{23})^2  (u_{13})^2 (u_{123})^3 \left(1+ u^{'}_{123}  u^{'}_1 u^{'}_{2} u^{'}_{3} u^{'}_{12} u^{'}_{23}  u^{'}_{13} \right), 1-u_{123} = u^{'}_1 u^{'}_{2} u^{'}_{3} u^{'}_{12} u^{'}_{23}  u^{'}_{13} u^{'}_{123}   \nonumber
-\eea}
-where $i,j,k \in {1,2,3}$ and $i \neq j \neq k$.
-
-The 8 facets of the 3d permutahedron corresponding to $u_i \rightarrow 0, u^{'}_i \rightarrow 0,u_{123} \rightarrow 0 ~and ~u^{'}_{123} \rightarrow 0$  are all $B_2$'s.
-Similarly, the 6 facets corresponding to  $u_{ij} \rightarrow 0, u^{'}_{ij} \rightarrow 0$ are all  $A^{2}_1$.
-
-Thus, the 3d permutahedron integral factorizes nicely on all massless poles at finite $\alpha^{'}$ !!
+Though many examples of degenerations of $A_n$ and $B_n$ were products of lower dimensional objects of the same type, there were examples where we got non-trivial degenerations which did not factor.
+We would like to completely classify these cases and this would settle the question of identifying all the ``atoms'' of binary geometries with perfect $u$-equations.
+One class of examples which is certainly of both mathematical and physical interest in this context are the Stokes polytopes (and more generally Accordiohedra).
+
+\section{Appendix}
+
 \section*{4d permutahedron}
@@
 
-\section*{Associahedra}
-If $B=\{ \{i,i+1,\cdots,j \} | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then $P_n({\bf Y})$ is the associahedron .
-\section*{2d associahedron as generalized permutahedron}
-In this case the building set $B=\{ \{ 0,1,2\},\{ 0,1\},\{1,2\},\{0\},\{1\},\{2\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y, ~x_{01}=1+x,~ x_{12}=x+y,~ x_{012}=1+x+y$.
-
-We can write down the Newton polynomial for the Minkowski sum as $ x_1~ x_2~(1+x_1)~(x_1+x_2)~(1+x_1+x_2)$.
-
-The $u$-variables can be written in terms of $x$ variables as:
-\bea
-u_1=\frac{x
-   (x+y+1)}{(x+1)
-   (x+y)},u_2=\frac{x +y}
-   {x+y+1},u_3=\frac{y}{x+y},u_4=\frac{x+1}{x+y+1},u_5=\frac{1}{x+1} \nonumber
-\eea
-The $u$-equations are:
-\bea
-1-u_1=u_3 u_5,1-u_2=u_4
-   u_5,1-u_3=u_1 u_4,1-u_4=u_2
-   u_3,1-u_5=u_1 u_2 \nonumber
-\eea
-Notice that these are precisely the $u$ equations for the ABHY realisation of $A_2$.
-\section*{3d associahedron as generalized permutahedron}
-In this case the building set $B=\{ \{ 0,1,2,3\},\{ 0,1,2\},\{1,2,3\},\{0,1\},\{1,2\},\{2,3\},\{0\},\{1\},\{2\},\{3\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y,~x_3 =y, ~x_{01}=1+x,~ x_{12}=x+y,~x_{23}=y+z,~ x_{012}=1+x+y,~ x_{123}=x+y+z,~ x_{0123}=1+x+y+z$.
-
-We can write down the Newton polynomial for the Minkowski sum as $ x_1~ x_2~x_3~(1+x_1)~(x_1+x_2)~(x_2+x_3)~(1+x_1+x_2)~(x_1+x_2+x_3)~(1+x_1+x_2+x_3)$. \\
-
-The $u$-variables can be written in terms of $x$ variables as:
-{\scriptsize \bea
-u_1&=&\frac{x
-   (x+y+1)}{(x+1)
-   (x+y)},~u_2=\frac{(x+y
-   )
-   (x+y+ z+1)}{(x+y+1)
-   (x+ y+z)},~u_3=\frac{x+
-   y+ z}{x+y+z +1},~u_4=
-   \frac{y}{x+z},\nonumber \\ u_5&=&\frac{
-   y
-   (x+y+z)}{(x+y)
-   (y+z)},~u_6= \frac{y+z}
-   {x+y+z},u_7=\frac{x+y+1}{x+y+z+1},u_8=\frac{x+1}{x+y+1},u_9=\frac{
-   1}{x+1} \nonumber
-   \eea}
-   and satisfy the $u$-equations 
-   \bea
-   1-u_1&=&u_5 u_6 u_9,~1-u_2=u_4
-   u_6 u_8 u_9,~1-u_3=u_7 u_8
-   u_9,~1-u_4=u_2 u_5 u_7, \nonumber \\ 1-u_5&=&u_1
-   u_4 u_8,1-u_6=u_1 u_2 u_7
-   u_8,1-u_7=u_3 u_4 u_6,1-u_8=u_2
-   u_3 u_5 u_6,1-u_9=u_1 u_2
-   u_3 \nonumber
-   \eea
-  We see again that these are precisely the $u$ equations of ABHY realisation of $A_3$ !
-
-This is not a coincidence and it extends to all $n$ since the corresponding Newton polytope is given by $\prod_{1\leq  i \leq j \leq n} (x_i +x_{i+1}+\cdots+x_j)$ is nothing but the Loday's realisation of the associahedron which is equivalent to the ABHY type $A_n$ associahedron.
-
-Thus remarkably both the generalised permutahedron realisation and ABHY realisation of the associahedra $A_n$ are  the same. \\
-\section*{Cyclohedra}
-If $B$  is the set of cyclic intervals, then $P_n({\bf Y})$ is a cyclohedron.
-\section*{3d cyclohedron}
-The 2d cyclohedron is the same as the 2d permutahedron as they both have the same building sets.
-
- Let us look at the 3d case. In this case the building set $B=\{ \{ 0,1,2,3\},\{ 0,1,2\},\{1,2,3\},\{2,3,0\},\{3,0,1\}, \\  \{0,1\},\{1,2\},\{2,3\},\{0,3\},\{0\},\{1\},\{2\},\{3\}\}$.
-
- The Newton polynomial of the Minkowski sum is $x y z(1+x)(x+y)(y+z)(1+z)(1+x+y)(x+y+z)(y+z+1)(z+1+x)(1+x+y+z)$ and
-
- we  find the relevant $u$'s as:
-\bea
-u_1 &=&\frac{x (x+y+1)}{(x+1) (x+y)},~u_2 = \frac{(x+y) (x+y+z+1)}{(x+y+1) (x+y+z)},~u_3 = \frac{x+y+z}{x+y+z+1},~~~~~~~~~~~~~~u_4= \frac{z
-   (y+z+1)}{(z+1) (y+z)}, \nonumber \\
-   u_5 &=& \frac{y (x+y+z)}{(x+y) (y+z)},~u_6 = \frac{(y+z) (x+y+z+1)}{(y+z+1) (x+y+z)},~u_7 =
-   \frac{y+z+1}{x+y+z+1},~~~~~~~~~~~~~~~u_8= \frac{x+z+1}{x+y+z+1}, \nonumber \\
-   u_9 &=& \frac{x+y+1}{x+y+z+1},~u_{10} = \frac{(z+1) (x+y+z+1)}{(x+z+1) (y+z+1)},~u_{11}=
-   \frac{(x+1) (x+y+z+1)}{(x+y+1) (x+z+1)},~u_{12} =\frac{x+z+1}{(x+1) (z+1)} \nonumber
-\eea
-and the u-equations  are:
-\bea
-1-u_1&=&u_5 u_6 u_7^2 u_{10} u_{12},~1-u_2=u_4 u_6 u_7^2 u_8^2 u_{10}^2 u_{11} u_{12},~1-u_3=u_7 u_8 u_9 u_{10} u_{11} u_{12},~1-u_4=u_2 u_5
-   u_9^2 u_{11} u_{12}, \nonumber \\
-   1-u_5 &=& u_1 u_4 u_8^2 u_{10} u_{11},~1-u_6=u_1 u_2 u_8^2 u_9^2 u_{10} u_{11}^2 u_{12},~1-u_7=u_1 u_2 u_3 u_8 u_9
-   u_{11},~1-u_8=u_2 u_3 u_5 u_6 u_7 u_9, \nonumber \\
-   1-u_9&=&u_3 u_4 u_6 u_7 u_8 u_{10},~1-u_{10}=u_1 u_2^2 u_3^2 u_5 u_6 u_9^2 u_{11},~1-u_{11}=u_2 u_3^2 u_4
-   u_5 u_6^2 u_7^2 u_{10},~1-u_{12}=u_1 u_2 u_3^2 u_4 u_6 \nonumber
-\eea
-The $u$-equations above are that of ABHY realisation $B_3$ of the cyclohedron. This fact also generalizes to all $n$.
-
-Thus, the gen.permutahedron realisation and ABHY type $B_n$ realisation of the cyclohedron are one and the same.
-
-We can now consider several degenerations of both $A_n$ and $B_n$ and show that they are binary geometries with perfect $u$-equations.
-\newpage
-\section*{Minkowski sum of $n$ A2's }
-We can also consider general Minkowski sums of non-simplices and see if these also give us any instance of polytopes with perfect $u$ equations. One such case is the following:
-
-We consider the Minkowski sum of $n-1$ $A_2$'s with following Newton polynomial :
-\bea \label {new}
-\prod_{i=1}^{n} (1+x_i ) \prod_{i=1}^{n-1} (1+x_i +x_i x_{i+1}) 
-\eea 
-This gives a family of simple $n$-dimensional polytopes with $3n-1$ facets  and Pell number $P_n$ (~recursively defined as $ P_n=2 P_{n-1} +P_{n-2}$ with $P_1=1,~ P_2=2$) of vertices which we shall call $X_n$.
-
-We can solve for $u$-variables for this family and we get :
-\bea
-u_1 &=& \frac{p_n}{q_n}, ~u_2 = \frac{p_{n-1}q_n}{p_{n-1,n}},~u_3 = \frac{p_{n-2}q_{n-1}}{p_{n-2,n-1}}, \cdots,
-u_{n-2} = \frac{p_1 q_2}{p_{12}}, ~u_{n-1} = \frac{p_{2}q_3}{p_{23}},~u_n = \frac{p_{3}q_{4}}{p_{34}}, \nonumber \\
-u_{n+1} &=& \frac{1}{q_1}, ~u_{n+2} = \frac{p_{12}}{q_{1}q_{2}},~u_{n+3} = \frac{q_{1}}{p_{23}}, \cdots,
-u_{3n-1} = \frac{ q_{n-1}}{p_{n-1n}} \nonumber
-\eea
-where $p_i =x_i$, $q_i= 1+x_i$ and $p_{i~i+1}=1+x_i+ x_i x_{i+1}$.
-
-The $u$ equations obtained from these $u$ variables are of three types viz. $1-u$ being the product of two, three or four $u$'s  for any $n$.
-
-There are exactly 4 $u$'s which have $1-u$ is product of 2 u's:
-\bea
-1-u_{1} =u_{3n-2} u_{3n-1},~
-1-u_{n-2} =u_{n+1} u_{n+3},~
-1-u_{n+1} =u_{n-2} u_{n+2},~
-1-u_{3n-1} = \begin{cases}
-u_{2} u_{3} , n=3\\
-u_{1} u_{4} , n=4\\
-u_{1} u_{2} , n\geq 5
-\end{cases} \nonumber 
-\eea
-The facets corresponding to setting any of these $u \to 0$ is $X_{n-1}$.
-
-There are exactly $n-3$ $u$'s which have $1-u$ is product of 4 u's:
-\bea
-1-u_{n+4} =u_{n} u_{n+2}u_{n+4} u_{n+6} ~~and~~
-1-u_{n+6+ 2 i} =u_{n-3-i} u_{n+4+2 i} u_{n+5+2 i} u_{n+8+2 i}~ for~i=0,\cdots,(n-5) \nonumber 
-\eea
-The facets corresponding to setting any of these $u \to 0$ is $A^{m}_1 \times X_{n-m-1}$.
-
-All the other $2n-2$ $u$'s correspond to $1-u$ is product of 3 u's and we do not yet have a complete classification of the facets.
-
-We can also replace the first the first term in the Newton polynomial \eqref{ new} with $(1+x_1+ x_2)$ and we get an identical system of $u$-equations
-
-\bea
-u_1 &=& \frac{p_n}{q_n}, ~u_2 = \frac{p_{n-1}q_n}{p_{n-1,n}},~u_3 = \frac{p_{n-2}q_{n-1}}{p_{n-2,n-1}}, \cdots,
-u_{n-3} = \frac{p_4 q_5}{p_{45}}, ~u_{n-2} = \frac{p_{1}}{q_{1}},~u_{n-1} = \frac{p_{2}q_{3}}{p_{23}},~u_{n} = \frac{p_{3}q_{4}}{p_{34}}, \nonumber \\
-u_{n+1} &=& \frac{q_2}{p_{12}}, ~u_{n+2} = \frac{q_{1}}{p_{12}},~u_{n+3} = \frac{p_{23}}{q_{2}q_{3}}, \cdots,
-u_{3n-1} = \frac{ p_{12}}{q_{1}q_{2}} \nonumber
-\eea
-where $p_i =x_i$, $q_i= 1+x_i$ and $p_{i~i+1}=1+x_i+ x_i x_{i+1}$ with $p_{12}= 1+x_1+x_2$.
-
-The $u$ equations obtained from these $u$ variables are of three types viz. $1-u$ being the product of two, three or four $u$'s  for any $n$.
-
-There are exactly 4 $u$'s which have $1-u$ is product of 2 u's:
-\bea
-1-u_{1} =u_{3n-2} u_{3n-3},~
-1-u_{n-2} =u_{n+1} u_{3n-1},~
-1-u_{n+1} =u_{n-2} u_{n+2},~
-1-u_{3n-1} = \begin{cases}
-u_{2} u_{3} , n=3\\
-u_{1} u_{4} , n=4\\
-u_{1} u_{2} , n\geq 5
-\end{cases} \nonumber 
-\eea
-The facets corresponding to setting any of these $u \to 0$ is $X_{n-1}$.
-
-There are exactly $n-3$ $u$'s which have $1-u$ is product of 4 u's:
-\bea
-1-u_{n+3} =u_{n} u_{n+2}u_{n+5} u_{3n-1} ~~and~~
-1-u_{n+5+ 2 i} =u_{n-3-i} u_{n+3+2 i} u_{n+4+2 i} u_{n+7+2 i}~ for~i=0,\cdots,(n-5) \nonumber 
-\eea
-It would be nice to see if these also correspond to some degeneration of the associahedron or if they  are generalised permutahedra. 
-\newpage
-\section{Discussions}
-There are several interesting open questions, like the question of  whether degenerations of other cluster types (in particular $C_n$ and $D_n$ can also give binary geometries with (perfect?) $u$-equations.\\\\
-\noindent
-Though many examples of degenerations of $A_n$ and $B_n$ were products of lower dimensional objects of the same type, there were examples where we got non-trivial degenerations which did not factor.
-We would like to completely classify these cases and this would settle the question of identifying all the ``atoms'' of binary geometries with perfect $u$-equations.
-One class of examples which is certainly of both mathematical and physical interest in this context are the Stokes polytopes (and more generally Accordiohedra).
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-04-27 draft_ABP.tex
Updates from Overleaf

@@
 \end{equation}
-where $F_{[k,l]}:=0$ when $k>l$ or $[k,l]=[0,n]$. Using this solution to rewrite 
+where $F_{[k,l]}:=0$ when $k>l$ or $[k,l]=[0,n]$.
+The usual $X$-variable $X_{ij}=\sum_{i\leq k<l<j}s_{kl}$ in string integrals here is $F_{[i,j-2]}$. 
+Using this solution to rewrite 
 the integrand of the stringy canonical form $\mathcal I_{\mathbf B}(\{S\})$
@@
 \[
-	S_{[i,j]}=-c_{[i,j]} \,\,\text{ for all $i<j$,}\quad
+	S_{[i,j]}=-C_{[i,j]} \,\,\text{ for all $i<j$,}\quad
 	F_{[i,j]}\geq 0 \,\,\text{ for all $i\leq j$},
 \]
-where $c$s are positive numbers. We can use a mesh to represent these conditions.
+where $C$s are positive numbers. We can use a mesh to represent these conditions.
 For example, the mesh of $\mathscr A_3$ is 
@@
 in each diamond. This is because the mismatch of the correspondence of labels 
-$F_{ij}=F_{[i,j-2]}$ and $s_{ij}=S_{[i,j-1]}$.
+$X_{ij}=F_{[i,j-2]}$ and $s_{ij}=S_{[i,j-1]}$.
 }
@@
 \[
-	c_{[i,j]}=F_{[i,j-l]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]},
+	C_{[i,j]}=F_{[i,j-l]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]},
 \]
@@
 \]
+Since the building set of $\mathscr A_n$ is contained in the building set of $\mathscr B_n$, $\mathscr A_n$ is a degeneration of $\mathscr B_n$.
 
@@
 	F_{[i,j-1]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]}
-	=c_{[i,j]}\,\,\text{for $i\neq j$ and $[i,j]\neq [0,n]$}, \quad 
+	=C_{[i,j]}\,\,\text{for $i\neq j$ and $[i,j]\neq [0,n]$}, \quad 
 \]
@@
 \begin{equation}\label{abhyB}
-	c_{[0,n]}=\sum_{i=0}^n F_{[i,i-2]}-\sum_{i=0}^n F_{[i,i-3]},
-\end{equation}
-where $F_{[i+1,i]}=0$ and $c$s are all positive constants. We can also
-use a mesh to represent this conditions. For example, the mesh for $\mathscr B_3$
-is 
-\begin{center}
-\begin{tikzpicture}
-	\draw[thick] (-1,-2) node[below]{$0$} -- (2,1);
-	\draw[thick] (-2,-1) -- (-1,-2);
-	\draw[thick] (-1,0) -- (1,-2) node[below]{$0$}-- (4,1);
-	\draw[thick] (2,1) -- (4,-1) -- (5,-2);
-	\draw[thick] (4,1) -- (6,-1);
-	\draw[thick] (5,-2) node[below]{$0$} -- (7,0) -- (6,1) ;
-	\draw[thick] (-2,-1) -- (0,1) -- (2,-1);
-	\draw[thick] (2,-1) -- (3,-2) node[below]{$0$} -- (6,1);
-	\node at (-2.5,-1) {$[0,0]$};
-	\node at (-0.65,-1) {$[1,1]$};
-	\node at (1.35,-1) {$[2,2]$};
-	\node at (3.35,-1) {$[3,3]$};
-	\node at (5.35,-1) {$[0,0]$};
-	\node at (-1.5,0) {$[0,1]$};
-	\node at (0.35,0) {$[1,2]$};
-	\node at (2.35,0) {$[2,3]$};
-	\node at (4.35,0) {$[3,0]$};
-	\node at (6.35,0) {$[0,1]$};
-	\node at (0,1.2) {$[0,2]$};
-	\node at (2,1.2) {$[1,3]$};
-	\node at (4,1.2) {$[2,0]$};
-	\node at (6,1.2) {$[3,1]$};
-\end{tikzpicture}
-\end{center}
-with an additional equation \eqref{abhyB}.
+	C_{[0,n]}=\sum_{i=0}^n F_{[i,i-2]}-\sum_{i=0}^n F_{[i,i-3]},
+\end{equation}
+where $F_{[i+1,i]}=0$ and $C$s are all positive constants. 
+%We can also use a mesh to represent this conditions. For example, the mesh for $\mathscr B_3$ is 
+%\begin{center}
+%\begin{tikzpicture}
+%	\draw[thick] (-1,-2) node[below]{$0$} -- (2,1);
+%	\draw[thick] (-2,-1) -- (-1,-2);
+%	\draw[thick] (-1,0) -- (1,-2) node[below]{$0$}-- (4,1);
+%	\draw[thick] (2,1) -- (4,-1) -- (5,-2);
+%	\draw[thick] (4,1) -- (6,-1);
+%	\draw[thick] (5,-2) node[below]{$0$} -- (7,0) -- (6,1) ;
+%	\draw[thick] (-2,-1) -- (0,1) -- (2,-1);
+%	\draw[thick] (2,-1) -- (3,-2) node[below]{$0$} -- (6,1);
+%	\node at (-2.5,-1) {$[0,0]$};
+%	\node at (-0.65,-1) {$[1,1]$};
+%	\node at (1.35,-1) {$[2,2]$};
+%	\node at (3.35,-1) {$[3,3]$};
+%	\node at (5.35,-1) {$[0,0]$};
+%	\node at (-1.5,0) {$[0,1]$};
+%	\node at (0.35,0) {$[1,2]$};
+%	\node at (2.35,0) {$[2,3]$};
+%	\node at (4.35,0) {$[3,0]$};
+%	\node at (6.35,0) {$[0,1]$};
+%	\node at (0,1.2) {$[0,2]$};
+%	\node at (2,1.2) {$[1,3]$};
+%	\node at (4,1.2) {$[2,0]$};
+%	\node at (6,1.2) {$[3,1]$};
+%\end{tikzpicture}
+%\end{center}
+%with an additional equation \eqref{abhyB}.
 
@@
 
-The degenerations of $A_n$ is given by setting some $c$s in ABHY construction or deleting the corresponding elements in the building set.
+The degenerations of $A_n$ is given by setting some $C$s in ABHY construction or deleting the corresponding elements in the building set.
 Note that the building set after deletion doesn't need to be a new building set, \emph{i.e.} a degeneration of $A_n$ may not be a generalized permutohedron.
@@
 	F_{[i,k]}+F_{[j,l]}-F_{[i,l]}-F_{[j,k]}=
-	\sum_{i\leq a<j\atop{k<b\leq l}} c_{[a,b]} 
+	\sum_{i\leq a<j\atop{k<b\leq l}} C_{[a,b]} 
 \]
 where $F_{[a,b]}:=0$ when $a>b$ or $[a,b]=[0,n]$,
-an economical way to get a degeneration which satisfies the above property is setting all $c$s on the RHS of 
+an economical way to get a degeneration which satisfies the above property is setting all $C$s on the RHS of 
 \begin{align*}
-&F_{[i,j-1]}+F_{[j,l]}-F_{[i,l]}= \sum_{i\leq a<j\leq b\leq l} c_{[a,b]} 
+&F_{[i,j-1]}+F_{[j,l]}-F_{[i,l]}= \sum_{i\leq a<j\leq b\leq l} C_{[a,b]} 
 \quad \text{for $i<j=k+1\leq l$ }\\[-1.5ex]
 \text{or}&\\
-&F_{[0,k]}+F_{[j,n]}-F_{[j,k]}= \sum_{0\leq a<j\atop{k<b\leq n}} c_{[a,b]} 
+&F_{[0,k]}+F_{[j,n]}-F_{[j,k]}= \sum_{0\leq a<j\atop{k<b\leq n}} C_{[a,b]} 
 \quad \text{for $0<j\leq n$ and $0\leq k<n$}
 \end{align*}
-to be zero, and all wanted degenerations can be got by setting $c$s in several above equations.
-
-From the viewpoint of mesh, an equation above corresponds to a big diamond whose top or bottom corner and all $c$s are zero. For example,
+to be zero, and all wanted degenerations can be got by setting $C$s in several above equations.
+
+From the viewpoint of mesh, an equation above corresponds to a big diamond whose top or bottom corner and all $C$s are zero. For example,
 \begin{center}
@@
 Similarly, black points are all vanishing facets in the above example, and generally
-the number of vanishing facets equals the number of deleted $c$s for degenerations of this type.
+the number of vanishing facets equals the number of deleted $C$s for degenerations of this type.
 
@@
 \end{center}
-after setting $c$s in green and purple diamonds to be zero, three facets (black points) vanish and building set after deletion is 
+after setting $C$s in green and purple diamonds to be zero, three facets (black points) vanish and building set after deletion is 
 \[
@@
 
-We can play the game for any degenerations of $A_n$, count black points and deleted $c$s in each degeneration, and find that for $A_2$, $A_3$ and $A_4$, there're respectively $4$, $41$ and $580$ possible degenerations whose big polytopes are simplices.
+We can play the game for any degenerations of $A_n$, count black points and deleted $C$s in each degeneration, and find that for $A_2$, $A_3$ and $A_4$, there're respectively $4$, $41$ and $580$ possible degenerations whose big polytopes are simplices.
 For these degenerations, we can easily find their $u$-variables if their sets of all vanishing facets are known.
@@
 \end{center}
-where $c$s in green region vanish, \emph{i.e.} $c_{[a,b]}=0$ for $0\leq a<i<b\leq n$.
+where $C$s in green region vanish, \emph{i.e.} $c_{[a,b]}=0$ for $0\leq a<i<b\leq n$.
 Vanishing facets of this degeneration are
@@
 \end{center}
-
-(better figure?)
-
-One could use this construction of products to produce any finite product $\mathscr A_{i_1}\times \cdots \times \mathscr A_{i_k}$, and this construction is also valid for any generalized permutahderon.
-The direct proof of this argument for $\mathscr A_n$ is using global $u$-equations of $\mathscr A_n$. ...
+One could use this construction of products to produce any finite product $\mathscr A_{i_1}\times \cdots \times \mathscr A_{i_k}$.
+The direct proof of this argument for $\mathscr A_n$ is using global $u$-equations \cite{} of $\mathscr A_n$.
+
+We can generalize the simplest cases in another way:
+\begin{center}
+\begin{tikzpicture}[scale=1.5]
+\fill[green!20] (4.44,-1.45) -- (1.3,-1.4584) -- (2.88,0.12) --(2,1);
+\draw (-0.5,-1.5) -- (2,1) -- (4.5,-1.5);
+\draw[decorate,decoration=zigzag] (-0.5,-1.5)--(4.5,-1.5);
+\node at (1.3,-1.3) {$[i,i]$};
+\node at (3.1,0.2) {$[i,n]$};
+\end{tikzpicture}
+\end{center}
+setting 
+\[
+C_{[k,l]}=0 \quad \text{for $0<i\leq k< l\leq n$}.
+\]
+In this case, 
+\[
+F_{[k,l]}=\sum_{m=k}^l F_{[m,m]}
+\]
+for $i\leq k < l \leq n$. Therefore,
+\[
+\tilde u_{[k,k]}=\prod_{i\leq p\leq k\leq q \leq n}u_{[p,q]}=\frac{x_k}{x_{[i-1,k]}}\quad 
+\text{for $k\in [i,n]$},\quad \tilde u_I=u_I\quad \text{for the other $I$},
+\]
+and their $u$-equations are
+\[
+1-\tilde u_{[k,k]}=\prod_{j=0}^{i-1}\tilde u_{[j,k-1]},
+\]
+and the other $u$-equations are old $u$-equations in terms of new variables.
+When $i=1$, the degeneration is $\mathscr A_1^n$.
+
+Similarly, we can also consider the following degenerations:
+\begin{center}
+\begin{tikzpicture}[scale=1.5]
+\fill[green!20] (3.4,-0.4) -- (2,-0.4) -- (0.6,-0.4) --(2,1);
+%\fill[green!20,decorate,decoration=zigzag] (0.6,-0.4)--(3.4,-0.4);
+\draw (-0.5,-1.5) -- (2,1) -- (4.5,-1.5);
+\draw[decorate,decoration=zigzag] (-0.5,-1.5)--(4.5,-1.5);
+\node at (0.4,-0.2) {$[0,i]$};
+\node at (3.7,-0.2) {$[n-i,n]$};
+\end{tikzpicture}
+\end{center}
+setting
+\[
+C_{[k,l]}=0 \quad \text{for $l-k>i$}.
+\]
+In this case,
+\[
+F_{[k,l]}=F_{[0,l]}+F_{[k,n]}\quad \text{for $l-k\geq i$, $1\leq k\leq n-i-1$ and $i+1\leq l\leq n-1$},
+\]
+then 
+\[
+\tilde u_{[0,l]}=\prod_{j=0}^{l-i+1}  u_{[j,l]},\quad 
+\tilde u_{[k,n]}=\prod_{j=k+i-1}^{n}  u_{[k,j]}.
+\]
+Their $u$-equations are 
+\[
+1-\tilde u_{[0,l]}=\prod_{a=l-i+2}^{l+1}\tilde u_{[a,n]}\cdot\prod_{a=l-i+2}^{l+1}\prod_{b=l+1}^{a+i-2} \tilde u_{[a,b]},\quad
+1-\tilde u_{[k,n]}=\prod_{b=k-1}^{k+i-2}\tilde u_{[0,b]}\cdot \prod_{b=k-1}^{k+i-2}\prod_{a=\max(b-i+2,1)}^{k-1} \tilde u_{[a,b]}.
+\]
+When $i=1$, we will get $\mathscr A_1^n$ again.
 
@@
 
-Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
+Let $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
 \bea
@@
 \eea
- for some collection of subsets $I \in [0,n]$
+for some collection of subsets $I \in [0,n]$.
 We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation only as Minkowski sums i.e., all $y_I \ge 0$ \footnote{This is mainly due to the subtle nature of the Minkowski difference operation, which makes the shape of the resulting polytope dependent on the relative magnitudes of $y_I$'s.}which are called Nestohedra.
@@
 
-\subsubsection*{Nested Complex}
+\paragraph*{Nested Complex} 
 A subset ${\mathbf N}$ in the building set ${\mathbf B}$ is called a {\it nested set} if it satisfies the following conditions:
@@
 
- {\bf Facial structure:}
-
+\paragraph*{Facial structure} 
 Let us assume that the set ${\mathbf B}$ associated with a generalised permutahedron ${\mathscr P_n}^{y}$ is a building set on $[0,n]$.
@@
 
-In summary the above results mean the following:\\
-
-(1) We can look at any collection of subsets of $[0, n]$ which form a building set ${\mathbf B}$ and associate  coordinate simplex $\Delta_I$ for each $I \in {\mathbf B}$ and resulting Minkowski sum with positive weights $y_I$ generates a polytope of dimension $n$ called the generalised permutahedron (Nestohedron) associated with the building set.
-\\
-
-(2) The number of facets $N$ of the generalised permutahedron just corresponds to the set of all elements in ${\mathbf B}$ excluding the maximal set. \\
-
-(3) Two facets corresponding to the sets $I$ and $J$ in ${\mathbf B}$ intersect i.e., are {\it compatible} with each other if and only if  either $I \subset J$,~ $J \subset I$~ or $I \cap J = \emptyset ~{\text and} ~ I \cup J \notin {\mathbf B}$.
-
-Let us look at a couple of examples to appreciate these facts better:\\
-(1) Consider the generalized permutahedron with building set ${\mathbf B}= \{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,1,2\} \}$.
-
+In summary the above results mean the following:
+
+\begin{compactitem}
+\item We can look at any collection of subsets of $[0, n]$ which form a building set ${\mathbf B}$ and associate  coordinate simplex $\Delta_I$ for each $I \in {\mathbf B}$ and resulting Minkowski sum with positive weights $y_I$ generates a polytope of dimension $n$ called the generalised permutahedron (Nestohedron) associated with the building set.
+
+\item The number of facets $N$ of the generalised permutahedron just corresponds to the set of all elements in ${\mathbf B}$ excluding the maximal set.
+
+\item Two facets corresponding to the sets $I$ and $J$ in ${\mathbf B}$ intersect i.e., are {\it compatible} with each other if and only if  either $I \subset J$,~ $J \subset I$~ or $I \cap J = \emptyset ~{\text and} ~ I \cup J \notin {\mathbf B}$.
+\end{compactitem}
+
+Let us look at a couple of examples to appreciate these facts better:
+
+(1) Consider the generalized permutahedron with building set 
+\[{\mathbf B}= \{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,1,2\} \}.\]
 The polygon has 5 facets which correspond to the sets $\{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\}\}$ and their compatability is shown in the figure below.
 
-The polytope in this case is the 2d associahedron ${\mathscr A_2}$.\\
-(2) Consider the generalized permutahedron with building set ${\mathbf B}= \{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,2\},\{0,1,2\} \}$
-
+The polytope in this case is the 2d associahedron ${\mathscr A_2}$.
+
+(2) Consider the generalized permutahedron with building set 
+\[{\mathbf B}= \{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,2\},\{0,1,2\} \}.\]
 The polygon has 6 facets which correspond to the sets $\{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,2\}\}$ and their compatability is shown in the figure below.
@@
 The polytope in this case is the 2d cyclohedron ${\mathscr B_2}$ which also coincides with 2d permutahderon ${\mathscr P_2}$.
+
 \begin{figure}[H]
 \begin{center}       
-
 \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
@@
 % Text Node
-\draw (226,96) node [anchor=north west][inner sep=0.75pt]   [align=left] {12};
+\draw (226,96) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
 % Text Node
-\draw (310,100) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
+\draw (310,100) node [anchor=north west][inner sep=0.75pt]   [align=left] {12};
 % Text Node
@@
 \draw (155,263) node [anchor=north west][inner sep=0.75pt]   [align=left] {Figure showing the compatible\textbackslash incompatible facets of the 2d associahedron  \\ and permutahedron as generalized permutahedra};
-
 \end{tikzpicture}
@@
 \end{figure}
+
 An improtant fact about generalised permutahedra which makes them particularly interesting is the following:
@@
 \bea
-N &=& |{\mathbf B}|-1 \nonumber \\
- &=& (n+1+m)-1 \nonumber  \\
- &=& n+m \nonumber
+N = |{\mathbf B}|-1 
+ = (n+1+m)-1
+ = n+m \nonumber
 \eea
@@
 
-(4)If ${\mathbf B}=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr P_n}({\bf Y})$ is the associahedron. \\
+(4) If ${\mathbf B}=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr P_n}({\bf Y})$ is the associahedron. \\
 
@@
 This makes the permutahedron a very important example of generalized permutahedra and we shall devote the rest of this section to studying its properties and proving it is binary.
-\subsubsection*{Permutahedron}
-
-Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_{n+1})$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$.
-For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull}(e_i~|~i\in I)$ denote the face of the $\Delta_{[0,n]}$.
-The polytope $P_n(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I > 0$ for all nonempty subsets $I \subset [n+1]$
- \bea
- P_n(\{y_I \})= \sum_{I \subset[n+1]} y_I . \Delta_I  
- \eea
- is the permutahedron ${\mathscr P_n}$
-
-{\bf Facial Structure:}
-
-The $(n-k)$ faces of ${\mathscr P_n}$ are in an $1-1$ correspondence with the decomposition of $[0,n]$ into $k$ parts.
-More precisely, for each $(S_1,\cdots,S_k)$ with $S_i \neq \emptyset ~ \forall i$ and $[0,n] = S_1 \sqcup \cdots \sqcup S_k$ the corresponding face $\pi_{S_1,\cdots,S_k}$ has vertices which are permutations such that the entries $ \{x_i | i \in S_1 \}$ are largest $|S_1|$ numbers in $[0,n]$, $\{x_i | i \in S_2 \}$ are largest $|S_2|$ numbers in $[0,n]$ and so on.
-
-Further the face $\pi_{S_1,\cdots,S_k}$   is isomorphic to ${\mathscr P_{\left(| S_1|-1\right)} }\times {\mathscr P_{\left(| S_2|-1\right)} } \cdots \times{\mathscr P_{\left(| S_k|-1\right)} } $.
-
-It follows from above that ${\mathscr P_n}$ has $2^{n+1} -2$ facets corresponding to all the non-empty proper subsets of $[0,n]$ for which we have a decomposition $[0,n] = S \sqcup S^c$ and the facets are isomorphic to one of the following product of lower dimensional permutahedra  $ \{ {\mathscr P_{n-1}}, {\mathscr P_{n-2}} \times A_1, \cdots ,{\mathscr P_{\lfloor{n/2 \rfloor}}} \times {\mathscr P_{n-1-\lfloor n/2 \rfloor}}  \} $\footnote {More generally the number of $(n-k)$ facets of ${\mathscr P_n}$ is $ k!
-S(n,k)$ where $S(n,k)$ is the Stirling number of the second kind which counts the number $k$ partitions of  $I$ and there are $p(n+1,k)$ types where $p(n+1,k)$ is the number of $k$ partitions of $(n+1)$.}.
-
-It also follows from above that a face $\pi_{S_1,\cdots,S_k}$ is contained in another face $\pi_{T_1,\cdots,T_l}$ if and only if each $T_i$ is a union of consecutive $S_j$ or equivalently if $(S_1,\cdots,S_k)$ is a refinement of $(T_1,\cdots,T_l)$.
-
-\section*{ABHY like realisation for the Permutahedron}
-The following set of equations to define the $n$-dimensional Permutahedron: 
-\bea
-C_I = (-1)^{|I|} \left( \sum_{i \in I} F_i - \sum _{{i<j}\atop{i,j \in I}} F_{ij} +\cdots + (-1)^{|I|}  F_I \right) \nonumber
-\eea
-for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $F_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.
-
-It is clear that
-\bea
-m= \text{No. of  C's }&=& 2^{n+1}-(n+2) \nonumber \\
-N= \text{No. of F's} &=& 2^{n+1}- 2 \nonumber 
-\eea
-Thus we see that $N= d+m$ as expected. We can write down the stringy integral as usual to be 
-\bea
-\int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} d x_i x_i^{\alpha^{'} F_i -1} \prod_{I} \left (\sum_{a\in I} x_a \right) ^{-\alpha^{'} C_I} \nonumber
-\eea 
-where the product is over all non-singlets $ I \subset \{0,1,\cdots,n\}$ with $x_{0} =1$.
-
-Let us look at the $n=2,3$ examples:
-
-\section*{2d permutahedron}
-In this case the building set $B=\{ \{ 0,1,2\},\{ 0,1\},\{0,2\},\{1,2\},\{0\},\{1\},\{2\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y, ~x_{01}=1+x, ~x_{02}=1+y,~ x_{12}=x+y,~ x_{012}=1+x+y$.
-
-We can write down the Newton polynomial for the Minkowski sum as $ x_1~ x_2~(1+x_1)~(1+x_2)~(x_1+x_2)~(1+x_1+x_2)$.
-
-The $u$-variables can be written in terms of $x$ variables as:
-\bea
-u_1&=&\frac{x(1+x+y)}{(x+y)(1+x)}, ~ u_2 =\frac{y(1+x+y)}{(x+y)(1+y)},~ u_{12}=\frac{(x+y)}{(1+x+y)}\nonumber \\
-u_{02}&=&\frac{(1+y)}{(1+x+y)}, ~~~~~ u_{01}=\frac{(1+x)}{(1+x+y)},~~~~~ u_{0}= \frac{(1+x+y)}{(1+x)(1+y)} \nonumber
-\eea
-The $u$-equations are:
-\bea
-1-u_i &=& (u_{0j})^2 u_j u_{0}, ~~~ 1-u_{12} = u_{02} u_{01} u_{0} \nonumber \\
-1-u_{0 j} &=& u_i u_{0 i} u_{12}, ~~~~~~~ 1-u_{0} = u_{1} u_{2} (u_{12})^2 \nonumber
-\eea
-where $i=1$ implies $j=2$ and vice versa.
-
-\section*{3d permutahedron}
-In this case the building set $B=\{ \{ 0,1,2,3\},\{ 0,1,2\},\{0,2,3\},\{0,1,3\},\{1,2,3\},\{0,1\},\{0,2\},\{0,3\},\{1,2\} \\ ,\{2,3\},\{1,3\},\{0\},\{1\},\{2\},\{3\}\}$ and the relevant $x$ variables are $x_0=1, ~x_1=x, ~x_2=y, ~x_3=z, ~x_{01}=1+x, ~x_{02}=1+y,~x_{03}=1+z,~ x_{12}=x+y,~x_{13}=x+z,~x_{23}=y+z,~ x_{012}=1+x+y,~ x_{013}=1+x+z,~ x_{023}=1+y+z,~ x_{123}=x+y+z,~ x_{0123}=1+x+y+z$.
-\\
-
-The $u$ and $u'$-variables can be written interms of $x$ variables as:
-{\scriptsize  \bea
-u_1&=&\frac{x(1+x+y)(1+x+z)(x+y+z)}{(x+y)(x+z)(1+x)(1+x+y+z)}, ~ u_2 =\frac{y(1+x+y)(1+y+z)(x+y+z)}{(x+y)(y+z)(1+y)(1+x+y+z)},~ u_{3}=\frac{z(1+x+z)(1+y+z)(x+y+z)}{(x+z)(y+z)(1+z)(1+x+y+z)},\nonumber \\
-u_{023}&=&\frac{(1+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u_{013} =\frac{(1+x+z)}{(1+x+y+z)},~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u_{012}=\frac{(1+x+y)}{(1+x+y+z)},\nonumber \\
-u_{12}&=&\frac{(x+y)(1+x+y+z)}{(1+x+y)(x+y+z)}, ~~~~~~~~~~~~~~~~~~ u_{23} =\frac{(y+z)(1+x+y+z)}{(1+y+z)(x+y+z)},~~~~~~~~~~~~~~~~~~~ u_{13}=\frac{(x+z)(1+x+y+z)}{(1+x+z)(x+y+z)},\nonumber \\
-u_{03}&=&\frac{(1+z)(1+x+y+z)}{(1+y+z)(1+x+z)}, ~~~~~~~~~~~~~~~~~~ u_{01} =\frac{(1+x)(1+x+y+z)}{(1+x+y)(1+x+z)},~~~~~~~~~~~~~~~~~~~ u_{02}=\frac{(1+y)(1+x+y+z)}{(1+x+y))(1+y+z)},\nonumber  \\
-u_{123}&=&\frac{(x+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~ u_{0} =\frac{(1+x+y)(1+y+z)}{(1+x)(1+y)(1+z)(1+x+y+z)}\nonumber
-\eea }
-The $u$-equations in this case are:
-{\small  \bea
-1-u_i &=& u_j u_k (u_{jk})^2 (u_{0jk})^3 (u_{0k})^2(u_{0 j})^2 u_{0} \left(1+ u_i u_{ij} u_{ik} u_{0ik} u^_{0ij}  u_{0i}\right),  1-u_{ij} = u_k u_{ik} u_{jk} (u_{0jk})^2 (u_{0ik})^2 (u_{0 k})^2 u_{0 j} u_{0 i} u_{0} \nonumber  \\
-1-u_{0 j k} &=& u_i u_{ij} u_{ik} u_{0 i k} u_{0 i j}  u_{0 i}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 1-u_{0 k} = u_i u_{j}  (u_{ij})^2 u_{ik} u_{jk} (u_{123})^2 (u_{0 i j})^2 u_{0 j} u_{0 i}  \nonumber \\
-1-u_{0} &=& u_1 u_{2} u_{3} (u_{12})^2 (u_{23})^2  (u_{13})^2 (u_{123})^3 \left(1+ u_{0}  u_{023} u_{013} u_{012} u_{03} u_{01}  u_{02} \right), 1-u_{123} = u_{023} u_{013} u_{012} u_{03} u_{01}  u_{02} u_{0}   \nonumber
-\eea}
-where $i,j,k \in {1,2,3}$ and $i \neq j \neq k$.
-
-The 8 facets of the 3d permutahedron corresponding to $u_i \rightarrow 0, u_{0jk} \rightarrow 0,u_{123} \rightarrow 0 ~and ~u_{0} \rightarrow 0$  are all $B_2$'s.
-Similarly, the 6 facets corresponding to  $u_{ij} \rightarrow 0, u_{0k} \rightarrow 0$ are all  $A^{2}_1$.
-
-Thus, the 3d permutahedron integral factorizes nicely on all massless poles at finite $\alpha^{'}$ !!
-We shall list a few results about permutahedra which shall be useful for later purposes: 
-\begin{enumerate}
-\item The $u$-variables for the permutahedron are: 
-\bea
-u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber 
-\eea
-The above relations can also be inverted to obtain $x_I$ as follows:
-
-For $0 \notin I $
-\bea
-x_I &=& \frac{\prod_{I \subset J} u_{J}}{1-\prod_{I \subset J} u_{J}} \\
-\frac{1}{1+ x_I} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}}
-\eea
-From the above relations it is clear that taking $u_I \rightarrow 0$ for $0 \notin I$ implies $x_J \rightarrow 0$ for all $J \subset I$ and taking $u_{\bar{I}} \rightarrow 0$ implies $x_J \rightarrow \infty $ for all $I \subset J$.
-In fact we shall argue that there is unique choice of $x_I$'s which we can take to $0$ or $\infty$ which corresponds to setting only a particular $u_I \rightarrow 0$ or $u_{\bar{I}} \rightarrow 0$ respectively.
-\item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :
-
-% {\bf compatible if} $I\cap J = \emptyset$ or $I\cap J \neq \emptyset$ and either $I \subset J$ or $J \subset I$
-
-% {\bf incompatible if}   $I\cap J \neq \emptyset$ or $I\cap J = \emptyset$ and neither $I \not\subset J$ or $J \not\subset I$
-
-{\bf compatible if and only if} $\{[0,n],I,J\}$ is a nested set, i.e.
-\[
-I\subset J\quad \text{or}\quad J\subset I\quad \text{or}\quad (J\cap I=\varnothing \quad \text{and}\quad J\cup I\not\in \mathscr P_n).
-\]
-For permutohedron, $J\cup I$ is always contained in $\mathscr P_n$ for any $I$ and $J$, so it's compatible if and only if $J\subset I$ or $I\subset J$.
-
-The above  follows directly from the following relations amongst $u$ for each $I$ such that $0\notin I$ :
-\bea
-1-\prod_{I \subset J} u_{J} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}} \\
-1-\prod_{J \subset I} u_{\bar{J}} &=& \prod_{I \subset J} u_{J} \prod_{J \subset \bar{I} } u_{\bar{J}}
-\eea
-\end{enumerate}
-
-\subsection*{Braid arrangement}
-The braid arrangement in $\mathbb{R}^{n+1}$ consists of $\left({n}\atop{2}\right)$ hyperplanes 
-\bea
-z_i =z_j ~~{\rm for ~ all}~~0 \leq i<j \leq n
-\eea
-
-\subsection*{Degenerations which lead to products}
-In this section we provide an answer to the question of which degenerations of $A_n$ and $B_n$ give the most general products of such geometries.
-We begin by stating the following results about Nestohedra.
-
-The maximal set of a building set $B_{max}$ is the set of all inclusion maximal elements of the building set $B$. A building set $B$ is connected if $B_{max}$ has a single element.
-
-{\bf Theorem:}If $B_1, B_2,\cdots B_n$ are connected subsets of a building set $B$ then the corresponding nestohedron ${\mathscr N_B}$ is isomorphic to the product of the nestohedra ${\mathscr N}_{ B_1} \times{\mathscr N}_{ B_2} \cdots \times {\mathscr N}_{B_n}$.
-
-We can use the above result to construct 	a degeneration of $A_n$ which is a most general product i.e., $\prod_{p_i} A_{p_i}$ such that $\sum_{i} p_{i} = n$.
-
-Let us consider the  $A_4$ example for which the allowed possibilities are : $A_1^{4}$, $A_1^2 \times A_2$, $A_1 \times A_3$ and $A^{2}_2$.
-
-For the $A_1^{4}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} \}$ where $\{0,01\} , \{1,12\},\{2,23\},\{3,34\}$ generate the 4 $A_1$'s.
-
-For the $A_1^{2} \times A_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{234} \}$ where $\{0,01\} , \{1,12\} $ generate the 2 $A_1$'s and $\{2,3,4,23,34,234\}$ generates the $A_2$'s.
-
-For the $A_1 \times A_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{123},{234},{1234} \}$ where $\{0,01\}$ is the generates the $A_1$ and $\{{1},{2},{3},{4},{12},{23},{34},{123},{234},{1234} \}$ generate  $A_3$'s.
-
-For the $A_2^{2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} ,{012},{234}\}$ where $\{0,1,2,01,12,012\}$  and $\{2,3,4,23,34,234\}$ generate the 2 $A_2$'s.
-
-We can similarly find a degeneration of $A_n,B_n,~or~ {\mathscr P_n}$ which would correspond to any product.
-
-\subsection{Natural stringy integrals with linear factors}
-
-{\bf introduce a natural stringy integrals for any generalized stringy canonical forms: variables $x_0=1, x_1, \cdots, x_n$ and define $x_I=\sum_{i \in I} x_i$, the factors are $x_I^{\alpha' S_I}$ (we can say monomials $S_\{i\}=X_i$ and polynomials $S_I=-c_I$.
-$N=n+m$ and big polytope is a simplex, then general formula for $u$ variables, which is equivalent to ABHY conditions; again $P_n$ in full details and others as degenerations.}
-
-*******************
+
+% This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
+
+% Based on the above conjecture,  there is a statement for the binary geometries corresponding to the facet $u_{I}\to 0$, 
+% that is the $u$-system for the facet $u_{I}\to 0$ is corresponding to the generlaized permutohedra $\mathcal{P}_{I}\otimes \mathcal{P}_{\bar{I}}$ with building sets  
+% \[
+% \mathcal{B}_{I} = \{J\vert J\subset I, J\in \mathcal{B}\}
+% \]
+% and 
+% \[
+% \mathcal{B}_{\bar{I}} = \{J-I\vert  J\in \mathcal{B}-\mathcal{B}_{I} \}
+% \]
+% where $J-I$ means the complement of $J$ with respect to $I$. This statement directly follow from the fact that $u_{I}\to 0$ is equivalent to take $x_{i}\to t x_{i} $ for $i\in I$ then take $t \to 0$
+% )
+
+\newpage
+
+\subsection{$\mathscr{P}_{n}$ as a binary geometry}
+
+\subsubsection{String canonical forms and ABHY conditions for $\mathscr{P}_{n}$}
 
@@
 gives that
-\[
-	u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}.
-\]
-For example, the $u$-variables of $\mathscr P_2$ are
+\begin{equation}
+  u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}. \label{uvarforPn}
+\end{equation}
+
+The following set of equations to define the $n$-dimensional Permutahedron: 
+\bea
+C_I = (-1)^{|I|} \left( \sum_{i \in I} S_i - \sum _{{i<j}\atop{i,j \in I}} S_{ij} +\cdots + (-1)^{|I|}  S_I \right) \nonumber
+\eea
+for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $F_{I} =0$ for $I=\{ 0,1,\cdots,n \}$. 
+%It is clear that
+%\bea
+%m= \text{No. of  C's }&=& 2^{n+1}-(n+2) \nonumber \\
+%N= \text{No. of F's} &=& 2^{n+1}- 2 \nonumber 
+%\eea
+%Thus we see that $N= d+m$ as expected.
+
+Let us look at the $n=2,3$ examples:
+
+\paragraph*{2d permutahedron}
+In this case, the $u$-variables can be written in terms of $x$ variables as:
 \[
@@
 \]
-They satisfy the following equations
+The $u$-equations are:
 \begin{align*}
@@
 \end{align*}
-We will discuss these $u$-equations in the next subsection.
-
-For permutahedra, we can give a ABHY construction from eq.\eqref{SinF} by setting 
-$S_I=-c_I$ for any non-singleton $I\in \mathscr P_n$, where $c_I$ are positive 
-constants, and a ABHY polytope is given by 
-\begin{equation}\label{ABHY}
-	F_I\geq 0,\quad -c_I=\sum_{J\neq \varnothing,J\subset I}(-1)^{|J|-|I|}F_J
-\end{equation}
-in $\{S_i=F_i\,:\,1\leq i\leq n\}$-space, where the last equation is a gauge fixing. 
-According to eq.\eqref{genperm_defi}, this polytope is a $n$-dimensional 
-permutahedron $\mathscr P_n$. {\bf (???)}
-The ABHY construction of any generalized permutohedra can be obtained by 
-setting $c_I=0$ for all $I$ not in the building set.
-
-For example, the building set of $\mathscr A_2$ is $\mathscr P_2-\{\{0,2\}\}$,
-its ABHY construction can be obtained from $\mathscr P_2$ by setting $c_{02}=0$, 
-\[
-	0=-c_{02}=F_{02}-F_2,
-\]
-therefore the whole ABHY conditions for $\mathscr A_2$ is 
-\[
-	-c_{01}=F_{01}-F_0-F_1,\quad -c_{12}=F_{12}-F_1-F_2,\quad 
-	-c_{012}=-F_{01}-F_{12}+F_1,\quad F_I\geq 0,
-\]
-and its solution in $(F_1,F_2)$ space is 
-\[
-	\left\{\begin{aligned}
-		F_1&\geq 0,F_2\geq 0\\
-		F_0&=c_{01}+c_{12}+c_{012}-F_1-F_2\geq 0,\\
-		F_{12}&=F_1+F_2-c_{12}\geq 0,\\
-		F_{01}&=c_{012}+c_{12}-F_2\geq 0.
-	\end{aligned}\right.
-\]
-
-\subsection{Binary geometries and $u$ equations}
-
-% {\bf argue in general to have binary geometries we must have $1-u=\prod u' p(\{u\})$ with $p(u=0)=1$, conjecture that this is true of ALL gen. perm. Show it for gen. perm. more examples?}
+where are the same as the $u$ equations for $\mathscr{B}_{2}$
+
+\paragraph*{3d permutahedron}
+In this case, 
+the $u$-variables can be written interms of $x$ variables as:
+%the building set $B=\{ \{ 0,1,2,3\},\{ 0,1,2\},\{0,2,3\},\{0,1,3\},\{1,2,3\},\{0,1\},\{0,2\},\{0,3\},\{1,2\} \\ ,\{2,3\},\{1,3\},\{0\},\{1\},\{2\},\{3\}\}$.
+\begin{align}
+  u_{0} &= \frac{x_{0}x_{012}x_{013}x_{023}}{x_{01}x_{02}x_{03}x_{0123}} \:,\qquad  
+  u_{01} = \frac{x_{01}x_{0123}}{x_{012}x_{013}} \:, \\
+  u_{02} &= \frac{x_{02}x_{0123}}{x_{012}x_{023}}\:, \qquad 
+  u_{012} = \frac{x_{012}}{x_{0123}}\:,
+\end{align}
+and their cyclic. The $u$-equations are
+\begin{align}
+  1-u_{0} &= u_1 u_{2} u_{3} u_{12}^2 u_{23}^2  u_{13}^2 u_{123}^3 \left(1+ u_{0}  u_{023} u_{013} u_{012} u_{03} u_{01}  u_{02} \right)\:,  \\
+  1-u_{0 1} &= u_{2} u_{3}  u_{23}^2 u_{12} u_{13} u_{123}^2 u_{023}^2 u_{02} u_{03} \:,\\
+  1-u_{02} &= u_{1}u_{3} u_{13}^{2}u_{12}u_{23} u_{123}^{2} u_{013}^{2}u_{01}u_{03} \:,\\
+ 1-u_{012} &= u_3 u_{03}u_{13} u_{23} u_{0 1 3} u_{0 2 3} u_{123}  \:,
+ %1-u_{0 j k} &=& u_i u_{ij} u_{ik} u_{0 i k} u_{0 i j}  u_{0 i}
+\end{align}
+and their cyclic.
+
+The 8 facets of the 3d permutahedron corresponding to $u_i \rightarrow 0, u_{0jk} \rightarrow 0,u_{123} \rightarrow 0 ~and ~u_{0} \rightarrow 0$  are all $B_2$'s.
+Similarly, the 6 facets corresponding to  $u_{ij} \rightarrow 0, u_{0k} \rightarrow 0$ are all  $A^{2}_1$.
+Thus, the 3d permutahedron integral factorizes nicely on all massless poles at finite $\alpha^{'}$!.
+
+% {\scriptsize  \bea
+% u_1&=&\frac{x(1+x+y)(1+x+z)(x+y+z)}{(x+y)(x+z)(1+x)(1+x+y+z)}, ~ u_2 =\frac{y(1+x+y)(1+y+z)(x+y+z)}{(x+y)(y+z)(1+y)(1+x+y+z)},~ u_{3}=\frac{z(1+x+z)(1+y+z)(x+y+z)}{(x+z)(y+z)(1+z)(1+x+y+z)},\nonumber \\
+% u_{023}&=&\frac{(1+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u_{013} =\frac{(1+x+z)}{(1+x+y+z)},~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ u_{012}=\frac{(1+x+y)}{(1+x+y+z)},\nonumber \\
+% u_{12}&=&\frac{(x+y)(1+x+y+z)}{(1+x+y)(x+y+z)}, ~~~~~~~~~~~~~~~~~~ u_{23} =\frac{(y+z)(1+x+y+z)}{(1+y+z)(x+y+z)},~~~~~~~~~~~~~~~~~~~ u_{13}=\frac{(x+z)(1+x+y+z)}{(1+x+z)(x+y+z)},\nonumber \\
+% u_{03}&=&\frac{(1+z)(1+x+y+z)}{(1+y+z)(1+x+z)}, ~~~~~~~~~~~~~~~~~~ u_{01} =\frac{(1+x)(1+x+y+z)}{(1+x+y)(1+x+z)},~~~~~~~~~~~~~~~~~~~ u_{02}=\frac{(1+y)(1+x+y+z)}{(1+x+y))(1+y+z)},\nonumber  \\
+% u_{123}&=&\frac{(x+y+z)}{(1+x+y+z)}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~ u_{0} =\frac{(1+x+y)(1+y+z)}{(1+x)(1+y)(1+z)(1+x+y+z)}\nonumber
+% \eea }
+% The $u$-equations in this case are:
+% {\scriptsize \bea
+% 1-u_i &=& u_j u_k (u_{jk})^2 (u_{0jk})^3 (u_{0k})^2(u_{0 j})^2 u_{0} \left(1+ u_i u_{ij} u_{ik} u_{0ik} u_{0ij}  u_{0i}\right),  1-u_{ij} = u_k u_{ik} u_{jk} (u_{0jk})^2 (u_{0ik})^2 (u_{0 k})^2 u_{0 j} u_{0 i} u_{0} \nonumber  \\
+% 1-u_{0 j k} &=& u_i u_{ij} u_{ik} u_{0 i k} u_{0 i j}  u_{0 i}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 1-u_{0 k} = u_i u_{j}  (u_{ij})^2 u_{ik} u_{jk} (u_{123})^2 (u_{0 i j})^2 u_{0 j} u_{0 i}  \nonumber \\
+% 1-u_{0} &=& u_1 u_{2} u_{3} (u_{12})^2 (u_{23})^2  (u_{13})^2 (u_{123})^3 \left(1+ u_{0}  u_{023} u_{013} u_{012} u_{03} u_{01}  u_{02} \right), 1-u_{123} = u_{023} u_{013} u_{012} u_{03} u_{01}  u_{02} u_{0}
+% \eea}
+% where $i,j,k \in {1,2,3}$ and $i \neq j \neq k$.
 
@@
 
-Here we will show that the $u_{I}$'s for the permutahderon $\mathscr{P}_{n}$, which is defined as 
-\begin{equation}
-   u_{I}:= \prod_{J\supset I}x_J^{(-1)^{|I|-|J|}} \:, \label{uforpn}
-\end{equation}
+Here we will show that the $u_{I}$'s for the permutahderon $\mathscr{P}_{n}$, which is defined by eq.\eqref{uvarforPn},
+% \begin{equation}
+%    u_{I}:= \prod_{J\supset I}x_J^{(-1)^{|I|-|J|}} \:, \label{uforpn}
+% \end{equation}
 have the desired binary property, that is, $u_{I}$ and $u_{J}$ are compatible if and only if $I \subset J$ or $J\subset I$, otherwise, they are incompatible.
@@
 
-A crucial observation here is that $u_{I}\to 0$ is equivalent to $x_{I}\to 0 $ according to \eqref{uforpn} since all $x_{i}$ are positive.
+A crucial observation here is that $u_{I}\to 0$ is equivalent to $x_{I}\to 0 $ according to \eqref{uvarforPn} since all $x_{i}$ are positive.
 We can approach this limit by replacing $x_{i}$ with $ \epsilon x_{i}$ for all $i\in I$ then taking $\epsilon \to 0$.
@@
 It is obvious that $u_{I}$ and $u_{J}$ are incompatible if either (1) $I\cap J=  \varnothing$  or (2) $I\cap J \neq \varnothing,I, J $.
-For the first case, let us denote $K=[0,n]-(I\cup J)$ as the complement set of $[0,n]$ with respect to $I\cup J$.
+For the first case, let us denote $K=[0,n]-I-J$ as the complement set of $[0,n]$ with respect to $I\cup J$.
 Then we find the logarithm of $u_{J}$ can be written as
@@
 \end{equation}
-where $I'=I-J$, $J'=J-I$ and $K=[0,n]-(I\cup J)$. Then a similar argument as in \eqref{incompn1} gives $\log u_{J}\to 0$ under the limits of all $x_{i}\to 0$ with $i\in I$.
-
-Now let us consider the behaviour of compatible $u$-variables under this limit. For $J\subset I$, we again introduce $I'=I-J$ and $K=[0,n]-I$, then the logarithm of $u_{J}$ can be written as 
+where $I'=I-J$, $J'=J-I$ and $K=[0,n]-(I\cup J)$. Then a similar argument as in \eqref{incompn1} gives $\log u_{J}\to 0$ under the limit of all $x_{i}\to 0$ with $i\in I$.
+
+Now let us consider the behaviour of compatible $u$-variables under this limit. For $J\subset I$, we again introduce $I'=I-J$ and $K=[0,n]-I$, then the logarithm of $u_{J}$ can written as 
 \begin{equation}
@@
 
-\subsubsection{The binary aspects of $u$-variables for generalized permutohedra}
+\subsubsection{$u$-equations of ${\mathscr P_n}$}
+
+For a permutohedra $\mathscr P_n$, we can directly use eq.\eqref{GPfacet} to express $x_I$ by $\{u_I\}$ which gives us many algebraic equations of $u$-variables:
+\[
+\prod_{I}x_I^{S_I}=\prod_{J}u_J^{F_J}=\prod_{J}\prod_{I\subset J}u_J^{S_I}=\prod_{I}\biggl(\prod_{J\supset I}u_J\bigg)^{S_I},
+\]
+so
+\begin{equation}\label{xinu}
+x_I=\prod_{J\supset I}u_J
+\end{equation}
+for any $I\in \mathscr P_n$, where we introduce a fake $u$-variable 
+$u_{[0,n]}:=x_{[0,n]}$. We know some algebraic equations of $\{x_I\}$, 
+for example, linear equations $x_I+x_J=x_{I\cup J}$ for $I\cap J=\varnothing$, 
+so
+\begin{equation*}
+	\prod_{K\supset I}u_K+\prod_{K\supset J}u_K=\prod_{K\supset I\cup J}u_K
+\end{equation*}
+or equivalently
+\begin{equation}
+\prod_{I\subset K,K\not\supset I\cup J}u_K +
+\prod_{J\subset K,K\not\supset I\cup J}u_K = 1.
+\end{equation}
+
+Let us consider the $2 d$ example for which the relations are :
+\bea
+1-u_1 u_{12} &=&u_0 u_{02}, ~~1-u_2 u_{12} =u_0 u_{01},~~1-u_{12}= u_0 u_{01} u_{02} \nonumber \\
+1- u_{01}&=& u_{0}u_1 u_{01}u_{12},~~1-u_0 u_{02}= u_{0}u_2 u_{02} u_{12}
+\eea
+By rewriting $(1-u_i)= (1-u_i u_{12})-u_i(1-u_{12}))$ we can get $u$-equations for $u_i$ with $i=1,2$.
+Similarly by rewriting $(1-u_0)=(1-u_0 u_{01} u_{02})-u_0 (1-u_{01})-u_0 u_{01}(1-u_{02}) $ we can get the $u$-equation for $u_0$
+\bea
+1-u_1&=&u_0 u_{02}(1-u_1 u_{01}), ~~1-u_2 =u_0 u_{01}(1-u_2 u_{02}),~~1-u_{12}= u_0 u_{01} u_{02} \nonumber \\
+1- u_{01}&=& u_{0}u_1 u_{01}u_{12},~~1-u_0 u_{02}= u_{0}u_2 u_{02} u_{12}~~1-u_0=u_1 u_{12}(1-u_0 u_{01})
+\eea
+More generally we can rewrite 
+\bea
+(1-u_I)= (1- \prod_{I \subset J} u_I) -u_I(1-u_{I_1})-u_I u_{I_1}(1-u_{I_2})-\cdots-\prod_{I \subsetneq [1~n]}(1-u_{12\cdots n})
+\eea
+Since $I \subsetneq I_1,I_2$ $|I|< |I_1|,|I_2|$ thus we already know the $u$-equations for $I_1,I_2,\cdots,[1,n]$ as we recursively find them starting from $|I|=n$.
+
+A nice fact about the $u$-equations we obtain is that $1-u_I$ are all at most linear and multi term in $u_I$ for any $n$.
+However, they do not make the factorization manifest at the level of $u$-equations as we take some $u_I \rightarrow 0$.
+The $u$-equations for $\mathscr{P}_n$ which make factorization manifest are complicated polynomials of order $n-|I|-1$ in the corresponding $u$'s.
+Thus, the most general $u$-equations can be conjectured to be:
+\bea
+1-u_{I} = \prod_{J} u^{s_J}_{J} F(u_I, u_J,u_K) 
+\eea
+where, $J$ are all sets incompatible with $I$, $K$ are all sets compatible with $I$ excluding itself and $s_J$ are positive integers.
+$F(u_I, u_J,u_K) $ is polynomial of degree $n-|I|-1$ in $u_I$ and we conjecture that $F(u_I =0, u_J,u_K) = 1$ which makes $\mathscr{P}_n$ binary as we proved using a different method in the previous section.
+But we do not have a closed form expression for $F(u_I, u_J,u_K)$ for all $n$.
+
+Some of the simplest ones are:\\
+
+For $|I| =n-1$ and $s_K = \begin{cases}  1,~ if K \not\subset I & \\ 2, ~if K \subset I\end{cases}$
+
+\bea
+1-u_{I} &=& \prod_ {S - I \subset J } u_{J} \prod_ {K \cap I \ne \Phi } (u_{\bar{K}})^{s_K}  \nonumber \\
+1-u_{12\cdots n} &=& \prod_ {{I \subset S}\atop {I \ne \Phi}} u_{\bar{I}} \nonumber
+\eea
+and for $|I| =n-2$ with $ \bar{I} = \{i, j\}$
+\bea
+1-u_{I}= u_i u_j u^{2}_{ij} \prod_{J \subset I} u_{J \cup \{i\}} u_{J \cup \{j\}} u^{2}_{J \cup \{i,j\}} \prod_{K \subset S-I} (u_{\bar{K}})^{3} (u_{\bar{K \cup \{i\}}})^{2}  (u_{\bar{K \cup\{j\}}})^{2}  u_{\bar{K\cup \{i,j\}}} \left( 1+ u_{\bar{\{i\}}} u_{\bar{\{j\}}} u^{'}_{\bar{\{ij\}}} \prod_{I \subset L} u_L \right)                       \nonumber
+\eea
+
+Using eq.\eqref{xinu}, we can say more on $u$-equations,
+\[
+1-u_I=1-\prod_{J\supset I}x_J^{(-1)^{|J|-|I|}}=\frac{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J-\prod_{|J|-|I| \text{ even}; J\supset I}x_J}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J}
+=\frac{f_{I,n}\prod_{i\not\in I}x_i}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J},
+\]
+where $f_{I,n}$ is a polynomial with positive coefficients. It's easy to see $x_i$ for $i\not\in I$ is a factor of the numerator by setting $x_i=0$.
+From
+\[
+\prod_{i\not\in I}x_i=\prod_J u_J^{|J|-|I\cap J|}
+\quad\text{and}\quad
+\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
+=
+\prod_{J\supsetneq I}u_J^{2^{|J|-|I|-1}},
+\]
+then
+\[
+\prod_{i\not\in I}x_i\bigg/\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
+=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supsetneq I} u_J^{|J|-|I|-2^{|J|-|I|-1}}.
+\]
+Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's natural to conjecture that
+\begin{equation}
+1-u_I=g(u)\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
+\end{equation}
+where $g$ is a polynomial.
+The product $\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}$ has appeared in all known examples with right powers.
+It's clear that any compatible $u_J$ for $J\subset I$ doesn't appear in the product because $I\cap J=J$.
+Thus, the final conjecture is about the compatibility degree:
+\[
+(I||J)=|J|-|I\cap J|\text{ for $I\not\subset J$},\quad  (I||J)=0 \text{ for $I\subset J$}.
+\]
+It's not symmetric when $|I|\neq |J|$.
+
+We conjecture (and have checked upto $n=6$) that we can solve the $u$-equations in terms of $u_1,u_{12},\cdots,u_{12\cdots n} $ for the rest of the $u$'s.
+
+ \bea
+\int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} \frac{d x_i}{x_i} \prod_{I} \left(x_I \right) ^{-\alpha^{'} S_I} &=& \int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} \frac{d x_i}{x_i} \prod_{\alpha} \left(u_I \right) ^{-\alpha^{'} F_{\alpha}} \\
+&=&\int_{[0,1]^n} \prod_{i =1}^{n} \frac{d u_{1\cdots i}}{u_{1\cdots i}(1-u_{1\cdots i})} \prod_{\alpha} \left(u_I(u_{1\cdots i}) \right) ^{-\alpha^{'} F_{\alpha}}
+\eea
+
+\subsubsection{Degenerations of ${\mathscr P_n}$ which lead to  products}
+
+In this section we provide an answer to the question of which degenerations of $\mathscr{P_n}$ give the most general products of such geometries.
+We begin by stating the following results about Nestohedra.
+
+The maximal set of a building set $B_{max}$ is the set of all inclusion maximal elements of the building set $B$. A building set $B$ is connected if $B_{max}$ has a single element.
+
+{\bf Theorem:} If $B_1, B_2,\cdots B_n$ are connected subsets of a building set $B$ then the corresponding nestohedron ${\mathscr N_B}$ is isomorphic to the product of the nestohedra ${\mathscr N}_{ B_1} \times{\mathscr N}_{ B_2} \cdots \times {\mathscr N}_{B_n}$.
+
+We can use the above result to construct a degeneration of  ${\mathscr P_n}$ which are the most general products i.e., $\prod_{p_i} X_{p_i}$ such that $\sum^{k}_{i=1} p_{i} = n$ and $X = {\mathscr A} ,{\mathscr B}, {\mathscr P }$ by dividing the $(n+1)$ singlets into $k$ parts $\{0,\cdots,p_1\}, \{p_1,\cdots,p_1+p_2\},\cdots \{\sum^{k-1}_{i=1}p_{i},\cdots,\sum^{k}_{i=1}p_{i}= n\}$ and constructing the corresponding $X_{p_i}$'s which we denote by $X_{p_i}\left(\sum^{(i-1)}_{j=1}p_{j},\cdots,\sum^{i}_{j=1}p_{j}\right).$
+
+Let us consider the $P_4$ example for which the allowed possibilities are : $A_1^{4}$, $A_1^2 \times A_2$, $A_1 \times A_3$, $A^{2}_2$, $A_1^2 \times B_2$, $A_1 \times B_3$,$A_1 \times P_3$,$ A_2\times B_2$ and $B^{2}_2$.
+
+For $A_1^{4}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} \}$ where $\{0,01\} , \{1,12\},\{2,23\},\{3,34\}$ generate the 4 $A_1$'s which we denote as $A_1(0,1) \times A_1(1,2) \times A_1(2,3) \times A_1(3,4) $.
+
+For $A_1^{2} \times A_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{234} \}$ generated by $A_1(0,1)\times A_1(1,2) \times A_2(2,3,4)$'s.
+
+For  $A_1 \times A_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{123},{234},{1234} \}$ generated by  $A_1(0,1)\times A_3(1,2,3,4)$.
+
+For  $A_2^{2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} ,{012},{234}\}$ generated by $A_2(0,1,2)\times A_2(2,3,4)$
+
+For $A_1^{2} \times B_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{24},{234} \}$ generated by $A_1(0,1)\times A_1(1,2) \times B_2(2,3,4)$'s.
+
+For $A_1 \times B_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{14},{123},{234},{134},{124},{1234} \}$ generated by  $A_1(0,1)\times B_3(1,2,3,4)$.
+
+For $A_1 \times P_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{14},{13},{24},{123},{234},{134},{124},{1234} \}$ generated by  $A_1(0,1)\times P_3(1,2,3,4)$.
+
+For $A_2 \times B_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{24},{012},{234}\}$ generated by $A_2(0,1,2)\times B_2(2,3,4)$
+
+For $B_2^{2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{02},{23},{34},{24} ,{012},{234}\}$ generated by $B_2(0,1,2)\times B_2(2,3,4)$
+
+We can similarly find a degeneration of ${\mathscr P_n}$ which would correspond to any product.
+
+\subsection{Binary aspects of generalized Permutohedra}
 
 Inspired by the $u$-variables for permutahdera, we come up with the $u$-variables for generalized permutohedra.
-To this end, let us define the generating set $\mathbf{I}$ for $I\in\mathbf{B}$ as the set of the minimum extensions of $I$ on $\mathbf{B}$, that is there is no $J\in\mathbf{B}$ such that $I\subsetneq J\subsetneq I_{a}$ for any $I_{a}\in \mathbf{I}$.
+To this end, we first find all minimum extensions $I_{a}$ of $I$ in $\mathbf{B}$, that is there is no $J\in\mathbf{B}$ such that $I\subsetneq J\subsetneq I_{a}$, and we denote the collection of these extensions by $\mathscr{G}_{I}$.
 Then, the $u$-variables for the generalized permutohedron with building set $\mathbf{B}$ are
 \begin{equation}
-   \log u_{I} :=  \log x_{I}- \sum_{I_{a}\in \mathbf{I}} \log x_{I_{a}}+\cdots +(-1)^{k}\sum _{I_{a_{1}},\cdots,I_{a_{k}}\in \mathbf{I}} \log x_{I_{a_{1}}\cup\cdots \cup I_{a_{k}}} +\cdots \:.
-\label{uvarforgenpermu}
-\end{equation}
-It is easy to check that the $u$-variables for associahedra, cyclohedra and permutohedra defined above can be viewed as the special cases of \eqref{uvarforgenpermu}.
-Let us give another slight nontrivial example to illustrate this defination.
-
-\paragraph{Example:} For the generalized permutahderon with building set 
-\[
-\mathbf{B}=\{\{0\},\{1\},\{2\},\{3\},\{0,1,2\},\{1,3\},\{0,1,2,3\}\},
-\]
-the corresponding $u$-variables are
-\begin{gather*}
-   u_{0}=\frac{x_{0}}{x_{012}} \:,\quad  u_{1}=\frac{x_{1}x_{0123}}{x_{012}x_{13}} \:,\quad 
-   u_{2}=\frac{x_{2}}{x_{012}} \:, \quad u_{3}=\frac{x_{3}}{x_{13}} \\
-   u_{012}=\frac{x_{012}}{x_{0123}}\:,\qquad u_{13}=\frac{x_{13}}{x_{0123}} \:, \quad 
-\end{gather*}
+   \log u_{I} :=  \log x_{I} +(-1)^{k}\sum _{\varnothing\neq\{I_{a_{1}},\cdots,I_{a_{k}}\}\subset \mathscr{G}_{I}} \log x(I_{a_{1}},\ldots, I_{a_{k}})  \label{uvarforgenpermu}
+\end{equation}
+where the sum is over all nonemepty subsets of $\mathscr{G}_{I}$, and we introduce
+\[
+x(I_{a_{1}},\ldots,I_{a_{k}}):=x_{I_{a_{1}}\cup \cdots \cup I_{a_{k}}}   
+\]
+to avoid too many subscripts. Obviously, an equivalent form of eq.\eqref{uvarforgenpermu} is
+\begin{equation}
+   \log u_{I} := (-1)^{k}\sum _{\{I_{a_{1}},\cdots,I_{a_{k}}\}\subset \mathscr{G}_{I}} \log \bigl(x_{I}+x(I_{a_{1}}-I,\ldots, I_{a_{k}}-I)\bigr)  \label{uvarforgenpermu1}
+\end{equation}
+It is easy to check that the $u$-variables for simplices, hypertubes, associahedra, cyclohedra and permutohedra defined above can be viewed as the special cases of \eqref{uvarforgenpermu}:
+\begin{enumerate}
+   \item For a $n$-dimensional simplex, $\mathscr{G}_{\{i\}}=\{[0,n]\}$ for every singleton $\{i\}$.
+   \item For a $n$-dimensional hypertube, $\mathscr{G}_{\{0\}}=\{[0,1]\}$, $\mathscr{G}_{\{i\neq 0\}}=\{[0,i]\}$ and $\mathscr{G}_{[0,i]}=\{[0,i+1]\}$.
+   \item For a $n$-dimensional associahedron,
+   \[
+   \mathscr{G}_{[i,j]}=\begin{cases}
+      \{[i-1,j],[i,j+1]\}   & \quad \text{if $i\neq 0$ and $j\neq n $}\\
+      \{[0,j+1]\} &\quad \text{if $i= 0$ and $j\neq n $} \\
+      \{[i-1,j]\} &\quad \text{if $i\neq 0$ and $j= n $}
+   \end{cases}   
+   \]
+   \item For a $n$-dimensional cyclohedron, $\mathscr{G}_{[i,j]}=\{[i-1,j],[i,j+1]\}$
+   \item For a $n$-dimensional permutohedron, $\mathscr{G}_{I}=\{I\cup\{j\}\vert j\in [0,n]-I \}$
+\end{enumerate}
+
+% \paragraph{Example:} For the generalized permutahderon with building set 
+% \[
+% \mathbf{B}=\{\{0\},\{1\},\{2\},\{3\},\{0,1,2\},\{1,3\},\{0,1,2,3\}\},
+% \]
+% the corresponding $u$-variables are
+% \begin{gather*}
+%    u_{0}=\frac{x_{0}}{x_{012}} \:,\quad  u_{1}=\frac{x_{1}x_{0123}}{x_{012}x_{13}} \:,\quad 
+%    u_{2}=\frac{x_{2}}{x_{012}} \:, \quad u_{3}=\frac{x_{3}}{x_{13}} \\
+%    u_{012}=\frac{x_{012}}{x_{0123}}\:,\qquad u_{13}=\frac{x_{13}}{x_{0123}} \:, \quad 
+% \end{gather*}
 
@@
 We will follow the argument in the cases of permutahdera: replacing $x_{i}$ with $ \epsilon x_{i}$ for all $i\in I$ and taking $\epsilon \to 0$, then considering the behaviour of the other $u_{J}$'s under this limit case by case.
-For future convenience, we assume that the generating set $\mathbf{J}$ for $J$ has $s$ elements denoted by $J_{a}$ with $a\in[1,s]$, and introduce
-\begin{equation}
-   p(J_{1},\ldots,J_{r}) = \sum_{a\in J_{1}\cup\cdots\cup J_{r}}x_{a}
-\end{equation}
-
-For case (1), some elements in $\mathbf{J}$ are subsets of $I\cup J$ since $I\cup J \in \mathbf{B}$ (an extreme case is that  $I\cup J$ is one element in $\mathbf{J}$, but the argument is the same).
-Without loss of generality, we denote such elements by $J_{1},\ldots J_{s'}$.
+% For future convenience, we assume that the generating set $\mathbf{J}$ for $J$ has $s$ elements denoted by $J_{a}$ with $a\in[1,s]$, and introduce 
+% \begin{equation}
+%    p(J_{1},\ldots,J_{r}) = \sum_{a\in J_{1}\cup\cdots\cup J_{r}}x_{a}
+% \end{equation}
+
+For case (1), some elements in $\mathscr{G}_{J}$ are subsets of $I\cup J$ since $I\cup J \in \mathbf{B}$.
+We denote the collection of such elements by $\mathscr{G}^{I\cup J}_{J}$.
 Then the logarithm of $u_{J}$ can be written as
 \begin{equation}
-   \log u_{J}= \sum_{\substack {1 \leq a_{1}<\cdots<a_{k}\leq s'\\ s'<b_{1}<\cdots b_{l}\leq s}}(-1)^{k+l}\log\Bigl( x_{J}+ p(J_{a_{1}}-J,\ldots,J_{a_{k}}-J) + p(J_{b_{1}}-J,\ldots, J_{b_{l}}-J)\Bigr) \:.
+   \log u_{J}= \sum_{\substack {\{J_{a_{1}},\ldots,J_{a_{k}}\}\subset \mathscr{G}^{I\cup J}_{J}\\ \{J_{b_{1}},\ldots J_{b_{l}}\}\subset \mathscr{G}_{J}-\mathscr{G}^{I\cup J}_{J}}}(-1)^{k+l}\log\Bigl( x_{J}+ x(J_{a_{1}}-J,\ldots,J_{a_{k}}-J, J_{b_{1}}-J,\ldots, J_{b_{l}}-J)\Bigr) \:.
 \label{logu1}
 \end{equation}
-Since the second term in eq.\eqref{logu1} goes to 0 under the limits of $x_{i}\to 0$ with $i\in I$, $\log u_{J}$ goes to 0 under this limit as in eq.\eqref{1incompuvarforPn}.
+Since the second term in eq.\eqref{logu1} goes to $x(J_{b_{1}}-J-I,\ldots, J_{b_{l}}-J-I)$ under the limits of $x_{i}\to 0$ with $i\in I$, $\log u_{J}$ goes to 0 under this limit as in eq.\eqref{1incompuvarforPn}.
 The whole argument can be carried over to case (2) by replacing $x_{J}$ with $x_{I\cap J}+ x_{J-I}$.
 
-For case (3), we again denote $J_{1},\ldots J_{s'}$ as the elements in $\mathbf{J}$ which are subsets of $ I$.
+For case (3), we again denote $\mathscr{G}^{I}_{J}$ as the collection of the elements in $\mathscr{G}_{J}$ which are subsets of $ I$.
 After replacing $x_{i}$ with $\epsilon x_{i}$ for $i\in I$, we find the limit of $\log u_{J}$ as $\epsilon \to 0$ is
 \begin{align}
-  &\quad \lim_{\epsilon\to 0}  \sum_{\substack {1 \leq a_{1}<\cdots<a_{k}\leq s'\\ s'<b_{1}<\cdots b_{l}\leq s}}(-1)^{k+l}\log\Bigl( \epsilon x_{J}+\epsilon p(J_{a_{1}}-J,\ldots,J_{a_{k}}-J) + p(J_{b_{1}}-J,\ldots, J_{b_{l}}-J)\Bigr) \nonumber \\
-  &=\sum_{\substack {1 \leq a_{1}<\cdots<a_{k}\leq s'}}(-1)^{k}\log\Bigl( x_{J}+ p(J_{a_{1}}-J,\ldots,J_{a_{k}}-J) \Bigr). 
+  &\quad \lim_{\epsilon\to 0}  \sum_{\substack {\{J_{a_{1}},\ldots,J_{a_{k}}\}\subset \mathscr{G}^{I}_{J}\\ \{J_{b_{1}},\ldots J_{b_{l}}\}\subset \mathscr{G}_{J}-\mathscr{G}^{I}_{J}}}(-1)^{k+l}\log\Bigl( \epsilon x_{J}+\epsilon x(J_{a_{1}}{-}J,\ldots,J_{a_{k}}{-}J,(J_{b_{1}}{-}J)\cap I,\ldots, (J_{b_{l}}{-}J)\cap I) \nonumber \\
+  & \qquad \qquad\qquad \qquad \qquad \qquad    + x (J_{b_{1}}{-}I,\ldots,J_{b_{l}}{-}I)\Bigr) \nonumber  \\
+  &=\sum_{\{J_{a_{1}},\ldots,J_{a_{k}}\}\subset \mathscr{G}_{J}^{I}} (-1)^{k+l}\log\Bigl( x_{J}+ x(J_{a_{1}}{-}J,\ldots,J_{a_{k}}{-}J) \Bigr). 
 \end{align}
@@
 \begin{equation}
-   \mathbf{B}_{I} = \{J\in\mathbf{B} \vert J\subset I\}.
+   \mathbf{B}_{I} = \{J \vert J\subset I, J\in \mathbf{B}\}.
 \end{equation}
@@
 \begin{equation}
-   \mathbf{B}_{\bar{I}} = \{J-I \vert J\subset I\}.
-\end{equation}
-
-% This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
-
-% Based on the above conjecture,  there is a statement for the binary geometries corresponding to the facet $u_{I}\to 0$, 
-% that is the $u$-system for the facet $u_{I}\to 0$ is corresponding to the generlaized permutohedra $\mathcal{P}_{I}\otimes \mathcal{P}_{\bar{I}}$ with building sets  
-% \[
-% \mathcal{B}_{I} = \{J\vert J\subset I, J\in \mathcal{B}\}
-% \]
-% and 
-% \[
-% \mathcal{B}_{\bar{I}} = \{J-I\vert  J\in \mathcal{B}-\mathcal{B}_{I} \}
-% \]
-% where $J-I$ means the complement of $J$ with respect to $I$. This statement directly follow from the fact that $u_{I}\to 0$ is equivalent to take $x_{i}\to t x_{i} $ for $i\in I$ then take $t \to 0$
-% )
-
-\subsection{u eqs}
-
-({\bf Zhenjie}: A possible way to find some $u$-equations of generalized permutohedra)
-
-For a generic generalized permutohedra $\mathscr P$, it's usually difficult to solve $S_I$ by $\{F_I\}$  from eq.\eqref{GPfacet} and then get $u$-variables in terms of $\{x_I\}$, but we can directly use eq.\eqref{GPfacet} to express $x_I$ by $\{u_I\}$ which gives us many algebraic equations of $u$-variables.
-In fact,
-\[
-\prod_{I\in \mathscr P}x_I^{S_I}=\prod_{J\in \mathscr P}u_J^{F_J}=\prod_{J\in\mathscr P}\prod_{I\subset J,I\in \mathscr P}u_J^{S_I}=\prod_{I\in\mathscr P}\biggl(\prod_{J\supset I,J\in\mathscr P}u_J\bigg)^{S_I},
-\]
-so
+   \mathbf{B}_{\bar{I}} = \{J-I \vert J\in \mathbf{B}\}.
+\end{equation}
+
+We start with the Cayley graph proposed in \cite{} and further studied in \cite{}.
+In \cite{}, the ABHY realization for general Cayley graphs have been proposed, here we will use several examples to illustrate that the binary geometries exist for general Cayley graphs.
+The first Cayley graph which is nether associahedron nor permutahderon is so-called  ``next-to-$A_{3}$'', in terms of generalized permutahdera, the building set for next-to-$A_{3}$ is
 \begin{equation}
-x_I=\prod_{J\supset I,J\in\mathscr P}u_J
-\end{equation}
-for any $I\in \mathscr P$, where we introduce a fake $u$-variable 
-$u_{[0,n]}:=x_{[0,n]}$. We know some algebraic equations of $\{x_I\}$, 
-for example, linear equations $x_I+x_J=x_{I\cup J}$ for $I\cap J=\varnothing$, 
-so (I will omit all $\text{sth}\in \mathscr P$ for convenience.)
-\begin{equation*}
-	\prod_{K\supset I}u_K+\prod_{K\supset J}u_K=\prod_{K\supset I\cup J}u_K
-\end{equation*}
-or equivalently
-\begin{equation}
-\prod_{I\subset K,K\not\supset I\cup J}u_K +
-\prod_{J\subset K,K\not\supset I\cup J}u_K = 1.
-\end{equation}
-({\bf Zhenjie}: I conjecture that all possible $u$-equations are consequences of 
-some algebraic equations of $x_I$ which is in fact we have seen in 
-the calculation of $1-u_I$. For example, the nonlinear equation (although it's
-the consequence of linear equations)
-\[
-	x_0x_{012}+x_1x_2=x_{01}x_{02}
-\]
-tells us the $u$-equation of $u_0$ of 2d permutohedron $\mathscr P_2$. Therefore,
-another related conjecture is that the variety generated by $u$-equations 
-is the one generated by eq.(\theequation) for all disjoint $I$, $J\in \mathscr P$ 
-in $u$-space. Can we prove that generalized permutohedra are binary geometries in
-this way?
-)
-
-For permutohedron $\mathscr P_n$, I conjecture that
-\[
-1-u_I=1-\prod_{J\supset I}x_J^{(-1)^{|J|-|I|}}=\frac{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J-\prod_{|J|-|I| \text{ even}; J\supset I}x_J}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J}
-=\frac{f_{I,n}\prod_{i\not\in I}x_i}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J},
-\]
-where $f_{I,n}$ is an irreducible polynomial with positive coefficients.
-It's easy to see $x_i$ for $i\not\in I$ is a factor of the numerator by setting $x_i=0$, but it's not obvious whether $f_{I,n}$ is irreducible.
-I've checked many examples, and corresponding polynomials $f_{I,n}$ are always irreducible.
-
-From
-\[
-\prod_{i\not\in I}x_i=\prod_J u_J^{|J|-|I\cap J|}
-\quad\text{and}\quad
-\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
-=
-\prod_{J\supsetneq I}u_J^{2^{|J|-|I|-1}},
-\]
-then
-\[
-\prod_{i\not\in I}x_i\bigg/\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
-=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supsetneq I} u_J^{|J|-|I|-2^{|J|-|I|-1}}.
-\]
-Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's natural to conjecture that
-\begin{equation}
-1-u_I=g(u)\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
-\end{equation}
-where $g$ is a polynomial.
-The product $\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}$ has appeared in all known examples with right powers.
-It's clear that any compatible $u_J$ for $J\subset I$ doesn't appear in the product because $I\cap J=J$.
-Thus, the final conjecture is about the compatibility degree:
-\[
-(I||J)=|J|-|I\cap J|\text{ for $I\not\subset J$},\quad  (I||J)=0 \text{ for $I\subset J$}.
-\]
-It's not symmetric when $|I|\neq |J|$.
-
-\subsection{Permutahedron as a binary geometry}
-
-\textcolor{red}{(Prashanth: An attempt to prove $P_n$ is binary using Chi's method.)}
-
-In this section we shall try to argue that the permutahedron is a binary geometry.
-
-Since, the permutahedron is permutation invariant in all $x_i$'s this should be reflected at the level of $u$'s and this is indeed the case as $u_I$ with the same $|I|$ have similar $u$'s.
-i.e $u_J$ can be obtained from $u_I$ for $|J|=|I|$ by interchange of some of the $x_i$'s.
-
-We shall prove $\mathscr P_{n+1}$ is binary by showing that whenever we take some $u_I \rightarrow 0$ (by taking a unique set of $x_i \rightarrow 0, \infty$) then $u_J \rightarrow 1$ for $J$ incompatible with $I$ and the remaining $u$'s reduce to the $u$'s corresponding to $\mathscr P_{k-1} \times \mathscr P_{(n+1)-k}$.
-
-By the argument given above it is sufficient to consider $u_1, u_{12},\cdots,u_{12...n(n+1)} \rightarrow 0$ and $u_0, u_{0(n+1)},u_{0,n(n+1)}\cdots,u_{02...n(n+1)} \rightarrow 0$.
-
-We have the following cases:
-\begin{enumerate}
-    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e $I =  \{1,2,\cdots, k \}$ with $k= 1,2,\cdots, \lfloor \frac{n+1}{2} \rfloor -1$
-
-    In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots, k $ and consider the limit $t \rightarrow 0$ to get:
-    \bea
-    u^{(n+1)}_{J \cup  I} &\rightarrow& u_{J}^{((n+1)-k )} ~\text{with}~ J\subseteq\bar{I}\\
-     u^{(n+1)}_{K} &\rightarrow& u_{K}^{(k-1)} ~\text{with}~ K\subsetneq I
-    \eea
-   which is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$
-
-    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{1,2,\cdots,k \}$ with $k= \lfloor \frac{n+1}{2} \rfloor,\cdots,(n+1)$
-
-     In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots k-1$ and $x_{k} \rightarrow t$ and  consider the limit $t \rightarrow 0$ to get:
-    \bea
-    u^{(n+1)}_{J } &\rightarrow& u_{J}^{((n+1)-k)} ~\text{with}~ J\subseteq \{1,\cdots,k-1\}\\
-     u^{(n+1)}_{J \cup \{k\}} &\rightarrow& u_{K \cup\{0\}}^{((n+1)-k)} ~\text{with}~ J\subsetneq \{1,\cdots,k-1\}
-    \eea
-     \bea
-    u^{(n+1)}_{K \cup I } &\rightarrow& u_{J}^{(k-1)} ~\text{with}~ K\subseteq \{k +1,\cdots,n+1\}\\
-     u^{(n+1)}_{K \cup \{0\}\cup I} &\rightarrow& u_{K \cup\{0\}}^{(k-1)} ~\text{with}~ K\subsetneq \{k +1,\cdots,n+1\}
-    \eea
-   which is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$ 
-    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{0,(k+1),\cdots,(n+1)\}$ with $k= \lfloor \frac{n+1}{2} \rfloor+1,\cdots,(n+1)$
-
-    In this case we take $x_i \rightarrow \frac{ x_i}{t}$ for $i=1,\cdots k-1$ and $x_{k} \rightarrow \frac{1}{t}$ and  consider the limit $t \rightarrow 0$ to get:
-    \bea
-    u^{(n+1)}_{J \cup I } &\rightarrow& u_{J}^{(n+1)-k} ~\text{with}~ J\subseteq \{1,\cdots,(k-1)\}\\
-     u^{(n+1)}_{J \cup \{k\}\cup I} &\rightarrow& u_{J \cup\{0\}}^{(k-1)} ~\text{with}~ J\subsetneq \{1 ,\cdots, k\}
-    \eea
-     \bea
-    u^{(n+1)}_{K} &\rightarrow& u_{K}^{k-1} ~\text{with}~ K\subseteq I
-    \eea
-    which again is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$. 
-    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ $I = \{0,(k+1),\cdots,(n+1)\}$ with $k= 1,\cdots, \lfloor \frac{n+1}{2} \rfloor+1$.
-
-    In this case we take $x_i \rightarrow \frac{x_i}{t}$ for $i=1,\cdots, k$ and consider the limit $t \rightarrow 0$ to get:
-    \bea
-    u^{(n+1)}_{J} &\rightarrow& u_{J}^{(n+1)-k} ~\text{with}~ J\subseteq I
-    \eea
-     \bea
-    u^{(n+1)}_{K \cup I} &\rightarrow& u_{K}^{k-1} ~\text{with}~ K\subsetneq \{1,\cdots,k\}
-    \eea
-
-     which again is a $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$. 
-\end{enumerate}
-This proves that the permutahedron $\mathscr P_n$ is indeed a binary geometry for all $n$.
-
-The above proof did not explicitly use the $u$- equations for $\mathscr P_n$. 
-The $u$-equations for $\mathscr P_n$ are complicated polynomials and Some of them are:\\
-
-For $|I| =n-1$ and $s_K = \begin{cases}  1,~ if K \not\subset I & \\ 2, ~if K \subset I\end{cases}$
-
-\bea
-1-u_{I} &=& \prod_ {S - I \subset J } u_{J} \prod_ {K \cap I \ne \Phi } (u^{'}_{K})^{s_K}  \nonumber \\
-1-u_{12\cdots n} &=& \prod_ {{I \subset S}\atop {I \ne \Phi}} u^{'}_{I} \nonumber
-\eea
-
-For $t_J = \begin{cases}  1,~ if I  \not\subset J & \\ 2, ~if I \subset J \end{cases}$
-
-\bea
-1-u^{'}_{i} &=& \prod_ {\{ i \} \subset J } u_{J} \prod_ {K \subset S- \{i\} } u^{'}_{K} \nonumber \\
-1-u^{'}_{i j} &=& \prod_ {\{i,j \}\cap J \ne \Phi} u^{t_J}_{J} \prod_ {K \subset S-\{i, j \} } (u^{'}_{K})^{2} u^{'}_{K \cup {i}} u^{'}_{K \cup{j} } \nonumber 
-\eea
-
-and for $|I| =n-2$ with $S- I = \{i, j\}$
-
-\bea
-1-u_{I}= u_i u_j u^{2}_{ij} \prod_{J \subset I} u_{J \cup \{i\}} u_{J \cup \{j\}} u^{2}_{J \cup \{i,j\}} \prod_{K \subset S-I} (u^{'}_K)^{3} (u^{'}_{K \cup \{i\}})^{2}  (u^{'}_{K \cup\{j\}})^{2}  u^{'}_{K\cup \{i,j\}} \left( 1+ u^{'}_i u^{'}_j u^{'}_{ij} \prod_{I \subset L} u_L \right)                       \nonumber
-\eea
-
-The other $u$-equations are not two or three term equations and seem to be polynomials of order $|I|=n-2$ in the corresponding $u$'s. Thus, the most general $u$-equations can be conjectured to be:
-\bea
-1-u_{I} = \prod_{J} u^{s_J}_{J} P_{|I|}(u_I, u_J,u_K) 
-\eea
-where, $J$ are all sets incompatible with $I$
-
- $K$ are all sets compatible with $I$ excluding itself 
- $s_J$ are positive integers.
-
-\section*{A degeneration of ${\mathescr P_n}$ with perfect $u$-equations}
+   \mathscr{NA}_{3}=\{\{1,2,3,4\},\{1,2,3\},\{1,3,4\},\{2,3,4\},\{1,2\},\{1,3\},\{2,3\},\{3,4\},\{1\},\{2\},\{3\},\{4\}\}
+\end{equation}
+
+the $u$ variables are 
+\begin{align}
+   &u_{1}=\frac{x_{1}x_{123}}{x_{12}x_{13}} \:, \quad  u_{2}=\frac{x_{2}x_{123}}{x_{12}x_{23}} \:,  \quad 
+   u_{3}=\frac{x_{3}x_{134}x_{234}x_{123}}{x_{34}x_{13}x_{23}x_{1234}} \:, \quad 
+   u_{4}=\frac{x_{4}}{x_{34}} \\
+   &u_{12}=\frac{x_{12}}{x_{123}} \:, \quad u_{13}=\frac{x_{13}x_{1234}}{x_{134}x_{123}} \:,\quad 
+   u_{23}=\frac{x_{23}x_{1234}}{x_{123}x_{234}} \:, \quad u_{34}=\frac{x_{34}x_{1234}}{x_{134}x_{234}} \\
+   &u_{123}=\frac{x_{123}}{x_{1234}} \:, \quad u_{134}=\frac{x_{134}}{x_{1234}} \:, \quad 
+   u_{234}=\frac{x_{234}}{x_{1234}}
+\end{align}
+The $u$ equations are
+\begin{align}
+   &1-u_{1}=u_{2}u_{3}u_{23}^{2}u_{34}u_{234}^{2} \:, \\
+   &1-u_{2}=u_{1}u_{3}u_{13}^{2}u_{34}u_{134}^{2} \:, \\
+   &1-u_{3}= u_{1}u_{2}u_{4}u_{12}^{2}(1+u_{3}u_{13}u_{23}u_{34}u_{123}u_{134}u_{234}) \:, \\
+   &1-u_{4}=u_{3}u_{13}u_{23}u_{123}  \:, \\
+   &1-u_{12} =u_{3}u_{13}u_{23}u_{34}u_{134}u_{234} \:, \\
+   &1-u_{13} =u_{2}u_{4}u_{12}u_{23}u_{34}u_{234}^{2} \:, \\
+   &1-u_{23}= u_{1}u_{4}u_{12}u_{13}u_{34}u_{134}^{2} \:, \\
+   &1-u_{34}= u_{1}u_{2}u_{12}^{2}u_{13}u_{23}u_{123}^{2} \:, \\
+   &1-u_{123}=u_{4}u_{34}u_{134}u_{234} \:, \\
+   &1-u_{134}=u_{2}u_{12}u_{23}u_{123}u_{234} \:, \\
+   &1-u_{234}=u_{1}u_{12}u_{13}u_{123}u_{134} \:, 
+\end{align}
+
+\subsection {Binary geometries with non-linear factors}
 We can also consider general Minkowski sums of non-simplices and see if these also give us any instance of polytopes with perfect $u$ equations. One such case is the following:
@@
 We consider the Minkowski sum of $n-1$ $A_2$'s with following Newton polynomial :
-\bea \label {new}
+\bea \label{new}
 \prod_{i=1}^{n} (1+x_i ) \prod_{i=1}^{n-1} (1+x_i +x_i x_{i+1}) 
@@
 u_{n+1} &=& \frac{1}{q_1}, ~u_{n+2} = \frac{p_{12}}{q_{1}q_{2}},~u_{n+3} = \frac{q_{1}}{p_{23}}, \cdots,
-u_{3n-1} = \frac{ q_{n-1}}{p_{n-1n}} \nonumber
+u_{3n-1} = \frac{ q_{n-1}}{p_{n-1n}} 
 \eea
@@
 u_{1} u_{2} , n\geq 5
-\end{cases} \nonumber 
+\end{cases} 
 \eea
@@
 1-u_{n+4} =u_{n} u_{n+2}u_{n+4} u_{n+6} ~~and~~
-1-u_{n+6+ 2 i} =u_{n-3-i} u_{n+4+2 i} u_{n+5+2 i} u_{n+8+2 i}~ for~i=0,\cdots,(n-5) \nonumber 
+1-u_{n+6+ 2 i} =u_{n-3-i} u_{n+4+2 i} u_{n+5+2 i} u_{n+8+2 i}~ for~i=0,\cdots,(n-5) 
 \eea
@@
 
-We can also replace the first the first term in the Newton polynomial \eqref{ new} with $(1+x_1+ x_2)$ and we get an identical system of $u$-equations
+We can also replace the first the first term in the Newton polynomial \eqref{new} with $(1+x_1+ x_2)$ and we get an identical system of $u$-equations
 
@@
 u_{n+1} &=& \frac{q_2}{p_{12}}, ~u_{n+2} = \frac{q_{1}}{p_{12}},~u_{n+3} = \frac{p_{23}}{q_{2}q_{3}}, \cdots,
-u_{3n-1} = \frac{ p_{12}}{q_{1}q_{2}} \nonumber
+u_{3n-1} = \frac{ p_{12}}{q_{1}q_{2}} 
 \eea
@@
 \eea
-It would be nice to see if these also correspond to some degeneration of the associahedron or if they  are generalised permutahedra.
+It would be nice to see if these also correspond to degenerations of some generalised permutahedra.
 

### 2020-05-06 draft_ABP.tex
Updates from Overleaf

@@
 
+%\usepackage{enumerate}
 \usepackage{enumitem}
@@
 
-In \cite{} the study of stringy canonical forms and binary geometries with ``perfect'' u equations, associated with the scattering of particles and strings was initiated.
+In \cite{Arkani-Hamed:2019mrd} the study of stringy canonical forms and binary geometries with ``perfect'' $u$-equations, associated with the scattering of particles and strings was initiated.
 In this paper we continue the study of binary geometries and find two large classes of new examples.
@@
 
-In \cite{} the notion of {\it stringy canonical forms} were introduced as a general framework for generalizing tree-level string amplitudes, or integrals over the moduli space ${\cal M}_{0, n}$.
+In \cite{Arkani-Hamed:2019mrd} the notion of {\it stringy canonical forms} were introduced as a general framework for generalizing tree-level string amplitudes, or integrals over the moduli space ${\cal M}_{0, n}$.
 Various nice properties of string amplitudes and their field-theory limits, such as factorizations for $\alpha' \to 0$ limit and finite $\alpha'$, channel duality and exponent softness, scattering equations, {\it etc.} all naturally extend to stringy canonical forms.
@@
 
-\paragraph{Stringy canonical forms} Motivated by this rewriting of string integral~\eqref{stringint}, we define a general stringy integral as a $d$-dimensional integral~\cite{}
+\paragraph{Stringy canonical forms} Motivated by this rewriting of string integral~\eqref{stringint}, we define a general stringy integral as a $d$-dimensional integral~\cite{Arkani-Hamed:2019mrd}
 \begin{equation}\label{stringycanonicalform}
@@
 \end{equation}
-where we allow $m$ arbitrary Laurent polynomial with non-negative coefficients, $p_I(x)$, and without loss of generality we assume exponents $X_i>0$ and $c_I>0$~\footnote{These are ``positive" stringy canonical forms, which are integrals over $\mathbb R_+^d$.
-We can also consider ``complex" case with the integrand mod-squared and integrated over $\mathbb C^d$, which are generalizations of closed-string amplitudes~\cite{}.}.
+where we allow $m$ arbitrary Laurent polynomial with non-negative coefficients, $p_I(x)$, and without loss of generality we assume exponents $X_i>0$ and $c_I>0$~\footnote{These are ``positive'' stringy canonical forms, which are integrals over $\mathbb R_+^d$.
+We can also consider ``complex'' case with the integrand mod-squared and integrated over $\mathbb C^d$, which are generalizations of closed-string amplitudes~\cite{}.}.
 
@@
 
-For the string integral \eqref{stringint}, ${\cal P}$ is nothing but the ABHY associahedron~\cite{}, whose canonical form gives bi-adjoint $\phi^3$ amplitude as the $\alpha'\to 0$ limit of \eqref{stringint}~\cite{}.
+For the string integral \eqref{stringint}, ${\cal P}$ is nothing but the ABHY associahedron~\cite{Arkani-Hamed:2017mur}, whose canonical form gives bi-adjoint $\phi^3$ amplitude as the $\alpha'\to 0$ limit of \eqref{stringint}~\cite{}.
 The poles are the planar variables $X_{i,j}$, on which \eqref{stringint} factorizes into lower-point integrals even for finite $\alpha'$.
-Moreover, the saddle point equations as $\alpha' \to \infty$ can be written as $X_i=\sum_I c_I \partial \log p_I/\partial \log x_i$ for $i=1,\cdots, d$; they provide a diffeomorphism from the integration domain to ${\cal P}$, thus $\Omega(\mathcal P)$ can be computed as a pushforward of $\prod_i d\log x_i$ via summing over the saddle points~\cite{}.
+Moreover, the saddle point equations as $\alpha' \to \infty$ can be written as $X_i=\sum_I c_I \partial \log p_I/\partial \log x_i$ for $i=1,\cdots, d$; they provide a diffeomorphism from the integration domain to ${\cal P}$, thus $\Omega(\mathcal P)$ can be computed as a pushforward of $\prod_i d\log x_i$ via summing over the saddle points~\cite{Arkani-Hamed:2017tmz}.
 In particular, for the string integral \eqref{stringint}, the scattering equations provide a map from ${\cal M}_{0,n}^+$ to ABHY associahedron, and the pushforward is equivalent to the CHY formula for $\phi^3$ amplitude~\cite{}.
@@
 $\{F_\alpha\}_{1\leq \alpha \leq v}$.  Therefore, the integral $\mathcal I(\mathbf S)$
-can be seen as a function of ``dual coordinates" $\{F_A\}$ which encourages us to 
+can be seen as a function of ``dual coordinates'' $\{F_\alpha\}$ which encourages us to 
 rewrite the integral to make it manifest by (here we collectively denote $p_J=(x_1, \cdots, x_d, p_1, \cdots, p_m)$)~\footnote{Note that one can indeed treat the monomials $x_i^{\alpha' X_i}$ on the equal footing as polynomials, since Minkowski sum w.r.t.
@@
 
-The nest simplest degenerations of $\mathscr A_n$ may be products 
+The next simplest degenerations of $\mathscr A_n$ may be products 
 $\mathscr A_i\times \mathscr A_{n-i}$, which can be realized as the following
@@
 %\end{center}
-
+\newpage
 \section{Stringy canonical forms and $u$-equations for generalized permutahedra}
@@
 for some collection of subsets $I \in [0,n]$.
-We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation only as Minkowski sums i.e., all $y_I \ge 0$ \footnote{This is mainly due to the subtle nature of the Minkowski difference operation, which makes the shape of the resulting polytope dependent on the relative magnitudes of $y_I$'s.}which are called Nestohedra.
-Throughout the paper we shall mean Nestohedra whenever we refer to generalized permutahedra unless stated otherwise.\\
+We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation only as Minkowski sums except translations i.e, $y_I \ge 0$ for all non-singlets $I$\footnote{This is mainly due to the subtle nature of the Minkowski difference operation, which makes the shape of the resulting polytope dependent on the relative magnitudes of $y_I$'s.
+We allow $y_I$ for singlets to be  negative as it is only a translation and to connect with \eqref{intgenperm}.}which are called Nestohedra.
+Throughout the paper we shall mean Nestohedra or products of Nestohedra whenever we refer to generalized permutahedra unless stated otherwise.\\
 
@@
 \end{compactenum}
-To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
-
-\paragraph*{Nested Complex} 
-A subset ${\mathbf N}$ in the building set ${\mathbf B}$ is called a {\it nested set} if it satisfies the following conditions:
-\begin{compactenum}[\quad (1)]
-    \item For any $I,J \in {\mathbf N}$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
-    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
-    \item ${\mathbf N}$ contains all maximal elements of $B$.
-\end{compactenum}
-The {\it nested complex} ${\mathbf N}({\mathbf B})$ is defined as the poset of the set of all nested sets in ${\mathbf B}$ ordered by inclusion.\\
-
-\paragraph*{Facial structure} 
-Let us assume that the set ${\mathbf B}$ associated with a generalised permutahedron ${\mathscr P_n}^{y}$ is a building set on $[0,n]$.
-Then the poset of faces ${\mathscr P_n}^{y}$ ordered by reverse inclusion is isomorphic to the nested complex ${\mathbf N}({\mathbf B})$.
-
-For each decomposition $[0,n]=  \sqcup_{I \subset {\mathbf N} } S_I $ where $S_I$ are non-empty, the face $P_n$ of ${\mathscr P_n}^{y}(y_I)$ associated with the nested set ${\mathbf N} \in {\mathbf N}({\mathbf B})$ is:
-\bea
-P_n = \sum_{{J \subset {\mathbf B}}\atop{J \cap S_I \neq \emptyset}} y_{J} \Delta_{J \cap S_I}
-\eea
-
-In summary the above results mean the following:
+To describe the combinatorial structure we need the notion of {\it Nested complex} which shall be defined in appendix \ref{appendix: A}.
+We shall only sumarize the nessecary results here and let the reader interested in the details refer appendix \ref{appendix: A}.
 
@@
 
-An improtant fact about generalised permutahedra which makes them particularly interesting is the following:
-Let, $m$ denote the number of non-singlet elements in ${\mathbf B}$ i.e., the number of $c_J$'s as explained in equation (2) 
-\bea
-N = |{\mathbf B}|-1 
- = (n+1+m)-1
- = n+m \nonumber
-\eea
-{\bf Number of facets = Number of linear equations + dimension of  gen permutahedron}
-
-Thus, generalised permutahedra have big Polytopes which are simplices. Thus its quite natural to wonder if the associated $u$-variables satisfy some kind of $u$-equations.
+Generalised permutahedra have big Polytopes which are simplices. Thus its quite natural to wonder if the associated $u$-variables satisfy some kind of $u$-equations.
 
@@
 
-(2) If ${\mathbf B}= \{[i] | i=1,\cdots,n+1 \}$ is the complete flag of intervals, then ${\mathscr P_n}^y({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
+(2) If ${\mathbf B}= \{[i] | i=0,\cdots,n \}$ is the complete flag of intervals, then ${\mathscr P_n}^y({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
 The Newton polytope of the Minkowski sum is $x_1\cdots x_n (1+x_1) \cdots (1+x_1+\cdots +x_n)$ and $u$-variables are 
@@
 
-(4) If ${\mathbf B}=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr P_n}({\bf Y})$ is the associahedron. \\
-
-(5) If ${\mathbf B}=\{ [1,i] \cup [j,n] | 1\leq  i \leq j \leq n\}$ is the set of cyclic intervals, then ${\mathscr P_n}({\bf Y})$ is the Cyclohedron.\\
+(4) If ${\mathbf B}=\{ [i,j] | 0\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr P_n}({\bf Y})$ is the associahedron. \\
+
+(5) If ${\mathbf B}=\{ [1,i] \cup [j,n] | 0 \leq  i \leq j \leq n\}$ is the set of cyclic intervals, then ${\mathscr P_n}({\bf Y})$ is the Cyclohedron.\\
 
@@
 it is natrual to associate the linear polynomial $x_I=\sum_{i\in I}x_i$ whose Newton polytope is the corresponding simplex.
-Therefore, we can write down a natrual stringy canonical form for the generalized permutahedron with the building set
-$\mathscr P$
+Therefore, we can write down a natrual stringy canonical form for the generalized permutahedron with the building set $\mathbf{B}$
 \begin{equation} \label{stringyintforgenpermutohedron}
-   \mathcal I_{\mathscr P}(\{S_I\})=\int_{\mathbb R^{n}_+}
+   \mathcal I_{\mathbf{B}}(\{S_I\})=\int_{\mathbb R^{n}_+}
 	\frac{\prod_{i=0}^n \mathrm{d}\log x_i}
-	{\operatorname{GL}(1)_+}\prod_{I\in\mathscr P}x_I^{\alpha' S_I},
+	{\operatorname{GL}(1)_+}\prod_{I\in\mathbf{B}}x_I^{\alpha' S_I},
 \end{equation}
 where the global $\operatorname{GL}(1)_+$ redundance $x_i\mapsto a x_i$ require that 
-$\sum_{I\in\mathscr P}S_I = 0$.
+$\sum_{I\in\mathbf{B}}S_I = 0$.
 
@@
 Let's first write down equations of facets of a generalised permutahedron
-with the building set $\mathscr P$. The polytope of 
-eq.\eqref{stringyintforgenpermutohedron} is given by the Minkowski sum
-\[
-	- \sum_{I\in\mathscr P,|I|>1}S_I.\Delta_I
+with the building set $\mathbf{B}$. The polytope of eq.\eqref{stringyintforgenpermutohedron} is given by the Minkowski sum
+\[
+	- \sum_{I\in\mathbf{B},|I|>1}S_I.\Delta_I
 \]
@@
 	\biggl\{(S_0,S_1,\dots,S_n)\in \mathbb R^{n+1}\,\bigg |\,
-		\sum_{i\in I}S_i = -\sum_{J\subset I,|J|>1,J\in \mathscr P}S_J,
+		\sum_{i\in I}S_i = -\sum_{J\subset I,|J|>1,J\in \mathbf{B}}S_J,
 		\quad
-		&\sum_{i=0}^nS_i=-\sum_{J\in \mathscr P,|J|>1}S_J,\\
-		&\sum_{i\in K}S_i\geq -\sum_{J\subset I,|J|>1,J\in \mathscr P}S_J
+		&\sum_{i=0}^nS_i=-\sum_{J\in \mathbf{B},|J|>1}S_J,\\
+		&\sum_{i\in K}S_i\geq -\sum_{J\subset I,|J|>1,J\in \mathbf{B}}S_J
 	\biggr\},
 \end{align*}
-where the second constrain is just $\sum_{I\in \mathscr P}S_I=0$, so the equation 
+where the second constrain is just $\sum_{I\in \mathbf{B}}S_I=0$, so the equation 
 of this facet is 
 \begin{equation}\label{GPfacet}
-	F_I:=\sum_{J\subset I,J\in\mathscr P}S_J=0.
+	F_I:=\sum_{J\subset I,J\in\mathbf{B}}S_J=0.
 \end{equation}
@@
 \end{equation}
-then
+This give us the following ABHY construction for $\mathscr{P}_{n}$:
+\begin{equation}
+    F_{I}>0 \qquad  \text{for all non-empty proper subsets of $[0,n]$ }
+\end{equation}
+and
+\begin{equation}
+    C_I = (-1)^{|I|} \left( \sum_{i \in I} X_i - \sum _{{i<j}\atop{i,j \in I}} X_{ij} +\cdots + (-1)^{|I|}  X_I \right) \text{ are positive constants.}
+\end{equation}
+Using the picture of big polytope, this also gives $u$-variables
+\begin{equation}
+  u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}. \label{uvarforPn}
+\end{equation}
+since
 \[
@@
 	\prod_{J\neq \varnothing,J\subset [0,n]}
-	\prod_{I\supset J}(x_I^{(-1)^{|J|-|I|}})^{F_J}
-\]
-gives that
-\begin{equation}
-  u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}. \label{uvarforPn}
-\end{equation}
-
-The following set of equations to define the $n$-dimensional Permutahedron: 
-\bea
-C_I = (-1)^{|I|} \left( \sum_{i \in I} S_i - \sum _{{i<j}\atop{i,j \in I}} S_{ij} +\cdots + (-1)^{|I|}  S_I \right) \nonumber
-\eea
-for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $F_{I} =0$ for $I=\{ 0,1,\cdots,n \}$. 
+	\prod_{I\supset J}(x_I^{(-1)^{|J|-|I|}})^{F_J}.
+\]
+% The following set of equations define the $n$-dimensional Permutahedron: 
+% \bea
+% C_I = (-1)^{|I|} \left( \sum_{i \in I} S_i - \sum _{{i<j}\atop{i,j \in I}} S_{ij} +\cdots + (-1)^{|I|}  S_I \right) \nonumber
+% \eea
+% for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $F_{I} =0$ for $I=\{ 0,1,\cdots,n \}$. 
 %It is clear that
@@
 
-The 8 facets of the 3d permutahedron corresponding to $u_i \rightarrow 0, u_{0jk} \rightarrow 0,u_{123} \rightarrow 0 ~and ~u_{0} \rightarrow 0$  are all $B_2$'s.
-Similarly, the 6 facets corresponding to  $u_{ij} \rightarrow 0, u_{0k} \rightarrow 0$ are all  $A^{2}_1$.
-Thus, the 3d permutahedron integral factorizes nicely on all massless poles at finite $\alpha^{'}$!.
+The 8 facets of the 3d permutahedron corresponding to $u_i \rightarrow 0$ and $u_{ijk} \rightarrow 0$ are all $\mathscr{B}_2$.
+Similarly, the 6 facets corresponding to  $u_{ij} \rightarrow 0$ are all  $\mathscr{A}^{2}_1$.
+Thus, the 3d permutahedron integral factorizes nicely on all massless poles at finite $\alpha'$!.
 
@@
 \[
-1-u_I=1-\prod_{J\supset I}x_J^{(-1)^{|J|-|I|}}=\frac{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J-\prod_{|J|-|I| \text{ even}; J\supset I}x_J}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J}
-=\frac{f_{I,n}\prod_{i\not\in I}x_i}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J},
-\]
-where $f_{I,n}$ is a polynomial with positive coefficients. It's easy to see $x_i$ for $i\not\in I$ is a factor of the numerator by setting $x_i=0$.
+1-u_I=1-\prod_{J\supset I}x_J^{(-1)^{|J|-|I|}}=\frac{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J-\prod_{|J|-|I| \text{ even}; J\supset I}x_J}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J}=:\frac{N_{I,n}(x)}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J},
+\]
+where $N_{I,n}(x)$ is a polynomial of degree $D_{I,n}=2^{|\bar I|-1}$.
+It's easy to see that $x_i$ for $i\not\in I$ is a factor of $N_{I,n}(x)$ by setting $x_i=0$, so we can define a new polynomial $f_{I,n}$ of degree $D_{I,n}-|\bar I|$ with non-negative coefficients such that
+\[
+N_{I,n}(x)=f_{I,n}(x)\prod_{i\not\in I}x_i.
+\]
+It's not so obvious that $x_i$ for $i\not\in I$ is not a factor of $f_{I,n}$, which means that the above factorization of $N_{I,n}$ is reasonable.
+In fact, the $(D_{I,n}-|\bar I|)$-th derivative of $N_{I,n}$ with respect to $x_I$ is $a_{I,n}\prod_{i\not\in I}x_i$,
+where $a_{I,n}$ is a positive integer. It's conjectured that $a_{I,n}=(|\bar I|-1)!=(n-|I|)!$.
+
 From
@@
 \prod_{i\not\in I}x_i\bigg/\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
-=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supsetneq I} u_J^{|J|-|I|-2^{|J|-|I|-1}}.
-\]
-Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's natural to conjecture that
-\begin{equation}
-1-u_I=g(u)\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
-\end{equation}
-where $g$ is a polynomial.
+=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supsetneq I} u_J^{|J|-|I|-2^{|J|-|I|-1}}
+\]
+is a rational function of $x$.
+Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's natural to rewrite that
+\begin{equation}\label{ueqofPn}
+1-u_I=g_{I,n}\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
+\end{equation}
+where 
+\[
+g_{I,n}:=f_{I,n}\bigg /\prod_{J\supsetneq I} u_J^{2^{|J|-|I|-1}-(|J|-|I|)}
+=f_{I,n}\bigg /\prod_{J\supset I, |J|-|I|\, \text{odd}\atop{|J|-|I|\geq 3}} x_J.
+\]
+We conjecture that $g$ is a polynomial of $u$ with non-negative coefficients.
 The product $\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}$ has appeared in all known examples with right powers.
 It's clear that any compatible $u_J$ for $J\subset I$ doesn't appear in the product because $I\cap J=J$.
-Thus, the final conjecture is about the compatibility degree:
-\[
-(I||J)=|J|-|I\cap J|\text{ for $I\not\subset J$},\quad  (I||J)=0 \text{ for $I\subset J$}.
+Thus, there's a conjecture about the compatibility degree:
+\[
+I||J=|J|-|I\cap J|\text{ for $I\not\subset J$},\quad  I||J=0 \text{ for $I\subset J$}.
 \]
@@
 
-\subsubsection{Degenerations of ${\mathscr P_n}$ which lead to  products}
-
-In this section we provide an answer to the question of which degenerations of $\mathscr{P_n}$ give the most general products of such geometries.
-We begin by stating the following results about Nestohedra.
-
-The maximal set of a building set $B_{max}$ is the set of all inclusion maximal elements of the building set $B$. A building set $B$ is connected if $B_{max}$ has a single element.
-
-{\bf Theorem:} If $B_1, B_2,\cdots B_n$ are connected subsets of a building set $B$ then the corresponding nestohedron ${\mathscr N_B}$ is isomorphic to the product of the nestohedra ${\mathscr N}_{ B_1} \times{\mathscr N}_{ B_2} \cdots \times {\mathscr N}_{B_n}$.
-
-We can use the above result to construct a degeneration of  ${\mathscr P_n}$ which are the most general products i.e., $\prod_{p_i} X_{p_i}$ such that $\sum^{k}_{i=1} p_{i} = n$ and $X = {\mathscr A} ,{\mathscr B}, {\mathscr P }$ by dividing the $(n+1)$ singlets into $k$ parts $\{0,\cdots,p_1\}, \{p_1,\cdots,p_1+p_2\},\cdots \{\sum^{k-1}_{i=1}p_{i},\cdots,\sum^{k}_{i=1}p_{i}= n\}$ and constructing the corresponding $X_{p_i}$'s which we denote by $X_{p_i}\left(\sum^{(i-1)}_{j=1}p_{j},\cdots,\sum^{i}_{j=1}p_{j}\right).$
-
-Let us consider the $P_4$ example for which the allowed possibilities are : $A_1^{4}$, $A_1^2 \times A_2$, $A_1 \times A_3$, $A^{2}_2$, $A_1^2 \times B_2$, $A_1 \times B_3$,$A_1 \times P_3$,$ A_2\times B_2$ and $B^{2}_2$.
-
-For $A_1^{4}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} \}$ where $\{0,01\} , \{1,12\},\{2,23\},\{3,34\}$ generate the 4 $A_1$'s which we denote as $A_1(0,1) \times A_1(1,2) \times A_1(2,3) \times A_1(3,4) $.
-
-For $A_1^{2} \times A_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{234} \}$ generated by $A_1(0,1)\times A_1(1,2) \times A_2(2,3,4)$'s.
-
-For  $A_1 \times A_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{123},{234},{1234} \}$ generated by  $A_1(0,1)\times A_3(1,2,3,4)$.
-
-For  $A_2^{2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} ,{012},{234}\}$ generated by $A_2(0,1,2)\times A_2(2,3,4)$
-
-For $A_1^{2} \times B_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{24},{234} \}$ generated by $A_1(0,1)\times A_1(1,2) \times B_2(2,3,4)$'s.
-
-For $A_1 \times B_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{14},{123},{234},{134},{124},{1234} \}$ generated by  $A_1(0,1)\times B_3(1,2,3,4)$.
-
-For $A_1 \times P_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{14},{13},{24},{123},{234},{134},{124},{1234} \}$ generated by  $A_1(0,1)\times P_3(1,2,3,4)$.
-
-For $A_2 \times B_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{24},{012},{234}\}$ generated by $A_2(0,1,2)\times B_2(2,3,4)$
-
-For $B_2^{2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{02},{23},{34},{24} ,{012},{234}\}$ generated by $B_2(0,1,2)\times B_2(2,3,4)$
-
-We can similarly find a degeneration of ${\mathscr P_n}$ which would correspond to any product.
-
 \subsection{Binary aspects of generalized Permutohedra}
 
-Inspired by the $u$-variables for permutahdera, we come up with the $u$-variables for generalized permutohedra.
+Inspired by the $u$-variables for permutahdera, we directly come up with the $u$-variables for generalized permutohedra.
 To this end, we first find all minimum extensions $I_{a}$ of $I$ in $\mathbf{B}$, that is there is no $J\in\mathbf{B}$ such that $I\subsetneq J\subsetneq I_{a}$, and we denote the collection of these extensions by $\mathscr{G}_{I}$.
@@
 It is easy to check that the $u$-variables for simplices, hypertubes, associahedra, cyclohedra and permutohedra defined above can be viewed as the special cases of \eqref{uvarforgenpermu}:
-\begin{enumerate}
+\begin{enumerate}[label=(\roman*)]
    \item For a $n$-dimensional simplex, $\mathscr{G}_{\{i\}}=\{[0,n]\}$ for every singleton $\{i\}$.
@@
 
-We start with the Cayley graph proposed in \cite{} and further studied in \cite{}.
-In \cite{}, the ABHY realization for general Cayley graphs have been proposed, here we will use several examples to illustrate that the binary geometries exist for general Cayley graphs.
+\paragraph{Example}  We start with the Cayley graph proposed in \cite{} and further studied in \cite{}.
+In \cite{}, the ABHY realization for general Cayley graphs have been proposed, here we will use several examples of Cayley graphs to illustrate that the binary geometries exist for general permutohedra.
 The first Cayley graph which is nether associahedron nor permutahderon is so-called  ``next-to-$A_{3}$'', in terms of generalized permutahdera, the building set for next-to-$A_{3}$ is
@@
 
-\section{Appendix}
+\newpage
+
+\appendix 
+\section{Appendix: Nested Complex}\label{appendix: A}
+
+A subset ${\mathbf N}$ in the building set ${\mathbf B}$ is called a {\it nested set} if it satisfies the following conditions:
+\begin{compactenum}[\quad (1)]
+    \item For any $I,J \in {\mathbf N}$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
+    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
+    \item ${\mathbf N}$ contains all maximal elements of $B$.
+\end{compactenum}
+The {\it nested complex} ${\mathbf N}({\mathbf B})$ is defined as the poset of the set of all nested sets in ${\mathbf B}$ ordered by inclusion.\\
+
+\paragraph*{Facial structure} 
+Let us assume that the set ${\mathbf B}$ associated with a generalised permutahedron ${\mathscr P_n}^{y}$ is a building set on $[0,n]$.
+Then the poset of faces ${\mathscr P_n}^{y}$ ordered by reverse inclusion is isomorphic to the nested complex ${\mathbf N}({\mathbf B})$.
+
+The face $P_N$ of ${\mathscr P_n(y)}$ associated with the nested set $N \in \mathcal{N}(B)$ is given by:
+\bea
+P_N = \left \{ \right (t_1,\cdots,t_{n}) \in \mathbb{R}^{n} | \sum_{i \in I} t_i =y_{I}~{\rm for}~I \in N; ~ \sum_{i \in J}~t_i \geq y_J,~ {\rm for} ~J \in B  )\}
+\eea
+In particular the dimension of the face $P_N$ equals $n+1-|N|$.\\ 
+Another description of the faces is the following:
+
+For each decomposition $[0,n]=  \sqcup_{I \subset {\mathbf N} } S_I $ where $S_I$ are non-empty, the face $P_N$ of ${\mathscr P_N}^{y}(y_I)$ associated with the nested set ${\mathbf N} \in {\mathbf N}({\mathbf B})$ is:
+\bea
+P_N = \sum_{{J \subset {\mathbf B}}\atop{J \cap S_I \neq \emptyset}} y_{J} \Delta_{J \cap S_I}
+\eea
+\subsubsection{Degenerations of ${\mathscr P_n}$ which lead to  products}
+
+In this section we provide an answer to the question of which degenerations of $\mathscr{P_n}$ give the most general products of such geometries.
+We begin by stating the following results about Nestohedra.
+
+The maximal set of a building set $B_{max}$ is the set of all inclusion maximal elements of the building set $B$. A building set $B$ is connected if $B_{max}$ has a single element.
+
+{\bf Theorem:} If $B_1, B_2,\cdots B_n$ are connected subsets of a building set $B$ then the corresponding nestohedron ${\mathscr N_B}$ is isomorphic to the product of the nestohedra ${\mathscr N}_{ B_1} \times{\mathscr N}_{ B_2} \cdots \times {\mathscr N}_{B_n}$.
+
+We can use the above result to construct a degeneration of  ${\mathscr P_n}$ which are the most general products i.e., $\prod_{p_i} X_{p_i}$ such that $\sum^{k}_{i=1} p_{i} = n$ and $X = {\mathscr A} ,{\mathscr B}, {\mathscr P }$ by dividing the $(n+1)$ singlets into $k$ parts $\{0,\cdots,p_1\}, \{p_1,\cdots,p_1+p_2\},\cdots \{\sum^{k-1}_{i=1}p_{i},\cdots,\sum^{k}_{i=1}p_{i}= n\}$ and constructing the corresponding $X_{p_i}$'s which we denote by $X_{p_i}\left(\sum^{(i-1)}_{j=1}p_{j},\cdots,\sum^{i}_{j=1}p_{j}\right).$
+
+Let us consider the $P_4$ example for which the allowed possibilities are : $A_1^{4}$, $A_1^2 \times A_2$, $A_1 \times A_3$, $A^{2}_2$, $A_1^2 \times B_2$, $A_1 \times B_3$,$A_1 \times P_3$,$ A_2\times B_2$ and $B^{2}_2$.
+
+For $A_1^{4}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} \}$ where $\{0,01\} , \{1,12\},\{2,23\},\{3,34\}$ generate the 4 $A_1$'s which we denote as $A_1(0,1) \times A_1(1,2) \times A_1(2,3) \times A_1(3,4) $.
+
+For $A_1^{2} \times A_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{234} \}$ generated by $A_1(0,1)\times A_1(1,2) \times A_2(2,3,4)$'s.
+
+For  $A_1 \times A_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{123},{234},{1234} \}$ generated by  $A_1(0,1)\times A_3(1,2,3,4)$.
+
+For  $A_2^{2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} ,{012},{234}\}$ generated by $A_2(0,1,2)\times A_2(2,3,4)$
+
+For $A_1^{2} \times B_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{24},{234} \}$ generated by $A_1(0,1)\times A_1(1,2) \times B_2(2,3,4)$'s.
+
+For $A_1 \times B_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{14},{123},{234},{134},{124},{1234} \}$ generated by  $A_1(0,1)\times B_3(1,2,3,4)$.
+
+For $A_1 \times P_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{14},{13},{24},{123},{234},{134},{124},{1234} \}$ generated by  $A_1(0,1)\times P_3(1,2,3,4)$.
+
+For $A_2 \times B_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{24},{012},{234}\}$ generated by $A_2(0,1,2)\times B_2(2,3,4)$
+
+For $B_2^{2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{02},{23},{34},{24} ,{012},{234}\}$ generated by $B_2(0,1,2)\times B_2(2,3,4)$
+
+We can similarly find a degeneration of ${\mathscr P_n}$ which would correspond to any product.
 
@@
 \bibliographystyle{utphys}
-\bibliography{final}
+\bibliography{draft_ABP}
 \end{document}

### 2020-05-15 draft_ABP.tex
Update draft_ABP.tex
Updates from Overleaf

@@
 
-{\Large \bf  Binary geometries: Associahedra, Cyclohedra and (Generalized) Permutahedra}
+{\Large \bf Stringy canonical forms and binary geometries from associahedra, cyclohedra and generalized permutohedra}
 
@@
 
-In \cite{Arkani-Hamed:2019mrd} the study of stringy canonical forms and binary geometries with ``perfect'' $u$-equations, associated with the scattering of particles and strings was initiated.
-In this paper we continue the study of binary geometries and find two large classes of new examples.
-The first class corresponds to degenerations of $A_n$ and $B_n$ (associahedra and cyclohedra respectively) which have perfect $u$-equations.
-The second class corresponds to a large subset of  generalized permutahedra which can be realised as degenerations of the permutahedron $P_n$ which are binary positive geometries despite not having perfect $u$-equations.
-Both these large classes of examples have stringy integrals which factorise at any finite $\alpha^{'}$  on all the massless poles.
+Stringy canonical forms are a class of integrals that provide $\alpha'$-deformations of the canonical form of any polytopes.
+For generalized associahedra of finite-type cluster algebra, there exist completely rigid stringy integrals, whose configuration spaces are the so-called binary geometries, and for classical types are associated with (generalized) scattering of particles and strings.
+In this paper we propose a large class of rigid stringy canonical forms for another class of polytopes, generalized permutohedra, which also include associahedra and cyclohedra as special cases (type $A_n$ and $B_n$ generalized associahedra).
+Remarkably, we find that the configuration spaces of such integrals are also binary geometries, which were suspected to exist for generalized associahedra only.
+For any generalized permutohedron that can be written as Minkowski sum of coordinate simplices, we show that its rigid stringy integral factorizes into products of lower integrals for massless poles at finite $\alpha'$, and the configuration space is binary although the $u$ equations take a more general form than those ``perfect'' ones for cluster cases.
+Moreover, we provide an infinite class of examples obtained by degenerations of type $A_n$ and $B_n$ integrals, which have perfect $u$ equations as well.
+Our results provide yet another family of generalizations of the usual string integral and moduli space, whose physical interpretations remain to be explored.
 
@@
 \newpage
+
 \section{Introduction}
-
-In \cite{Arkani-Hamed:2019mrd} the notion of {\it stringy canonical forms} were introduced as a general framework for generalizing tree-level string amplitudes, or integrals over the moduli space ${\cal M}_{0, n}$.
-Various nice properties of string amplitudes and their field-theory limits, such as factorizations for $\alpha' \to 0$ limit and finite $\alpha'$, channel duality and exponent softness, scattering equations, {\it etc.} all naturally extend to stringy canonical forms.
-To briefly summarize the idea, let's begin with the disk integral for open-string amplitudes with ordering $(1,2,\cdots, n)$:
+In \cite{Arkani-Hamed:2019mrd} the notion of {\it stringy canonical forms} was introduced which provides vast generalizations of tree-level string amplitudes as integrals over the moduli space ${\cal M}_{0, n}$~\footnote{The study of these types of integrals perhaps dates back to Euler, and more recently they are studied in various contexts, see~\cite{Mellin, Eulermellin, Panzer:2019yxl}.
+}.
+Various nice properties of string amplitudes and their field-theory limits, such as factorizations for $\alpha' \to 0$ limit and finite $\alpha'$, channel duality and exponential softness at UV, scattering equations, {\it etc.} all naturally extend to stringy canonical forms.
+To briefly summarize the idea, let's begin with the disk integral for the open-string amplitudes with ordering $(1,2,\dots, n)$:
 \begin{equation}\label{stringint}
-{\cal I}^{\rm open-string}_{1,2,\cdots,n} (\{s\}):=\int_{\mathcal M_{0,n}^+}
+{\cal I}^{\rm open-string}_{1,2,\dots,n} (\{s\}):=\int_{\mathcal M_{0,n}^+}
 \frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i{+}1}}
@@
 \end{equation}
-where $\mathcal M_{0,n}^+$ is the positive part of moduli space for the ordering, and $\mathsf{PT}_n:=\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i+1}}$ its canonical form~\cite{};  %each factor  $(z_j-z_i)$ in the Kobe-Nieson factor $\prod_{i<j}(z_j-z_i)^{\alpha' s_{ij}}$ is a nowhere vanishing function on $\mathcal M_{0,n}^+$.
-With a positive parameterization $\{x_1,\dots,x_{n-3}\}$ of $\mathcal M_{0,n}^+$, 
-this canonical form becomes $\prod_{i=1}^{n-3}\mathrm d \log x_i$, and the Koba-Nieson factor $\prod_{i<j}(z_j-z_i)^{\alpha' s_{i j}}$ becomes a product of powers of polynomials with 
-non-negative coefficients~\cite{}: $\prod_i x_i^{\alpha' X_i} \prod_I p_I(x)^{-\alpha' c_I}$.
+where $\mathcal M_{0,n}^+$ is the positive part of moduli space for the ordering, and $\mathsf{PT}_n:=\frac{\mathrm d^{n}z}{\mathrm{SL}(2,\mathbb{R})} \prod_{i=1}^{n}\frac{1}{z_{i}-z_{i+1}}$ its canonical form~\cite{Arkani-Hamed:2017mur}.
+%each factor  $(z_j-z_i)$ in the Kobe-Nieson factor $\prod_{i<j}(z_j-z_i)^{\alpha' s_{ij}}$ is a nowhere vanishing function on $\mathcal M_{0,n}^+$.
+With a positive parametrization $\{x_1,\dots,x_{n-3}\}$ of $\mathcal M_{0,n}^+$, 
+this canonical form becomes $\prod_{i=1}^{n-3}\mathrm d \log x_i$, and the Koba-Nielsen factor $\prod_{i<j}(z_j-z_i)^{\alpha' s_{i j}}$ becomes a product of powers of polynomials with 
+non-negative coefficients~\cite{Arkani-Hamed:2019mrd}: $\prod_i x_i^{\alpha' X_i} \prod_I p_I(x)^{-\alpha' c_I}$.
 Note that we have factored out $n{-}3$ monomials, $x_i$, and left with $n(n{-}3)/2-(n{-}3)$ positive polynomials $p_I(x)$, with exponents $X_i$'s and $c_I$'s given by linear combinations of the Mandelstam variables $s_{i,j}$.
@@
 \end{equation}
-where we allow $m$ arbitrary Laurent polynomial with non-negative coefficients, $p_I(x)$, and without loss of generality we assume exponents $X_i>0$ and $c_I>0$~\footnote{These are ``positive'' stringy canonical forms, which are integrals over $\mathbb R_+^d$.
-We can also consider ``complex'' case with the integrand mod-squared and integrated over $\mathbb C^d$, which are generalizations of closed-string amplitudes~\cite{}.}.
-
-Any integral of the form \eqref{stringycanonicalform} inherits various remarkable properties of string amplitudes \eqref{stringint}, which all depend on the existence of a polytope $\mathcal P:=\sum_I c_I N[p_I]$; here $N[p_I]$ is the Newton polytope of the polynomial $p_I$, and we take the (weighted) Minkowski sum~\cite{}.
+where we allow $m$ arbitrary Laurent polynomials with non-negative coefficients, $p_I(x)$, and without loss of generality we assume exponents $X_i>0$ and $c_I>0$~\footnote{These are ``positive'' stringy canonical forms, which are integrals over $\mathbb R_+^d$.
+We can also consider ``complex'' cases with the integrand mod-squared and integrated over $\mathbb C^d$, which are generalizations of closed-string amplitudes~\cite{Arkani-Hamed:2019mrd}.}.
+
+Any integral of the form \eqref{stringycanonicalform} inherits various remarkable properties of string amplitudes \eqref{stringint}, which all depends on the existence of a polytope $\mathcal P:=\sum_I c_I N[p_I]$; here $N[p_I]$ is the Newton polytope of the polynomial $p_I$, and we take the (weighted) Minkowski sum~\cite{Arkani-Hamed:2019mrd}.
 First of all, one can show that the integral \eqref{stringycanonicalform} is convergent if and only if $\mathbf X=(X_1,\dots,X_d)$ is in the interior of the polytope $\mathcal P$ (we assume that ${\cal P}$ is $d$ dimensional).
-The leading order of the integral in its $\alpha'$ expansion, dressed with $d^d \mathbf X$, is given by the canonical form of the polytope, ${\Omega}(\cal P)$, thus it can be viewed as $\alpha'$-deformation of $\Omega(\cal P)$ (hence the name ``stringy canonical form").
+The leading order of the integral in its $\alpha'$ expansion, dressed with $d^d \mathbf X$, is given by the canonical form of the polytope, ${\Omega}(\cal P)$, thus it can be viewed as an $\alpha'$-deformation of $\Omega(\cal P)$ (hence the name ``stringy canonical form'').
 Generically the poles of $\Omega(\cal P)$ are given by equations of
-facets for $\mathcal P$, which are also poles of the integral at finite $\alpha'$, and the residue on any such pole is given by a stringy canonical form defined for that facet (see~\cite{} for details).
-
-For the string integral \eqref{stringint}, ${\cal P}$ is nothing but the ABHY associahedron~\cite{Arkani-Hamed:2017mur}, whose canonical form gives bi-adjoint $\phi^3$ amplitude as the $\alpha'\to 0$ limit of \eqref{stringint}~\cite{}.
+facets for $\mathcal P$, which are also poles of the integral at finite $\alpha'$, and the residue on any such pole is given by a stringy canonical form defined for that facet (see~\cite{Arkani-Hamed:2019mrd} for details).
+
+For the string integral \eqref{stringint}, ${\cal P}$ is nothing but the ABHY associahedron~\cite{Arkani-Hamed:2017mur}, whose canonical form gives bi-adjoint $\phi^3$ amplitude as the $\alpha'\to 0$ limit of \eqref{stringint}~\cite{Cachazo:2013iea}.
 The poles are the planar variables $X_{i,j}$, on which \eqref{stringint} factorizes into lower-point integrals even for finite $\alpha'$.
-Moreover, the saddle point equations as $\alpha' \to \infty$ can be written as $X_i=\sum_I c_I \partial \log p_I/\partial \log x_i$ for $i=1,\cdots, d$; they provide a diffeomorphism from the integration domain to ${\cal P}$, thus $\Omega(\mathcal P)$ can be computed as a pushforward of $\prod_i d\log x_i$ via summing over the saddle points~\cite{Arkani-Hamed:2017tmz}.
-In particular, for the string integral \eqref{stringint}, the scattering equations provide a map from ${\cal M}_{0,n}^+$ to ABHY associahedron, and the pushforward is equivalent to the CHY formula for $\phi^3$ amplitude~\cite{}.
-
-\paragraph{Configuration spaces} One way to describe the combinatorics of the polytope ${\cal P}$ is through the {\it configuration space}, {\it e.g.} as blow-up of $\mathbb R_+^D$ in the $\mathbf x$-space.
+Moreover, the saddle point equations as $\alpha' \to \infty$ can be written as $X_i=\sum_I c_I \partial \log p_I/\partial \log x_i$ for $i=1,\dots, d$; they provide a diffeomorphism from the integration domain to ${\cal P}$, thus $\Omega(\mathcal P)$ can be computed as a pushforward of $\prod_i d\log x_i$ via summing over the saddle points~\cite{Arkani-Hamed:2017tmz}.
+In particular, for the string integral \eqref{stringint}, the scattering equations provide a map from ${\cal M}_{0,n}^+$ to ABHY associahedron, and the pushforward is equivalent to the CHY formula for $\phi^3$ amplitude~\cite{Cachazo:2013hca,Cachazo:2013iea}.
+
+\paragraph{Configuration spaces} One way to describe the combinatorics of the polytope ${\cal P}$ is through the {\it configuration space}, {\it e.g.} as the blow-up of $\mathbb R_+^D$ in the $\mathbf x$-space.
 However, it is usually difficult to use $\mathbf x$ for this, even for the string integrals \eqref{stringint}.
 For example, a facet usually corresponds to a complicated limit process with $x \to 0$ or $\infty$.
-As proposed in~\cite{}, an elegant way to realize ${\cal P}$ in configuration space is by introducing a set of constrained $u$ variables $\{u_\alpha\}$.
+As proposed in~\cite{Arkani-Hamed:2019plo}, an elegant way to realize ${\cal P}$ in configuration space is by introducing a set of constrained $u$ variables $\{u_\alpha\}$.
 The configuration space is the variety defined by a set of polynomial equations satisfied by $\{u_\alpha\}$ (or $u$ equations), and the polytope ${\cal P}$ can be realized combinatorially by $\{u_\alpha \geq 0\}$.
@@
 rewrite the integral to make it manifest by (here we collectively denote $p_J=(x_1, \cdots, x_d, p_1, \cdots, p_m)$)~\footnote{Note that one can indeed treat the monomials $x_i^{\alpha' X_i}$ on the equal footing as polynomials, since Minkowski sum w.r.t.
-them amounts to merely translating the polytope $c_I N[p_I]$ by $-X_i$ in the $i$-th direction~\cite{}.}.
-
+them amounts to merely translating the polytope $c_I N[p_I]$ by $-X_i$ in the $i$-th direction~\cite{Arkani-Hamed:2019mrd}.}
 \begin{equation}
@@
 $\alpha=1,\dots, v$. Note that there's no unique way to write $S_J=F_\alpha V_J^\alpha$ if the big polyhedron is not a simplex, \textit{i.e.} $v>d+m$, and in this case,
-$u$-variables $\{u_\alpha \}$ are not independent. Therefore, it is an important special case when the big polyhedron is a simplex, \textit{i.e.} $N=v=d+m$, where $N$ is 
+$u$ variables $\{u_\alpha \}$ are not independent. Therefore, it is an important special case when the big polyhedron is a simplex, \textit{i.e.} $N=v=d+m$, where $N$ is 
 the number of facets of the big polyhedron or the original polytope $\mathcal P$,
 and inequalities $F_\alpha=S_J(V^{-1})^J_\alpha \geq 0$ are exactly the inequalities $W_a^J S_J\geq 0$ up to resales $F_\alpha \mapsto t F_\alpha$ for non-zero factors $t$, because
-there's no nontrivial linear isometry from the simplex to itself besides permutations of vertices. Therefore, we identity the label of facets $a$ with the label of 
-vertices $A$ and get $V=W^{-1}$. Furthermore, every facet of the original polytope $\mathcal P$ can be associated with a single $u_\alpha$ going to zero. 
+there's no nontrivial linear isometry from the simplex to itself besides permutations of vertices. Therefore, we identity the label of facets $\alpha$ with the label of 
+vertices $J$ and get $V=W^{-1}$. Furthermore, every facet of the original polytope $\mathcal P$ can be associated with a single $u_\alpha$ going to zero. 
 %Generally, the big polyhedron of a stringy integral is not necessary to be a simplex.
 
-\paragraph{Cluster stringy integrals and binary geometries} A class of very special integrals belong to this case~\cite{}: stringy canonical forms for generalized associahedra of finite-type cluster algebras, namely $A_n$, $B_n$, $C_n$, $D_n$, and exceptional cases ($E_6$, $E_7$, $E_8$, $F_4$, $G_2$).
-These ``cluster stringy integrals"~\cite{}, and the associated ``cluster configuration space"~\cite{}, turn out to be much more special and rigid extensions of string amplitudes \eqref{stringint} and the moduli space ${\cal M}_{0,n}$, which correspond to the case of type $A_{n{-}3}$.
-The leading order of such an integral is given by canonical function of the corresponding generalized associahedra, whose combinatorics is attached to the Dynkin diagram (each facet is given by removing a node), {\it e.g.} $D_n \to D_m \times A_{n{-}1{-}m}$ or $A_{n{-}1}$~\cite{}.
+\paragraph{Cluster stringy integrals and binary geometries} A class of very special integrals belong to this case~\cite{Arkani-Hamed:2019plo}: stringy canonical forms for generalized associahedra of finite-type cluster algebras, namely $A_n$, $B_n$, $C_n$, $D_n$, and exceptional cases ($E_6$, $E_7$, $E_8$, $F_4$, $G_2$).
+These ``cluster string integrals''~\cite{Arkani-Hamed:2019plo}, and the associated ``cluster configuration spaces''~\cite{Arkani-Hamed:2019plo,Arkani-Hamed:tobeappear}, turn out to be much more special and rigid extensions of string amplitudes \eqref{stringint} and the moduli space ${\cal M}_{0,n}$, which correspond to the case of type $A_{n{-}3}$.
+The leading order of such an integral is given by canonical function of the corresponding generalized associahedra, whose combinatorics is attached to the Dynkin diagram (each facet is given by removing a node), {\it e.g.} $D_n \to D_m \times A_{n{-}1{-}m}$ or $A_{n{-}1}$~\cite{Arkani-Hamed:2019plo}.
 Even at finite $\alpha'$, it has the remarkable factorization property tied to the Dynkin diagram.
-Moreover, for type $B/C$ (known as ``cyclohedron") and $D$, the leading order is associated with one-loop bi-adjoint $\phi^3$ amplitudes.
-
-These nice properties become manifest in the configuration space: not only the big polyhedron is a simplex, the $u$-equations are of very special form:
+Moreover, for type $B/C$ (known as ``cyclohedron'') and $D$, the leading orders are associated with tadpole emission and one-loop bi-adjoint $\phi^3$ amplitudes, respectively.
+
+These nice properties become manifest in the configuration space: not only the big polyhedron is a simplex, the $u$ equations are of very special form:
 \begin{equation}\label{perfectu}
-	1-u_\alpha=\prod_{\beta} u_\beta^{(\beta|\alpha)},
-\end{equation}
-where the product is over all $N$ variables ($N$ facets), and the integer $(\beta | \alpha)\geq 0$ is the so-called compatibility degree defined in the corresponding cluster algebra~\cite{}.
-%Varieties defined by $u$-equations associated with finite type clusters  are called cluster configuration spaces. 
-We see that when $u_\alpha$ (for a facet $\alpha$) goes to $0$, it forces all the $u_\beta$ with $\beta | \alpha>0$ goes to $1$ (for facets $\beta$ are exactly those {\it incompatible} with $\alpha$); the remaining $u$'s that are compatible with $u_\alpha$ satisfy $u$ equations for the facet, which factorizes as removing a node of the Dynkin diagram.
+	1-u_\alpha=\prod_{\beta} u_\beta^{(\beta||\alpha)},
+\end{equation}
+where the product is over all $N$ variables ($N$ facets), and the integer $(\beta || \alpha)\geq 0$ is the so-called compatibility degree defined in the corresponding cluster algebra~\cite{Zelevinskysys}.
+Varieties defined by $u$ equations associated with finite type clusters  are called cluster configuration spaces.
+We see that when $u_\alpha$ (for a facet $\alpha$) goes to $0$, it forces all the $u_\beta$ with $\beta || \alpha>0$ goes to $1$ (for facets $\beta$ are exactly those {\it incompatible} with $\alpha$); the remaining $u$'s that are compatible with $u_\alpha$ satisfy $u$ equations for the facet, which factorizes as removing a node of the Dynkin diagram.
 Therefore, we say that the configuration space is a {\it binary geometry}.
-Note that this is true also for the complex case, and if we further require all $u$ variables to be positive, we have $0<u<1$ which gives the positive configuration space~\cite{}.
+Note that this is true also for the complex case, and if we further require all $u$ variables to be positive, we have $0<u<1$ which gives the positive configuration space~\cite{Arkani-Hamed:2020cig}.
 The binary property is what guarantees the stringy integral to factorize even at finite $\alpha'$: on the pole $X_\alpha \to 0$, $u_\alpha\to 0$ forces all incompatible $u_\beta\to 1$ which decoupled from $\prod u^{\alpha' X}$, and the integral becomes the factorized one for the facet $\alpha$.
@@
 %\] where $p_{ij}=x_i+\cdots+x_{j-1}$. 
-and the $N=n(n{-}3)/2$ $u$ variables of this configuration space are~\cite{}
+and the $N=n(n{-}3)/2$ $u$ variables of this configuration space are~\cite{Arkani-Hamed:2020cig}
 \[
@@
 \]
-and they satisfy the $u$-equations
-\[
-	1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl},
-\]
+and they satisfy the $u$ equations (see {\it e.g.}~\cite{Brown:2009qja})
+\begin{equation}\label{Aueq}
+	1-u_{ij}=\prod_{(k,l)\not\sim (i,j)} u_{kl},
+\end{equation}
 where $(i,j)\not\sim (k,l)$ means that the diagonals $(i,j)$ and $(k,l)$ of $n$-gon are crossed, thus the two facets are incompatible (note here compatibility degree is just $0$ or $1$).
 For $u_{i,j}\to 0$, all incompatible $u_{k,l} \to 1$, and the remaining $u$'s fall into those of the two polygons divided by $(i,j)$, with their own $u$ equations.
-The Koba-Nilesen factor becomes $\prod_{i,j} u_{i,j}^{\alpha' X_{i,j}}$ where $X_{i,j}$ are planar variables for the facets of ABHY associahedron, which makes the factorization of string amplitude at finite $\alpha'$ manifest.
-All these generalize to integrals and configuration spaces for finite type cluster algebra.
+The Koba-Nielsen factor becomes $\prod_{i,j} u_{i,j}^{\alpha' X_{i,j}}$ where $X_{i,j}$ are planar variables for the facets of ABHY associahedron, which makes the factorization of string amplitude at finite $\alpha'$ manifest.
+All these generalize to integrals and configuration spaces for finite type cluster algebras.
 
@@
 
-It is a natural question to ask if binary geometries, whose stringy integrals factorize at any finite $\alpha^{'}$, are extremely special and can only be products of generalized associahedra of finite type.
+It is a natural question to ask if binary geometries, whose stringy integrals factorize at any finite $\alpha'$, are extremely special and can only be products of generalized associahedra of finite type.
 In this paper we answer the question in the negative by providing infinitely many new examples of binary geometries.
-Before proceeding, we remark that $u$ equations of the form \eqref{perfectu} (which we refer to as ``perfect" $u$ equations) imply binary geometries, but the converse is not true.
-Broadly speaking, for a $n$-dimensional polytope ${\cal P}$ where each facet is associated with a $u$ variable,  if for any $u_\alpha\to 0$, we have for all incompatible facets $\beta$, $u_\beta \to 1$, then we regard such an $n$-dimensional variety (defined by the $u$ equations) as a binary geometry.
-From this definition, we see that one can realize simplex as a binary geometry since all facets are compatible with each other.
-Consider $u$ equations for a $n$-dimensional simplex with facets labelled by $\alpha=0,1,\cdots, n$
+Before proceeding, we remark that $u$ equations of the form \eqref{perfectu} (which we refer to as ``perfect'' $u$ equations) imply binary geometries, but the converse is not true.
+Broadly speaking, for a $n$-dimensional polytope ${\cal P}$ where each facet is associated with a $u$ variable, if for any $u_\alpha\to 0$, we have for all incompatible facets $\beta$, $u_\beta \to 1$, then such an $n$-dimensional variety (defined by the $u$ equations) is a binary geometry.
+From this definition, we see that the simplest example of binary geometry is a simplex, where all facets are compatible with each other.
+One can realize the configurations space by the following $u$ equations for a $n$-dimensional simplex with facets labelled by $\alpha=0,1,\dots, n$:
 \[
@@
 \] 
-As $u_\alpha\to 1$, there is no $u\to 1$, and all $n$ remaining $u$ variables satisfy the same equations for that facet, which is an $(n{-}1)$-dim simplex.
+As $u_\alpha\to 0$, there is no $u\to 1$, and all $n$ remaining $u$ variables satisfy the same equations for that facet, which is an $(n{-}1)$-dim simplex.
 Although this example is trivial, it does show that we do not necessarily need perfect $u$ equations to have binary geometries.
-Generically, for a $n$-dimensional polytope ${\cal P}$ with $N$ facets,  have an $n$-dimensional configuration space defined by $u$ equations
+Generically,  a $n$-dimensional polytope ${\cal P}$ with $N$ facets have an $n$-dimensional configuration space defined by $u$ equations
 \be\label{genueq}
-1-u_\alpha=p_\alpha(\{u\}) \prod_\beta u_\beta^{\beta|\alpha} 
+1-u_\alpha=p_\alpha(\{u\}) \prod_\beta u_\beta^{\beta||\alpha} 
 \ee
-where $\beta |\alpha \geq 0$ are integers which vanishes for $\beta$ compatible with $\alpha$, and $p_\alpha(\{u\})$ is an arbitrary polynomial which must equal to unity on the facet $\alpha$, $p_\alpha (\{u\})|_{u_\alpha=0}=1$.
-When $u_\alpha \to 0$, since it appears on the RHS ofequation with $1-u_\beta$ for any incompatible $\beta$, we have $u_\beta\to 1$ for any polynomial $p_\beta (\{u\})$.
+where $\beta ||\alpha \geq 0$ are integers which vanishes for $\beta$ compatible with $\alpha$, and $p_\alpha(\{u\})$ is an arbitrary polynomial which must equal to unity on the facet $\alpha$, $p_\alpha (\{u\})|_{u_\alpha=0}=1$.
+When $u_\alpha \to 0$, since it appears on the RHS of equation with $1-u_\beta$ for any incompatible $\beta$, we have $u_\beta\to 1$ for any polynomial $p_\beta (\{u\})$.
 However, in the equation with $1-u_\alpha$, since all the incompatible $u_\beta \to 1$ we find $p_\alpha (\{u\})|_{u_\alpha=0}=1$ (where we evaluate the polynomial at $u_\alpha=0$ and all incompatible $u_\beta=1$).
@@
 As the main result of the paper, we present infinitely many new examples of binary geometries which have $u$ equations of the form \eqref{genueq}, and (also infinitely) many of them with perfect $u$ equations.
-The key is to consider a class of stringy integrals for {\it generalized permutohedra} that can be realized as Minkowski sum of coordinate simplices as follows (more details will be given later).
-Given the label set $[0,n]=\{0,1,\cdots, n\}$, we define a {\it building set} $\mathbf B$ as a collection of subsets $I \subset [0,n]$ that satisfy (1).
-if $I, J \in {\mathbf B}$ and $I\cap J\neq \emptyset$, then $I\cup J \in {\mathbf B}$, and (2).
+The key idea to consider a class of stringy integrals for {\it generalized permutohedra} that can be realized as the Minkowski sum of coordinate simplices as follows (more details will be given later).
+Given the label set $[0,n]=\{0,1,\dots, n\}$, we define a {\it building set} $\mathbf B$ as a collection of subsets $I \subset [0,n]$ that satisfy (1).
+if $I, J \in {\mathbf B}$ and $I\cap J\neq \varnothing$, then $I\cup J \in {\mathbf B}$, and (2).
 it contains all {\it singletons} $\{i\}$.
-For each subset $I$ we have a simplex $\Delta_I$ as the convex hull of unit vectors ${\bf e}_i$ with $i\in I$, and the generalized permutohedron ${\mathscr P}(\mathbf B)$ is given by (weighted) Minkowski sum of $\Delta_I$ (defined on a $n$-dimensional hyperplane of the $(n{+}1)$-dim space)~\cite{}.
+For each subset $I$ we have a simplex $\Delta_I$ as the convex hull of unit vectors ${\bf e}_i$ with $i\in I$, and the generalized permutohedron ${\mathscr P}(\mathbf B)$ is given by (weighted) Minkowski sum of $\Delta_I$ (defined on a $n$-dimensional hyperplane of the $(n{+}1)$-dim space)~\cite{Postnikov:2005}.
 It is very natural to define stringy canonical form for such a building set $\mathbf B$: for each subset $I$, we have the simplest {\it linear} polynomial $x_I:=\sum_{i\in I} x_i$ (for singletons, $x_{\{i\}}=x_i$ are the coordinates), and
 \begin{equation}\label{intgenperm}
-{\cal I}_{\mathbf B}(\{S\}):=\int_{\mathbb R_+^n}\frac{1}{{\rm vol}~GL(1)} \prod_{i=0}^n \frac{d x_i}{x_i} %x_i^{S_i}
+{\cal I}_{\mathbf B}(\{S\}):=(\alpha')^n~\int_{\mathbb R_+^n}\frac{1}{{\rm vol}~GL(1)} \prod_{i=0}^n \frac{d x_i}{x_i} %x_i^{S_i}
 \prod_{I \in {\mathbf B}} x_I^{\alpha' S_I}\,,
 \end{equation}
-where the integration domain is defined projectively, {\it i.e.} up to a $GL(1)$ redundancy which can be fixed by fixing, say, $x_0=1$; the exponents $S_I$ satisfy $\sum_I S_I=0$ (if we fix the gauge by $x_0=1$, $S_0$ drops out and the rest $S_I$ are independent).
-By construction, ${\cal I}_{\mathbf B}$ is indeed the stringy canonical form for the generalized permutohedron $\sum_I S_I N[x_I]=\sum_I S_I \Delta_I={\mathscr P}(\mathbf B)$.
-Note that one can split the product as $\prod_I x_I^{\alpha' S_I}=\prod_{i=1}^n x_i^{\alpha' X_i} \prod_I^m x_I^{-\alpha' c_I}$ with $X_i:=S_{\{i\}}$ for singletons, $-c_I=S_I$ for non-singleton $I$'s (we denote their total number as $m$), and it suffices to take the Minkowski sum w.r.t.
+where the integration domain is defined projectively, {\it i.e.} up to a $GL(1)$ redundancy thus the exponents $S_I$ satisfy $\sum_I S_I=0$ (one can fix the gauge by choosing {\it e.g.} $x_0=1$, then $S_0$ drops out and the remaining $S_I$ are independent).
+By construction, ${\cal I}_{\mathbf B}$ is a stringy canonical form for the generalized permutohedron $\sum_I S_I {\bf N} [x_I]=\sum_I S_I \Delta_I={\mathscr P}(\mathbf B)$, and the leading order is given by the volume of its dual.
+Note that one can split the product as $\prod_I x_I^{\alpha' S_I}=\prod_{i=1}^n x_i^{\alpha' X_i} \prod_I^m x_I^{-\alpha' c_I}$ with $X_i:=S_{\{i\}}$ for singletons, $-C_I=S_I$ for non-singleton $I$'s (we denote their total number as $m$), and it suffices to take the Minkowski sum w.r.t.
 the non-singelton $I$'s, since the singleton ones are merely translating the polytope.
-
-Let's list three examples of ${\mathscr P} (\mathbf B)$ and ${\cal I}_{\mathbf B}$ which will be our main examples throughout the paper. 
+Let's first present the simplest example with building set ${\mathbf B}$ given by all the singletons $\{i\}$ and $[0,n]$.
+In this case, ${\mathscr P}(\mathbb B)=c {\bf N} [\sum_{i=0}^n x_i]$ is the $n$-dim simplex (we denote $c:=C_{[0, n]}$), given by $X_i \geq 0$ with one (ABHY) constraint $\sum_{i=1}^n X_i=c$.
+It is straightforward to see that the $u$ variables are $u_i=\frac{x_i}{x_{[0,n]}}=\frac{x_i}{\sum_i x_i}$ and they satisfy $\sum_{i=0}^d u_i=1$ as expected.
+In this case, the integral is trivial to perform, which yields a generalization of beta function to higher dimensions:
+\[
+{\cal I}^{\rm simplex}_n=\frac{\prod_{i=1}^n \Gamma(\alpha' X_i)\Gamma(\alpha'(c- \sum_i X_i))}{\Gamma(\alpha'c)}:=B\left(\alpha' X_1, \dots, \alpha' X_n,\alpha'\left(c- \sum_i X_i\right)\right)\,,
+\]
+
+The most important three examples of ${\mathscr P} (\mathbf B)$ and ${\cal I}_{\mathbf B}$, which will be studied in detail throughout the paper, are summarized here:
 \begin{itemize}
-\item Consider $\mathbf B$ as the collection of all $n(n{+}3)/2+1$ consecutive intervals within $[0,n]$, ${\mathscr P}(\mathbf B) \equiv {\mathscr A}_n$ is the $n$-dim associahedron, \eqref{intgenperm} is nothing but $(n{+}3)$-pt string integral \eqref{stringint}; {\it e.g.} for $n=2$, ${\mathbf B}=\{\{i\}, \{0,1\}, \{1,2\}, \{0,1,2\}\}$, and we have a pentagon ${\mathscr A}_2$.
+\item Consider $\mathbf B$ as the collection of all $n(n{+}3)/2+1$ consecutive intervals of $[0,n]$, ${\mathscr P}(\mathbf B) \equiv {\mathscr A}_n$ is the $n$-dim associahedron, \eqref{intgenperm} is nothing but $(n{+}3)$-pt string integral \eqref{stringint}; {\it e.g.} for $n=2$, ${\mathbf B}=\{\{i\}, \{0,1\}, \{1,2\}, \{0,1,2\}\}$, and we have a pentagon ${\mathscr A}_2$.
 \item Consider $\mathbf B$ as the collection of all $n(n{+}1)+1$ cyclic intervals of $[0,n]$ which can wrap around $n$, ${\mathscr P} (\mathbf B) \equiv {\mathscr B}_n$ is the $n$-dim cyclohedron, and in sec.
 2 we will show that non-trivially \eqref{intgenperm} is the cluster stringy integral for type $B_n$ (not that for type $C_n$); {\it e.g.} $n=2$, ${\mathbf B}=\{\{i\}, \{0,1\}, \{1,2\}, \{2,0\}, \{0,1,2\}\}$, and we have a hexagon ${\mathscr B}_2$.
-\item Consider $\mathbf B$ as the collection of all $2^{n{+}1}-1$ subsets of $[0,n]$, ${\mathscr P}(\mathbf B) \equiv {\mathscr P}_n$ is the $n$-dim permutohedron (for $n=2$, it coincide with ${\mathscr B}_2$ the hexagon).
+\item Consider $\mathbf B$ as the collection of all $2^{n{+}1}-1$ subsets of $[0,n]$, ${\mathscr P}(\mathbf B) \equiv {\mathscr P}_n$ is the $n$-dim permutohedron (for $n=2$, it coincides with ${\mathscr B}_2$).
 All generalized permutohedra (and their stringy integrals) can be obtained from (that of) ${\mathscr P}_n$.
@@
 Although associahedra and cyclohedra are special cases of generalized permutohedra, it is interesting that \eqref{intgenperm} in these cases turn out to be exactly cluster stringy integrals of type $A$ and $B$!
-It is not completely surprising since these are the only two cases of cluster configuration spaces that can be identified with hyperplane arrangement (which is consistent with the linear polynomials), while {\it e.g.} for type $C$ we do not know such a hyperplane arrangement and for type $D_4$ {\it etc.} we know this is impossible from point-count argument~\cite{}.
+It is not completely surprising since these are the only two cases of cluster configuration spaces that can be identified with hyperplane arrangement~\cite{Arkani-Hamed:tobeappear}, which is consistent with the fact that here we only have linear polynomials $x_I$.
 In sec.
-2, we will go further and discover more binary geometries with perfect $u$ equations, which can be obtained by ``degenerating" type $A$ and $B$ integrals by requiring certain $S_I=0$ (for example, type $A$ integral is in fact a degeneration of the type $B$ integral, which was not obvious before).
+2, we will go further and discover more binary geometries with perfect $u$ equations, which can be obtained by ``degenerating'' type $A$ and $B$ integrals by requiring certain $S_I=0$ (for example, type $A$ integral is in fact a degeneration of the type $B$ integral, which was not obvious before).
 Some of these cases are products of lower-dim $A$'s and $B$'s, but we will see entirely new binary geometries with perfect $u$ equations.
@@
 3 is that, the configuration space for any ${\cal I}_{\mathbf B}$ is always binary, which means that any $u_\alpha \to 0$ forces all the incompatible ones $u_\beta\to 1$.
-As we will see explicitly with ${\mathscr P}_n$, its $u$ equations indeed take the form of \eqref{genueq}, which is no longer perfect for $n>2$, but the space is binary and the integral factorizes as product of lower-dim permutohedron integrals at finite $\alpha'$!.
-Note that an important feature of any generalized permutohedron is that its facets are labelled by all subsets $I$ in ${\mathbf B}$ except for the complete set $[0,n]$, and on each facet it factorizes as product of two generalized permutohedra.
+As we will see explicitly with ${\mathscr P}_n$, its $u$ equations indeed take the form of \eqref{genueq}, which is no longer perfect for $n>2$, but the space is binary and the integral factorizes as a product of lower-dim permutohedron integrals at finite $\alpha'$!
+Note that an important feature of any generalized permutohedron is that its facets are labelled by all subsets $I$ in ${\mathbf B}$ except for the complete set $[0,n]$, and on each facet it factorizes as a product of two generalized permutohedra.
 The total number of facets $N$ equals $|{\mathbf B}|-1=n+m$, thus the big polyhedron is indeed a simplex as expected.
 In sec.
-3, we will present the formula for $u$ variables for any generalized permutohedron (which is equivalent to the formula for its ABHY-like realization), from which the binary and factorization properties follows.
-%These fall broadly into two classes, the first of which corresponds to the permutahedron $P_n$ and more generally generalised permutahedra which do not have perfect $u$-equations but are still binary.
-The second class corresponds to various degenerations of the associahedra and cyclohedra which are binary geometries with perfect $u$-equations.
-In both these cases the configuration space can be realised as hyperplane arrangements and we discuss how this allows to understand why some degenerations give us binary geometries with perfect $u$-equations while others do not.
+3, we will present the formula for $u$ variables for any generalized permutohedron (which is equivalent to the formula for its ABHY-like realization), from which the binary and factorization properties follow.
+%These fall broadly into two classes, the first of which corresponds to the permutohedron $P_n$ and more generally generalized permutohedra which do not have perfect $u$ equations but are still binary.
+The second class corresponds to various degenerations of the associahedra and cyclohedra which are binary geometries with perfect $u$ equations.
+In both these cases the configuration space can be realised as hyperplane arrangements and we discuss how this allows to understand why some degenerations give us binary geometries with perfect $u$ equations while others do not.
 
@@
 
-%{\bf review of stringy canonical forms, mention big polytopes and $u$ variables in general; then specify to cluster string integrals, then cluster configuration spaces with perfect $u$ equations, do $A_n$, $B_n$ examples; define "binary geometries"}
+%{\bf review of stringy canonical forms, mention big polytopes and $u$ variables in general; then specify to cluster string integrals, then cluster configuration spaces with perfect $u$ equations, do $A_n$, $B_n$ examples; define ''binary geometries''}
 
@@
 %Many remarkable aspects of string integral, \textit{e.g.} field-theory limit, 
-%factorization, scattering equations, $u$-variables ..., can be carried to
+%factorization, scattering equations, $u$ variables ..., can be carried to
 %stringy canonical forms. Almost all of these aspects are related to a hidden 
@@
 %where the positive region is given by $0<z_i-z_j<1$ for $1\leq i<j \leq n+1$.
-%The $u$-variables of this configuration space are
+%The $u$ variables of this configuration space are
 %\[
@@
 %where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices live in $\mathbb Z_{2n+2}$.
-%They satisfy the following $u$-equations 
+%They satisfy the following $u$ equations 
 %\begin{align*}	
@@
 
-*******************
-
-\newpage
-
-\section{Configuration spaces with perfect $u$-equations from degenerating $A_n$ and $B_n$}
-In this section we shall consider some degenerations of $A_n$ and $B_n$ and show that these form an infinite class of examples of binary geometries with perfect $u$-equations.
-To do this we shall use the fact that both $A_n$ and $B_n$ are generalised permutahedra and can be realised as a Minkowski sum of coordinate simplices.
-For future convenience, let's define $[i,j]=\{i,i+1,\dots,j\}$ for 
-$i,j\in \mathbb Z/(n+1)\mathbb Z$.
-
-\subsection{$A_n$ and $B_n$ as generalized permutohedra}
-
-{\bf linear factors, (standard) string integrals, ABHY and $u$ variables, talk about hyperplane arrangement}
-
-\subsubsection*{$n$-dimensional associahedron $\mathscr A_n$}
-
-The building set of $\mathscr A_n$ is $\mathbf B= \{[i,j]\,:\, 0\leq i\leq j\leq n\}$.
+\section{Configuration spaces with perfect $u$ equations from degenerating ${\mathscr A_n}$ and ${\mathscr B_n}$}
+In this section we shall consider some degenerations of ${\mathscr A_n}$ and ${\mathscr B_n}$ and show that there are an infinite class of examples of binary geometries with perfect $u$ equations.
+To do this we shall use the fact that both ${\mathscr A_n}$ and ${\mathscr B_n}$ can be realised as a Minkowski sum of coordinate simplices.
+%For future convenience, let's define $[i,j]=\{i,i+1,\dots,j\}$ for $i,j\in \mathbb Z/(n+1)\mathbb Z$.
+
+\subsection{${\mathscr A_n}$ and ${\mathscr B_n}$ as generalized permutohedra} 
+\paragraph {Associahedron $\mathscr A_n$} The building set of $\mathscr A_n$ is $\mathbf B= \{[i,j]\,:\, 0\leq i\leq j\leq n\}$.
 The stringy canonical form of this building set $\mathcal I_{\mathbf B}(\{S\})$
@@
 \[
-	z_{j}-z_i=x_{[i,j-1]},
+	z_j-z_i=x_{[i,j-1]},
 \]
@@
 \]
-and their solution is 
+and their solution is (a rewriting of ABHY conditions in our notation):
 \begin{equation}\label{Ansf}
@@
 \end{equation}
-where $F_{[k,l]}:=0$ when $k>l$ or $[k,l]=[0,n]$.
-The usual $X$-variable $X_{ij}=\sum_{i\leq k<l<j}s_{kl}$ in string integrals here is $F_{[i,j-2]}$. 
-Using this solution to rewrite 
-the integrand of the stringy canonical form $\mathcal I_{\mathbf B}(\{S\})$
+where $F_{[k,l]}:=0$ when $k>l$ or $[k,l]=[0,n]$ and the usual planar $X$ variables $X_{ij}%=\sum_{i\leq k<l<j}s_{kl}
+$ is $F_{[i,j-2]}$. Using this solution to rewrite the integrand of the stringy canonical form $\mathcal I_{\mathbf B}(\{S\})$
 \begin{align*}
@@
 &=\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F_{[i,j]}}x_{[i,j]}^{F_{[i+1,j-1]}}\bigg /
-x_{[i,j]}^{F_{[i,j-1]}}x_{[i,j]}^{F_{[i+1,j]}}\\
-&=
-\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F_{[i,j]}}
-\prod_{1\leq i\leq j\leq n-1}x_{[i-1,j+1]}^{F_{[i,j]}}
-\prod_{0\leq i\leq j\leq n-1}x_{[i,j+1]}^{-F_{[i,j]}}
-\prod_{1\leq i\leq j\leq n}x_{[i-1,j]}^{-F_{[i,j]}},
+x_{[i,j]}^{F_{[i,j-1]}}x_{[i,j]}^{F_{[i+1,j]}}%\\
+%&=\prod_{0\leq i\leq j\leq n}x_{[i,j]}^{F_{[i,j]}} \prod_{1\leq i\leq j\leq n-1}x_{[i-1,j+1]}^{F_{[i,j]}} \prod_{0\leq i\leq j\leq n-1}x_{[i,j+1]}^{-F_{[i,j]}} \prod_{1\leq i\leq j\leq n}x_{[i-1,j]}^{-F_{[i,j]}},
 \end{align*}
-and we get that
-\[
-u_{i,j+2}:=u_{[i,j]}=\frac{x_{[i,j]}x_{[i-1,j+1]}}{x_{[i,j+1]}x_{[i-1,j]}} \quad \text{for $0\leq i\leq j\leq n$,}
-\]
-with $x_{[i,n+1]}:=1$ and $x_{[-1,j]}:=1$, whose $u$-equations are
-\[
-1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl}.
-\]
+and we get that the $u$ variables easily:
+\begin{equation}
+ u_{i,j+2}:=u_{[i,j]}=\frac{x_{[i,j]}x_{[i-1,j+1]}}{x_{[i,j+1]}x_{[i-1,j]}} \quad \text{for $0\leq i\leq j\leq n$,}   \label{uvarforAn}
+\end{equation}
+with $x_{[i,n+1]}:=1$ and $x_{[-1,j]}:=1$, and it is straightforward to see that they satisfy $u$ equations \eqref{Aueq}.
+%\[ 1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl}. \]
 
@@
 \]
-where $C$s are positive numbers. We can use a mesh to represent these conditions.
-For example, the mesh of $\mathscr A_3$ is 
+where $C$'s are positive numbers.
+As first introduced in~\cite{Arkani-Hamed:2019vag}, it is convenient and illuminating to represent these conditions in a meash diagram of $1+1$-D lattice.
+For example, we can have the following mesh for ABHY realization of $\mathscr A_3$:
 \begin{center}
@@
 \end{center}
-Each diamond in the mesh whose top corner\footnote{
-It looks different with the usual mesh where label of $c$ follows the left corner
+where each diamond is labelled by $[i,j]$ of the top corner~\footnote{
+It looks different with the usual mesh of $\mathscr A_n$~\cite{Arkani-Hamed:2019vag} where label of $c$ follows the left corner
 in each diamond. This is because the mismatch of the correspondence of labels 
 $X_{ij}=F_{[i,j-2]}$ and $s_{ij}=S_{[i,j-1]}$.
-}
-is label by $[i,j]$ represents 
-\[
-	C_{[i,j]}=F_{[i,j-l]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]},
-\]
-and each big diamond (which is made of several diamonds) gives us an equation
+}, and it gives
+\begin{equation}\label{CinFA}
+	C_{[i,j]}=F_{[i,j-l]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]}\,.
+\end{equation}
+For each causal diamond, we have the Gauss law:
 \[
@@
 
-\subsubsection*{$n$-dimensional cyclohedron $\mathscr B_n$}
-
-The building set of $\mathscr B_n$ is $\mathbf B=\{[i,i+k]\,:\,0\leq i, k\leq n\}$.
-The facets are given by 
+\paragraph{Cyclohedron $\mathscr B_n$} The building set of $\mathscr B_n$ is $\mathbf B=\{[i,i+k]\,:\,0\leq i, k\leq n\}$ where the labels are understood to be mod $n+1$. The facets are given by 
 \[
@@
 \]
-where $F_{[i+1,i]}=F_{[0,n]}=0$. Therefore, the $u$-variables are
-\[
+where $F_{[i+1,i]}=F_{[0,n]}=0$. Therefore, the $u$ variables are
+\begin{equation}
    u_i:=u_{[i,i-2]}=\frac{x_{[i,i-2]}}{x_{[0,n]}},\quad 
 u_{i,j+2}:=u_{[i,j]}=\frac{x_{[i,j]}x_{[i-1,j+1]}}{x_{[i,j+1]}x_{[i-1,j]}}
-\quad \text{for $i-j\neq 2$}.
-\]
-$u$-equations are
-\[
+\quad \text{for $i-j\neq 2$}.  \label{uvarforBn}
+\end{equation}
+It is straightforward to work out the $u$ equations, which can be put in a compact form~\cite{Arkani-Hamed:2019plo}
+\begin{equation}\label{Bueq}
 1-u_i=U_{[i+1,i-1]},\quad 
 1-u_{ij}=U_{[i+1,j],[j+1,i-1]}U_{[j+1,i-1],[i,j-1]}U^2_{[j+1,i-1]},
-\]
-where 
+\end{equation}
+where we introduce the notation 
 \[
@@
 \]
-Since the building set of $\mathscr A_n$ is contained in the building set of $\mathscr B_n$, $\mathscr A_n$ is a degeneration of $\mathscr B_n$.
-
-The ABHY construction of $\mathscr B_n$ is similar: $F_{[i,j]}\geq 0$ for all $[i,j]\in\mathbf B$,
-\[
+
+Since the building set of $\mathscr A_n$ is contained in the building set of $\mathscr B_n$, $\mathscr A_n$ is a degeneration of $\mathscr B_n$, which was not obvious in the previous construction of $\mathscr B_n$.
+
+The ABHY construction of $\mathscr B_n$ is similar: $F_{[i,j]}\geq 0$ for all $[i,j]\in\mathbf B$ and for $i\neq j$
+\begin{equation}\label{abhyB}
 F_{[i,j-1]}+F_{[i+1,j]}-F_{[i,j]}-F_{[i+1,j-1]}
-	=C_{[i,j]}\,\,\text{for $i\neq j$ and $[i,j]\neq [0,n]$}, \quad 
-\]
-and 
-\begin{equation}\label{abhyB}
-	C_{[0,n]}=\sum_{i=0}^n F_{[i,i-2]}-\sum_{i=0}^n F_{[i,i-3]},
-\end{equation}
-where $F_{[i+1,i]}=0$ and $C$s are all positive constants. 
+	=C_{[i,j]}\,\,\text{for $[i,j]\neq [0,n]$}, \quad C_{[0,n]}=\sum_{i=0}^n F_{[i,i-2]}-\sum_{i=0}^n F_{[i,i-3]},
+\end{equation}
+where $F_{[i+1,i]}=0$ and the $C$'s are all positive constants. 
 %We can also use a mesh to represent this conditions. For example, the mesh for $\mathscr B_3$ is 
@@
 Like $A_n$, $B_n$ type cluster stringy canonical form also comes from a hyperplane 
-arrangement, the Shi arrangement. The Shi arrangement contains $n+1$ punctures 
+arrangement, the Shi arrangement~\cite{shi1986kazhdan}. The Shi arrangement contains $n+1$ punctures 
 $\{z_i\}_{i=1,\dots,n+1}$ on the real line with the freedom of global transformation 
@@
 and its stringy integral is 
-\[
+\begin{equation}
 \mathcal I_n = \int_{1>z_1>z_2>\cdots >z_n>0}
@@
 \prod_{0\leq i<j \leq n}(z_i-z_j)^{s_{ij}}(1-z_i+z_j)^{t_{ij}},
-\]
+\end{equation}
 where the positive region is given by $0<z_i-z_j<1$ for $1\leq i<j \leq n+1$.
-The $u$-variables of this configuration space are
-\[
-    u_1=\tilde z_1-z_2,\quad \dots,\quad u_{n}=\tilde z_{n}-z_{n+1},
-    \quad u_{n+1}=z_{n+1}-z_1
-\]
-and 
+We can also write the $u$ variables in terms of the $z$'s:
 \begin{align*}
-    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad \text{for $i<j$},\\
-    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad \text{for $i<j$},
+    &u_1=\tilde z_1-z_2,\quad \dots,\quad u_{n}=\tilde z_{n}-z_{n+1},
+    \quad u_{n+1}=z_{n+1}-z_1,\\
+    &u_{ji}=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad \text{for $i<j$},\\
+    &u_{ij}=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad \text{for $i<j$},
 \end{align*}
 where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices live in $\mathbb Z_{2n+2}$.
-%They satisfy the following $u$-equations 
+%They satisfy the following $u$ equations 
 %\begin{align*}	
@@
 
-\subsection{Degenerations of $A_n$ and $B_n$ with perfect $u$ equations}
-
-{\bf things I wrote in my handwritten notes...}
-
-The degenerations of $A_n$ is given by setting some $C$s in ABHY construction or deleting the corresponding elements in the building set.
-Note that the building set after deletion doesn't need to be a new building set, \emph{i.e.} a degeneration of $A_n$ may not be a generalized permutohedron.
+\subsection{Degenerations of $\mathscr A_n$ with perfect $u$ equations}
+
+The degenerations of $\mathscr A_n$ are given by setting some $C$'s in ABHY construction to zero or deleting the corresponding elements in the building set.
+Note that the building set after deletion doesn't need to be a new building set, \emph{i.e.} a degeneration of $\mathscr A_n$ may not be a generalized permutohedron.
 However, we can still ask the following question: are these degenerations binary geometries?
-Of course, we should require at least that the number of facets of the degeneration of $A_n$ should be equal to the size of the corresponding deleted building set minus one, \emph{i.e.} its big polytope is a simplex.
-Before answer this question, let's first find all degenerations of $A_n$ with this property.
+Of course, we should require at least that the number of facets of the degeneration of $\mathscr A_n$ should be equal to the size of the corresponding deleted building set minus one, \emph{i.e.} its big polyhedron is a simplex.
+Before answer this question, let's first try to find all degenerations of $\mathscr A_n$ with this property.
 
@@
 
-From the following equations for facets $\{F_{[i,j]}\}$ of $A_n$
+From the following equations for facets $\{F_{[i,j]}\}$ of $\mathscr A_n$
 \[
@@
 where $F_{[a,b]}:=0$ when $a>b$ or $[a,b]=[0,n]$,
-an economical way to get a degeneration which satisfies the above property is setting all $C$s on the RHS of 
-\begin{align*}
+an standard way to get a degeneration whose big polyhedron is a simplex is setting all $C$'s on the RHS of 
+\begin{align}
 &F_{[i,j-1]}+F_{[j,l]}-F_{[i,l]}= \sum_{i\leq a<j\leq b\leq l} C_{[a,b]} 
-\quad \text{for $i<j=k+1\leq l$ }\\[-1.5ex]
-\text{or}&\\
+\quad \text{for $i<j=k+1\leq l$ }\\\nonumber
+%\text{or}&\\
 &F_{[0,k]}+F_{[j,n]}-F_{[j,k]}= \sum_{0\leq a<j\atop{k<b\leq n}} C_{[a,b]} 
 \quad \text{for $0<j\leq n$ and $0\leq k<n$}
-\end{align*}
-to be zero, and all wanted degenerations can be got by setting $C$s in several above equations.
-
-From the viewpoint of mesh, an equation above corresponds to a big diamond whose top or bottom corner and all $C$s are zero. For example,
+\end{align}
+to be zero, and all wanted degenerations can be got by setting $C$'s to zero in several equations above.
+
+From the viewpoint of the mesh picture, an equation above corresponds to a big diamond whose top or bottom corner and all $C$'s are zero. For example,
 \begin{center}
-\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
+\begin{tikzpicture}[scale=0.75,baseline={([yshift=-.5ex]current bounding box.center)}]
 \draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$0$}
@@
 \qquad \text{or}\qquad
-\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
+\begin{tikzpicture}[scale=0.75,baseline={([yshift=-.5ex]current bounding box.center)}]
 \draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$B$}
@@
 Similarly, black points are all vanishing facets in the above example, and generally
-the number of vanishing facets equals the number of deleted $C$s for degenerations of this type.
-
-One can use these diamonds to build a degeneration with more vanishing facets whose big polytope is a simplex. For example, in $A_3$
+the number of vanishing facets equals the number of deleted $C$'s for degenerations of this type.
+
+One can use these diamonds to build a degeneration with more vanishing facets whose big polyhedron is a simplex. For example, in $\mathscr A_3$
 \begin{center}
@@
 \end{center}
-after setting $C$s in green and purple diamonds to be zero, three facets (black points) vanish and building set after deletion is 
+after setting $C$'s in green and purple diamonds to be zero, three facets (black points) vanish and building set after deletion is 
 \[
@@
 \]
-One can further check that it's a cube (or $A_1^3$).
-
-We can play the game for any degenerations of $A_n$, count black points and deleted $C$s in each degeneration, and find that for $A_2$, $A_3$ and $A_4$, there're respectively $4$, $41$ and $580$ possible degenerations whose big polytopes are simplices.
-For these degenerations, we can easily find their $u$-variables if their sets of all vanishing facets are known.
+One can further check that it's a cube (or $\mathscr A_1^3$).
+
+We can play the game for any degenerations of $\mathscr A_n$, count black points and deleted $C$'s in each degeneration, and find that for $\mathscr A_2$, $\mathscr A_3$ and $\mathscr A_4$, there're respectively $4$, $41$ and $580$ possible degenerations whose big polyhedra are simplices.
+For these degenerations, we can easily find their $u$ variables if the set of all vanishing facets are known.
 
@@
 \]
-for any $I'\in \mathscr D$, where $M$ is a matrix with non-negative entries. 
-Therefore,
+for any $I'\in \mathscr D$, where $M$ is a matrix with non-negative entries. Therefore,
 \[
@@
 \]
-so the new $u$-variables of the degeneration are
-\[
+so the new $u$ variables of the degeneration are
+\begin{equation}
     \tilde u_{I}=u_I\prod_{I'\in \mathscr D}u_{I'}^{M_{I'}^I}
-\]
-for any $I\not\in \mathscr D$.
-
-The simplest degenerations of $A_n$ are those with one $c_{[i,i+1]}$ vanishing. For the one with $c_{[i,i+1]}=0$, we get 
+\end{equation}
+for any $I\not\in \mathscr D$.  The simplest degenerations of $\mathscr A_n$ are those with one $C_{[i,i+1]}$ vanishing, where we get 
 \[
@@
 \]
-where $F_i=F_{[i,i]}$, so 
+with $F_i=F_{[i,i]}$, and we find the $u$ variables become
 \[
@@
 \]
-They satisfy the following $u$-equation
-\[
+They satisfy the following $u$ equation
+\begin{equation}
 	1-\tilde u_{i}=\prod_{0\leq a\leq i-1}\tilde u_{[a,i-1]}
@@
 	\prod_{i+2\leq b\leq n} \tilde u_{[i+2,b]},\quad 
-\]
-and the other $u$-equations are original $u$-equations for
-$\{u_{[i,j]}\,:\, [i,j]\neq [i,i],[i,i+1],[i+1,i+1]\}$ in terms of new variables.
-Similarly, one can easily find the $u$-variables and $u$-equations for the degenerations with $c_{[i,i+1]}=0$ for several $i$.
+\end{equation}
+and the other $u$ equations are original $u$ equations for $\{u_{[i,j]}\,:\, [i,j]\neq [i,i],[i,i+1],[i+1,i+1]\}$ in terms of new variables.
+Similarly, one can easily find the $u$ variables and $u$ equations for the degenerations with $C_{[i,i+1]}=0$ for several $i$.
 
@@
 %\]
-%so $u$-variables of this degeneration are 
+%so $u$ variables of this degeneration are 
 %\[
@@
 \end{center}
-where $C$s in green region vanish, \emph{i.e.} $c_{[a,b]}=0$ for $0\leq a<i<b\leq n$.
+where $C$'s in green region vanish, \emph{i.e.} $C_{[a,b]}=0$ for $0\leq a<i<b\leq n$.
 Vanishing facets of this degeneration are
@@
 \]
-so new $u$-variables are
-\[
+so new $u$ variables are
+\begin{equation}
 	\tilde u_{[0,b]} = u_{[0,b]}\prod_{a=1}^{i} u_{[a,b]},\quad 
 	\tilde u_{[a,n]} = u_{[a,n]}\prod_{b=i}^{n-1} u_{[a,b]},
-\]
-and $\tilde u_{I}=u_{I}$ for the other $I$. The $u$-equations are the union of 
-$u$-equations of the following two independent meshes
+\end{equation}
+and $\tilde u_{I}=u_{I}$ for the other $I$. The $u$ equations are the union of 
+$u$ equations of the following two independent meshes
 \begin{center}\footnotesize
@@
 One could use this construction of products to produce any finite product $\mathscr A_{i_1}\times \cdots \times \mathscr A_{i_k}$.
-The direct proof of this argument for $\mathscr A_n$ is using global $u$-equations \cite{} of $\mathscr A_n$.
+The direct proof of this argument for $\mathscr A_n$ is using extended $u$ equations \cite{Brown:2009qja,Arkani-Hamed:2019plo} of $\mathscr A_n$.
 
@@
 \]
-and their $u$-equations are
-\[
+and their $u$ equations are
+\begin{equation}
 1-\tilde u_{[k,k]}=\prod_{j=0}^{i-1}\tilde u_{[j,k-1]},
-\]
-and the other $u$-equations are old $u$-equations in terms of new variables.
+\end{equation}
+and the other $u$ equations are old $u$ equations in terms of new variables.
 When $i=1$, the degeneration is $\mathscr A_1^n$.
@@
 \]
-Their $u$-equations are 
-\[
+Their $u$ equations are 
+\begin{equation}
 1-\tilde u_{[0,l]}=\prod_{a=l-i+2}^{l+1}\tilde u_{[a,n]}\cdot\prod_{a=l-i+2}^{l+1}\prod_{b=l+1}^{a+i-2} \tilde u_{[a,b]},\quad
 1-\tilde u_{[k,n]}=\prod_{b=k-1}^{k+i-2}\tilde u_{[0,b]}\cdot \prod_{b=k-1}^{k+i-2}\prod_{a=\max(b-i+2,1)}^{k-1} \tilde u_{[a,b]}.
-\]
-When $i=1$, we will get $\mathscr A_1^n$ again.
-
-The story of degenerations of $B_n$ is very similar. 
-% The first thing to do is to find degenerations whose big polytopes are simplices. 
-With the help of the mesh of $\mathscr B_n$, we could get many classes of degenerations with perfect $u$-equations. 
-For example, setting $c_{[i,i+1]}=0$, then
+\end{equation}
+When $i=1$, we get $\mathscr A_1^n$ again.
+
+\subsection{Degenerations of $\mathscr B_n$ and products}
+\subsubsection{Degenerations of $\mathscr B_n$}
+
+The general treatment of degenerations of $\mathscr B_n$ is more difficult than $\mathscr A_n$ because it has a long ABHY condition eq.\eqref{abhyB}.
+Here we only show some examples of degenerations of $\mathscr B_n$ with perfect $u$ equations.
+
+The first degeneration of $\mathscr B_n$ with perfect $u$ equations is $\mathscr A_n$ because the building set of $\mathscr A_n$ is contained in the building set of $\mathscr B_n$.
+
+The simplest degenerations of $\mathscr B_n$ are those with $C_{[i,i+1]}=0$. For which we get,
 \[
@@
 \]
-The $u$-equations of this degeneration are
-\[
-	1-\tilde u_i=\tilde u_{[i+1,i-1]}
-	\prod_{a=i+2}^{i-1}\tilde u_{[a,i-1]}\tilde u_{[i+1,a]},\quad
+The $u$ equations of this degeneration are
+\[
+	1-\tilde u_i=\tilde u_{[i+1,i-1]}^2\tilde u_{[i-1,i-1]}
+	\prod_{a=i+2}^{i-2}\tilde u_{[a,i-1]}\tilde u_{[i+1,a]},\quad
 	1-\tilde u_{i+1}=
-	\tilde u_{[i+2,i]}\prod_{a=i+2}^{i-1}\tilde u_{[a,i]}\tilde u_{[i+2,a]},
-\]
-and the other $u$-equations are old $u$-equations in terms of new $u$-variables.
-
-A more interesting degeneration is the product $\mathscr B_i\times \mathscr A_{n-i}$.
-In particular,$\mathscr A_n$ is also a degeneration of $\mathscr B_n$.
-
-(Zhenjie: the only known example for me $\mathscr B_3\to \mathscr B_{2}\times \mathscr A_1$: $c_{[i-1,i]}=c_{[i-1,i+1]}=c_{[i,i+2]}=c_{[i+1,i+2]}=0$)
+	\tilde u_{[i+2,i]}^2\tilde u_{[i+2,i+2]}\prod_{a=i+3}^{i-1}\tilde u_{[a,i]}\tilde u_{[i+2,a]},
+\]
+and the other $u$ equations are old $u$ equations in terms of new $u$ variables.
+
+The above degeneration corresponds to deleting an element in $\mathscr B_n$, and the following degeneration corresponds to adding an element to $\mathscr A_n$.
+
+Consider the building set obtained by adding the set $K_i=[0,i]\cup [i+2,n]$ to $\mathscr A_n$.
+It is also a degeneration of $\mathscr B_n$ by setting the other $C$'s to be zero.
+It's easy to solve equations of the facets and get that
+\[
+C_{K_i}=F_{[0,i]}+F_{[i+2,n]}-F_{K_i},\quad 
+C_{[0,n]}=F_{K_i}+F_{[0,n-1]}+F_{[1,n-1]}-F_{[1,n-1]}-F_{[0,i]}-F_{[i+2,n]},
+\]
+the other $C_I$ are given by eq.\eqref{CinFA}. Therefore, new $u$ variables are
+\[
+\tilde u_{K_i}=\frac{x_{K_i}}{x_{[0,n]}},\quad 
+\tilde u_{[0,i]}=\frac{x_{[0,n]}}{x_{K_i}}u_{[0,i]},\quad 
+\tilde u_{[i+2,n]}=\frac{x_{[0,n]}}{x_{K_i}}u_{[i+2,n]},
+\]
+and the other $\tilde u_I$ is equal to $u_I$. The $u$ equations are
+\[
+1-\tilde u_{K_i}=\prod_{I\ni i+1}\tilde u_I,\quad
+1-\tilde u_{[0,i]}=\prod_{J}\tilde u_J^{J||[0,i]}\prod_{K\supset [i+2,n]}\tilde u_K,\quad 
+1-\tilde u_{[i+2,n]}=\prod_{J}\tilde u_J^{J||[i+2,n]}\prod_{K\supset [0,i]}\tilde u_K, 
+\]
+where $I||J$ are compatability degree of $I$ and $J$ in $\mathscr A_n$,
+and the other $u$ equations are corresponding $u$ equations for $\mathscr A_n$ in new variables.
+
+For example, adding $K_0$ to $\mathscr A_2$ we get $\mathscr B_2$, and  adding $K_0$ to $\mathscr A_3$ gives the following $u$ equations
+\begin{align*}
+1-\tilde u_{3}&=\tilde u_{2} \tilde u_{12} \tilde u_{012}&
+1-\tilde u_{01}&=\tilde u_{2} \tilde u_{12} \tilde u_{23} \tilde u_{023} \tilde u_{123}\\
+1-\tilde u_{1}&=\tilde u_{0} \tilde u_{2} \tilde u_{23} \tilde u_{023}^2&
+1-\tilde u_{2}&=\tilde u_{1} \tilde u_{3} \tilde u_{01}\\
+1-\tilde u_{012}&=\tilde u_{3} \tilde u_{23} \tilde u_{023} \tilde u_{123}&
+1-\tilde u_{023}&=\tilde u_{1} \tilde u_{01} \tilde u_{12} \tilde u_{012} \tilde u_{123}\\
+1-\tilde u_{123}&=\tilde u_{0} \tilde u_{01} \tilde u_{012} \tilde u_{023}&
+1-\tilde u_{0}&=\tilde u_{1} \tilde u_{12} \tilde u_{23} \tilde u_{123}^2\\
+1-\tilde u_{12}&=\tilde u_{0} \tilde u_{3} \tilde u_{01} \tilde u_{23} \tilde u_{023}^2&
+1-\tilde u_{23}&=\tilde u_{0} \tilde u_{1} \tilde u_{01}^2 \tilde u_{12} \tilde u_{012}^2.
+\end{align*}
+
+More generally we can consider adding a triangle namely $\cup_{l=0}^{k-1}\cup_{m=l}^{k-1} K_{i,l,m}$ with $K_{i,l,m}=\{[0,i+l]\cup [i+2+m,n] \}$ and $k=1,\dots,(n-1)$ to the building set of $\mathscr{A}_n$.
+For $k=1$ we get the previous example and for $k=n-1$ we get ${\mathscr B_n}$.
+
+Without loss of generality we shall consider only the $i=0$ case and we shall denote $K_{0,l,m}$ by just $K_{l,m}$.
+The $u$ variables are
+\bea
+\tilde u_{K_{l,m}}=\begin{cases} \frac{x_{K_{l,m}}}{x_{[0,n]}},~~~~~~ {\rm if} ~m=l \\
+\frac{x_{K_{l,m}} x_{K_{l+1,m-1}}}{x_{K_{l+1,m}}x_{K_{l,m-1}}}
+,~ m\neq l \end{cases}\quad 
+\tilde u_{[0,l]}=\frac{u_{[0,l]}}{\prod_{j=0}^{k-l-1} \tilde u_{K_{l,l+j}}},\quad 
+\tilde u_{[m+2,n]}=\frac{u_{[m+2,n]}}{\prod_{j=0}^{m}\tilde u_{K_{j,m}}},
+\eea
+with the  understanding that $K_{1,0}=K_{2,0}=[0,n]$ and the other $\tilde u_I$ is equal to $u_I$.
+
+The $u$ equations are:
+\begin{align*}
+1-\tilde u_{[0,l]}&=\left(\prod_{i=0}^{l-1} \prod_{j=i+1}^{k+1}  \tilde u_{[0,i]\cup [j,n]} \prod_{j=i+1}^{l+1} \tilde u_{[0,i]\cup [j,n]}\right) \left(\prod_{i=1}^{l+1} \prod_{j=l+1}^{n}\tilde u_{[i,j]} \right) \left(\prod_{i=1}^{k+1} \tilde u_{[i,n]} \right),\\\\
+1-\tilde u_{[m+2,n]}&=\left( \prod_{j=0}^{m}\tilde u_{[0,j]} \prod_{i=1}^{n-m-1}\tilde u_{[0,m+i]}^2 \right) \left( \prod_{i=m+1}^{n-1}\prod_{j=1}^{m+1}\tilde u_{[j,i]} \right) \left(\prod_{j=0}^{k-m-2} \prod_{i=1}^{m} \tilde u_{[0,i]\cup [3+j+m, n]} \prod_{i= m+1}^{j+m+1} \tilde u_{[0,i]\cup [3+j+m,n]}^2 \right) \\\\
+1-\tilde u_{K_{l,m}}&=\left(\prod_{a=0}^1\prod_{i=l+1}^{n}\tilde u_{[a,i]}\right) \left(\prod_{{\tiny {K_{l',m'} \not\subset K_{l,m}}\atop{K_{l,m} \not\subset K_{l',m'}} }} \tilde u_{K_{l',m'}}^{(l',m')||(l,m)}\right)\left(\prod_{j=2}^{m+1} \prod_{i=l+1}^{n} \tilde u_{[j,i]} \right)\times
+\begin{cases}
+ 1, ~{\rm if} ~ l=m  \\
+ \prod_{i=0}^{l+1} \prod_{j=m+1}^n \tilde u_{[i,j]},~ {\rm if}~l \neq m
+\end{cases}
+\end{align*}
+where $(l',m')||(l,m)$ is the compatability degree of $K_{l,m}$ with respect to $K_{l',m'}$ in $\mathscr B_n$ with the understanding that $\tilde u_{[0,n]}=1$ and the other $u$ equations are corresponding $u$ equations for $\mathscr A_n$ in new variables.
+
+%A more interesting degeneration is the product $\mathscr B_i\times \mathscr A_{n-i}$.
+%In particular,$\mathscr A_n$ is also a degeneration of $\mathscr B_n$.
+
+%(Zhenjie: the only known example for me $\mathscr B_3\to \mathscr B_{2}\times \mathscr A_1$: $c_{[i-1,i]}=c_{[i-1,i+1]}=c_{[i,i+2]}=c_{[i+1,i+2]}=0$)
 
@@
 %\end{center}
-\newpage
-\section{Stringy canonical forms and $u$-equations for generalized permutahedra}
-In this section we shall argue that  a large subset of generalised permutahedra which are realised as degenerations of permutahderon ${\mathscr P_n}$ are binary geometries.
-Before we proceed we shall review some details about the generalised permutahedra which we shall use throughout the paper.
-\subsection{Generalized permutohedra} 
-A generalised permutahedron is a polytope that obtained as Minkowski sums and diffrences of co-ordinate simplices.
-
-Let $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
+\subsubsection{Products of ${\mathscr A}$ and $\mathscr{B}$}
+We can also construct binary geometries which are of the type $\prod_{i=1}^n X_i$ where $X_i={\mathscr A_i}~{\rm or}~{\mathscr B_i}$ which are not necessarily degenerations of ${\mathscr A}~{\rm or}~{\mathscr B}$.
+Without loss of generality we consider only the case ${\mathscr A_n}\times {\mathscr B_m}$.
+We can do this in a couple of simple ways as follows:
+
+(1) We consider the building set $\mathbf{B}_{1}\cup \mathbf{B}_{2}$ with $\mathbf B_1= \{[i,j]\,:\, 0\leq i\leq j\leq n\}$ and $\mathbf B_2= \{[i,i+k]\,:\, n\leq i, k \leq m+n\}$.
+Notice that these are just the building sets of ${\mathscr A_n}$ and ${\mathscr B_m}$ respectively.
+
+If $\mathbf{B}_{1}$ and $\mathbf{B}_{2}$ were disjoint then its obvious that the stringy integral ${\cal I}_{\mathbf B}$ in \eqref{stringycanonicalform} directly factorizes into ${\cal I}_{\mathbf B_1}\times {\cal I}_{\mathbf B_2}$, however the singlet $\{n\}$ belongs to both $B_1$ and $B_2$.
+But by rescaling the variables in $B_2$ by $x_i \rightarrow x_n x_i$ for all $i=n+1,\dots,n+m $ it is straightforward to see that the ${\cal I}_{\mathbf B}$ does indeed factorize into ${\cal I}_{\mathbf B_1}\times {\cal I}_{\mathbf B_2}$ with $x_n$ playing the role of $x_0=1$ in $B_2$.
+
+Notice that the above proof did not use the fact that ${\mathbf B_1}, {\mathbf B_2}$ were building sets of ${\mathscr A},~{\mathscr B}$ and can easily be carried forward to obtain any product of generalized permutohedra.
+The interested reader may refer appendix (\ref{appendix:A}) for details.
+
+(2) Consider the building set  $\mathbf{B}_{1}\cup \mathbf{B}_{2}$ with $\mathbf{B}_{1}=\{[i,i{+}k]\,:\,0\leq i, k\leq m\}$ and $\mathbf{B}_{2}=\{[i,j]: m<i<j\leq n+m \}\cup \{[0,i]:  m\leq i\leq n+m\}$.
+$\mathbf{B}_{1}$ is obviously the building set for $\mathscr{B}_{m}$, while $\mathbf{B}_{2}$ can be viewed as the building set for $\mathscr{A}_{n}$ by identifying $[0,n]$ as a \emph{singleton} in $\mathbf{B}_{2}$.
+Due to this identification, one can easily write down the $u$ variables separately for $\mathbf{B}_{1}$ and $\mathbf{B}_{2}$, and check that these $u$ variables satisfy the $u$ equations for $\mathscr{A}_{n}\times \mathscr{B}_{m}$.
+
+\section{Stringy canonical forms and binary geometries for generalized permutohedra}
+In this section we shall argue that a large class of generalized permutohedra which are realised as degenerations of permutohedron ${\mathscr P_n}$ are binary geometries.
+Before we proceed we shall review some details about the generalized permutohedra \cite{Postnikov:2005,Postnikov:2006} which we shall use throughout the paper.
+\subsection{Generalized permutohedra}\label{GP}
+A generalized permutohedron is a polytope that can obtained be as Minkowski sums and differences of co-ordinate simplices.
+
+Let $\Delta_{[0,n]} = \operatorname{ConvexHull}(e_1,\dots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
 \bea
-{\mathscr P_n}^y(\{y_I \})= \sum y_I . \Delta_I  
+{\mathscr P_n}(\{y_I \})= \sum y_I . \Delta_I  
 \eea
 for some collection of subsets $I \in [0,n]$.
-We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation only as Minkowski sums except translations i.e, $y_I \ge 0$ for all non-singlets $I$\footnote{This is mainly due to the subtle nature of the Minkowski difference operation, which makes the shape of the resulting polytope dependent on the relative magnitudes of $y_I$'s.
-We allow $y_I$ for singlets to be  negative as it is only a translation and to connect with \eqref{intgenperm}.}which are called Nestohedra.
-Throughout the paper we shall mean Nestohedra or products of Nestohedra whenever we refer to generalized permutahedra unless stated otherwise.\\
-
-The combinatorial structure of the generalised permutahedron ${\mathscr P_n({y_I})}$ (Nestohedra) is independent of the parameters $y_I$ and depends only on the collection of subsets $I \in [0,n]$ called the  building set ${\mathbf B}$.
-A collection of non-empty subsets of $[0,n]$ is called a building set ${\mathbf B}$ if it satisfies the following:
+We shall restrict ourselves to the large class of generalized permutohedra which admit such a realisation only as Minkowski sums except translations i.e, $y_I \ge 0$ for all non-singlets $I$\footnote{This is mainly due to the subtle nature of the Minkowski difference operation, which makes the shape of the resulting polytope dependent on the relative magnitudes of $y_I$'s.
+We allow $y_I$ for singlets to be  negative as it is only a translation and to connect with \eqref{intgenperm}.} which are called Nestohedra.
+Throughout the paper we shall mean Nestohedra or products of Nestohedra whenever we refer to generalized permutohedra.
+
+The combinatorial structure of the generalized permutohedron ${\mathscr P_n(\{y_I\})}$ (Nestohedra) is independent of $y_I$ and depends only on the collection of subsets $I \in [0,n]$ of the  building set ${\mathbf B}$, which is
+a collection of non-empty subsets of $[0,n]$ satisfying the following: %is called a building set ${\mathbf B} if it satisfies the following:
 \begin{compactenum}[\quad (1)]
-    \item If $I,J \in {\mathbf B}$ and $I \cap J \neq \phi $, then $I \cup J \in {\mathbf B}$.
+    \item If $I,J \in {\mathbf B}$ and $I \cap J \neq \varnothing $, then $I \cup J \in {\mathbf B}$.
     \item ${\mathbf B}$ contains all singletons $\{ i\}$ for $i \in S$.
 \end{compactenum}
-To describe the combinatorial structure we need the notion of {\it Nested complex} which shall be defined in appendix \ref{appendix: A}.
-We shall only sumarize the nessecary results here and let the reader interested in the details refer appendix \ref{appendix: A}.
-
-\begin{compactitem}
-\item We can look at any collection of subsets of $[0, n]$ which form a building set ${\mathbf B}$ and associate  coordinate simplex $\Delta_I$ for each $I \in {\mathbf B}$ and resulting Minkowski sum with positive weights $y_I$ generates a polytope of dimension $n$ called the generalised permutahedron (Nestohedron) associated with the building set.
-
-\item The number of facets $N$ of the generalised permutahedron just corresponds to the set of all elements in ${\mathbf B}$ excluding the maximal set.
-
-\item Two facets corresponding to the sets $I$ and $J$ in ${\mathbf B}$ intersect i.e., are {\it compatible} with each other if and only if  either $I \subset J$,~ $J \subset I$~ or $I \cap J = \emptyset ~{\text and} ~ I \cup J \notin {\mathbf B}$.
-\end{compactitem}
-
-Let us look at a couple of examples to appreciate these facts better:
-
-(1) Consider the generalized permutahedron with building set 
+Here are some interesting examples of generalized permutohedra:
+\begin{itemize}
+    \item  If ${\mathbf B}= \{[i] | i=0,\dots,n \}$ is the complete flag of intervals, then ${\mathscr P_n(\{y_I\})}$ is the Stanley-Pitman polytope or Hypercube.
+    \item If ${\mathbf B}$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then ${\mathscr P_n(\{y_I\})}$ is the usual permutohedron ${\mathscr P_n}$.
+    \item If ${\mathbf B}=\{ [i,j] | 0\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr P_n(\{y_I\})}$ is the associahedron ${\mathscr A_n}$. 
+    \item If  $\mathbf B=\{[i,i+k]\,:\,0\leq i, k\leq n\}$ is the set of cyclic intervals, then ${\mathscr P_n(\{y_I\})}$ is the cyclohedron ${\mathscr B_n}$.
+    \item Let $\Gamma$ be a graph on the vertex set $[0,n]$.
+Let us assume that ${\mathbf B} = {\mathbf B}(\Gamma)$ is the set of subsets $I \in [0,n]$ such that the induced graph $\Gamma$ is connected, then  ${\mathscr P_n(\{y_I\})}$ is a graph associahedron.
+\end{itemize}
+
+\paragraph{Nested complex} To describe the combinatorial structure we need the notion of {\it Nested complex}.
+We shall only summarize the necessary results here and let the reader interested in the details to refer \cite{Postnikov:2005,Postnikov:2006}.
+A subset ${\mathbf N}$ in the building set ${\mathbf B}$ is called a {\it nested set} if it satisfies the following conditions:
+\begin{compactenum}[\quad (1)]
+    \item For any $I,J \in {\mathbf N}$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
+    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\dots, J_k \in \mathbf N$ their union $J_1 \cup \cdots \cup J_k$ is not in $\mathbf B$.
+    \item ${\mathbf N}$ contains all maximal elements of $\mathbf B$.
+\end{compactenum}
+The {\it nested complex} ${\mathbf N}({\mathbf B})$ is defined as the poset of the set of all nested sets in ${\mathbf B}$ ordered by inclusion.
+\paragraph*{Facial structure} 
+Let us assume that the set ${\mathbf B}$ associated with a generalized permutohedron ${\mathscr P_n(\{y_I\})}$ is a building set on $[0,n]$.
+\emph{Then the poset of faces ${\mathscr P_n(\{y_I\})}$ ordered by reverse inclusion is isomorphic to the nested complex ${\mathbf N}({\mathbf B})$}.
+
+In particular, it means that (1) the number of facets $N$ of the generalized permutohedron just corresponds to the set of all elements in ${\mathbf B}$ excluding the maximal element, and (2) two facets corresponding to the sets $I$ and $J$ in ${\mathbf B}$ intersect i.e., are {\it compatible} with each other if and only if  either $I \subset J$,~ $J \subset I$~ or $I \cap J = \varnothing ~{\text and} ~ I \cup J \notin {\mathbf B}$.
+
+The face $P_\mathbf{N}$ of ${\mathscr P_n(\{y_I\})}$ associated with the nested set $\mathbf{N} \in \mathbf{N}(\mathbf{B})$ is given by
+\bea\label{deffacet}
+P_{\mathbf{N}} = \bigl\{ (t_0,\dots,t_{n}) \in \mathbb{R}^{n+1} | \sum_{i \in I} t_i =z_{I}~{\rm for}~I \in \mathbf{N}; ~ \sum_{i \in J}~t_i \geq z_J,~ {\rm for} ~J \in \mathbf{B}  \bigr\} \:,
+\eea
+where $z_I=\sum_{J\subset I,J\in\mathbf B}y_J$ for $I\in \mathbf B$ and coordinate simplices $\{\Delta_I\}_{I\in\mathbf B}$ are living in $\{t_i\}_{0\leq i\leq n}$-space.
+In particular, the equation of the facet labeled by nested set $\{[0,n],I\}$ of ${\mathscr P_n(\{y_I\})}$ is given by
+\begin{equation}\label{eqoffacet}
+\sum_{i\in I}t_i=\sum_{J\subset I,J\in\mathbf B}y_J.
+\end{equation}
+
+Another description of the faces is the following: for each decomposition $[0,n]=  \sqcup_{I \subset {\mathbf N} } S_I $ where $S_I$ are non-empty, the face $P_\mathbf{N}$ of ${\mathscr P_n(\{y_I\})}$ associated with the nested set ${\mathbf N} \in {\mathbf N}({\mathbf B})$ is
+\bea
+P_\mathbf{N} = \sum_{{J \subset {\mathbf B}}\atop{J \cap S_I \neq \varnothing}} y_{J} \Delta_{J \cap S_I} \:.
+\eea
+In particular each facet of $\mathscr{P}_{n}(\{y\})$ corresponding to a set $I \in \mathbf{B}$ is isomorphic to the product $\mathscr{P}_{ \mathbf{B}_{I}} \times \mathscr{P}_{\mathbf{B}_{\bar{I}}}$ of generalized permutohedra corresponding to the building sets
+\begin{equation}\label{BI}
+    \mathbf{B}_{I} = \{J \vert J\subset I, J\in \mathbf{B}\}
+\end{equation}
+and
+\begin{equation} \label{BIbar}
+    \mathbf{B}_{\bar{I}}=\{J-I \vert J\in \mathbf{B}\}
+\end{equation}
+
+% \begin{compactitem}
+% \item We can look at any collection of subsets of $[0, n]$ which form a building set ${\mathbf B}$ and associate  coordinate simplex $\Delta_I$ for each $I \in {\mathbf B}$ and resulting Minkowski sum with positive weights $y_I$ generates a polytope of dimension $n$ called the generalized permutohedron (Nestohedron) associated with the building set.
+
+% \item The number of facets $N$ of the generalized permutohedron just corresponds to the set of all elements in ${\mathbf B}$ excluding the maximal set.
+
+% \item Two facets corresponding to the sets $I$ and $J$ in ${\mathbf B}$ intersect i.e., are {\it compatible} with each other if and only if  either $I \subset J$,~ $J \subset I$~ or $I \cap J = \varnothing ~{\text and} ~ I \cup J \notin {\mathbf B}$.
+% \end{compactitem}
+
+Let us look at a couple of examples to appreciate these facts better: \\
+(1) Consider the 2d associahedron with building set 
 \[{\mathbf B}= \{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,1,2\} \}.\]
-The polygon has 5 facets which correspond to the sets $\{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\}\}$ and their compatability is shown in the figure below.
-
-The polytope in this case is the 2d associahedron ${\mathscr A_2}$.
-
-(2) Consider the generalized permutahedron with building set 
+This polygon has 5 facets which correspond to the sets $\{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\}\}$ and their compatability is shown in the figure below. \\
+%The polytope in this case is the 2d associahedron ${\mathscr A_2}$.\\
+(2) Consider the 2d cyclohedron/permutohedron with building set 
 \[{\mathbf B}= \{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,2\},\{0,1,2\} \}.\]
-The polygon has 6 facets which correspond to the sets $\{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,2\}\}$ and their compatability is shown in the figure below.
-
-The polytope in this case is the 2d cyclohedron ${\mathscr B_2}$ which also coincides with 2d permutahderon ${\mathscr P_2}$.
+This polygon has 6 facets which correspond to the sets $\{ \{0\},\{1\},\{2\},\{0,1\},\{1,2\},\{0,2\}\}$ and their compatability is shown in the figure below.
+
+%The polytope in this case is the 2d cyclohedron ${\mathscr B_2}$ which also coincides with 2d permutohedron ${\mathscr P_2}$.
 
@@
 % Text Node
-\draw (155,263) node [anchor=north west][inner sep=0.75pt]   [align=left] {Figure showing the compatible\textbackslash incompatible facets of the 2d associahedron  \\ and permutahedron as generalized permutahedra};
+% \draw (155,263) node [anchor=north west][inner sep=0.75pt]   [align=left] {Figure showing the compatible\textbackslash incompatible facets of the 2d associahedron  \\ and permutohedron as generalized permutohedra};
 \end{tikzpicture}
 \end{center}
+\caption{Compatible\textbackslash incompatible facets of the 2d associahedron (a) and permutohedron (b) as generalized permutohedra}
 \end{figure}
 
-Generalised permutahedra have big Polytopes which are simplices. Thus its quite natural to wonder if the associated $u$-variables satisfy some kind of $u$-equations.
-
-We claim and we shall show in the next section that this indeed the case. Further we show that all these polytopes are binary geometries even though some of them do not admit perfect $u$-equations.
-
-Here are some interesting examples of generalised permutahedra:
-
-(1) If ${\mathbf B}$ consists of only singlets i.e., ${\mathbf B}=\{ \{ 0,1,\cdots,n \}, \{ 0 \},\{ 1 \},\cdots ,\{ n \} \}$ then the generalised permutahedron is a Simplex.
-In this case the relevant $x$ variables are $x_i,~ i=0,\cdots,n$ with $x_0=1$ and $\sum_{i=0}^n x_i$.
-The Newton polytope of the Minkowski sum is $\prod_{i=1}^{n} x_i (1+\sum_{j=1}^{n} x_j)$ and $u$-variables are 
-$u_i =\frac{ x_i}{1+\sum_{i=1}^n x_i} $
-which satisfy $\sum u_i =1$ as their only $u$-equation. \\
-
-(2) If ${\mathbf B}= \{[i] | i=0,\cdots,n \}$ is the complete flag of intervals, then ${\mathscr P_n}^y({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
-The Newton polytope of the Minkowski sum is $x_1\cdots x_n (1+x_1) \cdots (1+x_1+\cdots +x_n)$ and $u$-variables are 
-$u_i =\frac{ 1}{1+\sum_{j=1}^{i} x_j} $, ~~$u^{'}_i =\frac{ \sum_{j=1}^{i} x_j}{1+\sum_{j=1}^{i} x_j} $ for $j=1,\cdots,n$ \\
-which satisfy $u_i +u^{'}_{i} =1$ as their $u$-equation. \\
-
-(3) If ${\mathbf B}$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then ${\mathscr P_n}({\bf Y})$ is the usual permutahedron ${\mathscr P_n}$.
-\\
-
-(4) If ${\mathbf B}=\{ [i,j] | 0\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr P_n}({\bf Y})$ is the associahedron. \\
-
-(5) If ${\mathbf B}=\{ [1,i] \cup [j,n] | 0 \leq  i \leq j \leq n\}$ is the set of cyclic intervals, then ${\mathscr P_n}({\bf Y})$ is the Cyclohedron.\\
-
-(6) Let $\Gamma$ be a graph on the vertex set $[0,n]$.
-Let us assume that ${\mathbf B} = {\mathbf B}(\Gamma)$ is the set of subsets $I \in [n]$ such that the induced graph $\Gamma$ is connected, then  ${\mathscr P_n}({\bf Y})$ is a graph associahedron.
-
-It is clear that any  generalized permutahedron can be obtained as a degeneration of  permutahedron ${\mathscr P_n}$i.e., by removing some elements from its building set.
-This makes the permutahedron a very important example of generalized permutahedra and we shall devote the rest of this section to studying its properties and proving it is binary.
+\vspace{1ex}
+
+Generalized permutohedra have big polyhedra which are simplices.
+Thus its quite natural to wonder if the associated $u$ variables satisfy some kind of $u$ equations.
+We claim and we shall show in the next section that this indeed the case.
+Further we show that all these polytopes are binary geometries even though some of them do not admit perfect $u$ equations.
+
+% Here are some interesting examples of generalized permutohedra:
+
+% (1) If ${\mathbf B}= \{[i] | i=0,\cdots,n \}$ is the complete flag of intervals, then ${\mathscr P_n(y)}$ is the Stanley-Pitman polytope or Hypercube.
+
+% (2) If ${\mathbf B}$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then ${\mathscr P_n(y)}$ is the usual permutohedron ${\mathscr P_n}$.
+
+% (3) If ${\mathbf B}=\{ [i,j] | 0\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr P_n(y)}$ is the associahedron.
+
+% (4) If ${\mathbf B}=\{ [1,i] \cup [j,n] | 0 \leq  i \leq j \leq n\}$ is the set of cyclic intervals, then ${\mathscr P_n(y)}$ is the cyclohedron.
+
+% (5) Let $\Gamma$ be a graph on the vertex set $[0,n]$.
+Let us assume that ${\mathbf B} = {\mathbf B}(\Gamma)$ is the set of subsets $I \in [0,n]$ such that the induced graph $\Gamma$ is connected, then  ${\mathscr P_n(y)}$ is a graph associahedron.
 
@@
 
-\newpage
-
-\subsection{$\mathscr{P}_{n}$ as a binary geometry}
-
-\subsubsection{String canonical forms and ABHY conditions for $\mathscr{P}_{n}$}
-
-In the last subsection, we have seen that any $n$-dimensional generalized 
-permutahedron can be constructed by a Minkowski sum of some simplices labeled by
-subsets of $[0,n]$. For a simplex labeled by a subset $I$, 
-it is natrual to associate the linear polynomial $x_I=\sum_{i\in I}x_i$ whose Newton polytope is the corresponding simplex.
-Therefore, we can write down a natrual stringy canonical form for the generalized permutahedron with the building set $\mathbf{B}$
-\begin{equation} \label{stringyintforgenpermutohedron}
-   \mathcal I_{\mathbf{B}}(\{S_I\})=\int_{\mathbb R^{n}_+}
-	\frac{\prod_{i=0}^n \mathrm{d}\log x_i}
-	{\operatorname{GL}(1)_+}\prod_{I\in\mathbf{B}}x_I^{\alpha' S_I},
-\end{equation}
-where the global $\operatorname{GL}(1)_+$ redundance $x_i\mapsto a x_i$ require that 
-$\sum_{I\in\mathbf{B}}S_I = 0$.
-
-Generally, we can consider an arbitrary set of subsets of $[0,n]$ in eq.\eqref{stringyintforgenpermutohedron}. 
-However, the big polytope for such integral in general is not a simplex.
-It's highly non-trivial to figure out all such sets whose big polytopes are simplices,
-but we can easily see that every generalized permutahedron satisfies $N=n+m$
-because each facet $F_I$ is given by a nested set $\{[0,n],I\}$ for $I\neq [0,n]$.
-Therefore, for a generalized permutahedron $\mathscr P$, we can write down the matrix 
-$W^J_A$ of facets and then get $S_J=F_A(W^{-1})^A_J\geq 0$ and 
-its $u$-variables $u_A=\prod_J p_J^{(W^{-1})^A_J}$.
-
-Let's first write down equations of facets of a generalised permutahedron
-with the building set $\mathbf{B}$. The polytope of eq.\eqref{stringyintforgenpermutohedron} is given by the Minkowski sum
-\[
-	- \sum_{I\in\mathbf{B},|I|>1}S_I.\Delta_I
-\]
-in $(S_0,\dots,S_n)$-space, where $\Delta_I=\operatorname{ConvexHull}
-(\{e_i\}_{i\in I})$. Meanwhile, we know from the last subsection that the facet 
-labeled by a nested set $\{[0,n],I\}$ is given by
-\begin{align*}
-	\biggl\{(S_0,S_1,\dots,S_n)\in \mathbb R^{n+1}\,\bigg |\,
-		\sum_{i\in I}S_i = -\sum_{J\subset I,|J|>1,J\in \mathbf{B}}S_J,
-		\quad
-		&\sum_{i=0}^nS_i=-\sum_{J\in \mathbf{B},|J|>1}S_J,\\
-		&\sum_{i\in K}S_i\geq -\sum_{J\subset I,|J|>1,J\in \mathbf{B}}S_J
-	\biggr\},
-\end{align*}
-where the second constrain is just $\sum_{I\in \mathbf{B}}S_I=0$, so the equation 
-of this facet is 
+\subsection{ABHY-like realizations and $u$ variables for generalized permutohedra}
+
+%We have seen that any $n$-dimensional generalized permutohedron can be constructed by a Minkowski sum of simplices labeled by subsets in the building set $\mathbf{B}$, which satisfy the conditions given above.
+As we mentioned earlier, one can write down a natural stringy integral \eqref{intgenperm} for generalized permutahedron $\mathscr{P}(\bf B)$,
+%it is a highly non-trivial fact about generalized permutohedra that the number of facets is given by $N=n+m$, where $m$ is the number of non-singletons in $\bf B$. 
+%because each facet $F_I$ is given by a nested set $\{[0,n],I\}$ for $I\neq [0,n]$.
+and its polytope is given by the Minkowski sum
+\[
+	\mathscr P_n(\{-S_I\,|\,I\in \mathbf B,\,|I|>1\}) =- \sum_{I\in\mathbf{B},|I|>1}S_I.\Delta_I,
+\]
+where $\Delta_I=\operatorname{ConvexHull}
+(\{e_i\}_{i\in I})$ is the coordinate simplex in $(S_0,\dots,S_n)$-space, so the equation of the facet labeled by $I$ is given by eq.\eqref{eqoffacet}:
 \begin{equation}\label{GPfacet}
@@
 \end{equation}
-
-Within all generalized permutahedra, the original permutahedron is quite simple
-and important because any other generalized permutahedron can be degenerated from
-permutahedron by setting some $S_I$ to be zero.
-The building set of the $n$-dimensional permutahedron $\mathscr P_n$ is 
+From the previous subsection we know that the big polyhedron of a generalized permutohedron is a simplex.
+Therefore, we can write down the matrix $W^J_A$ of the facets and obtain  
+\[
+S_J=F_A(W^{-1})^A_J
+\]
+and 
+its $u$ variables 
+\[ u_A=\prod_J x_J^{(W^{-1})^A_J}. \]
+
+Within generalized permutohedra, the original permutohedron is quite simple and important because any other generalized permutohedron can be obtained as a degenerated of the permutohedron.
+The building set of the $n$-dimensional permutohedron $\mathscr P_n$ is 
 the set of all non-empty subsets of $[0,n]$. 
-To get $u$-equations, we should solve $S_J$ by $F_J$ from eq.\eqref{GPfacet}, the 
-solution for permutahedron $\mathscr P_n$ is 
+To get $u$ equations, we should solve for $S_J$ from $F_J$ in eq.\eqref{GPfacet}, the 
+solution for the permutohedron $\mathscr P_n$ is 
 \begin{equation}\label{SinF}
-	S_I=\sum_{J\neq \varnothing,J\subset I} (-1)^{|J|-|I|}F_J,
-\end{equation}
-This give us the following ABHY construction for $\mathscr{P}_{n}$:
-\begin{equation}
-    F_{I}>0 \qquad  \text{for all non-empty proper subsets of $[0,n]$ }
-\end{equation}
-and
-\begin{equation}
-    C_I = (-1)^{|I|} \left( \sum_{i \in I} X_i - \sum _{{i<j}\atop{i,j \in I}} X_{ij} +\cdots + (-1)^{|I|}  X_I \right) \text{ are positive constants.}
-\end{equation}
-Using the picture of big polytope, this also gives $u$-variables
+	S_I=\sum_{J\subset I} (-1)^{|J|-|I|}F_J,
+\end{equation}
+This gives us the following ABHY polytope:
+setting 
+$S_I=-C_I$ for any non-singleton $I\in \mathscr P_n$, where $C_I$ are positive 
+constants, and the polytope is given by the alternating sum
+\begin{equation}\label{ABHY}
+	F_I\geq 0,\quad -C_I=\sum_{J\neq \varnothing,J\subset I}(-1)^{|J|-|I|}F_J
+\end{equation}
+in the $\{F_I\}$-space.
+By eq.\eqref{deffacet}, this polytope is the $n$-dimensional 
+permutohedron $\mathscr P_n(\{C_I\})$, and it is nice that it admits a simple ABHY-like realization.
+The ABHY construction of any generalized permutohedron can be obtained by 
+setting $C_I=0$ in $\mathscr P_n(\{C_I\})$ for all $I$ not in its building set.
+
+For example, the building set of $\mathscr A_2$ is $\mathbf B(\mathscr P_2)-\{\{0,2\}\}$,
+its ABHY construction can be obtained from $\mathscr P_2$ by setting $C_{02}=0$, 
+\[
+	0=-C_{02}=F_{02}-F_2,
+\]
+therefore the whole ABHY conditions for $\mathscr A_2$ is 
+\[
+	-C_{01}=F_{01}-F_0-F_1,\quad -C_{12}=F_{12}-F_1-F_2,\quad 
+	-C_{012}=-F_{01}-F_{12}+F_1,\quad F_I\geq 0,
+\]
+and its solution in $(F_1,F_2)$-space is 
+\[
+	\left\{\begin{aligned}
+		F_1&\geq 0,F_2\geq 0\\
+		F_0&=C_{01}+C_{12}+C_{012}-F_1-F_2\geq 0,\\
+		F_{12}&=F_1+F_2-C_{12}\geq 0,\\
+		F_{01}&=C_{012}+C_{12}-F_2\geq 0.
+	\end{aligned}\right.
+\]
+
+For another example, consider the building set
+\[
+\mathbf{B}=\{\{0\},\{1\},\{2\},\{3\},\{0,1,2\},\{1,3\},\{0,1,2,3\}\}.
+\]
+It's a degeneration of $\mathscr P_3$, where
+\[
+C_{01},C_{02},C_{03},C_{12},C_{23},C_{013},C_{023},C_{123}=0.
+\]
+Its $u$ variables and $u$ equations can be found at the end of section (\ref{sect3.4}). By solving the ABHY conditions for these $C_I=0$, we get the vanishing facets
+\begin{align*}
+&F_{0i}=F_0+F_i,\quad F_{12}=F_1+F_2,\quad F_{23}=F_2+F3,\\
+&F_{013}=F_{13}+F_0,\quad F_{023}=F_0+F_2+F_3,\quad F_{123}=F_2+F_{13},
+\end{align*}
+and the remaining ABHY conditions
+\[
+C_{13}=F_1+F_3-F_{13},\quad C_{012}=F_{0}+F_{1}+F_2-F_{012},
+\quad C_{0123}=F_{012}+F_{13}-F_1,
+\]
+its solution in $(F_1,F_2,F_3)$-space is 
+\[
+	\left\{\begin{aligned}
+		F_1&\geq 0,F_2\geq 0,F_3\geq 0\\
+		F_0&=C_{012}+C_{0123}+C_{13}-F_1-F_2-F_3\geq 0,\\
+		F_{13}&=F_1+F_3-C_{13}\geq 0,\\
+		F_{012}&=C_{0123}+C_{13}-F_3\geq 0.
+	\end{aligned}\right.
+\]
+
+Thanks to eq.\eqref{SinF}, using the picture of big polyhedron, it gives $u$ variables of permutohedron $\mathscr P_n$
 \begin{equation}
@@
 \[
-	\prod_{I\neq \varnothing,I\subset [0,n]}u_I^{F_I}=
-	\prod_{I\neq \varnothing,I\subset [0,n]}x_I^{S_I}=
-	\prod_{\varnothing\neq J\subset I\subset [0,n]}
+	\prod_{I\subset [0,n]}u_I^{F_I}=
+	\prod_{I\subset [0,n]}x_I^{S_I}=
+	\prod_{ J\subset I\subset [0,n]}
 	x_I^{(-1)^{|J|-|I|}F_J}=
-	\prod_{J\neq \varnothing,J\subset [0,n]}
+	\prod_{J\subset [0,n]}
 	\prod_{I\supset J}(x_I^{(-1)^{|J|-|I|}})^{F_J}.
 \]
-% The following set of equations define the $n$-dimensional Permutahedron: 
+% The following set of equations define the $n$-dimensional permutohedron: 
 % \bea
@@
 %Thus we see that $N= d+m$ as expected.
-
 Let us look at the $n=2,3$ examples:
 
-\paragraph*{2d permutahedron}
-In this case, the $u$-variables can be written in terms of $x$ variables as:
+\paragraph*{2d permutohedron}
+In this case, the $u$ variables can be written in terms of $x$ variables as:
 \[
@@
 \]
-The $u$-equations are:
-\begin{align*}
+The $u$ equations are:
+\begin{align}\label{perm2}
 	&1-u_{0}=u_{1} u_{2} u_{12}^2,
 	1-u_{1}=u_{0} u_{2} u_{02}^2,
-	1-u_{2}=u_{0} u_{1} u_{01}^2,\\
+	1-u_{2}=u_{0} u_{1} u_{01}^2,\nonumber\\
 	&1-u_{01}=u_{2} u_{02} u_{12},
@@
 	1-u_{12}=u_{0} u_{01} u_{02}.
+\end{align}
+which are the same as the $u$ equations for $\mathscr{B}_{2}$.
+
+\paragraph*{3d permutohedron}
+In this case, 
+the $u$ variables can be written in terms of $x$ variables as:
+%the building set $B=\{ \{ 0,1,2,3\},\{ 0,1,2\},\{0,2,3\},\{0,1,3\},\{1,2,3\},\{0,1\},\{0,2\},\{0,3\},\{1,2\} \\ ,\{2,3\},\{1,3\},\{0\},\{1\},\{2\},\{3\}\}$.
+\begin{align*}
+  u_{0} = \frac{x_{0}x_{012}x_{013}x_{023}}{x_{01}x_{02}x_{03}x_{0123}} \:,\qquad  
+  u_{01} = \frac{x_{01}x_{0123}}{x_{012}x_{013}} \:,\qquad
+  u_{02} = \frac{x_{02}x_{0123}}{x_{012}x_{023}}\:, \qquad 
+  u_{012} = \frac{x_{012}}{x_{0123}},
 \end{align*}
-where are the same as the $u$ equations for $\mathscr{B}_{2}$
-
-\paragraph*{3d permutahedron}
-In this case, 
-the $u$-variables can be written interms of $x$ variables as:
-%the building set $B=\{ \{ 0,1,2,3\},\{ 0,1,2\},\{0,2,3\},\{0,1,3\},\{1,2,3\},\{0,1\},\{0,2\},\{0,3\},\{1,2\} \\ ,\{2,3\},\{1,3\},\{0\},\{1\},\{2\},\{3\}\}$.
-\begin{align}
-  u_{0} &= \frac{x_{0}x_{012}x_{013}x_{023}}{x_{01}x_{02}x_{03}x_{0123}} \:,\qquad  
-  u_{01} = \frac{x_{01}x_{0123}}{x_{012}x_{013}} \:, \\
-  u_{02} &= \frac{x_{02}x_{0123}}{x_{012}x_{023}}\:, \qquad 
-  u_{012} = \frac{x_{012}}{x_{0123}}\:,
-\end{align}
-and their cyclic. The $u$-equations are
-\begin{align}
-  1-u_{0} &= u_1 u_{2} u_{3} u_{12}^2 u_{23}^2  u_{13}^2 u_{123}^3 \left(1+ u_{0}  u_{023} u_{013} u_{012} u_{03} u_{01}  u_{02} \right)\:,  \\
-  1-u_{0 1} &= u_{2} u_{3}  u_{23}^2 u_{12} u_{13} u_{123}^2 u_{023}^2 u_{02} u_{03} \:,\\
-  1-u_{02} &= u_{1}u_{3} u_{13}^{2}u_{12}u_{23} u_{123}^{2} u_{013}^{2}u_{01}u_{03} \:,\\
+and their cyclic permutations. The $u$ equations are
+\begin{align}\label{perm3}
+  1-u_{0} &= u_1 u_{2} u_{3} u_{12}^2 u_{23}^2  u_{13}^2 u_{123}^3 \left(1+ u_{0}  u_{023} u_{013} u_{012} u_{03} u_{01}  u_{02} \right)\:,  \nonumber\\
+  1-u_{0 1} &= u_{2} u_{3}  u_{23}^2 u_{12} u_{13} u_{123}^2 u_{023}^2 u_{02} u_{03} \:,\nonumber\\
+  1-u_{02} &= u_{1}u_{3} u_{13}^{2}u_{12}u_{23} u_{123}^{2} u_{013}^{2}u_{01}u_{03} \:,\nonumber\\
  1-u_{012} &= u_3 u_{03}u_{13} u_{23} u_{0 1 3} u_{0 2 3} u_{123}  \:,
@@
 \end{align}
-and their cyclic.
-
-The 8 facets of the 3d permutahedron corresponding to $u_i \rightarrow 0$ and $u_{ijk} \rightarrow 0$ are all $\mathscr{B}_2$.
+and their cyclic permutations.The $u$ variables and $u$ equations of $\mathscr P_4$ can be found in appendix (\ref{appendix:B}).
+
+%The 8 facets of the 3d permutohedron corresponding to $u_i \rightarrow 0$ and $u_{ijk} \rightarrow 0$ are all $\mathscr{B}_2$.
 Similarly, the 6 facets corresponding to  $u_{ij} \rightarrow 0$ are all  $\mathscr{A}^{2}_1$.
-Thus, the 3d permutahedron integral factorizes nicely on all massless poles at finite $\alpha'$!.
+%Thus, the 3d permutohedron integral factorizes nicely on all massless poles at finite $\alpha'$!.
 
@@
 % \eea }
-% The $u$-equations in this case are:
+% The $u$ equations in this case are:
 % {\scriptsize \bea
@@
 
-\subsubsection{The binary aspects of $u$-variables for permutohedra}
-
-Here we will show that the $u_{I}$'s for the permutahderon $\mathscr{P}_{n}$, which is defined by eq.\eqref{uvarforPn},
+\subsection{Permutohedra as binary geometries}
+
+Int this subsection, we will show that the $u_{I}$'s for the permutohedron $\mathscr{P}_{n}$, which are defined by eq.\eqref{uvarforPn},
 % \begin{equation}
@@
 % \end{equation}
-have the desired binary property, that is, $u_{I}$ and $u_{J}$ are compatible if and only if $I \subset J$ or $J\subset I$, otherwise, they are incompatible.
-Forthermore, we will show that the $u$-variables compatible with $u_{I}$ will become the $u$-variables for the facet $\mathscr{P}_{\lvert I \rvert-1}\times \mathscr{P}_{n-\lvert I\rvert}$ as $u_{I}$ gose to 0.
+have the desired binary property.
+Recall that $u_{I}$ and $u_{J}$ are compatible if and only if $I \subset J$ or $J\subset I$, otherwise they are incompatible.
+We will see that as  $u_{I} \to 0$, all the incompatible $u_J \to 1$.
+Furthermore, we will show that the $u$ variables compatible with $u_{I}$ become the $u$ variables for the facet $\mathscr{P}_{\lvert I \rvert-1}\times \mathscr{P}_{n-\lvert I\rvert}$.
 % In other words, this means that $u_{I}$ and $u_{J}$ are incompatible if $I$ and $J$ are one of the following two cases:
 % \begin{enumerate}[resume]
-%    \item $I\cap J=\emptyset$ and $I\cup J \in \mathcal{B}$ \:, 
-%    \item $I\cap J \neq \emptyset,I, J $ \:.
+%    \item $I\cap J=\varnothing$ and $I\cup J \in \mathcal{B}$ \:, 
+%    \item $I\cap J \neq \varnothing,I, J $ \:.
 % \end{enumerate}
@@
 
-Let us first show that the $u$-variables incompatible with $u_{I}$ become 1 as $u_{I}$ goes to 0.
+Let us first show that the $u$ variables incompatible with $u_{I}$ become 1 as $u_{I}$ goes to 0.
 It is obvious that $u_{I}$ and $u_{J}$ are incompatible if either (1) $I\cap J=  \varnothing$  or (2) $I\cap J \neq \varnothing,I, J $.
@@
 \begin{equation}
-   \log u_{J} \to \sum_{\kappa\subset K} (-1)^{\lvert \kappa\rvert } \log (x_{J}+x_{ \kappa})\Biggl(\sum_{\psi\subset I}(-1)^{\lvert\psi\rvert}\binom{\lvert \psi \rvert }{\lvert I \rvert }\Biggr)=0 \label{incompn1}
+   \log u_{J} \to \sum_{\kappa\subset K} (-1)^{\lvert \kappa\rvert } \log (x_{J}+x_{ \kappa})\Biggl(\sum_{\psi\subset I}(-1)^{\lvert\psi\rvert}\binom{\lvert I \rvert }{\lvert \psi \rvert }\Biggr)=0 \label{incompn1}
 \end{equation}
@@
 
-Now let us consider the behaviour of compatible $u$-variables under this limit. For $J\subset I$, we again introduce $I'=I-J$ and $K=[0,n]-I$, then the logarithm of $u_{J}$ can written as 
+Now let us consider the behaviour of compatible $u$ variables under this limit. For $J\subset I$, we again introduce $I'=I-J$ and $K=[0,n]-I$, then the logarithm of $u_{J}$ can written as 
 \begin{equation}
@@
 \end{equation}
-Next, we replac $x_{i}$ with $ \epsilon x_{i}$ for all $i\in I$ and take $\epsilon \to 0$, then 
+Next, we replace $x_{i}$ with $ \epsilon x_{i}$ for all $i\in I$ and take $\epsilon \to 0$, then 
 \begin{align}
    \log u_{J} &\to \lim_{\epsilon \to 0} \sum_{\psi'\subset I', \kappa \subset K} (-1)^{\lvert \psi'\rvert +\lvert \kappa \rvert} \log (\epsilon x_{J}+ \epsilon x_{\psi'}+x_{\kappa}) \nonumber  \\
-    &=\lim_{\epsilon\to 0} \biggl(\log \epsilon+\sum_{\kappa\subset K,\kappa \neq \varnothing}\log x_{\kappa}\biggr)\Biggr( \sum_{\psi'\subset I'}(-1)^{\lvert\psi'\rvert}\binom{\lvert \psi' \rvert }{\lvert I \rvert }\Biggr)
+    &=\lim_{\epsilon\to 0} \biggl(\log \epsilon+\sum_{\kappa\subset K,\kappa \neq \varnothing}\log x_{\kappa}\biggr)\Biggr( \sum_{\psi'\subset I'}(-1)^{\lvert\psi'\rvert}\binom{\lvert I \rvert }{\lvert  \psi' \rvert }\Biggr)
     +\sum_{\psi'\subset I'} (-1)^{\lvert \psi'\rvert }\log (x_{J}+x_{\psi'}) \nonumber \\
@@
 \end{align}
-Obviously, the expression in the last line of \eqref{subP1} is exactly the $u$-variable for the permutahderon $\mathscr{P}_{\lvert I\rvert -1}$.
+Obviously, the expression in the last line of \eqref{subP1} is a $u$ variable for the permutohedron $\mathscr{P}_{\lvert I\rvert -1}$.
 For $J\supset I$, under the limit of $x_I\to 0$, the logarithm of $u_{J}$ simply becomes
@@
 \end{equation}
-where $K=[0,n]-J$, which is exactly the $u$-variable for the permutahderon $\mathscr{P}_{n-\lvert I\rvert}$
-
-\subsubsection{$u$-equations of ${\mathscr P_n}$}
-
-For a permutohedra $\mathscr P_n$, we can directly use eq.\eqref{GPfacet} to express $x_I$ by $\{u_I\}$ which gives us many algebraic equations of $u$-variables:
+where $K=[0,n]-J$, which is a $u$ variable for the permutohderon $\mathscr{P}_{n-\lvert I\rvert}$. 
+%Now that we have shown that
+
+\subsubsection{The $u$ equations of ${\mathscr P_n}$}
+
+For a permutohedron $\mathscr P_n$, we can directly use eq.\eqref{GPfacet} to express $x_I$ in terms of $\{u_I\}$ which gives us many algebraic equations for the $u$ variables:
 \[
@@
 \end{equation}
-for any $I\in \mathscr P_n$, where we introduce a fake $u$-variable 
+for any $I\in \mathscr P_n$, where we introduce a fake $u$ variable 
 $u_{[0,n]}:=x_{[0,n]}$. We know some algebraic equations of $\{x_I\}$, 
@@
 \end{equation}
+We can in fact use the above relations to find the $u$ equations for $\mathscr{P}_n$ recursively as follows:
+
+For $I,J$ such that $|I|=n$ and $J=[0,n]-I = \{ i \}$ we have 
+$1-u_{I}= \prod_{i \in J} u_{J}$
+which is already an $u$ equation for $u_{I}$. For $|I|=n-1,~J=\{i\}$ and $\{k\}=[0,n]-(I\cup J)$ we have 
+$1- u_{I}u_{I\cup\{k\}} = \prod_{{\{i\} \in J}\atop{J\neq I\cup\{i\}}} u_J $ by rewriting $1- u_{I}u_{I\cup\{k\}}  =1-u_{I}+u_{I}(1-u_{I\cup\{k\}})$ and using the above equations we get 
+\bea
+1-u_{I}=\prod_{{\{i\} \in J}\atop{J\neq I\cup\{i\}}} u_J - u_{I} \prod_{\{i\} \in K} u_K =\prod_{{\{i\} \in J}\atop{J\neq I\cup\{i\}}} u_J \left(1- u_{I}  u_{I\cup\{i\}}\right)
+\eea
+More generally we can find the $u$ equation for any $I$ recursively by starting from $|I|=n$. We can argue this inductively by assuming we know the $u$ equations for all $I$ such that $|I|\geq k$.
+
+We can now look at all the sets $\{I_1,\dots,I_n\}$ that contain $|I|=k-1$ but not $I\cup J$ and arrange them as $|I|<|I_1|\leq |I_2|\leq \cdots \leq |I_n|$
+\bea
+1-\prod_{I\subset K,K\not\supset I\cup J}u_K &=&1-u_{I}u_{I_1}\cdots u_{I_n}= 1-u_I+u_I(1-u_{I_1}\cdots u_{I_n})\nonumber \\
+&=&(1-u_I)+u_I(1-u_{I_1})+u_I u_{I_1}(1-u_{I_2})+\cdots+u_I\prod_{i=1}^{n-1}u_{I_{i}}(1-u_{I_n})
+\eea
+Since $|I|< |I_i|$ for any $i$, we already know the $u$ equations for $I_i$ and we can find the equation for $u_I$.
 
 Let us consider the $2 d$ example for which the relations are :
-\bea
-1-u_1 u_{12} &=&u_0 u_{02}, ~~1-u_2 u_{12} =u_0 u_{01},~~1-u_{12}= u_0 u_{01} u_{02} \nonumber \\
-1- u_{01}&=& u_{0}u_1 u_{01}u_{12},~~1-u_0 u_{02}= u_{0}u_2 u_{02} u_{12}
+\[
+1-u_1 u_{12} =u_0 u_{02}, ~1-u_2 u_{12} =u_0 u_{01},~1-u_{12}= u_0 u_{01} u_{02},~1- u_{01}= u_2 u_{01}u_{12},~1-u_{02}= u_1 u_{02} u_{12}
+\]
+and the $u$ equations
+\begin{align}\label{npu}
+1-u_1&=u_0 u_{02}(1-u_1 u_{01}), \quad 1-u_2 =u_0 u_{01}(1-u_2 u_{02}),\quad 1-u_{12}= u_0 u_{01} u_{02} \nonumber\\
+1- u_{01}&= u_2 u_{01}u_{12},\qquad \qquad \:1-u_{02} = u_1 u_{02} u_{12} \quad\qquad \qquad \: 1-u_0=u_1 u_{12}(1-u_0 u_{01})
+\end{align}
+which is different non-perfect set of $u$ equations for ${\mathscr P}_2$ unlike eq.\eqref{perm2}!
+
+A nice fact about the $u$ equations we obtain is that $1-u_I$ are all at most linear and multi-term in $u_I$ for any $n$.
+However, they do not make the factorization manifest at the level of $u$ equations as we take some $u_I \rightarrow 0$ all incompatible $u_J \rightarrow 1$ but the $u$ equations corresponding to other $u$'s are trivially satisfied thereby not reflecting the facets of ${\mathscr P}_n$ (as can be seen by taking $u_{12} \rightarrow 0$ in eq.\eqref{npu}).
+
+The $u$ equations for $\mathscr{P}_n$ similar to eqs.\eqref{perm2}, \eqref{perm3} which do make factorization manifest are complicated polynomials %of order $n-|I|-1$
+in the corresponding $u$'s. 
+The most general $u$ equations can be conjectured to be:
+\bea \label{ueqforpn}
+1-u_{I} = (1+h_{I,n}(u)) \prod_{J} u^{(J||I)}_{J} 
 \eea
-By rewriting $(1-u_i)= (1-u_i u_{12})-u_i(1-u_{12}))$ we can get $u$-equations for $u_i$ with $i=1,2$.
-Similarly by rewriting $(1-u_0)=(1-u_0 u_{01} u_{02})-u_0 (1-u_{01})-u_0 u_{01}(1-u_{02}) $ we can get the $u$-equation for $u_0$
-\bea
-1-u_1&=&u_0 u_{02}(1-u_1 u_{01}), ~~1-u_2 =u_0 u_{01}(1-u_2 u_{02}),~~1-u_{12}= u_0 u_{01} u_{02} \nonumber \\
-1- u_{01}&=& u_{0}u_1 u_{01}u_{12},~~1-u_0 u_{02}= u_{0}u_2 u_{02} u_{12}~~1-u_0=u_1 u_{12}(1-u_0 u_{01})
-\eea
-More generally we can rewrite 
-\bea
-(1-u_I)= (1- \prod_{I \subset J} u_I) -u_I(1-u_{I_1})-u_I u_{I_1}(1-u_{I_2})-\cdots-\prod_{I \subsetneq [1~n]}(1-u_{12\cdots n})
-\eea
-Since $I \subsetneq I_1,I_2$ $|I|< |I_1|,|I_2|$ thus we already know the $u$-equations for $I_1,I_2,\cdots,[1,n]$ as we recursively find them starting from $|I|=n$.
-
-A nice fact about the $u$-equations we obtain is that $1-u_I$ are all at most linear and multi term in $u_I$ for any $n$.
-However, they do not make the factorization manifest at the level of $u$-equations as we take some $u_I \rightarrow 0$.
-The $u$-equations for $\mathscr{P}_n$ which make factorization manifest are complicated polynomials of order $n-|I|-1$ in the corresponding $u$'s.
-Thus, the most general $u$-equations can be conjectured to be:
-\bea
-1-u_{I} = \prod_{J} u^{s_J}_{J} F(u_I, u_J,u_K) 
-\eea
-where, $J$ are all sets incompatible with $I$, $K$ are all sets compatible with $I$ excluding itself and $s_J$ are positive integers.
-$F(u_I, u_J,u_K) $ is polynomial of degree $n-|I|-1$ in $u_I$ and we conjecture that $F(u_I =0, u_J,u_K) = 1$ which makes $\mathscr{P}_n$ binary as we proved using a different method in the previous section.
-But we do not have a closed form expression for $F(u_I, u_J,u_K)$ for all $n$.
-
-Some of the simplest ones are:\\
-
-For $|I| =n-1$ and $s_K = \begin{cases}  1,~ if K \not\subset I & \\ 2, ~if K \subset I\end{cases}$
-
-\bea
-1-u_{I} &=& \prod_ {S - I \subset J } u_{J} \prod_ {K \cap I \ne \Phi } (u_{\bar{K}})^{s_K}  \nonumber \\
-1-u_{12\cdots n} &=& \prod_ {{I \subset S}\atop {I \ne \Phi}} u_{\bar{I}} \nonumber
-\eea
-and for $|I| =n-2$ with $ \bar{I} = \{i, j\}$
-\bea
-1-u_{I}= u_i u_j u^{2}_{ij} \prod_{J \subset I} u_{J \cup \{i\}} u_{J \cup \{j\}} u^{2}_{J \cup \{i,j\}} \prod_{K \subset S-I} (u_{\bar{K}})^{3} (u_{\bar{K \cup \{i\}}})^{2}  (u_{\bar{K \cup\{j\}}})^{2}  u_{\bar{K\cup \{i,j\}}} \left( 1+ u_{\bar{\{i\}}} u_{\bar{\{j\}}} u^{'}_{\bar{\{ij\}}} \prod_{I \subset L} u_L \right)                       \nonumber
-\eea
-
-Using eq.\eqref{xinu}, we can say more on $u$-equations,
-\[
+where $J$ runs over all sets incompatible with $I$, $(J||I)$ is a positive integer, called the ``compatibility degree'', and $h_{I,n}(u)$ is polynomial %of degree $n-|I|-1$
+in $u_I$ such that $h_{I,n}|_{u_I =0} = 0$ which makes $\mathscr{P}_n$ binary as we proved using a different method in the previous section.
+But we do not have a closed form expression for $h_{I,n}(u)$ for all $n$ and $I$.
+We list some of them along with the ${\mathscr P_4}$ example in appendix (\ref{appendix:B}).
+
+%Some of the simplest ones are:\\
+
+%For $|I| =n-1$ and $s_K = \begin{cases}  1,~ if K \not\subset I & \\ 2, ~if K \subset I\end{cases}$
+
+%\bea
+%1-u_{I} &=& \prod_ {S - I \subset J } u_{J} \prod_ {K \cap I \ne \Phi } (u_{\bar{K}})^{s_K}  \nonumber \\
+%1-u_{12\cdots n} &=& \prod_ {{I \subset S}\atop {I \ne \Phi}} u_{\bar{I}} \nonumber
+%\eea
+%and for $|I| =n-2$ with $ \bar{I} = \{i, j\}$
+%\bea
+%1-u_{I}= u_i u_j u^{2}_{ij} \prod_{J \subset I} u_{J \cup \{i\}} u_{J \cup \{j\}} u^{2}_{J \cup \{i,j\}} \prod_{K \subset S-I} (u_{\bar{K}})^{3} (u_{\bar{K \cup \{i\}}})^{2}  (u_{\bar{K \cup\{j\}}})^{2}  u_{\bar{K\cup \{i,j\}}} \left( 1+ u_{\bar{\{i\}}} u_{\bar{\{j\}}} u^{'}_{\bar{\{ij\}}} \prod_{I \subset L} u_L \right)                       \nonumber
+%\eea
+
+Although the polynomial $h_{I,n}$ is very complicated for general $I$ and $n$, we can still say something about its  ``compatibility degree'' $J||I$ in eq.\eqref{ueqforpn}.
+Using eq.\eqref{uvarforPn}, 
+\begin{equation}\label{oneminusui}
 1-u_I=1-\prod_{J\supset I}x_J^{(-1)^{|J|-|I|}}=\frac{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J-\prod_{|J|-|I| \text{ even}; J\supset I}x_J}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J}=:\frac{N_{I,n}(x)}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J},
-\]
-where $N_{I,n}(x)$ is a polynomial of degree $D_{I,n}=2^{|\bar I|-1}$.
-It's easy to see that $x_i$ for $i\not\in I$ is a factor of $N_{I,n}(x)$ by setting $x_i=0$, so we can define a new polynomial $f_{I,n}$ of degree $D_{I,n}-|\bar I|$ with non-negative coefficients such that
+\end{equation}
+where $N_{I,n}(x)$ is a polynomial of degree $2^{|\bar I|-1}$ in $x$.
+It's easy to see that $x_i$ for $i\not\in I$ is a factor of $N_{I,n}(x)$ by setting $x_i=0$, so we can define a new polynomial $f_{I,n}$ of degree $2^{|\bar I|-1}-|\bar I|$ with non-negative coefficients such that
 \[
@@
 \]
-It's not so obvious that $x_i$ for $i\not\in I$ is not a factor of $f_{I,n}$, which means that the above factorization of $N_{I,n}$ is reasonable.
-In fact, the $(D_{I,n}-|\bar I|)$-th derivative of $N_{I,n}$ with respect to $x_I$ is $a_{I,n}\prod_{i\not\in I}x_i$,
-where $a_{I,n}$ is a positive integer. It's conjectured that $a_{I,n}=(|\bar I|-1)!=(n-|I|)!$.
-
-From
-\[
-\prod_{i\not\in I}x_i=\prod_J u_J^{|J|-|I\cap J|}
-\quad\text{and}\quad
-\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
-=
-\prod_{J\supsetneq I}u_J^{2^{|J|-|I|-1}},
-\]
-then
+%It's not so obvious that $x_i$ for $i\not\in I$ is not a factor of $f_{I,n}$, which means that the above factorization of $N_{I,n}$ is reasonable.
+It will be clear when we calculate $N_{I,n}(x)|_{x_I=0}$ below.
+%In fact, the coefficient of $x_I^{D_{I,n}-|\bar I|}$ in $N_{I,n}(x)$ is $a_{I,n}\prod_{i\not\in I}x_i$, 
+%where $a_{I,n}$ is a positive integer. It's conjectured that $a_{I,n}=(|\bar I|-1)!=(n-|I|)!$.
+Using eq.\eqref{xinu},
+%\[
+%\prod_{i\not\in I}x_i=\prod_J u_J^{|J|-|I\cap J|}
+%\quad\text{and}\quad
+%\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
+%=
+%\prod_{J\supsetneq I}u_J^{2^{|J|-|I|-1}},
+%\]
+%then
 \[
 \prod_{i\not\in I}x_i\bigg/\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
-=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supsetneq I} u_J^{|J|-|I|-2^{|J|-|I|-1}}
-\]
-is a rational function of $x$.
-Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's natural to rewrite that
+=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supsetneq I} u_J^{|J|-|I|-2^{|J|-|I|-1}}.
+\]
+Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$ for $J\supsetneq I$, it's natural to rewrite eq.\eqref{oneminusui} as
+\[
+1-u_I=g_{I,n}\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
+\]
+where 
+\[
+g_{I,n}=f_{I,n}\bigg /\prod_{J\supsetneq I} u_J^{2^{|J|-|I|-1}-(|J|-|I|)}
+=f_{I,n}\bigg /\prod_{J\supset I, |J|-|I|\, \text{odd}\atop{|J|-|I|\geq 3}} x_J.
+\]
+It's easy to see that $g_{I,n}=1+h_{I,n}$ by taking $x_I\to 0$, where $h_{I,n}$ is a rational function of $x$ such that $h_{I,n}|_{x_I=0}=0$. In fact, 
+\[
+N_{I,n}|_{x_I=0}=\prod_{|J|-|I| \text{ odd}; J\supset I}x_{J-I}=\prod_{i\not\in I}x_i\prod_{J\supset I, |J|-|I|\, \text{odd}\atop{|J|-|I|\geq 3}} x_{J-I}=f_{I,n}|_{x_I=0}\prod_{i\not\in I}x_i\quad \Rightarrow\quad g_{I,n}|_{x_I=0}=1.
+\]
+Therefore, 
 \begin{equation}\label{ueqofPn}
-1-u_I=g_{I,n}\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
-\end{equation}
-where 
-\[
-g_{I,n}:=f_{I,n}\bigg /\prod_{J\supsetneq I} u_J^{2^{|J|-|I|-1}-(|J|-|I|)}
-=f_{I,n}\bigg /\prod_{J\supset I, |J|-|I|\, \text{odd}\atop{|J|-|I|\geq 3}} x_J.
-\]
-We conjecture that $g$ is a polynomial of $u$ with non-negative coefficients.
-The product $\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}$ has appeared in all known examples with right powers.
+1-u_I=(1+h_{I,n})\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
+\end{equation}
+and we conjecture that $h_{I,n}$ is a polynomial of $u$ with non-negative coefficients, and the ``compatibility degree'' is 
+\[
+J||I=|J|-|I\cap J|\text{ for $I\not\subset J$},\quad  J||I=0 \text{ for $I\subset J$}.
+\]
 It's clear that any compatible $u_J$ for $J\subset I$ doesn't appear in the product because $I\cap J=J$.
-Thus, there's a conjecture about the compatibility degree:
-\[
-I||J=|J|-|I\cap J|\text{ for $I\not\subset J$},\quad  I||J=0 \text{ for $I\subset J$}.
-\]
-It's not symmetric when $|I|\neq |J|$.
-
-We conjecture (and have checked upto $n=6$) that we can solve the $u$-equations in terms of $u_1,u_{12},\cdots,u_{12\cdots n} $ for the rest of the $u$'s.
-
- \bea
-\int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} \frac{d x_i}{x_i} \prod_{I} \left(x_I \right) ^{-\alpha^{'} S_I} &=& \int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} \frac{d x_i}{x_i} \prod_{\alpha} \left(u_I \right) ^{-\alpha^{'} F_{\alpha}} \\
-&=&\int_{[0,1]^n} \prod_{i =1}^{n} \frac{d u_{1\cdots i}}{u_{1\cdots i}(1-u_{1\cdots i})} \prod_{\alpha} \left(u_I(u_{1\cdots i}) \right) ^{-\alpha^{'} F_{\alpha}}
-\eea
-
-\subsection{Binary aspects of generalized Permutohedra}
-
-Inspired by the $u$-variables for permutahdera, we directly come up with the $u$-variables for generalized permutohedra.
+Note that it's not symmetric when $|I|\neq |J|$.
+
+% In the case of $n$-dimensional cluster polytopes, all $u$ variables can be expressed \emph{rationally} in terms of $n$ of them, which correspond a acyclic quiver, by solving $u$ equations~\cite{Arkani-Hamed:2019plo}.
+Then the configuration space can be described by a $n$-dimensional hypercube $0<u_{\alpha}<1$ with the canonical form $\prod \mathrm{d} \log \frac{u_{\alpha}}{1-u_{\alpha}}$.
+The situation becomes quite different for the $n$-dimensional permutohedron when $n>2$ (since $\mathscr{P}_{2}=\mathscr{B}_{2}$).
+First, all vertices (for which the coresponding $u$ variables can freely take values from 0 to 1) of a permutohedron are equivalent up to a permutation of indices.
+Then we can simply solve all $u$'s in terms of $u_{[1,i]}$ with $i\in [1,n]$, and the solutions are not rational when $n=3$.
+Thus, the stringy integral \eqref{intgenperm} for the $(n>2)$-dimensional permutahderon dose \emph{not} admit a form of
+% \begin{equation}
+%     (\alpha')^{n}\int_{[0,1]^{n}} \prod_{\alpha=1}^{n}\mathrm{d}\log\frac{u_{\alpha}}{1-u_{\alpha}} \: \prod_{a=1}^{N} u_{a}^{\alpha' X_{a}} \:,
+% \end{equation} 
+% as in the case of cluster polytopes \cite{Arkani-Hamed:2019plo}.
+Of course, this doesn't mean the stringy integral \eqref{intgenperm} for $\mathscr{P}_{n>2}$ cannot be expressed rationally in terms of $u$ variables.
+For example, one can use $u_{\bar{\imath}}:= u_{[0,n]-\{i\}}$ to describe this configuration space rationally since $x_{i}=(u_{\bar{\imath}}-1)/\bigl(n-1-\sum u_{\bar{\imath}} \bigr)$ under the gauge fixing of $x_{0}=1$, then the stringy integral
+% \begin{equation}
+%   \mathcal{I}(\mathscr{P}_{n>2})= \int_{U} \frac{1}{\sum_{i=1}^{n}u_{\bar{\imath}}-(n-1)} \prod_{i=1}^{n}\frac{\mathrm{d}u_{\bar{\imath}}}{1-u_{\bar{\imath}}} \prod_{I\subset [0,n]} u_{I}(\{u_{\bar{\imath}}\})^{\alpha' F_{I}}
+% \end{equation}
+% where 
+% \begin{equation*}
+%   U=\biggl\{\sum_{i=1}^{n} u_{\bar{\imath}}>n-1 \quad \text{and}\quad  0<u_{\bar{\imath}}<1\biggr\} \:.
+% \end{equation*}
+% There are certainly lots of other choices of $u$'s to describe this configuration space rationally, however, the integration region $U$ depends on these choices now.
+% rather than just an $n$-dimensional hypercube.
+% We conjecture (and have checked upto $n=6$) that we can solve the $u$ equations in terms of $u_1,u_{12},\cdots,u_{12\cdots n} $ for the rest of the $u$'s.
+
+% \bea
+% \int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} \frac{d x_i}{x_i} \prod_{I} \left(x_I \right) ^{-\alpha' S_I} &=& \int_{\mathbb{R}^{n}_{+}} \prod_{i =1}^{n} \frac{d x_i}{x_i} \prod_{\alpha} \left(u_I \right) ^{-\alpha' F_{\alpha}} \\
+% &=&\int_{[0,1]^}n} \prod_{i =1}^{n} \frac{d u_{1\cdots i}}{u_{1\cdots i}(1-u_{1\cdots i})} \prod_{\alpha} \left(u_I(u_{1\cdots i}) \right) ^{-\alpha' F_{\alpha}}
+% \eea
+
+\subsection{Generalized permutohedra as binary geometries}\label{sect3.4}
+
+Inspired by the $u$ variables for permutohdera, we directly come up with the $u$ variables for generalized permutohedra.
 To this end, we first find all minimum extensions $I_{a}$ of $I$ in $\mathbf{B}$, that is there is no $J\in\mathbf{B}$ such that $I\subsetneq J\subsetneq I_{a}$, and we denote the collection of these extensions by $\mathscr{G}_{I}$.
-Then, the $u$-variables for the generalized permutohedron with building set $\mathbf{B}$ are
+Then, the $u$ variables for the generalized permutohedron with the building set $\mathbf{B}$ are
 \begin{equation}
-   \log u_{I} :=  \log x_{I} +(-1)^{k}\sum _{\varnothing\neq\{I_{a_{1}},\cdots,I_{a_{k}}\}\subset \mathscr{G}_{I}} \log x(I_{a_{1}},\ldots, I_{a_{k}})  \label{uvarforgenpermu}
-\end{equation}
-where the sum is over all nonemepty subsets of $\mathscr{G}_{I}$, and we introduce
+   \log u_{I} :=  \log x_{I} +(-1)^{k}\sum _{\varnothing\neq\{I_{a_{1}},\dots,I_{a_{k}}\}\subset \mathscr{G}_{I}} \log x(I_{a_{1}},\ldots, I_{a_{k}})  \label{uvarforgenpermu}
+\end{equation}
+where the sum is over all nonempty subsets of $\mathscr{G}_{I}$, and we introduce
 \[
@@
 \begin{equation}
-   \log u_{I} := (-1)^{k}\sum _{\{I_{a_{1}},\cdots,I_{a_{k}}\}\subset \mathscr{G}_{I}} \log \bigl(x_{I}+x(I_{a_{1}}-I,\ldots, I_{a_{k}}-I)\bigr)  \label{uvarforgenpermu1}
-\end{equation}
-It is easy to check that the $u$-variables for simplices, hypertubes, associahedra, cyclohedra and permutohedra defined above can be viewed as the special cases of \eqref{uvarforgenpermu}:
+   \log u_{I} := (-1)^{k}\sum _{\{I_{a_{1}},\dots,I_{a_{k}}\}\subset \mathscr{G}_{I}} \log \bigl(x_{I}+x(I_{a_{1}}-I,\ldots, I_{a_{k}}-I)\bigr)  \label{uvarforgenpermu1}
+\end{equation}
+Let us consider several simple examples to illustrate this construction:
+% It is easy to check that the $u$ variables for simplices, hypercubes, associahedra, cyclohedra and permutohedra defined above can be viewed as the special cases of \eqref{uvarforgenpermu}:
 \begin{enumerate}[label=(\roman*)]
-   \item For a $n$-dimensional simplex, $\mathscr{G}_{\{i\}}=\{[0,n]\}$ for every singleton $\{i\}$.
-   \item For a $n$-dimensional hypertube, $\mathscr{G}_{\{0\}}=\{[0,1]\}$, $\mathscr{G}_{\{i\neq 0\}}=\{[0,i]\}$ and $\mathscr{G}_{[0,i]}=\{[0,i+1]\}$.
+   %\item For a $n$-dimensional simplex, $\mathscr{G}_{\{i\}}=\{[0,n]\}$ for every singleton $\{i\}$.
+   \item For a $n$-dimensional hypercube, $\mathscr{G}_{\{0\}}=\{[0,1]\}$, $\mathscr{G}_{\{i\neq 0\}}=\{[0,i]\}$ and $\mathscr{G}_{[0,i]}=\{[0,i+1]\}$.
+This gives $u_{0}=x_{0}/x_{01}$, $u_{i}=x_{i}/x_{[0,i]}$ and $u_{[0,i]}=x_{[0,i]}/x_{[0,i+1]}$.
+These are indeed the $u$ variables for the $n$-dimensional hypercube since  $u_{i+1}+u_{[0,i]}=1$ for $i\in [0,n{-}1]$.
    \item For a $n$-dimensional associahedron,
@@
       \{[i-1,j]\} &\quad \text{if $i\neq 0$ and $j= n $}
-   \end{cases}   
-   \]
-   \item For a $n$-dimensional cyclohedron, $\mathscr{G}_{[i,j]}=\{[i-1,j],[i,j+1]\}$
-   \item For a $n$-dimensional permutohedron, $\mathscr{G}_{I}=\{I\cup\{j\}\vert j\in [0,n]-I \}$
+   \end{cases}   \:.
+   \]
+   This reproduces the $u$ variables \eqref{uvarforAn} for the $n$-dimensional associahedron.
+   \item For a $n$-dimensional cyclohedron, $\mathscr{G}_{[i,i+k]}=\{[i-1,i+k],[i,i+k+1]\}$.  This reproduces the $u$ variables \eqref{uvarforBn} for the $n$-dimensional cyclohedron.
+   \item For a $n$-dimensional permutohedron, $\mathscr{G}_{I}=\{I\cup\{j\}\vert j\in [0,n]-I \}$. This reproduces the $u$ variables \eqref{uvarforPn} for the $n$-dimensional permutohedron.
 \end{enumerate}
 
-% \paragraph{Example:} For the generalized permutahderon with building set 
+% \paragraph{Example:} For the generalized permutohedron with building set 
 % \[
@@
 % \]
-% the corresponding $u$-variables are
+% the corresponding $u$ variables are
 % \begin{gather*}
@@
 
-For generalized permutahdera, $u_{I}$ and $u_{J}$ are incompatible if $I$ and $J$ are one of the following two cases:
-\begin{enumerate}
+For generalized permutohedra, as we have reviewed in sec.(\ref{GP}), $u_{I}$ and $u_{J}$ are incompatible if $I$ and $J$ are one of the following two cases:
+\begin{enumerate}[label=(\arabic*)]
    \item $I\cap J=\varnothing$ and $I\cup J \in \mathbf{B}$ \:, 
@@
 \end{enumerate}
-while $u_{I}$ and $u_{J}$ are compatible if $I$ and $J$ are one of the following three cases:
-\begin{enumerate}[resume]
+while $u_{I}$ and $u_{J}$ are compatible if $I$ and $J$ satify one of the following three conditions:
+\begin{enumerate}[resume,label=(\arabic*)]
    \item $J\subset I$\:,
@@
 \end{enumerate}
-We will follow the argument in the cases of permutahdera: replacing $x_{i}$ with $ \epsilon x_{i}$ for all $i\in I$ and taking $\epsilon \to 0$, then considering the behaviour of the other $u_{J}$'s under this limit case by case.
+We will follow the same argument as in the case of permutohedra: replacing $x_{i}$ with $ \epsilon x_{i}$ for all $i\in I$ and taking $\epsilon \to 0$, then considering the behaviour of the other $u_{J}$'s under this limit case by case.
 % For future convenience, we assume that the generating set $\mathbf{J}$ for $J$ has $s$ elements denoted by $J_{a}$ with $a\in[1,s]$, and introduce 
@@
 \end{align}
-Remarkably, they are $u$-variables for the generalized permutohedron with the building set
-\begin{equation}
-   \mathbf{B}_{I} = \{J \vert J\subset I, J\in \mathbf{B}\}.
-\end{equation}
+Remarkably, these are $u$ variables for the generalized permutohedron with the building set $\mathbf{B}_{I}$ defined by \eqref{BI}.
+% \begin{equation}
+%   \mathbf{B}_{I} = \{J \vert J\subset I, J\in \mathbf{B}\}.
+% \end{equation}
 
 Case (4) and (5) are quite trivial.
-For case (4), the limit behaviour of $u_{J}$ as $x_{I}\to 0$ can be simply obtained by replacing each $x_{K}$ in eq.\eqref{uvarforgenpermu} with $x_{K-I}$.
-For case (5), $u_{J}$ is  independent of $x_{i}$ with $i\in I$.
-Remarkably, they are $u$-variables for the generalized permutohedron with the building set
-\begin{equation}
-   \mathbf{B}_{\bar{I}} = \{J-I \vert J\in \mathbf{B}\}.
-\end{equation}
-
-\paragraph{Example}  We start with the Cayley graph proposed in \cite{} and further studied in \cite{}.
+For both cases, the limit behaviour of $u_{J}$ as $x_{I}\to 0$ can be simply obtained by replacing each $x_{K}$ in eq.\eqref{uvarforgenpermu} with $x_{K-I}$.
+%For case (5), $u_{J}$ is  independent of $x_{i}$ with $i\in I$.
+Remarkably, these are the $u$ variables for the generalized permutohedron with the building set $ \mathbf{B}_{\bar{I}}$ defined by \eqref{BIbar}.
+
+Here we just showed that binary geometries exist for generalized permutohedra and gave the corresponding $u$ variables.
+The $u$ equations are quite complicated in general, and we only have closed formulas for $\mathscr{A}_{n}$, $\mathscr{B}_{n}$ and their several degenerations.
+For permutohedra, we have just conjectured the $u$ equations are of form \eqref{ueqforpn}.
+More general, the $u$ equations don't even take the form of \eqref{ueqforpn}.
+For example, consider the generalized permutohedron with building set
+\[
+\mathbf{B}=\{\{0\},\{1\},\{2\},\{3\},\{0,1,2\},\{1,3\},\{0,1,2,3\}\},
+\]
+the corresponding $u$ variables are
+\begin{gather*}
+   u_{0}=\frac{x_{0}}{x_{012}} \:,\quad  u_{1}=\frac{x_{1}x_{0123}}{x_{012}x_{13}} \:,\quad 
+   u_{2}=\frac{x_{2}}{x_{012}} \:, \quad u_{3}=\frac{x_{3}}{x_{13}} \\
+   u_{012}=\frac{x_{012}}{x_{0123}}\:,\qquad u_{13}=\frac{x_{13}}{x_{0123}} \:. \quad 
+\end{gather*}
+The $u$ equations are\footnote{If we introduce $\tilde{u}_{02}=u_{0}+u_{2}$, then $\tilde{u}_{02}$ together with the remaining 4 $u$'s form $\mathscr{A}_{2}$}
+\begin{gather*}
+u_{0}+u_{2}+u_{1}u_{13}=1\:, \quad  u_{1}+(u_{0}+u_{2})u_{3}=1 \:, \quad u_{3}+u_{1}u_{012}=1\:, \\
+u_{012}+u_{3}u_{13}=1\:, \quad u_{13}+(u_{0}+u_{2})u_{012}=1\:.
+\end{gather*}
+We leave the study of compatible degrees and $u$ equations for general permutohedra to future work.
+%(Chi: If we denote $\tilde{u}_{02}=u_{0}+u_{2}$, then $\tilde{u}_{02}$ together with the remaining 4 $u$'s form $\mathscr{A}_{2}$ )
+% \begin{equation}
+%   \mathbf{B}_{\bar{I}} = \{J-I \vert J\in \mathbf{B}\}.
+% \end{equation}
+
+% \paragraph{Example}  We start with the Cayley graph proposed in \cite{He:2018pue} and further studied in \cite{}.
 In \cite{}, the ABHY realization for general Cayley graphs have been proposed, here we will use several examples of Cayley graphs to illustrate that the binary geometries exist for general permutohedra.
-The first Cayley graph which is nether associahedron nor permutahderon is so-called  ``next-to-$A_{3}$'', in terms of generalized permutahdera, the building set for next-to-$A_{3}$ is
-\begin{equation}
-   \mathscr{NA}_{3}=\{\{1,2,3,4\},\{1,2,3\},\{1,3,4\},\{2,3,4\},\{1,2\},\{1,3\},\{2,3\},\{3,4\},\{1\},\{2\},\{3\},\{4\}\}
-\end{equation}
-
-the $u$ variables are 
-\begin{align}
-   &u_{1}=\frac{x_{1}x_{123}}{x_{12}x_{13}} \:, \quad  u_{2}=\frac{x_{2}x_{123}}{x_{12}x_{23}} \:,  \quad 
-   u_{3}=\frac{x_{3}x_{134}x_{234}x_{123}}{x_{34}x_{13}x_{23}x_{1234}} \:, \quad 
-   u_{4}=\frac{x_{4}}{x_{34}} \\
-   &u_{12}=\frac{x_{12}}{x_{123}} \:, \quad u_{13}=\frac{x_{13}x_{1234}}{x_{134}x_{123}} \:,\quad 
-   u_{23}=\frac{x_{23}x_{1234}}{x_{123}x_{234}} \:, \quad u_{34}=\frac{x_{34}x_{1234}}{x_{134}x_{234}} \\
-   &u_{123}=\frac{x_{123}}{x_{1234}} \:, \quad u_{134}=\frac{x_{134}}{x_{1234}} \:, \quad 
-   u_{234}=\frac{x_{234}}{x_{1234}}
-\end{align}
-The $u$ equations are
-\begin{align}
-   &1-u_{1}=u_{2}u_{3}u_{23}^{2}u_{34}u_{234}^{2} \:, \\
-   &1-u_{2}=u_{1}u_{3}u_{13}^{2}u_{34}u_{134}^{2} \:, \\
-   &1-u_{3}= u_{1}u_{2}u_{4}u_{12}^{2}(1+u_{3}u_{13}u_{23}u_{34}u_{123}u_{134}u_{234}) \:, \\
-   &1-u_{4}=u_{3}u_{13}u_{23}u_{123}  \:, \\
-   &1-u_{12} =u_{3}u_{13}u_{23}u_{34}u_{134}u_{234} \:, \\
-   &1-u_{13} =u_{2}u_{4}u_{12}u_{23}u_{34}u_{234}^{2} \:, \\
-   &1-u_{23}= u_{1}u_{4}u_{12}u_{13}u_{34}u_{134}^{2} \:, \\
-   &1-u_{34}= u_{1}u_{2}u_{12}^{2}u_{13}u_{23}u_{123}^{2} \:, \\
-   &1-u_{123}=u_{4}u_{34}u_{134}u_{234} \:, \\
-   &1-u_{134}=u_{2}u_{12}u_{23}u_{123}u_{234} \:, \\
-   &1-u_{234}=u_{1}u_{12}u_{13}u_{123}u_{134} \:, 
-\end{align}
-
-\subsection {Binary geometries with non-linear factors}
-We can also consider general Minkowski sums of non-simplices and see if these also give us any instance of polytopes with perfect $u$ equations. One such case is the following:
-
-We consider the Minkowski sum of $n-1$ $A_2$'s with following Newton polynomial :
+The first Cayley graph which is nether associahedron nor permutohedron is so-called  ``next-to-$A_{3}$'', in terms of generalized permutohedra, the building set for next-to-$A_{3}$ is
+% \begin{equation}
+%   \mathscr{NA}_{3}=\{\{1,2,3,4\},\{1,2,3\},\{1,3,4\},\{2,3,4\},\{1,2\},\{1,3\},\{2,3\},\{3,4\},\{1\},\{2\},\{3\},\{4\}\}\nonumber
+% \end{equation}
+% (Prashanth:@Chi there an obvious symmetry between 1 and 2 in this example. Can you use it to make it more compact ?)
+% the $u$ variables are 
+% \begin{align}
+%   &u_{1}=\frac{x_{1}x_{123}}{x_{12}x_{13}} \:, \quad  u_{2}=\frac{x_{2}x_{123}}{x_{12}x_{23}} \:,  \quad 
+%   u_{3}=\frac{x_{3}x_{134}x_{234}x_{123}}{x_{34}x_{13}x_{23}x_{1234}} \:, \quad 
+%   u_{4}=\frac{x_{4}}{x_{34}}\nonumber \\
+%   &u_{12}=\frac{x_{12}}{x_{123}} \:, \quad u_{13}=\frac{x_{13}x_{1234}}{x_{134}x_{123}} \:,\quad 
+%   u_{23}=\frac{x_{23}x_{1234}}{x_{123}x_{234}} \:, \quad u_{34}=\frac{x_{34}x_{1234}}{x_{134}x_{234}} \nonumber\\
+%   &u_{123}=\frac{x_{123}}{x_{1234}} \:, \quad u_{134}=\frac{x_{134}}{x_{1234}} \:, \quad 
+%   u_{234}=\frac{x_{234}}{x_{1234}}
+% \end{align}
+% The $u$ equations are
+% \begin{align*}
+%   &1-u_{1}=u_{2}u_{3}u_{23}^{2}u_{34}u_{234}^{2}\\
+%   &1-u_{2}=u_{1}u_{3}u_{13}^{2}u_{34}u_{134}^{2}\\
+%   &1-u_{3}= u_{1}u_{2}u_{4}u_{12}^{2}(1+u_{3}u_{13}u_{23}u_{34}u_{123}u_{134}u_{234})\\
+%   &1-u_{4}=u_{3}u_{13}u_{23}u_{123} \\
+%   &1-u_{12} =u_{3}u_{13}u_{23}u_{34}u_{134}u_{234}\\
+%   &1-u_{13} =u_{2}u_{4}u_{12}u_{23}u_{34}u_{234}^{2}\\
+%   &1-u_{23}= u_{1}u_{4}u_{12}u_{13}u_{34}u_{134}^{2}\\
+%   &1-u_{34}= u_{1}u_{2}u_{12}^{2}u_{13}u_{23}u_{123}^{2}\\
+%   &1-u_{123}=u_{4}u_{34}u_{134}u_{234}\\
+%   &1-u_{134}=u_{2}u_{12}u_{23}u_{123}u_{234}\\
+%   &1-u_{234}=u_{1}u_{12}u_{13}u_{123}u_{134}, 
+% \end{align*}
+
+\section{Discussions}
+
+In this paper we introduced a large class of integrals,  ${\cal I}_{\bf B}$, which can be regarded as a family of rigid stringy canonical forms%~\cite{Arkani-Hamed:2019mrd} 
+for generalized permutohedra ${\mathscr P}(\bf B)$, and we show that corresponding configuration spaces are always binary geometries.
+These rigid integrals satisfy the remarkable property that, at any ``massless'' pole, {\it i.e.} poles of the leading order $\Omega({\mathscr P}(\bf B) )$, the residue is given by a product of two such integrals, ${\cal I}_{{\bf B}_L} \times {\cal I}_{{\bf B}_R}$.
+Our results greatly extended the scope of binary geometries and associated integrals with such ``perfect'' factorization properties, which were originally thought to tie to the more special class of generalized associahedra for finite-type cluster algebras.
+For infinite families of cases as degenerations of associahedra and cyclohedra (which belong to both generalized permutohedra and generalized associahedra), we find additionally that the $u$ equations are ``perfect'' just like the case for cluster configuration spaces.
+Our preliminary investigations have opened up various new avenues to be explored, and we end with listing some open questions.
+
+\paragraph{Generalized permutohedra vs.
+generalized associahedra} Our results provide an infinite number of examples generalizing ordinary string integrals (and cluster string integrals of type $B_n$), where the configuration space is determined by {\it linear} factors, or equivalently hyperplane arrangement.
+In this sense, it is fair to say that we have only explored a very special corner in the world of binary configuration spaces and associated stringy integrals.
+Even for cluster cases, it is unknown if the cluster configuration space of type $C_n$ can be realized by hyperplane arrangement (see also \cite{Li:2018mnq}), and for type $ D_n$ and exceptional cases, the conjecture is that the spaces cannot be obtained this way~\cite{Arkani-Hamed:2019plo}; we expect that these cases do not belong to integrals with ``linear'' factors.
+It would be highly desirable to look for a wider class of binary geometries which naturally incorporate both generalized permutohedra and generalized associahedra.
+
+On the other hand, it would be interesting to study the configuration spaces for generalized permutohedra in a way similar to the cluster case.
+The $u$ equations for {\it e.g.} ${\mathscr P}_d$ are certainly worth further investigations, and one could ask if there might be any analog/generalization of cluster algebra behind it.
+Another question concerns going beyond positive part of the space since it is binary even in the complex case, and it would be nice to study complex space and connected components of the real space.
+For the cluster case, connected components are in bijection with sign patterns of the $u$ variables allowed by the so-called extended $u$ equations~\cite{Arkani-Hamed:2019plo}.
+It would be highly desirable to see if one could obtain all the extended $u$ equations for {\it e.g.} ${\mathscr P}_d$, which can help us understand these questions better.
+Relatedly, the number of connected components and other interesting properties of the space can be inferred by counting the number of points in the space for a finite field; since we are dealing with hyperplane arrangement, the point count $N(p)$ is always a polynomial.
+Just to illustrate the counting with some examples, since ${\mathscr P}_2={\mathscr B}_2$, the point count is $N(p)=(p-3)^2$, and if we plug in $p=-1$ we have $|N(-1)|=16$ connected components; we find for ${\mathscr P}_3$, $N(p)=(p-4)(p^2-10p+26)$, thus there are $185$ connected components, and for ${\mathscr P}_4$, $N(p)=p^4- 30 p^3+ 345 p^2- 1785 p+3485$ thus $5646$ connected components.
+
+Moreover, since we have found a variety of such geometries with perfect $u$ equations from degenerating ${\mathscr A}_n$ and ${\mathscr B}_n$, it'd be very interesting to explore more cases with perfect $u$ equations from degenerations of other types, {\it e.g.} ${\mathscr C_n}$ and ${\mathscr D_n}$.
+Along this direction, an intriguing possibility is to classify binary geometries with perfect $u$ equations from degenerating cluster cases; since any product of such geometries still has perfect $u$ equations, this amounts to find all elementary, non-factorizing geometries with perfect $u$ equations.
+More importantly,  what are the possible interpretations of these degenerations from cluster algebra; even for ${\mathscr A}_{n-3}$, what are the meaning of these degenerations of ${\cal M}_{0,n}$ and the string integrals?
+
+\paragraph{Generalized string integrals and applications} One of the most pressing questions is to study further these stringy integrals and their potential applications to physics.
+We would like to understand why these integrals factorize at finite $\alpha'$ just as cluster stringy integrals, though most of them are not related to cluster algebra.
+Recall that cluster stringy integrals of classical types are natural $\alpha'$-deformation of bi-adjoint $\phi^3$ amplitudes through one-loop~\cite{Arkani-Hamed:2019vag}, and in general the physical meaning of these integrals and their leading orders are unclear.
+A special class of generalized permutohedra, called Cayley polytopes, have natural interpretations as sum of certain tree-level $\phi^3$ diagrams~\cite{Gao:2017dek,He:2018pue}; for these cases, the stringy integrals provide a rigid $\alpha'$-deformation of these $\phi^3$ ``amplitudes''~\footnote{For other applications of generalized permutohedra to physics, see~\cite{early2017generalized,Early:2018zuw}.}.
+It would be interesting to see what role do generalize permutohedra play in the general story of formulating scattering amplitudes as differential forms~\cite{Arkani-Hamed:2017tmz, He:2018okq, Arkani-Hamed:2017mur, Arkani-Hamed:2019vag}.
+
+We have not touched various properties of these stringy integrals, such as recurrence relations, complex (and real) integrals with two different ``orderings'' and scattering (saddle-point) equations and pushforward, It would be interesting to understand these points better, especially for the ${\mathscr P}_d$ case, which is completely symmetric in the labels.
+The scattering equations read
+\[\frac{X_i}{x_i}=\sum_{I \ni i} \frac{c_I}{\sum_{j \in i} x_j}\,,
+\]
+which provide a one-to-one map from ${\bf x}\in \mathbb{R}_{\geq 0}^d$ to ${\mathscr P}_d$, and $\Omega({\mathscr P}_d)$ is given by the pushforward via summing over the solutions.
+By plugging in $p=1$ in the point count $N(p)$, one can obtain the number of solutions (saddle points), which also gives the dimension of the space of integral functions~\cite{Arkani-Hamed:2019mrd}.
+For example, for $d=2, 3, 4$, we have $4, 51, 2016$ solutions respectively.
+
+One class of examples which are particularly interesting are the Stokes polytopes and Accordiohedra~\cite{Banerjee:2018tun,Raman:2019utu} associated with planar $\phi^{p}$ amplitudes.
+A nice fact about Stokes polytopes~\cite{Chapoton, Raman:2019utu} is that any product of associahedra ${\mathscr A}_{i_1}\times \cdots \times {\mathscr A}_{i_k}$ is a Stokes polytope of dimension $n=i_1+\cdots+i_k$; more interestingly, degenerations of ${\mathscr A_3}$ with perfect $u$ equations correspond to $3d$ Stokes polytopes.
+Furthermore every Stokes polytope is a Minkowski sum of associahedra \cite{Baryshnikov} and thus it would be natural to consider them as these might provide nice class of physically relevant examples which also play a role in classifying binary geometries with perfect $u$ equations.
+
+\paragraph {Beyond linear factors}
+Throughout the paper we have considered stringy integrals with linear factors whose Newton polytopes are coordinate simplices.
+In fact, one can discover more polytopes which also have perfect $u$ equations, once we consider non-linear factors.
+One particularly simple class of examples we discover concern polytopes that are Minkowski sum of $n$ line intervals and $n-1$ triangles, with Newton polynomials:
 \bea \label{new}
-\prod_{i=1}^{n} (1+x_i ) \prod_{i=1}^{n-1} (1+x_i +x_i x_{i+1}) 
+\prod_{i=1}^{n} (1+x_i )^{-\alpha' c_i}  \prod_{i=1}^{n-1} (1+x_i +x_i x_{i+1})^{-\alpha' c_{i, i+1}}\,.
 \eea 
-This gives a family of simple $n$-dimensional polytopes with $3n-1$ facets  and Pell number $P_n$ (~recursively defined as $ P_n=2 P_{n-1} +P_{n-2}$ with $P_1=1,~ P_2=2$) of vertices which we shall call $X_n$.
-
-We can solve for $u$-variables for this family and we get :
+It turns out this gives a family of simple $n$-dimensional polytopes with $3n-1$ facets and the number of vertices is given by the Pell number $P_n$ (recursively defined as $ P_n=2 P_{n-1} +P_{n-2}$ with $P_1=1,~ P_2=2$).
+We refer to the polytope as $\mathscr{X}_n$.
+
+The big polyhedron is a simplex, and we find that the $u$ variables take a very simple form:
 \bea
-u_1 &=& \frac{p_n}{q_n}, ~u_2 = \frac{p_{n-1}q_n}{p_{n-1,n}},~u_3 = \frac{p_{n-2}q_{n-1}}{p_{n-2,n-1}}, \cdots,
+u_1 &=& \frac{p_n}{q_n}, ~u_2 = \frac{p_{n-1}q_n}{p_{n-1,n}},~u_3 = \frac{p_{n-2}q_{n-1}}{p_{n-2,n-1}}, \dots,
 u_{n-2} = \frac{p_1 q_2}{p_{12}}, ~u_{n-1} = \frac{p_{2}q_3}{p_{23}},~u_n = \frac{p_{3}q_{4}}{p_{34}}, \nonumber \\
-u_{n+1} &=& \frac{1}{q_1}, ~u_{n+2} = \frac{p_{12}}{q_{1}q_{2}},~u_{n+3} = \frac{q_{1}}{p_{23}}, \cdots,
+u_{n+1} &=& \frac{1}{q_1}, ~u_{n+2} = \frac{p_{12}}{q_{1}q_{2}},~u_{n+3} = \frac{q_{1}}{p_{23}}, \dots,
 u_{3n-1} = \frac{ q_{n-1}}{p_{n-1n}} 
 \eea
-where $p_i =x_i$, $q_i= 1+x_i$ and $p_{i~i+1}=1+x_i+ x_i x_{i+1}$.
-
-The $u$ equations obtained from these $u$ variables are of three types viz. $1-u$ being the product of two, three or four $u$'s  for any $n$.
-
-There are exactly 4 $u$'s which have $1-u$ is product of 2 u's:
+where we denote $p_i :=x_i$, $q_i := 1+x_i$ and $p_{i~i+1}:=1+x_i+ x_i x_{i+1}$.
+Remarkably, for any $n$, we have perfect $u$ equations which fall into three types viz.
+$1-u$ being the product of two, three or four $u$'s.
+The first type has 4 equations:
 \bea
@@
 \eea
-The facets corresponding to setting any of these $u \to 0$ is $X_{n-1}$.
-
-There are exactly $n-3$ $u$'s which have $1-u$ is product of 4 u's:
+with the corresponding facets being $\mathscr{X}_{n-1}$. The second type has $n-3$ equations
 \bea
-1-u_{n+4} =u_{n} u_{n+2}u_{n+4} u_{n+6} ~~and~~
-1-u_{n+6+ 2 i} =u_{n-3-i} u_{n+4+2 i} u_{n+5+2 i} u_{n+8+2 i}~ for~i=0,\cdots,(n-5) 
+1-u_{n+4} =u_{n} u_{n+2}u_{n+4} u_{n+6}, \quad 1-u_{n+6+2 i} =u_{n-3-i} u_{n+4+2 i} u_{n+5+2 i} u_{n+8+2 i}~ {\rm for}~i=0,\dots,n-5;
 \eea
-The facets corresponding to setting any of these $u \to 0$ is $A^{m}_1 \times X_{n-m-1}$.
-
-All the other $2n-2$ $u$'s correspond to $1-u$ is product of 3 u's and we do not yet have a complete classification of the facets.
-
-We can also replace the first the first term in the Newton polynomial \eqref{new} with $(1+x_1+ x_2)$ and we get an identical system of $u$-equations
-
+with the corresponding facets being $\mathscr{A}^{m}_1 \times \mathscr{X}_{n-m-1}$.
+The third type has $2n-2$ equations, but we do not yet have a complete classification of these facets.
+It would be nice to see if $\mathscr{X}_n$'s are equivalent to some degeneration of $\mathscr{P}_n$, or if they are genuinely new binary geometries with perfect $u$ equations.
+%We can also replace the first the first term in the Newton polynomial \eqref{new} with $(1+x_1+ x_2)$ and we get an identical system of $u$ equations
+%
+%\bea
+%u_1 &=& \frac{p_n}{q_n}, ~u_2 = \frac{p_{n-1}q_n}{p_{n-1,n}},~u_3 = \frac{p_{n-2}q_{n-1}}{p_{n-2,n-1}}, \cdots,
+%u_{n-3} = \frac{p_4 q_5}{p_{45}}, ~u_{n-2} = \frac{p_{1}}{q_{1}},~u_{n-1} = \frac{p_{2}q_{3}}{p_{23}},~u_{n} = \frac{p_{3}q_{4}}{p_{34}}, \nonumber \\
+%u_{n+1} &=& \frac{q_2}{p_{12}}, ~u_{n+2} = \frac{q_{1}}{p_{12}},~u_{n+3} = \frac{p_{23}}{q_{2}q_{3}}, \cdots,
+%u_{3n-1} = \frac{ p_{12}}{q_{1}q_{2}} 
+%\eea
+%where $p_i =x_i$, $q_i= 1+x_i$ and $p_{i~i+1}=1+x_i+ x_i x_{i+1}$ with $p_{12}= 1+x_1+x_2$.
+%
+%The $u$ equations obtained from these $u$ variables are of three types viz. $1-u$ being the product of two, three or four $u$'s  for any $n$.  
+%
+%There are exactly 4 $u$'s which have $1-u$ is product of 2 u's:
+%\bea
+%1-u_{1} =u_{3n-2} u_{3n-3},~
+%1-u_{n-2} =u_{n+1} u_{3n-1},~
+%1-u_{n+1} =u_{n-2} u_{n+2},~
+%1-u_{3n-1} = \begin{cases}
+%u_{2} u_{3} , n=3\\
+%u_{1} u_{4} , n=4\\
+%u_{1} u_{2} , n\geq 5
+%\end{cases} \nonumber 
+%\eea
+%The facets corresponding to setting any of these $u \to 0$ is $X_{n-1}$.
+%
+%There are exactly $n-3$ $u$'s which have $1-u$ is product of 4 u's:
+%\bea
+%1-u_{n+3} =u_{n} u_{n+2}u_{n+5} u_{3n-1} ~~and~~
+%1-u_{n+5+ 2 i} =u_{n-3-i} u_{n+3+2 i} u_{n+4+2 i} u_{n+7+2 i}~ for~i=0,\cdots,(n-5) \nonumber
+%\eea
+
+\paragraph{Stringy integrals at finite $\alpha'$}
+
+An important open question for stringy canonical form in general is to understand structures both at higher orders in the $\alpha'$-expansion and even at finite $\alpha'$. 
+The leading order of \eqref{stringycanonicalform} computes the canonical form of the corresponding polytope, which does not depend on the coefficients of the polynomials, but higher orders do, and it would be interesting to study $\alpha'$ expansion for stringy integrals for {\it e.g.} permutohedra.
+
+Moreover, having closed form expressions at finite $\alpha'$ is certainly desirable.
+Our preliminary study already provides some examples, and let us look at a toy example which was considered in~\cite{Arkani-Hamed:2019mrd}:
  \bea
-u_1 &=& \frac{p_n}{q_n}, ~u_2 = \frac{p_{n-1}q_n}{p_{n-1,n}},~u_3 = \frac{p_{n-2}q_{n-1}}{p_{n-2,n-1}}, \cdots,
-u_{n-3} = \frac{p_4 q_5}{p_{45}}, ~u_{n-2} = \frac{p_{1}}{q_{1}},~u_{n-1} = \frac{p_{2}q_{3}}{p_{23}},~u_{n} = \frac{p_{3}q_{4}}{p_{34}}, \nonumber \\
-u_{n+1} &=& \frac{q_2}{p_{12}}, ~u_{n+2} = \frac{q_{1}}{p_{12}},~u_{n+3} = \frac{p_{23}}{q_{2}q_{3}}, \cdots,
-u_{3n-1} = \frac{ p_{12}}{q_{1}q_{2}} 
+I(\alpha') &=& \int_{0}^{\infty} \int_{0}^{\infty} \frac{dx}{x} ~\frac{dy}{y} \left( \frac{1}{x} + \frac{1}{y}+ x y \right)^{-\alpha' } \nonumber 
 \eea 
-where $p_i =x_i$, $q_i= 1+x_i$ and $p_{i~i+1}=1+x_i+ x_i x_{i+1}$ with $p_{12}= 1+x_1+x_2$.
-
-The $u$ equations obtained from these $u$ variables are of three types viz. $1-u$ being the product of two, three or four $u$'s  for any $n$.
-
-There are exactly 4 $u$'s which have $1-u$ is product of 2 u's:
+We can use the symmetry in $x,~y$ to make a symmetric change of variables to $u=x+y$ and $v =x y$, and the integral can be easily evaluated as
  \bea
-1-u_{1} =u_{3n-2} u_{3n-3},~
-1-u_{n-2} =u_{n+1} u_{3n-1},~
-1-u_{n+1} =u_{n-2} u_{n+2},~
-1-u_{3n-1} = \begin{cases}
-u_{2} u_{3} , n=3\\
-u_{1} u_{4} , n=4\\
-u_{1} u_{2} , n\geq 5
-\end{cases} \nonumber 
+I(\alpha') &=& \int_{0}^{\infty} \int_{0}^{\frac{u^2}{4}} \frac{2 du ~ dv}{v \sqrt{u^2-4 v} }\left( \frac{u}{v} + v  \right)^{-\alpha'}= \frac{\Gamma{\left[\frac{\alpha'}{3}\right]^{3}}}{3 \Gamma{ \left[\alpha'\right]}} \nonumber
 \eea
-The facets corresponding to setting any of these $u \to 0$ is $X_{n-1}$.
-
-There are exactly $n-3$ $u$'s which have $1-u$ is product of 4 u's:
+%We can expand the result in $\alpha'$ to get 
+%{\scriptsize \bea
+%I(\alpha') = \frac{9}{(\alpha') ^2}-\frac{\pi ^2}{2}+\frac{8 \alpha'  \zeta
+%   (3)}{3}-\frac{11 \pi ^4 (\alpha') ^2}{1080}+(\alpha') ^3 \left(\frac{16
+%   \zeta (5)}{9}-\frac{4 \pi ^2 \zeta (3)}{27}\right)+(\alpha') ^4
+%   \left(\frac{32 \zeta (3)^2}{81}-\frac{613 \pi
+%   ^6}{1224720}\right)+O\left((\alpha') ^5\right)  \nonumber 
+%\eea}
+%The coefficient $9$ of the leading term is the area of the dual triangle corresponding to the one with vertices $\{(0,-1),~(-1,0),~(1,1) \}$ and sub leading term is zero as expected.
+%
+%The simplest example of such an integral whose result is known in any dimension is the Hypercube:
+%\bea
+%I(\alpha',~X_i,~c_i ) &=&  \int_{0}^{\infty} \cdots \int_{0}^{\infty} \prod_{i=1}^{n} ~dx_i ~x_i^{\alpha' X_i -1} \prod_{i=1}^{n} \left(  a_i ~x_i^{m_i} +b_i \right)^{-\alpha' c_i } \nonumber  \\
+%&=&\prod_{i=1}^n \frac{b_i^{\alpha'\left(c_i- \frac{X_i}{m_i}\right)}}{m_i~ a_i ^{\frac{\alpha' X_i}{m_i}}} B\left(\frac{\alpha' X_i}{m_i}, \alpha' \left(c_i- \frac{X_i}{m_i}\right) \right) \nonumber
+%\eea
+
+This is in fact a special class of a large class of integrals which all correspond to simplex case.
+By using the integral identity $\int_{{\mathbb R_{+}^{n}}} \prod_{i=1}^{n} \frac{d x_i }{x_i}~x_i^{a_i}  f\left(\sum_{i=1}^{n} x_i \right)   = \frac{\prod_{i=1}^n \Gamma{(a_i)}}{\Gamma{(\sum_{i=1}^n a_i)}} \int_{0}^{\infty} f(\beta) \beta^{\sum_{i=1}^{n} a_n -1} d\beta$, we can easily evaluate the following general integral for simplex:
 \bea
-1-u_{n+3} =u_{n} u_{n+2}u_{n+5} u_{3n-1} ~~and~~
-1-u_{n+5+ 2 i} =u_{n-3-i} u_{n+3+2 i} u_{n+4+2 i} u_{n+7+2 i}~ for~i=0,\cdots,(n-5) \nonumber
-\eea
-It would be nice to see if these also correspond to degenerations of some generalised permutahedra.
-
- \newpage
-\section{Discussions}
-There are several interesting open questions, like the question of  whether degenerations of other cluster types (in particular $C_n$ and $D_n$ can also give binary geometries with (perfect?) $u$-equations.\\\\
-\noindent
-Though many examples of degenerations of $A_n$ and $B_n$ were products of lower dimensional objects of the same type, there were examples where we got non-trivial degenerations which did not factor.
-We would like to completely classify these cases and this would settle the question of identifying all the ``atoms'' of binary geometries with perfect $u$-equations.
-One class of examples which is certainly of both mathematical and physical interest in this context are the Stokes polytopes (and more generally Accordiohedra).
-
-\newpage
+I(\alpha',~X_i,~c ) &=&  \int_{0}^{\infty} \cdots \int_{0}^{\infty} \prod_{i=1}^{n} ~dx_i ~x_i^{\alpha' X_i -1}  \left( b+\sum_{i=1}^n a_i x_i^{m_i} \right)^{-\alpha' c } \nonumber  \\
+&=& \frac{b^{\alpha' \left(\sum_{i=1}^n \frac{X_i}{m_i}-c \right) }}{(\prod_{i=1}^n m_i) (\prod_{i=1}^n a_i^{\alpha' X_i /m_i})} \int_{0}^{\infty} \cdots \int_{0}^{\infty} \prod_{i=1}^{n} ~dy_i ~y_i^{ \frac{\alpha' X_i}{m_i} -1}  \left( 1+\sum_{i=1}^n y_i \right)^{-\alpha' c } \nonumber  \\
+&=&\frac{b^{\alpha' \left(\sum_{i=1}^n \frac{X_i}{m_i}-c \right) }}{(\prod_{i=1}^n m_i) (\prod_{i=1}^n a_i^{\alpha' X_i /m_i})} B\left(\frac{ \alpha' X_1}{m_1},\dots,~\frac{ \alpha' X_n}{m_n}, ~ \alpha' \left(c- \sum_{i=1}^n \frac{X_i}{m_i} \right) \right) \nonumber \eea
+%More generally by interpreting the stringy integral \eqref{stringycanonicalform} as a Mellin transform it was shown in \cite{Mellin,Eulermellin} that the result of any stringy integral with linear factors i.e any generalized permutohedron is given by product of gamma functions of the facets of the Newton polytope times an entire function.
+
+We shall leave the evaluation of more stringy integrals and related topics to future work.
+
+\section*{ Acknowledgements}
+We are grateful to Nima Arkani-Hamed, Thomas Lam, Hugh Thomas for stimulating discussions and collaborations on related projects.
+P.R.
+would like to thank the generous hospitality of the Institute of Theoretical Physics, Chinese Academy of Sciences, Beijing during a visit when part of this work was done.
+The research of S.H., Z.L.
+and C.Z.
+is supported in part by NSF of China under Grant No.
+11947302 and 11935013.
 
 \appendix
-\section{Appendix: Nested Complex}\label{appendix: A}
-
-A subset ${\mathbf N}$ in the building set ${\mathbf B}$ is called a {\it nested set} if it satisfies the following conditions:
-\begin{compactenum}[\quad (1)]
-    \item For any $I,J \in {\mathbf N}$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
-    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
-    \item ${\mathbf N}$ contains all maximal elements of $B$.
-\end{compactenum}
-The {\it nested complex} ${\mathbf N}({\mathbf B})$ is defined as the poset of the set of all nested sets in ${\mathbf B}$ ordered by inclusion.\\
-
-\paragraph*{Facial structure} 
-Let us assume that the set ${\mathbf B}$ associated with a generalised permutahedron ${\mathscr P_n}^{y}$ is a building set on $[0,n]$.
-Then the poset of faces ${\mathscr P_n}^{y}$ ordered by reverse inclusion is isomorphic to the nested complex ${\mathbf N}({\mathbf B})$.
-
-The face $P_N$ of ${\mathscr P_n(y)}$ associated with the nested set $N \in \mathcal{N}(B)$ is given by:
-\bea
-P_N = \left \{ \right (t_1,\cdots,t_{n}) \in \mathbb{R}^{n} | \sum_{i \in I} t_i =y_{I}~{\rm for}~I \in N; ~ \sum_{i \in J}~t_i \geq y_J,~ {\rm for} ~J \in B  )\}
-\eea
-In particular the dimension of the face $P_N$ equals $n+1-|N|$.\\ 
-Another description of the faces is the following:
-
-For each decomposition $[0,n]=  \sqcup_{I \subset {\mathbf N} } S_I $ where $S_I$ are non-empty, the face $P_N$ of ${\mathscr P_N}^{y}(y_I)$ associated with the nested set ${\mathbf N} \in {\mathbf N}({\mathbf B})$ is:
-\bea
-P_N = \sum_{{J \subset {\mathbf B}}\atop{J \cap S_I \neq \emptyset}} y_{J} \Delta_{J \cap S_I}
-\eea
-\subsubsection{Degenerations of ${\mathscr P_n}$ which lead to  products}
-
-In this section we provide an answer to the question of which degenerations of $\mathscr{P_n}$ give the most general products of such geometries.
-We begin by stating the following results about Nestohedra.
-
-The maximal set of a building set $B_{max}$ is the set of all inclusion maximal elements of the building set $B$. A building set $B$ is connected if $B_{max}$ has a single element.
-
-{\bf Theorem:} If $B_1, B_2,\cdots B_n$ are connected subsets of a building set $B$ then the corresponding nestohedron ${\mathscr N_B}$ is isomorphic to the product of the nestohedra ${\mathscr N}_{ B_1} \times{\mathscr N}_{ B_2} \cdots \times {\mathscr N}_{B_n}$.
-
-We can use the above result to construct a degeneration of  ${\mathscr P_n}$ which are the most general products i.e., $\prod_{p_i} X_{p_i}$ such that $\sum^{k}_{i=1} p_{i} = n$ and $X = {\mathscr A} ,{\mathscr B}, {\mathscr P }$ by dividing the $(n+1)$ singlets into $k$ parts $\{0,\cdots,p_1\}, \{p_1,\cdots,p_1+p_2\},\cdots \{\sum^{k-1}_{i=1}p_{i},\cdots,\sum^{k}_{i=1}p_{i}= n\}$ and constructing the corresponding $X_{p_i}$'s which we denote by $X_{p_i}\left(\sum^{(i-1)}_{j=1}p_{j},\cdots,\sum^{i}_{j=1}p_{j}\right).$
-
-Let us consider the $P_4$ example for which the allowed possibilities are : $A_1^{4}$, $A_1^2 \times A_2$, $A_1 \times A_3$, $A^{2}_2$, $A_1^2 \times B_2$, $A_1 \times B_3$,$A_1 \times P_3$,$ A_2\times B_2$ and $B^{2}_2$.
-
-For $A_1^{4}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} \}$ where $\{0,01\} , \{1,12\},\{2,23\},\{3,34\}$ generate the 4 $A_1$'s which we denote as $A_1(0,1) \times A_1(1,2) \times A_1(2,3) \times A_1(3,4) $.
-
-For $A_1^{2} \times A_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{234} \}$ generated by $A_1(0,1)\times A_1(1,2) \times A_2(2,3,4)$'s.
-
-For  $A_1 \times A_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{123},{234},{1234} \}$ generated by  $A_1(0,1)\times A_3(1,2,3,4)$.
-
-For  $A_2^{2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} ,{012},{234}\}$ generated by $A_2(0,1,2)\times A_2(2,3,4)$
-
-For $A_1^{2} \times B_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{24},{234} \}$ generated by $A_1(0,1)\times A_1(1,2) \times B_2(2,3,4)$'s.
-
-For $A_1 \times B_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{14},{123},{234},{134},{124},{1234} \}$ generated by  $A_1(0,1)\times B_3(1,2,3,4)$.
-
-For $A_1 \times P_3$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{14},{13},{24},{123},{234},{134},{124},{1234} \}$ generated by  $A_1(0,1)\times P_3(1,2,3,4)$.
-
-For $A_2 \times B_2$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{24},{012},{234}\}$ generated by $A_2(0,1,2)\times B_2(2,3,4)$
-
-For $B_2^{2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{02},{23},{34},{24} ,{012},{234}\}$ generated by $B_2(0,1,2)\times B_2(2,3,4)$
+
+\section{Appendix: Degenerations of ${\mathscr P_n}$ which lead to products}\label{appendix:A}
+In this section we consider degenerations of $\mathscr{P_n}$ give the most general products.
+
+The maximal set of a building set ${\mathbf B_{max}}$ is the set of all inclusion maximal elements of the building set ${\mathbf B}$.
+A building set ${\mathbf B}$ is connected if ${\mathbf B_{max}}$ has a single element\cite{Postnikov:2006}.
+
+\vspace{1ex}
+
+\noindent {\bf Theorem:} If ${\mathbf B_1},{\mathbf B_2},\dots {\mathbf B_n}$ are connected subsets of a building set ${\mathbf B}$ then the corresponding nestohedron ${\mathscr N_{{\mathbf B}}}$ is isomorphic to the product of the nestohedra ${\mathscr N}_{ {\mathbf B_1}} \times{\mathscr N}_{ {\mathbf B_2}} \cdots \times {\mathscr N}_{{\mathbf B_n}}$\cite{Postnikov:2006}.
+
+\vspace{1ex}
+
+The result follows as for any pair of connected building sets ${\mathbf B_{i}},{\mathbf B_{j}}$ either  ${\mathbf B_{i}} \cup {\mathbf B_{j}} = \varnothing $ in which case ${\cal I}_{{\mathbf B_i}\cup {\mathbf B_j}} = {\cal I}_{\mathbf B_i} \times {\cal I}_{\mathbf B_j}$ or ${\mathbf B_{i}} \cup {\mathbf B_{j}} = \{k\}$ in this we can rescale the $x_l \rightarrow x_k x_l$ for $l \in {\mathbf B_{j}} $ to decouple the integrals.
+Thus we always get ${\cal I}_{\mathbf B}={\cal I}_{\mathbf B_1}\times{\cal I}_{\mathbf B_2}\cdots \times{\cal I}_{\mathbf B_n}$.
+\\
+Using the above result we construct a degeneration of  ${\mathscr P_n}$ which are the most general products i.e., $\prod_{p_i} X_{p_i}$ such that $\sum^{k}_{i=1} p_{i} = n$ by dividing the $(n+1)$ singlets into $k$ parts
+\[
+[0,p_1],\quad [p_1,p_1+p_2],\quad \dots ,\quad [\sum^{k-1}_{i=1}p_{i},\sum^{k}_{i=1}p_{i}= n]
+\]
+and using them to construct the building sets $\mathbf B_{p_i}$ of $X_{p_i}\left[\sum^{(i-1)}_{j=1}p_{j},\sum^{i}_{j=1}p_{j}\right].$
+
+{\bf Example:} degenerations of ${\mathscr P_4}$ into ${\mathscr A_1^{4}}$, ${\mathscr A_1^2} \times{\mathscr A_2}$, ${\mathscr A_1} \times {\mathscr A_3}$, ${\mathscr A^{2}_2}$, ${\mathscr A_1^2} \times {\mathscr B_2}$, ${\mathscr A_1} \times {\mathscr B_3}$,${\mathscr A_1} \times {\mathscr P_3}$,$ {\mathscr A_2}\times {\mathscr B_2}$ and ${\mathscr B^{2}_2}$.
+
+For ${\mathscr A_1^{4}}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} \}$ where $\{0,01\} , \{1,12\},\{2,23\},\{3,34\}$ generate the 4 ${\mathscr A_1}$'s which we denote as ${\mathscr A_1}(0,1) \times {\mathscr A_1}(1,2) \times {\mathscr A_1}(2,3) \times {\mathscr A_1}(3,4) $.
+
+For ${\mathscr A_1}^{2} \times {\mathscr A_2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{234} \}$ generated by ${\mathscr A_1}(0,1)\times {\mathscr A_1}(1,2) \times {\mathscr A_2}(2,3,4)$'s.
+
+For  ${\mathscr A_1} \times {\mathscr A_3}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{123},{234},{1234} \}$ generated by  ${\mathscr A_1}(0,1)\times {\mathscr A_3}(1,2,3,4)$.
+
+For  ${\mathscr A_2^{2}}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34} ,{012},{234}\}$ generated by ${\mathscr A_2}(0,1,2)\times {\mathscr A_2}(2,3,4)$
+
+For ${\mathscr A_1}^{2} \times {\mathscr B_2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{24},{234} \}$ generated by ${\mathscr A_1}(0,1)\times {\mathscr A_1}(1,2) \times {\mathscr B_2}(2,3,4)$'s.
+
+For ${\mathscr A_1} \times {\mathscr B_3}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{14},{123},{234},{134},{124},{1234} \}$ generated by  ${\mathscr A_1}(0,1)\times {\mathscr B_3}(1,2,3,4)$.
+
+For ${\mathscr A_1} \times {\mathscr P_3}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{14},{13},{24},{123},{234},{134},{124},{1234} \}$ generated by  ${\mathscr A_1}(0,1)\times {\mathscr P_3}(1,2,3,4)$.
+
+For ${\mathscr A_2} \times {\mathscr B_2}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{23},{34},{24},{012},{234}\}$ generated by ${\mathscr A_2}(0,1,2)\times {\mathscr B_2}(2,3,4)$
+
+For ${\mathscr B_2^{2}}$ the building set is $ \{ {0},{1},{2},{3},{4},{01},{12},{02},{23},{34},{24} ,{012},{234}\}$ generated by ${\mathscr B_2}(0,1,2)\times {\mathscr B_2}(2,3,4)$.
 
@@
 
-\section*{4d permutahedron}
-The $u$ variables for the 4d permutahedron are:
-{\tiny
+\section{Appendix: Some $u$ equations of ${\mathscr P_n}$}\label{appendix:B}
+
+Some of the $u$ equations for the $n$-dimensional permutohedron are:\\
+For $|I|=n$ or $n-1$ we have  
+\[
+1-u_{I} = \prod_{J\not\supset I} u_{J}^{|J|-|I\cap J|}
+\]
+%For $|I| =n-1$ and $s_K = \begin{cases}  1,~ if K \not\subset I & \\ 2, ~if K \subset I\end{cases}$
+% we have 
+% \bea1-u_{I} &=& \prod_ {S - I \subset J } u_{J} \prod_ {K \cap I \ne \Phi } (u_{\bar{K}})^{s_K}
+% \eea
+and for $|I| =n-2$,
+\[
+1-u_{I}= \left(1+\prod_{J\supset I}u_J\right)\prod_{J\not\supset I} u_{J}^{|J|-|I\cap J|}
+\]
+The other $u$ equations are not two or three term equations,
+%and seem to be polynomials of order $n-|I|-1$ in the corresponding $u$'s. 
+and in general it has the form 
+\[
+1-u_I=(1+h_{I,n}(u))\prod_{J\not\supset I} u_{J}^{|J|-|I\cap J|},
+\]
+where $h_{I,n}(u)$ is conjectured to be a polynomial of $\{u_J\,|\, J\supset I\}$ such that $h_{I,n}(u)|_{u_I=0}=0$.
+
+Let us write down the ${\mathscr P_4}$ example:
+\[
+u_0= \frac{x_{0} x_{012} x_{013} x_{014} x_{023} x_{024} x_{034} x_{01234}}{x_{01} x_{02} x_{03} x_{04} x_{0123} x_{0124} x_{0134} x_{0234}},
+u_{01} =  \frac{x_{01} x_{0123} x_{0124} x_{0134}}{x_{012} x_{013} x_{014} x_{01234}},
+u_{012} = \frac{x_{012} x_{01234}}{x_{0123} x_{0124}},
+u_{0123} = \frac{x_{0123}}{x_{01234}}
+\]
+The $u$ equations are 
 \begin{align*}
-u_1&= \frac{x (w+x+1) (x+y+1) (w+x+y) (x+z+1) (w+x+z)
-   (x+y+z) (w+x+y+z+1)}{(x+1) (w+x) (x+y) (w+x+y+1) (x+z) (w+x+z+1) (x+y+z+1)
-   (w+x+y+z)},\nonumber \\  u_2 &= \frac{y (w+y+1) (x+y+1) (w+x+y) (y+z+1) (w+y+z) (x+y+z)
-   (w+x+y+z+1)}{(y+1) (w+y) (x+y) (w+x+y+1) (y+z) (w+y+z+1) (x+y+z+1)
-   (w+x+y+z)} \nonumber \\  u_3 &= \frac{z (w+z+1) (x+z+1) (w+x+z) (y+z+1) (w+y+z) (x+y+z)
-   (w+x+y+z+1)}{(z+1) (w+z) (x+z) (w+x+z+1) (y+z) (w+y+z+1) (x+y+z+1)
-   (w+x+y+z)},\nonumber \\ u_4 &= \frac{w (w+x+1) (w+y+1) (w+x+y) (w+z+1) (w+x+z) (w+y+z) (w+x+y+z+1)}{(w+1)
-   (w+x) (w+y) (w+x+y+1) (w+z) (w+x+z+1) (w+y+z+1) (w+x+y+z)},\nonumber \\
-   u_{12} &=  \frac{(x+y) (w+x+y+1) (x+y+z+1) (w+x+y+z)}{(x+y+1) (w+x+y)
-   (x+y+z) (w+x+y+z+1)},~u_{13} = \frac{(x+z) (w+x+z+1) (x+y+z+1) (w+x+y+z)}{(x+z+1) (w+x+z)
-   (x+y+z) (w+x+y+z+1)},\nonumber \\ ~ u_{14} &= \frac{(w+x)(w+x+y+1) (w+x+z+1) (w+x+y+z)}{(w+x+1) (w+x+y) (w+x+z) (w+x+y+z+1)}, u_{24} = \frac{(w+y) (w+x+y+1) (w+y+z+1) (w+x+y+z)}{(w+y+1) (w+x+y) (w+y+z) (w+x+y+z+1)},\nonumber \\ ~u_{23} &=
-   \frac{(y+z) (w+y+z+1) (x+y+z+1) (w+x+y+z)}{(y+z+1) (w+y+z) (x+y+z)(w+x+y+z+1)},~ u_{34} = \frac{(w+z) (w+x+z+1) (w+y+z+1) (w+x+y+z)}{(w+z+1) (w+x+z) (w+y+z) (w+x+y+z+1)}, \nonumber \\  
-  u_{123} &= \frac{(x+y+z) (w+x+y+z+1)}{(x+y+z+1)(w+x+y+z)},~u_{134}= \frac{(w+x+z) (w+x+y+z+1)}{(w+x+z+1)(w+x+y+z)},~ u_{124}= \frac{(w+x+y) (w+x+y+z+1)}{(w+x+y+1) (w+x+y+z)},~ u_{234} = \frac{(w+y+z) (w+x+y+z+1)}{(w+y+z+1) (w+x+y+z)},\nonumber \\
-    u_{1234} &= \frac{w+x+y+z}{w+x+y+z+1},\nonumber \\ u'_1&= \frac{w+y+z+1}{w+x+y+z+1},~~u'_2= \frac{w+x+z+1}{w+x+y+z+1}, u'_3=  \frac{w+x+y+1}{w+x+y+z+1},u'_4 = \frac{x+y+z+1}{w+x+y+z+1}, \nonumber \\  u'_{12} &= \frac{(w+z+1) (w+x+y+z+1)}{(w+x+z+1) (w+y+z+1)}, u'_{13} = \frac{(w+y+1) (w+x+y+z+1)}{(w+x+y+1) (w+y+z+1)},\nonumber \\  u'_{14} &= \frac{(y+z+1) (w+x+y+z+1)}{(w+y+z+1) (x+y+z+1)},u'_{23} = \frac{(w+x+1) (w+x+y+z+1)}{(w+x+y+1) (w+x+z+1)}, \nonumber \\ u'_{24}&= \frac{(x+z+1) (w+x+y+z+1)}{(w+x+z+1)(x+y+z+1)}, u'_{34}=  \frac{(x+y+1) (w+x+y+z+1)}{(w+x+y+1) (x+y+z+1)},\nonumber \\
-u'_{123} &=  \frac{(w+1) (w+x+y+1) (w+x+z+1) (w+y+z+1)}{(w+x+1) (w+y+1) (w+z+1) (w+x+y+z+1)},~u'_{124}= \frac{(z+1) (w+x+z+1) (w+y+z+1) (x+y+z+1)}{(w+z+1) (x+z+1) (y+z+1) (w+x+y+z+1)},\nonumber \\  u'_{134}&= \frac{(y+1) (w+x+y+1) (w+y+z+1) (x+y+z+1)}{(w+y+1)(x+y+1) (y+z+1) (w+x+y+z+1)},u'_{234} = \frac{(x+1) (w+x+y+1) (w+x+z+1) (x+y+z+1)}{(w+x+1) (x+y+1) (x+z+1) (w+x+y+z+1)},\nonumber \\  u'_{1234} &= \frac{(w+x+1) (w+y+1)(x+y+1) (w+z+1) (x+z+1) (y+z+1) (w+x+y+z+1)}{(w+1) (x+1) (y+1) (w+x+y+1) (z+1) (w+x+z+1) (w+y+z+1) (x+y+z+1)} \nonumber
+   &1-u_0=u_{1} u_{2} u_{3} u_{4} u_{12}^2 u_{13}^2 u_{14}^2 u_{23}^2 u_{24}^2 u_{34}^2 u_{123}^3 u_{124}^3 u_{134}^3 u_{234}^3u_{1234}^4 
+    (1+h_{\{0\},4}),\\
+   &1-u_{01}=u_{2} u_{3} u_{4} u_{02} u_{03} u_{04} u_{12} u_{13} u_{14} u_{23}^2 u_{24}^2 u_{34}^2 u_{023}^2 u_{024}^2 u_{034}^2 u_{123}^2 u_{124}^2 u_{134}^2 u_{234}^3 u_{0234}^3 u_{1234}^3(1+h_{\{0,1\},4}),\\
+   &1-u_{012}=u_{3} u_{4} u_{03} u_{04} u_{13} u_{14} u_{23} u_{24} u_{34}^2 u_{013} u_{014} u_{023} u_{024} u_{034}^2 u_{123} u_{124} u_{134}^2 u_{234}^2 u_{0134}^2 u_{0234}^2 u_{1234}^2,\\ 
+   &1-u_{0123}=u_{4} u_{04} u_{14} u_{24} u_{34} u_{014} u_{024} u_{034} u_{124} u_{134} u_{234} u_{0124} u_{0134} u_{0234} u_{1234}
 \end{align*}
-}
-\newpage
-\vspace*{-25pt}
-The $u$ equations are 
-{\tiny
-{\begin{align*}
-1-u_1&=u_2 u_3 u_4 u_{2,3}^2 u_{24}^2 u_{34}^2 u_{234}^4
-   \left(u'\right)_1^8 \left(u'\right)_{12}^4 \left(u'\right)_{13}^4
-   \left(u'\right)_{14}^4 \left(u'\right)_{123}^2
-   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2 u'_{1234}+ 6~
- \textcolor{red}{  u_1^2} u_2 u_3 u_4 u_{12}^2 u_{13}^2 u_{14}^2 u_{23}^2 u_{24}^2
-   u_{34}^2 u_{123}^2 u_{124}^2 u_{134}^2 u_{234}^3 u_{1234}
-   u'_2 u'_3 u'_4 \left(u'\right)_1^4  \nonumber \\ &\left(u'\right)_{12}^3
-   \left(u'\right)_{13}^3 \left(u'\right)_{14}^3
-   \left(u'\right)_{23}^2 \left(u'\right)_{24}^2
-   \left(u'\right)_{34}^2 \left(u'\right)_{123}^2
-   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2
-   \left(u'\right)_{234}^2 u'_{1234}+~2 ~\textcolor{red}{u_1} u_2 u_3 u_4 u_{12}
-   u_{13} u_{14} u_{23}^2 u_{24}^2 u_{34}^2 u_{123} u_{124}
-   u_{134} u_{234}^3 \left(u'\right)_1^4 \left(u'\right)_{12}^3
-   \left(u'\right)_{13}^3 \nonumber \\ & \left(u'\right)_{14}^3 u'_{23} u'_{24}
-   u'_{34} \left(u'\right)_{123}^2 \left(u'\right)_{124}^2
-   \left(u'\right)_{134}^2 u'_{234} \left(u_{234}
-   \left(1-u_{1234}\right) u_{1234} u'_1+u'_2 u'_3
-   \left(1-u'_{23}\right)+u'_2 u'_4 \left(1-u'_{24}\right)+u'_3 u'_4
-   \left(1-u'_{34}\right)+\left(u'\right)_1^2\right) u'_{1234} ,\nonumber \\
-   1-u_2&=u_1 u_3 u_4 u_{13}^2 u_{14}^2 u_{34}^2 u_{134}^4
-   \left(u'\right)_2^8 \left(u'\right)_{12}^4 \left(u'\right)_{23}^4
-   \left(u'\right)_{24}^4 \left(u'\right)_{123}^2
-   \left(u'\right)_{124}^2 \left(u'\right)_{234}^2 u'_{1234}+~6
-   u_1 \textcolor{red}{u_2^2} u_3 u_4 u_{1,2}^2 u_{13}^2 u_{14}^2 u_{23}^2 u_{24}^2
-   u_{34}^2 u_{123}^2 u_{124}^2 u_{134}^3 u_{234}^2 u_{1234}
-   u'_1 u'_3 u'_4 \left(u'\right)_2^4 \nonumber \\ &\left(u'\right)_{12}^3
-   \left(u'\right)_{13}^2 \left(u'\right)_{14}^2
-   \left(u'\right)_{23}^3 \left(u'\right)_{24}^3
-   \left(u'\right)_{34}^2 \left(u'\right)_{123}^2
-   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2
-   \left(u'\right)_{234}^2 u'_{1234}+~2~ u_1 \textcolor{red}{u_2} u_3 u_4 u_{12}
-   u_{13}^2 u_{14}^2 u_{23} u_{24} u_{34}^2 u_{123} u_{124}
-   u_{134}^3 u_{234} \left(u'\right)_2^4 \left(u'\right)_{12}^3
-   u'_{13} u'_{14} \nonumber \\ & \left(u'\right)_{23}^3 \left(u'\right)_{24}^3
-   u'_{34} \left(u'\right)_{123}^2 \left(u'\right)_{124}^2
-   u'_{134} \left(u'\right)_{234}^2 \left(u_{134}
-   \left(1-u_{1234}\right) u_{1234} u'_2+u'_1 u'_3
-   \left(1-u'_{13}\right)+u'_1 u'_4 \left(1-u'_{14}\right)+u'_3 u'_4
-   \left(1-u'_{34}\right)+\left(u'\right)_2^2\right) u'_{1234} ,\nonumber \\
-   1-u_3&=u_1 u_2 u_4 u_{12}^2 u_{14}^2 u_{24}^2 u_{124}^4
-   \left(u'\right)_3^8 \left(u'\right)_{13}^4 \left(u'\right)_{23}^4
-   \left(u'\right)_{34}^4 \left(u'\right)_{123}^2
-   \left(u'\right)_{134}^2 \left(u'\right)_{234}^2 u'_{1234}+~6
-   u_1 u_2 \textcolor{red}{u_3^2} u_4 u_{12}^2 u_{13}^2 u_{14}^2 u_{23}^2 u_{24}^2
-   u_{34}^2 u_{123}^2 u_{124}^3 u_{134}^2 u_{234}^2 u_{1234}
-   u'_1 u'_2 u'_4 \left(u'\right)_3^4 \nonumber \\ & \left(u'\right)_{12}^2
-   \left(u'\right)_{13}^3 \left(u'\right)_{14}^2
-   \left(u'\right)_{23}^3 \left(u'\right)_{24}^2
-   \left(u'\right)_{34}^3 \left(u'\right)_{123}^2
-   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2
-   \left(u'\right)_{234}^2 u'_{1234} +~2 ~u_1 u_2 \textcolor{red}{u_3} u_4 u_{1,2}^2
-   u_{13} u_{14}^2 u_{23} u_{24}^2 u_{34} u_{123} u_{124}^3
-   u_{134} u_{234} \left(u'\right)_3^4 u'_{12}
-   \left(u'\right)_{13}^3 u'_{14} \nonumber \\ &\left(u'\right)_{23}^3 u'_{24}
-   \left(u'\right)_{34}^3 \left(u'\right)_{123}^2 u'_{124}
-   \left(u'\right)_{134}^2 \left(u'\right)_{234}^2 \left(u_{124}
-   \left(1-u_{1234}\right) u_{1234} u'_3+u'_1 u'_2
-   \left(1-u'_{12}\right)+u'_1 u'_4 \left(1-u'_{14}\right)+u'_2 u'_4
-   \left(1-u'_{24}\right)+\left(u'\right)_3^2\right) u'_{1234} ,\nonumber \\
-   1-u_4 &= u_1 u_2 u_3 u_{12}^2 u_{13}^2 u_{23}^2 u_{123}^4
-   \left(u'\right)_4^8 \left(u'\right)_{14}^4 \left(u'\right)_{24}^4
-   \left(u'\right)_{34}^4 \left(u'\right)_{124}^2
-   \left(u'\right)_{134}^2 \left(u'\right)_{234}^2 u'_{1234}+~6
-   u_1 u_2 u_3 \textcolor{red}{u_4^2} u_{12}^2 u_{13}^2 u_{14}^2 u_{23}^2 u_{24}^2
-   u_{34}^2 u_{123}^3 u_{124}^2 u_{134}^2 u_{234}^2 u_{1234}
-   u'_1 u'_2 u'_3 \left(u'\right)_4^4 \nonumber\\ &\left(u'\right)_{12}^2
-   \left(u'\right)_{13}^2 \left(u'\right)_{14}^3
-   \left(u'\right)_{23}^2 \left(u'\right)_{24}^3
-   \left(u'\right)_{34}^3 \left(u'\right)_{123}^2
-   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2
-   \left(u'\right)_{234}^2 u'_{1234}+~2 u_1 u_2 u_3 \textcolor{red}{u_4} u_{12}^2
-   u_{13}^2 u_{14} u_{23}^2 u_{24} u_{34} u_{123}^3 u_{124}
-   u_{134} u_{234} \left(u'\right)_4^4 u'_{12} u'_{13}
-   \left(u'\right)_{14}^3 \nonumber\\ &u'_{23} \left(u'\right)_{24}^3
-   \left(u'\right)_{34}^3 u'_{123} \left(u'\right)_{124}^2
-   \left(u'\right)_{134}^2 \left(u'\right)_{234}^2 \left(u_{123}
-   \left(1-u_{1234}\right) u_{1234} u'_4+u'_1 u'_2
-   \left(1-u'_{12}\right)+u'_1 u'_3 \left(1-u'_{13}\right)+u'_2 u'_3
-   \left(1-u'_{23}\right)+\left(u'\right)_4^2\right) u'_{1234},\nonumber \\
-    1-u_{12}&= u_3 u_4
-   u_{13} u_{14} u_{23} u_{24} u_{34}^2 u_{134}^2 u_{234}^2 \left(u'\right)_1^3
-   \left(u'\right)_2^3 \left(u'\right)_{12}^3 \left(u'\right)_{13}^2
-   \left(u'\right)_{14}^2 \left( u'\right)_{23}^2 \left(u'\right)_{24}^2 \left(1+u_{12}
-   u_{123} u_{124} u_{1234} u'_3 u'_4 u'_{34}\right) \left(u'\right)_{123}^2
-   \left(u'\right)_{124}^2 u'_{134} u'_{234} u'_{1234},\nonumber \\
-     1-u_{13}&=u_2 u_4 u_{12}
-   u_{14} u_{23} u_{24}^2 u_{34} u_{124}^2 u_{234}^2 \left(u'\right)_1^3
-   \left(u'\right)_3^3 \left(u'\right)_{12}^2 \left(u'\right)_{13}^3
-   \left(u'\right)_{14}^2 \left(u'\right)_{23}^2 \left(1+ u_{13} u_{123} u_{134} u_{1234}
-   u'_2 u'_4 u'_{24}\right) \left(u'\right)_{34}^2 \left(u'\right)_{123}^2 u'_{124}
-   \left(u'\right)_{134}^2 u'_{234} u'_{1234},\nonumber \\ 
-   1-u_{14}&= u_2 u_3 u_{12} u_{13} u_{23}^2 u_{24} u_{34} u_{123}^2 u_{234}^2
-   \left(u'\right)_1^3 \left(u'\right)_4^3 \left(u'\right)_{12}^2 \left(u'\right)_{13}^2
-   \left(u'\right)_{14}^3 \left(1+ u_{14} u_{124} u_{134} u_{1234} u'_2 u'_3
-   u'_{23}\right) \left(u'\right)_{24}^2 \left(u'\right)_{34}^2 u'_{123}
-   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2 u'_{234} u'_{1234}, \nonumber \\ 
-    1-u_{34}&= u_1 u_2 u_{12}^2 u_{13}
-   u_{14} u_{23} u_{24} u_{123}^2 u_{124}^2 \left(u'\right)_3^3 \left(u'\right)_4^3
-   \left(1+u_{34} u_{134} u_{234} u_{1234} u'_1 u'_2 u'_{12}\right)
-   \left(u'\right)_{13}^2 \left(u'\right)_{14}^2 \left(u'\right)_{23}^2
-   \left(u'\right)_{24}^2 \left(u'\right)_{34}^3 u'_{123} u'_{124}
-   \left(u'\right)_{134}^2 \left(u'\right)_{234}^2 u'_{1234}, \nonumber \\ 
-   1-u_{24}&=u_1 u_3 u_{12} u_{13}^2 u_{14}
-   u_{23} u_{34} u_{123}^2 u_{134}^2 \left(u'\right)_2^3 \left(u'\right)_4^3
-   \left(u'\right)_{12}^2 \left(1+ u_{24} u_{124} u_{234} u_{1234} u'_1 u'_3
-   u'_{13}\right) \left(u'\right)_{14}^2 \left(u'\right)_{23}^2 \left(u'\right)_{24}^3
-   \left(u'\right)_{34}^2 u'_{123} \left(u'\right)_{124}^2 u'_{134}
-   \left(u'\right)_{234}^2 u'_{1234},\nonumber \\
-    1-u_{23}&=u_1 u_4 u_{12} u_{13} u_{14}^2 u_{24}
-   u_{34} u_{124}^2 u_{134}^2 \left(u'\right)_2^3 \left(u'\right)_3^3
-   \left(u'\right)_{12}^2 \left(u'\right)_{13}^2 \left(1+u_{23} u_{123} u_{234} u_{1234}
-   u'_1 u'_4 u'_{14}\right) \left(u'\right)_{23}^3 \left(u'\right)_{24}^2
-   \left(u'\right)_{34}^2 \left(u'\right)_{123}^2 u'_{124} u'_{134}
-   \left(u'\right)_{234}^2 u'_{1234},\nonumber \\ 
-   1-u_{124}&=u_3 u_{13} u_{23} u_{34} u_{123} u_{134}
-   u_{234} \left(u'\right)_1^2 \left(u'\right)_2^2 \left(u'\right)_4^2
-   \left(u'\right)_{12}^2 u'_{13} \left(u'\right)_{14}^2 u'_{23} \left(u'\right)_{24}^2
-   u'_{34} u'_{123} \left(u'\right)_{124}^2 u'_{134} u'_{234} u'_{1234},\nonumber \\ 
-   1-u_{123}&=u_4 u_{14}
-   u_{24} u_{34} u_{124} u_{134} u_{234} \left(u'\right)_1^2 \left(u'\right)_2^2
-   \left(u'\right)_3^2 \left(u'\right)_{12}^2 \left(u'\right)_{13}^2 u'_{14}
-   \left(u'\right)_{23}^2 u'_{24} u'_{34} \left(u'\right)_{123}^2 u'_{124} u'_{134}
-   u'_{234} u'_{1234},\nonumber \\ 
-   1-u_{134}&=u_2 u_{12} u_{23} u_{24} u_{123} u_{124} u_{234}
-   \left(u'\right)_1^2 \left(u'\right)_3^2 \left(u'\right)_4^2 u'_{12}
-   \left(u'\right)_{13}^2 \left(u'\right)_{14}^2 u'_{23} u'_{24} \left(u'\right)_{34}^2
-   u'_{123} u'_{124} \left(u'\right)_{134}^2 u'_{234} u'_{1234},\nonumber \\ 
-   1-u_{234}&=u_1 u_{12} u_{13} u_{14} u_{123} u_{124} u_{134}
-   \left(u'\right)_2^2 \left(u'\right)_3^2 \left(u'\right)_4^2 u'_{12} u'_{13} u'_{14}
-   \left(u'\right)_{23}^2 \left(u'\right)_{24}^2 \left(u'\right)_{34}^2 u'_{123} u'_{124}
-   u'_{134} \left(u'\right)_{234}^2 u'_{1234},\nonumber \\ 
-   1-u_{1234}&=u'_1
-   u'_2 u'_3 u'_4 u'_{12} u'_{13} u'_{14} u'_{23} u'_{24} u'_{34} u'_{123} u'_{124}
-   u'_{134} u'_{234} u'_{1234},\nonumber \\ 
-   1-u'_1&=u_1 u_{12} u_{13} u_{14} u_{123}
-   u_{124} u_{134} u_{1234} u'_2 u'_3 u'_4 u'_{23} u'_{24} u'_{34} u'_{234},\nonumber \\ 
-   1-u'_2&=u_2
-   u_{12} u_{23} u_{24} u_{123} u_{124} u_{234} u_{1234} u'_1 u'_3 u'_4 u'_{13} u'_{14}
-   u'_{34} u'_{134},\nonumber \\ 
-   1-u'_3&=u_3 u_{13} u_{23} u_{34} u_{123} u_{134} u_{234} u_{1234} u'_1
-   u'_2 u'_4 u'_{12} u'_{14} u'_{24} u'_{124},\nonumber \\ 
-   1-u'_4&=u_4 u_{14} u_{24} u_{34} u_{124}
-   u_{134} u_{234} u_{1234} u'_1 u'_2 u'_3 u'_{12} u'_{13} u'_{23} u'_{123},\nonumber \\ 
-   1-u'_{12}&=u_1
-   u_2 u_{12}^2 u_{13} u_{14} u_{23} u_{24} u_{123}^2 u_{124}^2 u_{134} u_{234}
-   u_{1234}^2 \left(u'\right)_3^2 \left(u'\right)_4^2 u'_{13} u'_{14} u'_{23} u'_{24}
-   \left(u'\right)_{34}^2 u'_{134} u'_{234},\nonumber \\
-   1-u'_{13}&=u_1 u_3 u_{12} u_{13}^2 u_{14}
-   u_{23} u_{34} u_{123}^2 u_{124} u_{134}^2 u_{234} u_{1234}^2 \left(u'\right)_2^2
-   \left(u'\right)_4^2 u'_{12} u'_{14} u'_{23} \left(u'\right)_{24}^2 u'_{34} u'_{124}
-   u'_{234},\nonumber \\
-   1-u'_{14}&=u_1 u_4 u_{12} u_{13} u_{14}^2 u_{24} u_{34} u_{123} u_{124}^2
-   u_{134}^2 u_{234} u_{1234}^2 \left(u'\right)_2^2 \left(u'\right)_3^2 u'_{12} u'_{13}
-   \left(u'\right)_{23}^2 u'_{24} u'_{34} u'_{123} u'_{234},\nonumber \\ 1-u'_{23}&=u_2 u_3 u_{12}
-   u_{13} u_{23}^2 u_{24} u_{34} u_{123}^2 u_{124} u_{134} u_{234}^2 u_{1234}^2
-   \left(u'\right)_1^2 \left(u'\right)_4^2 u'_{12} u'_{13} \left(u'\right)_{14}^2 u'_{24}
-   u'_{34} u'_{124} u'_{134},\nonumber \\ 1-u'_{24}&=u_2 u_4 u_{12} u_{14} u_{23} u_{24}^2 u_{34}
-   u_{123} u_{124}^2 u_{134} u_{234}^2 u_{1234}^2 \left(u'\right)_1^2 \left(u'\right)_3^2
-   u'_{12} \left(u'\right)_{13}^2 u'_{14} u'_{23} u'_{34} u'_{123} u'_{134},\nonumber \\ 1-u'_{34}&=u_3
-   u_4 u_{13} u_{14} u_{23} u_{24} u_{34}^2 u_{123} u_{124} u_{134}^2 u_{234}^2
-   u_{1234}^2 \left(u'\right)_1^2 \left(u'\right)_2^2 \left(u'\right)_{12}^2 u'_{13}
-   u'_{14} u'_{23} u'_{24} u'_{123} u'_{124},\nonumber \\
-   1-u'_{123}&=u_1 u_2 u_3 u_{12}^2 u_{13}^2
-   u_{14} u_{23}^2 u_{24} u_{34} u_{123}^3 u_{124}^2 u_{134}^2 u_{234}^2 u_{1234}^3
-   \left(u'\right)_4^3 \left(u'\right)_{14}^2 \left(u'\right)_{24}^2
-   \left(u'\right)_{34}^2 \left(1+ u'_1 u'_2 u'_3 u'_{12} u'_{13} u'_{23} u'_{123}\right)
-   u'_{124} u'_{134} u'_{234},\nonumber \\ 
-   1-u'_{124}&=u_1 u_2 u_4 u_{12}^2 u_{13} u_{14}^2 u_{23}
-   u_{24}^2 u_{34} u_{123}^2 u_{124}^3 u_{134}^2 u_{234}^2 u_{1234}^3 \left(u'\right)_3^3
-   \left(u'\right)_{13}^2 \left(u'\right)_{23}^2 \left(u'\right)_{34}^2 u'_{123}
-   \left(1+u'_1 u'_2 u'_4 u'_{12} u'_{14} u'_{24} u'_{124}\right) u'_{134}
-   u'_{234},\nonumber \\ 
-   1-u'_{134}&=u_1 u_3 u_4 u_{12} u_{13}^2 u_{14}^2 u_{23} u_{24} u_{34}^2
-   u_{123}^2 u_{124}^2 u_{134}^3 u_{234}^2 u_{1234}^3 \left(u'\right)_2^3
-   \left(u'\right)_{12}^2 \left(u'\right)_{23}^2 \left(u'\right)_{24}^2 u'_{123} u'_{124}
-   \left(1+ u'_1 u'_3 u'_4 u'_{13} u'_{14} u'_{34} u'_{134}\right) u'_{234},\nonumber \\ 
-   1-u'_{234}&=u_2
-   u_3 u_4 u_{12} u_{13} u_{14} u_{23}^2 u_{24}^2 u_{34}^2 u_{123}^2 u_{124}^2 u_{134}^2
-   u_{234}^3 u_{1234}^3 \left(u'\right)_1^3 \left(u'\right)_{12}^2 \left(u'\right)_{13}^2
-   \left(u'\right)_{14}^2 u'_{123} u'_{124} u'_{134} \left(u'_2 u'_3 u'_4 u'_{23} u'_{24}
-   u'_{34} u'_{234}+1\right) ,\nonumber \\
-   1-u'_{1234}&=6 u_1 u_2 u_3 u_4 u_{12}^2 u_{13}^2 u_{14}^2 u_{23}^2
-   u_{24}^2 u_{34}^2 u_{123}^3 u_{124}^3 u_{134}^3 u_{234}^3
-   u_{1234}^4 u'_1 u'_2 u'_3 u'_4 \left(u'\right)_{12}^2
-   \left(u'\right)_{13}^2 \left(u'\right)_{14}^2
-   \left(u'\right)_{23}^2 \left(u'\right)_{24}^2
-   \left(u'\right)_{34}^2 \left(u'\right)_{123}^2
-   \left(u'\right)_{124}^2 \left(u'\right)_{134}^2
-   \left(u'\right)_{234}^2 \textcolor{red}{\left(u'\right)_{1234}^2} - \nonumber \\  u_1 u_2& u_3 u_4
-   u_{12}^2 u_{13}^2 u_{14}^2 u_{23}^2 u_{24}^2 u_{34}^2
-   u_{123}^3 u_{124}^3 u_{134}^3 u_{234}^3 u_{1234}^4
-   u'_{12} u'_{13} u'_{14} u'_{23} u'_{24} u'_{34} u'_{123}
-   u'_{124} u'_{134} u'_{234} \left(-3
-   u_{1234}^2+\left(1-u'_1\right){}^2+\left(1-u'_2\right){}^2+\left(1
-   -u'_3\right){}^2+\left(1-u'_4\right){}^2\right) \textcolor{red}{u'_{1234}} \nonumber \\ & + u_1 u_2
-   u_3 u_4 u_{12}^2 u_{13}^2 u_{14}^2 u_{23}^2 u_{24}^2 u_{34}^2
-   u_{123}^4 u_{124}^4 u_{134}^4 u_{234}^4 u_{1234}^8 \nonumber
-  \end{align*} }}
-The $u$-equations for $u_1,u_2,u_3,u_4,u^{'}_{1234}$ are quadratic in the coresponding $u$'s.
-The 10 facets obtained by setting $u^{'}_{i}, ~u_{i}, u^{'}_{1234}, u_{1234} \rightarrow 0$ are all $P_3$ and the 20 facets obtained by setting $u^{'}_{ij}, ~u_{ij}, ~u^{'}_{ijk},~u_{ijk} \rightarrow 0$ are all $A_1 \times P_2$ .
-Thus, 4d permutahderon is indeed a binary positive geometry!
-
-More generally the following are some of the $u$-equations for the $n$-dimensional permutahderon:\\
-
-For $|I| =n-1$ and $s_K = \begin{cases}  1,~ if K \not\subset I & \\ 2, ~if K \subset I\end{cases}$
-
-\bea
-1-u_{I} &=& \prod_ {S - I \subset J } u_{J} \prod_ {K \cap I \ne \Phi } (u^{'}_{K})^{s_K}  \nonumber \\
-1-u_{12\cdots n} &=& \prod_ {{I \subset S}\atop {I \ne \Phi}} u^{'}_{I} \nonumber
-\eea
-
-For $t_J = \begin{cases}  1,~ if I  \not\subset J & \\ 2, ~if I \subset J \end{cases}$
-
-\bea
-1-u^{'}_{i} &=& \prod_ {\{ i \} \subset J } u_{J} \prod_ {K \subset S- \{i\} } u^{'}_{K} \nonumber \\
-1-u^{'}_{i j} &=& \prod_ {\{i,j \}\cap J \ne \Phi} u^{t_J}_{J} \prod_ {K \subset S-\{i, j \} } (u^{'}_{K})^{2} u^{'}_{K \cup {i}} u^{'}_{K \cup{j} } \nonumber 
-\eea
-
-and for $|I| =n-2$ with $S- I = \{i, j\}$
-
-\bea
-1-u_{I}= u_i u_j u^{2}_{ij} \prod_{J \subset I} u_{J \cup \{i\}} u_{J \cup \{j\}} u^{2}_{J \cup \{i,j\}} \prod_{K \subset S-I} (u^{'}_K)^{3} (u^{'}_{K \cup \{i\}})^{2}  (u^{'}_{K \cup\{j\}})^{2}  u^{'}_{K\cup \{i,j\}} \left( 1+ u^{'}_i u^{'}_j u^{'}_{ij} \prod_{I \subset L} u_L \right)                       \nonumber
-\eea
-The other $u$-equations are not two or three term equations and seem to be some higher  order polynomials in the corresponding $u$'s and it would be nice if we could classify all of them.
+where 
+\[
+h_{\{0,1\},4}=u_{01} u_{012} u_{013} u_{014} u_{0123} u_{0124} u_{0134},
+\]
+\begin{align*}
+h_{\{0\},4}(u)=&\,u_{0} u_{01}^3 u_{02} u_{03} u_{04} u_{012}^3 u_{013}^3 u_{023} u_{024} u_{034} u_{0123}^2 u_{0124}^2 u_{0134}^2 u_{0234} u_{014}^3\\
+&+u_{0} u_{01} u_{02} u_{03} u_{04} u_{012}^2 u_{013}^2 u_{023} u_{024} u_{034} u_{0123}^2 u_{0124}^2 u_{0134}^2 u_{014}^2\\
+&+u_{0}^2 u_{01}^2 u_{02}^2 u_{03}^2 u_{04}^2 u_{012}^2 u_{013}^2 u_{023}^2 u_{024}^2 u_{034}^2 u_{0123} u_{0124} u_{0134} u_{0234}^2 u_{014}^2\\
+&+u_{0} u_{01}^2 u_{02} u_{03} u_{04} u_{012}^2 u_{013}^2 u_{023} u_{024} u_{034} u_{0123} u_{0124} u_{0134} u_{0234}^2 u_{014}^2\\
+&+u_{0} u_{01} u_{02} u_{03} u_{04} u_{012} u_{013} u_{023} u_{024} u_{034} u_{0234} u_{014}.
+\end{align*}
+The other $u$ variables and $u$ equations can be obtained by permutation of the indices. %The $u$ equations for $u_i$ are quadratic in $u_i$'s.
+
+The 10 facets of $\mathscr P_4$ obtained by setting $u_{i}, u_{i j k l} \rightarrow 0$ are all $\mathscr{P}_3$ and the 20 facets obtained by setting $u_{i j},~u_{i j k} \rightarrow 0$ are all $\mathscr{A}_1 \times \mathscr{P}_2$ .
 

### 2020-05-15 draft_ABP.tex
Updates from Overleaf

@@
 where $C$'s are positive numbers.
-As first introduced in~\cite{Arkani-Hamed:2019vag}, it is convenient and illuminating to represent these conditions in a meash diagram of $1+1$-D lattice.
+As first introduced in~\cite{Arkani-Hamed:2019vag,Bazier-Matte:2018rat}, it is convenient and illuminating to represent these conditions in a meash diagram of $1+1$-D lattice.
 For example, we can have the following mesh for ABHY realization of $\mathscr A_3$:

### 2020-06-27 draft_ABP.tex
Updates from Overleaf

--- 2020-05-15 draft_ABP.tex
@@
 \pdfoutput=1
-\usepackage{epsfig,amsfonts,amssymb}
-
-\usepackage{comment}
-\input epsf.sty
-\topmargin -.1cm
-\textheight 21cm
-\oddsidemargin 0.15cm 
-\textwidth 14cm
-\usepackage{cite}
+\usepackage{jheppub}
+
+%\input epsf.sty
+%\topmargin -.1cm
+%\textheight 21cm
+%\oddsidemargin 0.15cm 
+%\textwidth 14cm
+\usepackage{cite,comment}
 \usepackage{epsfig,amssymb,euscript,xspace,xcolor}
-\usepackage{amsmath,mathtools,empheq,amsthm,hyperref,graphicx,paralist}
+\usepackage{amsfonts,amssymb,amsmath,mathtools,empheq,amsthm,hyperref,graphicx,paralist}
 \usepackage{mathrsfs,float}  
@@
 \usetikzlibrary{arrows}
-\usepackage[T1]{fontenc} 
+%\usepackage[T1]{fontenc} 
 \usepackage{tikz,caption,subcaption,marvosym} 
@@
 \usepackage[belowskip=-15pt,aboveskip=0pt]{caption}
-\usepackage[skip=10pt]{caption} % example skip set to 2pt
-\usepackage{comment}
+%\usepackage[skip=10pt]{caption} % example skip set to 2pt
 
@@
 Stringy canonical forms are a class of integrals that provide $\alpha'$-deformations of the canonical form of any polytopes.
-For generalized associahedra of finite-type cluster algebra, there exist completely rigid stringy integrals, whose configuration spaces are the so-called binary geometries, and for classical types are associated with (generalized) scattering of particles and strings.
+For generalized associahedra of finite-type cluster algebras, there exist completely rigid stringy integrals, whose configuration spaces are the so-called binary geometries, and for classical types are associated with (generalized) scattering of particles and strings.
 In this paper we propose a large class of rigid stringy canonical forms for another class of polytopes, generalized permutohedra, which also include associahedra and cyclohedra as special cases (type $A_n$ and $B_n$ generalized associahedra).
@@
 non-negative coefficients~\cite{Arkani-Hamed:2019mrd}: $\prod_i x_i^{\alpha' X_i} \prod_I p_I(x)^{-\alpha' c_I}$.
-Note that we have factored out $n{-}3$ monomials, $x_i$, and left with $n(n{-}3)/2-(n{-}3)$ positive polynomials $p_I(x)$, with exponents $X_i$'s and $c_I$'s given by linear combinations of the Mandelstam variables $s_{i,j}$.
+Note that we have factored out $n{-}3$ monomials, $x_i$, and left with $n(n{-}3)/2-(n{-}3)$ positive polynomials $p_I(x)$, with exponents $X_i$'s and $c_I$'s given by linear combinations of the Mandelstam variables $s_{ij}$.
 
@@
 First of all, one can show that the integral \eqref{stringycanonicalform} is convergent if and only if $\mathbf X=(X_1,\dots,X_d)$ is in the interior of the polytope $\mathcal P$ (we assume that ${\cal P}$ is $d$ dimensional).
-The leading order of the integral in its $\alpha'$ expansion, dressed with $d^d \mathbf X$, is given by the canonical form of the polytope, ${\Omega}(\cal P)$, thus it can be viewed as an $\alpha'$-deformation of $\Omega(\cal P)$ (hence the name ``stringy canonical form'').
+The leading order of the integral in its $\alpha'$ expansion, dressed with $\mathrm{d}^d \mathbf X$, is given by the canonical form of the polytope, ${\Omega}(\cal P)$, thus it can be viewed as an $\alpha'$-deformation of $\Omega(\cal P)$ (hence the name ``stringy canonical form'').
 Generically the poles of $\Omega(\cal P)$ are given by equations of
@@
 The poles are the planar variables $X_{i,j}$, on which \eqref{stringint} factorizes into lower-point integrals even for finite $\alpha'$.
-Moreover, the saddle point equations as $\alpha' \to \infty$ can be written as $X_i=\sum_I c_I \partial \log p_I/\partial \log x_i$ for $i=1,\dots, d$; they provide a diffeomorphism from the integration domain to ${\cal P}$, thus $\Omega(\mathcal P)$ can be computed as a pushforward of $\prod_i d\log x_i$ via summing over the saddle points~\cite{Arkani-Hamed:2017tmz}.
+Moreover, the saddle point equations as $\alpha' \to \infty$ can be written as $X_i=\sum_I c_I \partial \log p_I/\partial \log x_i$ for $i=1,\dots, d$; they provide a diffeomorphism from the integration domain to ${\cal P}$, thus $\Omega(\mathcal P)$ can be computed as a pushforward of $\prod_i \mathrm{d}\log x_i$ via summing over the saddle points~\cite{Arkani-Hamed:2017tmz}.
 In particular, for the string integral \eqref{stringint}, the scattering equations provide a map from ${\cal M}_{0,n}^+$ to ABHY associahedron, and the pushforward is equivalent to the CHY formula for $\phi^3$ amplitude~\cite{Cachazo:2013hca,Cachazo:2013iea}.
@@
 $\alpha=1,\dots, v$. Note that there's no unique way to write $S_J=F_\alpha V_J^\alpha$ if the big polyhedron is not a simplex, \textit{i.e.} $v>d+m$, and in this case,
-$u$ variables $\{u_\alpha \}$ are not independent. Therefore, it is an important special case when the big polyhedron is a simplex, \textit{i.e.} $N=v=d+m$, where $N$ is 
+$u$ variables $\{u_\alpha \}$ are not multiplicatively independent. Therefore, it is an important special case when the big polyhedron is a simplex, \textit{i.e.} $N=v=d+m$, where $N$ is 
 the number of facets of the big polyhedron or the original polytope $\mathcal P$,
-and inequalities $F_\alpha=S_J(V^{-1})^J_\alpha \geq 0$ are exactly the inequalities $W_a^J S_J\geq 0$ up to resales $F_\alpha \mapsto t F_\alpha$ for non-zero factors $t$, because
+and inequalities $F_\alpha=S_J(V^{-1})^J_\alpha \geq 0$ are exactly the inequalities $W_a^J S_J\geq 0$ up to resales $F_\alpha \mapsto t F_\alpha$ for positive factors $t$, because
 there's no nontrivial linear isometry from the simplex to itself besides permutations of vertices. Therefore, we identity the label of facets $\alpha$ with the label of 
@@
 These ``cluster string integrals''~\cite{Arkani-Hamed:2019plo}, and the associated ``cluster configuration spaces''~\cite{Arkani-Hamed:2019plo,Arkani-Hamed:tobeappear}, turn out to be much more special and rigid extensions of string amplitudes \eqref{stringint} and the moduli space ${\cal M}_{0,n}$, which correspond to the case of type $A_{n{-}3}$.
-The leading order of such an integral is given by canonical function of the corresponding generalized associahedra, whose combinatorics is attached to the Dynkin diagram (each facet is given by removing a node), {\it e.g.} $D_n \to D_m \times A_{n{-}1{-}m}$ or $A_{n{-}1}$~\cite{Arkani-Hamed:2019plo}.
+The leading order of such an integral is given by the canonical function of the corresponding generalized associahedra, whose combinatorics is attached to the Dynkin diagram (each facet is given by removing a node), {\it e.g.} $D_n \to D_m \times A_{n{-}1{-}m}$ or $A_{n{-}1}$~\cite{Arkani-Hamed:2019plo}.
 Even at finite $\alpha'$, it has the remarkable factorization property tied to the Dynkin diagram.
@@
 \begin{equation}\label{perfectu}
-	1-u_\alpha=\prod_{\beta} u_\beta^{(\beta||\alpha)},
-\end{equation}
-where the product is over all $N$ variables ($N$ facets), and the integer $(\beta || \alpha)\geq 0$ is the so-called compatibility degree defined in the corresponding cluster algebra~\cite{Zelevinskysys}.
+	1-u_\alpha=\prod_{\beta} u_\beta^{\beta||\alpha},
+\end{equation}
+where the product is over all $N$ variables ($N$ facets), and the integer $\beta || \alpha\geq 0$ is the so-called compatibility degree defined in the corresponding cluster algebra~\cite{Zelevinskysys}.
 Varieties defined by $u$ equations associated with finite type clusters  are called cluster configuration spaces.
@@
 \] 
-As $u_\alpha\to 0$, there is no $u\to 1$, and all $n$ remaining $u$ variables satisfy the same equations for that facet, which is an $(n{-}1)$-dim simplex.
+As $u_\alpha\to 0$, there is no $u\to 1$, and all $n$ remaining $u$ variables satisfy the same equations for that facet, which is an $(n{-}1)$-dimensional simplex.
 Although this example is trivial, it does show that we do not necessarily need perfect $u$ equations to have binary geometries.
@@
 where $\beta ||\alpha \geq 0$ are integers which vanishes for $\beta$ compatible with $\alpha$, and $p_\alpha(\{u\})$ is an arbitrary polynomial which must equal to unity on the facet $\alpha$, $p_\alpha (\{u\})|_{u_\alpha=0}=1$.
-When $u_\alpha \to 0$, since it appears on the RHS of equation with $1-u_\beta$ for any incompatible $\beta$, we have $u_\beta\to 1$ for any polynomial $p_\beta (\{u\})$.
+When $u_\alpha \to 0$, since it appears on the RHS of the equation with $1-u_\beta$ for any incompatible $\beta$, we have $u_\beta\to 1$ for any polynomial $p_\beta (\{u\})$.
 However, in the equation with $1-u_\alpha$, since all the incompatible $u_\beta \to 1$ we find $p_\alpha (\{u\})|_{u_\alpha=0}=1$ (where we evaluate the polynomial at $u_\alpha=0$ and all incompatible $u_\beta=1$).
@@
 As the main result of the paper, we present infinitely many new examples of binary geometries which have $u$ equations of the form \eqref{genueq}, and (also infinitely) many of them with perfect $u$ equations.
-The key idea to consider a class of stringy integrals for {\it generalized permutohedra} that can be realized as the Minkowski sum of coordinate simplices as follows (more details will be given later).
+The key idea to consider a class of stringy integrals for {\it generalized permutohedra} that can be realized as the Minkowski sum of coordinate simplices is as follows (more details will be given later).
 Given the label set $[0,n]=\{0,1,\dots, n\}$, we define a {\it building set} $\mathbf B$ as a collection of subsets $I \subset [0,n]$ that satisfy (1).
@@
 it contains all {\it singletons} $\{i\}$.
-For each subset $I$ we have a simplex $\Delta_I$ as the convex hull of unit vectors ${\bf e}_i$ with $i\in I$, and the generalized permutohedron ${\mathscr P}(\mathbf B)$ is given by (weighted) Minkowski sum of $\Delta_I$ (defined on a $n$-dimensional hyperplane of the $(n{+}1)$-dim space)~\cite{Postnikov:2005}.
+For each subset $I$ we have a simplex $\Delta_I$ as the convex hull of unit vectors ${\bf e}_i$ with $i\in I$, and the generalized permutohedron ${\mathscr P}(\mathbf B)$ is given by (weighted) Minkowski sum of $\Delta_I$ (defined on a $n$-dimensional hyperplane of the $(n{+}1)$-dimensional space)~\cite{Postnikov:2005}.
 It is very natural to define stringy canonical form for such a building set $\mathbf B$: for each subset $I$, we have the simplest {\it linear} polynomial $x_I:=\sum_{i\in I} x_i$ (for singletons, $x_{\{i\}}=x_i$ are the coordinates), and
@@
 Let's first present the simplest example with building set ${\mathbf B}$ given by all the singletons $\{i\}$ and $[0,n]$.
-In this case, ${\mathscr P}(\mathbb B)=c {\bf N} [\sum_{i=0}^n x_i]$ is the $n$-dim simplex (we denote $c:=C_{[0, n]}$), given by $X_i \geq 0$ with one (ABHY) constraint $\sum_{i=1}^n X_i=c$.
+In this case, ${\mathscr P}(\mathbb B)=c {\bf N} [\sum_{i=0}^n x_i]$ is the $n$-dimensional simplex (we denote $c:=C_{[0, n]}$), given by $X_i \geq 0$ with one (ABHY) constraint $\sum_{i=1}^n X_i=c$.
 It is straightforward to see that the $u$ variables are $u_i=\frac{x_i}{x_{[0,n]}}=\frac{x_i}{\sum_i x_i}$ and they satisfy $\sum_{i=0}^d u_i=1$ as expected.
@@
 \begin{itemize}
-\item Consider $\mathbf B$ as the collection of all $n(n{+}3)/2+1$ consecutive intervals of $[0,n]$, ${\mathscr P}(\mathbf B) \equiv {\mathscr A}_n$ is the $n$-dim associahedron, \eqref{intgenperm} is nothing but $(n{+}3)$-pt string integral \eqref{stringint}; {\it e.g.} for $n=2$, ${\mathbf B}=\{\{i\}, \{0,1\}, \{1,2\}, \{0,1,2\}\}$, and we have a pentagon ${\mathscr A}_2$.
-\item Consider $\mathbf B$ as the collection of all $n(n{+}1)+1$ cyclic intervals of $[0,n]$ which can wrap around $n$, ${\mathscr P} (\mathbf B) \equiv {\mathscr B}_n$ is the $n$-dim cyclohedron, and in sec.
+\item Consider $\mathbf B$ as the collection of all $n(n{+}3)/2+1$ consecutive intervals of $[0,n]$, ${\mathscr P}(\mathbf B) \equiv {\mathscr A}_n$ is the $n$-dimensional associahedron, \eqref{intgenperm} is nothing but $(n{+}3)$-pt string integral \eqref{stringint}; {\it e.g.} for $n=2$, ${\mathbf B}=\{\{i\}, \{0,1\}, \{1,2\}, \{0,1,2\}\}$, and we have a pentagon ${\mathscr A}_2$.
+\item Consider $\mathbf B$ as the collection of all $n(n{+}1)+1$ cyclic intervals of $[0,n]$ which can wrap around $n$, ${\mathscr P} (\mathbf B) \equiv {\mathscr B}_n$ is the $n$-dimensional cyclohedron, and in sec.
 2 we will show that non-trivially \eqref{intgenperm} is the cluster stringy integral for type $B_n$ (not that for type $C_n$); {\it e.g.} $n=2$, ${\mathbf B}=\{\{i\}, \{0,1\}, \{1,2\}, \{2,0\}, \{0,1,2\}\}$, and we have a hexagon ${\mathscr B}_2$.
-\item Consider $\mathbf B$ as the collection of all $2^{n{+}1}-1$ subsets of $[0,n]$, ${\mathscr P}(\mathbf B) \equiv {\mathscr P}_n$ is the $n$-dim permutohedron (for $n=2$, it coincides with ${\mathscr B}_2$).
+\item Consider $\mathbf B$ as the collection of all $2^{n{+}1}-1$ subsets of $[0,n]$, ${\mathscr P}(\mathbf B) \equiv {\mathscr P}_n$ is the $n$-dimensional permutohedron (for $n=2$, it coincides with ${\mathscr B}_2$).
 All generalized permutohedra (and their stringy integrals) can be obtained from (that of) ${\mathscr P}_n$.
@@
 2, we will go further and discover more binary geometries with perfect $u$ equations, which can be obtained by ``degenerating'' type $A$ and $B$ integrals by requiring certain $S_I=0$ (for example, type $A$ integral is in fact a degeneration of the type $B$ integral, which was not obvious before).
-Some of these cases are products of lower-dim $A$'s and $B$'s, but we will see entirely new binary geometries with perfect $u$ equations.
+Some of these cases are products of lower-dimensional $A$'s and $B$'s, but we will see entirely new binary geometries with perfect $u$ equations.
 
@@
 3 is that, the configuration space for any ${\cal I}_{\mathbf B}$ is always binary, which means that any $u_\alpha \to 0$ forces all the incompatible ones $u_\beta\to 1$.
-As we will see explicitly with ${\mathscr P}_n$, its $u$ equations indeed take the form of \eqref{genueq}, which is no longer perfect for $n>2$, but the space is binary and the integral factorizes as a product of lower-dim permutohedron integrals at finite $\alpha'$!
+As we will see explicitly with ${\mathscr P}_n$, its $u$ equations indeed take the form of \eqref{genueq}, which is no longer perfect for $n>2$, but the space is binary and the integral factorizes as a product of lower-dimensional permutohedron integrals at finite $\alpha'$!
 Note that an important feature of any generalized permutohedron is that its facets are labelled by all subsets $I$ in ${\mathbf B}$ except for the complete set $[0,n]$, and on each facet it factorizes as a product of two generalized permutohedra.
@@
 \section{Configuration spaces with perfect $u$ equations from degenerating ${\mathscr A_n}$ and ${\mathscr B_n}$}
-In this section we shall consider some degenerations of ${\mathscr A_n}$ and ${\mathscr B_n}$ and show that there are an infinite class of examples of binary geometries with perfect $u$ equations.
+In this section we shall consider some degenerations of $n$-dimensional associahedron ${\mathscr A_n}$ and $n$-dimensional cyclohedron ${\mathscr B_n}$ and show that there are an infinite class of examples of binary geometries with perfect $u$ equations.
 To do this we shall use the fact that both ${\mathscr A_n}$ and ${\mathscr B_n}$ can be realised as a Minkowski sum of coordinate simplices.
@@
 where $C$'s are positive numbers.
-As first introduced in~\cite{Arkani-Hamed:2019vag}, it is convenient and illuminating to represent these conditions in a meash diagram of $1+1$-D lattice.
+As first introduced in~\cite{Arkani-Hamed:2019vag,Bazier-Matte:2018rat}, it is convenient and illuminating to represent these conditions in a meash diagram of $(1+1)$-D lattice.
 For example, we can have the following mesh for ABHY realization of $\mathscr A_3$:
@@
 \frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(1-z_1)(z_1-z_2)\cdots (z_{n}-0)}
-\prod_{0\leq i<j \leq n}(z_i-z_j)^{s_{ij}}(1-z_i+z_j)^{t_{ij}},
+\prod_{1\leq i<j \leq n+1}(z_i-z_j)^{s_{ij}}(1-z_i+z_j)^{t_{ij}},
 \end{equation}
@@
 where $F_{[a,b]}:=0$ when $a>b$ or $[a,b]=[0,n]$,
-an standard way to get a degeneration whose big polyhedron is a simplex is setting all $C$'s on the RHS of 
+a standard way to get a degeneration whose big polyhedron is a simplex is setting all $C$'s on the RHS of 
 \begin{align}
@@
 \end{equation}
-for any $I\not\in \mathscr D$.  The simplest degenerations of $\mathscr A_n$ are those with one $C_{[i,i+1]}$ vanishing, where we get 
+for any $I\not\in \mathscr D$.
+
+The simplest degenerations of $\mathscr A_n$ are those with one $C_{[i,i+1]}$ vanishing, where we get 
 \[
@@
 \subsubsection{Products of ${\mathscr A}$ and $\mathscr{B}$}
-We can also construct binary geometries which are of the type $\prod_{i=1}^n X_i$ where $X_i={\mathscr A_i}~{\rm or}~{\mathscr B_i}$ which are not necessarily degenerations of ${\mathscr A}~{\rm or}~{\mathscr B}$.
+We can also construct binary geometries of the type $\prod_{i=1}^n X_i$ where $X_i={\mathscr A_i}~{\rm or}~{\mathscr B_i}$ which are not necessarily degenerations of ${\mathscr A}~{\rm or}~{\mathscr B}$.
 Without loss of generality we consider only the case ${\mathscr A_n}\times {\mathscr B_m}$.
@@
 
-If $\mathbf{B}_{1}$ and $\mathbf{B}_{2}$ were disjoint then its obvious that the stringy integral ${\cal I}_{\mathbf B}$ in \eqref{stringycanonicalform} directly factorizes into ${\cal I}_{\mathbf B_1}\times {\cal I}_{\mathbf B_2}$, however the singlet $\{n\}$ belongs to both $B_1$ and $B_2$.
+If $\mathbf{B}_{1}$ and $\mathbf{B}_{2}$ were disjoint then it's obvious that the stringy integral ${\cal I}_{\mathbf B}$ in \eqref{stringycanonicalform} directly factorizes into ${\cal I}_{\mathbf B_1}\times {\cal I}_{\mathbf B_2}$, however the singlet $\{n\}$ belongs to both $B_1$ and $B_2$.
 But by rescaling the variables in $B_2$ by $x_i \rightarrow x_n x_i$ for all $i=n+1,\dots,n+m $ it is straightforward to see that the ${\cal I}_{\mathbf B}$ does indeed factorize into ${\cal I}_{\mathbf B_1}\times {\cal I}_{\mathbf B_2}$ with $x_n$ playing the role of $x_0=1$ in $B_2$.
@@
 %More generally by interpreting the stringy integral \eqref{stringycanonicalform} as a Mellin transform it was shown in \cite{Mellin,Eulermellin} that the result of any stringy integral with linear factors i.e any generalized permutohedron is given by product of gamma functions of the facets of the Newton polytope times an entire function.
-
+All stringy integrals (including the ones with non-linear factors) can in principle be evaluated as linear combination of A-hypergeometric functions with special arguments by identification the with a GKZ system \cite{saito2013grobner,gelfand1990generalized} (see also \cite{delaCruz:2019skx}).
 We shall leave the evaluation of more stringy integrals and related topics to future work.

### 2020-06-27 draft_ABP.tex
Updates from Overleaf

@@
 \pdfoutput=1
-\usepackage{jheppub}
 
@@
 %\textwidth 14cm
-\usepackage{cite,comment}
+\usepackage{comment}
 \usepackage{epsfig,amssymb,euscript,xspace,xcolor}
-\usepackage{amsfonts,amssymb,amsmath,mathtools,empheq,amsthm,hyperref,graphicx,paralist}
+\usepackage{amsfonts,amssymb,amsmath,mathtools,empheq,amsthm,graphicx,paralist}
 \usepackage{mathrsfs,float}  
@@
 
-\usepackage[titles]{tocloft}
-\renewcommand{\cftdot}{} %Don't want dots in TOC
+% \usepackage[titles]{tocloft}
+% \renewcommand{\cftdot}{} %Don't want dots in TOC
 
@@
 
-\usepackage{hyperref,cite}
-\hypersetup{linktocpage, colorlinks=true,linkcolor= blue,citecolor=blue,urlcolor=lightblue}
+% \usepackage{hyperref}
+% \hypersetup{linktocpage, colorlinks=true,linkcolor= blue,citecolor=blue,urlcolor=lightblue}
+
+\usepackage{jheppub}
 
@@
 
-\textwidth 16.9cm
-\oddsidemargin -.25cm
+% \textwidth 16.9cm
+% \oddsidemargin -.25cm
 
@@
 
-\renewcommand{\theequation}{\thesection.\arabic{equation}}
-\renewcommand{\theequation}{\arabic{equation}}
+% \renewcommand{\theequation}{\thesection.\arabic{equation}}
+% \renewcommand{\theequation}{\arabic{equation}}
 
@@
 \makeatletter
+
 \newenvironment{calc}{\allowdisplaybreaks\start@align\@ne\st@rredtrue\m@ne}
@@
 
+\date{\today}
+\title{Stringy canonical forms and binary geometries from associahedra, cyclohedra and generalized permutohedra}
+
 \begin{document}
 
-\baselineskip 24pt
-
-\begin{center}
-
-{\Large \bf Stringy canonical forms and binary geometries from associahedra, cyclohedra and generalized permutohedra}
-
-\end{center}
-
-\vskip .5cm
-\medskip
-
-\vspace*{4.0ex}
-
-\baselineskip=15 pt
-
-\centerline{\large \rm  {\bf Song He$^{a, b}$, Zhenjie Li$^{a, b}$, Prashanth Raman$^{a, c,d}$, Chi Zhang$^{a, b}$ } }
-
-\vspace*{4.0ex}
-{\it ~ $^a$ CAS Key Laboratory of Theoretical Physics, Institute of Theoretical Physics, Chinese Academy}
-
-{\it of Sciences, Beijing 100190, China}
-
-{\it ~$^b$ School of Physical Sciences, University of Chinese Academy of Sciences, No.19A Yuquan Road,}
-
-{\it Beijing 100049, China}
-
-{\it ~$^c$ Institute of Mathematical Sciences, Taramani, Chennai 600 113, India}
-
-{\it ~$^d$ Homi Bhabha National Institute, Anushakti Nagar, Mumbai 400085, India}
-
-\vspace*{1.0ex}
-\centerline{\it ~E-mail : songhe@itp.ac.cn, lizhenjie@itp.ac.cn, prashanthr@imsc.res.in, zhangchi@itp.ac.cn} 
-\vspace*{5.0ex}
-\centerline{\bf Abstract} \bigskip
-
-Stringy canonical forms are a class of integrals that provide $\alpha'$-deformations of the canonical form of any polytopes.
+% \baselineskip 24pt
+
+\author[a,b]{Song He}
+\author[a,b]{,\,Zhenjie Li}
+\author[a,c,d]{,\,Prashanth Raman}
+\author[a,b]{,\,Chi Zhang}
+\affiliation[a]{CAS Key Laboratory of Theoretical Physics, Institute of Theoretical Physics, Chinese Academy of Sciences, Beijing 100190, China}
+\affiliation[b]{School of Physical Sciences, University of Chinese Academy of Sciences, No.19A Yuquan Road, Beijing 100049, China}
+\affiliation[c]{Institute of Mathematical Sciences, Taramani, Chennai 600 113, India}
+\affiliation[d]{Homi Bhabha National Institute, Anushakti Nagar, Mumbai 400085, India}
+\emailAdd{songhe@itp.ac.cn}
+\emailAdd{lizhenjie@itp.ac.cn}
+\emailAdd{prashanthr@imsc.res.in}
+\emailAdd{zhangchi@itp.ac.cn}
+\date{\today}
+\abstract{Stringy canonical forms are a class of integrals that provide $\alpha'$-deformations of the canonical form of any polytopes.
 For generalized associahedra of finite-type cluster algebras, there exist completely rigid stringy integrals, whose configuration spaces are the so-called binary geometries, and for classical types are associated with (generalized) scattering of particles and strings.
@@
 Our results provide yet another family of generalizations of the usual string integral and moduli space, whose physical interpretations remain to be explored.
-
-\vfill \eject
-
-\baselineskip=18pt
-
-\tableofcontents
-
-\newpage
+}
+
+\maketitle
 
@@
 \begin{align*}
-1-\tilde u_{[0,l]}&=\left(\prod_{i=0}^{l-1} \prod_{j=i+1}^{k+1}  \tilde u_{[0,i]\cup [j,n]} \prod_{j=i+1}^{l+1} \tilde u_{[0,i]\cup [j,n]}\right) \left(\prod_{i=1}^{l+1} \prod_{j=l+1}^{n}\tilde u_{[i,j]} \right) \left(\prod_{i=1}^{k+1} \tilde u_{[i,n]} \right),\\\\
-1-\tilde u_{[m+2,n]}&=\left( \prod_{j=0}^{m}\tilde u_{[0,j]} \prod_{i=1}^{n-m-1}\tilde u_{[0,m+i]}^2 \right) \left( \prod_{i=m+1}^{n-1}\prod_{j=1}^{m+1}\tilde u_{[j,i]} \right) \left(\prod_{j=0}^{k-m-2} \prod_{i=1}^{m} \tilde u_{[0,i]\cup [3+j+m, n]} \prod_{i= m+1}^{j+m+1} \tilde u_{[0,i]\cup [3+j+m,n]}^2 \right) \\\\
-1-\tilde u_{K_{l,m}}&=\left(\prod_{a=0}^1\prod_{i=l+1}^{n}\tilde u_{[a,i]}\right) \left(\prod_{{\tiny {K_{l',m'} \not\subset K_{l,m}}\atop{K_{l,m} \not\subset K_{l',m'}} }} \tilde u_{K_{l',m'}}^{(l',m')||(l,m)}\right)\left(\prod_{j=2}^{m+1} \prod_{i=l+1}^{n} \tilde u_{[j,i]} \right)\times
+&1-\tilde u_{[0,l]}=\left(\prod_{i=0}^{l-1} \prod_{j=i+1}^{k+1}  \tilde u_{[0,i]\cup [j,n]} \prod_{j=i+1}^{l+1} \tilde u_{[0,i]\cup [j,n]}\right) \left(\prod_{i=1}^{l+1} \prod_{j=l+1}^{n}\tilde u_{[i,j]} \right) \left(\prod_{i=1}^{k+1} \tilde u_{[i,n]} \right),\\[2ex]
+&1-\tilde u_{[m+2,n]}=\left( \prod_{j=0}^{m}\tilde u_{[0,j]} \prod_{i=1}^{n-m-1}\tilde u_{[0,m+i]}^2 \right) \left( \prod_{i=m+1}^{n-1}\prod_{j=1}^{m+1}\tilde u_{[j,i]} \right) \left(\prod_{j=0}^{k-m-2} \prod_{i=1}^{m} \tilde u_{[0,i]\cup [3+j+m, n]} \prod_{i= m+1}^{j+m+1} \tilde u_{[0,i]\cup [3+j+m,n]}^2 \right) \\[2ex]
+&1-\tilde u_{K_{l,m}}=\left(\prod_{a=0}^1\prod_{i=l+1}^{n}\tilde u_{[a,i]}\right) \left(\prod_{{\tiny {K_{l',m'} \not\subset K_{l,m}}\atop{K_{l,m} \not\subset K_{l',m'}} }} \tilde u_{K_{l',m'}}^{(l',m')||(l,m)}\right)\left(\prod_{j=2}^{m+1} \prod_{i=l+1}^{n} \tilde u_{[j,i]} \right)\times
 \begin{cases}
@@
 \subsection{Generalized permutohedra}\label{GP}
-A generalized permutohedron is a polytope that can obtained be as Minkowski sums and differences of co-ordinate simplices.
+A generalized permutohedron is a polytope that can be obtained as Minkowski sums and differences of co-ordinate simplices.
 
@@
 for some collection of subsets $I \in [0,n]$.
-We shall restrict ourselves to the large class of generalized permutohedra which admit such a realisation only as Minkowski sums except translations i.e, $y_I \ge 0$ for all non-singlets $I$\footnote{This is mainly due to the subtle nature of the Minkowski difference operation, which makes the shape of the resulting polytope dependent on the relative magnitudes of $y_I$'s.
-We allow $y_I$ for singlets to be  negative as it is only a translation and to connect with \eqref{intgenperm}.} which are called Nestohedra.
-Throughout the paper we shall mean Nestohedra or products of Nestohedra whenever we refer to generalized permutohedra.
-
-The combinatorial structure of the generalized permutohedron ${\mathscr P_n(\{y_I\})}$ (Nestohedra) is independent of $y_I$ and depends only on the collection of subsets $I \in [0,n]$ of the  building set ${\mathbf B}$, which is
+We shall restrict ourselves to the large class of generalized permutohedra which admit such a realisation only as Minkowski sums except translations i.e, $y_I \ge 0$ for all non-singlets $I$~\footnote{This is mainly due to the subtle nature of the Minkowski difference operation, which makes the shape of the resulting polytope dependent on the relative magnitudes of $y_I$'s.
+We allow $y_I$ for singlets to be  negative as it is only a translation and to connect with \eqref{intgenperm}.} which are called nestohedra.
+Throughout the paper we shall mean nestohedra or products of nestohedra whenever we refer to generalized permutohedra.
+
+The combinatorial structure of the generalized permutohedron ${\mathscr P_n(\{y_I\})}$ (nestohedra) is independent of $y_I$ and depends only on the collection of subsets $I \in [0,n]$ of the  building set ${\mathbf B}$, which is
 a collection of non-empty subsets of $[0,n]$ satisfying the following: %is called a building set ${\mathbf B} if it satisfies the following:
@@
     \item  If ${\mathbf B}= \{[i] | i=0,\dots,n \}$ is the complete flag of intervals, then ${\mathscr P_n(\{y_I\})}$ is the Stanley-Pitman polytope or Hypercube.
-    \item If ${\mathbf B}$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then ${\mathscr P_n(\{y_I\})}$ is the usual permutohedron ${\mathscr P_n}$.
+    \item If ${\mathbf B}$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ {\it i.e.}, the variables $Y_I$ are equal for all subsets of the same cardinality, then ${\mathscr P_n(\{y_I\})}$ is the usual permutohedron ${\mathscr P_n}$.
     \item If ${\mathbf B}=\{ [i,j] | 0\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr P_n(\{y_I\})}$ is the associahedron ${\mathscr A_n}$. 
@@
 
-\paragraph{Nested complex} To describe the combinatorial structure we need the notion of {\it Nested complex}.
+\paragraph{Nested complex} To describe the combinatorial structure we need the notion of {\it nested complex}.
 We shall only summarize the necessary results here and let the reader interested in the details to refer \cite{Postnikov:2005,Postnikov:2006}.
@@
 
-In particular, it means that (1) the number of facets $N$ of the generalized permutohedron just corresponds to the set of all elements in ${\mathbf B}$ excluding the maximal element, and (2) two facets corresponding to the sets $I$ and $J$ in ${\mathbf B}$ intersect i.e., are {\it compatible} with each other if and only if  either $I \subset J$,~ $J \subset I$~ or $I \cap J = \varnothing ~{\text and} ~ I \cup J \notin {\mathbf B}$.
+In particular, it means that (1) the set of facets of the generalized permutohedron just corresponds to the set of all elements in ${\mathbf B}$ excluding the maximal element, and (2) two facets corresponding to the sets $I$ and $J$ in ${\mathbf B}$ intersect {\it i.e.}, are {\it compatible} with each other, if and only if  either $I \subset J$,~ $J \subset I$~ or $I \cap J = \varnothing ~{\text and} ~ I \cup J \notin {\mathbf B}$.
 
@@
 \end{center}
-\caption{Compatible\textbackslash incompatible facets of the 2d associahedron (a) and permutohedron (b) as generalized permutohedra}
+\caption{Facets of the 2d associahedron (a) and permutohedron (b) as generalized permutohedra}
 \end{figure}
@@
 
-Generalized permutohedra have big polyhedra which are simplices.
-Thus its quite natural to wonder if the associated $u$ variables satisfy some kind of $u$ equations.
-We claim and we shall show in the next section that this indeed the case.
+The big polyhedron of generalized permutohedron is a simplex.
+Thus it's quite natural to wonder if the associated $u$ variables satisfy some kind of $u$ equations.
+We claim and we shall show in the next section that this is indeed the case.
 Further we show that all these polytopes are binary geometries even though some of them do not admit perfect $u$ equations.
@@
 %We have seen that any $n$-dimensional generalized permutohedron can be constructed by a Minkowski sum of simplices labeled by subsets in the building set $\mathbf{B}$, which satisfy the conditions given above.
-As we mentioned earlier, one can write down a natural stringy integral \eqref{intgenperm} for generalized permutahedron $\mathscr{P}(\bf B)$,
+As mentioned earlier, one can write down a natural stringy integral \eqref{intgenperm} for generalized permutahedron $\mathscr{P}(\bf B)$,
 %it is a highly non-trivial fact about generalized permutohedra that the number of facets is given by $N=n+m$, where $m$ is the number of non-singletons in $\bf B$. 
@@
 setting 
-$S_I=-C_I$ for any non-singleton $I\in \mathscr P_n$, where $C_I$ are positive 
+$S_I=-C_I$ for any non-singleton $I$, where $C_I$ are positive 
 constants, and the polytope is given by the alternating sum
@@
 \[
-C_{01},C_{02},C_{03},C_{12},C_{23},C_{013},C_{023},C_{123}=0.
-\]
-Its $u$ variables and $u$ equations can be found at the end of section (\ref{sect3.4}). By solving the ABHY conditions for these $C_I=0$, we get the vanishing facets
+C_{01},C_{02},C_{03},C_{12},C_{23},C_{013},C_{023},C_{123}=0,
+\]
+and its $u$ variables and $u$ equations can be found at the end of section (\ref{sect3.4}). By solving the ABHY conditions for these $C_I=0$, we get the vanishing facets
 \begin{align*}
@@
 
-In this paper we introduced a large class of integrals,  ${\cal I}_{\bf B}$, which can be regarded as a family of rigid stringy canonical forms%~\cite{Arkani-Hamed:2019mrd} 
+In this paper we introduce a large class of integrals,  ${\cal I}_{\bf B}$, which can be regarded as a family of rigid stringy canonical forms%~\cite{Arkani-Hamed:2019mrd} 
 for generalized permutohedra ${\mathscr P}(\bf B)$, and we show that corresponding configuration spaces are always binary geometries.
 These rigid integrals satisfy the remarkable property that, at any ``massless'' pole, {\it i.e.} poles of the leading order $\Omega({\mathscr P}(\bf B) )$, the residue is given by a product of two such integrals, ${\cal I}_{{\bf B}_L} \times {\cal I}_{{\bf B}_R}$.
-Our results greatly extended the scope of binary geometries and associated integrals with such ``perfect'' factorization properties, which were originally thought to tie to the more special class of generalized associahedra for finite-type cluster algebras.
+Our results greatly extend the scope of binary geometries and associated integrals with such ``perfect'' factorization properties, which were originally thought to tie to the more special class of generalized associahedra for finite-type cluster algebras.
 For infinite families of cases as degenerations of associahedra and cyclohedra (which belong to both generalized permutohedra and generalized associahedra), we find additionally that the $u$ equations are ``perfect'' just like the case for cluster configuration spaces.
@@
 Along this direction, an intriguing possibility is to classify binary geometries with perfect $u$ equations from degenerating cluster cases; since any product of such geometries still has perfect $u$ equations, this amounts to find all elementary, non-factorizing geometries with perfect $u$ equations.
-More importantly,  what are the possible interpretations of these degenerations from cluster algebra; even for ${\mathscr A}_{n-3}$, what are the meaning of these degenerations of ${\cal M}_{0,n}$ and the string integrals?
+More importantly,  what are the possible interpretations of these degenerations from cluster algebra; even for ${\mathscr A}_{n-3}$, what is the meaning of these degenerations of ${\cal M}_{0,n}$ and the string integrals?
 
@@
 
-We have not touched various properties of these stringy integrals, such as recurrence relations, complex (and real) integrals with two different ``orderings'' and scattering (saddle-point) equations and pushforward, It would be interesting to understand these points better, especially for the ${\mathscr P}_d$ case, which is completely symmetric in the labels.
+We have not touched various properties of these stringy integrals, such as recurrence relations, complex (and real) integrals with two different ``orderings'' and scattering (saddle-point) equations and pushforward.
+It would be interesting to understand these points better, especially for the ${\mathscr P}_d$ case, which is completely symmetric in the labels.
 The scattering equations read
-\[\frac{X_i}{x_i}=\sum_{I \ni i} \frac{c_I}{\sum_{j \in i} x_j}\,,
-\]
+\bea
+\frac{S_i}{x_i}=\sum_{I \ni i} \frac{C_I}{x_I}\,,
+\eea
 which provide a one-to-one map from ${\bf x}\in \mathbb{R}_{\geq 0}^d$ to ${\mathscr P}_d$, and $\Omega({\mathscr P}_d)$ is given by the pushforward via summing over the solutions.
@@
 u_{n+1} &=& \frac{1}{q_1}, ~u_{n+2} = \frac{p_{12}}{q_{1}q_{2}},~u_{n+3} = \frac{q_{1}}{p_{23}}, \dots,
-u_{3n-1} = \frac{ q_{n-1}}{p_{n-1n}} 
+u_{3n-1} = \frac{ q_{n-1}}{p_{n-1n}} ,
 \eea
@@
 The first type has 4 equations:
-\bea
+\[
 1-u_{1} =u_{3n-2} u_{3n-1},~
@@
 u_{1} u_{2} , n\geq 5
-\end{cases} 
-\eea
+\end{cases},
+\]
 with the corresponding facets being $\mathscr{X}_{n-1}$. The second type has $n-3$ equations
-\bea
-1-u_{n+4} =u_{n} u_{n+2}u_{n+4} u_{n+6}, \quad 1-u_{n+6+2 i} =u_{n-3-i} u_{n+4+2 i} u_{n+5+2 i} u_{n+8+2 i}~ {\rm for}~i=0,\dots,n-5;
-\eea
+\[
+1-u_{n+4} =u_{n} u_{n+2}u_{n+4} u_{n+6},
+1-u_{n+6+2 i} =u_{n-3-i} u_{n+4+2 i} u_{n+5+2 i} u_{n+8+2 i}~ {\rm for}~i=0,\dots,n-5;
+\]
 with the corresponding facets being $\mathscr{A}^{m}_1 \times \mathscr{X}_{n-m-1}$.
@@
  \bea
-I(\alpha') &=& \int_{0}^{\infty} \int_{0}^{\infty} \frac{dx}{x} ~\frac{dy}{y} \left( \frac{1}{x} + \frac{1}{y}+ x y \right)^{-\alpha' } \nonumber 
+I(\alpha') &=& \int_{0}^{\infty} \int_{0}^{\infty} \frac{\mathrm{d}x}{x} ~\frac{\mathrm{d}y}{y} \left( \frac{1}{x} + \frac{1}{y}+ x y \right)^{-\alpha' }. \nonumber 
 \eea 
@@
  \bea
-I(\alpha') &=& \int_{0}^{\infty} \int_{0}^{\frac{u^2}{4}} \frac{2 du ~ dv}{v \sqrt{u^2-4 v} }\left( \frac{u}{v} + v  \right)^{-\alpha'}= \frac{\Gamma{\left[\frac{\alpha'}{3}\right]^{3}}}{3 \Gamma{ \left[\alpha'\right]}} \nonumber
+I(\alpha') &=& \int_{0}^{\infty} \int_{0}^{\frac{u^2}{4}} \frac{2 \mathrm{d}u ~ \mathrm{d}v}{v \sqrt{u^2-4 v} }\left( \frac{u}{v} + v  \right)^{-\alpha'}= \frac{\Gamma{\left[\frac{\alpha'}{3}\right]^{3}}}{3 \Gamma{ \left[\alpha'\right]}}.
+\nonumber
 \eea
@@
 
-This is in fact a special class of a large class of integrals which all correspond to simplex case.
-By using the integral identity $\int_{{\mathbb R_{+}^{n}}} \prod_{i=1}^{n} \frac{d x_i }{x_i}~x_i^{a_i}  f\left(\sum_{i=1}^{n} x_i \right)   = \frac{\prod_{i=1}^n \Gamma{(a_i)}}{\Gamma{(\sum_{i=1}^n a_i)}} \int_{0}^{\infty} f(\beta) \beta^{\sum_{i=1}^{n} a_n -1} d\beta$, we can easily evaluate the following general integral for simplex:
+This is in fact a special class of a large class of integrals which all correspond to simplex case. By using the integral identity 
+\[\int_{{\mathbb R_{+}^{n}}} \prod_{i=1}^{n} \frac{\mathrm{d} x_i }{x_i}~x_i^{a_i}  f\left(\sum_{i=1}^{n} x_i \right)   = \frac{\prod_{i=1}^n \Gamma{(a_i)}}{\Gamma{(\sum_{i=1}^n a_i)}} \int_{0}^{\infty} f(\beta) \beta^{\sum_{i=1}^{n} a_n -1} \mathrm{d}\beta,
+\]
+we can easily evaluate the following general integral for simplex:
 \bea
-I(\alpha',~X_i,~c ) &=&  \int_{0}^{\infty} \cdots \int_{0}^{\infty} \prod_{i=1}^{n} ~dx_i ~x_i^{\alpha' X_i -1}  \left( b+\sum_{i=1}^n a_i x_i^{m_i} \right)^{-\alpha' c } \nonumber  \\
-&=& \frac{b^{\alpha' \left(\sum_{i=1}^n \frac{X_i}{m_i}-c \right) }}{(\prod_{i=1}^n m_i) (\prod_{i=1}^n a_i^{\alpha' X_i /m_i})} \int_{0}^{\infty} \cdots \int_{0}^{\infty} \prod_{i=1}^{n} ~dy_i ~y_i^{ \frac{\alpha' X_i}{m_i} -1}  \left( 1+\sum_{i=1}^n y_i \right)^{-\alpha' c } \nonumber  \\
-&=&\frac{b^{\alpha' \left(\sum_{i=1}^n \frac{X_i}{m_i}-c \right) }}{(\prod_{i=1}^n m_i) (\prod_{i=1}^n a_i^{\alpha' X_i /m_i})} B\left(\frac{ \alpha' X_1}{m_1},\dots,~\frac{ \alpha' X_n}{m_n}, ~ \alpha' \left(c- \sum_{i=1}^n \frac{X_i}{m_i} \right) \right) \nonumber \eea
+I(\alpha',~X_i,~c ) &=&  \int_{0}^{\infty} \cdots \int_{0}^{\infty} \prod_{i=1}^{n} ~\mathrm{d}x_i ~x_i^{\alpha' X_i -1}  \left( b+\sum_{i=1}^n a_i x_i^{m_i} \right)^{-\alpha' c } \nonumber  \\
+&=& \frac{b^{\alpha' \left(\sum_{i=1}^n \frac{X_i}{m_i}-c \right) }}{(\prod_{i=1}^n m_i) (\prod_{i=1}^n a_i^{\alpha' X_i /m_i})} \int_{0}^{\infty} \cdots \int_{0}^{\infty} \prod_{i=1}^{n} ~\mathrm{d}y_i ~y_i^{ \frac{\alpha' X_i}{m_i} -1}  \left( 1+\sum_{i=1}^n y_i \right)^{-\alpha' c } \nonumber  \\
+&=&\frac{b^{\alpha' \left(\sum_{i=1}^n \frac{X_i}{m_i}-c \right) }}{(\prod_{i=1}^n m_i) (\prod_{i=1}^n a_i^{\alpha' X_i /m_i})} B\left(\frac{ \alpha' X_1}{m_1},\dots,~\frac{ \alpha' X_n}{m_n}, ~ \alpha' \left(c- \sum_{i=1}^n \frac{X_i}{m_i} \right) \right).
+\nonumber \eea
 %More generally by interpreting the stringy integral \eqref{stringycanonicalform} as a Mellin transform it was shown in \cite{Mellin,Eulermellin} that the result of any stringy integral with linear factors i.e any generalized permutohedron is given by product of gamma functions of the facets of the Newton polytope times an entire function.
@@
 
-\section*{ Acknowledgements}
+\section*{Acknowledgements}
 We are grateful to Nima Arkani-Hamed, Thomas Lam, Hugh Thomas for stimulating discussions and collaborations on related projects.
@@
 \\
-Using the above result we construct a degeneration of  ${\mathscr P_n}$ which are the most general products i.e., $\prod_{p_i} X_{p_i}$ such that $\sum^{k}_{i=1} p_{i} = n$ by dividing the $(n+1)$ singlets into $k$ parts
+Using the above result we construct a degeneration of  ${\mathscr P_n}$ which are the most general products {\it i.e.}, $\prod_{p_i} X_{p_i}$ such that $\sum^{k}_{i=1} p_{i} = n$ by dividing the $(n+1)$ singlets into $k$ parts
 \[

### 2020-07-16 draft_ABP.tex
Updates from Overleaf

@@
 the number of facets of the big polyhedron or the original polytope $\mathcal P$,
-and inequalities $F_\alpha=S_J(V^{-1})^J_\alpha \geq 0$ are exactly the inequalities $W_a^J S_J\geq 0$ up to resales $F_\alpha \mapsto t F_\alpha$ for positive factors $t$, because
+and inequalities $F_\alpha=S_J(V^{-1})^J_\alpha \geq 0$ are exactly the inequalities $W_a^J S_J\geq 0$ up to rescaling $F_\alpha \mapsto t F_\alpha$ for positive factors $t$, because
 there's no nontrivial linear isometry from the simplex to itself besides permutations of vertices. Therefore, we identity the label of facets $\alpha$ with the label of 
@@
 Varieties defined by $u$ equations associated with finite type clusters  are called cluster configuration spaces.
-We see that when $u_\alpha$ (for a facet $\alpha$) goes to $0$, it forces all the $u_\beta$ with $\beta || \alpha>0$ goes to $1$ (for facets $\beta$ are exactly those {\it incompatible} with $\alpha$); the remaining $u$'s that are compatible with $u_\alpha$ satisfy $u$ equations for the facet, which factorizes as removing a node of the Dynkin diagram.
+We see that when $u_\alpha$ (for a facet $\alpha$) goes to $0$, it forces all the $u_\beta$ with $\beta || \alpha>0$ to go to $1$ (for facets $\beta$ are exactly those {\it incompatible} with $\alpha$); the remaining $u$'s that are compatible with $u_\alpha$ satisfy $u$ equations for the facet, which factorizes as removing a node of the Dynkin diagram.
 Therefore, we say that the configuration space is a {\it binary geometry}.
@@
 
-In this paper we introduce a large class of integrals,  ${\cal I}_{\bf B}$, which can be regarded as a family of rigid stringy canonical forms%~\cite{Arkani-Hamed:2019mrd} 
+In this paper we introduce a large class of integrals,  ${\cal I}_{\bf B}$, which can be regarded as a family of rigid stringy canonical forms %~\cite{Arkani-Hamed:2019mrd} 
 for generalized permutohedra ${\mathscr P}(\bf B)$, and we show that corresponding configuration spaces are always binary geometries.
